### 2021-03-15 reports/replication.Rmd
replicate gächter et al.s viz

---
title: "Gächter et al (2007, JPE) replication"
description: |
  A new article created using the Distill format.
author:
  - name: Hauke Roggenkamp 
    affiliation: CLICCS
    affiliation_url: https://www.cliccs.uni-hamburg.de/
date: "`r Sys.Date()`"
bibliography: biblio.bib
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: false
    code_folding: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(haven)
library(data.table)
library(magrittr)
library(kableExtra)
library(Rmisc)
library(ggplot2)
library(wesanderson)

DT <- read_dta(file="../data/gaechteretal/GMTV-data.dta") %>% data.table()
```

# Background

In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree]. The current demo version of the experiments can be found [here](https://cliccs.herokuapp.com/).^[Some of the demo experiments will model three-player games as this is the maximum number of players one can open in split-screen mode.] One of these experiments will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances) to allow for comparisons. I'll therefore run seesions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of 20 points and a group account with a return of $1.5$, such that:
$$
N_i^{t+1}=N-i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
$$

To this end, I aim to incorporate Gächter et al's data into my analysis.

# Data

## Original Data

The data can be found in the supplementary materials they provide in their [online appendix](https://www.sciencedirect.com/science/article/pii/S0047272717300361#s0115).

```{r data, include = FALSE}
noPunish10 <- DT[exp_num == 5 | exp_num == 8 | exp_num == 9]
```

Within the appendix, one also learns that the NOPUNISH 10-period data were collected in sessions 5, 8 and 9. Subsetting the data correspondingly yields a ```data.table``` consisting of 23 observations and $4 \times 10 \times 23=$ `r NROW(noPunish10)` rows and 27 variables.

For this purpose only a few variables are relevant:

- ```exp_num``` is a seesion identifier
- ```per``` denotes the period
- ```gr_id``` is a group identifier (carrying treatment information)
- ```subj_id``` is a subject indentifier
- ```tokens``` reports a subject's endowment in a period
- ```other[1-3]``` report the other group members' endowments in a period
- ```gdp ``` equals the sum of endowments of a group in a period
- ```putin``` reports a subject's contribution in a period
- ```pu[1-3]``` report the other group members' contributions in a period
- ```sum``` euqals the sum of contributions of a group in a period.

As a consequence, the first few rows of the data looks as follows and is quite intuitive:

```{r showData, layout = "l-body-outset"}
noPunish10[order(gr_id, per),
           .(exp_num, gr_id, per, subj_id, # IDs
             tokens, other1, other2, other3, gdp, #endowments
             putin, pu1, pu2, pu3, sum # contributions
             )] %>% 
  head(n = 9) %>%
  kbl() %>% 
  # scroll_box(height = "200px") %>%
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)

```

We see group 501 in the first two periods where subjects 511 to 514 start with an initial endowment of 20 which makes a GDP of 80. Subject 511 does not contribute (```putin==0``` in the first row and ```pu1==0```in rows 2 to 4) while the others contribute 5, 15 and 15 in the first period, respectively. The ```sum``` of contributions therefore equals 35 period 1.

With a sum of contributions being 35 and a return of contributions of $1.5$, each subject receives ```ceil(13.125)``` $=14$ points from the group project such that the next period's gdp equals $101$.

## Data Manipulation

To resemble the oTree data, the orginal data has to be transformed a little. therefore, variables will be renamed, variables (such as ```stock```[^Gächter et al called this variable _Wealth_] and ```gain```) will be created and, most notbaly, the unit of observations will be groups such that subject-level variables will be dropped.

```{r}

gaechter <- noPunish10[order(gr_id, per),
           .(treatment = "noPunish10", 
             groupID = gr_id, 
             round = per,
             contribution = sum,
             endowment = gdp,
             share = mean,
             stock = gdp + ceiling(sum/4*1.5)*4-sum,
             gain = ceiling(sum/4*1.5)*4-sum,
             bot_active = 0)] %>% unique()

gaechter %>%
  head(n = 12) %>%
  kbl() %>% 
  # scroll_box(height = "200px") %>%
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)
```

# Visualizations

```{r}
layout <- theme(panel.background = element_rect(fill = "white"),
                panel.grid = element_line(colour="gray", size=0),
                panel.grid.major.y = element_line(colour="gray", size=0.25),
                legend.key = element_rect(fill = "white"),
                axis.line.x.bottom = element_line(size = 0.25),
                axis.line.y.left = element_line(size = 0.25),
                plot.margin = unit(c(1,1,1,1), "cm"),
                legend.title = element_blank()
                )
```

```{r plotContribution}
plotDT <- summarySE(data = gaechter, 
                      measurevar = "contribution", 
                      groupvars=c("treatment", "round"),
                      na.rm = FALSE,
                      conf.interval = 0.95,
                      .drop = TRUE)

temp <- plotDT[, "contribution"]

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
    labs(y = "Average Amount of Points contributed") +
    scale_color_manual(values = wes_palette("Moonrise3", n = 1))
```

```{r plotShare}
plotDT <- summarySE(data = gaechter, 
                      measurevar = "share", 
                      groupvars=c("treatment", "round"),
                      na.rm = FALSE,
                      conf.interval = 0.95,
                      .drop = TRUE)

temp <- plotDT[, "share"]

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
    labs(y = "Share of Current Endowment contributed") +
    scale_color_manual(values = wes_palette("Moonrise3", n = 1))
```

```{r plotStock}
plotDT <- summarySE(data = gaechter, 
                      measurevar = "stock", 
                      groupvars=c("treatment", "round"),
                      na.rm = FALSE,
                      conf.interval = 0.95,
                      .drop = TRUE)

temp <- plotDT[, "stock"]

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
    labs(y = "Wealth") +
    scale_color_manual(values = wes_palette("Moonrise3", n = 1))
```

### 2021-03-15 analysis/R/config.R

@@ -3,11 +3,14 @@
 listOfPackages <- c("renv",          # package management
                     "rmarkdown",
                     "knitr",
+                    "distill",       # good looking HTML articles
+                    "kableExtra",    # HTML tables
+                    "tidyverse",     # many useful packages
+                    "haven",         # read dta data from stata
                     "glue",          # get some python-like string operations
-                    "stringr",       # working with strings
+                    # "stringr",       # working with strings included in tidyverse
                     "lubridate",     # working with dates
                     "plotly",        # interactive visualizations
-                    "ggplot2",       # static visualizations
                     "wesanderson",   # color palette
                     "highcharter",   # get nice viz
                     "Rmisc",         # Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
@@ -26,3 +29,4 @@ for(package in listOfPackages){
 }
 
 snapshot()
+# create_article("../reports/replication.Rmd")

### 2021-03-15 analysis/R/gaechteretal.R

@@ -1,0 +1,35 @@
+original <- read_dta(file="../data/gaechteretal/GMTV-data.dta") %>% data.table()
+
+# select no punish out of the first 10 sessions as subsequent sessions added further treatment variations
+original <- original[punish == 0 & exp_num <=10]
+
+# setnames(original,
+#          old = c("treat", "per", "gr_id", "sumputin", "tokens", "putin", "gdp"),
+#          new = c("treatment", "round", "groupID", "groupContribution", "endowment", "contribution", "groupEndowment"))
+
+longGaechter <- original[,
+                         .(treatment = treat,
+                           groupID = gr_id,
+                           round = per,
+                           contribution = sumputin/4,
+                           endowment = gdp/4,
+                           share = mean, # or sumputin/gdp
+                           stock = gdp - sumputin + sumputin * 1.5)] %>% unique()
+
+unique(original$gr_id) %>% length()
+
+original[,
+   .N,
+   by = gr_id]
+
+x <- original[gr_id == 501]
+x[,
+  debug := shift(gdp, n = -1, fill = NA, type = "lag")]
+x[,
+  gain := debug-gdp]
+x[,
+  efficiency := gain/sum]
+
+original <- original[order(gr_id, per)]
+x <- x[order(gr_id, per)]
+View(x)

### 2021-03-15 analysis/R/source.R

@@ -1,5 +1,6 @@
 rm(list = ls())
 
 source("R/config.R")
+source("R/gaechteretal.R")
 source("R/data.R")
 source("R/viz.R")

### 2021-03-15 analysis/R/viz.R

@@ -42,6 +42,7 @@ for(outcome in outcomes){
          height = 10, 
          units = "cm",
          bg = "transparent")
+  
   rm(list = c("plotTitle", "plot", "temp", "plotDT", "outcome"))
 }
 

### 2021-03-16 oTree/dPGG/models.py
adjust belief elicitation

@@ -32,7 +32,7 @@ class Constants(BaseConstants):
     safe_rounds = 2 # number of rounds without any risk
     threshold = 0.5 # fraction of a group's endowment that has to be contributed such that no disaster can occur
     belief_elicitation_round = 1
-    elicitation_bonus = 10 # points
+    elicitation_bonus = 30 # points
     timeout = 3 # minutes
     patience = 6 # minutes
     patience_bonus = 10 # points
@@ -147,16 +147,17 @@ class Group(BaseGroup):
 
             # add payoff if belief was correct
             if self.round_number == Constants.belief_elicitation_round:
-                others_average_contribution = (self.total_contribution - p.contribution) / Constants.num_others_per_group
+                others_contribution = (self.total_contribution - p.contribution)
                 # vars for Outro
-                p.participant.vars["correct_guess"] = False
-                p.participant.vars["others_average_contribution"] = others_average_contribution
+                p.participant.vars["guess"] = 0
+                p.participant.vars["others_average_contribution"] = others_contribution
                 p.participant.vars["belief"] = p.belief
                 p.participant.vars["belief_bonus"] = c(Constants.elicitation_bonus).to_real_world_currency(self.session)
                 # actual payoff operation
-                if p.belief > others_average_contribution * 0.9 and p.belief < others_average_contribution * 1.1:
-                    p.payoff = c(p.payoff + Constants.elicitation_bonus)
-                    p.participant.vars["correct_guess"] = True
+                guess = c(Constants.elicitation_bonus - abs(p.belief - others_contribution))
+                if guess >= 0:
+                    p.payoff = c(p.payoff + guess)
+                    p.participant.vars["guess"] = guess.to_real_world_currency(self.session)
 
 
 class Player(BasePlayer):

### 2021-03-16 oTree/dPGG/pages.py

@@ -12,6 +12,23 @@ class dPGG_InitialWaitPage(WaitPage):
             return True
 
 
+class dPGG_Belief(Page):
+    form_model = "player"
+    form_fields = ["review_instructions", "belief"]
+
+    def is_displayed(self):
+        if self.round_number == Constants.belief_elicitation_round:
+            return True
+
+    def js_vars(self):
+        return dict(
+            template="decision",
+            current_round=self.round_number,
+            endowments=self.participant.vars["endowments"],
+            num_rounds=self.session.config["num_rounds"],
+        )
+
+
 class dPGG_Decision(Page):
     form_model = "player"
     form_fields = ["review_instructions", "contribution"]
@@ -66,23 +83,6 @@ class dPGG_Decision(Page):
         )
 
 
-class dPGG_Belief(Page):
-    form_model = "player"
-    form_fields = ["review_instructions", "belief"]
-
-    def is_displayed(self):
-        if self.round_number == Constants.belief_elicitation_round:
-            return True
-
-    def js_vars(self):
-        return dict(
-            template="decision",
-            current_round=self.round_number,
-            endowments=self.participant.vars["endowments"],
-            num_rounds=self.session.config["num_rounds"],
-        )
-
-
 class ResultsWaitPage(WaitPage):
     def is_displayed(self):
         if self.round_number <= self.session.config["num_rounds"]:
@@ -94,7 +94,7 @@ class ResultsWaitPage(WaitPage):
 
 class dPGG_Results(Page):
     def is_displayed(self):
-        if self.round_number == self.session.config["num_rounds"]:
+        if self.round_number >= self.session.config["num_rounds"]:
             return True
 
     def vars_for_template(self):
@@ -119,7 +119,7 @@ class dPGG_Results(Page):
 
 
 page_sequence = [dPGG_InitialWaitPage,
-                 dPGG_Decision,
                  dPGG_Belief,
+                 dPGG_Decision,
                  ResultsWaitPage,
                  dPGG_Results]

### 2021-03-16 oTree/dPGG/models.py
fix drop_out bugs

@@ -35,7 +35,7 @@ class Constants(BaseConstants):
     elicitation_bonus = 30 # points
     timeout = 3 # minutes
     patience = 6 # minutes
-    patience_bonus = 10 # points
+    patience_bonus = 20 # points
 
 
 
@@ -59,6 +59,7 @@ class Subsession(BaseSubsession):
             player.wait_time_left = int(math.ceil(Constants.patience - (time.time() - player.participant.vars['wait_page_arrival']) / 60))
             if player.waiting_too_long():
                 player.participant.vars["is_residual_player"] = True
+                player.group.residual = True
                 # make a single-player group.
                 return [player]
 
@@ -66,6 +67,7 @@ class Subsession(BaseSubsession):
 
 class Group(BaseGroup):
 
+    residual = models.BooleanField(initial=False, doc="if true, group is incomplete")
     EWE = models.BooleanField(initial=False, doc="if true, extreme weather event occurred")
     disaster = models.BooleanField(initial=False, doc="if true, the EWE has negative effects on stock ")
     total_contribution = models.IntegerField(doc="sum of contributions in this round")
@@ -86,11 +88,12 @@ class Group(BaseGroup):
 
     def set_disaster(self):
         # random risk lottery
-        if self.round_number > Constants.safe_rounds:
-            if self.session.config["risk"] > random.uniform(0, 1):
-                self.EWE = True
-                if self.total_contribution < Constants.threshold * self.wealth:
-                    self.disaster = True
+        if not self.residual:
+            if self.round_number > Constants.safe_rounds:
+                if self.session.config["risk"] > random.uniform(0, 1):
+                    self.EWE = True
+                    if self.total_contribution < Constants.threshold * self.wealth:
+                        self.disaster = True
 
     def set_payoffs(self):
 
@@ -145,19 +148,19 @@ class Group(BaseGroup):
                     if not p.is_dropout == p.in_round(self.round_number - 1).is_dropout:
                         p.payoff = -p.endowment
 
-            # add payoff if belief was correct
-            if self.round_number == Constants.belief_elicitation_round:
-                others_contribution = (self.total_contribution - p.contribution)
-                # vars for Outro
-                p.participant.vars["guess"] = 0
-                p.participant.vars["others_average_contribution"] = others_contribution
-                p.participant.vars["belief"] = p.belief
-                p.participant.vars["belief_bonus"] = c(Constants.elicitation_bonus).to_real_world_currency(self.session)
-                # actual payoff operation
[…]

### 2021-04-06 oTree/settings.py
misc

@@ -8,14 +8,7 @@ SESSION_CONFIGS = [
         num_demo_participants=2,
         risk=0.0,
         app_sequence=["Intro", "dPGG", "Outro"]
-    ), dict(
-        name="risky_dPGG",
-        display_name="dPGG with risk & without instructions",
-        num_rounds=10,
-        num_demo_participants=4,
-        risk=0.33,
-        app_sequence=["dPGG", "Outro"]
-    ),
+    )
 ]
 
 # if you set a property in SESSION_CONFIG_DEFAULTS, it will be inherited by all configs

### 2021-04-06 reports/Mar21JourFixe.Rmd
misc

---
title: "Gächter et al (2007, JPE) replication"
description: |
  Reproducing Gächter et al.'s Visualizations.
author:
  - name: Hauke Roggenkamp 
    affiliation: CLICCS
    affiliation_url: https://www.cliccs.uni-hamburg.de/
date: "`r Sys.Date()`"
bibliography: biblio.bib
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: false
    code_folding: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(data.table)
library(tidyverse)
library(kableExtra)

library(Rmisc)
library(wesanderson)

base::load(file = "../data/processed/simulations.rda") 
base::load(file = "../data/processed/demoSession.rda") 
base::load(file = "../data/processed/gaechter2017.rda") 
```

# Background

In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), we plan to run a series of remote online experiments using oTree [@oTree]. One of these experiments will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances) to allow for comparisons.

# Replication

## Model

We'll therefore run sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of $N_i^1 = 20$ points $T=10$ periods, a private account with a return of $1$ and a group account with a return of $1.5$ ($\Rightarrow$ MPCR $= \frac{1.5}{4}$), such that:
$$
N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
$$
**Proposition 1:** Consider the public good game with growth as defined above. The unique SPE of the game is such that all players contribute 0 throughout the entire game (both on and off the equilibrium path).^[See @GACHTER2017's Appendix for a formal proof.]

## Data

The resulting data looks as follows. Each row represents a group, not a player. The displayed ```treatment``` names reflect the risk of extreme weather events as well as the share of current endowments contributed. ```Hi033``` indicates that the simulated subjects contributed a relatively high share of endowments facing a risk of 33 percent. In contrast, ```Lo000``` was parameterized such that there were no extreme weather events and contributions were relatively low. ```noPunish10``` represents @GACHTER2017's data from the no punish treatment with ten periods.^[The data were collected in sessions 5, 8 and 9 -- yielding 23 observations.]

The ```contribution``` shows a group's average contribution and the ```endowment``` their average endowment at the beginning of a period. The reported ```share``` is the fraction of both. ```stock``` is the group's average income at the end of the period and gain lists the difference between the ```stock``` and ```endowment```.

```{r combineData}
combined <- rbindlist(list(longDT[treatment == "Hi000"],# | treatment == "Lo000"], 
                           gaechter,
                           demoSession))

combined[treatment == "demoSession"] %>%
  # head(n = 9) %>%
  kbl() %>% 
  scroll_box(height = "400px") %>%
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)
```

```{r vizSetup, include = FALSE}
layout <- theme(panel.background = element_rect(fill = "white"),
                panel.grid = element_line(colour="gray", size=0),
                panel.grid.major.y = element_line(colour="gray", size=0.25),
                legend.key = element_rect(fill = "white"),
                axis.line.x.bottom = element_line(size = 0.25),
                axis.line.y.left = element_line(size = 0.25),
                plot.margin = unit(c(1,1,1,1), "cm"),
                legend.title = element_blank()
                )
```

## Visualization

The following graph displays the zero risk treatments together with @GACHTER2017's data. The original ```noPunish10``` data lies between both sets of simulations.

```{r plotShare}
plotDT <- summarySE(data = combined, 
                      measurevar = "share", 
                      groupvars=c("treatment", "round"),
                      na.rm = FALSE,
                      conf.interval = 0.95,
                      .drop = TRUE)

temp <- plotDT[, "share"]

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    scale_fill_manual(values = wes_palette("GrandBudapest1")) +
    scale_color_manual(values = wes_palette("GrandBudapest1")) +
    geom_errorbar(aes(ymin=temp-se, ymax=temp+se), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, 1)) +
    labs(y = "Share of Current Endowment contributed")
```

The different shares of contributions result in very different absolute contributions. The following graph illustrates the resulting heterogeneity between treatments.

```{r plotContribution}
plotDT <- summarySE(data = combined, 
                      measurevar = "contribution", 
                      groupvars=c("treatment", "round"),
                      na.rm = FALSE,
                      conf.interval = 0.95,
                      .drop = TRUE)

temp <- plotDT[, "contribution"]

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    scale_fill_manual(values = wes_palette("GrandBudapest1")) +
    scale_color_manual(values = wes_palette("GrandBudapest1")) +
    geom_errorbar(aes(ymin=temp-se, ymax=temp+se), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
    labs(y = "Average Amount of Points contributed")
```

Finally, one finds the same pattern in ```Wealth``` levels:

```{r plotStock}
plotDT <- summarySE(data = combined, 
                      measurevar = "stock", 
                      groupvars=c("treatment", "round"),
                      na.rm = FALSE,
                      conf.interval = 0.95,
                      .drop = TRUE)

temp <- plotDT[, "stock"]

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    scale_fill_manual(values = wes_palette("GrandBudapest1")) +
    scale_color_manual(values = wes_palette("GrandBudapest1")) +
    geom_errorbar(aes(ymin=temp-se, ymax=temp+se), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
    labs(y = "Wealth")
```

# Incorporating Risk or Uncertainty

The basic idea is that, in every period, there is a (known or unknown)^[TBD] constant probability of an extreme weather event (EWE) occurring in a group denoted by $r=prob(\text{EWE}=1)$. Such an extreme weather event can bring about some endogenous damage $D$. The question we are discussing is what $D$ should look like.

We can either model $D$ as some weighted punishment, that is: 
$$
N_i^{t+1}=
\begin{cases}
N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t, & \text{if EWE}=0 \\
N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t - D \Big(1-\frac{\sum_{j=1}^4 c_j^t}{\sum_{j=1}^4 N_j^t}\Big) & \text{else}
\end{cases}
$$

or as a weight itself:
$$
N_i^{t+1}=
\begin{cases}
N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t, & \text{if EWE}=0 \\
\Big(N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t\Big) \cdot \frac{\sum_{j=1}^4 c_j^t}{\sum_{j=1}^4 N_j^t}, & \text{else}
\end{cases}
$$

We can also model it entirely different (suggestions?). The most important consideration is that we have to find a $D$ and $r$ such that, given the original group size of 4, the corresponding MPCR $=\frac{1.5}{4}$ and $0 \leq c_i^t \leq N_i^t \leq\sum_{j=1}^4 N_j^t$, the game remains characterized as a dilemma where individual and collective interest are in conflict.

### 2021-04-06 reports/constantDamage.Rmd
misc

---
title: "Gächter et al (2007, JPE) replication"
description: |
  Reproducing Gächter et al.'s Visualizations.
author:
  - name: Hauke Roggenkamp 
    affiliation: CLICCS
    affiliation_url: https://www.cliccs.uni-hamburg.de/
date: "`r Sys.Date()`"
bibliography: biblio.bib
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: false
    code_folding: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Background

In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), we plan to run a series of remote online experiments using oTree [@oTree]. One of these experiments will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances) to allow for comparisons.

# Replication

We'll therefore run sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of $N_i^1 = 20$ points $T=10$ rounds, a private account with a return of $1$ and a group account with a return of $1.5$ ($\Rightarrow$ MPCR$\equiv \frac{1.5}{4}$), such that:
$$
N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
$$
**Proposition 1:** Consider the public good game with growth as defined above. The unique SPE of the game is such that all players contribute 0 throughout the entire game (both on and off the equilibrium path).^[See @GACHTER2017's Appendix for a formal proof.]

# Incorporating Risk or Uncertainty

The basic idea is that, in every period, there is a (known or unknown)^[TBD] constant probability of an extreme weather event occurring in a group denoted by $r \equiv \frac{5}{16}=31.25$%. Such an extreme weather event can bring about damage $D$. This damage will, however, only occur if the group's contributions are smaller than a threshold $X$, which is half of their endowment, i.e. if:

$$
\sum_{j=1}^4 c_j^t < \frac{1}{2} \sum_{j=1}^4 E_j^t \equiv X
$$
As a consequence, the _expected_ earnings look as follows

$$
N_i^t=
\begin{cases}
N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t, & \text{if}\ \sum_{j=1}^4 c_j^t \geq \frac{1}{2} \sum_{j=1}^4 E_j^t\\
N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t -rD, & \text{else}
\end{cases}
$$

With $D=0$ the game collapses to @GACHTER2017's model. The first derivative yields $-1$ implying that the individually rational contribution $c_{FC}^t=0$. 
If $A=4$ denotes the number of players and $C^t$ the aggregate contribution with $C^t=\sum_{j=1}^{A}c_j^t$, the aggregate payoff with $D=0$ is described by:

\begin{align}
\sum_{j=1}^{A}N_j^{t+1} & =\sum_{j=1}^{A}N_j^t - C^t + A \cdot \frac{1.5}{4} \cdot C^t\\
&=\sum_{j=1}^{A}N_j^t + C^t(4 \cdot \frac{1.5}{4} - 1) \\
&=\sum_{j=1}^{A}N_j^t + \frac{C^t}{2}
\end{align}

The collectively rational (that is, the efficient) contribution is $C_{FC}^t=\sum_{j=1}^{A}N_j^t$ because the first derivative is strictly positive.

As a consequence, the game is a dilemma where the individual and collective interest are in conflict.

Incorporating $D>0$, we want the game to remain a dilemma in which and observe whether positive contributions evolve despite contrasting incentives. As a consequence, we have to set $D$ such that freeriding ($c_i^t=0$ for all $i$) and risking to suffer that damage (LHS) remains more attractive than any contribution ($\bar c^t \geq \frac{\bar{N}^t}{2}$) that leads to damage control (RHS).

\begin{align}
N_i^t rD &> N_i^t - \bar{c}^t + A \cdot \frac{1.5}{4} \bar{c}^t \\
N_i^t (rD-1) &> \frac{\bar{c}^t}{2}
\end{align}

## The last period

There are two cases where $i$'s contribution is not pivotal, that is, where the threshold $X$ is (not) reached no matter $i$'s action. If $\sum_{j \neq i}^4 c_j^t \geq X$, the other group members' contributions are large enough to prevent damage. $i$ therefore faces the strategic environment of a regular public goods game where freeriding ($c_i^t=0$) is her best response. If $\sum_{j \neq i}^4 c_j^t + E_i^t < X$, $i$'s endowment is too small to prevent the damage in case of an extreme weather event. She can then just as well give up and freeride with ($c_i^t=0$) to maximize her payoff.

But what is the best thing to do in those cases, where $i$'s contribution can make a difference in damage control, that is, where $\sum_{j \neq i}^4 c_j^t < X < \sum_{j \neq i}^4 c_j^t + E_i^t$? In these cases, $i$ can contribute anything in  between $0 \leq c_i^t \leq X-\sum_{j \neq i}^4 c_j^t$ (the upper limit is the bare minimum required to prevent damages.

But how much is $i$ actually willing to contribute? $i$ will contribute as long as her earnings from these contributions with successful damage control (LHS) are larger than her reduced earnings from $c_i^t=0$ with expected damage (RHS).

\begin{align}
N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t & \geq 
 N_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t-rD\\

N_i^t - c_i^t \Big(1-\frac{1.5}{4}\Big) + \frac{1.5}{4}\sum_{j\neq i}^4 c_j^t & \geq 
 N_i^t + \frac{1.5}{4}\sum_{j\neq i}^4 c_j^t-rD\\

- c_i^t\Big(1-\frac{1.5}{4}\Big) & \geq -rD\\

c_i^t & \leq \frac{rD}{1-\frac{1.5}{4}}\\

c_i^t & \leq \frac{D}{2} \; \text{ with }r=\frac{5}{16}\\ 
\end{align}

There are two things to note. First and unsurprisingly, the maximal contribution increases in risk and Damage. Second and given the MPCR and the (indeed artificial) risk level, the maximum amount any player would contribute is half the damage they would have suffered due to an extreme weather event if they had not reached the threshold. It is important to remember that they only make that contribution if their contribution is pivotal in controlling the damage.

Because the game is symmetrical and because it requires every player to contribute at least half of her endowment to control the damage, there is a Nash equilibrium where each player contributes $c_i^t = \frac{1}{2} N_i^t$ if $D_i^t \geq N_i^t$.

If players cannot make any debt (limited liability), the damage cannot be larger than their endowment. In that case, the players are indifferent in contributing nothing or exactly half of their endowments. If the risk was larger than $31.25$%, positive contributions (that is $c_i^t = \frac{1}{2} N_i^t$) become more likely in the last round.

### 2021-04-06 reports/replication.Rmd
misc

@@
 description: |
-  A new article created using the Distill format.
+  Reproducing Gächter et al.'s Visualizations.
 author:
@@
 The current demo version of the experiments can be found [here](https://cliccs.herokuapp.com/).^[Some of the demo experiments will model three-player games as this is the maximum number of players one can open in split-screen mode.] One of these experiments will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances) to allow for comparisons.
-I'll therefore run seesions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of 20 points and a group account with a return of $1.5$, such that:
+I'll therefore run sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of 20 points and a group account with a return of $1.5$, such that:
 $$
-N_i^{t+1}=N-i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
+N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
 $$
@@
 
-```{r}
+```{r writeData}
 
@@
              round = per,
-             contribution = sum,
-             endowment = gdp,
+             contribution = sum/4,
+             endowment = gdp/4,
              share = mean,
-             stock = gdp + ceiling(sum/4*1.5)*4-sum,
-             gain = ceiling(sum/4*1.5)*4-sum,
-             bot_active = 0)] %>% unique()
+             stock = (gdp + ceiling(sum/4*1.5)*4-sum)/4,
+             gain = (ceiling(sum/4*1.5)*4-sum)/4,
+             bot_active = 0,
+             disaster = 0,
+             EWE = 0,
+             noComprehension = 0)] %>% unique()
 
@@
               fixed_thead = TRUE)
+
+save(gaechter, file = "../data/processed/gaechter2017.rda")
+write.csv(gaechter, file ="../data/processed/gaechter2017.csv")
+
 ```

### 2021-04-06 analysis/R/config.R

@@ -8,14 +8,13 @@ listOfPackages <- c("renv",          # package management
                     "tidyverse",     # many useful packages
                     "haven",         # read dta data from stata
                     "glue",          # get some python-like string operations
-                    # "stringr",       # working with strings included in tidyverse
                     "lubridate",     # working with dates
                     "plotly",        # interactive visualizations
                     "wesanderson",   # color palette
                     "highcharter",   # get nice viz
                     "Rmisc",         # Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
                     "data.table",
-                    "magrittr"       # get %>% and %<>% opeartors
+                    "magrittr"       # get %>% and %<>% operators
                     )
 
 newPackages <- listOfPackages[!(listOfPackages %in% installed.packages()[, "Package"])]
@@ -28,5 +27,4 @@ for(package in listOfPackages){
   require(package, character.only = TRUE)
 }
 
-snapshot()
-# create_article("../reports/replication.Rmd")
+# snapshot()

### 2021-04-06 analysis/R/data.R

@@ -1,18 +1,22 @@
-# read raw data
-sim1 <- read.csv("../data/simulation/jawroz7g.csv", stringsAsFactors = FALSE) %>% data.table()
-sim2 <- read.csv("../data/simulation/etvc9q2x.csv", stringsAsFactors = FALSE) %>% data.table()
-
-
-# pretend we had a treatment
-sim1[, session.code := "control"]
-sim2[, session.code := "treatment"]
-
-dt <- rbindlist(list(sim1, sim2),
-                use.names = FALSE)
+# # read raw data
+# Lo000 <- read.csv("../data/simulation/Lo000.csv", stringsAsFactors = FALSE) %>% data.table()
+# Hi000 <- read.csv("../data/simulation/Hi000.csv", stringsAsFactors = FALSE) %>% data.table()
+# Lo033 <- read.csv("../data/simulation/Lo033.csv", stringsAsFactors = FALSE) %>% data.table()
+# Hi033 <- read.csv("../data/simulation/Hi033.csv", stringsAsFactors = FALSE) %>% data.table()
+# 
+# 
+# # pretend we had a treatment
+# Lo000[, session.code := "Lo000"]
+# Hi000[, session.code := "Hi000"]
+# Lo033[, session.code := "Lo033"]
+# Hi033[, session.code := "Hi033"]
+# 
+# dt <- rbindlist(list(Lo000, Hi000, Lo033, Hi033),
+#                 use.names = FALSE)
 
 # or use the data gathered in a demo session
-# dt <- read.csv("../data/demoSessions/all_apps_wide-2021-03-09.csv", stringsAsFactors = FALSE) %>% data.table()
-# dt <- dt[, session.code := "demoSession"]
+dt <- read.csv("../data/demoSessions/all_apps_wide-2021-03-25.csv", stringsAsFactors = FALSE) %>% data.table()
+dt <- dt[, session.code := "demoSession"]
 
 # control variables
 cRegex <- "participant\\.code$|participant\\..time_started|session\\.code$|_index_in_pages|Intro\\.1\\.player\\.window.*|Intro\\.1\\.player\\.browser|participant\\.payoff$|^Outro"
@@ -22,11 +26,17 @@ ct <- dt[, ..controlVariables]
 
 
 # main data frame
-mRegex <- "participant\\.code$|participant\\.time_started|session\\.code$|dPGG\\.1\\.group\\.id_in_subsession|\\.1\\.player.belief|endowment|contribution|stock|gain$|bot_active|EWE|disaster"
[…]

### 2021-04-06 analysis/R/gaechteretal.R

@@ -1,35 +1,1 @@
-original <- read_dta(file="../data/gaechteretal/GMTV-data.dta") %>% data.table()
-
-# select no punish out of the first 10 sessions as subsequent sessions added further treatment variations
-original <- original[punish == 0 & exp_num <=10]
-
-# setnames(original,
-#          old = c("treat", "per", "gr_id", "sumputin", "tokens", "putin", "gdp"),
-#          new = c("treatment", "round", "groupID", "groupContribution", "endowment", "contribution", "groupEndowment"))
-
-longGaechter <- original[,
-                         .(treatment = treat,
-                           groupID = gr_id,
-                           round = per,
-                           contribution = sumputin/4,
-                           endowment = gdp/4,
-                           share = mean, # or sumputin/gdp
-                           stock = gdp - sumputin + sumputin * 1.5)] %>% unique()
-
-unique(original$gr_id) %>% length()
-
-original[,
-   .N,
-   by = gr_id]
-
-x <- original[gr_id == 501]
-x[,
-  debug := shift(gdp, n = -1, fill = NA, type = "lag")]
-x[,
-  gain := debug-gdp]
-x[,
-  efficiency := gain/sum]
-
-original <- original[order(gr_id, per)]
-x <- x[order(gr_id, per)]
-View(x)
+rmarkdown::render("../reports/replication.Rmd")

### 2021-04-06 analysis/R/source.R

@@ -1,6 +1,8 @@
 rm(list = ls())
 
 source("R/config.R")
-# source("R/gaechteretal.R")
-source("R/data.R", echo = TRUE)
+source("R/data.R")
+source("R/gaechteretal.R", echo = TRUE)
 source("R/viz.R")
+
+# create_article("../reports/Mar21JourFixe.Rmd")

### 2021-04-06 analysis/R/viz.R

@@ -1,3 +1,10 @@
+# Load Data -----
+base::load(file = "../data/processed/simulations.rda") 
+base::load(file = "../data/processed/gaechter2017.rda") 
+
+# run Markdown files -----
+rmarkdown::render("../reports/simulations.Rmd")
+
 # Themes -----
 layout <- theme(panel.background = element_rect(fill = "white"),
                 panel.grid = element_line(colour="gray", size=0),
@@ -22,17 +29,16 @@ for(outcome in outcomes){
                       .drop = TRUE)
   
   temp <- plotDT[, outcome]
-
+  
   # plot
   plot <- ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + # linetype = treatment
     layout +
     geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
     geom_line() +
     # geom_point() + 
-    scale_x_continuous(name="Period",  breaks = 1:15) +
+    scale_x_continuous(name="Period",  breaks = 1:10, limits = c(1, 10.5)) +
     scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
-    labs(y = outcome %>% str_to_title()) +
-    scale_color_manual(values = wes_palette("Moonrise3", n = 2))
+    labs(y = outcome %>% str_to_title())
 
   plotTitle <- glue("plot{str_to_title(outcome)}")
   # assign(x = plotTitle,

### 2021-04-10 reports/01_replication.Rmd
update report structure

---
title: "1. Original Data"
description: |
  Reproducing Gächter et al.'s main findings.
author:
  - name: Hauke Roggenkamp 
    url: https://github.com/Howquez
    affiliation: CLICCS
    affiliation_url: https://www.cliccs.uni-hamburg.de/
date: "`r Sys.Date()`"
bibliography: biblio.bib
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: false
    code_folding: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(haven)
library(data.table)
library(magrittr)
library(kableExtra)
library(DescTools) # gini coefficient
library(downloadthis)
library(Rmisc)
library(ggplot2)
library(wesanderson)

DT <- read_dta(file="../data/gaechteretal/GMTV-data.dta") %>% data.table()
```

# Background

In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree]. The first experiment will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances). The current demo version of the experiment can be found [here](https://cliccs.herokuapp.com/). Click [here](https://github.com/Howquez/coopUncertainty) to visit the corresponding Github repository.

This report is the first in a series of reports covering this project. It prepares the original data and replicates main visualizations & tables.

# Original Data

The data can be found in the supplementary materials they provide in their [online appendix](https://www.sciencedirect.com/science/article/pii/S0047272717300361#s0115).

```{r data, include = FALSE}
noPunish10 <- DT[exp_num == 5 | exp_num == 8 | exp_num == 9]
```

Within the appendix, one also learns that the NOPUNISH 10-period data were collected in sessions 5, 8 and 9. Subsetting the data correspondingly yields a ```data.table``` consisting of 23 observations and $4 \times 10 \times 23=$ `r NROW(noPunish10)` rows and 27 variables.

For this purpose only a few variables are relevant:

- ```exp_num``` is a session identifier
- ```per``` denotes the period
- ```gr_id``` is a group identifier (carrying treatment information)
- ```subj_id``` is a subject identifier
- ```tokens``` reports a subject's endowment in a period
- ```other[1-3]``` report the other group members' endowments in a period
- ```gdp ``` equals the sum of endowments of a group in a period
- ```putin``` reports a subject's contribution in a period
- ```pu[1-3]``` report the other group members' contributions in a period
- ```sum``` equals the sum of contributions of a group in a period.
- ```gini``` reports a group's Gini coefficient in a period.
- ```mean``` reports the fraction of sum/gdp -- but only in some cases.

As a consequence, the first few rows of the data look as follows:

```{r showData, layout = "l-body-outset"}
noPunish10[,
           gini2 := Gini(c(tokens, other1, other2, other3)),
           by = .(subj_id, per)]

noPunish10[order(gr_id, per),
           .(exp_num, gr_id, per, subj_id, # IDs
             tokens, other1, other2, other3, gdp, #endowments
             putin, pu1, pu2, pu3, sum, mean, # contributions
             gini, gini2
           )] %>% 
  head(n = 15) %>%
  kbl() %>% 
  # scroll_box(height = "200px") %>%
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)

```

We see group 501 in the first two periods where subjects 511 to 514 start with an initial endowment of 20 which makes a GDP of 80. Subject 511 does not contribute (as represented in ```putin==0``` in the first row and ```pu1==0```in rows 2 to 4) while the others contribute 5, 15 and 15 in the first period, respectively. The ```sum``` of contributions therefore equals 35 period 1.

With a sum of contributions being 35 and a return of contributions of 1.5, each subject receives ```ceil(13.125)``` =14 points from the group project such that the next period's ```gdp``` equals 101.

Unfortunately, the Gini coefficient (```gini```) is a little off as one can see in the second period: Even though this is a group level variable, the group has three different coefficient in the same period. For this reason, I re-calculated the coefficient and called it ```gini2```.

# Data Manipulation

To resemble the oTree data, the original data has to be transformed a little. Therefore, some variables will be renamed, variables (such as ```stock```^[Gächter et al. called this variable _Wealth_] and ```gain```) will be created and, most notably, the unit of observations will be groups such that subject-level variables will be dropped.^[In addition, I will ignore the original Gini coefficient and use mine instead.]

```{r writeData}

noPunish10[,
           share := sum/gdp,
           by = .(subj_id, per)]

gaechter <- noPunish10[order(gr_id, per),
           .(treatment = "noPunish10", 
             session.code = exp_num,
             groupID = gr_id, 
             round = per,
             contribution = sum,
             endowment = gdp,
             share = mean, # share,
             stock = (gdp + ceiling(sum/4*1.5)*4-sum),
             gain = (ceiling(sum/4*1.5)*4-sum),
             gini = gini2,
             bot_active = 0,
             # disaster = 0,
             # EWE = 0,
             noComprehension = 0)] %>% unique()

gaechter %>%
  head(n = 15) %>%
  kbl() %>% 
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)

save(gaechter, file = "../data/processed/rda/gaechter2017.rda")
write.csv(gaechter, file ="../data/processed/csv/gaechter2017.csv")

```

```{r downloadData}
gaechter %>%
      download_this(
        output_name = "Gaechter2017noPunish10",
        output_extension = ".csv", # CSV output
        button_label = "Download csv",
        button_type = "default"
        )
```

# Visualizations

```{r}
layout <- theme(panel.background = element_rect(fill = "white"),
                panel.grid = element_line(colour="gray", size=0),
                panel.grid.major.y = element_line(colour="gray", size=0.25),
                legend.key = element_rect(fill = "white"),
                axis.line.x.bottom = element_line(size = 0.25),
                axis.line.y.left = element_line(size = 0.25),
                plot.margin = unit(c(1,1,1,1), "cm"),
                legend.title = element_blank()
                )
```

```{r plotContribution}
plotDT <- summarySE(data = gaechter, 
                      measurevar = "contribution", 
                      groupvars=c("treatment", "round"),
                      na.rm = FALSE,
                      conf.interval = 0.95,
                      .drop = TRUE)

temp <- plotDT[, "contribution"]

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, 150)) +
    labs(y = "Average Amount of Points contributed") +
    scale_color_manual(values = wes_palette("Moonrise3"))
```

```{r plotShare}
plotDT <- summarySE(data = gaechter, 
                      measurevar = "share", 
                      groupvars=c("treatment", "round"),
                      na.rm = FALSE,
                      conf.interval = 0.95,
                      .drop = TRUE)

temp <- plotDT[, "share"]

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, 1)) +
    labs(y = "Share of Current Endowment contributed") +
    scale_color_manual(values = wes_palette("Moonrise3"))
```

```{r plotStock}
plotDT <- summarySE(data = gaechter, 
                      measurevar = "stock", 
                      groupvars=c("treatment", "round"),
                      na.rm = FALSE,
                      conf.interval = 0.95,
                      .drop = TRUE)

temp <- plotDT[, "stock"]

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
    labs(y = "Wealth") +
    scale_color_manual(values = wes_palette("Moonrise3"))
```

```{r plotGini}
plotDT <- summarySE(data = gaechter, 
                      measurevar = "gini", 
                      groupvars=c("treatment", "round"),
                      na.rm = FALSE,
                      conf.interval = 0.95,
                      .drop = TRUE)

temp <- plotDT[, "gini"]

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, 0.4)) +
    labs(y = "Gini coefficient") +
    scale_color_manual(values = wes_palette("Moonrise3"))
```

# Tables

```{r regressions}
# reg gdp punish if longgame==0  & treat<3 & per==10, cluster(gr_id)
lm(gdp ~ punish, data = DT[longgame==0 & treat < 3 & per==10])
```

# Discussion

Even though the figures above were created using the original data, they do not look the same as the original figures. This becomes obvious if one looks at the figures that visualize the contributions. The arising question therefore is whether I made a mistake in processing and interpreting the data. After all I thought to have found wrong Gini coefficients and struggle to interpret the ```mean``` of the original data.

# First round

Eventually, we'll also be interested in the participants' first round's behavior, as it indicates their willingness to cooperate before they interact with one another. As a consequence, we can compare all noPunish sessions, regardless of whether they ran for 10 or 15 rounds.

```{r firstRound}
noPunish <- DT[exp_num == 1 | exp_num == 3 | # noPunish15
                 exp_num == 5 | exp_num == 8 | exp_num == 9] # noPunish10

temp <- noPunish[per == 1]
temp <- temp[,
             treatment := "noPunish10"]
temp <- temp[exp_num == 1 | exp_num == 3,
             treatment := "noPunish15"]

gaechterFirstRound <- temp[,
                           .(participant.code = subj_id,
                             treatment,
                             session.code = exp_num,
                             groupID = gr_id,
                             belief = NA,
                             othersContribution = sumputin - putin,
                             ownContribution = putin,
                             fairness = NA,
                             trust = NA,
                             comprehension = NA)]

rm(list = c("temp"))

# save data
fileName <- "gaechter2017"
save(gaechterFirstRound, 
     file = paste0("../data/processed/rda/", fileName, "_R1", ".rda"))
write.csv(gaechterFirstRound, 
          file = paste0("../data/processed/csv/", fileName, "_R1", ".csv"))
```

`r NROW(gaechterFirstRound)` participants yield `r NROW(gaechterFirstRound)` independent observations that are stored in a data table called ```gaechterFirstRound```. These observations are displayed below and can, once more, be downloaded by a click on the button. As before, the data is also saved in ```../data/processed/```.

```{r displayFirstRound}
# display data
gaechterFirstRound %>%
  head(n = 15) %>%
  kbl() %>% 
  # scroll_box(height = "200px") %>%
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)

# create download button
gaechterFirstRound %>%
      download_this(
        output_name = "gaechter2017_R1",
        output_extension = ".csv", # CSV output
        button_label = "Download csv",
        button_type = "default"
        )
```

# Outlook

Having replicated Gaechter et al.'s main figures (more or less) the next step is to prepare the data we obtain in our experiment for the analysis. This will be done in the second report using simulated data.^[Eventually, one can use that report and apply it to the actual data.]

### 2021-04-10 reports/02_dataProcessing.Rmd
update report structure

---
title: "2. Simulated Data"
description: |
  Making the raw oTree output tangible.
author:
  - name: Hauke Roggenkamp 
    url: https://github.com/Howquez
    affiliation: CLICCS
    affiliation_url: https://www.cliccs.uni-hamburg.de/
date: "`r Sys.Date()`"
bibliography: biblio.bib
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: false
    code_folding: true
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = FALSE)
library(data.table)
library(magrittr)
library(stringr)
library(glue)
library(DescTools) # gini coefficient
library(kableExtra)
library(downloadthis)
```

# Background

In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree]. The first experiment will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances). The current demo version of the experiment can be found [here](https://cliccs.herokuapp.com/). Click [here](https://github.com/Howquez/coopUncertainty) to visit the corresponding Github repository.

This report is the second in a series of reports covering this project. It explains how simulated data is processed and prepared for analyses.

# Simulations

```{r loadData}
# read simulated data
DT <- read.csv("../data/simulation/all_apps_wide.csv", stringsAsFactors = FALSE) %>%
  data.table()
```

I simulated `r NROW(DT)` participants. To do so, I wrote oTree bots that follow rather simple rules and act mostly random. As a consequence, this data yields no information apart from the structure of the data itself.

Eventually, this report can also be used to process real data. This only requires us to load a different data set.^[It may also require us to merge multiple data sets -- that depends on whether the lab delivers one or several data sets and remains to be discussed.]

## First round

Eventually, we'll be interested in the participants' first round's behavior, as it indicates their willingness to cooperate before they interact with one another. As a consequence, `r NROW(DT)` participants yield `r NROW(DT)` observations that shall be stored in a data table called ```replicationFirstRound```. This table carries information on a participant's ```belief``` about the sum of other group members' contributions, their actual contribution ```othersContribution```, the participant's ```ownContribution```, some fairness measure that equals the difference between the own contribution and the expected average contribution of others and a trust measure^["Generally, others can be trusted". Likert scale ranging from 0 (do not agree) to 6 (agree).] obtained from the personality test at the end of the experiment.

```{r firstRound}
# create data table 
replicationFirstRound <- DT[,
                 .(participant.code,
                   treatment = "replication",
                   session.code,
                   groupID = dPGG.1.group.id_in_subsession,
                   belief = dPGG.1.player.belief,
                   othersContribution = dPGG.1.group.total_contribution - dPGG.1.player.contribution,
                   ownContribution = dPGG.1.player.contribution,
                   fairness = dPGG.1.player.contribution - dPGG.1.player.belief/3,
                   trust = Outro.1.player.PQ11,
                   comprehension = Outro.1.player.Comprehension)]

# save data
fileName <- "replication2021"
save(replicationFirstRound, file = paste0("../data/processed/rda/", fileName, "_R1", ".rda"))
write.csv(replicationFirstRound, file = paste0("../data/processed/csv/", fileName, "_R1", ".csv"))

# display data
replicationFirstRound %>%
  head(n = 12) %>%
  kbl() %>% 
  # scroll_box(height = "200px") %>%
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)

# create download button
replicationFirstRound %>%
      download_this(
        output_name = glue("{Sys.Date()}_Simulation_firstRound"),
        output_extension = ".csv", # CSV output
        button_label = "Download csv",
        button_type = "default"
        )
```

The data is saved in two formats (```csv``` and ```rda```) in ```../data/processed/```. If you have not downloaded the repository and access the html file, you can also obtain a csv-file by clicking on the button above.

## All rounds

Because we are most interested in the dynamics of the game, the most important data frame shall reflect the interactions within groups over time. I'll subset the data using a regular expression such that one obtains the initial belief as well as endowments, contributions, gains and stocks for each individual (preliminarily).^[There will also be information on the respondent's self stated comprehension of the task as well as a dummy indicating whether a bot was active (which implies that some group member dropped out.)] ^[In addition the data table contains a ```participant.code```, a ```session.code``` as well as some group and individual ID for identification and merging purposes.]

```{r subsetData}

# most relevant variables
mRegex <- "participant\\.code$|session\\.code$|dPGG\\.1\\.group\\.id_in_subsession|^dPGG.1.player.id_in_group$|\\.1\\.player.belief|endowment|contribution|stock|gain$|bot_active|Comprehension"
mainVariables <- str_subset(string = names(DT),
                            pattern = mRegex)
subset <- DT[, ..mainVariables]
```

Because the the endowments are dynamic, the contributions may vary within and across groups. For this reason, a ```share``` (reporting the share of a respondent's current endowment contributed) is calculated. The first few rows of the data table look as follows:

```{r newVars}

# refactor groupID such that it also contains treatment-info
subset[,
   groupID := paste(session.code, dPGG.1.group.id_in_subsession, 
                    sep = "_")]

# add share as contribution/endowment
for(round in 1:15){
  contribution <- glue("dPGG.{round}.player.contribution")
  endowment <- glue("dPGG.{round}.player.endowment")
  subset[, glue("dPGG.{round}.player.share") := subset[[contribution]]/subset[[endowment]] ]
}

# add treatment variable
subset[,
       treatment := "replication"]

# display data
subset %>%
  head(n = 12) %>%
  kbl() %>% 
  scroll_box(width = "100%") %>%
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)
```

To obtain a long (instead of a wide) table that reports these variables for independent observations over time, the data hast be be transformed and aggregated. Instead of listing individuals, it shall list groups over time.^[These steps are eliminating lots of information. If one desires an extensive data table containing individual- and group-level information over time, one can merge the resulting table with the small grained data.]

This process takes a few steps:

```{r calcAverages}
cluster <- c("treatment", "session.code", "groupID")
outcomes <- c("contribution", "endowment", "share", "stock", "gain", "bot_active")
# outcome = "contribution"
DTs <- list()
for(outcome in outcomes){
  if(outcome == "bot_active"){
    var = names(subset) %>% str_subset(pattern = glue("group\\.{outcome}$"))
  } else {
    var = names(subset) %>% str_subset(pattern = glue("player\\.{outcome}$"))
  }

  # calculate either averages or the sum per round per group
  if(outcome == "share"){
    aggregates = subset[, 
                lapply(.SD, mean, na.rm=TRUE), 
                by = cluster, 
                .SDcols=var
                ]
  } else {
    aggregates = subset[, 
                lapply(.SD, sum, na.rm=TRUE), 
                by = cluster, 
                .SDcols=var
                ]
  }

  # transform from wide to long
  meltedAggregates <- melt(aggregates, id.vars = cluster, measure.vars = var)
  DTname <- glue("{str_to_title(outcome)}")
  DTs[[DTname]] <- meltedAggregates
  rm(list = c("DTname", "meltedAggregates", "aggregates", "var", "outcome"))
}
```

```{r renameVars}
for(i in 1:length(outcomes)){
  DTs[[i]] <- DTs[[i]][,
                       .(treatment,
                         session.code,
                         groupID,
                         round = str_replace_all(string = variable,
                                                 pattern = "\\D", 
                                                 replacement="") %>% as.integer(),
                         value # to be renamed afterwards
                       )
  ]
  # rename "value" to outcome variable
  setnames(DTs[[i]], old = "value", new = outcomes[i])
}
```

Also, the Gini coefficient has to be calculated to measure inequality within groups.

```{r calcGini}
# it would make more sense to calculate the stocks' gini but gaechter et al use the endowments
var = names(subset) %>% str_subset(pattern = "player\\.endowment$")
gini = subset[,
              lapply(.SD, Gini, na.rm=TRUE), 
                by = cluster, 
                .SDcols=var
              ]
Gini <- melt(gini, id.vars = cluster, measure.vars = var)

DTs[["Gini"]] <- Gini[,
                    .(treatment,
                      session.code,
                      groupID,
                      round = str_replace_all(string = variable,
                                              pattern = "\\D", 
                                              replacement="") %>% as.integer(),
                      gini = value
                       )]
rm(list = c("var", "gini", "Gini"))
```

Finally, the data that was stored in a list will be reduced to a single data table.

```{r finalData}
replication <- Reduce(function(...) merge(..., by=c(cluster, "round"), all = TRUE), DTs)
```

```{r misc}
# flag observations where at least one participant did not understand the game
noComp <- subset[Outro.1.player.Comprehension == 0,
                 groupID] %>% unique()
replication[,
     noComprehension := 0]
replication[groupID %in% noComp,
     noComprehension := 1]

# drop observations (i.e. groups in rounds) with dropouts (bot_active == 1) and
# where round > 10
replication <- replication[bot_active == 0 & round <= 10]
```

The result contains ```NROW(DT)/4``` observations in 10 rounds and is saved as a ```csv``` and as a ```rda``` file in ```../data/processed/```.

```{r saveData}
save(replication, file = paste0("../data/processed/rda/", fileName, ".rda"))
write.csv(replication, file = paste0("../data/processed/csv/", fileName, ".csv"))
```

The first few rows look as follows. The full data set can be downloaded with a click on the button below (in case you only have access to this ```html``` file).

```{r displayData}
replication %>%
  head(n = 12) %>%
  kbl() %>% 
  # scroll_box(height = "200px") %>%
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)
```

```{r downloadData}
replication %>%
      download_this(
        output_name = glue("{Sys.Date()}_Simulation"),
        output_extension = ".csv", # CSV output
        button_label = "Download csv",
        button_type = "default"
        )
```

# Outlook

The next step is to reproduce Gaechter et al.'s figures and tables and to compare our results to their results. This will be done in the third report.

### 2021-04-10 reports/03_dataAnalyses.Rmd
update report structure

---
title: "3. Analyses Plan"
description: |
  Analyze and compare data
author:
  - name: Hauke Roggenkamp 
    url: https://github.com/Howquez
    affiliation: CLICCS
    affiliation_url: https://www.cliccs.uni-hamburg.de/
date: "`r Sys.Date()`"
bibliography: biblio.bib
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: false
    code_folding: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(data.table)
library(magrittr)
library(kableExtra)
library(downloadthis)
```

# Background

In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree]. The first experiment will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances). The current demo version of the experiment can be found [here](https://cliccs.herokuapp.com/). Click [here](https://github.com/Howquez/coopUncertainty) to visit the corresponding Github repository.

This report is the third in a series of reports covering this project. It reads the data prepared in the previous reports and analyzes them.

```{r readData}
load(file="../data/processed/rda/gaechter2017.rda")        # read gaechter
load(file="../data/processed/rda/gaechter2017_R1.rda")     # read gaechterFirstRound
load(file="../data/processed/rda/replication2021.rda")     # read replication
load(file="../data/processed/rda/replication2021_R1.rda")  # read replicationFirstRound
```

```{r cbind}
main <- rbindlist(list(replication, gaechter), 
                  use.names = TRUE)

R1   <- rbindlist(list(replicationFirstRound, gaechterFirstRound), 
                  use.names = TRUE)
```

### 2021-04-10 reports/0_generalIdea.Rmd
update report structure

--- 2021-04-06 reports/Mar21JourFixe.Rmd
@@
 ---
-title: "Gächter et al (2007, JPE) replication"
+title: "Replicate and extend Gächter et al's (2007, JPE) dynamic public goods game"
 description: |
-  Reproducing Gächter et al.'s Visualizations.
+  Draft.
 author:
@@
     affiliation_url: https://www.cliccs.uni-hamburg.de/
+  - name: Stefan Traub 
+    affiliation: Helmut Schmidt University
+    affiliation_url: https://www.hsu-hh.de/en/
+  - name: Michael Berlemann 
+    affiliation: Helmut Schmidt University
+    affiliation_url: https://www.hsu-hh.de/en/
 date: "`r Sys.Date()`"
@@
 
-base::load(file = "../data/processed/simulations.rda") 
-base::load(file = "../data/processed/demoSession.rda") 
-base::load(file = "../data/processed/gaechter2017.rda") 
+base::load(file = "../data/processed/rda/replication2021.rda") 
+base::load(file = "../data/processed/rda/gaechter2017.rda") 
 ```
@@
 In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), we plan to run a series of remote online experiments using oTree [@oTree].
-One of these experiments will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances) to allow for comparisons.
+One of these experiments will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances).
+The current demo version of the experiment can be found [here](https://cliccs.herokuapp.com/).
+Click [here](https://github.com/Howquez/coopUncertainty) to visit the corresponding Github repository.
+
+This report first reproduces the main visualizations from the original paper using @GACHTER2017's data as well as data simulated by rather simple oTree bots.
+Afterwards, a very broad idea of an additional treatment is drafted.
 
@@
 ```{r combineData}
-combined <- rbindlist(list(longDT[treatment == "Hi000"],# | treatment == "Lo000"], 
-                           gaechter,
-                           demoSession))
+combined <- rbindlist(list(gaechter,
+                           replication),
+                      use.names = TRUE)
 
-combined[treatment == "demoSession"] %>%
+combined %>%
   # head(n = 9) %>%
@@
 
-The following graph displays the zero risk treatments together with @GACHTER2017's data. The original ```noPunish10``` data lies between both sets of simulations.
+The following graphs display simulated data together with @GACHTER2017's data.
 
@@
     geom_point() + 
-    scale_x_continuous(name="Period",  breaks = 1:15) +
     scale_y_continuous(expand = c(0, 0), limits = c(0, 1)) +
-    labs(y = "Share of Current Endowment contributed")
+    labs(y = "Share of Current Endowment contributed", x = "Period")
 ```
@@
     geom_point() + 
-    scale_x_continuous(name="Period",  breaks = 1:15) +
     scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
-    labs(y = "Average Amount of Points contributed")
+    labs(y = "Average Amount of Points contributed", x = "Period")
 ```
@@
     geom_point() + 
-    scale_x_continuous(name="Period",  breaks = 1:15) +
     scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
-    labs(y = "Wealth")
+    labs(y = "Wealth", x = "Period")
 ```
 
-# Incorporating Risk or Uncertainty
+Finally, the gini plot looks as follows:
+
+```{r plotGini}
+plotDT <- summarySE(data = combined, 
+                      measurevar = "gini", 
+                      groupvars=c("treatment", "round"),
+                      na.rm = FALSE,
+                      conf.interval = 0.95,
+                      .drop = TRUE)
+
+temp <- plotDT[, "gini"]
+
+# plot
+ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
+    layout +
+    scale_fill_manual(values = wes_palette("GrandBudapest1")) +
+    scale_color_manual(values = wes_palette("GrandBudapest1")) +
+    geom_errorbar(aes(ymin=temp-se, ymax=temp+se), width=.25, alpha = 0.5) +
+    geom_line() +
+    geom_point() + 
+    scale_y_continuous(expand = c(0, 0), limits = c(0, 1)) +
+    labs(y = "Wealth", x = "Period")
+```
+
+# Incorporating Extreme Weather Events
 

### 2021-04-10 reports/_legacy/equilibria.Rmd
update report structure

--- 2021-04-06 reports/constantDamage.Rmd
@@
 **Proposition 1:** Consider the public good game with growth as defined above.
-The unique SPE of the game is such that all players contribute 0 throughout the entire game (both on and off the equilibrium path).^[See @GACHTER2017's Appendix for a formal proof.]
+The unique SPE of both the game without punishment and with punishment is such that all players contribute 0 throughout the entire game (both on and off the equilibrium path).^[See @GACHTER2017's Appendix for a formal proof.]
 
@@
 
-The basic idea is that, in every period, there is a (known or unknown)^[TBD] constant probability of an extreme weather event occurring in a group denoted by $r \equiv \frac{5}{16}=31.25$%.
-Such an extreme weather event can bring about damage $D$.
+The basic idea is that, in every period, there is a (known or unknown)^[TBD] constant probability of an extreme weather event occurring in a group denoted by $r \equiv \frac{1}{3}$.
+Such an extreme weather event can bring about damage (denoted as $d\equiv\frac{1}{2}$), i.e.
+cut each group member's earnings $N_i^{t+1}$ in half.
 This damage will, however, only occur if the group's contributions are smaller than a threshold $X$, which is half of their endowment, i.e.
@@
 $$
-N_i^t=
+\mathbb{E}\big[N_i^t\big]=
 \begin{cases}
 N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t, & \text{if}\ \sum_{j=1}^4 c_j^t \geq \frac{1}{2} \sum_{j=1}^4 E_j^t\\
-N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t -rD, & \text{else}
+\Big(N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t\Big) \Big(1-r(1-d)\Big), & \text{else}
 \end{cases}
@@
 
-With $D=0$ the game collapses to @GACHTER2017's model. The first derivative yields $-1$ implying that the individually rational contribution $c_{FC}^t=0$. 
-If $A=4$ denotes the number of players and $C^t$ the aggregate contribution with $C^t=\sum_{j=1}^{A}c_j^t$, the aggregate payoff with $D=0$ is described by:
+with $\Big(1-r(1-d)\Big)=\frac{5}{6}$ in our setting.
 
-\begin{align}
-\sum_{j=1}^{A}N_j^{t+1} & =\sum_{j=1}^{A}N_j^t - C^t + A \cdot \frac{1.5}{4} \cdot C^t\\
-&=\sum_{j=1}^{A}N_j^t + C^t(4 \cdot \frac{1.5}{4} - 1) \\
-&=\sum_{j=1}^{A}N_j^t + \frac{C^t}{2}
-\end{align}
+## The last period without inequality
 
-The collectively rational (that is, the efficient) contribution is $C_{FC}^t=\sum_{j=1}^{A}N_j^t$ because the first derivative is strictly positive.
-
-As a consequence, the game is a dilemma where the individual and collective interest are in conflict.
-
-Incorporating $D>0$, we want the game to remain a dilemma in which and observe whether positive contributions evolve despite contrasting incentives.
-As a consequence, we have to set $D$ such that freeriding ($c_i^t=0$ for all $i$) and risking to suffer that damage (LHS) remains more attractive than any contribution ($\bar c^t \geq \frac{\bar{N}^t}{2}$) that leads to damage control (RHS).
-
-\begin{align}
-N_i^t rD &> N_i^t - \bar{c}^t + A \cdot \frac{1.5}{4} \bar{c}^t \\
-N_i^t (rD-1) &> \frac{\bar{c}^t}{2}
-\end{align}
-
-## The last period
+Let's consider the artificial case of risk neutral players and symmetric endowments during the last period to dive deeper into the players' strategic environment.
+What is the best response $c_i \in BR_i(c_{-i})$, i.e.
+the optimal contribution of $i$ given the contributions of all $j \neq i$?
 
@@
 But what is the best thing to do in those cases, where $i$'s contribution can make a difference in damage control, that is, where $\sum_{j \neq i}^4 c_j^t < X < \sum_{j \neq i}^4 c_j^t + E_i^t$?
-In these cases, $i$ can contribute anything in  between $0 \leq c_i^t \leq X-\sum_{j \neq i}^4 c_j^t$ (the upper limit is the bare minimum required to prevent damages.
+In these cases, $i$ will either contribute nothing ($c_i^t=0$) or the bare minimum to prevent expected damages ($c_i^t= X-\sum_{j \neq i}^4 c_j^t$).
 
-But how much is $i$ actually willing to contribute?
-$i$ will contribute as long as her earnings from these contributions with successful damage control (LHS) are larger than her reduced earnings from $c_i^t=0$ with expected damage (RHS).
+$i$ will contribute as long as her earnings from these contributions with successful damage control (LHS) are larger than her reduced earnings with damage (RHS).
 
-\begin{align}
+\begin{align*}
 N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t & \geq 
- N_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t-rD\\
+ \Big(1-r(1-d)\Big)\Big(N_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t\Big)\\
 
-N_i^t - c_i^t \Big(1-\frac{1.5}{4}\Big) + \frac{1.5}{4}\sum_{j\neq i}^4 c_j^t & \geq 
- N_i^t + \frac{1.5}{4}\sum_{j\neq i}^4 c_j^t-rD\\
+N_i^t - c_i^t(1-\frac{1.5}{4}) + \frac{1.5}{4}\sum_{j\neq i}^4 c_j^t & \geq 
+ \Big(1-r(1-d)\Big) \Big(N_i^t + \frac{1.5}{4}\sum_{j\neq i}^4 c_j^t\Big)\\
 
-- c_i^t\Big(1-\frac{1.5}{4}\Big) & \geq -rD\\
+-c_i^t(1-\frac{1.5}{4}) & \geq 
+\Big(-r(1-d)\Big) \Big(N_i^t + \frac{1.5}{4}\sum_{j\neq i}^4 c_j^t\Big)\\
 
-c_i^t & \leq \frac{rD}{1-\frac{1.5}{4}}\\
+c_i^t & \leq \frac{r(d-1)}{\frac{1.5}{4} - 1} \Big(N_i^t + \frac{1.5}{4}\sum_{j\neq i}^4 c_j^t\Big)\\
 
-c_i^t & \leq \frac{D}{2} \; \text{ with }r=\frac{5}{16}\\ 
-\end{align}
+c_i^t & \leq \frac{8}{30} N_i^t + \frac{1}{10}\sum_{j\neq i}^4 c_j^t\\
 
-There are two things to note.
-First and unsurprisingly, the maximal contribution increases in risk and Damage.
-Second and given the MPCR and the (indeed artificial) risk level, the maximum amount any player would contribute is half the damage they would have suffered due to an extreme weather event if they had not reached the threshold.
-It is important to remember that they only make that contribution if their contribution is pivotal in controlling the damage.
+\end{align*}
 
-Because the game is symmetrical and because it requires every player to contribute at least half of her endowment to control the damage, there is a Nash equilibrium where each player contributes $c_i^t = \frac{1}{2} N_i^t$ if $D_i^t \geq N_i^t$.
+Given the others' contributions, $c_i^t$ depends on the income $i$ would lose if the group fails to control the damage (and the fixed parameters $r$, $d$ as well as the MPCR).
 
-If players cannot make any debt (limited liability), the damage cannot be larger than their endowment.
-In that case, the players are indifferent in contributing nothing or exactly half of their endowments.
-If the risk was larger than $31.25$%, positive contributions (that is $c_i^t = \frac{1}{2} N_i^t$) become more likely in the last round.
+Because this is a symmetric game (by assumption), we can set $c_i^t=c_j^t=c^t$ and find that the maximal contribution players would be willing to make falls short the threshold:
+
+\begin{align*}
+c^t & = \frac{8}{30} N^t + \frac{3}{10} c^t\\
+\frac{7}{10}c^t & = \frac{8}{30} N^t\\
+c^t & = \frac{8}{21} N^t < \frac{N^t}{2}\\
+\Rightarrow c^* & = 0
+\end{align*}
+
+Because each individual's maximum contribution is smaller than half of her Endowment, the extreme weather event's damage is inevitable.
+As a consequence, the individuals do not contribute in the first place.
+
+## The last period with inequality
+
+(How) does this change if endowments are heterogeneous?
+
+## Any period with inequality
+
+...

### 2021-04-10 reports/_legacy/simulations.Rmd
update report structure

---
title: "Visualize Simulations"
description: |
  Using Gächter et al.'s Graphs
author:
  - name: Hauke Roggenkamp 
    affiliation: CLICCS
    affiliation_url: https://www.cliccs.uni-hamburg.de/
date: "`r Sys.Date()`"
bibliography: biblio.bib
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: false
    code_folding: true
---

This document attaches the simulated data to @GACHTER2017's data and reproduces their key visualizations.

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = FALSE)

library(data.table)
library(tidyverse)
library(kableExtra)

library(Rmisc)
library(wesanderson)

base::load(file = "../data/processed/simulations.rda") 
base::load(file = "../data/processed/gaechter2017.rda")

```

# Data

The resulting data looks as follows. Each row represents a group, not a player. The displayed ```treatment``` names reflect the risk of extreme weather events as well as the share of current endowments contributed. ```Hi033``` indicates that the simulated subjects contributed a relatively high share of endowments facing a risk of 33 percent. In contrast, ```Lo000``` was parameterized such that there were no extreme weather events and contributions were relatively low. ```noPunish10``` represents @GACHTER2017's data from the no punish treatment with ten rounds.

The ```contribution``` shows a group's average contribution and the ```endowment``` their average endowment at the beginning of a round. The reported ```share``` is the fraction of both. ```stock``` is the group's average income at the end of the round and gain lists the difference between the ```stock``` and ```endowment```.

```{r combineData}
combined <- rbindlist(list(longDT, gaechter))

combined %>%
  head(n = 9) %>%
  kbl() %>% 
  # scroll_box(height = "200px") %>%
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)
```

```{r vizSetup, include = FALSE}
layout <- theme(panel.background = element_rect(fill = "white"),
                panel.grid = element_line(colour="gray", size=0),
                panel.grid.major.y = element_line(colour="gray", size=0.25),
                legend.key = element_rect(fill = "white"),
                axis.line.x.bottom = element_line(size = 0.25),
                axis.line.y.left = element_line(size = 0.25),
                plot.margin = unit(c(1,1,1,1), "cm"),
                legend.title = element_blank()
                )
```

# Visualization

The following graph shows that both ```Hi``` -treatments were parameterized similarly. The same applies to the two ```Lo``` -treatments. The original ```noPunish10``` data lies between both sets of simulations. The horizontal dashed line represents the threshold required for damage control.

```{r plotShare}
plotDT <- summarySE(data = combined, 
                      measurevar = "share", 
                      groupvars=c("treatment", "round"),
                      na.rm = FALSE,
                      conf.interval = 0.95,
                      .drop = TRUE)

temp <- plotDT[, "share"]

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    geom_hline(yintercept = 0.5, color = "#666666", lty = 2) +
    scale_fill_manual(values = wes_palette("Zissou1")) +
    scale_color_manual(values = wes_palette("Zissou1")) +
    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
    labs(y = "Share of Current Endowment contributed")
```

The different shares of contributions result in very different absolute contributions. The following graph illustrates the resulting heterogeneity between treatments. Combining this and the previous graph, it becomes clear that the ```033``` treatments lead to lower absolute contributions because of extreme weather events that occurred: The two blue lines (representing the ```Hi```-treatments) follow the same direction until the share of contributions falls short of the 50% benchmark in period 5 that makes damaged possible. From there on, damages reduce contributions in the ```Hi033```-treatment but not in the ```Hi000``` (where extreme weather events and thus, damages don't occur.)

```{r plotContribution}
plotDT <- summarySE(data = combined, 
                      measurevar = "contribution", 
                      groupvars=c("treatment", "round"),
                      na.rm = FALSE,
                      conf.interval = 0.95,
                      .drop = TRUE)

temp <- plotDT[, "contribution"]

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    geom_vline(xintercept = 5, color = "#666666", lty = 2) +
    scale_fill_manual(values = wes_palette("Zissou1")) +
    scale_color_manual(values = wes_palette("Zissou1")) +
    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
    labs(y = "Average Amount of Points contributed")
```

One finds the same pattern in ```Wealth``` levels:

```{r plotStock}
plotDT <- summarySE(data = combined, 
                      measurevar = "stock", 
                      groupvars=c("treatment", "round"),
                      na.rm = FALSE,
                      conf.interval = 0.95,
                      .drop = TRUE)

temp <- plotDT[, "stock"]

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    scale_fill_manual(values = wes_palette("Zissou1")) +
    scale_color_manual(values = wes_palette("Zissou1")) +
    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
    labs(y = "Wealth")
```

### 2021-04-10 reports/a_originalData.Rmd
update report structure

--- 2021-04-10 reports/01_replication.Rmd
@@
 library(wesanderson)
-
-DT <- read_dta(file="../data/gaechteretal/GMTV-data.dta") %>% data.table()
 ```
@@
 
-# Original Data
+# Load Data
 
-The data can be found in the supplementary materials they provide in their [online appendix](https://www.sciencedirect.com/science/article/pii/S0047272717300361#s0115).
-
-```{r data, include = FALSE}
-noPunish10 <- DT[exp_num == 5 | exp_num == 8 | exp_num == 9]
+```{r readData}
+DT <- read_dta(file="../data/gaechteretal/GMTV-data.dta") %>% data.table()
+DT <- DT[order(treat, gr_id, per)]
 ```
 
-Within the appendix, one also learns that the NOPUNISH 10-period data were collected in sessions 5, 8 and 9.
-Subsetting the data correspondingly yields a ```data.table``` consisting of 23 observations and $4 \times 10 \times 23=$ `r NROW(noPunish10)` rows and 27 variables.
+# Calulate Variables
 
-For this purpose only a few variables are relevant:
-
-- ```exp_num``` is a session identifier
-- ```per``` denotes the period
-- ```gr_id``` is a group identifier (carrying treatment information)
-- ```subj_id``` is a subject identifier
-- ```tokens``` reports a subject's endowment in a period
-- ```other[1-3]``` report the other group members' endowments in a period
-- ```gdp ``` equals the sum of endowments of a group in a period
-- ```putin``` reports a subject's contribution in a period
-- ```pu[1-3]``` report the other group members' contributions in a period
-- ```sum``` equals the sum of contributions of a group in a period.
-- ```gini``` reports a group's Gini coefficient in a period.
-- ```mean``` reports the fraction of sum/gdp -- but only in some cases.
-
-As a consequence, the first few rows of the data look as follows:
-
-```{r showData, layout = "l-body-outset"}
-noPunish10[,
+```{r calcVars}
+DT[,
    gini2 := Gini(c(tokens, other1, other2, other3)),
@@
 
-noPunish10[order(gr_id, per),
+DT[,
+   mean2 := sum/gdp]
+```
+
+# Subset
+
+```{r}
+temp <- DT[exp_num == 5 | exp_num == 8 | exp_num == 9]
+temp[order(gr_id, per),
          .(exp_num, gr_id, per, subj_id, # IDs
              tokens, other1, other2, other3, gdp, #endowments
-             putin, pu1, pu2, pu3, sum, mean, # contributions
-             gini, gini2
-           )] %>% 
-  head(n = 15) %>%
-  kbl() %>% 
-  # scroll_box(height = "200px") %>%
-  kable_paper("hover", 
-              full_width = TRUE,
-              fixed_thead = TRUE)
-
+             putin, pu1, pu2, pu3, sum, mean, mean2, # contributions
+             gini, gini2)] %>% 
+  head(n = 9) %>%
+  kbl()
 ```
-
-We see group 501 in the first two periods where subjects 511 to 514 start with an initial endowment of 20 which makes a GDP of 80.
-Subject 511 does not contribute (as represented in ```putin==0``` in the first row and ```pu1==0```in rows 2 to 4) while the others contribute 5, 15 and 15 in the first period, respectively.
-The ```sum``` of contributions therefore equals 35 period 1.
-
-With a sum of contributions being 35 and a return of contributions of 1.5, each subject receives ```ceil(13.125)``` =14 points from the group project such that the next period's ```gdp``` equals 101.
-
-Unfortunately, the Gini coefficient (```gini```) is a little off as one can see in the second period: Even though this is a group level variable, the group has three different coefficient in the same period.
-For this reason, I re-calculated the coefficient and called it ```gini2```.
-
-# Data Manipulation
-
-To resemble the oTree data, the original data has to be transformed a little.
-Therefore, some variables will be renamed, variables (such as ```stock```^[Gächter et al.
-called this variable _Wealth_] and ```gain```) will be created and, most notably, the unit of observations will be groups such that subject-level variables will be dropped.^[In addition, I will ignore the original Gini coefficient and use mine instead.]
-
-```{r writeData}
-
-noPunish10[,
-           share := sum/gdp,
-           by = .(subj_id, per)]
-
-gaechter <- noPunish10[order(gr_id, per),
-           .(treatment = "noPunish10", 
-             session.code = exp_num,
-             groupID = gr_id, 
-             round = per,
-             contribution = sum,
-             endowment = gdp,
-             share = mean, # share,
-             stock = (gdp + ceiling(sum/4*1.5)*4-sum),
-             gain = (ceiling(sum/4*1.5)*4-sum),
-             gini = gini2,
-             bot_active = 0,
-             # disaster = 0,
-             # EWE = 0,
-             noComprehension = 0)] %>% unique()
-
-gaechter %>%
-  head(n = 15) %>%
-  kbl() %>% 
-  kable_paper("hover", 
-              full_width = TRUE,
-              fixed_thead = TRUE)
-
-save(gaechter, file = "../data/processed/rda/gaechter2017.rda")
-write.csv(gaechter, file ="../data/processed/csv/gaechter2017.csv")
-
-```
-
-```{r downloadData}
-gaechter %>%
-      download_this(
-        output_name = "Gaechter2017noPunish10",
-        output_extension = ".csv", # CSV output
-        button_label = "Download csv",
-        button_type = "default"
-        )
-```
-
-# Visualizations
-
-```{r}
-layout <- theme(panel.background = element_rect(fill = "white"),
-                panel.grid = element_line(colour="gray", size=0),
-                panel.grid.major.y = element_line(colour="gray", size=0.25),
-                legend.key = element_rect(fill = "white"),
-                axis.line.x.bottom = element_line(size = 0.25),
-                axis.line.y.left = element_line(size = 0.25),
-                plot.margin = unit(c(1,1,1,1), "cm"),
-                legend.title = element_blank()
-                )
-```
-
-```{r plotContribution}
-plotDT <- summarySE(data = gaechter, 
-                      measurevar = "contribution", 
-                      groupvars=c("treatment", "round"),
-                      na.rm = FALSE,
-                      conf.interval = 0.95,
-                      .drop = TRUE)
-
-temp <- plotDT[, "contribution"]
-
-# plot
-ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
-    layout +
-    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
-    geom_line() +
-    geom_point() + 
-    scale_x_continuous(name="Period",  breaks = 1:15) +
-    scale_y_continuous(expand = c(0, 0), limits = c(0, 150)) +
-    labs(y = "Average Amount of Points contributed") +
-    scale_color_manual(values = wes_palette("Moonrise3"))
-```
-
-```{r plotShare}
-plotDT <- summarySE(data = gaechter, 
-                      measurevar = "share", 
-                      groupvars=c("treatment", "round"),
-                      na.rm = FALSE,
-                      conf.interval = 0.95,
-                      .drop = TRUE)
-
-temp <- plotDT[, "share"]
-
-# plot
-ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
-    layout +
-    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
-    geom_line() +
-    geom_point() + 
-    scale_x_continuous(name="Period",  breaks = 1:15) +
-    scale_y_continuous(expand = c(0, 0), limits = c(0, 1)) +
-    labs(y = "Share of Current Endowment contributed") +
-    scale_color_manual(values = wes_palette("Moonrise3"))
-```
-
-```{r plotStock}
-plotDT <- summarySE(data = gaechter, 
-                      measurevar = "stock", 
-                      groupvars=c("treatment", "round"),
-                      na.rm = FALSE,
-                      conf.interval = 0.95,
-                      .drop = TRUE)
-
-temp <- plotDT[, "stock"]
-
-# plot
-ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
-    layout +
-    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
-    geom_line() +
-    geom_point() + 
-    scale_x_continuous(name="Period",  breaks = 1:15) +
-    scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
-    labs(y = "Wealth") +
-    scale_color_manual(values = wes_palette("Moonrise3"))
-```
-
-```{r plotGini}
-plotDT <- summarySE(data = gaechter, 
-                      measurevar = "gini", 
-                      groupvars=c("treatment", "round"),
-                      na.rm = FALSE,
-                      conf.interval = 0.95,
-                      .drop = TRUE)
-
-temp <- plotDT[, "gini"]
-
-# plot
-ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
-    layout +
-    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
-    geom_line() +
-    geom_point() + 
-    scale_x_continuous(name="Period",  breaks = 1:15) +
-    scale_y_continuous(expand = c(0, 0), limits = c(0, 0.4)) +
-    labs(y = "Gini coefficient") +
-    scale_color_manual(values = wes_palette("Moonrise3"))
-```
-
-# Tables
-
-```{r regressions}
-# reg gdp punish if longgame==0  & treat<3 & per==10, cluster(gr_id)
-lm(gdp ~ punish, data = DT[longgame==0 & treat < 3 & per==10])
-```
-
-# Discussion
-
-Even though the figures above were created using the original data, they do not look the same as the original figures.
-This becomes obvious if one looks at the figures that visualize the contributions.
-The arising question therefore is whether I made a mistake in processing and interpreting the data.
-After all I thought to have found wrong Gini coefficients and struggle to interpret the ```mean``` of the original data.
-
-# First round
-
-Eventually, we'll also be interested in the participants' first round's behavior, as it indicates their willingness to cooperate before they interact with one another.
-As a consequence, we can compare all noPunish sessions, regardless of whether they ran for 10 or 15 rounds.
-
-```{r firstRound}
-noPunish <- DT[exp_num == 1 | exp_num == 3 | # noPunish15
-                 exp_num == 5 | exp_num == 8 | exp_num == 9] # noPunish10
-
-temp <- noPunish[per == 1]
-temp <- temp[,
-             treatment := "noPunish10"]
-temp <- temp[exp_num == 1 | exp_num == 3,
-             treatment := "noPunish15"]
-
-gaechterFirstRound <- temp[,
-                           .(participant.code = subj_id,
-                             treatment,
-                             session.code = exp_num,
-                             groupID = gr_id,
-                             belief = NA,
-                             othersContribution = sumputin - putin,
-                             ownContribution = putin,
-                             fairness = NA,
-                             trust = NA,
-                             comprehension = NA)]
-
-rm(list = c("temp"))
-
-# save data
-fileName <- "gaechter2017"
-save(gaechterFirstRound, 
-     file = paste0("../data/processed/rda/", fileName, "_R1", ".rda"))
-write.csv(gaechterFirstRound, 
-          file = paste0("../data/processed/csv/", fileName, "_R1", ".csv"))
-```
-
-`r NROW(gaechterFirstRound)` participants yield `r NROW(gaechterFirstRound)` independent observations that are stored in a data table called ```gaechterFirstRound```.
-These observations are displayed below and can, once more, be downloaded by a click on the button.
-As before, the data is also saved in ```../data/processed/```.
-
-```{r displayFirstRound}
-# display data
-gaechterFirstRound %>%
-  head(n = 15) %>%
-  kbl() %>% 
-  # scroll_box(height = "200px") %>%
-  kable_paper("hover", 
-              full_width = TRUE,
-              fixed_thead = TRUE)
-
-# create download button
-gaechterFirstRound %>%
-      download_this(
-        output_name = "gaechter2017_R1",
-        output_extension = ".csv", # CSV output
-        button_label = "Download csv",
-        button_type = "default"
-        )
-```
-
-# Outlook
-
-Having replicated Gaechter et al.'s main figures (more or less) the next step is to prepare the data we obtain in our experiment for the analysis.
-This will be done in the second report using simulated data.^[Eventually, one can use that report and apply it to the actual data.]

### 2021-06-20 reports/00_reproduction.Rmd
tidy up the R project

---
title: "Growth & Inequality in Dynamic Public Goods Games"
description: |
  Reproducing Gächter et al.'s main findings.
author: "Hauke Roggenkamp"
date: "`r Sys.Date()`"
bibliography: biblio.bib
output:
  pdf_document: default
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: false
    code_folding: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(haven)
library(data.table)
library(magrittr)
library(DescTools) # gini coefficient
library(sjPlot)
library(stargazer)
library(plm)
library(lmtest)
library(ggplot2)
library(wesanderson)
library(patchwork)

```

```{r functions}

# regressions 
gdp_ols <- function(DT, var = "gdp", output = "plm"){
  p.df <- DT %>% pdata.frame(index = c("gr_id"))
  plm <- plm(get(var) ~ punish, data = p.df, model = "pooling")
  # plm
  G <- length(unique(p.df$gr_id))
  N <- length(p.df$gr_id)
  dfa <- (G/(G - 1)) * (N - 1) / plm$df.residual
  group_c_vcov <- dfa * vcovHC(plm, type = "HC0", cluster = "group", adjust = T)
  # coeftest(plm, vcov = group_c_vcov)
  se <- sqrt(diag(group_c_vcov))
  # se

  if (output == "plm") {
    plm
  } else {
    se
  }

}

layout <- theme(panel.background = element_rect(fill = "white"),
                panel.grid = element_blank(),
                panel.grid.major.y = element_line(colour="gray", size=0.25),
                legend.key = element_rect(fill = "white"),
                axis.line.x.bottom = element_line(size = 0.25),
                axis.line.y.left = element_line(size = 0.25),
                # plot.margin = unit(c(1,1,1,1), "cm"),
                legend.title = element_blank()
                )

```

# Introduction

In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree]. The first experiment will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances). The current demo version of the experiment can be found [here](https://cliccs.herokuapp.com/). Click [here](https://github.com/Howquez/coopUncertainty) to visit the corresponding Github repository.

This document explores the data provided by @GACHTER2017 and finds that some of the variables are a little off. In addition, it fails to replicate the orginal article's figures. The following chapter will describe the available data. Subsequently, [data excerpts](#Tables) will demonstrate that the original _Gini coefficient_ varies within groups (in selected periods) and the _share of current endowment contributed_ is calculated using the last round's endowment. [Afterwards](#Downloads), the data is processsed and made available for downloads.The [Visualizations](#Visualizations) chapter will then present the original figures as well as figures reproduced using the original and re-calculated variables to demonstrate differences.

# Original Data

## Description

The data can be found in the supplementary materials they provide in the [online appendix](https://www.sciencedirect.com/science/article/pii/S0047272717300361#s0115) and contains, among others, the following variables:

- ```exp_num``` is a session identifier
- ```per``` denotes the period
- ```gr_id``` is a group identifier (carrying treatment information)
- ```subj_id``` is a subject identifier
- ```tokens``` reports a subject's endowment in a period
- ```other[1-3]``` report the other group members' endowments in a period
- ```gdp ``` equals the sum of endowments of a group in a period
- ```putin``` reports a subject's contribution in a period
- ```pu[1-3]``` report the other group members' contributions in a period
- ```sum``` equals the sum of contributions of a group in a period
- ```gini``` reports a group's Gini coefficient in a period
- ```mean``` reports the fraction of sum/lagged(gdp)
- ```totallost``` ?

I add three new measures, namely: ```gini2```, ```mean2``` and ```gpd2```. ```gini2``` differs from the original as it is constant within groups. ```mean2``` is equivalent to the original ```mean``` but relies on the current ```gdp``` instead of the lagged measure. In addition to the ```gpd``` (stating the endowment at the _beginning_ of a period), I calculate ```gpd2``` for the noPunish treatments and thereby report the income at the _end_ of a period. Finally, I create a ```treatment``` string-variable .

```{r createVars, include = FALSE}

GMTV <- read_dta(file="../data/gaechteretal/GMTV-data.dta") %>% data.table()

# treatments

  GMTV[punish == 0 & longgame == 0, # exp_num == 5 | exp_num == 8 | exp_num == 9,
       treatment := "noPunish10"]

  GMTV[punish == 0 & longgame == 1, # exp_num == 1 | exp_num == 3,
       treatment := "noPunish15"]

  GMTV[punish == 1 & longgame == 0, # exp_num == 4 | exp_num == 6 | exp_num == 10,
       treatment := "Punish10"]

  GMTV[punish == 1 & longgame == 1, # exp_num == 2 | exp_num == 7,
       treatment := "Punish15"]

# gdp, mean & gini
  GMTV[treatment == "noPunish10" | treatment == "noPunish15",
       gdp2 := (gdp + ceiling(sum/4*1.5)*4-sum)]

  GMTV[,
       mean2 := sum/gdp]

  GMTV[,
       gini2 := Gini(c(tokens, other1, other2, other3)),
       by = .(treatment, gr_id, per)]

  GMTV[is.nan(gini2),
       gini2 := 0]

# rearrange & subset

GMTV <- GMTV[exp_num <= 10]
GMTV <- GMTV[order(treatment, gr_id, per),
             .(treatment, treat, punish = as.logical(punish), longgame = as.logical(longgame),        # treatment vars 
               exp_num, gr_id, per, subj_id,              # IDs
               tokens, other1, other2, other3, gdp, gdp2, # endowments
               putin, pu1, pu2, pu3, sum, mean, mean2,    # contributions
               gini, gini2,                               # ginis
               totallost,                                 # punishment var
               highgdp
              )]

# remove duplicate rows while subsetting only group level variables
GMTVgroups <- GMTV[exp_num <= 10,
                   .(treatment,
                     treat,
                     punish = as.logical(punish),
                     longgame = as.logical(longgame),
                     exp_num,
                     gr_id,
                     per,
                     sum,
                     gdp,
                     mean,
                     mean2,
                     # gini,
                     gini2,
                     highgdp = as.logical(highgdp))] %>% unique()

# GMTVgroups <- GMTV[exp_num <= 10,
#                    lapply(.SD, mean, na.rm = TRUE),
#                    by = c("gr_id"),
#                    .SDcols = c()]

# subsets for regression tables
GMTV_short_all  <- GMTV[longgame == 0 & treat < 3 & per == 10]
GMTV_short_poor <- GMTV[longgame == 0 & treat < 3 & per == 10 & highgdp == 0]
GMTV_short_rich <- GMTV[longgame == 0 & treat < 3 & per == 10 & highgdp == 1]
GMTV_long_all   <- GMTV[longgame == 1 & treat > 100 & per == 15]
GMTV_long_poor  <- GMTV[longgame == 1 & treat > 100 & per == 15 & highgdp == 0]
GMTV_long_rich  <- GMTV[longgame == 1 & treat > 100 & per == 15 & highgdp == 1]
```

# Tables

## Table 2: OLS Regression Wealth

```{r stargazerGDP, results = "asis"}

if(knitr::is_html_output()){
  type <- "html"
} else {
  type = "latex"
}

stargazer(gdp_ols(GMTV_short_all),
          gdp_ols(GMTV_short_poor),
          gdp_ols(GMTV_short_rich),
          gdp_ols(GMTV_long_all),
          gdp_ols(GMTV_long_poor),
          gdp_ols(GMTV_long_rich),

          se = list(gdp_ols(GMTV_short_all,  output = "se"),
                    gdp_ols(GMTV_short_poor, output = "se"),
                    gdp_ols(GMTV_short_rich, output = "se"),
                    gdp_ols(GMTV_long_all,   output = "se"),
                    gdp_ols(GMTV_long_poor,  output = "se"),
                    gdp_ols(GMTV_long_rich,  output = "se")),

          add.lines = list(c("Long Game?", "No", "No", "No", "Yes", "Yes", "Yes")),

          column.labels = rep(c("All", "Below median", "Above median"), 2),
          model.numbers = FALSE,
          dep.var.labels = "Wealth (Table 2)",
          notes = "Robust standard errors in parentheses",
          header=FALSE,

          type = type, digits = 2, omit.stat = c("adj.rsq", "f")
          )
```

## Table 3: OLS Regression Gini coefficient

```{r stargazerGini, results = "asis"}

if(knitr::is_html_output()){
  type <- "html"
} else {
  type = "latex"
}

stargazer(gdp_ols(GMTV_short_all,  var = "gini"),
          gdp_ols(GMTV_short_poor, var = "gini"),
          gdp_ols(GMTV_short_rich, var = "gini"),
          gdp_ols(GMTV_long_all,   var = "gini"),
          gdp_ols(GMTV_long_poor,  var = "gini"),
          gdp_ols(GMTV_long_rich,  var = "gini"),

          se = list(gdp_ols(GMTV_short_all,  var = "gini", output = "se"),
                    gdp_ols(GMTV_short_poor, var = "gini", output = "se"),
                    gdp_ols(GMTV_short_rich, var = "gini", output = "se"),
                    gdp_ols(GMTV_long_all,   var = "gini", output = "se"),
                    gdp_ols(GMTV_long_poor,  var = "gini", output = "se"),
                    gdp_ols(GMTV_long_rich,  var = "gini", output = "se")),

          add.lines = list(c("Long Game?", "No", "No", "No", "Yes", "Yes", "Yes")),

          column.labels = rep(c("All", "Below median", "Above median"), 2),
          model.numbers = FALSE,
          dep.var.labels = "Original Gini coefficient (Table 3)",
          notes = "Robust standard errors in parentheses",
          header=FALSE,

          type = type, digits = 2, omit.stat = c("adj.rsq", "f")
          )
```

Table 3: OLS Regression re-calculated Gini

```{r stargazerGini2, results = "asis"}

if(knitr::is_html_output()){
  type <- "html"
} else {
  type = "latex"
}

stargazer(gdp_ols(GMTV_short_all,  var = "gini2"),
          gdp_ols(GMTV_short_poor, var = "gini2"),
          gdp_ols(GMTV_short_rich, var = "gini2"),
          gdp_ols(GMTV_long_all,   var = "gini2"),
          gdp_ols(GMTV_long_poor,  var = "gini2"),
          gdp_ols(GMTV_long_rich,  var = "gini2"),

          se = list(gdp_ols(GMTV_short_all,  var = "gini2", output = "se"),
                    gdp_ols(GMTV_short_poor, var = "gini2", output = "se"),
                    gdp_ols(GMTV_short_rich, var = "gini2", output = "se"),
                    gdp_ols(GMTV_long_all,   var = "gini2", output = "se"),
                    gdp_ols(GMTV_long_poor,  var = "gini2", output = "se"),
                    gdp_ols(GMTV_long_rich,  var = "gini2", output = "se")),

          add.lines = list(c("Long Game?", "No", "No", "No", "Yes", "Yes", "Yes")),

          column.labels = rep(c("All", "Below median", "Above median"), 2),
          model.numbers = FALSE,
          dep.var.labels = "Re-calculated Gini coefficient",
          notes = "Robust standard errors in parentheses",
          header=FALSE,

          type = type, digits = 2, omit.stat = c("adj.rsq", "f")
          )
```

# Figures

```{r plotContributions}

SUM <- GMTVgroups[, 
                    lapply(.SD, mean, na.rm = TRUE),
                    by = c("per", "treatment", "punish", "longgame"),
                    .SDcols = "sum"]

SUM[,
    sum := round(sum/4)]

ggplot(data = SUM, aes(x = per, y = sum, fill = treatment, color = treatment, lty = punish)) +
          layout +
          theme(legend.position="bottom") +
          geom_vline(xintercept = 10, alpha = 0.66) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="",  breaks = 1:15) +
          scale_y_continuous(breaks = seq(0, 150, by = 50), limits = c(0, 170), expand = c(0, 0)) +
          labs(y = "Average Amount of Tokens contributed") +
          scale_color_manual(values = wes_palette("Zissou1"))
```

```{r plotMeans}

means <- GMTVgroups[,
                    lapply(.SD, mean, na.rm = TRUE),
                    by = c("per", "treatment", "punish", "longgame"),
                    .SDcols = c("mean", "mean2")]

mean <- ggplot(data = means, aes(x = per, y = mean, fill = treatment, color = treatment, lty = punish)) +
          layout +
          theme(legend.position="none") +
          geom_vline(xintercept = 10, alpha = 0.66, size = 0.25) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="",  breaks = 1:15) +
          scale_y_continuous(breaks = seq(0, 1.2, by = 0.2), limits = c(0, 1.25), expand = c(0, 0)) +
          labs(y = "Share of past Endowment contributed") +
          scale_color_manual(values = wes_palette("Zissou1"))

mean2 <- ggplot(data = means, aes(x = per, y = mean2, fill = treatment, color = treatment, lty = punish)) +
          layout +
          theme(legend.position="none") +
          geom_vline(xintercept = 10, alpha = 0.66, size = 0.25) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="", breaks = 1:15) +
          scale_y_continuous(breaks = seq(0, 1.2, by = 0.2), limits = c(0, 1.25), expand = c(0, 0)) +
          labs(y = "Share of current Endowment contributed") +
          scale_color_manual(values = wes_palette("Zissou1"))

patchwork <- mean + mean2 & theme(legend.position = "bottom")
patchwork <- patchwork + plot_layout(guides = "collect")
patchwork

```
```{r summary1, results = "asis", warning = FALSE}

if(knitr::is_html_output()){
  type <- "html"
} else {
  type = "latex"
}

nopunish10 <- GMTVgroups[punish == FALSE & longgame == FALSE & exp_num <= 10 & per == 10, gdp]
punish10   <- GMTVgroups[punish == TRUE & longgame == FALSE & exp_num <= 10 & per == 10, gdp]
nopunish15 <- GMTVgroups[punish == FALSE & longgame == TRUE & exp_num <= 10 & per == 15, gdp]
punish15   <- GMTVgroups[punish == TRUE & longgame == TRUE & exp_num <= 10 & per == 15, gdp]

rows <- sapply(X = list(nopunish10, punish10, nopunish15, punish15), FUN = NROW) %>% max()
temp <- data.frame(nopunish10 = c(nopunish10, rep(NA, rows - NROW(nopunish10))),
                   punish10 = c(punish10, rep(NA, rows - NROW(punish10))),
                   nopunish15 = c(nopunish15, rep(NA, rows - NROW(nopunish15))),
                   punish15 = c(punish15, rep(NA, rows - NROW(punish15))))

stargazer(temp,
          summary.stat = c("mean", "median","sd", "max", "min", "n"),
          type = type, 
          flip = TRUE, 
          header=FALSE)

rs1 <- wilcox.test(nopunish10, punish10)$p.value %>% round(digits = 4)
rs2 <- wilcox.test(nopunish15, punish15)$p.value %>% round(digits = 4)

```

The rank sum tests yield p-Values of `r rs1` and `r rs2` for the mean ```gdp```s during the last period of the short and long games, respectively. This indicates that there is no significant difference between punish and nopunish treatments (at the 5%-level).

```{r olsWealth, eval = FALSE, include = FALSE}
m2.1  <- lm(gdp ~ punish, data = GMTV[longgame == 0 & treat < 3 & per == 10])
m2.2  <- lm(gdp ~ punish, data = GMTV[longgame == 0 & treat < 3 & per == 10 & highgdp == 0])
m2.3  <- lm(gdp ~ punish, data = GMTV[longgame == 0 & treat < 3 & per == 10 & highgdp == 1])

m2.4  <- lm(gdp ~ punish, data = GMTV[longgame == 1 & treat > 100 & per == 15])
m2.5  <- lm(gdp ~ punish, data = GMTV[longgame == 1 & treat > 100 & per == 15 & highgdp == 0])
m2.6  <- lm(gdp ~ punish, data = GMTV[longgame == 1 & treat > 100 & per == 15 & highgdp == 1])

tab_model(m2.1, m2.2, m2.3, m2.4, m2.5, m2.6,
          dv.labels = c("10All", "10Below", "10Above", "15All", "15Below", "15Above"),
          p.style = "stars",
          show.se = TRUE,
          show.ci = FALSE,
          show.p = FALSE, 
          transform = NULL)

# this function replicates the table but, unfortunately only row by row
tab_model(
  m2.2,
  vcov.fun = "CL", 
  vcov.type = "HC1",
  vcov.args = list(cluster = GMTV[longgame == 0 & treat < 3 & per == 10 & highgdp == 0, gr_id]),
  p.style = "stars",
  show.se = TRUE,
  show.ci = FALSE,
  show.p = FALSE,
  transform = NULL
)

# p.df <- GMTV[longgame == 0 & treat < 3 & per == 10 & highgdp == 0] %>% pdata.frame(index = c("gr_id"))
# plm <- plm(gdp ~ punish, data = p.df, model = "pooling")
# G <- length(unique(p.df$gr_id))
# N <- length(p.df$gr_id)
# dfa <- (G/(G - 1)) * (N - 1) / plm$df.residual
# group_c_vcov <- dfa * vcovHC(plm, type = "HC0", cluster = "group", adjust = T)
# # coeftest(plm, vcov = group_c_vcov)
# se <- sqrt(diag(group_c_vcov))
# 
# stargazer(plm, type = "html", digits = 2, se = list(se), omit.stat = c("rsq", "f"))

```

```{r olsGini2, eval = FALSE, include = FALSE}

m4.1  <- lm(gini2 ~ punish, data = GMTVgroups[longgame == 0 & treat < 3 & per == 10])
m4.2  <- lm(gini2 ~ punish, data = GMTVgroups[longgame == 0 & treat < 3 & per == 10 & highgdp == 0])
m4.3  <- lm(gini2 ~ punish, data = GMTVgroups[longgame == 0 & treat < 3 & per == 10 & highgdp == 1])

m4.4  <- lm(gini2 ~ punish, data = GMTVgroups[longgame == 1 & treat > 100 & per == 15])
m4.5  <- lm(gini2 ~ punish, data = GMTVgroups[longgame == 1 & treat > 100 & per == 15 & highgdp == 0])
m4.6  <- lm(gini2 ~ punish, data = GMTVgroups[longgame == 1 & treat > 100 & per == 15 & highgdp == 1])

tab_model(m4.1, m4.2, m4.3, m4.4, m4.5, m4.6,
          dv.labels = c("10All", "10Below", "10Above", "15All", "15Below", "15Above"),
          p.style = "stars",
          show.ci = FALSE,
          show.p = FALSE, 
          transform = NULL)
```

```{r eval = FALSE, include = FALSE}
# install.packages("plm")
# install.packages("lmtest")
# load packages
require(plm)
require(lmtest)  # for waldtest()
# get data and load as pdata.frame
url <- "http://www.kellogg.northwestern.edu/faculty/petersen/htm/papers/se/test_data.txt"
p.df <- read.table(url)
names(p.df) <- c("firmid", "year", "x", "y")
p.df <- pdata.frame(p.df, index = c("firmid", "year"), drop.index = F, row.names = T)
head(p.df)

# fit pooled OLS
m1 <- lm(y ~ x, data = p.df)
# fit same model with plm (needed for clustering)
pm1 <- plm(y ~ x, data = p.df, model = "pooling")

G <- length(unique(p.df$firmid))
N <- length(p.df$firmid)
dfa <- (G/(G - 1)) * (N - 1)/pm1$df.residual

firm_c_vcov <- dfa * vcovHC(pm1, type = "HC0", cluster = "group", adjust = T)
coeftest(pm1, vcov = firm_c_vcov)

tempDT <- p.df
names(tempDT)[names(tempDT) == "firmid"] <- "gr_id"
pm <- plm(y ~ x, data = tempDT, model = "pooling")
G <- length(unique(tempDT$gr_id))
N <- length(tempDT$gr_id)
dfa <- (G/(G - 1)) * (N - 1) / pm$df.residual
group_c_vcov <- dfa * vcovHC(pm1, type = "HC0", cluster = "group", adjust = T)
coeftest(pm1, vcov = group_c_vcov)

```

```{r, eval = FALSE, include = FALSE}
m2.1  <- lm(gdp ~ punish, data = GMTV[longgame == 0 & treat < 3 & per == 10])

plm2.1 <- plm(formula = gdp ~ punish,
              data = GMTV[longgame == 0 & treat < 3 & per == 10],
              model = "pooling",
              index = c("gr_id"))

summary(m2.1, cluster=c("gr_id"))
coeftest(plm2.1, vcov=vcovHC(plm2.1, type="sss", cluster="group"))

m3.4  <- lm(gini ~ punish, data = GMTV[longgame == 1 & treat > 100 & per == 15])
plm3.4 <- plm(formula = gini ~ punish,
              data = GMTV[longgame == 1 & treat > 100 & per == 15],
              model = "pooling",
              index = c("gr_id"))
summary(m3.4, cluster=c("gr_id"))
coeftest(plm3.4, vcov=vcovHC(plm3.4, type="sss", cluster="group"))

```

```{r, eval = FALSE, include = FALSE}
data(iris)
model <- lm(Petal.Length ~ Sepal.Length + Sepal.Width, data = iris)

# model parameters, where SE, CI and p-values are based on robust estimation
tab_model(model, vcov.fun = "HC", show.se = TRUE)

iris$cluster <- factor(rep(LETTERS[1:8], length.out = nrow(iris)))
# change estimation-type, defining additional arguments
tab_model(
  model, 
  vcov.fun = "CL", 
  vcov.type = "HC1",
  vcov.args = list(cluster = iris$cluster),
  show.se = TRUE
)

```

```{r eval = FALSE, include = FALSE}
library(data.table)
library(sjPlot)
data(iris)
DT <- data.table(iris)
DT[, cluster := factor(rep(LETTERS[1:8], length.out = nrow(iris)))]

m0 <- lm(Petal.Length ~ Sepal.Length + Sepal.Width, data = DT)
m1 <- lm(Petal.Length ~ Sepal.Length + Sepal.Width, data = DT[Petal.Width >= 1])
m2 <- lm(Petal.Length ~ Sepal.Length + Sepal.Width, data = DT[Petal.Width < 1])

tab_model(
  m0,
  vcov.fun = "CL", 
  vcov.type = "HC1",
  vcov.args = list(cluster = DT$cluster),
  show.se = TRUE
)

tab_model(
  m1,
  vcov.fun = "CL", 
  vcov.type = "HC1",
  vcov.args = list(cluster = DT[Petal.Width >= 1, cluster]),
  show.se = TRUE
)

```

# References

### 2021-06-20 reports/01_replication.Rmd
tidy up the R project

@@
 - ```gini``` reports a group's Gini coefficient in a period.
-- ```mean``` reports the fraction of sum/gdp -- but only in some cases.
+- ```mean``` reports the fraction of sum/lagged(gdp).
+
+Additionally, I compute two new measures, ```gini2``` as well as ```share```.
+The new ```gini2``` differs from the original as it is constant within groups.
+```share``` is equivalent to the original mean but relies on the current gdp instead of the past one as a denominator.
 
@@
 ```{r showData, layout = "l-body-outset"}
+noPunish10[,
+           share := sum/gdp,
+           by = .(subj_id, per)]
+
 noPunish10[,
@@
              tokens, other1, other2, other3, gdp, #endowments
-             putin, pu1, pu2, pu3, sum, mean, # contributions
+             putin, pu1, pu2, pu3, sum, mean, share, # contributions
              gini, gini2
@@
 
-Unfortunately, the Gini coefficient (```gini```) is a little off as one can see in the second period: Even though this is a group level variable, the group has three different coefficient in the same period.
-For this reason, I re-calculated the coefficient and called it ```gini2```.
+The Gini coefficient (```gini```) is a little off as one can see in the second period: Even though this is a group level variable, the group has three different coefficient in the same period.
+With the same absolute amount of contributions as in the first period,the second period ```mean``` (based on the past ```gdp```) is larger than ```share``` in the second period, because the ```gdp``` grew.
 
@@
 To resemble the oTree data, the original data has to be transformed a little.
-Therefore, some variables will be renamed, variables (such as ```stock```^[Gächter et al.
-called this variable _Wealth_] and ```gain```) will be created and, most notably, the unit of observations will be groups such that subject-level variables will be dropped.^[In addition, I will ignore the original Gini coefficient and use mine instead.]
+Therefore, some variables will be renamed, variables (such as ```stock```^[The income at the end of a period.] and ```gain```^[The tokens earned in a period.]) will be created and, most notably, the unit of observations will be groups such that subject-level variables will be dropped.
 
@@
                              groupID = gr_id,
-                             belief = NA,
                              othersContribution = sumputin - putin,
                              ownContribution = putin,
-                             fairness = NA,
                              trust = NA,
@@
 
+# Covariates
+
 # Outlook

### 2021-06-20 reports/02_dataProcessing.Rmd
tidy up the R project

@@
 As a consequence, `r NROW(DT)` participants yield `r NROW(DT)` observations that shall be stored in a data table called ```replicationFirstRound```.
-This table carries information on a participant's ```belief``` about the sum of other group members' contributions, their actual contribution ```othersContribution```, the participant's ```ownContribution```, some fairness measure that equals the difference between the own contribution and the expected average contribution of others and a trust measure^["Generally, others can be trusted".
+This table carries information on a participant's group members'  contributions ```othersContribution```, the participant's ```ownContribution``` and a trust measure^["Generally, others can be trusted".
 Likert scale ranging from 0 (do not agree) to 6 (agree).] obtained from the personality test at the end of the experiment.
@@
                    groupID = dPGG.1.group.id_in_subsession,
-                   belief = dPGG.1.player.belief,
                    othersContribution = dPGG.1.group.total_contribution - dPGG.1.player.contribution,
                    ownContribution = dPGG.1.player.contribution,
-                   fairness = dPGG.1.player.contribution - dPGG.1.player.belief/3,
                    trust = Outro.1.player.PQ11,
-                   comprehension = Outro.1.player.Comprehension)]
+                   comprehension = dPGG.10.player.comprehension)]
 
@@
 # most relevant variables
-mRegex <- "participant\\.code$|session\\.code$|dPGG\\.1\\.group\\.id_in_subsession|^dPGG.1.player.id_in_group$|\\.1\\.player.belief|endowment|contribution|stock|gain$|bot_active|Comprehension"
+mRegex <- "participant\\.code$|session\\.code$|dPGG\\.1\\.group\\.id_in_subsession|^dPGG.1.player.id_in_group$|\\.1\\.player.belief|endowment|contribution|stock|gain$|bot_active|10.player.comprehension|10.player.donation"
 mainVariables <- str_subset(string = names(DT),
@@
 # add share as contribution/endowment
-for(round in 1:15){
+for(round in 1:10){
   contribution <- glue("dPGG.{round}.player.contribution")
@@
 # flag observations where at least one participant did not understand the game
-noComp <- subset[Outro.1.player.Comprehension == 0,
+noComp <- subset[dPGG.10.player.comprehension == 0,
                  groupID] %>% unique()

### 2021-06-20 reports/03_dataAnalyses.Rmd
tidy up the R project

@@
 library(downloadthis)
+library(ggplot2)
+library(wesanderson)
 ```
@@
 ```
+
+# Graphs
+
+```{r layout}
+layout <- theme(panel.background = element_rect(fill = "white"),
+                panel.grid = element_line(colour="gray", size=0),
+                panel.grid.major.y = element_line(colour="gray", size=0.25),
+                legend.key = element_rect(fill = "white"),
+                axis.line.x.bottom = element_line(size = 0.25),
+                axis.line.y.left = element_line(size = 0.25),
+                plot.margin = unit(c(1,1,1,1), "cm"),
+                legend.title = element_blank()
+                )
+```
+
+```{r firstRound}
+ggplot(R1, aes(y=othersContribution, x=belief)) +
+  layout +
+  geom_abline(intercept = 0, slope = 1, linetype="dashed", alpha = 0.66) +
+  geom_point() +
+  geom_point(color = wes_palette("Moonrise3")[1]) +
+  scale_y_continuous(expand = c(0, 0), limits = c(0, 60)) +
+  scale_x_continuous(expand = c(0, 0), limits = c(0, 60))
+
+ggplot(R1, aes(y=ownContribution, x=belief/3)) +
+  layout +
+  geom_abline(intercept = 0, slope = 1, linetype="dashed", alpha = 0.66)+ 
+  geom_point() +
+  geom_point(color = wes_palette("Moonrise3")[1]) +
+  scale_y_continuous(expand = c(0, 0), limits = c(0, 25)) +
+  scale_x_continuous(expand = c(0, 0), limits = c(0, 25))
+
+ggplot(R1, aes(y=ownContribution, x=othersContribution/3)) +
+  layout +
+  geom_abline(intercept = 0, slope = 1, linetype="dashed", alpha = 0.66) +
+  geom_point(color = wes_palette("Moonrise3")[1]) +
+  scale_y_continuous(expand = c(0, 0), limits = c(-1, 25)) +
+  scale_x_continuous(expand = c(0, 0), limits = c(-1, 25))
+
+```

### 2021-06-20 analysis/R/config.R

@@ -11,11 +11,18 @@ listOfPackages <- c("renv",          # package management
                     "lubridate",     # working with dates
                     "plotly",        # interactive visualizations
                     "wesanderson",   # color palette
-                    "highcharter",   # get nice viz
+                    "gridExtra",
+                    "patchwork",
+                    "highcharter",   # get nice interactive viz
                     "Rmisc",         # Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
                     "data.table",
-                    "magrittr"       # get %>% and %<>% operators
+                    "magrittr",      # get %>% and %<>% operators
+                    "sjPlot",        # regression tables
+                    "stargazer",     # regression tables
+                    "plm",           # clustered standard errors
+                    "lmtest"
                     )
+
 
 newPackages <- listOfPackages[!(listOfPackages %in% installed.packages()[, "Package"])]
 
@@ -27,4 +34,4 @@ for(package in listOfPackages){
   require(package, character.only = TRUE)
 }
 
-# snapshot()
+# renv::snapshot()

### 2021-06-20 analysis/R/source.R

@@ -5,4 +5,10 @@ source("R/data.R")
 source("R/gaechteretal.R", echo = TRUE)
 source("R/viz.R")
 
-# create_article("../reports/Mar21JourFixe.Rmd")
+# install.packages("DescTools")
+# library(DescTools)
+# create_article("../reports/researchProposal.Rmd")
+
+rmarkdown::render(input = "../reports/Treatments.Rmd",
+                  output_format = "all",
+                  output_file = "Treatments")

### 2021-06-20 oTree/Outro/models.py

@@ -79,7 +79,7 @@ class Player(BasePlayer):
                                     widget=widgets.RadioSelect)
 
     Income = models.IntegerField(doc="Respondent's income",
-                                 label="Wie hoch war das gesamte Einkommen aller Mitglieder Ihres Haushalts im letzten Monat?",
+                                 label="Welches monatliche Budget haben Sie zur Verfügung? Bitte geben Sie Ihr eigenes monatliches Nettoeinkommen an.",
                                  choices=[
                                      [0, "0-500 €"],
                                      [1, "501-1.000 €"],

### 2021-06-21 reports/01_replication.Rmd
prepare pre-registration

@@
 library(wesanderson)
+library(lubridate)
+```
 
+```{r readData}
 DT <- read_dta(file="../data/gaechteretal/GMTV-data.dta") %>% data.table()
+CT <- read_dta(file="../data/gaechteretal/GMTV-questionnaire-data.dta") %>% data.table()
 ```
@@
 noPunish10 <- DT[exp_num == 5 | exp_num == 8 | exp_num == 9]
+# noPunish10 <- DT[longgame == 0 & punish == 0 & exp_num <= 10]
 ```
@@
 
-```{r writeData}
-
+```{r manipulateData}
 noPunish10[,
@@
 
-gaechter <- noPunish10[order(gr_id, per),
+GMTV <- noPunish10[order(gr_id, per),
            .(treatment = "noPunish10", 
@@
 
-gaechter %>%
+# create rich indicator (just as highgdp in original data)
+median <- GMTV[round == 10,
+                   median(stock)]
+
+richGroups <- GMTV[round == 10 & stock > median,
+                       unique(groupID)]
+
+poorGroups <- GMTV[round == 10 & stock < median,
+                       unique(groupID)]
+
+GMTV[groupID %in% richGroups,
+         rich := TRUE]
+
+GMTV[groupID %in% poorGroups,
+         rich := FALSE]
+
+# display data
+GMTV %>%
   head(n = 15) %>%
@@
 
-save(gaechter, file = "../data/processed/rda/gaechter2017.rda")
-write.csv(gaechter, file ="../data/processed/csv/gaechter2017.csv")
+```
+
+```{r writeData}
+save(GMTV, file = "../data/processed/rda/GMTV2017.rda")
+write.csv(GMTV, file ="../data/processed/csv/GMTV2017.csv")
 
@@
 ```{r downloadData}
-gaechter %>%
+GMTV %>%
       download_this(
-        output_name = "Gaechter2017noPunish10",
+        output_name = "GMTV2017noPunish10",
         output_extension = ".csv", # CSV output
@@
 ```{r plotContribution}
-plotDT <- summarySE(data = gaechter, 
+plotDT <- summarySE(data = GMTV, 
                       measurevar = "contribution", 
@@
 ```{r plotShare}
-plotDT <- summarySE(data = gaechter, 
+plotDT <- summarySE(data = GMTV, 
                       measurevar = "share", 
@@
 ```{r plotStock}
-plotDT <- summarySE(data = gaechter, 
+plotDT <- summarySE(data = GMTV, 
                       measurevar = "stock", 
@@
 ```{r plotGini}
-plotDT <- summarySE(data = gaechter, 
+plotDT <- summarySE(data = GMTV, 
                       measurevar = "gini", 
@@
 
-gaechterFirstRound <- temp[,
+GMTVFirstRound <- temp[,
                            .(participant.code = subj_id,
@@
 # save data
-fileName <- "gaechter2017"
-save(gaechterFirstRound, 
+fileName <- "GMTV2017"
+save(GMTVFirstRound, 
      file = paste0("../data/processed/rda/", fileName, "_R1", ".rda"))
-write.csv(gaechterFirstRound, 
+write.csv(GMTVFirstRound, 
           file = paste0("../data/processed/csv/", fileName, "_R1", ".csv"))
@@
 
-`r NROW(gaechterFirstRound)` participants yield `r NROW(gaechterFirstRound)` independent observations that are stored in a data table called ```gaechterFirstRound```.
+`r NROW(GMTVFirstRound)` participants yield `r NROW(GMTVFirstRound)` independent observations that are stored in a data table called ```GMTVFirstRound```.
 These observations are displayed below and can, once more, be downloaded by a click on the button.
@@
 # display data
-gaechterFirstRound %>%
+GMTVFirstRound %>%
   head(n = 15) %>%
@@
 # create download button
-gaechterFirstRound %>%
+GMTVFirstRound %>%
       download_this(
-        output_name = "gaechter2017_R1",
+        output_name = "GMTV2017_R1",
         output_extension = ".csv", # CSV output
@@
 
+```{r subsetCovs}
+GMTVCovariates <- CT[exp_num == 5 | exp_num == 8 | exp_num == 9,
+                         .(treatment = "noPunish10",
+                           session.code = exp_num,
+                           groupID = gr_id,
+                           participant.code = subj_id,
+                           gender,
+                           age = Sys.Date() %>% lubridate::year() - age,
+                           pq01 = q1,
+                           pq02 = q2,
+                           pq03 = q3,
+                           pq04 = q4,
+                           pq05 = q5,
+                           pq06 = q6,
+                           pq07 = q7,
+                           pq08 = q8,
+                           pq09 = q9,
+                           pq10 = q10,
+                           pq11 = q11,
+                           pq12 = q12,
+                           pq13 = q13,
+                           pq14 = q14,
+                           donation = don
+                           )]
+
+# write data
+fileName <- "GMTV2017"
+save(GMTVCovariates, 
+     file = paste0("../data/processed/rda/", fileName, "_COVS", ".rda"))
+write.csv(GMTVCovariates, 
+          file = paste0("../data/processed/csv/", fileName, "_COVS", ".csv"))
+
+# no display or download button as these data were not made available online by the authors
+```
+
 # Outlook

### 2021-06-21 reports/02_dataProcessing.Rmd
prepare pre-registration

@@
 
-```{r loadData}
+```{r readData}
 # read simulated data
@@
 Eventually, this report can also be used to process real data.
-This only requires us to load a different data set.^[It may also require us to merge multiple data sets -- that depends on whether the lab delivers one or several data sets and remains to be discussed.]
+This only requires us to read a different data set.^[It may also require us to merge multiple data sets -- that depends on whether the lab delivers one or several data sets and remains to be discussed.]
 
@@
                    session.code,
-                   groupID = dPGG.1.group.id_in_subsession,
+                   groupID = paste(session.code, dPGG.1.group.id_in_subsession, sep = "_"),
                    othersContribution = dPGG.1.group.total_contribution - dPGG.1.player.contribution,
@@
 
+Next, we'll flag groups that are richer and poorer than the median group.
+
+```{r calcRich}
+
+median <- replication[round == 10,
+                      median(stock)]
+
+richGroups <- replication[round == 10 & stock > median,
+                          unique(groupID)]
+
+poorGroups <- replication[round == 10 & stock < median,
+                          unique(groupID)]
+
+replication[groupID %in% richGroups,
+            rich := TRUE]
+
+replication[groupID %in% poorGroups,
+            rich := FALSE]
+
+```
+
 ```{r misc}
@@
 
+```{r createCovs}
+
+# add variables
+DT[, treatment := "replication"]
+
+DT[, groupID := paste(session.code, dPGG.1.group.id_in_subsession, 
+                    sep = "_")]
+
+# subset
+cRegex <- "participant.code|session.code|treatment|groupID|Outro.1.player|10.player.donation"
+covariates <- str_subset(string = names(DT),
+                            pattern = cRegex)
+CT <- DT[, ..covariates]
+
+# rename
+names(CT) <- names(CT) %>% 
+  str_replace_all(pattern =".*player\\.",
+                  replacement = "") %>%
+  str_to_lower()
+
+names(CT)[names(CT) == "groupid"] <- "groupID"
+
+# refactor
+CT[, donation := donation/20]
+
+CT[, gender := ifelse(test = gender == "female",
+                      yes  = 1,
+                      no   = 0)]
+
+replicationCovariates <- CT
+
+# write data
+fileName <- "replication2021"
+save(replicationCovariates, 
+     file = paste0("../data/processed/rda/", fileName, "_COVS", ".rda"))
+write.csv(replicationCovariates, 
+          file = paste0("../data/processed/csv/", fileName, "_COVS", ".csv"))
+
+# no display or download button as these data may qualify as PII
+```
+
 # Outlook

### 2021-06-21 reports/03_dataAnalyses.Rmd
prepare pre-registration

@@
 library(wesanderson)
+library(patchwork)
+library(stargazer)
 ```
@@
 ```{r readData}
-load(file="../data/processed/rda/gaechter2017.rda")        # read gaechter
-load(file="../data/processed/rda/gaechter2017_R1.rda")     # read gaechterFirstRound
+load(file="../data/processed/rda/GMTV2017.rda")          # read GMTV
+load(file="../data/processed/rda/GMTV2017_R1.rda")       # read GMTVFirstRound
+load(file="../data/processed/rda/GMTV2017_COVS.rda")     # read GMTVCovariates
 load(file="../data/processed/rda/replication2021.rda")       # read replication
 load(file="../data/processed/rda/replication2021_R1.rda")    # read replicationFirstRound
+load(file="../data/processed/rda/replication2021_COVS.rda")  # read replicationCovariates
 ```
@@
 ```{r cbind}
-main <- rbindlist(list(replication, gaechter), 
+main <- rbindlist(list(replication, GMTV), 
                   use.names = TRUE)
 
-R1   <- rbindlist(list(replicationFirstRound, gaechterFirstRound), 
+R1   <- rbindlist(list(replicationFirstRound, GMTVFirstRound), 
                   use.names = TRUE)
+
+covs <- rbindlist(list(replicationCovariates, GMTVCovariates), 
+                  use.names = TRUE,
+                  fill = TRUE)
+
+rm(list = c("replication", "GMTV", "replicationFirstRound", "GMTVFirstRound", "GMTVCovariates", "replicationCovariates"))
 ```
 
-# Graphs
+# Results
 
@@
 
-```{r firstRound}
+## First Round
+
+```{r firstRound, eval = FALSE}
 ggplot(R1, aes(y=othersContribution, x=belief)) +
@@
 ```
+
+## Provision of the public good and wealth creation
+
+```{r plotContributions}
+
+SUM <- main[,
+            lapply(.SD, mean, na.rm = TRUE),
+            by = c("round", "treatment"),
+            .SDcols = "contribution"]
+
+SUM[,
+    sum := round(contribution/4)]
+
+upperLimit <- SUM$contribution %>% max() %>% round() + 10
+
+p1 <- ggplot(data = SUM, 
+             aes(x = round, y = contribution, fill = treatment, color = treatment, lty = treatment)) +
+  layout +
+  theme(legend.position="bottom") +
+  geom_line(show.legend=FALSE) +
+  geom_point() +
+  scale_x_continuous(name="",  breaks = 1:15) +
+  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
+  labs(y = "Average Amount of Tokens contributed") +
+  scale_color_manual(values = wes_palette("GrandBudapest1"))
+
+rm(list = c("SUM"))
+```
+
+```{r plotShareOfContributions, fig.cap = "The average amount of tokens contributed over time in treatments."}
+
+SHARE <- main[,
+            lapply(.SD, mean, na.rm = TRUE),
+            by = c("round", "treatment"),
+            .SDcols = "share"]
+
+upperLimit <- 1
+
+p2 <- ggplot(data = SHARE, 
+             aes(x = round, y = share, fill = treatment, color = treatment, lty = treatment)) +
+  layout +
+  theme(legend.position="bottom") +
+  geom_line(show.legend=FALSE) +
+  geom_point() +
+  scale_x_continuous(name="",  breaks = 1:15) +
+  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
+  labs(y = "Share of Current Endowment contributed") +
+  scale_color_manual(values = wes_palette("GrandBudapest1"))
+
+patchwork <- p1 + p2 & theme(legend.position = "bottom")
+patchwork <- patchwork + plot_layout(guides = "collect")
+patchwork
+
+rm(list = c("SHARE", "p1", "p2"))
+```
+
+```{r summary1, results = "asis", warning = FALSE, fig.cap = "test"}
+
+if(knitr::is_html_output()){
+  type <- "html"
+} else {
+  type = "latex"
+}
+
+replication <- main[treatment == "replication" & round == 10, stock]
+GMTV    <- main[treatment == "noPunish10" & round == 10, stock]
+
+rows <- sapply(X = list(replication, GMTV), FUN = NROW) %>% max()
+temp <- data.frame(replication = c(replication, rep(NA, rows - NROW(replication))),
+                   GMTV = c(GMTV, rep(NA, rows - NROW(GMTV))))
+
+stargazer(temp,
+          summary.stat = c("mean", "median","sd", "max", "min", "n"),
+          type = type, 
+          flip = TRUE, 
+          header=FALSE)
+
+rs1 <- wilcox.test(replication, GMTV)$p.value %>% round(digits = 4) %>% formatC(format = "f", digits = 4)
+
+```
+
+The rank sum test yields a p-Value of `r rs1` for the mean ```stock``` a.k.a _Wealth_ during the last period of the game.
+
+```{r tableStock, results = "asis", warning = FALSE}
+
+# create subsets
+main_all  <- main[round == 10]
+main_poor <- main[round == 10 & rich == FALSE]
+main_rich <- main[round == 10 & rich == TRUE]
+
+# create table
+if(knitr::is_html_output()){
+  type <- "html"
+} else {
+  type = "latex"
+}
+
+stargazer(lm(formula = stock ~ treatment, data = main_all),
+          lm(formula = stock ~ treatment, data = main_poor),
+          lm(formula = stock ~ treatment, data = main_rich),
+
+          column.labels = c("All", "Below median", "Above median"),
+          model.numbers = FALSE,
+          dep.var.labels = "Wealth (Table 2)",
+          header=FALSE,
+          covariate.labels = c("Replication"),
+
+          type = type, digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
+          )
+```
+
+```{r plotStock, fig.cap = "Average wealth over time across treatments."}
+STOCK <- main[,
+            lapply(.SD, mean, na.rm = TRUE),
+            by = c("round", "treatment"),
+            .SDcols = "stock"]
+
+upperLimit <- STOCK$stock %>% max() %>% round() + 10
+
+ggplot(data = STOCK, 
+       aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
+          layout +
+          theme(legend.position="bottom") +
+          # geom_vline(xintercept = 10, alpha = 0.66) +
+          geom_line(show.legend=FALSE) +
+          geom_point() +
+          scale_x_continuous(name="",  breaks = 1:10) +
+          scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
+          labs(y = "Wealth") +
+          scale_color_manual(values = wes_palette("GrandBudapest1"))
+
+rm(list = c("STOCK"))
+```
+
+## Inequality
+
+```{r plotInequality, fig.cap = "Average Gini coefficient over time across treatments."}
+GINI <- main[,
+            lapply(.SD, mean, na.rm = TRUE),
+            by = c("round", "treatment"),
+            .SDcols = "gini"]
+
+upperLimit <- GINI$gini %>% max() %>% round(digits = 1) + 0.10
+
+ggplot(data = GINI, 
+       aes(x = round, y = gini, fill = treatment, color = treatment, lty = treatment)) +
+          layout +
+          theme(legend.position="bottom") +
+          # geom_vline(xintercept = 10, alpha = 0.66) +
+          geom_line(show.legend=FALSE) +
+          geom_point() +
+          scale_x_continuous(name="",  breaks = 1:10) +
+          scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
+          labs(y = "Gini coefficient") +
+          scale_color_manual(values = wes_palette("GrandBudapest1"))
+
+rm(list = c("GINI"))
+```
+
+```{r tableGINI, results = "asis", warning = FALSE}
+
+# create subsets
+main_all  <- main[round == 10]
+main_poor <- main[round == 10 & rich == FALSE]
+main_rich <- main[round == 10 & rich == TRUE]
+
+# create table
+if(knitr::is_html_output()){
+  type <- "html"
+} else {
+  type = "latex"
+}
+
+stargazer(lm(formula = gini ~ treatment, data = main_all),
+          lm(formula = gini ~ treatment, data = main_poor),
+          lm(formula = gini ~ treatment, data = main_rich),
+
+          column.labels = c("All", "Below median", "Above median"),
+          model.numbers = FALSE,
+          dep.var.labels = "Wealth (Table 2)",
+          header=FALSE,
+          covariate.labels = c("Replication"),
+
+          type = type, digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
+          )
+```
+
+```{r summary2, results = "asis", warning = FALSE}
+
+if(knitr::is_html_output()){
+  type <- "html"
+} else {
+  type = "latex"
+}
+
+replication <- main[treatment == "replication" & round == 10, gini]
+GMTV    <- main[treatment == "noPunish10" & round == 10, gini]
+
+rows <- sapply(X = list(replication, GMTV), FUN = NROW) %>% max()
+temp <- data.frame(replication = c(replication, rep(NA, rows - NROW(replication))),
+                   GMTV = c(GMTV, rep(NA, rows - NROW(GMTV))))
+
+stargazer(temp,
+          summary.stat = c("mean", "median","sd", "max", "min", "n"),
+          type = type, 
+          flip = TRUE, 
+          header=FALSE)
+
+rs2 <- wilcox.test(replication, GMTV)$p.value %>% round(digits = 4) %>% formatC(format = "f", digits = 4)
+
+```
+
+The rank sum test yields a p-Value of `r rs2` for the mean ```gini``` during the last period of the game.
+
+## Sample Properties

### 2021-06-21 oTree/Outro/models.py

@@ -102,6 +102,6 @@ class Player(BasePlayer):
                                      blank=True)
 
     # donation
-    donation = models.CurrencyField(doc="Donation",
-                                    label="Möchten Sie einen Teil Ihres Verdienstes spenden? Wenn ja, wie viel?",
-                                    blank=True)
+    # donation = models.CurrencyField(doc="Donation",
+    #                                 label="Möchten Sie einen Teil Ihres Verdienstes spenden? Wenn ja, wie viel?",
+    #                                 blank=True)

### 2021-06-21 oTree/Outro/pages.py

@@ -27,7 +27,6 @@ class Outro_CLICCS(Page):
 
 class Outro_Final(Page):
     form_model = "player"
-    form_fields = ["donation"]
 
     def vars_for_template(self):
         return dict(

### 2021-06-21 oTree/settings.py

@@ -5,17 +5,18 @@ SESSION_CONFIGS = [
         name="GMTV",
         display_name="GMTV Replication",
         num_rounds=10,
-        num_demo_participants=2,
+        num_demo_participants=4,
         risk=0.0,
         belief_elicitation=False,
         app_sequence=["Intro", "dPGG", "HLPL", "Outro"]
-    ), dict(
-        name="HLPL",
-        display_name="Hault & Laury Price List",
-        num_rounds=10,
-        num_demo_participants=1,
-        app_sequence=["HLPL"]
-    )
+    ),
+    #     dict(
+    #     name="HLPL",
+    #     display_name="Hault & Laury Price List",
+    #     num_rounds=10,
+    #     num_demo_participants=1,
+    #     app_sequence=["HLPL"]
+    # )
 ]
 
 # if you set a property in SESSION_CONFIG_DEFAULTS, it will be inherited by all configs

### 2021-06-22 reports/03_dataAnalyses.Rmd
work on covariates and plot layouts

@@
                 axis.line.y.left = element_line(size = 0.25),
-                plot.margin = unit(c(1,1,1,1), "cm"),
+                axis.title.y = element_text(size = rel(0.75)),
+                plot.margin = margin(c(0.25,0.25,0.25,0.25), "cm"),
                 legend.title = element_blank()
@@
   labs(y = "Average Amount of Tokens contributed") +
-  scale_color_manual(values = wes_palette("GrandBudapest1"))
+  scale_color_manual(values = wes_palette("GrandBudapest1")) + 
+  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
 
@@
 
-patchwork <- p1 + p2 & theme(legend.position = "bottom")
-patchwork <- patchwork + plot_layout(guides = "collect")
-patchwork
+p1 + p2 + plot_layout(guides = "collect") & theme(legend.position = "bottom")
 
@@
           model.numbers = FALSE,
-          dep.var.labels = "Wealth (Table 2)",
+          dep.var.labels = "Wealth",
           header=FALSE,
@@
 
-upperLimit <- STOCK$stock %>% max() %>% round() + 10
+STOCKr <- main[rich == TRUE,
+               lapply(.SD, mean, na.rm = TRUE),
+               by = c("round", "treatment"),
+               .SDcols = "stock"]
 
-ggplot(data = STOCK, 
+STOCKp <- main[rich == FALSE,
+               lapply(.SD, mean, na.rm = TRUE),
+               by = c("round", "treatment"),
+               .SDcols = "stock"]
+
+upperLimit <- STOCKr$stock %>% max() %>% round() + 20
+
+p1 <- ggplot(data = STOCK, 
        aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
@@
           labs(y = "Wealth") +
+          scale_color_manual(values = wes_palette("GrandBudapest1")) + 
+          theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
+
+p2 <- ggplot(data = STOCKr, 
+       aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
+          layout +
+          theme(legend.position="bottom") +
+          # geom_vline(xintercept = 10, alpha = 0.66) +
+          geom_line(show.legend=FALSE) +
+          geom_point() +
+          scale_x_continuous(name="",  breaks = 1:10) +
+          scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
+          labs(y = "Wealth (Rich)") +
           scale_color_manual(values = wes_palette("GrandBudapest1"))
 
-rm(list = c("STOCK"))
+p3 <- ggplot(data = STOCKp, 
+       aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
+          layout +
+          theme(legend.position="bottom") +
+          # geom_vline(xintercept = 10, alpha = 0.66) +
+          geom_line(show.legend=FALSE) +
+          geom_point() +
+          scale_x_continuous(name="",  breaks = 1:10) +
+          scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
+          labs(y = "Wealth (Poor)") +
+          scale_color_manual(values = wes_palette("GrandBudapest1"))
+
+(p1 | (p2 / p3)) + plot_layout(guides = "collect") & theme(legend.position = "bottom")
+
+rm(list = c("STOCK", "STOCKr", "STOCKp", "p1", "p2", "p3"))
 ```
@@
 
+GINIr <- main[rich == TRUE,
+              lapply(.SD, mean, na.rm = TRUE),
+              by = c("round", "treatment"),
+              .SDcols = "gini"]
+
+GINIp <- main[rich == FALSE,
+              lapply(.SD, mean, na.rm = TRUE),
+              by = c("round", "treatment"),
+              .SDcols = "gini"]
+
 upperLimit <- GINI$gini %>% max() %>% round(digits = 1) + 0.10
 
-ggplot(data = GINI, 
+p1 <- ggplot(data = GINI, 
        aes(x = round, y = gini, fill = treatment, color = treatment, lty = treatment)) +
@@
           scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-          labs(y = "Gini coefficient") +
+          labs(y = "Gini Coefficient") +
+          scale_color_manual(values = wes_palette("GrandBudapest1")) + 
+          theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
+
+p2 <- ggplot(data = GINIr, 
+       aes(x = round, y = gini, fill = treatment, color = treatment, lty = treatment)) +
+          layout +
+          theme(legend.position="bottom") +
+          # geom_vline(xintercept = 10, alpha = 0.66) +
+          geom_line(show.legend=FALSE) +
+          geom_point() +
+          scale_x_continuous(name="",  breaks = 1:10) +
+          scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
+          labs(y = "Gini (Rich)") +
           scale_color_manual(values = wes_palette("GrandBudapest1"))
 
-rm(list = c("GINI"))
+p3 <- ggplot(data = GINIp, 
+       aes(x = round, y = gini, fill = treatment, color = treatment, lty = treatment)) +
+          layout +
+          theme(legend.position="bottom") +
+          # geom_vline(xintercept = 10, alpha = 0.66) +
+          geom_line(show.legend=FALSE) +
+          geom_point() +
+          scale_x_continuous(name="",  breaks = 1:10) +
+          scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
+          labs(y = "Gini (Poor)") +
+          scale_color_manual(values = wes_palette("GrandBudapest1"))
+
+(p1 | (p2 / p3)) + plot_layout(guides = "collect") & theme(legend.position = "bottom")
+
+rm(list = c("GINI", "GINIp", "GINIr", "p1", "p2", "p3"))
 ```
@@
           model.numbers = FALSE,
-          dep.var.labels = "Wealth (Table 2)",
+          dep.var.labels = "Gini",
           header=FALSE,
@@
 ## Sample Properties
+
+```{r matchOutcomes}
+covariates <- data.table::merge.data.table(x  = covs,
+                                           y  = main[round == 10, .(groupID, stock, gini)],
+                                           by = c("groupID"),
+                                           allow.cartesian = TRUE)
+```
+
+```{r tableCovariates, results = "asis", warning = FALSE}
+
+# create table
+if(knitr::is_html_output()){
+  type <- "html"
+} else {
+  type = "latex"
+}
+
+olsStock1 <- lm(formula = stock ~ gender + age + pq01 + pq02 + pq03 + pq04 + pq05 + pq06 +
+                  pq07 +pq08 + pq09 + pq10 + pq11 + pq12 + pq13 + pq14, 
+                data = covariates[treatment == "replication"])
+olsStock2  <- lm(formula = stock ~ gender + age,
+                data = covariates[treatment == "replication"])
+olsGINI1  <- lm(formula = gini ~ gender + age + pq01 + pq02 + pq03 + pq04 + pq05 + pq06 +
+                  pq07 + pq08 + pq09 + pq10 + pq11 + pq12 + pq13 + pq14, 
+                data = covariates[treatment == "replication"])
+olsGINI2  <- lm(formula = gini ~ gender + age,
+                data = covariates[treatment == "replication"])
+
+stargazer(olsStock1, olsStock2,
+          olsGINI1, olsGINI2,
+
+          se = list(coef(summary(olsStock1, cluster = c("groupID")))[, 2],
+                    coef(summary(olsStock2, cluster = c("groupID")))[, 2],
+                    coef(summary(olsGINI1,  cluster = c("groupID")))[, 2],
+                    coef(summary(olsGINI2,  cluster = c("groupID")))[, 2]),
+
+          column.labels   = c("Wealth", "Gini"),
+          dep.var.labels.include = FALSE,
+          column.separate = c(2, 2),
+          model.numbers = FALSE,
+          header=FALSE,
+          covariate.labels = c("female", "age", 
+                               "I am a quick thinker",
+                               "I get easily offended",
+                               "very satisfied",
+                               "very dependent",
+                               "generally happy",
+                               "work important",
+                               "family important",
+                               "friends important",
+                               "religion important",
+                               "politics important",
+                               "most people trusted",
+                               "hard work better",
+                               "government responsible",
+                               "incomes equal"),
+          notes = "Robust standard errors in parentheses, clustered by group ID.",
+
+          type = type, digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
+          )
+```

### 2021-06-22 reports/03_dataAnalyses.Rmd
change color palette & generate new data

@@
 library(ggplot2)
-library(wesanderson)
 library(patchwork)
@@
                 axis.title.y = element_text(size = rel(0.75)),
-                plot.margin = margin(c(0.25,0.25,0.25,0.25), "cm"),
+                plot.margin = unit(c(0.25,0.25,0.25,0.25), "cm"),
                 legend.title = element_blank()
                 )
+
+colors <- c("#F3B05C", "#1E4A75", "#65B5C0", "#AD5E21")
 ```
@@
 ```{r firstRound, eval = FALSE}
-ggplot(R1, aes(y=othersContribution, x=belief)) +
-  layout +
-  geom_abline(intercept = 0, slope = 1, linetype="dashed", alpha = 0.66) +
-  geom_point() +
-  geom_point(color = wes_palette("Moonrise3")[1]) +
-  scale_y_continuous(expand = c(0, 0), limits = c(0, 60)) +
-  scale_x_continuous(expand = c(0, 0), limits = c(0, 60))
-
-ggplot(R1, aes(y=ownContribution, x=belief/3)) +
-  layout +
-  geom_abline(intercept = 0, slope = 1, linetype="dashed", alpha = 0.66)+ 
-  geom_point() +
-  geom_point(color = wes_palette("Moonrise3")[1]) +
-  scale_y_continuous(expand = c(0, 0), limits = c(0, 25)) +
-  scale_x_continuous(expand = c(0, 0), limits = c(0, 25))
-
 ggplot(R1, aes(y=ownContribution, x=othersContribution/3)) +
@@
   geom_abline(intercept = 0, slope = 1, linetype="dashed", alpha = 0.66) +
-  geom_point(color = wes_palette("Moonrise3")[1]) +
+  geom_point(color = colors) +
   scale_y_continuous(expand = c(0, 0), limits = c(-1, 25)) +
@@
   labs(y = "Average Amount of Tokens contributed") +
-  scale_color_manual(values = wes_palette("GrandBudapest1")) + 
+  scale_color_manual(values = colors) + 
   theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
@@
   labs(y = "Share of Current Endowment contributed") +
-  scale_color_manual(values = wes_palette("GrandBudapest1"))
+  scale_color_manual(values = colors)
 
@@
           labs(y = "Wealth") +
-          scale_color_manual(values = wes_palette("GrandBudapest1")) + 
+          scale_color_manual(values = colors) + 
           theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
@@
           labs(y = "Wealth (Rich)") +
-          scale_color_manual(values = wes_palette("GrandBudapest1"))
+          scale_color_manual(values = colors)
 
@@
           labs(y = "Wealth (Poor)") +
-          scale_color_manual(values = wes_palette("GrandBudapest1"))
+          scale_color_manual(values = colors)
 
@@
           labs(y = "Gini Coefficient") +
-          scale_color_manual(values = wes_palette("GrandBudapest1")) + 
+          scale_color_manual(values = colors) + 
           theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
@@
           labs(y = "Gini (Rich)") +
-          scale_color_manual(values = wes_palette("GrandBudapest1"))
+          scale_color_manual(values = colors)
 
@@
           labs(y = "Gini (Poor)") +
-          scale_color_manual(values = wes_palette("GrandBudapest1"))
+          scale_color_manual(values = colors)
 

### 2021-06-23 reports/01_dataGMTV.Rmd
add risk measure, change reports file structure

--- 2021-06-21 reports/01_replication.Rmd
@@
 
+# Risk
+
+```{r calcSwitchingPoint}
+GMTVRisk <- CT[exp_num == 5 | exp_num == 8 | exp_num == 9,
+               .(participant.code = subj_id,
+                 e10, e20, e30, e40, e50, e60, e70,
+                 inconsistent = ifelse(test = e60 < e70 | e50 < e60 | e40 < e50 | e30 < e40 | e20 < e30 | e10 < e20,
+                                       yes  = TRUE,
+                                       no   = FALSE)
+                 )]
+
+GMTVRisk[,
+         switching_row := ifelse(test = inconsistent == TRUE,
+                                yes  = NA,
+                                no   = e10 + e20 + e30 + e40 + e50 + e60 + e70 + 1)
+         ]
+```
+
 # Covariates
@@
 ```{r subsetCovs}
-GMTVCovariates <- CT[exp_num == 5 | exp_num == 8 | exp_num == 9,
+temp <- CT[exp_num == 5 | exp_num == 8 | exp_num == 9,
                          .(treatment = "noPunish10",
@@
 
+temp[donation %>% is.na, donation := 0]
+
+```
+
+```{r mergeAndWrite}
+
+GMTVCovariates <- data.table::merge.data.table(x = temp,
+                                               y = GMTVRisk[, .(participant.code, inconsistent, switching_row)],
+                                               by = c("participant.code"))
+
 # write data

### 2021-06-23 reports/02_dataProcessing.Rmd
work on covariates and plot layouts
add risk measure, change reports file structure

@@
 # subset
-cRegex <- "participant.code|session.code|treatment|groupID|Outro.1.player|10.player.donation"
+cRegex <- "participant.code|session.code|treatment|groupID|Outro.1.player|10.player.donation|switching_row|inconsistent"
 covariates <- str_subset(string = names(DT),
@@
 CT[, donation := donation/20]
+CT[donation %>% is.na, donation := 0]
 
@@
                       no   = 0)]
+
+CT[, inconsistent := as.logical(inconsistent)]
 

### 2021-06-23 reports/03_dataAnalyses.Rmd
add risk measure, change reports file structure

@@
 layout <- theme(panel.background = element_rect(fill = "white"),
-                panel.grid = element_line(colour="gray", size=0),
+                panel.grid = element_blank(),
                 panel.grid.major.y = element_line(colour="gray", size=0.25),
@@
                                            allow.cartesian = TRUE)
+
+covariates[,
+           gender := gender %>% as.numeric()]
+
+```
+
+```{r summary3, results = "asis"}
+
+# create table
+if(knitr::is_html_output()){
+  type <- "html"
+} else {
+  type = "latex"
+}
+
+temp <- covariates[treatment == "replication",
+                   .(gender, age, switching_row, education, donation, pq01, pq02, pq03, pq04,
+                     pq05, pq06, pq07, pq08, pq09, pq10, pq11, pq12, pq13, pq14)]
+stargazer(temp, type = type, flip = FALSE)
+
 ```
@@
 
-olsStock1 <- lm(formula = stock ~ gender + age + pq01 + pq02 + pq03 + pq04 + pq05 + pq06 +
-                  pq07 +pq08 + pq09 + pq10 + pq11 + pq12 + pq13 + pq14, 
+olsStock1 <- lm(formula = stock ~ gender + age + switching_row + pq01 + pq02 + pq03 + pq04 + 
+                  pq05 + pq06 + pq07 +pq08 + pq09 + pq10 + pq11 + pq12 + pq13 + pq14, 
                 data = covariates[treatment == "replication"])
-olsStock2  <- lm(formula = stock ~ gender + age,
+olsStock2  <- lm(formula = stock ~ gender + age + switching_row,
                 data = covariates[treatment == "replication"])
-olsGINI1  <- lm(formula = gini ~ gender + age + pq01 + pq02 + pq03 + pq04 + pq05 + pq06 +
-                  pq07 + pq08 + pq09 + pq10 + pq11 + pq12 + pq13 + pq14, 
+olsGINI1  <- lm(formula = gini ~ gender + age + switching_row + pq01 + pq02 + pq03 + pq04 +
+                  pq05 + pq06 + pq07 + pq08 + pq09 + pq10 + pq11 + pq12 + pq13 + pq14, 
                 data = covariates[treatment == "replication"])
-olsGINI2  <- lm(formula = gini ~ gender + age,
+olsGINI2  <- lm(formula = gini ~ gender + age + switching_row,
                 data = covariates[treatment == "replication"])
@@
           header=FALSE,
-          covariate.labels = c("female", "age", 
+          covariate.labels = c("female", "age", "risk",
                                "I am a quick thinker",

### 2021-06-23 analysis/R/source.R

@@ -1,14 +1,41 @@
 rm(list = ls())
 
-source("R/config.R")
-source("R/data.R")
-source("R/gaechteretal.R", echo = TRUE)
-source("R/viz.R")
+# source("R/config.R")
+# source("R/data.R")
+# source("R/gaechteretal.R", echo = TRUE)
+# source("R/viz.R")
 
-# install.packages("DescTools")
-# library(DescTools)
-# create_article("../reports/researchProposal.Rmd")
+library(rmarkdown)
+library(distill)
 
-rmarkdown::render(input = "../reports/Treatments.Rmd",
-                  output_format = "all",
-                  output_file = "Treatments")
+# Render HTML Report -----
+rmarkdown::render(input = "../reports/01_dataGMTV.Rmd",
+                  output_format = "distill_article",
+                  output_dir = "../reports/html/",
+                  output_file = "01_GMTV")
+
+rmarkdown::render(input = "../reports/02_dataProcessing.Rmd",
+                  output_format = "distill_article",
+                  output_dir = "../reports/html/",
+                  output_file = "02_Replication")
+
+rmarkdown::render(input = "../reports/03_dataAnalyses.Rmd",
+                  output_format = "distill_article",
+                  output_dir = "../reports/html/",
+                  output_file = "03_Analyses")
+
+# Render PDF Report -----
+rmarkdown::render(input = "../reports/01_dataGMTV.Rmd",
+                  output_format = "pdf_document",
+                  output_dir = "../reports/pdf/",
+                  output_file = "01_GMTV")
+
+rmarkdown::render(input = "../reports/02_dataProcessing.Rmd",
+                  output_format = "pdf_document",
+                  output_dir = "../reports/pdf/",
+                  output_file = "02_Replication")
+
+rmarkdown::render(input = "../reports/03_dataAnalyses.Rmd",
+                  output_format = "pdf_document",
+                  output_dir = "../reports/pdf/",
+                  output_file = "03_Analyses")

### 2021-06-23 oTree/HLPL/tests.py

@@ -2,6 +2,7 @@ from otree.api import Currency as c, currency_range
 from . import pages
 from ._builtin import Bot
 from .models import Constants
+import random
 
 
 class PlayerBot(Bot):
@@ -11,7 +12,7 @@ class PlayerBot(Bot):
                                              choice_3="lottery",
                                              choice_4="lottery",
                                              choice_5="lottery",
-                                             choice_6="certainty",
+                                             choice_6= random.choice(["lottery", "certainty"]),
                                              choice_7="certainty",
                                              choice_8="certainty",
                                              choice_9="certainty",

### 2021-06-23 oTree/Outro/tests.py

@@ -21,7 +21,7 @@ class PlayerBot(Bot):
                                             PQ13=random.randint(0, 6),
                                             PQ14=random.randint(0, 6))
         yield pages.Outro_Covariates, dict(Age=random.randint(18, 66),
-                                           Gender="diverse",
+                                           Gender=random.choice(["diverse", "male", "female", "not specified"]),
                                            Education=random.randint(0, 8),
                                            Income=random.randint(0, 5))
         yield pages.Outro_CLICCS, dict(CLICCS1="lorem ipsum 1", CLICCS2="lorem ipsum 2")

### 2021-06-23 analysis/R/source.R
render PDF

@@ -25,15 +25,15 @@ rmarkdown::render(input = "../reports/03_dataAnalyses.Rmd",
                   output_file = "03_Analyses")
 
 # Render PDF Report -----
-rmarkdown::render(input = "../reports/01_dataGMTV.Rmd",
-                  output_format = "pdf_document",
-                  output_dir = "../reports/pdf/",
-                  output_file = "01_GMTV")
-
-rmarkdown::render(input = "../reports/02_dataProcessing.Rmd",
-                  output_format = "pdf_document",
-                  output_dir = "../reports/pdf/",
-                  output_file = "02_Replication")
+# rmarkdown::render(input = "../reports/01_dataGMTV.Rmd",
+#                   output_format = "pdf_document",
+#                   output_dir = "../reports/pdf/",
+#                   output_file = "01_GMTV")
+# 
+# rmarkdown::render(input = "../reports/02_dataProcessing.Rmd",
+#                   output_format = "pdf_document",
+#                   output_dir = "../reports/pdf/",
+#                   output_file = "02_Replication")
 
 rmarkdown::render(input = "../reports/03_dataAnalyses.Rmd",
                   output_format = "pdf_document",

### 2021-06-24 reports/01_dataGMTV.Rmd
recalculate gini using the stock instead of the endowments

@@
 
+# calculate gini based on endowments (as GMTV did)
 noPunish10[,
@@
 
+# calculate gini based on stock (i.e. end of period earnings)
+noPunish10[, stock0 := tokens - putin + sum/4]
+noPunish10[, stock1 := other1 - pu1 + sum/4]
+noPunish10[, stock2 := other2 - pu2 + sum/4]
+noPunish10[, stock3 := other3 - pu3 + sum/4]
+
+noPunish10[, 
+           gini3 := Gini(c(stock0, stock1, stock2, stock3)),
+           by = .(subj_id, per)]
+
+# show table
 noPunish10[order(gr_id, per),
@@
              putin, pu1, pu2, pu3, sum, mean, share, # contributions
-             gini, gini2
+             gini, gini2, gini3
            )] %>% 
@@
              gain = (ceiling(sum/4*1.5)*4-sum),
-             gini = gini2,
+             gini = gini3,
              bot_active = 0,

### 2021-06-24 reports/02_dataProcessing.Rmd
recalculate gini using the stock instead of the endowments

@@
 ```{r calcGini}
-# it would make more sense to calculate the stocks' gini but gaechter et al use the endowments
-var = names(subset) %>% str_subset(pattern = "player\\.endowment$")
+# note that GMTV used start of period earnnings, i.e. endowments. We use end of period earnings, i.e. stock.
+# this adjustment has been considered in our processing of GMTVs data.
+
+var = names(subset) %>% str_subset(pattern = "player\\.stock$")
 gini = subset[,

### 2021-06-24 reports/03_dataAnalyses.Rmd
recalculate gini using the stock instead of the endowments

@@
 ```{r readData}
-load(file="../data/processed/rda/GMTV2017.rda")          # read GMTV
-load(file="../data/processed/rda/GMTV2017_R1.rda")       # read GMTVFirstRound
-load(file="../data/processed/rda/GMTV2017_COVS.rda")     # read GMTVCovariates
-load(file="../data/processed/rda/replication2021.rda")       # read replication
-load(file="../data/processed/rda/replication2021_R1.rda")    # read replicationFirstRound
-load(file="../data/processed/rda/replication2021_COVS.rda")  # read replicationCovariates
+base::load(file="../data/processed/rda/GMTV2017.rda")              # read GMTV
+base::load(file="../data/processed/rda/GMTV2017_R1.rda")           # read GMTVFirstRound
+base::load(file="../data/processed/rda/GMTV2017_COVS.rda")         # read GMTVCovariates
+base::load(file="../data/processed/rda/replication2021.rda")       # read replication
+base::load(file="../data/processed/rda/replication2021_R1.rda")    # read replicationFirstRound
+base::load(file="../data/processed/rda/replication2021_COVS.rda")  # read replicationCovariates
 ```

### 2021-06-24 analysis/R/config.R

@@ -20,7 +20,9 @@ listOfPackages <- c("renv",          # package management
                     "sjPlot",        # regression tables
                     "stargazer",     # regression tables
                     "plm",           # clustered standard errors
-                    "lmtest"
+                    "lmtest",
+                    "DescTools",     # gini coefficient
+                    "downloadthis"   # download button 4 HTML reports
                     )
 
 

### 2021-06-24 analysis/R/source.R

@@ -1,12 +1,6 @@
 rm(list = ls())
 
-# source("R/config.R")
-# source("R/data.R")
-# source("R/gaechteretal.R", echo = TRUE)
-# source("R/viz.R")
-
-library(rmarkdown)
-library(distill)
+source("R/config.R")
 
 # Render HTML Report -----
 rmarkdown::render(input = "../reports/01_dataGMTV.Rmd",

### 2021-06-29 analysis/reports/00_reproduction.Rmd
Restructure the Project's Analysis

--- 2021-06-20 reports/00_reproduction.Rmd
@@
 Subsequently, [data excerpts](#Tables) will demonstrate that the original _Gini coefficient_ varies within groups (in selected periods) and the _share of current endowment contributed_ is calculated using the last round's endowment.
-[Afterwards](#Downloads), the data is processsed and made available for downloads.The [Visualizations](#Visualizations) chapter will then present the original figures as well as figures reproduced using the original and re-calculated variables to demonstrate differences.
+[Afterwards](#Downloads), the data is processed and made available for downloads.The [Visualizations](#Visualizations) chapter will then present the original figures as well as figures reproduced using the original and re-calculated variables to demonstrate differences.
 
@@
 
-GMTV <- read_dta(file="../data/gaechteretal/GMTV-data.dta") %>% data.table()
+GMTV <- read_dta(file="../../data/gaechteretal/GMTV-data.dta") %>% data.table()
 
@@
 ```
+
 ```{r summary1, results = "asis", warning = FALSE}

### 2021-06-29 analysis/reports/differences.Rmd
Restructure the Project's Analysis

---
title: "Growth & Inequality in Dynamic Public Goods Games"
description: |
  Reproducing Gächter et al.'s main findings.
author:
  - name: Hauke Roggenkamp 
    url: https://github.com/Howquez
    affiliation: CLICCS
    affiliation_url: https://www.cliccs.uni-hamburg.de/
date: "`r Sys.Date()`"
bibliography: biblio.bib
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: false
    code_folding: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(haven)
library(data.table)
library(magrittr)
library(kableExtra)
library(DescTools) # gini coefficient
library(downloadthis)
library(stringr)
# library(Rmisc)
library(ggplot2)
library(highcharter)
library(wesanderson)
library(patchwork)
library(sjPlot)

GMTV <- read_dta(file="../data/gaechteretal/GMTV-data.dta") %>% data.table()
```

# Introduction

In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree]. The first experiment will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances). The current demo version of the experiment can be found [here](https://cliccs.herokuapp.com/). Click [here](https://github.com/Howquez/coopUncertainty) to visit the corresponding Github repository.

This document explores the data provided by @GACHTER2017 and finds that some of the variables are a little off. In addition, it fails to replicate the orginal article's figures. The following chapter will describe the available data. Subsequently, [data excerpts](#Tables) will demonstrate that the original _Gini coefficient_ varies within groups (in selected periods) and the _share of current endowment contributed_ is calculated using the last round's endowment. [Afterwards](#Downloads), the data is processsed and made available for downloads.The [Visualizations](#Visualizations) chapter will then present the original figures as well as figures reproduced using the original and re-calculated variables to demonstrate differences.

# Original Data

## Description

The data can be found in the supplementary materials they provide in the [online appendix](https://www.sciencedirect.com/science/article/pii/S0047272717300361#s0115) and contains, among others, the following variables:

- ```exp_num``` is a session identifier
- ```per``` denotes the period
- ```gr_id``` is a group identifier (carrying treatment information)
- ```subj_id``` is a subject identifier
- ```tokens``` reports a subject's endowment in a period
- ```other[1-3]``` report the other group members' endowments in a period
- ```gdp ``` equals the sum of endowments of a group in a period
- ```putin``` reports a subject's contribution in a period
- ```pu[1-3]``` report the other group members' contributions in a period
- ```sum``` equals the sum of contributions of a group in a period
- ```gini``` reports a group's Gini coefficient in a period
- ```mean``` reports the fraction of sum/lagged(gdp)
- ```totallost``` ?

I add three new measures,namely: ```gini2```, ```mean2``` and ```gpd2```. ```gini2``` differs from the original as it is constant within groups. ```mean2``` is equivalent to the original ```mean``` but relies on the current ```gdp``` instead of the lagged one. In addition to the ```gpd``` (stating the endowment at the beginning of a period), I calculate ```gpd2``` for the noPunish treatments and thereby report the income at the end of a period. Finally, I create a ```treatment``` string-variable .

```{r createVars, include = FALSE}
# treatments

  GMTV[punish == 0 & longgame == 0, # exp_num == 5 | exp_num == 8 | exp_num == 9,
       treatment := "noPunish10"]

  GMTV[punish == 0 & longgame == 1, # exp_num == 1 | exp_num == 3,
       treatment := "noPunish15"]

  GMTV[punish == 1 & longgame == 0, # exp_num == 4 | exp_num == 6 | exp_num == 10,
       treatment := "Punish10"]

  GMTV[punish == 1 & longgame == 1, # exp_num == 2 | exp_num == 7,
       treatment := "Punish15"]

# gdp, mean & gini
  GMTV[treatment == "noPunish10" | treatment == "noPunish15",
       gdp2 := (gdp + ceiling(sum/4*1.5)*4-sum)]

  GMTV[,
       mean2 := sum/gdp]

  GMTV[,
       gini2 := Gini(c(tokens, other1, other2, other3)),
       by = .(treatment, gr_id, per)]

# rearrange & subset
GMTV <- GMTV[order(treatment, gr_id, per),
             .(treatment, treat, punish, longgame,        # treatment vars 
               exp_num, gr_id, per, subj_id,              # IDs
               tokens, other1, other2, other3, gdp, gdp2, # endowments
               putin, pu1, pu2, pu3, sum, mean, mean2,    # contributions
               gini, gini2,                               # ginis
               totallost,                                 # punishment var
               highgdp
              )]
```

## Excerpts {#Tables}

The first few rows of the resulting data look as follows:

```{r showData, layout = "l-body-outset"}

GMTV[gr_id == 501] %>% 
  head(n = 10) %>%
  kbl() %>% 
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)

```

The Table shows group 501 in the first two periods where subjects 511 to 514 start with an initial endowment of 20 which makes a GDP of 80. Subject 511 does not contribute (as represented in ```putin==0``` in the first row and ```pu1==0```in rows 2 to 4) while the others contribute 5, 15 and 15 in the first period, respectively. The ```sum``` of contributions therefore equals 35 period 1.

With a sum of contributions being 35 and a return of contributions of 1.5, each subject receives ```ceil(13.125)``` =14 points from the group project such that the next period's ```gdp``` equals 101.

The Gini coefficient (```gini```) is a little off as one can see in the second period: Even though this is a group level variable, the group has three different coefficient levels in the same period.

The mean is calculated such that it can be interpreted as the _share of past endowments contributed_. This differs from the interpretation in the paper's [Figure 1 Panel (b)](https://www.sciencedirect.com/science/article/pii/S0047272717300361#f0005). Furthermore, the ```mean``` can take values greater than one which becomes  clear if one focuses on group 402 in the Table below:

```{r showData2, layout = "l-body-outset"}

GMTV[gr_id == 402 & per > 4] %>% 
  head(n = 8) %>%
  kbl() %>% 
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)

```

The Table above shows the group members contributing almost all of their current endowments, which leads to significant growth. Using the lagged ```gdp``` as a denominator, the ```mean``` is larger than 1 and thus, considerably greater than _share of current endowment contributed_ could possibly be.

# Data Processing {#Downloads}

To reproduce the main visualizations of the paper, I change the unit of observations to groups such that subject-level variables will be dropped. Because the ```gini``` has shown to differ within groups and periods, I 'll report its average in what follows. Furthermore, I'll subset the data and only consider the first ten, that is, the original experiment-sessions.

```{r aggregateData, layout = "l-body-outset"}

# set gini to group average
GMTV[,
     gini := mean(gini, na.rm = TRUE),
     by = c("treatment", "exp_num", "gr_id", "per")]

# remove duplicate rows while subsetting only group level variables
GMTVgroups <- GMTV[exp_num <= 10,
                   .(treatment,
                     treat,
                     punish = as.logical(punish),
                     longgame = as.logical(longgame),
                     exp_num,
                     gr_id,
                     per,
                     sum,
                     gdp,
                     mean,
                     mean2,
                     gini,
                     gini2,
                     highgdp = as.logical(highgdp))] %>% unique()

# show
GMTVgroups %>%
  head(n = 10) %>%
  kbl() %>% 
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)

```

You can download the data here:

```{r downloadData}
GMTV %>%
      download_this(
        output_name = "GMTV_individuals",
        output_extension = ".csv", # CSV output
        button_label = "individual data",
        button_type = "default"
        )

GMTVgroups %>%
      download_this(
        output_name = "GMTV_groups",
        output_extension = ".csv", # CSV output
        button_label = "group data",
        button_type = "default"
        )
```

# Figures

The following code chunks aim to reproduce some of the panels presented in the original paper's figures. Reproducing [Figure 2 Panel (a)](https://www.sciencedirect.com/science/article/pii/S0047272717300361#f0010) is relatively simple as the corresponding ```gdp``` is free of doubt. The ```mean``` and ```gini``` in contrast, need some [additional attention](#Visualizations).

```{r}
layout <- theme(panel.background = element_rect(fill = "white"),
                panel.grid = element_line(colour="gray", size=0),
                panel.grid.major.y = element_line(colour="gray", size=0.25),
                legend.key = element_rect(fill = "white"),
                axis.line.x.bottom = element_line(size = 0.25),
                axis.line.y.left = element_line(size = 0.25),
                # plot.margin = unit(c(1,1,1,1), "cm"),
                legend.title = element_blank()
                )
```

## Pure Reproductions?

![Original Figure 2 (a)](../gaechterSupplementaryMaterials/Figures/Figure2a.jpeg)

```{r plotGDP, layout="l-body", fig.cap="Figure 2 (a) using original data"}

GDP <- GMTVgroups[,
                    lapply(.SD, mean, na.rm = TRUE),
                    by = c("per", "treatment", "punish", "longgame"),
                    .SDcols = "gdp"]

GDP[,
    gdp := round(gdp)]

hchart(GDP, "line", hcaes(x = per, y = gdp, group = treatment),
       dashStyle = c("solid", "solid", "longdash", "longdash")) %>%
  hc_yAxis(title = list(text = "Wealth"),
           min = 0, max = 3100, minTickInterval = 500) %>%
  hc_xAxis(title = list(text = "Period"),
           min = 0, max = 15, minTickInterval = 1,
           plotLines = list(list(
    value = 10
  ))) %>%
  hc_tooltip(shared = TRUE, headerFormat = "Period {point.key} <br>") %>%
  hc_colors(wes_palette("Zissou1")[1:4])

```

```{r plotStaticGDP, include = FALSE, layout="l-body"}
ggplot(data = GDP, aes(x = per, y = gdp, fill = treatment, color = treatment, lty = punish)) +
          layout +
          theme(legend.position="bottom") +
          geom_vline(xintercept = 10, alpha = 0.66) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="",  breaks = 1:15) +
          scale_y_continuous(breaks = seq(0, 3000, by = 500), limits = c(0, 3100), expand = c(0, 0)) +
          labs(y = "Wealth") +
          scale_color_manual(values = wes_palette("Zissou1"))
```

![Original Figure 1 (a)](../gaechterSupplementaryMaterials/Figures/Figure1a.jpeg)

```{r plotSum, layout="l-body", fig.cap="Figure 1 (a) using original data"}

SUM <- GMTVgroups[,
                    lapply(.SD, mean, na.rm = TRUE),
                    by = c("per", "treatment", "punish", "longgame"),
                    .SDcols = "sum"]

SUM[,
    sum := round(sum/4)]

hchart(SUM, "line", hcaes(x = per, y = sum, group = treatment),
       dashStyle = c("solid", "solid", "longdash", "longdash")) %>%
  hc_yAxis(title = list(text = "Average Amount of Tokens contributed"),
           min = 0, max = 150, minTickInterval = 50) %>%
  hc_xAxis(title = list(text = "Period"),
           min = 0, max = 15, minTickInterval = 1,
           plotLines = list(list(
    value = 10
  ))) %>%
  hc_tooltip(shared = TRUE, headerFormat = "Period {point.key} <br>") %>%
  hc_colors(wes_palette("Zissou1")[1:4])

```

```{r plotStaticSum, include = FALSE, layout="l-body"}
ggplot(data = SUM, aes(x = per, y = sum, fill = treatment, color = treatment, lty = punish)) +
          layout +
          theme(legend.position="bottom") +
          geom_vline(xintercept = 10, alpha = 0.66) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="",  breaks = 1:15) +
          scale_y_continuous(breaks = seq(0, 150, by = 50), limits = c(0, 170), expand = c(0, 0)) +
          labs(y = "Average Amount of Tokens contributed") +
          scale_color_manual(values = wes_palette("Zissou1"))
```

## Implications {#Visualizations}

What changes if one defines the ```mean``` as well as the ```gini``` differently? The following Figure illustrates the share of past endowments contributed in the left panel as well as the share of current endowments contributed in the right panel. Both panels correspond to [Figure 1 Panel (b)](https://www.sciencedirect.com/science/article/pii/S0047272717300361#f0005) and illustrate the share over time.

![Original Figure 1 (b)](../gaechterSupplementaryMaterials/Figures/Figure1b.jpeg)

```{r plotMean, layout="l-body", fig.cap="Figure 1 (b) using original data"}
means <- GMTVgroups[,
                    lapply(.SD, mean, na.rm = TRUE),
                    by = c("per", "treatment", "punish", "longgame"),
                    .SDcols = c("mean", "mean2")]

means[, mean := round(mean, digits = 2)]
means[, mean2 := round(mean2, digits = 2)]

# plots
mean <- hchart(means, "line", hcaes(x = per, y = mean, group = treatment),
               dashStyle = c("solid", "solid", "longdash", "longdash")) %>%
  hc_yAxis(title = list(text = "Share of Past Endowment contributed"),
           min = 0, max = 1.1, minTickInterval = 0.2) %>%
  hc_xAxis(title = list(text = "Period"),
           min = 0, max = 15, minTickInterval = 1,
           plotLines = list(list(
    value = 10
  ))) %>%
  hc_tooltip(shared = TRUE, headerFormat = "Period {point.key} <br>") %>%
  hc_colors(wes_palette("Zissou1")[1:4])

mean
```

```{r  plotMean2, layout="l-body", fig.cap="Figure 1 (b) using re-calculated data"}

mean2 <- hchart(means, "line", hcaes(x = per, y = mean2, group = treatment),
               dashStyle = c("solid", "solid", "longdash", "longdash")) %>%
  hc_yAxis(title = list(text = "Share of Current Endowment contributed"),
           min = 0, max = 1.1, minTickInterval = 0.2) %>%
  hc_xAxis(title = list(text = "Period"),
           min = 0, max = 15, minTickInterval = 1,
           plotLines = list(list(
    value = 10
  ))) %>%
  hc_tooltip(shared = TRUE, headerFormat = "Period {point.key} <br>") %>%
  hc_colors(wes_palette("Zissou1")[1:4])

mean2
```

```{r plotMeans, include = FALSE}
# view
hw_grid(
  mean, mean2,
  ncol = 2,
  rowheight = NULL,
  add_htmlgrid_css = TRUE,
  browsable = TRUE
)
```

```{r plotStaticMeans, include = FALSE, layout="l-body"}
mean <- ggplot(data = means, aes(x = per, y = mean, fill = treatment, color = treatment, lty = punish)) +
          layout +
          theme(legend.position="none") +
          geom_vline(xintercept = 10, alpha = 0.66) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="",  breaks = 1:15) +
          scale_y_continuous(breaks = seq(0, 1, by = 0.2), limits = c(0, 1.1), expand = c(0, 0)) +
          labs(y = "Share of Endowment contributed") +
          scale_color_manual(values = wes_palette("Zissou1"))

mean2 <- ggplot(data = means, aes(x = per, y = mean2, fill = treatment, color = treatment, lty = punish)) +
          layout +
          theme(legend.position="none") +
          geom_vline(xintercept = 10, alpha = 0.66) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="", breaks = 1:15) +
          scale_y_continuous(breaks = seq(0, 1, by = 0.2), limits = c(0, 1.1), expand = c(0, 0)) +
          labs(y = "") +
          scale_color_manual(values = wes_palette("Zissou1"))

patchwork <- mean + mean2 & theme(legend.position = "bottom")
patchwork <- patchwork + plot_layout(guides = "collect")
patchwork
```

Note that there are some groups in the punishment treatments that (almost) went bankrupt. Having endowments of one or two tokens, even low contributions become _relatively_ large. This may drive differences between treatments in any measure of the _share of endowments contributed_.

Just as in [Figure 3 Panel (a)](https://www.sciencedirect.com/science/article/pii/S0047272717300361#f0015), the following figure illustrates the two Gini coefficients over time. The left panel visualizes the group-level mean of original variable, while the right panel shows the re-calculated one.

![Original Figure 3 (a)](../gaechterSupplementaryMaterials/Figures/Figure3a.jpeg)

```{r plotGini, layout="l-body", fig.cap="Figure 3 (a) using original data"}
ginis <- GMTVgroups[,
                    lapply(.SD, mean, na.rm = TRUE),
                    by = c("per", "treatment", "punish", "longgame"),
                    .SDcols = c("gini", "gini2")]

ginis[, gini := round(gini, digits = 2)]
ginis[, gini2 := round(gini2, digits = 2)]

# plots
gini <- hchart(ginis, "line", hcaes(x = per, y = gini, group = treatment),
               dashStyle = c("solid", "solid", "longdash", "longdash")) %>%
  hc_yAxis(title = list(text = "Original Gini Coefficients"),
           min = 0, max = 0.4, minTickInterval = 0.1) %>%
  hc_xAxis(title = list(text = "Period"),
           min = 0, max = 15, minTickInterval = 1,
           plotLines = list(list(
    value = 10
  ))) %>%
  hc_tooltip(shared = TRUE, headerFormat = "Period {point.key} <br>") %>%
  hc_colors(wes_palette("Zissou1")[1:4])

gini
```

```{r plotGini2, layout="l-body", fig.cap="Figure 3 (a) using re-calculated data"}

gini2 <- hchart(ginis, "line", hcaes(x = per, y = gini2, group = treatment),
               dashStyle = c("solid", "solid", "longdash", "longdash")) %>%
  hc_yAxis(title = list(text = "Re-calculated Gini Coefficients"),
           min = 0, max = 0.4, minTickInterval = 0.1) %>%
  hc_xAxis(title = list(text = "Period"),
           min = 0, max = 15, minTickInterval = 1,
           plotLines = list(list(
    value = 10
  ))) %>%
  hc_tooltip(shared = TRUE, headerFormat = "Period {point.key} <br>") %>%
  hc_colors(wes_palette("Zissou1")[1:4])

gini2
```

```{r plotGinis, include = FALSE}

# view 
# hw_grid(
#   gini, gini2,
#   ncol = 2,
#   rowheight = NULL,
#   add_htmlgrid_css = TRUE,
#   browsable = TRUE
# )

```

```{r plotStaticGinis, include = FALSE, layout="l-body"}
# plot
gini <- ggplot(data = ginis, aes(x = per, y = gini, fill = treatment, color = treatment, lty = punish)) +
          layout +
          theme(legend.position="none") +
          geom_vline(xintercept = 10, alpha = 0.66) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="",  breaks = 1:15) +
          scale_y_continuous(breaks = seq(0, 0.4, by = 0.1), limits = c(0, 0.4), expand = c(0, 0)) +
          labs(y = "Gini coefficient") +
          scale_color_manual(values = wes_palette("Zissou1"))

gini2 <- ggplot(data = ginis, aes(x = per, y = gini2, fill = treatment, color = treatment, lty = punish)) +
          layout +
          theme(legend.position="none") +
          geom_vline(xintercept = 10, alpha = 0.66) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="", breaks = 1:15) +
          scale_y_continuous(breaks = seq(0, 0.4, by = 0.1), limits = c(0, 0.4), expand = c(0, 0)) +
          labs(y = "") +
          scale_color_manual(values = wes_palette("Zissou1"))

patchwork <- gini + gini2 & theme(legend.position = "bottom")
patchwork <- patchwork + plot_layout(guides = "collect")
patchwork
```

# Tables

Table 2: OLS Regression Wealth ✅

```{r olsWealth}
m2.1  <- lm(gdp ~ punish, data = GMTVgroups[longgame == 0 & treat < 3 & per == 10])
m2.2  <- lm(gdp ~ punish, data = GMTVgroups[longgame == 0 & treat < 3 & per == 10 & highgdp == 0])
m2.3  <- lm(gdp ~ punish, data = GMTVgroups[longgame == 0 & treat < 3 & per == 10 & highgdp == 1])

m2.4  <- lm(gdp ~ punish, data = GMTVgroups[longgame == 1 & treat > 100 & per == 15])
m2.5  <- lm(gdp ~ punish, data = GMTVgroups[longgame == 1 & treat > 100 & per == 15 & highgdp == 0])
m2.6  <- lm(gdp ~ punish, data = GMTVgroups[longgame == 1 & treat > 100 & per == 15 & highgdp == 1])

tab_model(m2.1, m2.2, m2.3, m2.4, m2.5, m2.6,
          dv.labels = c("10All", "10Below", "10Above", "15All", "15Below", "15Above"),
          p.style = "stars",
          show.ci = FALSE,
          show.p = FALSE, 
          transform = NULL)
```

Table 3: OLS Regression Gini ✅

```{r olsGini}

m3.1  <- lm(gini ~ punish, data = GMTVgroups[longgame == 0 & treat < 3 & per == 10])
m3.2  <- lm(gini ~ punish, data = GMTVgroups[longgame == 0 & treat < 3 & per == 10 & highgdp == 0])
m3.3  <- lm(gini ~ punish, data = GMTVgroups[longgame == 0 & treat < 3 & per == 10 & highgdp == 1])

m3.4  <- lm(gini ~ punish, data = GMTVgroups[longgame == 1 & treat > 100 & per == 15])
m3.5  <- lm(gini ~ punish, data = GMTVgroups[longgame == 1 & treat > 100 & per == 15 & highgdp == 0])
m3.6  <- lm(gini ~ punish, data = GMTVgroups[longgame == 1 & treat > 100 & per == 15 & highgdp == 1])

tab_model(m3.1, m3.2, m3.3, m3.4, m3.5, m3.6,
          dv.labels = c("10All", "10Below", "10Above", "15All", "15Below", "15Above"),
          p.style = "stars",
          show.ci = FALSE,
          show.p = FALSE, 
          transform = NULL)
```

Table 3: OLS Regression re-calculated Gini

```{r olsGini2}

m4.1  <- lm(gini2 ~ punish, data = GMTVgroups[longgame == 0 & treat < 3 & per == 10])
m4.2  <- lm(gini2 ~ punish, data = GMTVgroups[longgame == 0 & treat < 3 & per == 10 & highgdp == 0])
m4.3  <- lm(gini2 ~ punish, data = GMTVgroups[longgame == 0 & treat < 3 & per == 10 & highgdp == 1])

m4.4  <- lm(gini2 ~ punish, data = GMTVgroups[longgame == 1 & treat > 100 & per == 15])
m4.5  <- lm(gini2 ~ punish, data = GMTVgroups[longgame == 1 & treat > 100 & per == 15 & highgdp == 0])
m4.6  <- lm(gini2 ~ punish, data = GMTVgroups[longgame == 1 & treat > 100 & per == 15 & highgdp == 1])

tab_model(m4.1, m4.2, m4.3, m4.4, m4.5, m4.6,
          dv.labels = c("10All", "10Below", "10Above", "15All", "15Below", "15Above"),
          p.style = "stars",
          show.ci = FALSE,
          show.p = FALSE, 
          transform = NULL)
```

### 2021-06-29 analysis/reports/rmd/01_dataGMTV.Rmd
Restructure the Project's Analysis

--- 2021-06-24 reports/01_dataGMTV.Rmd
@@
 date: "`r Sys.Date()`"
-bibliography: biblio.bib
+bibliography: ../biblio.bib
 output:
@@
 ```{r readData}
-DT <- read_dta(file="../data/gaechteretal/GMTV-data.dta") %>% data.table()
-CT <- read_dta(file="../data/gaechteretal/GMTV-questionnaire-data.dta") %>% data.table()
+DT <- read_dta(file="../../../data/gaechteretal/GMTV-data.dta") %>% data.table()
+CT <- read_dta(file="../../../data/gaechteretal/GMTV-questionnaire-data.dta") %>% data.table()
 ```
@@
 Within the appendix, one also learns that the NOPUNISH 10-period data were collected in sessions 5, 8 and 9.
-Subsetting the data correspondingly yields a ```data.table``` consisting of 23 observations and $4 \times 10 \times 23=$ `r NROW(noPunish10)` rows and 27 variables.
+Subsetting the data correspondingly yields a `data.table` consisting of 23 observations and $4 \times 10 \times 23=$ `r NROW(noPunish10)` rows and 27 variables.
 
@@
 
-- ```exp_num``` is a session identifier
-- ```per``` denotes the period
-- ```gr_id``` is a group identifier (carrying treatment information)
-- ```subj_id``` is a subject identifier
-- ```tokens``` reports a subject's endowment in a period
-- ```other[1-3]``` report the other group members' endowments in a period
-- ```gdp ``` equals the sum of endowments of a group in a period
-- ```putin``` reports a subject's contribution in a period
-- ```pu[1-3]``` report the other group members' contributions in a period
-- ```sum``` equals the sum of contributions of a group in a period.
-- ```gini``` reports a group's Gini coefficient in a period.
-- ```mean``` reports the fraction of sum/lagged(gdp).
+-   `exp_num` is a session identifier
+-   `per` denotes the period
+-   `gr_id` is a group identifier (carrying treatment information)
+-   `subj_id` is a subject identifier
+-   `tokens` reports a subject's endowment in a period
+-   `other[1-3]` report the other group members' endowments in a period
+-   `gdp` equals the sum of endowments of a group in a period
+-   `putin` reports a subject's contribution in a period
+-   `pu[1-3]` report the other group members' contributions in a period
+-   `sum` equals the sum of contributions of a group in a period.
+-   `gini` reports a group's Gini coefficient in a period.
+-   `mean` reports the fraction of sum/lagged(gdp).
 
-Additionally, I compute two new measures, ```gini2``` as well as ```share```.
-The new ```gini2``` differs from the original as it is constant within groups.
-```share``` is equivalent to the original mean but relies on the current gdp instead of the past one as a denominator.
+Additionally, I compute two new measures, `gini2` as well as `share`.
+The new `gini2` differs from the original as it is constant within groups.
+`share` is equivalent to the original mean but relies on the current gdp instead of the past one as a denominator.
 
@@
 
+if(knitr::is_html_output()){
   # show table
@@
                 fixed_thead = TRUE)
+  }
 
@@
 We see group 501 in the first two periods where subjects 511 to 514 start with an initial endowment of 20 which makes a GDP of 80.
-Subject 511 does not contribute (as represented in ```putin==0``` in the first row and ```pu1==0```in rows 2 to 4) while the others contribute 5, 15 and 15 in the first period, respectively.
-The ```sum``` of contributions therefore equals 35 period 1.
+Subject 511 does not contribute (as represented in `putin==0` in the first row and `pu1==0`in rows 2 to 4) while the others contribute 5, 15 and 15 in the first period, respectively.
+The `sum` of contributions therefore equals 35 period 1.
 
-With a sum of contributions being 35 and a return of contributions of 1.5, each subject receives ```ceil(13.125)``` =14 points from the group project such that the next period's ```gdp``` equals 101.
+With a sum of contributions being 35 and a return of contributions of 1.5, each subject receives `ceil(13.125)` =14 points from the group project such that the next period's `gdp` equals 101.
 
-The Gini coefficient (```gini```) is a little off as one can see in the second period: Even though this is a group level variable, the group has three different coefficient in the same period.
-With the same absolute amount of contributions as in the first period,the second period ```mean``` (based on the past ```gdp```) is larger than ```share``` in the second period, because the ```gdp``` grew.
+The Gini coefficient (`gini`) is a little off as one can see in the second period: Even though this is a group level variable, the group has three different coefficient in the same period.
+With the same absolute amount of contributions as in the first period,the second period `mean` (based on the past `gdp`) is larger than `share` in the second period, because the `gdp` grew.
 
@@
 To resemble the oTree data, the original data has to be transformed a little.
-Therefore, some variables will be renamed, variables (such as ```stock```^[The income at the end of a period.] and ```gain```^[The tokens earned in a period.]) will be created and, most notably, the unit of observations will be groups such that subject-level variables will be dropped.
+Therefore, some variables will be renamed, variables (such as `stock`^[The income at the end of a period.] and `gain`^[The tokens earned in a period.]) will be created and, most notably, the unit of observations will be groups such that subject-level variables will be dropped.
 
@@
 
+if(knitr::is_html_output()){
   # display data
@@
 ```{r writeData}
-save(GMTV, file = "../data/processed/rda/GMTV2017.rda")
-write.csv(GMTV, file ="../data/processed/csv/GMTV2017.csv")
+save(GMTV, file = "../../../data/processed/rda/GMTV2017.rda")
+write.csv(GMTV, file ="../../../data/processed/csv/GMTV2017.csv")
 
@@
 ```{r downloadData}
+if(knitr::is_html_output()){
   GMTV %>%
@@
         )
+  }
 ```
@@
 
-# Tables
-
-```{r regressions}
+```{r regressions, eval = FALSE}
 # reg gdp punish if longgame==0  & treat<3 & per==10, cluster(gr_id)
@@
 This becomes obvious if one looks at the figures that visualize the contributions.
-The arising question therefore is whether I made a mistake in processing and interpreting the data.
-After all I thought to have found wrong Gini coefficients and struggle to interpret the ```mean``` of the original data.
 
@@
 save(GMTVFirstRound, 
-     file = paste0("../data/processed/rda/", fileName, "_R1", ".rda"))
+     file = paste0("../../../data/processed/rda/", fileName, "_R1", ".rda"))
 write.csv(GMTVFirstRound, 
-          file = paste0("../data/processed/csv/", fileName, "_R1", ".csv"))
+          file = paste0("../../../data/processed/csv/", fileName, "_R1", ".csv"))
 ```
 
-`r NROW(GMTVFirstRound)` participants yield `r NROW(GMTVFirstRound)` independent observations that are stored in a data table called ```GMTVFirstRound```.
-These observations are displayed below and can, once more, be downloaded by a click on the button.
-As before, the data is also saved in ```../data/processed/```.
+`r NROW(GMTVFirstRound)` participants yield `r NROW(GMTVFirstRound)` independent observations that are stored in a data table called `GMTVFirstRound`.
+These observations are displayed below and can, once more, be downloaded by a click on the button (HTML-only feature).
+As before, the data is also saved in `../../../data/processed/`.
 
 ```{r displayFirstRound}
+
+if(knitr::is_html_output()){
   # display data
@@
 save(GMTVCovariates, 
-     file = paste0("../data/processed/rda/", fileName, "_COVS", ".rda"))
+     file = paste0("../../../data/processed/rda/", fileName, "_COVS", ".rda"))
 write.csv(GMTVCovariates, 
-          file = paste0("../data/processed/csv/", fileName, "_COVS", ".csv"))
+          file = paste0("../../../data/processed/csv/", fileName, "_COVS", ".csv"))
 

### 2021-06-29 analysis/reports/rmd/02_dataProcessing.Rmd
Restructure the Project's Analysis

--- 2021-06-24 reports/02_dataProcessing.Rmd
@@
 
-# Simulations
+# Replication Data
 
 ```{r readData}
-# read simulated data
-DT <- read.csv("../data/simulation/all_apps_wide.csv", stringsAsFactors = FALSE) %>%
+# read replication data
+DT <- read.csv(paste("../..", recentCSV, sep = "/"), 
+               stringsAsFactors = FALSE) %>%
   data.table()
 ```
-
-I simulated `r NROW(DT)` participants.
-To do so, I wrote oTree bots that follow rather simple rules and act mostly random.
-As a consequence, this data yields no information apart from the structure of the data itself.
-
-Eventually, this report can also be used to process real data.
-This only requires us to read a different data set.^[It may also require us to merge multiple data sets -- that depends on whether the lab delivers one or several data sets and remains to be discussed.]
 
@@
 fileName <- "replication2021"
-save(replicationFirstRound, file = paste0("../data/processed/rda/", fileName, "_R1", ".rda"))
-write.csv(replicationFirstRound, file = paste0("../data/processed/csv/", fileName, "_R1", ".csv"))
+save(replicationFirstRound, file = paste0("../../../data/processed/rda/", fileName, "_R1", ".rda"))
+write.csv(replicationFirstRound, file = paste0("../../../data/processed/csv/", fileName, "_R1", ".csv"))
 
+if(knitr::is_html_output()){
   # display data
@@
         )
+  }
 ```
 
-The data is saved in two formats (```csv``` and ```rda```) in ```../data/processed/```.
-If you have not downloaded the repository and access the html file, you can also obtain a csv-file by clicking on the button above.
+The data is saved in two formats (```csv``` and ```rda```) in ```../../../data/processed/```.
+If you have not downloaded the repository and access the html file, you can also obtain a csv-file by clicking on the button above (HTML-only feature).
 
@@
                 fixed_thead = TRUE)
+  }
 ```
@@
 
-The result contains ```NROW(DT)/4``` observations in 10 rounds and is saved as a ```csv``` and as a ```rda``` file in ```../data/processed/```.
+The result contains ```NROW(DT)/4``` observations in 10 rounds and is saved as a ```csv``` and as a ```rda``` file in ```../../../data/processed/```.
 
 ```{r saveData}
-save(replication, file = paste0("../data/processed/rda/", fileName, ".rda"))
-write.csv(replication, file = paste0("../data/processed/csv/", fileName, ".csv"))
+save(replication, file = paste0("../../../data/processed/rda/", fileName, ".rda"))
+write.csv(replication, file = paste0("../../../data/processed/csv/", fileName, ".csv"))
 ```
@@
 ```{r displayData}
+
+if(knitr::is_html_output()){
   replication %>%
@@
 ```{r downloadData}
+if(knitr::is_html_output()){
   replication %>%
@@
 save(replicationCovariates, 
-     file = paste0("../data/processed/rda/", fileName, "_COVS", ".rda"))
+     file = paste0("../../../data/processed/rda/", fileName, "_COVS", ".rda"))
 write.csv(replicationCovariates, 
-          file = paste0("../data/processed/csv/", fileName, "_COVS", ".csv"))
+          file = paste0("../../../data/processed/csv/", fileName, "_COVS", ".csv"))
 

### 2021-06-29 analysis/reports/rmd/03_dataAnalyses.Rmd
Restructure the Project's Analysis

--- 2021-06-23 reports/03_dataAnalyses.Rmd
@@
 ```{r readData}
-load(file="../data/processed/rda/GMTV2017.rda")          # read GMTV
-load(file="../data/processed/rda/GMTV2017_R1.rda")       # read GMTVFirstRound
-load(file="../data/processed/rda/GMTV2017_COVS.rda")     # read GMTVCovariates
-load(file="../data/processed/rda/replication2021.rda")       # read replication
-load(file="../data/processed/rda/replication2021_R1.rda")    # read replicationFirstRound
-load(file="../data/processed/rda/replication2021_COVS.rda")  # read replicationCovariates
+base::load(file="../../../data/processed/rda/GMTV2017.rda")              # read GMTV
+base::load(file="../../../data/processed/rda/GMTV2017_R1.rda")           # read GMTVFirstRound
+base::load(file="../../../data/processed/rda/GMTV2017_COVS.rda")         # read GMTVCovariates
+base::load(file="../../../data/processed/rda/replication2021.rda")       # read replication
+base::load(file="../../../data/processed/rda/replication2021_R1.rda")    # read replicationFirstRound
+base::load(file="../../../data/processed/rda/replication2021_COVS.rda")  # read replicationCovariates
 ```
@@
 
-rs1 <- wilcox.test(replication, GMTV)$p.value %>% round(digits = 4) %>% formatC(format = "f", digits = 4)
+rs1 <- wilcox.test(replication, 
+                   GMTV,
+                   exact = FALSE)$p.value %>% 
+  round(digits = 4) %>% 
+  formatC(format = "f", 
+          digits = 4)
 
@@
 
-rs2 <- wilcox.test(replication, GMTV)$p.value %>% round(digits = 4) %>% formatC(format = "f", digits = 4)
+rs2 <- wilcox.test(replication, 
+                   GMTV,
+                   exact = FALSE)$p.value %>% 
+  round(digits = 4) %>% 
+  formatC(format = "f", 
+          digits = 4)
 

### 2021-06-29 analysis/R/config.R

@@ -37,3 +37,11 @@ for(package in listOfPackages){
 }
 
 # renv::snapshot()
+
+# read most recent data
+cFiles <- file.info(list.files(path = "../data/replication",
+                               recursive = TRUE,
+                               full.names = TRUE,
+                               pattern = "all_apps_wide.csv$"),
+                    extra_cols = FALSE)
+recentCSV <- cFiles[cFiles$mtime == max(cFiles$mtime), ] %>% row.names()

### 2021-06-29 analysis/R/data.R

@@ -1,149 +1,0 @@
-# # read raw data
-# Lo000 <- read.csv("../data/simulation/Lo000.csv", stringsAsFactors = FALSE) %>% data.table()
-# Hi000 <- read.csv("../data/simulation/Hi000.csv", stringsAsFactors = FALSE) %>% data.table()
-# Lo033 <- read.csv("../data/simulation/Lo033.csv", stringsAsFactors = FALSE) %>% data.table()
-# Hi033 <- read.csv("../data/simulation/Hi033.csv", stringsAsFactors = FALSE) %>% data.table()
-# 
-# 
-# # pretend we had a treatment
-# Lo000[, session.code := "Lo000"]
-# Hi000[, session.code := "Hi000"]
-# Lo033[, session.code := "Lo033"]
-# Hi033[, session.code := "Hi033"]
-# 
-# dt <- rbindlist(list(Lo000, Hi000, Lo033, Hi033),
-#                 use.names = FALSE)
-
-# or use the data gathered in a demo session
-dt <- read.csv("../data/demoSessions/all_apps_wide-2021-03-25.csv", stringsAsFactors = FALSE) %>% data.table()
-dt <- dt[, session.code := "demoSession"]
-
-# control variables
-cRegex <- "participant\\.code$|participant\\..time_started|session\\.code$|_index_in_pages|Intro\\.1\\.player\\.window.*|Intro\\.1\\.player\\.browser|participant\\.payoff$|^Outro"
-controlVariables <- str_subset(string = names(dt),
-                               pattern = cRegex)
-ct <- dt[, ..controlVariables]
-
-
-# main data frame
-mRegex <- "participant\\.code$|participant\\.time_started|session\\.code$|dPGG\\.1\\.group\\.id_in_subsession|\\.1\\.player.belief|endowment|contribution|stock|gain$|bot_active|EWE|disaster|Comprehension"
-mainVariables <- str_subset(string = names(dt),
-                            pattern = mRegex)
-mt <- dt[, ..mainVariables]
-
-# select first round belief data -----
-firstRound <- mt[,
-                 .(belief = dPGG.1.player.belief,
-                   othersContribution = dPGG.1.group.total_contribution - dPGG.1.player.contribution,
-                   ownContribution = dPGG.1.player.contribution,
-                   conformity = dPGG.1.player.contribution - dPGG.1.player.belief/3)]
-
-# add share as contribution/endowment
-for(round in 1:15){
-  cont <- glue("dPGG.{round}.player.contribution")
[…]

### 2021-06-29 analysis/R/gaechteretal.R

@@ -1,1 +1,0 @@
-rmarkdown::render("../reports/replication.Rmd")

### 2021-06-29 analysis/R/renderHTML.R

@@ -1,0 +1,17 @@
+# Render HTML Report -----
+rmarkdown::render(input = "reports/rmd/01_dataGMTV.Rmd",
+                  output_format = "distill_article",
+                  output_dir = "reports/html/",
+                  output_file = "01_GMTV")
+
+rmarkdown::render(input = "reports/rmd/02_dataProcessing.Rmd",
+                  output_format = "distill_article",
+                  output_dir = "reports/html/",
+                  output_file = "02_Replication")
+
+rmarkdown::render(input = "reports/rmd/03_dataAnalyses.Rmd",
+                  output_format = "distill_article",
+                  output_dir = "reports/html/",
+                  output_file = "03_Analyses")
+
+print("PDFs rendered. You can find them in analysis/reports/html/. The processed data is stored in data/processed/.")

### 2021-06-29 analysis/R/renderPDF.R

@@ -1,0 +1,17 @@
+# Render PDF Report -----
+rmarkdown::render(input = "reports/rmd/01_dataGMTV.Rmd",
+                  output_format = "pdf_document",
+                  output_dir = "reports/pdf/",
+                  output_file = "01_GMTV")
+
+rmarkdown::render(input = "reports/rmd/02_dataProcessing.Rmd",
+                  output_format = "pdf_document",
+                  output_dir = "reports/pdf/",
+                  output_file = "02_Replication")
+
+rmarkdown::render(input = "reports/rmd/03_dataAnalyses.Rmd",
+                  output_format = "pdf_document",
+                  output_dir = "reports/pdf/",
+                  output_file = "03_Analyses")
+
+print("PDFs rendered. You can find them in analysis/reports/pdf/. The processed data is stored in data/processed/.")

### 2021-06-29 analysis/R/source.R

@@ -1,35 +1,5 @@
 rm(list = ls())
 
 source("R/config.R")
-
-# Render HTML Report -----
-rmarkdown::render(input = "../reports/01_dataGMTV.Rmd",
-                  output_format = "distill_article",
-                  output_dir = "../reports/html/",
-                  output_file = "01_GMTV")
-
-rmarkdown::render(input = "../reports/02_dataProcessing.Rmd",
-                  output_format = "distill_article",
-                  output_dir = "../reports/html/",
-                  output_file = "02_Replication")
-
-rmarkdown::render(input = "../reports/03_dataAnalyses.Rmd",
-                  output_format = "distill_article",
-                  output_dir = "../reports/html/",
-                  output_file = "03_Analyses")
-
-# Render PDF Report -----
-# rmarkdown::render(input = "../reports/01_dataGMTV.Rmd",
-#                   output_format = "pdf_document",
-#                   output_dir = "../reports/pdf/",
-#                   output_file = "01_GMTV")
-# 
-# rmarkdown::render(input = "../reports/02_dataProcessing.Rmd",
-#                   output_format = "pdf_document",
-#                   output_dir = "../reports/pdf/",
-#                   output_file = "02_Replication")
-
-rmarkdown::render(input = "../reports/03_dataAnalyses.Rmd",
-                  output_format = "pdf_document",
-                  output_dir = "../reports/pdf/",
-                  output_file = "03_Analyses")
+source("R/renderHTML.R")
+source("R/renderPDF.R")

### 2021-06-29 analysis/R/viz.R

@@ -1,73 +1,0 @@
-# Load Data -----
-base::load(file = "../data/processed/simulations.rda") 
-base::load(file = "../data/processed/gaechter2017.rda") 
-
-# run Markdown files -----
-rmarkdown::render("../reports/simulations.Rmd")
-
-# Themes -----
-layout <- theme(panel.background = element_rect(fill = "white"),
-                panel.grid = element_line(colour="gray", size=0),
-                panel.grid.major.y = element_line(colour="gray", size=0.25),
-                legend.key = element_rect(fill = "white"),
-                axis.line.x.bottom = element_line(size = 0.25),
-                axis.line.y.left = element_line(size = 0.25),
-                plot.margin = unit(c(1,1,1,1), "cm"),
-                legend.title = element_blank()
-                )
-
-# Static Graphs -----
-# chose variable to plot
-outcome <- "endowment"
-for(outcome in outcomes){
-  # line graph with 95%-CI -----
-  plotDT <- summarySE(data = na.omit(longDT, cols = outcome), 
-                      measurevar = outcome, 
-                      groupvars=c("treatment", "round"),
-                      na.rm = FALSE,
-                      conf.interval = 0.95,
-                      .drop = TRUE)
-  
-  temp <- plotDT[, outcome]
-  
-  # plot
-  plot <- ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + # linetype = treatment
-    layout +
-    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
-    geom_line() +
-    # geom_point() + 
-    scale_x_continuous(name="Period",  breaks = 1:10, limits = c(1, 10.5)) +
-    scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
-    labs(y = outcome %>% str_to_title())
-
-  plotTitle <- glue("plot{str_to_title(outcome)}")
-  # assign(x = plotTitle,
-  #        value = plot)
-  ggsave(plot, file = glue("../figures/ggplot2/{plotTitle}.png"), 
-         width = 14, 
-         height = 10, 
-         units = "cm",
-         bg = "transparent")
-  
-  rm(list = c("plotTitle", "plot", "temp", "plotDT", "outcome"))
-}
-
-# HighcharteR -----
-# see https://stackoverflow.com/questions/39752747/error-bars-with-highcharter
[…]

### 2021-06-30 oTree/HLPL/pages.py
update oTree Code: implement donation URL, etc.

@@ -7,7 +7,6 @@ class HLPL_Decision(Page):
     form_model = "player"
 
     def get_form_fields(self):
-
         # unzip list of form_fields from <mpl_choices> list
         form_fields = [list(t) for t in zip(*self.participant.vars['mpl_choices'])][1]
         form_fields.extend(["review_instructions", "review_contact"])
@@ -22,6 +21,10 @@ class HLPL_Decision(Page):
         return dict(
             template="risk",
         )
+
+    def get_timeout_seconds(self):
+        if self.participant.vars.get("is_dropout"):
+            return 1  # instant timeout, 1 second
 
     def before_next_page(self):
         form_fields = [list(t) for t in zip(*self.participant.vars['mpl_choices'])][1]

### 2021-06-30 oTree/Intro/models.py

@@ -55,31 +55,41 @@ class Player(BasePlayer):
 
 
 
-    CQ1_1 = models.IntegerField(doc="Comprehension Question 1.1", initial=int(Constants.initial_endowment), blank = True)
+    CQ1_1 = models.IntegerField(doc="Comprehension Question 1.1",
+                                # initial=int(Constants.initial_endowment),
+                                blank = True)
     def CQ1_1_error_message(self, value):
         if value != int(Constants.initial_endowment):
             self.wrong_answer1_1 += 1
             return "Leider falsch."
 
-    CQ1_2 = models.IntegerField(doc="Comprehension Question 1.2", initial=int(Constants.initial_endowment), blank = True)
+    CQ1_2 = models.IntegerField(doc="Comprehension Question 1.2",
+                                # initial=int(Constants.initial_endowment),
+                                blank = True)
     def CQ1_2_error_message(self, value):
         if value != int(Constants.initial_endowment):
             self.wrong_answer1_2 += 1
             return "Leider falsch."
 
-    CQ2_1 = models.IntegerField(doc="Comprehension Question 2.1", initial=int(Constants.initial_endowment * Constants.efficiency_factor), blank = True)
+    CQ2_1 = models.IntegerField(doc="Comprehension Question 2.1",
+                                # initial=int(Constants.initial_endowment * Constants.efficiency_factor),
+                                blank = True)
     def CQ2_1_error_message(self, value):
         if value != int(Constants.initial_endowment * Constants.efficiency_factor):
             self.wrong_answer2_1 += 1
             return "Leider falsch."
 
-    CQ2_2 = models.IntegerField(doc="Comprehension Question 2.2", initial=int(Constants.initial_endowment * Constants.efficiency_factor), blank = True)
+    CQ2_2 = models.IntegerField(doc="Comprehension Question 2.2",
+                                # initial=int(Constants.initial_endowment * Constants.efficiency_factor),
+                                blank = True)
     def CQ2_2_error_message(self, value):
         if value != int(Constants.initial_endowment * Constants.efficiency_factor):
             self.wrong_answer2_2 += 1
             return "Leider falsch."
 
[…]

### 2021-06-30 analysis/reports/rmd/03_dataAnalyses.Rmd
prepare pre-registration

@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+```{r setup, include=TRUE}
+knitr::opts_chunk$set(echo = TRUE)
 
@@
 
-This report is the third in a series of reports covering this project. It reads the data prepared in the previous reports and analyzes them.
+[This report](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd/03_dataAnalyses.Rmd) is the third in a series of reports covering this project.
+It reads the data prepared in the previous reports and analyzes them.
 
@@
 
+In addition to the summary statistics a regression table for each covariate as a dependent variable is needed. The independent variable will then be the data source (i.e. GMTV vs replication).
+
 ```{r summary3, results = "asis"}

### 2021-06-30 analysis/R/renderHTML.R

@@ -1,16 +1,13 @@
 # Render HTML Report -----
 rmarkdown::render(input = "reports/rmd/01_dataGMTV.Rmd",
-                  output_format = "distill_article",
                   output_dir = "reports/html/",
                   output_file = "01_GMTV")
 
 rmarkdown::render(input = "reports/rmd/02_dataProcessing.Rmd",
-                  output_format = "distill_article",
                   output_dir = "reports/html/",
                   output_file = "02_Replication")
 
 rmarkdown::render(input = "reports/rmd/03_dataAnalyses.Rmd",
-                  output_format = "distill_article",
                   output_dir = "reports/html/",
                   output_file = "03_Analyses")
 

### 2021-06-30 analysis/reports/rmd/01_dataGMTV.Rmd

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = TRUE)
 
@@
 The current demo version of the experiment can be found [here](https://cliccs.herokuapp.com/).
-Click [here](https://github.com/Howquez/coopUncertainty) to visit the corresponding Github repository.
+Click [here](https://github.com/Howquez/coopUncertainty/tree/July21Replication) to visit the corresponding Github repository.
 
-This report is the first in a series of reports covering this project. It prepares the original data and replicates main visualizations & tables.
+[This report](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd/01_dataGMTV.Rmd) is the first in a series of reports covering this project.
+It prepares the original data and replicates main visualizations & tables.
 
@@
 
-Within the appendix, one also learns that the NOPUNISH 10-period data were collected in sessions 5, 8 and 9.
+Within the appendix, one  learns that the NOPUNISH 10-period data were collected in sessions 5, 8 and 9.
 Subsetting the data correspondingly yields a `data.table` consisting of 23 observations and $4 \times 10 \times 23=$ `r NROW(noPunish10)` rows and 27 variables.

### 2021-06-30 analysis/reports/rmd/01_dataGMTV.Rmd
minor modifications: more regression tables, a typo, recalibration of GMTVs switching point

--- 2021-06-29 analysis/reports/rmd/01_dataGMTV.Rmd
@@
                                 yes  = NA,
-                                no   = e10 + e20 + e30 + e40 + e50 + e60 + e70 + 1)
+                                no   = e10 + e20 + e30 + e40 + e50 + e60 + e70 + 1 + 2) # because GMTV used a 7-point-likert scale
          ]

### 2021-06-30 analysis/reports/rmd/03_dataAnalyses.Rmd
minor modifications: more regression tables, a typo, recalibration of GMTVs switching point

--- 2021-06-29 analysis/reports/rmd/03_dataAnalyses.Rmd
@@
 ---
-title: "3. Analyses Plan"
+title: "3. Analysis Plan"
 description: |
@@
 
+```{r sampleDifferences1, results = "asis", warning = FALSE}
+
+# create table
+if(knitr::is_html_output()){
+  type <- "html"
+} else {
+  type = "latex"
+}
+
+stargazer(lm(formula = gender ~ treatment, data = covs),
+          lm(formula = age ~ treatment, data = covs),
+          lm(formula = switching_row ~ treatment, data = covs),
+          lm(formula = donation ~ treatment, data = covs),
+
+          column.labels = c("female", "age", "risk", "donations"),
+          model.numbers = FALSE,
+          dep.var.labels.include = FALSE,
+          header=FALSE,
+          covariate.labels = c("Replication"),
+
+          type = type, digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
+          )
+```
+
+```{r sampleDifferences2, results = "asis", warning = FALSE}
+
+# create table
+if(knitr::is_html_output()){
+  type <- "html"
+} else {
+  type = "latex"
+}
+
+stargazer(lm(formula = pq01 ~ treatment, data = covs),
+          lm(formula = pq02 ~ treatment, data = covs),
+          lm(formula = pq03 ~ treatment, data = covs),
+          lm(formula = pq04 ~ treatment, data = covs),
+          lm(formula = pq05 ~ treatment, data = covs),
+
+          column.labels = c("quick thinker", "easily offended", "very satisfied", "very dependent", "generally happy"),
+          model.numbers = FALSE,
+          dep.var.labels.include = FALSE,
+          header=FALSE,
+          covariate.labels = c("Replication"),
+
+          type = type, digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
+          )
+```
+
+```{r sampleDifferences3, results = "asis", warning = FALSE}
+
+# create table
+if(knitr::is_html_output()){
+  type <- "html"
+} else {
+  type = "latex"
+}
+
+stargazer(lm(formula = pq06 ~ treatment, data = covs),
+          lm(formula = pq07 ~ treatment, data = covs),
+          lm(formula = pq08 ~ treatment, data = covs),
+          lm(formula = pq09 ~ treatment, data = covs),
+          lm(formula = pq10 ~ treatment, data = covs),
+
+          column.labels = c("work important", "family important", "friends important", "religion important", "politics important"),
+          model.numbers = FALSE,
+          dep.var.labels.include = FALSE,
+          header=FALSE,
+          covariate.labels = c("Replication"),
+
+          type = type, digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
+          )
+```
+
+```{r sampleDifferences4, results = "asis", warning = FALSE}
+
+# create table
+if(knitr::is_html_output()){
+  type <- "html"
+} else {
+  type = "latex"
+}
+
+stargazer(lm(formula = pq11 ~ treatment, data = covs),
+          lm(formula = pq12 ~ treatment, data = covs),
+          lm(formula = pq13 ~ treatment, data = covs),
+          lm(formula = pq14 ~ treatment, data = covs),
+
+          column.labels = c("most people trusted", "hard work better", "government responsible", "incomes equal"),
+          model.numbers = FALSE,
+          dep.var.labels.include = FALSE,
+          header=FALSE,
+          covariate.labels = c("Replication"),
+
+          type = type, digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
+          )
+```
+
 ```{r tableCovariates, results = "asis", warning = FALSE}
@@
           covariate.labels = c("female", "age", "risk",
-                               "I am a quick thinker",
-                               "I get easily offended",
+                               "quick thinker",
+                               "easily offended",
                                "very satisfied",

### 2021-06-30 analysis/reports/rmd/02_dataProcessing.Rmd

@@
 ```{r setup, include=TRUE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = TRUE)
+
 library(data.table)
@@
 
-This report is the second in a series of reports covering this project. It explains how simulated data is processed and prepared for analyses.
+[This report](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd/02_dataProcessing.Rmd) is the second in a series of reports covering this project.
+It explains how simulated data is processed and prepared for analyses.
 

### 2021-07-02 oTree/HLPL/pages.py
last minute changes

@@ -6,6 +6,10 @@ from .models import Constants
 class HLPL_Decision(Page):
     form_model = "player"
 
+    def is_displayed(self):
+        if not self.participant.vars["is_residual_player"]:
+            return True
+
     def get_form_fields(self):
         # unzip list of form_fields from <mpl_choices> list
         form_fields = [list(t) for t in zip(*self.participant.vars['mpl_choices'])][1]

### 2021-07-02 oTree/Outro/pages.py

@@ -32,6 +32,9 @@ class Outro_Final(Page):
         return dict(
             is_residual_player=self.participant.vars["is_residual_player"],
             final_payoff=self.participant.payoff_plus_participation_fee().to_real_world_currency(self.session),
+            payment_data_survey_link='https://www.limesurvey.uni-hamburg.de/index.php/162819?token=' + str(
+                self.participant.label)
+
         )
 
     def js_vars(self):

### 2021-07-02 oTree/dPGG/models.py

@@ -34,7 +34,7 @@ class Constants(BaseConstants):
     belief_elicitation_round = 1
     elicitation_bonus = 30 # points
     timeout = 4 # minutes
-    patience = 8 # minutes
+    patience = 10 # minutes
     patience_bonus = 20 # points
 
 

### 2021-07-02 oTree/settings.py

@@ -38,7 +38,23 @@ LANGUAGE_CODE = "de"
 REAL_WORLD_CURRENCY_CODE = "EUR"
 USE_POINTS = True
 
-ROOMS = []
+ROOMS = [
+    {
+        'name': '2021_07_01_17_00',
+        'display_name': '2021_07_01_17_00',
+        'participant_label_file': '_rooms/2021_07_01_17_00.txt',
+    },
+    {
+        'name': '2021_07_03_15_00',
+        'display_name': '2021_07_03_15_00',
+        'participant_label_file': '_rooms/2021_07_03_15_00.txt',
+    },
+    {
+        'name': '2021_07_09_15_00',
+        'display_name': '2021_07_09_15_00',
+        'participant_label_file': '_rooms/2021_07_09_15_00.txt',
+    }
+]
 
 ADMIN_USERNAME = 'admin'
 # for security, best to set admin password in an environment variable
@@ -46,7 +62,7 @@ ADMIN_PASSWORD = environ.get('OTREE_ADMIN_PASSWORD')
 
 DEMO_PAGE_INTRO_HTML = """ """
 
-SECRET_KEY = ''
+SECRET_KEY = environ.get('OTREE_SECRET_KEY')
 
 # if an app is included in SESSION_CONFIGS, you don't need to list it here
 INSTALLED_APPS = ['otree']

### 2021-07-02 analysis/reports/rmd/03_dataAnalyses.Rmd
read & process broken data without risk info

@@
           lm(formula = age ~ treatment, data = covs),
-          lm(formula = switching_row ~ treatment, data = covs),
+          # lm(formula = switching_row ~ treatment, data = covs),
           lm(formula = donation ~ treatment, data = covs),
@@
 
-olsStock1 <- lm(formula = stock ~ gender + age + switching_row + pq01 + pq02 + pq03 + pq04 + 
+olsStock1 <- lm(formula = stock ~ gender + age + 
+                  # switching_row + 
+                  pq01 + pq02 + pq03 + pq04 + 
                   pq05 + pq06 + pq07 +pq08 + pq09 + pq10 + pq11 + pq12 + pq13 + pq14, 
                 data = covariates[treatment == "replication"])
-olsStock2  <- lm(formula = stock ~ gender + age + switching_row,
+olsStock2  <- lm(formula = stock ~ gender + age, # + switching_row,
                 data = covariates[treatment == "replication"])
-olsGINI1  <- lm(formula = gini ~ gender + age + switching_row + pq01 + pq02 + pq03 + pq04 +
+olsGINI1  <- lm(formula = gini ~ gender + age + 
+                  # switching_row + 
+                  pq01 + pq02 + pq03 + pq04 +
                   pq05 + pq06 + pq07 + pq08 + pq09 + pq10 + pq11 + pq12 + pq13 + pq14, 
                 data = covariates[treatment == "replication"])
-olsGINI2  <- lm(formula = gini ~ gender + age + switching_row,
+olsGINI2  <- lm(formula = gini ~ gender + age, # + switching_row,
                 data = covariates[treatment == "replication"])

### 2021-07-02 analysis/R/config.R

@@ -45,3 +45,4 @@ cFiles <- file.info(list.files(path = "../data/replication",
                                pattern = "all_apps_wide.csv$"),
                     extra_cols = FALSE)
 recentCSV <- cFiles[cFiles$mtime == max(cFiles$mtime), ] %>% row.names()
+recentCSV <- "../data/replication/all_apps_wide-2021-07-02.csv"

### 2021-07-02 analysis/reports/rmd/02_dataProcessing.Rmd
udate reports

@@
   data.table()
+
+# subset complete cases
+DT <- DT[participant._index_in_pages == 77 & !is.na(dPGG.1.player.contribution)]
 ```

### 2021-07-02 analysis/reports/rmd/03_dataAnalyses.Rmd
udate reports

@@
 
-The rank sum test yields a p-Value of `r rs1` for the mean ```stock``` a.k.a _Wealth_ during the last period of the game.
+The table above displays summary statistics for the 10th period's ```stock``` a.k.a _Wealth_. The rank sum test yields a p-Value of `r rs1` for the mean wealth during the last period of the game.
+
+The following table shows a simple regression to illustrate differences in the 10th period's wealth between the replication's data and GMTV's data.
 
@@
 ```
+
+These information are also plotted over all periods in the following figure.
 
@@
 
+The following figure plots the Gini-coefficient These over all periods.
+
 ```{r plotInequality, fig.cap = "Average Gini coefficient over time across treatments."}
@@
 
+The following table shows a simple regression to illustrate differences in the 10th period's Gini coefficient between the replication's data and GMTV's data.
+
 ```{r tableGINI, results = "asis", warning = FALSE}
@@
 
+The table above displays summary statistics for the 10th period's ```gini``` .
 The rank sum test yields a p-Value of `r rs2` for the mean ```gini``` during the last period of the game.
@@
           header=FALSE,
-          covariate.labels = c("female", "age", "risk",
+          covariate.labels = c("female", "age", 
+                               # "risk",
                                "quick thinker",

### 2021-07-02 oTree/settings.py
typo and deployment settings

@@ -63,6 +63,7 @@ ADMIN_PASSWORD = environ.get('OTREE_ADMIN_PASSWORD')
 DEMO_PAGE_INTRO_HTML = """ """
 
 SECRET_KEY = environ.get('OTREE_SECRET_KEY')
+# SECRET_KEY = ""
 
 # if an app is included in SESSION_CONFIGS, you don't need to list it here
 INSTALLED_APPS = ['otree']

### 2021-07-30 analysis/reports/rmd/02_dataProcessing.Rmd
post data collection

@@
 
-```{r readData}
+```{r readAll}
+
+# DT <- read.csv("../../../data/simulation/all_apps_wide.csv",
+#                stringsAsFactors = FALSE) %>% data.table()
+
+files <- list.files(path = "../../../data/replication/",
+                       recursive = TRUE,
+                       full.names = TRUE)
+csvs <- list()
+
+for(i in files){
+  name <- str_extract(string = i,
+                      pattern = "2021.*")
+
+  temp <- read.csv(i, 
+                   stringsAsFactors = FALSE) %>%
+    data.table()
+
+  csvs[[name]] <- temp
+}
+
+full <- rbindlist(l = csvs,
+                  use.names = TRUE) %>%
+  data.table()
+
+DT <- full[participant._index_in_pages > 2 & 
+             participant.time_started != "" & 
+             participant.label != "" &
+             !(is.na(dPGG.1.player.contribution))]
+
+rm(list = c("files", "temp", "full"))
+```
+
+```{r readData, eval = FALSE}
 # read replication data
@@
 
+Unfortunately, I made a mistake calculating the ```share```. For this reason, it will be recalculated here:
+
+```{r recalcShare}
+replication[, share := contribution/endowment]
+```
+
 The result contains ```NROW(DT)/4``` observations in 10 rounds and is saved as a ```csv``` and as a ```rda``` file in ```../../../data/processed/```.
@@
 The next step is to reproduce Gaechter et al.'s figures and tables and to compare our results to their results. This will be done in the third report.
+
+```{r}
+replication[,
+            .(contribution = mean(contribution),
+              endowment = mean(endowment),
+              share = mean(contribution/endowment),
+              share2 = mean(share)),
+            by = c("round")]
+```

### 2021-07-30 analysis/reports/rmd/03_dataAnalyses.Rmd
post data collection

--- 2021-06-30 analysis/reports/rmd/03_dataAnalyses.Rmd
@@
 
-upperLimit <- GINI$gini %>% max() %>% round(digits = 1) + 0.10
+upperLimit <- GINI$gini %>% max() %>% round(digits = 1) + 0.15
 
@@
 ```
+
+The following table shows a simple regression to illustrate differences in the 10th period's Gini coefficient between the replication's data and GMTV's data.
 
@@
 
-olsStock1 <- lm(formula = stock ~ gender + age + switching_row + pq01 + pq02 + pq03 + pq04 + 
+olsStock1 <- lm(formula = stock ~ gender + age + 
+                  switching_row + 
+                  pq01 + pq02 + pq03 + pq04 + 
                   pq05 + pq06 + pq07 +pq08 + pq09 + pq10 + pq11 + pq12 + pq13 + pq14, 
@@
                 data = covariates[treatment == "replication"])
-olsGINI1  <- lm(formula = gini ~ gender + age + switching_row + pq01 + pq02 + pq03 + pq04 +
+olsGINI1  <- lm(formula = gini ~ gender + age + 
+                  switching_row + 
+                  pq01 + pq02 + pq03 + pq04 +
                   pq05 + pq06 + pq07 + pq08 + pq09 + pq10 + pq11 + pq12 + pq13 + pq14, 
@@
           header=FALSE,
-          covariate.labels = c("female", "age", "risk",
+          covariate.labels = c("female", "age", 
+                               "risk",
                                "quick thinker",

### 2021-07-30 analysis/R/config.R

@@ -45,4 +45,4 @@ cFiles <- file.info(list.files(path = "../data/replication",
                                pattern = "all_apps_wide.csv$"),
                     extra_cols = FALSE)
 recentCSV <- cFiles[cFiles$mtime == max(cFiles$mtime), ] %>% row.names()
-recentCSV <- "../data/replication/all_apps_wide-2021-07-02.csv"
+recentCSV <- "../data/replication/all_apps_wide-2021-07-03.csv"

### 2021-07-30 analysis/R/renderHTML.R

@@ -1,7 +1,7 @@
 # Render HTML Report -----
-rmarkdown::render(input = "reports/rmd/01_dataGMTV.Rmd",
-                  output_dir = "reports/html/",
-                  output_file = "01_GMTV")
+# rmarkdown::render(input = "reports/rmd/01_dataGMTV.Rmd",
+#                   output_dir = "reports/html/",
+#                   output_file = "01_GMTV")
 
 rmarkdown::render(input = "reports/rmd/02_dataProcessing.Rmd",
                   output_dir = "reports/html/",

### 2021-07-30 analysis/R/renderPDF.R

@@ -1,8 +1,8 @@
 # Render PDF Report -----
-rmarkdown::render(input = "reports/rmd/01_dataGMTV.Rmd",
-                  output_format = "pdf_document",
-                  output_dir = "reports/pdf/",
-                  output_file = "01_GMTV")
+# rmarkdown::render(input = "reports/rmd/01_dataGMTV.Rmd",
+#                   output_format = "pdf_document",
+#                   output_dir = "reports/pdf/",
+#                   output_file = "01_GMTV")
 
 rmarkdown::render(input = "reports/rmd/02_dataProcessing.Rmd",
                   output_format = "pdf_document",

### 2021-07-30 oTree/dPGG/tests.py

@@ -15,10 +15,11 @@ class PlayerBot(Bot):
                                                                         self.player.endowment)*Constants.num_others_per_group
                                                   )
             yield Submission(pages.dPGG_Decision, # in Gächter et al, subjects first contribute around 60%, then 30%
-                             dict(contribution=int((100 - 6 * self.round_number)/100 * random.randint(int(self.player.endowment/5*2.5), #HI==2.5,LO==2
-                                                                                                       int(self.player.endowment/5*5))  #HI==5,  LO==3.5
-                                                   )
-                                  ),
+                             dict(contribution=int(self.player.endowment/2)),
+                             # dict(contribution=int((100 - 6 * self.round_number)/100 * random.randint(int(self.player.endowment/5*2.5), #HI==2.5,LO==2
+                             #                                                                           int(self.player.endowment/5*5))  #HI==5,  LO==3.5
+                             #                       )
+                             #      ),
                              check_html=False)
             if self.round_number == self.session.config["num_rounds"]:
                 yield pages.dPGG_Results

### 2021-08-06 analysis/reports/rmd/02_dataProcessing.Rmd
generate session info meta data

@@
 library(magrittr)
+library(lubridate)
 library(stringr)
@@
 
-rm(list = c("files", "temp", "full"))
+rm(list = c("files", "temp"))
 ```
@@
 # read replication data
-DT <- read.csv(paste("../..", recentCSV, sep = "/"), 
-               stringsAsFactors = FALSE) %>%
-  data.table()
+# DT <- read.csv(paste("../..", recentCSV, sep = "/"), 
+#                stringsAsFactors = FALSE) %>%
+#   data.table()
 
 # subset complete cases
-DT <- DT[participant._index_in_pages == 77 & !is.na(dPGG.1.player.contribution)]
+# DT <- DT[participant._index_in_pages == 77 & !is.na(dPGG.1.player.contribution)]
+```
+
+## Meta data
+
+```{r meta}
+meta_long <- full[participant.time_started != "" & 
+                    participant.label != "",
+                  .(session.code,
+                    participant.time_started,
+                    dPGG.1.player.contribution)]
+
+meta_long[,
+          `:=`(date = participant.time_started %>% ymd_hms() %>% date(),
+               hour = participant.time_started %>% ymd_hms() %>% hour())]
+
+meta <- meta_long[,
+                  .(date = date %>% unique(),
+                    time = hour %>% unique() %>% paste("00", sep = ":"),
+                    showups = participant.time_started %>% length(),
+                    dropouts = dPGG.1.player.contribution %>% is.na() %>% sum(na.rm = FALSE)),
+                  by = session.code]
+
+meta[,
+     `:=`(participants = showups - dropouts,
+          observations = (showups - dropouts)/4)]
+
+# save data
+fileName <- "replication2021"
+save(meta, file = paste0("../../../data/processed/rda/", fileName, "_meta", ".rda"))
+write.csv(meta, file = paste0("../../../data/processed/csv/", fileName, "_meta", ".csv"))
+
+rm(list = c("full", "meta_long"))
 ```
@@
 # save data
-fileName <- "replication2021"
 save(replicationFirstRound, file = paste0("../../../data/processed/rda/", fileName, "_R1", ".rda"))
@@
 The next step is to reproduce Gaechter et al.'s figures and tables and to compare our results to their results. This will be done in the third report.
-
-```{r}
-replication[,
-            .(contribution = mean(contribution),
-              endowment = mean(endowment),
-              share = mean(contribution/endowment),
-              share2 = mean(share)),
-            by = c("round")]
-```

### 2021-08-06 analysis/reports/Spendennachweis/Spendennachweis.Rmd
create Spendennachweis

---
title: Spendennachweise des Gruppenentscheidungsexperiments an der Uni Hamburg
author:
  - name: Hauke Roggenkamp
    email: roggenkh@hsu-hh.de
    affiliation: Helmut-Schmidt-Universität
    footnote: 1
  - name: Stefan Traub
    affiliation: Helmut-Schmidt-Universität
  - name: Michael Berlemann
    affiliation: Helmut-Schmidt-Universität
address:
  - code: Helmut-Schmidt-Universität
    address: Holstenhofweg 85, 22043 Hamburg
footnote:
  - code: 1
    text: "Corresponding Author"
journal: " "
abstract: "Im Juli 2021 wurden insgesamt 4 Sessions desselben Experiments durchgeführt. Bei diesem Experiment konnten TeilnehmerInnen Geld verdienen und, wenn sie wollten, spenden. Dieses Doukment zählt die einzelnen Spendenbeträge zusammen und weißt die Tätigung des Gesamtbetrages nach."
date: "`r Sys.Date()`"
bibliography: mybibfile.bib
#linenumbers: true
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
---

# Spendenbetrag

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)

library(knitr)
library(data.table)
library(stringr)
library(magrittr)
library(kableExtra)
```

```{r readAll}

files <- list.files(path = "../../../data/replication/",
                       recursive = TRUE,
                       full.names = TRUE)
csvs <- list()

for(i in files){
  name <- str_extract(string = i,
                      pattern = "2021.*")

  temp <- read.csv(i, 
                   stringsAsFactors = FALSE) %>%
    data.table()

  csvs[[name]] <- temp
}

full <- rbindlist(l = csvs,
                  use.names = TRUE) %>%
  data.table()

DT <- full[participant._index_in_pages > 2 & 
             participant.time_started != "" & 
             participant.label != ""]

rm(list = c("files", "temp", "full"))
```

```{r subsetComplete}

complete <- DT[participant._index_in_pages == 77 & 
                 !(is.na(dPGG.1.player.contribution)),
               .(`Participant Label` = participant.label,
                 `Participant Code`  = participant.code, 
                 `Spende (Punkte)`   = dPGG.10.player.donation,
                 `Spende (Euro)`     = dPGG.10.player.donation / 20)
               ]
```

```{r subsetIncomplete}
incomplete <- DT[participant._index_in_pages > 2 & 
                 is.na(dPGG.1.player.contribution),
               .(`Participant Label` = participant.label,
                 `Participant Code`  = participant.code, 
                 `Spende (Punkte)`   = NA,
                 `Spende (Euro)`     = NA)
               ]
```

```{r rbind}
Donations <- rbind(complete, incomplete)
```

Insgesamt haben `r Donations %>% NROW()` TeilnehmerInnen eine der Sessions beendet. `r incomplete %>% NROW()` davon sind frühzeitig aus dem Experiment ausgeschieden, weil sich nicht in jedem Fall 4 TeilnehmerInnen zu einer Gruppe zusammengefunden haben.

```{r manualAdjustments}
# two participants notified us that they want to donate all their earnings, i.e. their showup fee as well. As this option was not provided by design, we'll hard-code it:

Donations[`Participant Label` == "sj3u1U3YRr",
          `:=`(`Spende (Punkte)` = 6*20,
               `Spende (Euro)`   = 6)]

Donations[`Participant Label` == "NZTEc5upQR",
          `:=`(`Spende (Punkte)` = `Spende (Punkte)` + 5*20,
               `Spende (Euro)`   = `Spende (Euro)` + 5)]

total <- Donations[,`Spende (Euro)` %>% sum(na.rm = TRUE)]
```

In der folgenden Tabelle werden alle TeilnehmerInnen aufgelistet, die einen Betrag gespendet haben. Insgesamt kam ein Betrag von _`r total`_ Euro zusammen.

```{r print, include = TRUE}
kable(Donations[`Spende (Punkte)` > 0], # order(participant.label,  decreasing = FALSE)], 
      longtable = T, booktabs = T) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 7) %>%
  footnote(general = paste("Insgesamt wurden dementsprechend", total, "Euro gespendet."),
           general_title = "Summe: "
           )
```

# Spendennachweis

Der Gesamtbetrag von _`r total`_ Euro wurde am `r Sys.Date()` unter der Buchungsreferenz `Gruppenentscheidungsexperiment Juli 2021` an [compensators.org](compensators.org) gespendet. Ein entsprechender Nachweis kann online unter [https://www.compensators.org/compensatelist/?searchterm=GmbH](https://www.compensators.org/compensatelist/?searchterm=GmbH) eingesehen werden.

### 2021-08-11 analysis/reports/Spendennachweis/Spendennachweis.Rmd
update reports

@@
 ---
-title: Spendennachweise des Gruppenentscheidungsexperiments an der Uni Hamburg
+title: Spendennachweise des Gruppenentscheidungsexperiments an der Universität Hamburg
 author:
@@
   - code: Helmut-Schmidt-Universität
-    address: Holstenhofweg 85, 22043 Hamburg
+    address: Helmut-Schmidt-Universität, Holstenhofweg 85, 22043 Hamburg
 footnote:
@@
 Bei diesem Experiment konnten TeilnehmerInnen Geld verdienen und, wenn sie wollten, spenden.
-Dieses Doukment zählt die einzelnen Spendenbeträge zusammen und weißt die Tätigung des Gesamtbetrages nach."
+Dieses Doukment zählt die einzelnen Spendenbeträge zusammen und weißt die Überweisung des Gesamtbetrages (119.05 Euro) nach.
+Aus der Summe der Spendenbeträge konnten 1,82 Tonnen CO2 stillgelegt werden."
 date: "`r Sys.Date()`"
@@
 
-In der folgenden Tabelle werden alle TeilnehmerInnen aufgelistet, die einen Betrag gespendet haben. Insgesamt kam ein Betrag von _`r total`_ Euro zusammen.
+In der folgenden Tabelle werden alle TeilnehmerInnen aufgelistet, die einen Betrag gespendet haben.
+Insgesamt kam ein Betrag von _`r total`_ Euro zusammen.
+Dies entspricht der Stillegung von 1,82 Tonnen CO2^[Stand: 06.08.2021, 16:54 Uhr.]
 
 ```{r print, include = TRUE}
-kable(Donations[`Spende (Punkte)` > 0], # order(participant.label,  decreasing = FALSE)], 
+donations <- Donations[`Spende (Punkte)` > 0]
+kable(donations[order(`Participant Label`,  decreasing = FALSE)], 
       longtable = T, booktabs = T) %>%
@@
 
-Der Gesamtbetrag von _`r total`_ Euro wurde am `r Sys.Date()` unter der Buchungsreferenz `Gruppenentscheidungsexperiment Juli 2021` an [compensators.org](compensators.org) gespendet.
-Ein entsprechender Nachweis kann online unter [https://www.compensators.org/compensatelist/?searchterm=GmbH](https://www.compensators.org/compensatelist/?searchterm=GmbH) eingesehen werden.
+Der Gesamtbetrag von _`r total`_ Euro wurde am 6.
+August 2021 unter der Buchungsreferenz `Gruppenentscheidungsexperiment Juli 2021` an [compensators.org](compensators.org) gespendet, damit 1,82 Tonnen CO2 stillgelegt werden.
+Ein entsprechender Nachweis kann online unter [https://www.compensators.org/compensatelist/?searchterm=stefan+traub](https://www.compensators.org/compensatelist/?searchterm=stefan+traub) eingesehen werden.

### 2021-08-11 analysis/reports/rmd/02_dataProcessing.Rmd
update reports

@@
 
-```{r readData, eval = FALSE}
-# read replication data
-# DT <- read.csv(paste("../..", recentCSV, sep = "/"), 
-#                stringsAsFactors = FALSE) %>%
-#   data.table()
-
-# subset complete cases
-# DT <- DT[participant._index_in_pages == 77 & !is.na(dPGG.1.player.contribution)]
-```
-
 ## Meta data
@@
                   .(session.code,
+                    participant.label,
                     participant.time_started,
@@
 ```
+
+```{r students}
+sample_info <- read.table(file = "../../../data/sample/invited_students.txt",
+                          col.names = c("participant.label")) %>%
+  data.table()
+```
+
+We conducted a series a `r meta %>% NROW()` sessions in between `r meta[, date %>% min() %>% format("%A, %B %d")]` to `r meta[, date %>% max() %>% format("%A, %B %d")]` and collected `r meta[, observations %>% sum()]` observations (from `r meta[, participants %>% sum()]` participants) in total.
+This replication is registered in the AEA RCT Registry and the unique identifying number is: [AEARCTR-0007902](https://doi.org/10.1257/rct.7902-2.0) [@preregistration].
+
+```{r printMeta}
+meta %>% kable()
+```
+
+Unfortunately, w needed to recruit students for the last session as the sample of non-students was exhausted.
+As a consequence, we `r (sample_info$participant.label %in% DT$participant.label) %>% sum()` students participated in the last session.
 
@@
 
+# Page Times
+
+```{r readTime}
+
+files <- list.files(path = "../../../data/pageTimes/",
+                       recursive = TRUE,
+                       full.names = TRUE)
+csvs <- list()
+
+for(i in files){
+  name <- str_extract(string = i,
+                      pattern = "2021.*")
+
+  temp <- read.csv(i, 
+                   stringsAsFactors = FALSE) %>%
+    data.table()
+
+  csvs[[name]] <- temp
+}
+
+timeSpent <- rbindlist(l = csvs,
+                       use.names = TRUE) %>%
+  data.table()
+
+setorder(timeSpent, session_code, participant_code, epoch_time)
+```
+
+```{r calcDuration}
+timeSpent[,
+          lag := shift(epoch_time, fill = NA, type = "lag"),
+          by = c("session_code", "participant_code")]
+
+timeSpent[,
+          duration := epoch_time - lag,
+          by = c("session_code", "participant_code")]
+
+timeSpent[,
+          completion := epoch_time %>% max() - epoch_time %>% min(),
+          by = c("session_code", "participant_code")]
+
+duration <- timeSpent[participant_code %in% DT$participant.code,
+                      .(
+                        session_code,
+                        participant_code,
+                        app_name,
+                        page_name,
+                        page_index,
+                        page_submission = epoch_time,
+                        time_spent = duration,
+                        completion_time = completion
+                      )]
+
+save(duration, file = paste0("../../../data/processed/rda/", fileName, "_timeSpent", ".rda"))
+write.csv(duration, file = paste0("../../../data/processed/csv/", fileName, "_timeSpent", ".csv"))
+```
+
 # Outlook

### 2021-08-11 analysis/reports/rmd/03_dataAnalyses.Rmd
update reports

@@
     toc_float: false
-    code_folding: true
 ---
 
-```{r setup, include=TRUE}
+```{r setup, results = "hide", echo = FALSE}
+if(knitr::is_html_output()){
+  knitr::opts_chunk$set(echo = FALSE)
+}else{
   knitr::opts_chunk$set(echo = TRUE)
+}
 
+Sys.setlocale(category = "LC_ALL",
+              locale = "en_US.UTF-8")
+```
+
+```{r packages}
 library(data.table)
@@
 
-# Background
-
-In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree].
-The first experiment will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances).
-The current demo version of the experiment can be found [here](https://cliccs.herokuapp.com/).
-Click [here](https://github.com/Howquez/coopUncertainty) to visit the corresponding Github repository.
-
-[This report](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd/03_dataAnalyses.Rmd) is the third in a series of reports covering this project.
-It reads the data prepared in the previous reports and analyzes them.
+```{r layout}
+layout <- theme(panel.background = element_rect(fill = "white"),
+                panel.grid = element_blank(),
+                panel.grid.major.y = element_line(colour="gray", size=0.25),
+                legend.key = element_rect(fill = "white"),
+                axis.line.x.bottom = element_line(size = 0.25),
+                axis.line.y.left = element_line(size = 0.25),
+                axis.title.y = element_text(size = rel(0.75)),
+                plot.margin = unit(c(0.25,0.25,0.25,0.25), "cm"),
+                legend.title = element_blank()
+                )
+colors <- c("#F3B05C", "#1E4A75", "#65B5C0", "#AD5E21")
+```
 
@@
 base::load(file="../../../data/processed/rda/replication2021_COVS.rda")       # read replicationCovariates
+base::load(file="../../../data/processed/rda/replication2021_meta.rda")       # read meta data
+base::load(file="../../../data/processed/rda/replication2021_timeSpent.rda")  # read time spent
 ```
@@
                   fill = TRUE)
+```
 
+# Key Takeaways
+
+- We replicate a public goods experiment with dynamic interdependency and find similar results as @GACHTER2017.
+- Absolute contributions increase over time.
+- Just as in _static_ public goods experiments, the share of endowments contributed decreases over time.
+- The richest groups earn fifteen times more than the poorest groups.
+- While there clearly is growth, groups do not realize the maximal potential efficiency and earn just over `r main[treatment == "replication" & round == 10, mean(stock)/(80*1.5^10)*100] %>% round(digits=1)`% of what is possible.
+- Even though we conducted the experiment online and remotely, dropouts (or "attrition") are no concern.
+- Relying on an inexperienced non-convenience sample, `r trunc((R1[comprehension > 1] %>% NROW() / R1[!(is.na(comprehension))] %>% NROW())*100)`% of all participants stated that they understood the game.
+- Participants make relatively fast decisions which makes longer games feasible in the future.^[Taken together with inefficient growth and the lack of dropouts, additional rounds are fairly cheap.]
+
+# Background
+
+In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree].
+This experiment  replicated Gächter et al.'s NOPUNISH 10-round treatment arm as close as possible (given the remote circumstances).
+The current demo version of the experiment can be found [here](https://cliccs.herokuapp.com/).
+Click [here](https://github.com/Howquez/coopUncertainty) to visit the corresponding Github repository.
+
+[This report](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd/03_dataAnalyses.Rmd) is the third in a series of reports covering this project.
+It reads the data prepared in the previous reports and analyzes them.
+The whole replication project is registered in the AEA RCT Registry and the unique identifying number is: [AEARCTR-0007902](https://doi.org/10.1257/rct.7902-2.0) [@preregistration].
+
+# Data
+
+I'll refer to the data @GACHTER2017 provided as _GMTV_ or _noPunish10_ in what follows.
+GMTV conducted most of their sessions in late 2012.
+All of these sessions ran in Nottingham using a student sample.
+collected They `r GMTV[, groupID %>% unique() %>% length()]` observations in their NOPUNISH 10 treatment arm.
+Our data, refered to as _replication_ is more recent, gathered remotely in Hamburg using a different tech stack as well as a different sample.
+
+We conducted a series a `r meta %>% NROW()` sessions in between `r meta[, date %>% min() %>% format("%A, %B %d")]` to `r meta[, date %>% max() %>% format("%A, %B %d %Y")]` and collected `r meta[, observations %>% sum()]` observations (from `r meta[, participants %>% sum()]` participants) in total.
+`r meta[, dropouts %>% sum()]` additional participants could not be matched with other group members or failed to answer the comprehension questions.
+These participants are labeled as dropouts.
+None of them dropped out during the session such that attrition is no problem here.
+
+```{r meta}
+meta %>% kable()
+```
+
+Two of these sessions were special: The first (`r meta[1, session.code]`) as well as the last one (`r meta[, session.code %>% tail(n=1)]`).
+The first session suffered technical problems such that the risk elicitation task was omitted.
+The last session (almost exclusively) relied on a student sample as our non-student sample was exhausted after the first three sessions.
+As a consequence, the last session was conducted with 59 students while all others were conducted without any students.
+I'll therefore create a boolean `student` variable.
+
+```{r studentSample}
+main[, student := FALSE]
+main[session.code == "d6jrsxnr" | treatment == "noPunish10",
+     student := TRUE]
+
+R1[, student := FALSE]
+R1[session.code == "d6jrsxnr" | treatment == "noPunish10",
+   student := TRUE]
+```
+
+All participants were recruited in by the University of Hamburg's  WISO Research Lab using HROOT [@hroot].
+
+```{r cleanUp1}
 rm(list = c("replication", "GMTV", "replicationFirstRound", "GMTVFirstRound", "GMTVCovariates", "replicationCovariates"))
@@
 
-```{r layout}
-layout <- theme(panel.background = element_rect(fill = "white"),
-                panel.grid = element_blank(),
-                panel.grid.major.y = element_line(colour="gray", size=0.25),
-                legend.key = element_rect(fill = "white"),
-                axis.line.x.bottom = element_line(size = 0.25),
-                axis.line.y.left = element_line(size = 0.25),
-                axis.title.y = element_text(size = rel(0.75)),
-                plot.margin = unit(c(0.25,0.25,0.25,0.25), "cm"),
-                legend.title = element_blank()
-                )
+## First Round
 
-colors <- c("#F3B05C", "#1E4A75", "#65B5C0", "#AD5E21")
+We start by discussing initial contributions which assume the full range between 0 and 20 as Table 1 illustrates.
+Both the median as well as the mean are about 10 tokens, that is, 50% of the initial endowment in both data sources.
+This is comparable to initial contributions in the standard game with partner matching.^[See Figure 3B in @fehrgaechter2000, for instance.]
+
+```{r summary0, results = "asis", warning = FALSE, fig.cap = "test"}
+
+if(knitr::is_html_output()){
+  type <- "html"
+} else {
+  type = "latex"
+}
+
+replication <- R1[treatment == "replication", ownContribution]
+GMTV    <- R1[treatment == "noPunish10", ownContribution]
+
+rows <- sapply(X = list(replication, GMTV), FUN = NROW) %>% max()
+temp <- data.frame(replication = c(replication, rep(NA, rows - NROW(replication))),
+                   GMTV = c(GMTV, rep(NA, rows - NROW(GMTV))))
+
+stargazer(temp,
+          summary.stat = c("mean", "median","sd", "max", "min", "n"),
+          type = type, 
+          flip = TRUE, 
+          header=FALSE)
+
+rs1 <- wilcox.test(replication, 
+                   GMTV,
+                   exact = FALSE)$p.value %>% 
+  round(digits = 4) %>% 
+  formatC(format = "f", 
+          digits = 4)
 ```
 
-## First Round
+The two-sided rank sum test (comparing differences between data sources) yields a p-Value of `r rs1` for the mean contribution in first round of the game.
 
@@
 
-## Provision of the public good and wealth creation
+## Provision of the public good
+
+We proceed by further discussing contributions.
+The left panel in Figure 1 shows the average amount of tokens participants contributed over time.
+Contributions are clearly non-zero and are increasing over time in the replication treatment.^[Participants contribute about 10 tokens in the first round] While contributions flatten in the replication, the GMTV data exhibit a drop in the last round.
+Note that increasing contributions over time imply that participants have increasing endowments over time.
+Hence, increasing contributions do not necessarily imply that participants contribute increasing shares of their endowments.
+The right panel in Figure 1 shows the share of overall endowments contributed over time.
+In the original data, participants contribute around 53% of their endowment in round 1.
+This amount steadily decreases.
+The replication exhibits a similar pattern with an initial average contributions of 50%.
+Both treatments resemble the results from the standard game: Just as in @fehrgaechter2000 contributions start at a level of around 50-60% of endowments and decrease to around 10% of endowments in round 10.
 
@@
 
+# SHARE <- main[,
+#             .(share = sum(contribution)/sum(endowment)),
+#             by = c("round", "treatment")]
+
 upperLimit <- 1
@@
 
-```{r summary1, results = "asis", warning = FALSE, fig.cap = "test"}
+### Hm..?
 
-if(knitr::is_html_output()){
-  type <- "html"
-} else {
-  type = "latex"
-}
+The plot above puzzles me a little as the right panel visualizes the mean `share==contribution/endowment` by treatment and round.
+This yields a different result than the mean of the sum of contributions divided by the sum of endowments per treatment and round as the following table illustrates.
 
-replication <- main[treatment == "replication" & round == 10, stock]
-GMTV    <- main[treatment == "noPunish10" & round == 10, stock]
-
-rows <- sapply(X = list(replication, GMTV), FUN = NROW) %>% max()
-temp <- data.frame(replication = c(replication, rep(NA, rows - NROW(replication))),
-                   GMTV = c(GMTV, rep(NA, rows - NROW(GMTV))))
-
-stargazer(temp,
-          summary.stat = c("mean", "median","sd", "max", "min", "n"),
-          type = type, 
-          flip = TRUE, 
-          header=FALSE)
-
-rs1 <- wilcox.test(replication, 
-                   GMTV,
-                   exact = FALSE)$p.value %>% 
-  round(digits = 4) %>% 
-  formatC(format = "f", 
-          digits = 4)
-
+```{r}
+main[round == 10, 
+     .(contribution = mean(contribution), 
+       endowment = mean(endowment), 
+       # share = mean(share), # same thing as the following line
+       share = mean(contribution/endowment),
+       sumContBySumEndo = mean(sum(contribution)/sum(endowment))), 
+     by = c("treatment", "round")] %>% 
+  kable()
 ```
 
-The table above displays summary statistics for the 10th period's ```stock``` a.k.a _Wealth_. The rank sum test yields a p-Value of `r rs1` for the mean wealth during the last period of the game.
+```{r plotContributionsStudents, eval = FALSE}
+SUM <- main[treatment == "replication",
+            lapply(.SD, mean, na.rm = TRUE),
+            by = c("round", "student"),
+            .SDcols = "contribution"]
 
-The following table shows a simple regression to illustrate differences in the 10th period's wealth between the replication's data and GMTV's data.
+SUM[,
+    sum := round(contribution/4)]
 
-```{r tableStock, results = "asis", warning = FALSE}
+upperLimit <- SUM$contribution %>% max() %>% round() + 10
 
-# create subsets
-main_all  <- main[round == 10]
-main_poor <- main[round == 10 & rich == FALSE]
-main_rich <- main[round == 10 & rich == TRUE]
+p1 <- ggplot(data = SUM, 
+             aes(x = round, y = contribution, fill = student, color = student, lty = student)) +
+  layout +
+  theme(legend.position="bottom") +
+  geom_line(show.legend=FALSE) +
+  geom_point() +
+  scale_x_continuous(name="",  breaks = 1:15) +
+  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
+  labs(y = "Average Amount of Tokens contributed") +
+  scale_color_manual(values = colors) + 
+  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
 
-# create table
-if(knitr::is_html_output()){
-  type <- "html"
-} else {
-  type = "latex"
-}
-
-stargazer(lm(formula = stock ~ treatment, data = main_all),
-          lm(formula = stock ~ treatment, data = main_poor),
-          lm(formula = stock ~ treatment, data = main_rich),
-
-          column.labels = c("All", "Below median", "Above median"),
-          model.numbers = FALSE,
-          dep.var.labels = "Wealth",
-          header=FALSE,
-          covariate.labels = c("Replication"),
-
-          type = type, digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
-          )
+rm(list = c("SUM"))
 ```
 
-These information are also plotted over all periods in the following figure.
+## Wealth Creation
+
+Possibly of more interest are the implications contributions have for wealth generation and growth.
+To measure growth, we define a variable _stock_ which sums the endowments of all participants in a given group at the end of the round (that is, after the contributions have been made, multiplied and redistributed).
+@GACHTER2017 refer to that variable as "wealth" so we will do the same in what follows.
+Before the start of round 1, wealth will be 80 in all groups by construction.
+The maximal wealth that can be reached in round 10 (if everyone contributes their entire endowment in each round) is approximately `r (80*1.5^10) %>% trunc()` tokens or `r (80*1.5^10 /20) %>% trunc()` Euro per group.
+Table 3 shows some summary statistics regarding wealth.
+Groups do achieve growth on average.
+While there is clearly growth, groups do not realize the maximal potential efficiency as the replication groups reach on average a level of `r main[treatment == "replication" & round == 10, mean(stock)] %>% trunc()` tokens out of `r (80*1.5^10) %>% trunc()` maximally possible or `r main[treatment == "replication" & round == 10, mean(stock)/(80*1.5^10)*100] %>% round(digits=1)`%.
+As in the original data, there is large heterogeneity with the richest group reaching `r main[treatment == "replication" & round == 10, max(stock)]` tokens whereas the poorest group ends up with `r main[treatment == "replication" & round == 10, min(stock)]` tokens.
 
@@
 
+Figure 2 shows the dynamics of wealth over time.
+The left panel focuses on all groups, the upper right panel  on those with above median wealth after round 10 (“successful” groups) and the lower left panel on those with below median wealth after round 10 (“unsuccessful” groups).
+The average wealth is increasing across rounds and is substantially above 80 once round 10 was played as Table 2 illustrates.
+
+```{r summary1, results = "asis", warning = FALSE, fig.cap = "test"}
+
+if(knitr::is_html_output()){
+  type <- "html"
+} else {
+  type = "latex"
+}
+
+replication <- main[treatment == "replication" & round == 10, stock]
+GMTV    <- main[treatment == "noPunish10" & round == 10, stock]
+
+rows <- sapply(X = list(replication, GMTV), FUN = NROW) %>% max()
+temp <- data.frame(replication = c(replication, rep(NA, rows - NROW(replication))),
+                   GMTV = c(GMTV, rep(NA, rows - NROW(GMTV))))
+
+stargazer(temp,
+          summary.stat = c("mean", "median","sd", "max", "min", "n"),
+          type = type, 
+          flip = TRUE, 
+          header=FALSE)
+
+rs1 <- wilcox.test(replication, 
+                   GMTV,
+                   exact = FALSE)$p.value %>% 
+  round(digits = 4) %>% 
+  formatC(format = "f", 
+          digits = 4)
+
+```
+
+The two-sided rank sum test (comparing differences between data sources) yields a p-Value of `r rs1` for the mean wealth after the last round of the game.
+
+### Wealth Differences between Data Sources
+
+We next consider whether we were able to replicate GMTV's results with our data.
+Absolute contributions tended to be higher in @GACHTER2017 but end up at around the same level as in the replication due to a stark decline in contributions on the last round.
+In terms of shares contributed both data sources exhibit a similar pattern: they decline and do not stabilize.
+Even though the share of current endowments contributed in the last round is quite similar, the share declined a little faster in our data.
+
+Our groups also tend to be poorer.
+Median wealth is higher in GMTV.
+This difference in mean ranks is not significant according to a two-sided ranksum test, however.
+To assess the statistical significance of differences in means, we run OLS regressions where we regress wealth on a treatment dummy for _Replication_ (Table 3).
+These regressions show that differences in means are only significant for below median groups.
+
+```{r tableStock, results = "asis", warning = FALSE}
+
+# create subsets
+main_all  <- main[round == 10]
+main_poor <- main[round == 10 & rich == FALSE]
+main_rich <- main[round == 10 & rich == TRUE]
+
+# create table
+if(knitr::is_html_output()){
+  type <- "html"
+} else {
+  type = "latex"
+}
+
+stargazer(lm(formula = stock ~ treatment, data = main_all),
+          lm(formula = stock ~ treatment, data = main_poor),
+          lm(formula = stock ~ treatment, data = main_rich),
+
+          column.labels = c("All", "Below median", "Above median"),
+          model.numbers = FALSE,
+          dep.var.labels = "Wealth",
+          header=FALSE,
+          covariate.labels = c("Replication"),
+
+          type = type, digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
+          )
+```
+
 ## Inequality
 
-The following figure plots the Gini-coefficient These over all periods.
+In this subsection, we focus on the amount of inequality created endogenously in our setting.
+The smallest possible value the Gini coefficient takes is zero (if all four group members own one fourth of the wealth) and the largest possible value it takes is one (if one group member holds the entire wealth).
+Table 4 shows some summary statistics regarding the Gini coefficient.
+
+The round 10 Gini coefficient ranges between `r main[treatment == "replication" & round == 10, gini %>% min()] %>% round(digits = 3)` and `r main[treatment == "replication" & round == 10, gini %>% max()] %>% round(digits = 3)` in our data with a median of `r main[treatment == "replication" & round == 10, gini %>% median()] %>% round(digits = 3)`.
+
+```{r summary2, results = "asis", warning = FALSE}
+
+if(knitr::is_html_output()){
+  type <- "html"
+} else {
+  type = "latex"
+}
+
+replication <- main[treatment == "replication" & round == 10, gini]
+GMTV    <- main[treatment == "noPunish10" & round == 10, gini]
+
+rows <- sapply(X = list(replication, GMTV), FUN = NROW) %>% max()
+temp <- data.frame(replication = c(replication, rep(NA, rows - NROW(replication))),
+                   GMTV = c(GMTV, rep(NA, rows - NROW(GMTV))))
+
+stargazer(temp,
+          summary.stat = c("mean", "median","sd", "max", "min", "n"),
+          type = type, 
+          flip = TRUE, 
+          header=FALSE)
+
+rs2 <- wilcox.test(replication, 
+                   GMTV,
+                   exact = FALSE)$p.value %>% 
+  round(digits = 4) %>% 
+  formatC(format = "f", 
+          digits = 4)
+
+```
+
+The two-sided rank sum test yields a p-Value of `r rs2` for the mean ```gini``` during the last round of the game.
+
+Figure 3 illustrates the dynamics of the Gini coefficient (at the end of each round) over time and shows that inequality increases slightly.
 
@@
 
-The following table shows a simple regression to illustrate differences in the 10th period's Gini coefficient between the replication's data and GMTV's data.
+### Inequality Differences between Data Sources
+
+Once more, we consider whether we were able to replicate GMTV's results with our data.
+
+The following table shows a simple OLS regression to illustrate differences in the 10th round's Gini coefficient between the replication's data and GMTV's data.
+Mean Gini coefficients are similar across data sources and there are no statistically significant differences in mean Gini coefficients.
 
@@
 
-```{r summary2, results = "asis", warning = FALSE}
+# Time Spent
 
-if(knitr::is_html_output()){
-  type <- "html"
-} else {
-  type = "latex"
-}
+Participants spent approximately `r duration[, completion_time %>% unique() %>% mean()] %/% 60 + 1` minutes completing the experiment.
+Reading the instructions and answering the comprehension questions took the most time, that is, `r duration[page_name == "Intro_Instructions", time_spent %>% unique() %>% mean()] %/% 60 + 1` minutes.
+The public goods game required `r duration[app_name == "dPGG", time_spent %>% sum(), by = c("session_code", "participant_code")][,V1] %>% mean(na.rm = TRUE) %/% 60` minutes of the participants' time.
 
-replication <- main[treatment == "replication" & round == 10, gini]
-GMTV    <- main[treatment == "noPunish10" & round == 10, gini]
+```{r plotTime, fig.cap = "Average Time Spent for each Contribution per Round."}
+N <- duration[, participant_code %>% unique() %>% length()]
+plotDT <- duration[app_name == "dPGG" & page_name == "dPGG_Decision",
+                   .(time_spent = time_spent %>% sum()),
+                   by = c("session_code", "participant_code", "page_index", "page_name")]
 
-rows <- sapply(X = list(replication, GMTV), FUN = NROW) %>% max()
-temp <- data.frame(replication = c(replication, rep(NA, rows - NROW(replication))),
-                   GMTV = c(GMTV, rep(NA, rows - NROW(GMTV))))
+plotDT[, round := seq(from = 1, to = 10), by = c("participant_code")]
 
-stargazer(temp,
-          summary.stat = c("mean", "median","sd", "max", "min", "n"),
-          type = type, 
-          flip = TRUE, 
-          header=FALSE)
+upperLimit <- plotDT[, time_spent %>% mean(), by = c("round")] %>% max()
 
-rs2 <- wilcox.test(replication, 
-                   GMTV,
-                   exact = FALSE)$p.value %>% 
-  round(digits = 4) %>% 
-  formatC(format = "f", 
-          digits = 4)
-
+ggplot(data = summarySE(data = plotDT,
+                        measurevar = "time_spent",
+                        groupvars=c("round"),
+                        na.rm = FALSE,
+                        conf.interval = 0.95,
+                        .drop = TRUE),
+       mapping = aes(x = round, y = time_spent)) +
+  layout +
+  theme(legend.position="bottom") +
+  geom_line(show.legend=FALSE, color = colors[2], lty=2) +
+  geom_errorbar(aes(ymin=time_spent-ci, ymax=time_spent+ci), width=.25, alpha = 0.5, color = colors[2]) +
+  geom_point(color = colors[2]) +
+  scale_x_continuous(name="",  breaks = 1:10) +
+  scale_y_continuous(limits = c(0, upperLimit + 10), expand = c(0, 0)) +
+  labs(y = "Time Passed in Seconds", caption = "Bars indicate 95% confidence intervals.") +
+  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
 ```
 
-The table above displays summary statistics for the 10th period's ```gini``` .
-The rank sum test yields a p-Value of `r rs2` for the mean ```gini``` during the last period of the game.
+Figure 4 illustrates the time participants needed to make each of their contributions during the replication.
+One can see that the initial as well as most of the other contributions take about 20 seconds of time.
+Interestingly, the second contribution takes (on average) about 50% more time than the first one - presumably because this is the first time participants' learn their respective group members' actions.
+The third contribution is a little faster and all subsequent contributions stabilize at `r plotDT[round > 3, time_spent %>% mean()] %>% ceiling()` seconds.
 
-## Sample Properties
+Given that no participant dropped out after answering the comprehension questions correctly and given that participants need less than 20 seconds to make their contributions, more than 10 rounds are feasible.
+
+# Sample Properties
 
@@
 ```
-
-In addition to the summary statistics a regression table for each covariate as a dependent variable is needed. The independent variable will then be the data source (i.e. GMTV vs replication).
 
@@
 ```
+
+# Hamburg: How do Students compare to non-Students?
+
+This section considers the replication data only.
+Doing so, we'll exploit the circumstance that we recruited from both the convenience or "student" sample as well as the non-convenience sample _(Hamburg Panel)_ and analyze the differences between the two.
+
+```{r sample0, results = "asis", warning = FALSE, fig.cap = "test"}
+
+if(knitr::is_html_output()){
+  type <- "html"
+} else {
+  type = "latex"
+}
+
+students <- R1[treatment == "replication" & student == TRUE, ownContribution]
+HHpanel  <- R1[treatment == "replication" & student == FALSE, ownContribution]
+
+rows <- sapply(X = list(students, HHpanel), FUN = NROW) %>% max()
+temp <- data.frame(Students = c(students, rep(NA, rows - NROW(students))),
+                   `HH-panel` = c(HHpanel, rep(NA, rows - NROW(HHpanel))))
+
+stargazer(temp,
+          summary.stat = c("mean", "median","sd", "max", "min", "n"),
+          type = type, 
+          flip = TRUE, 
+          header=FALSE)
+
+rs1 <- wilcox.test(students, 
+                   HHpanel,
+                   exact = FALSE)$p.value %>% 
+  round(digits = 4) %>% 
+  formatC(format = "f", 
+          digits = 4)
+```
+
+We start by looking at the initial contributions.
+As Table 5 illustrates, there is no difference in averages, standard deviation or the range.
+The two-sided rank sum test (comparing differences between data sources) yields a p-Value of `r rs1` for the mean contribution in first round of the game.
+
+While the initial contributions are on average quite similar between the two sample, the subsequent contributions differ.
+In both absolute and relative terms, the Hamburg-Panel tends to contribute more than the student sample as the following Figure shows.
+
+```{r sampleContributions}
+
+SUM <- main[treatment == "replication",
+            lapply(.SD, mean, na.rm = TRUE),
+            by = c("round", "student"),
+            .SDcols = "contribution"]
+
+SUM[,
+    sum := round(contribution/4)]
+
+upperLimit <- SUM$contribution %>% max() %>% round() + 10
+
+p1 <- ggplot(data = SUM, 
+             aes(x = round, y = contribution, fill = student, color = student, lty = student)) +
+  layout +
+  theme(legend.position="bottom") +
+  geom_line(show.legend=FALSE) +
+  geom_point() +
+  scale_x_continuous(name="",  breaks = 1:15) +
+  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
+  labs(y = "Average Amount of Tokens contributed") +
+  scale_color_manual(values = colors, labels = c("Hamburg-Panel", "Students")) + 
+  guides(lty = FALSE, fill = FALSE) +
+  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
+
+SHARE <- main[treatment == "replication",
+            lapply(.SD, mean, na.rm = TRUE),
+            by = c("round", "student"),
+            .SDcols = "share"]
+
+upperLimit <- 1
+
+p2 <- ggplot(data = SHARE, 
+             aes(x = round, y = share, fill = student, color = student, lty = student)) +
+  layout +
+  theme(legend.position="bottom") +
+  geom_line(show.legend=FALSE) +
+  geom_point() +
+  scale_x_continuous(name="",  breaks = 1:15) +
+  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
+  labs(y = "Share of Current Endowment contributed") +
+  guides(lty = FALSE, fill = FALSE) +
+  scale_color_manual(values = colors, labels = c("Hamburg-Panel", "Students"))
+
+p1 + p2 + plot_layout(guides = "collect") & theme(legend.position = "bottom")
+
+rm(list = c("SUM", "SHARE", "p1", "p2"))
+```
+
+Differences in contributions lead to differences in wealth.
+The Hamburg-Panel therefore earned more during the public goods game than the student sample.
+This can be seen in the following figure as well as in the subsequent table:
+
+```{r sampleStock, fig.cap = "Average wealth over time across samples."}
+STOCK <- main[treatment == "replication",
+              lapply(.SD, mean, na.rm = TRUE),
+              by = c("round", "student"),
+              .SDcols = "stock"]
+
+upperLimit <- STOCK$stock %>% max() %>% round() + 20
+
+ggplot(data = STOCK, 
+       aes(x = round, y = stock, fill = student, color = student, lty = student)) +
+  layout +
+  theme(legend.position="bottom") +
+  geom_line(show.legend=FALSE) +
+  geom_point() +
+  scale_x_continuous(name="",  breaks = 1:10) +
+  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
+  labs(y = "Wealth") +
+  guides(lty = FALSE, fill = FALSE) +
+  scale_color_manual(values = colors, labels = c("Hamburg-Panel", "Students"))
+
+rm(list = c("STOCK"))
+```
+
+```{r}
+main[treatment == "replication" & round == 10, 
+     lapply(.SD, mean, na.rm = TRUE), 
+     by = c("round", "student"), 
+     .SDcols = c("contribution", "share", "stock")] %>%
+  kable()
+```

### 2022-10-08 analysis/R/paper.Rmd
added "quarto" and "paper" (already deprecated) + no clue what happened otherwise. Its been a long time

---
title: "Growth and inequality in public good provision: an extended replication"
description: |
  Report and analysis protocoll.
author:
  - name: Hauke Roggenkamp 
    url: https://www.ibt.unisg.ch/team/hauke-roggenkamp/
    affiliation: Helmut Schmidt University
    affiliation_url: https://www.hsu-hh.de/en/
  - affiliation: Institute for Behavioral Science and Technology
    affiliation_url: https://www.ibt.unisg.ch/
date: "`r Sys.Date()`"
bibliography: ../biblio.bib
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: false
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r packages}
# install this package once, it'll then install and load all remaining packages
# install.packages("pacman")

pacman::p_load(magrittr, data.table, stringr, lubridate, glue, DescTools, haven,
               stargazer, ggplot2, patchwork, MetBrewer, Rmisc)
```

```{r design}
# ggplot layout
layout <- theme(panel.background = element_rect(fill = "transparent", color = NA),
                plot.background = element_rect(fill = "transparent", color = NA),
                panel.grid = element_blank(),
                panel.grid.major.y = element_blank(),
                legend.key = element_rect(fill = "transparent"),
                axis.line = element_line(size = 0.25),
                axis.ticks = element_line(size = 0.25),
                plot.caption = element_text(colour = "#555555"),
                legend.title = element_blank()
)

# color
colors <- met.brewer(name="Tam",n=7,type="discrete")
cPrimary = "#ffd353"
cSecondary = "#9f2d55"
cInfo = "#34168"
```

<!-- OUR DATA -->

```{r readAllData}
# identify files of all sessions
files <- list.files(path = "../../data/replication/",
                       recursive = TRUE,
                       full.names = TRUE)

# load all of them into a list
csvs <- list()
for(i in files){
  name <- str_extract(string = i, pattern = "2021.*")
  temp <- read.csv(i, stringsAsFactors = FALSE) %>% data.table()
  csvs[[name]] <- temp
}

# bind list into single data table
full <- rbindlist(l = csvs, use.names = TRUE) %>% data.table()

# ignore observations who have not made it to the first contribution
DT <- full[participant._index_in_pages > 2 & 
             participant.time_started != "" & 
             participant.label != "" &
             !(is.na(dPGG.1.player.contribution))]

# tidy up
rm(list = c("files", "csvs", "i", "name", "temp"))
```

```{r metaData}
# aggregate each session's meta data
meta_long <- full[participant.time_started != "" & 
                    participant.label != "",
                  .(session.code,
                    participant.label,
                    participant.time_started,
                    dPGG.1.player.contribution)]

# reformat time stamp in new variables
meta_long[, `:=`(date = participant.time_started %>% ymd_hms() %>% date(),
                 hour = participant.time_started %>% ymd_hms() %>% hour())]

# aggregate and count 
meta <- meta_long[,
                  .(date = date %>% unique(),
                    time = hour %>% unique() %>% paste("00", sep = ":"),
                    showups = participant.time_started %>% length(),
                    dropouts = dPGG.1.player.contribution %>% is.na() %>% sum(na.rm = FALSE)),
                  by = session.code]

# get number of participants and observations (groups of 4)
meta[,
     `:=`(participants = showups - dropouts,
          observations = (showups - dropouts)/4)]

# save data
fileName <- "replication2021"
save(meta, file = paste0("../../data/processed/rda/", fileName, "_meta", ".rda"))
write.csv(meta, file = paste0("../../data/processed/csv/", fileName, "_meta", ".csv"))

rm(list = c("full", "meta_long"))
```

```{r identifyStudents}
# we had to invite students as the general population sample was exhausted, unfortunately. let's identify them:
invitedStudents <- read.table(file = "../../data/sample/invited_students.txt", col.names = c("participant.label")) %>%
  data.table()
# note that these students participated in the ultimate session
```

```{r focusOnFirstRound}
# create data table 
replicationFirstRound <- DT[,
                 .(participant.code,
                   treatment = "replication",
                   session.code,
                   groupID = paste(session.code, dPGG.1.group.id_in_subsession, sep = "_"),
                   othersContribution = dPGG.1.group.total_contribution - dPGG.1.player.contribution,
                   ownContribution = dPGG.1.player.contribution,
                   trust = Outro.1.player.PQ11,
                   comprehension = dPGG.10.player.comprehension)]

# save data
save(replicationFirstRound, file = paste0("../../data/processed/rda/", fileName, "_R1", ".rda"))
write.csv(replicationFirstRound, file = paste0("../../data/processed/csv/", fileName, "_R1", ".csv"))
```

```{r subsetData}

# identify most relevant variables
mRegex <- "participant\\.code$|session\\.code$|dPGG\\.1\\.group\\.id_in_subsession|^dPGG.1.player.id_in_group$|\\.1\\.player.belief|endowment|contribution|stock|gain$|bot_active|10.player.comprehension|10.player.donation"
mainVariables <- str_subset(string = names(DT), pattern = mRegex)

# prune all other variables
subset <- DT[, ..mainVariables]

# tidy up
rm(list = c("mRegex", "mainVariables"))
```

```{r addNewVariables}
# refactor groupID such that it eventually contains treatment-info
subset[, groupID := paste(session.code, 
                          dPGG.1.group.id_in_subsession,
                          sep = "_")]

# add share as contribution/endowment
for(round in 1:10){
  contribution <- glue("dPGG.{round}.player.contribution")
  endowment <- glue("dPGG.{round}.player.endowment")
  subset[, glue("dPGG.{round}.player.share") := subset[[contribution]]/subset[[endowment]] ]
}

# add treatment variable
subset[,
       treatment := "replication"]
```

```{r calculateAggregates}
# we need to aggregate some outcomes on a groupID level (per sessions per treatment)
# we'll do so using a loop
# this will yield a list of data tables that will be merged to a list eventually.
cluster <- c("treatment", "session.code", "groupID")
outcomes <- c("contribution", "endowment", "stock", "gain", "bot_active")

DTs <- list()
for(outcome in outcomes){
  if(outcome == "bot_active"){
    var = names(subset) %>% str_subset(pattern = glue("group\\.{outcome}$"))
  } else {
    var = names(subset) %>% str_subset(pattern = glue("player\\.{outcome}$"))
  }

  # calculate either averages or the sum per round per group
  aggregates = subset[, lapply(.SD, sum, na.rm=TRUE), 
                      by = cluster, 
                      .SDcols=var]

  # transform from wide to long
  meltedAggregates <- melt(aggregates, id.vars = cluster, measure.vars = var)
  DTname <- glue("{str_to_title(outcome)}")
  DTs[[DTname]] <- meltedAggregates
  rm(list = c("DTname", "meltedAggregates", "aggregates", "var", "outcome"))
}
```

```{r renameVariables}
# each data table in that list has the same column names.
# the outcomes are all named "value", for instance.
# now, we"ll infer the round number (contained in the variable name)
for(i in 1:length(outcomes)){
  DTs[[i]] <- DTs[[i]][,
                       .(treatment,
                         session.code,
                         groupID,
                         round = str_replace_all(string = variable,
                                                 pattern = "\\D", 
                                                 replacement="") %>% as.integer(),
                         value # to be renamed afterwards
                       )
  ]
  # rename "value" to outcome variable
  setnames(DTs[[i]], old = "value", new = outcomes[i])
}

# tidy up
rm("i")
```

```{r calculateGini}
# repeat everything for the gini
var = names(subset) %>% str_subset(pattern = "player\\.stock$")
gini = subset[,
              lapply(.SD, Gini, na.rm=TRUE), 
                by = cluster, 
                .SDcols=var
              ]
Gini <- melt(gini, id.vars = cluster, measure.vars = var)

DTs[["Gini"]] <- Gini[,
                    .(treatment,
                      session.code,
                      groupID,
                      round = str_replace_all(string = variable,
                                              pattern = "\\D", 
                                              replacement="") %>% as.integer(),
                      gini = value
                       )]
rm(list = c("var", "gini", "Gini"))

# note that GMTV used start of period earnnings, i.e. endowments. We use end of period earnings, i.e. stock.
# this adjustment has been considered in our processing of GMTVs data.
```

```{r mergerEverything4FinalData}
# now merge every table in the list to one final data table called "replication"
replication <- Reduce(function(...) merge(..., by=c(cluster, "round"), all = TRUE), DTs)

# tidy up
rm(list = c("cluster", "contribution", "endowment", "round", "DTs", "outcomes"))
```

```{r calculateShare}
# define the share (one of the main outcome variables) as 
# the sum of contributions devided by the sum of endowments
replication[, share := contribution/endowment]
```

```{r defineRichGroups}
# use the median to differentiate between poor and rich groups (as GMTV did)
median <- replication[round == 10,
                      median(stock)]

# find the groups that end up rich or poor
richGroups <- replication[round == 10 & stock > median,
                          unique(groupID)]

poorGroups <- replication[round == 10 & stock < median,
                          unique(groupID)]

# mark these groups for each period
replication[groupID %in% richGroups,
            rich := TRUE]

replication[groupID %in% poorGroups,
            rich := FALSE]

# tidy up
rm(list = c("median", "poorGroups", "richGroups"))

```

```{r misc}
# flag observations where at least one participant did not understand the game
noComp <- subset[dPGG.10.player.comprehension == 0,
                 groupID] %>% unique()
replication[,
     noComprehension := 0]
replication[groupID %in% noComp,
     noComprehension := 1]

# drop observations (i.e. groups in rounds) with dropouts (bot_active == 1) and
# where round > 10
replication <- replication[bot_active == 0 & round <= 10]

# tidy up
rm("noComp")
```

```{r saveData}
save(replication, file = paste0("../../data/processed/rda/", fileName, ".rda"))
write.csv(replication, file = paste0("../../data/processed/csv/", fileName, ".csv"))
```

```{r createCovariates}

# so far, I neglected many variables in what happened before. The following few lines
# deal with some of these variables in a similar procedure

# add variables
DT[, treatment := "replication"]
DT[, groupID := paste(session.code, dPGG.1.group.id_in_subsession, 
                    sep = "_")]

# subset
cRegex <- "participant.code|session.code|treatment|groupID|Outro.1.player|10.player.donation|10.player.stock|switching_row|inconsistent"
covariates <- str_subset(string = names(DT),
                            pattern = cRegex)
CT <- DT[, ..covariates]

# rename
names(CT) <- names(CT) %>% 
  str_replace_all(pattern =".*player\\.",
                  replacement = "") %>%
  str_to_lower()
names(CT)[names(CT) == "groupid"] <- "groupID"

# refactor
CT[, donation := donation/20] # exchange rate tokens to real world currency 1/20
CT[donation %>% is.na, donation := 0]
CT[, gender := ifelse(test = gender == "female",
                      yes  = 1,
                      no   = 0)]
CT[, inconsistent := as.logical(inconsistent)]

# reassign payoff (with stock of the last period)
CT[, payoff := stock]
CT[, stock := NULL]

# write data
replicationCovariates <- CT
save(replicationCovariates, 
     file = paste0("../../data/processed/rda/", fileName, "_COVS", ".rda"))
write.csv(replicationCovariates, 
          file = paste0("../../data/processed/csv/", fileName, "_COVS", ".csv"))

# tidy up
rm(list = c("CT", "cRegex", "covariates"))
```

```{r readTime}
# as before, we need to read a list of files (measuring the time spent per page)

# identify files
files <- list.files(path = "../../data/pageTimes/",
                       recursive = TRUE,
                       full.names = TRUE)

# loop
csvs <- list()
for(i in files){
  name <- str_extract(string = i,
                      pattern = "2021.*")

  temp <- read.csv(i, 
                   stringsAsFactors = FALSE) %>%
    data.table()

  csvs[[name]] <- temp
}

# bind files list to data.table
timeSpent <- rbindlist(l = csvs,
                       use.names = TRUE) %>%
  data.table()

# set oder
setorder(timeSpent, session_code, participant_code, epoch_time)

# tidy up
rm(list = c("files", "i", "name", "temp"))
```

```{r calcDuration}
# shift rows to calculate this duration (per page) as the distance between
# the current and the next time stamp
timeSpent[,
          lag := shift(epoch_time, fill = NA, type = "lag"),
          by = c("session_code", "participant_code")]

timeSpent[,
          duration := epoch_time - lag,
          by = c("session_code", "participant_code")]

# calculate overall time spent as the difference between the min and max time stamp
timeSpent[,
          completion := epoch_time %>% max() - epoch_time %>% min(),
          by = c("session_code", "participant_code")]

# create new data table with selected columns
duration <- timeSpent[participant_code %in% DT$participant.code,
                      .(
                        session_code,
                        participant_code,
                        app_name,
                        page_name,
                        page_index,
                        page_submission = epoch_time,
                        time_spent = duration,
                        completion_time = completion
                      )]

# save data
save(duration, file = paste0("../../data/processed/rda/", fileName, "_timeSpent", ".rda"))
write.csv(duration, file = paste0("../../data/processed/csv/", fileName, "_timeSpent", ".csv"))

# tidy up
rm(list = c("timeSpent", "csvs", "DT"))
```

<!-- ORIGINAL (GMTV) DATA -->

```{r readGMTV}
# having done all that, we need to prepare the original data and bind it to ours
# I'll thus, start by reading the orginal data

DT <- read_dta(file="../../data/gaechteretal/GMTV-data.dta") %>% data.table()
CT <- read_dta(file="../../data/gaechteretal/GMTV-questionnaire-data.dta") %>% data.table()
```

```{r subsetGMTV}
# because we only replicate one of their treatments, I subset accordingly
# noPunish10 <- DT[exp_num == 5 | exp_num == 8 | exp_num == 9]
noPunish10 <- DT[longgame == 0 & punish == 0 & exp_num <= 10]
```

```{r newVariablsGMTV}
# calculate the share of endowments contributed
noPunish10[,
           share := sum/gdp,
           by = .(subj_id, per)]

# calculate gini based on endowments (as GMTV did)
noPunish10[,
           gini2 := Gini(c(tokens, other1, other2, other3)),
           by = .(subj_id, per)]

# calculate gini based on stock (i.e. end of period earnings)
noPunish10[, stock0 := (tokens - putin + 1.5*sum/4) %>% ceiling()]
noPunish10[, stock1 := (other1 - pu1 + 1.5*sum/4) %>% ceiling()]
noPunish10[, stock2 := (other2 - pu2 + 1.5*sum/4) %>% ceiling()]
noPunish10[, stock3 := (other3 - pu3 + 1.5*sum/4) %>% ceiling()]
noPunish10[, 
           gini3 := Gini(c(stock0, stock1, stock2, stock3)),
           by = .(subj_id, per)]
```

```{r createGMTVtable}
# select columns we are interested in and rename a few to match our data

GMTV <- noPunish10[order(gr_id, per),
           .(treatment = "noPunish10", 
             session.code = exp_num,
             groupID = gr_id, 
             round = per,
             contribution = sum,
             endowment = gdp,
             share,
             stock = (gdp + ceiling(sum/4*1.5)*4-sum),
             gain = (ceiling(sum/4*1.5)*4-sum),
             gini = gini3,
             bot_active = 0,
             noComprehension = NA)] %>% unique()

# tidy up
rm(list = c("noPunish10"))
```

```{r richPoorGMTV}
 # create rich indicator (just as highgdp in original data)
median <- GMTV[round == 10,
                   median(stock)]

richGroups <- GMTV[round == 10 & stock > median,
                       unique(groupID)]

poorGroups <- GMTV[round == 10 & stock < median,
                       unique(groupID)]

GMTV[groupID %in% richGroups,
         rich := TRUE]

GMTV[groupID %in% poorGroups,
         rich := FALSE]

# tidy up
rm(list = c("median", "richGroups", "poorGroups", "fileName"))
```

```{r saveGMTV}
fileName <- "GMTV2017"
# save data
save(GMTV, file = paste0("../../data/processed/rda/", fileName, ".rda"))
write.csv(GMTV, file = paste0("../../data/processed/rda/", fileName, ".csv"))
```

```{r calcSwitchingPoint}
# GMTV gathered some risk data that I'll process in a separate DT and merge it
# with other covariates later on

GMTVRisk <- CT[exp_num == 5 | exp_num == 8 | exp_num == 9,
               .(participant.code = subj_id,
                 e10, e20, e30, e40, e50, e60, e70,
                 inconsistent = ifelse(test = e60 < e70 | e50 < e60 | e40 < e50 | e30 < e40 | e20 < e30 | e10 < e20,
                                       yes  = TRUE,
                                       no   = FALSE)
                 )]

GMTVRisk[,
         switching_row := ifelse(test = inconsistent == TRUE,
                                yes  = NA,
                                no   = e10 + e20 + e30 + e40 + e50 + e60 + e70 + 1 + 2) # because GMTV used a 7-point-likert scale
         ]
```

```{r subsetCovariates}
# subset covariate data and rename+refactor some variables
temp <- CT[exp_num == 5 | exp_num == 8 | exp_num == 9,
                         .(treatment = "noPunish10",
                           session.code = exp_num,
                           groupID = gr_id,
                           participant.code = subj_id,
                           gender,
                           age = Sys.Date() %>% lubridate::year() - age,
                           pq01 = q1,
                           pq02 = q2,
                           pq03 = q3,
                           pq04 = q4,
                           pq05 = q5,
                           pq06 = q6,
                           pq07 = q7,
                           pq08 = q8,
                           pq09 = q9,
                           pq10 = q10,
                           pq11 = q11,
                           pq12 = q12,
                           pq13 = q13,
                           pq14 = q14,
                           donation = don
                           )]

temp[donation %>% is.na, donation := 0]

```

```{r mergeAndWrite}

GMTVCovariates <- data.table::merge.data.table(x = temp,
                                               y = GMTVRisk[, .(participant.code, inconsistent, switching_row)],
                                               by = c("participant.code"))

# write data
save(GMTVCovariates, 
     file = paste0("../../data/processed/rda/", fileName, "_COVS", ".rda"))
write.csv(GMTVCovariates, 
          file = paste0("../../data/processed/csv/", fileName, "_COVS", ".csv"))

# tidy up
rm(list = c("temp", "GMTVRisk"))
```

```{r firstRound}
noPunish <- DT[exp_num == 1 | exp_num == 3 | # noPunish15
                 exp_num == 5 | exp_num == 8 | exp_num == 9] # noPunish10

temp <- noPunish[per == 1]
temp <- temp[,
             treatment := "noPunish10"]
temp <- temp[exp_num == 1 | exp_num == 3,
             treatment := "noPunish15"]

GMTVFirstRound <- temp[,
                           .(participant.code = subj_id,
                             treatment,
                             session.code = exp_num,
                             groupID = gr_id,
                             othersContribution = sumputin - putin,
                             ownContribution = putin,
                             trust = NA,
                             comprehension = NA)]

# save data
save(GMTVFirstRound, 
     file = paste0("../../data/processed/rda/", fileName, "_R1", ".rda"))
write.csv(GMTVFirstRound, 
          file = paste0("../../data/processed/csv/", fileName, "_R1", ".csv"))

rm(list = c("temp", "fileName"))
```

<!-- MERGE & TUNE DATA -->

```{r rbindOursAndGMTV, eval = TRUE}
main <- rbindlist(list(replication, GMTV), 
                  use.names = TRUE)

R1   <- rbindlist(list(replicationFirstRound, GMTVFirstRound), 
                  use.names = TRUE)

covs <- rbindlist(list(replicationCovariates, GMTVCovariates), 
                  use.names = TRUE,
                  fill = TRUE)

rm(list = c("CT", "DT", "GMTV", "GMTVCovariates", "GMTVFirstRound", 
            "invitedStudents", "noPunish", "replication", "replicationCovariates",
            "replicationFirstRound", "subset"))
```

```{r studentSample}

# Two of these sessions were special: The first (`r meta[1, session.code]`) as well as the last one (`r meta[, session.code %>% tail(n=1)]`). The first session suffered technical problems such that the risk elicitation task was omitted. The last session (almost exclusively) relied on a student sample as our non-student sample was exhausted after the first three sessions. As a consequence, the last session was conducted with 59 students while all others were conducted without any students. I'll therefore create a boolean `student` variable. Becaue all of the original experiments were conducted with students, `student` also equals 1 in the "noPunish10" treatments

main[, student := FALSE]
main[session.code == "d6jrsxnr" | treatment == "noPunish10",
     student := TRUE]

R1[, student := FALSE]
R1[session.code == "d6jrsxnr" | treatment == "noPunish10",
   student := TRUE]
```

<!-- PAPER STARTS HERE -->

<!-- 
# Key Takeaways

- We **[replicate](#gmtv-replication)** a public goods experiment with dynamic inter-dependencies and find similar results as @GMTV2017. 
    + Absolute contributions increase over time.
    + Just as in _static_ public goods experiments, the share of endowments contributed decreases over time.
    + The richest groups earn fifteen times more than the poorest groups.
    + While there clearly is growth, groups do not realize the maximal potential efficiency and earn just over `r main[treatment == "replication" & round == 10, mean(stock)/(80*1.5^10)*100] %>% round(digits=1)`% of what is possible.
- Varying the subject pool and including a voluntary climate action (VCA), we have a setup similar to @GKLS2020, which allows us to assess **[generalizability](#generalizability)**.^[Note that one can easily model the VCA as a dictator game, which relates to a literature summarized by @cartwright2022.]
- Studying a general population sample online, synchronously and over the course of multiple periods, we find that classic **[lab procedures](online-methodology)** can be applied outside of the lab too.
    + Even though we conducted the experiment online and remotely, dropouts (or "attrition") are no concern.
    + Relying on an inexperienced non-convenience sample that cannot interact with experimenters, `r trunc((R1[comprehension > 1] %>% NROW() / R1[!(is.na(comprehension))] %>% NROW())*100)`% of all participants stated that they understood the game.
    + Participants make relatively fast decisions which makes longer games feasible in the future.^[Taken together with inefficient growth and the lack of dropouts, additional rounds are fairly cheap.]

-->

***

**Hintergrund:** Ich habe diesen [post](https://groups.google.com/g/esa-announce/c/-_2OmbkdxEk) gesehen und überlege meine Replikation entsprechend [hier](https://www.sciencedirect.com/journal/journal-of-behavioral-and-experimental-economics/about/call-for-papers#transparency-reproducibility-and-generalizability-of-behavioral-economics-experiments) einzureichen. Ist das realistisch? Wenn ja, wie soll man die Story aufziehen? Soll man denen mal schreiben und fragen, ob noch Platz ist?

***

> "There are two possible articles you can write: (a) the article you planned to write when you designed your study or (b) the article that makes the most sense now that you have seen the results. They are rarely the same, and the correct answer is (b)." [@bem2021writing, p. 171]

# Introduction

Macroeconomists understand the world as dynamic where the timing matters: Today's savings decision affect lifetime consumption which is why it makes a difference whether you consume more today or tomorrow. Yet, experimental economists often design static games without dynamic inter-dependencies: participants face the same decisions multiple times and previous decisions do not affect current incentives of endowments.

To measure how cooperation affects growth and inequality, @GMTV2017 (to whom I often refer as GMTV in what follows) extended a standard public goods game with temporal inter-dependencies.^[As well as the option to punish group members.] Their results show that participants behave strikingly similar as in the static games (contributions are non-zero; the share of current endowments contributed declines over time; and the initial contribution is around half of their endowments) and illustrate how this affects growth and inequality.

Because environmental and climate action (or the absence of it) is characterized by pro-social behavior and inter-temporal dynamics (the more we hesitate to cut CO2 emissions, the more expensive it will be to reach a certain target in the future), we are interested in applying this setting in a behavioral and environmental economics context with a general population sample.

Due to COVID-19 and corresponding restrictions at that time, we decided to [replicate](#gmtv-replication) GMTV's no punishment 10 period game to evaluate, whether it is feasible to run a multi-period, synchronous group experiment with such a sample first.

As we were not able to recruit the expected number of subjects in the general population sample, we added student participants. Because of this and because the experiment also contains voluntary climate action (VCA), we have a setup similar to @GKLS2020, which allows us to assess [generalizability](#generalizability).

Hence, our paper makes three contributions: First, we run a pre-registered^[The replication project is registered in the AEA RCT Registry and the unique identifying number is: [AEARCTR-0007902](https://doi.org/10.1257/rct.7902-2.0) [@preregistration].] replication of one of GMTV's treatment arms and arrive at similar conclusions: Absolute contributions increase over time. Just as in _static_ public goods experiments, the share of endowments contributed decreases over time. The richest groups earn fifteen times more than the poorest groups. While there clearly is growth, groups do not realize the maximal potential efficiency and earn just over `r main[treatment == "replication" & round == 10, mean(stock)/(80*1.5^10)*100] %>% round(digits=1)`% of what is possible.

Second, like @AGM2018, we study a general population sample online, synchronously and over the course of multiple periods and we find that classic [lab procedures](online-methodology) can be applied outside of the lab too. Relying on an inexperienced sample that cannot interact with experimenters, `r trunc((R1[comprehension > 1] %>% NROW() / R1[!(is.na(comprehension))] %>% NROW())*100)`% of all participants stated that they understood the game. Participants make relatively fast decisions which makes longer games feasible in the future.^[Taken together with inefficient growth and the lack of dropouts, additional rounds are fairly cheap.] In addition, dropouts (or "attrition") are no concern.

Third, we extend the literature on generalizability and find that:

The paper is organized along these lines: Chapter x ...

# Experimental Design and Procedures

This experiment replicated Gächter et al.'s NOPUNISH 10-round treatment arm as close as possible (given the remote circumstances). A demonstration of the experiment can be found [here](https://cliccs.herokuapp.com/).^[Click [here](https://github.com/Howquez/coopUncertainty) to visit the corresponding Github repository.]

All participants were recruited in by the University of Hamburg's  WISO Research Lab using HROOT [@hroot].

# Pre-registered GMTV Replication

## First Round

```{r prepFirstSummary}
replication <- R1[treatment == "replication", ownContribution]
GMTV    <- R1[treatment == "noPunish10", ownContribution]

rows <- sapply(X = list(replication, GMTV), FUN = NROW) %>% max()
temp <- data.frame(replication = c(replication, rep(NA, rows - NROW(replication))),
                   GMTV = c(GMTV, rep(NA, rows - NROW(GMTV))))

rs1 <- wilcox.test(replication, 
                   GMTV,
                   exact = FALSE)$p.value %>% 
  round(digits = 4) %>% 
  formatC(format = "f", 
          digits = 4)
```

First, we ask whether the samples differ with respect to their initial contributions to the public good. Is our replication sample more pro-social than the original sample? As Figure 1 reveals, they are not. The distributions look fairly similar and both samples contributed 10 tokens, that is, 50% of their endowments on average (median and mean).^[The two-sided rank sum test (comparing differences between data sources) yields a p-Value of `r rs1` for the mean contribution in first round of the game.] As such, the individuals' behavior in both samples is not only comparable to each other but also to initial contributions in the standard game with partner matching.^[See Figure 3B in @fehrgaechter2000, for instance.] Because participants played a dynamic game, we are particularly interested in the subsequent periods. Do the two groups remain similar?

```{r firstRoundViz}
ggplot(data = R1[treatment != "noPunish15"],
       mapping = aes(x = ownContribution, fill = treatment)) +
  geom_density(alpha = 0.5) +
  scale_x_continuous(limits = c(0, 20),
                       expand = c(0, NA)) +
  scale_y_continuous(limits = c(0, 0.1),
                       expand = c(0, NA)) +
  scale_fill_manual(values = c(cPrimary, cSecondary),
                    labels = c("Original Sample", "Replication Sample")) +
  labs(title = "Individual contributions to the dynamic public good in the first period", 
       y = "", x = "Contributrions (Tokens)") +
  layout +
  theme(legend.position = "bottom")
```

```{r firstRoundSummary, results = "asis", warning = FALSE, fig.cap = "test", eval = FALSE}

if(knitr::is_html_output()){
  type <- "html"
} else {
  type = "latex"
}

stargazer(temp,
          summary.stat = c("mean", "median","sd", "max", "min", "n"),
          type = type, 
          flip = TRUE, 
          header=FALSE)
```

## Provision of the public good

We proceed by further discussing contributions over time on a group level. The left panel in Figure 1 shows the average amount of tokens groups contributed over time. Contributions are clearly non-zero and are increasing over the course of the first eight periods. While contributions flatten in the replication, the GMTV data exhibit a notable drop in the last round.

```{r plotContributions}

SUM <- main[,
            lapply(.SD, mean, na.rm = TRUE),
            by = c("round", "treatment"),
            .SDcols = "contribution"]

SUM[,
    sum := round(contribution)]

upperLimit <- SUM$contribution %>% max() %>% round() + 10

p1 <- ggplot(data = SUM, 
             aes(x = round, y = contribution, fill = treatment, color = treatment, lty = treatment)) +
  layout +
  theme(legend.position="bottom") +
  geom_line(show.legend=FALSE) +
  geom_point() +
  scale_x_continuous(name="",  breaks = 1:15) +
  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
  labs(y = "Average Amount of Tokens contributed") +
  scale_color_manual(values = c(cPrimary, cSecondary)) + 
  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))

rm(list = c("SUM"))
```

```{r plotShareOfContributions, fig.cap = "The average amount of tokens contributed over time in treatments."}

SHARE <- main[,
            lapply(.SD, mean, na.rm = TRUE),
            by = c("round", "treatment"),
            .SDcols = "share"]

# SHARE <- main[,
#             .(share = sum(contribution)/sum(endowment)),
#             by = c("round", "treatment")]

upperLimit <- 0.75

p2 <- ggplot(data = SHARE, 
             aes(x = round, y = share, fill = treatment, color = treatment, lty = treatment)) +
  layout +
  theme(legend.position="bottom") +
  geom_line(show.legend=FALSE) +
  geom_point() +
  scale_x_continuous(name="",  breaks = 1:15) +
  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
  labs(y = "Share of Current Endowment contributed") +
  scale_color_manual(values = c(cPrimary, cSecondary))

p1 + p2 + plot_layout(guides = "collect") & theme(legend.position = "bottom")

rm(list = c("p1", "p2"))
```

Note that increasing contributions over time imply that groups have increasing endowments over time. Hence, increasing contributions do not necessarily imply that groups contribute increasing shares of their endowments. The right panel in Figure 1 shows the share of overall endowments contributed over time. In the original data, groups contribute around `r SHARE[round == 1 & treatment == "noPunish10", round(share*100)]`% of their endowment in round 1. This amount steadily decreases to `r SHARE[round == 10 & treatment == "noPunish10", round(share*100)]`%. The replication data exhibit a similar pattern with shares ranging from `r SHARE[round == 1 & treatment == "replication", round(share*100)]`% to `r SHARE[round == 10 & treatment == "replication", round(share*100)]`%. `r rm("SHARE")`

Taken together, our replication partly mirrors the results of GMTV. Absolute contributions tended to be higher in @GMTV2017 but end up at around the same level as in the replication due to a stark decline in contributions in the last round. In terms of shares contributed both data sources exhibit a similar pattern: they decline and do not stabilize. Even though the share of current endowments contributed in the last round is quite similar, the share declined a little faster in our data, however.

## Wealth Creation

Possibly of more interest are the implications contributions have for wealth generation and growth. To measure growth, we define a variable called _stock_ which sums the endowments of all participants in a given group at the end of the round (that is, after the contributions have been made, multiplied and redistributed). @GMTV2017 refer to that variable as "wealth" so we will do the same in what follows. Before the start of round 1, wealth will be 80 in all groups by construction. The maximal wealth that can be reached in round 10 (if each group member contributes their entire endowment in each round) is approximately `r (80*1.5^10) %>% trunc()` tokens or `r (80*1.5^10 /20) %>% trunc()` Euro per group.

Table 3 shows some summary statistics regarding wealth at the end of the last period.  While there is clearly growth, groups do not realize the maximal potential efficiency as the replication groups reach on average a level of `r main[treatment == "replication" & round == 10, mean(stock)] %>% trunc()` tokens out of `r (80*1.5^10) %>% trunc()` maximally possible or `r main[treatment == "replication" & round == 10, mean(stock)/(80*1.5^10)*100] %>% round(digits=1)`%. As in the original data, there is large heterogeneity with the richest group reaching `r main[treatment == "replication" & round == 10, max(stock)]` tokens whereas the poorest group ends up with `r main[treatment == "replication" & round == 10, min(stock)]` tokens.

```{r summary1, results = "asis", warning = FALSE, fig.cap = "test"}

if(knitr::is_html_output()){
  type <- "html"
} else {
  type = "latex"
}

replication <- main[treatment == "replication" & round == 10, stock]
GMTV    <- main[treatment == "noPunish10" & round == 10, stock]

rows <- sapply(X = list(replication, GMTV), FUN = NROW) %>% max()
temp <- data.frame(replication = c(replication, rep(NA, rows - NROW(replication))),
                   GMTV = c(GMTV, rep(NA, rows - NROW(GMTV))))

stargazer(temp,
          summary.stat = c("mean", "median","sd", "max", "min", "n"),
          type = type, 
          flip = TRUE, 
          header=FALSE)

rs1 <- wilcox.test(replication, 
                   GMTV,
                   exact = FALSE)$p.value %>% 
  round(digits = 4) %>% 
  formatC(format = "f", 
          digits = 4)

```

We thus, observe growth even for the poorest group and spot heterogeneity even within data sources.

Figure 2 shows the dynamics of wealth over time. The left panel focuses on all groups, the upper right panel on those with above median wealth after round 10 (“successful” groups) and the lower left panel on those with below median wealth after round 10 (“unsuccessful” groups).

```{r plotStock, fig.cap = "Average wealth over time across treatments."}
STOCK <- main[,
              lapply(.SD, mean, na.rm = TRUE),
              by = c("round", "treatment"),
              .SDcols = "stock"]

STOCKr <- main[rich == TRUE,
               lapply(.SD, mean, na.rm = TRUE),
               by = c("round", "treatment"),
               .SDcols = "stock"]

STOCKp <- main[rich == FALSE,
               lapply(.SD, mean, na.rm = TRUE),
               by = c("round", "treatment"),
               .SDcols = "stock"]

upperLimit <- STOCKr$stock %>% max() %>% round() + 20

p1 <- ggplot(data = STOCK, 
       aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
          layout +
          theme(legend.position="bottom") +
          # geom_vline(xintercept = 10, alpha = 0.66) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          # annotate("segment", x = 1, xend = 10, 
          #          y = STOCK[round == 1 & treatment == "replication", stock],
          #          yend = STOCK[round == 10 & treatment == "replication", stock],
          #          colour = "black", lty = 2, alpha = 0.5) +
          # annotate("segment", x = 1, xend = 10, 
          #          y = STOCK[round == 1 & treatment == "noPunish10", stock],
          #          yend = STOCK[round == 10 & treatment == "noPunish10", stock],
          #          colour = "black", lty = 2, alpha = 0.5) +
          scale_x_continuous(name="",  breaks = 1:10) +
          scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
          labs(y = "Wealth") +
          scale_color_manual(values = colors) + 
          theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))

p2 <- ggplot(data = STOCKr, 
       aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
          layout +
          theme(legend.position="bottom") +
          # geom_vline(xintercept = 10, alpha = 0.66) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="",  breaks = 1:10) +
          scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
          labs(y = "Wealth (Rich)") +
          scale_color_manual(values = colors)

p3 <- ggplot(data = STOCKp, 
       aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
          layout +
          theme(legend.position="bottom") +
          # geom_vline(xintercept = 10, alpha = 0.66) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="",  breaks = 1:10) +
          scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
          labs(y = "Wealth (Poor)") +
          scale_color_manual(values = colors)

(p1 | (p2 / p3)) + plot_layout(guides = "collect") & theme(legend.position = "bottom")

rm(list = c("STOCK", "STOCKr", "STOCKp", "p1", "p2", "p3"))
```

The Figure illustrates that (in both data sources) growth was continuous and surprisingly linear, given the exponential character of the game's design.

To sum up, our groups also tend to be poorer, and median wealth is higher in GMTV. The difference in mean ranks is not significant according to a two-sided ranksum test^[The two-sided rank sum test (comparing differences between data sources) yields a p-Value of `r rs1` for the mean wealth after the last round of the game.], however.

To further assess the statistical significance of differences in means, we run OLS regressions where we regress wealth on a treatment dummy for _Replication_ (Table 3). These regressions show that differences in means are only significant for below median groups. This implies that the poor groups in our data are even less wealthy than GMTV's poor groups.

```{r tableStock, results = "asis", warning = FALSE}

# create subsets
main_all  <- main[round == 10]
main_poor <- main[round == 10 & rich == FALSE]
main_rich <- main[round == 10 & rich == TRUE]

# create table
if(knitr::is_html_output()){
  type <- "html"
} else {
  type = "latex"
}

m1 <- lm(formula = stock ~ treatment, data = main_all)
m2 <- lm(formula = stock ~ treatment, data = main_poor)
m3 <- lm(formula = stock ~ treatment, data = main_rich)

stargazer(m1, m2, m3,

          column.labels = c("All", "Below median", "Above median"),
          model.numbers = FALSE,
          dep.var.labels = "Wealth",
          header = FALSE,
          covariate.labels = c("Replication"),

          type = type, digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
          )
```

As such, our results look familiar to GMTV's findings, where poor groups grew ever so slightly, while only rich groups experienced growth (that became exponential only after the 10th round).

## Inequality

In this subsection, we focus on the degree of inequality created endogenously in our setting. The smallest possible value the Gini coefficient takes is zero (if all four group members own one fourth of the wealth) and the largest possible value it takes is one (if one group member holds the entire wealth). Table 4 shows some summary statistics regarding the Gini coefficient.

The round 10 Gini coefficient ranges between `r main[treatment == "replication" & round == 10, gini %>% min()] %>% round(digits = 3)` and `r main[treatment == "replication" & round == 10, gini %>% max()] %>% round(digits = 3)` in our data with a median of `r main[treatment == "replication" & round == 10, gini %>% median()] %>% round(digits = 3)`.

```{r summary2, results = "asis", warning = FALSE}

if(knitr::is_html_output()){
  type <- "html"
} else {
  type = "latex"
}

replication <- main[treatment == "replication" & round == 10, gini]
GMTV    <- main[treatment == "noPunish10" & round == 10, gini]

rows <- sapply(X = list(replication, GMTV), FUN = NROW) %>% max()
temp <- data.frame(replication = c(replication, rep(NA, rows - NROW(replication))),
                   GMTV = c(GMTV, rep(NA, rows - NROW(GMTV))))

stargazer(temp,
          summary.stat = c("mean", "median","sd", "max", "min", "n"),
          type = type, 
          flip = TRUE, 
          header=FALSE)

rs2 <- wilcox.test(replication, 
                   GMTV,
                   exact = FALSE)$p.value %>% 
  round(digits = 4) %>% 
  formatC(format = "f", 
          digits = 4)

```

The two-sided rank sum test yields a p-Value of `r rs2` for the mean ```gini``` during the last round of the game.

Figure 3 illustrates the dynamics of the Gini coefficient (at the end of each round) over time and shows that inequality increases slightly.

```{r plotInequality, fig.cap = "Average Gini coefficient over time across treatments."}
GINI <- main[,
             lapply(.SD, mean, na.rm = TRUE),
             by = c("round", "treatment"),
             .SDcols = "gini"]

GINIr <- main[rich == TRUE,
              lapply(.SD, mean, na.rm = TRUE),
              by = c("round", "treatment"),
              .SDcols = "gini"]

GINIp <- main[rich == FALSE,
              lapply(.SD, mean, na.rm = TRUE),
              by = c("round", "treatment"),
              .SDcols = "gini"]

upperLimit <- GINI$gini %>% max() %>% round(digits = 1) + 0.15

p1 <- ggplot(data = GINI, 
       aes(x = round, y = gini, fill = treatment, color = treatment, lty = treatment)) +
          layout +
          theme(legend.position="bottom") +
          # geom_vline(xintercept = 10, alpha = 0.66) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="",  breaks = 1:10) +
          scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
          labs(y = "Gini Coefficient") +
          scale_color_manual(values = colors) + 
          theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))

p2 <- ggplot(data = GINIr, 
       aes(x = round, y = gini, fill = treatment, color = treatment, lty = treatment)) +
          layout +
          theme(legend.position="bottom") +
          # geom_vline(xintercept = 10, alpha = 0.66) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="",  breaks = 1:10) +
          scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
          labs(y = "Gini (Rich)") +
          scale_color_manual(values = colors)

p3 <- ggplot(data = GINIp, 
       aes(x = round, y = gini, fill = treatment, color = treatment, lty = treatment)) +
          layout +
          theme(legend.position="bottom") +
          # geom_vline(xintercept = 10, alpha = 0.66) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="",  breaks = 1:10) +
          scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
          labs(y = "Gini (Poor)") +
          scale_color_manual(values = colors)

(p1 | (p2 / p3)) + plot_layout(guides = "collect") & theme(legend.position = "bottom")

rm(list = c("GINI", "GINIp", "GINIr", "p1", "p2", "p3"))
```

### Inequality Differences between Data Sources

Once more, we consider whether we were able to replicate GMTV's results with our data.

The following table shows a simple OLS regression to illustrate differences in the 10th round's Gini coefficient between the replication's data and GMTV's data. Mean Gini coefficients are similar across data sources and there are no statistically significant differences in mean Gini coefficients.

```{r tableGINI, results = "asis", warning = FALSE}

# create subsets
main_all  <- main[round == 10]
main_poor <- main[round == 10 & rich == FALSE]
main_rich <- main[round == 10 & rich == TRUE]

# create table
if(knitr::is_html_output()){
  type <- "html"
} else {
  type = "latex"
}

m1 <- lm(formula = gini ~ treatment, data = main_all)
m2 <- lm(formula = gini ~ treatment, data = main_poor)
m3 <- lm(formula = gini ~ treatment, data = main_rich)

stargazer(m1, m2, m3,

          column.labels = c("All", "Below median", "Above median"),
          model.numbers = FALSE,
          dep.var.labels = "Gini",
          header=FALSE,
          covariate.labels = c("Replication"),

          type = type, digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
          )
```

# Online Methodology

## Time Spent

Participants spent approximately `r duration[, completion_time %>% unique() %>% mean()] %/% 60 + 1` minutes completing the experiment. Reading the instructions and answering the comprehension questions took the most time, that is, `r duration[page_name == "Intro_Instructions", time_spent %>% unique() %>% mean()] %/% 60 + 1` minutes. The public goods game required `r duration[app_name == "dPGG", time_spent %>% sum(), by = c("session_code", "participant_code")][,V1] %>% mean(na.rm = TRUE) %/% 60` minutes of the participants' time.

```{r plotTime, fig.cap = "Average Time Spent for each Contribution per Round."}
N <- duration[, participant_code %>% unique() %>% length()]
plotDT <- duration[app_name == "dPGG" & page_name == "dPGG_Decision",
                   .(time_spent = time_spent %>% sum()),
                   by = c("session_code", "participant_code", "page_index", "page_name")]

plotDT[, round := seq(from = 1, to = 10), by = c("participant_code")]

upperLimit <- plotDT[, time_spent %>% mean(), by = c("round")] %>% max()

ggplot(data = summarySE(data = plotDT,
                        measurevar = "time_spent",
                        groupvars=c("round"),
                        na.rm = FALSE,
                        conf.interval = 0.95,
                        .drop = TRUE),
       mapping = aes(x = round, y = time_spent)) +
  layout +
  theme(legend.position="bottom") +
  geom_line(show.legend=FALSE, color = cSecondary, lty=2) +
  geom_errorbar(aes(ymin=time_spent-ci, ymax=time_spent+ci), width=.25, alpha = 0.5, color = cSecondary) +
  geom_point(color = cSecondary) +
  scale_x_continuous(name="",  breaks = 1:10) +
  scale_y_continuous(limits = c(0, upperLimit + 10), expand = c(0, 0)) +
  labs(y = "Time Passed in Seconds", caption = "Bars indicate 95% confidence intervals.") +
  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
```

Figure 4 illustrates the time participants needed to make each of their contributions during the replication. One can see that the initial as well as most of the other contributions take about 20 seconds of time. Interestingly, the second contribution takes (on average) about 50% more time than the first one - presumably because this is the first time participants' learn their respective group members' actions. The third contribution is a little faster and all subsequent contributions stabilize at `r plotDT[round > 3, time_spent %>% mean()] %>% ceiling()` seconds.

Given that no participant dropped out after answering the comprehension questions correctly and given that participants need less than 20 seconds to make their contributions, more than 10 rounds are feasible.

# Exporatory: Generalizability

The following figure gives a first overview over the distribution of contributions across the two sorts of contributions. The density-plots in the top panel show the fraction of the initial endowment contributed in the first round of the experiment. The two plots in the bottom panel show contribution behavior in the VCA, that is, donations to climate change mitigation. The left panels depict the general population's behavior while the right panelshows the students' behavior. All contributions are relative to the maximum amount a participant could have contributed.

Means are indicated by vertical dashed lines and are positive in both settings across samples.^[While the medians are similar in the bottom panel, that is, the experiment's contributions, they are smaller in the taop panel and zero in the student sample.] Overall contributions in the VCA setting are smaller than in the experiment's first round.

```{r vizGeneralizability}
R1covs <- covs[, .(participant.code,
                   donation = donation * 20 ,
                   donationShare = (donation * 20) / payoff * 100,
                   payoff)]
temp <- R1[R1covs, on = .(participant.code = participant.code)][treatment == "replication"]
temp[, contributionShare := ownContribution/20 * 100]

# viz wrapper
plotShares <- function(stud = FALSE,
                       var  = "donationShare",
                       col  = cPrimary,
                       xlab = "",
                       ylab = ""){

  dt <- temp[student == stud, .(x = get(var))]

  ggplot(data = dt,
         mapping = aes(x = x)) +
    geom_density(alpha = 1,
                 fill = col) +
    scale_x_continuous(limits = c(0, 100),
                       expand = c(0, NA)) +
    scale_y_continuous(limits = c(0, NA),
                       expand = c(0, NA)) +
    geom_vline(xintercept = dt[,mean(x, na.rm = TRUE)],
               lty = 2) +
    labs(x = xlab,
         y = ylab) +
  layout
}

p1 <- plotShares(stud = FALSE, col = cPrimary,   var = "donationShare", ylab = "Density in VCA")
p2 <- plotShares(stud = FALSE, col = cPrimary,   var = "contributionShare", 
                 xlab = "Share of general pop. contributions", ylab = "Density in Experiment (round 1)")
p3 <- plotShares(stud = TRUE,  col = cSecondary, var = "donationShare")
p4 <- plotShares(stud = TRUE,  col = cSecondary, var = "contributionShare", xlab = "Share of students' contributions")

(p1 / p2) | (p3 / p4)

rm(list = c("R1covs", "p1", "p2", "p3", "p4"))
```

lorem ipsum.

```{r}
ggplot(data = temp[, 
                   .(vca = donation / payoff * 100,
                     dpgg = ownContribution / 20 * 100)],
       mapping = aes(y = vca, x = dpgg)) +
  annotate("segment", x = 0, xend = 100,
                   y = 0,
                   yend = 100,
                   colour = "black", lty = 2, alpha = 0.5) +
  geom_point(alpha = 0.33, col = cSecondary, size = 2) +
  scale_x_continuous(limits = c(0, 105),
                     expand = c(0, NA)) +
  scale_y_continuous(limits = c(0, 105),
                     expand = c(0, NA)) +
  labs(y = "VCA: Percentage of endowment donated",
       x = "Experiment: Percentage of endowment contributed in round 1") +
  layout
```
A visual inspection of the scatter plot (where the saturation of the points is proportional to the frequency of a pair of contribution choices) does not hint at an association between the two sorts of contributions.

## To do

- explain similarities and differences to @GKLS2020 setup and how they came to be
- compare samples across tasks
- who generalizes (better)?
- who is more heterogeneous and what does that mean?
- How do the results compare to @GKLS2020

# Conclusion

### 2022-10-08 analysis/quarto/paper.qmd
added "quarto" and "paper" (already deprecated) + no clue what happened otherwise. Its been a long time

--- 2022-10-08 analysis/R/paper.Rmd
@@
 ---
-title: "Growth and inequality in public good provision: an extended replication"
-description: |
-  Report and analysis protocoll.
+title: Growth and inequality in public good provision | an extended replication
 author:
   - name: Hauke Roggenkamp
-    url: https://www.ibt.unisg.ch/team/hauke-roggenkamp/
-    affiliation: Helmut Schmidt University
-    affiliation_url: https://www.hsu-hh.de/en/
-  - affiliation: Institute for Behavioral Science and Technology
-    affiliation_url: https://www.ibt.unisg.ch/
-date: "`r Sys.Date()`"
+    email: hauke.roggenkamp@unisg.ch
+    affiliations:
+        - id: HSU
+          name: Helmut Schmidt University
+          department: Department of Economics
+          address:  Holstenhofweg 85
+          city: Hamburg
+          state: Germany
+          postal-code: 22043
+        - id: HSG
+          name: University of St. Gallen
+          department: Institute for Behavioral Science and Technology
+          address: Torstrasse 25
+          city: St. Gallen
+          state: Switzerland
+          postal-code: 9000
+    # attributes:
+    #     corresponding: true
+    # note: This is the first author footnote.
+abstract: |
+  This is the abstract.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Vestibulum augue turpis, dictum non malesuada a, volutpat eget velit.
+Nam placerat turpis purus, eu tristique ex tincidunt et.
+Mauris sed augue eget turpis ultrices tincidunt.
+Sed et mi in leo porta egestas.
+Aliquam non laoreet velit.
+Nunc quis ex vitae eros aliquet auctor nec ac libero.
+Duis laoreet sapien eu mi luctus, in bibendum leo molestie.
+Sed hendrerit diam diam, ac dapibus nisl volutpat vitae.
+Aliquam bibendum varius libero, eu efficitur justo rutrum at.
+Sed at tempus elit.
+keywords: 
+  - Replication study
+  - Non-convenience sample
+  - Open science
+  - Dynamic public good game
+  - Online experiment
+  - Generalizability
+date: last-modified
 bibliography:  ../biblio.bib
-output:
-  distill::distill_article:
-    toc: true
-    toc_depth: 2
-    toc_float: false
+format:
+  elsevier-pdf:
+    keep-tex: true
+    journal:
+      name: Journal of Behavioral and Experimental Economics
+      formatting: preprint
+      model: 3p
+      cite-style: authoryear
 ---
@@
 
+```{r treatmentAsFactor}
+main[, treatment := as.factor(treatment)]
+R1[, treatment := as.factor(treatment)]
+covs[, treatment := as.factor(treatment)]
+```
+
 ```{r studentSample}
@@
 > "There are two possible articles you can write: (a) the article you planned to write when you designed your study or (b) the article that makes the most sense now that you have seen the results.
-They are rarely the same, and the correct answer is (b)." [@bem2021writing, p.
+They are rarely the same, and the correct answer is (b)." [@bemwriting, p.
 171]
 
-# Introduction
-
-Macroeconomists understand the world as dynamic where the timing matters: Today's savings decision affect lifetime consumption which is why it makes a difference whether you consume more today or tomorrow.
-Yet, experimental economists often design static games without dynamic inter-dependencies: participants face the same decisions multiple times and previous decisions do not affect current incentives of endowments.
-
-To measure how cooperation affects growth and inequality, @GMTV2017 (to whom I often refer as GMTV in what follows) extended a standard public goods game with temporal inter-dependencies.^[As well as the option to punish group members.] Their results show that participants behave strikingly similar as in the static games (contributions are non-zero; the share of current endowments contributed declines over time; and the initial contribution is around half of their endowments) and illustrate how this affects growth and inequality.
-
-Because environmental and climate action (or the absence of it) is characterized by pro-social behavior and inter-temporal dynamics (the more we hesitate to cut CO2 emissions, the more expensive it will be to reach a certain target in the future), we are interested in applying this setting in a behavioral and environmental economics context with a general population sample.
-
-Due to COVID-19 and corresponding restrictions at that time, we decided to [replicate](#gmtv-replication) GMTV's no punishment 10 period game to evaluate, whether it is feasible to run a multi-period, synchronous group experiment with such a sample first.
-
-As we were not able to recruit the expected number of subjects in the general population sample, we added student participants.
-Because of this and because the experiment also contains voluntary climate action (VCA), we have a setup similar to @GKLS2020, which allows us to assess [generalizability](#generalizability).
-
-Hence, our paper makes three contributions: First, we run a pre-registered^[The replication project is registered in the AEA RCT Registry and the unique identifying number is: [AEARCTR-0007902](https://doi.org/10.1257/rct.7902-2.0) [@preregistration].] replication of one of GMTV's treatment arms and arrive at similar conclusions: Absolute contributions increase over time.
-Just as in _static_ public goods experiments, the share of endowments contributed decreases over time.
-The richest groups earn fifteen times more than the poorest groups.
-While there clearly is growth, groups do not realize the maximal potential efficiency and earn just over `r main[treatment == "replication" & round == 10, mean(stock)/(80*1.5^10)*100] %>% round(digits=1)`% of what is possible.
-
-Second, like @AGM2018, we study a general population sample online, synchronously and over the course of multiple periods and we find that classic [lab procedures](online-methodology) can be applied outside of the lab too.
-Relying on an inexperienced sample that cannot interact with experimenters, `r trunc((R1[comprehension > 1] %>% NROW() / R1[!(is.na(comprehension))] %>% NROW())*100)`% of all participants stated that they understood the game.
-Participants make relatively fast decisions which makes longer games feasible in the future.^[Taken together with inefficient growth and the lack of dropouts, additional rounds are fairly cheap.] In addition, dropouts (or "attrition") are no concern.
-
-Third, we extend the literature on generalizability and find that:
-
-The paper is organized along these lines: Chapter x ...
-
-# Experimental Design and Procedures
-
-This experiment replicated Gächter et al.'s NOPUNISH 10-round treatment arm as close as possible (given the remote circumstances).
-A demonstration of the experiment can be found [here](https://cliccs.herokuapp.com/).^[Click [here](https://github.com/Howquez/coopUncertainty) to visit the corresponding Github repository.]
-
-All participants were recruited in by the University of Hamburg's  WISO Research Lab using HROOT [@hroot].
-
 # Pre-registered GMTV Replication
 
-## First Round
+## Provision of the public good
 
@@
 Is our replication sample more pro-social than the original sample?
-As Figure 1 reveals, they are not.
-The distributions look fairly similar and both samples contributed 10 tokens, that is, 50% of their endowments on average (median and mean).^[The two-sided rank sum test (comparing differences between data sources) yields a p-Value of `r rs1` for the mean contribution in first round of the game.] As such, the individuals' behavior in both samples is not only comparable to each other but also to initial contributions in the standard game with partner matching.^[See Figure 3B in @fehrgaechter2000, for instance.] Because participants played a dynamic game, we are particularly interested in the subsequent periods.
+Figure 1 reveals, that it is not.
+The distributions of both samples look fairly similar.
+Both samples contributed 10 tokens, that is, 50% of their endowments on average (median and mean).^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean contribution in first round of the game.] Moreover, both samples' initial contributions resemble initial contributions participants usually make in the standard game with partner matching.^[See Figure 3B in @fehrgaechter2000 (p.989), for instance.] In the dynamic game presented here, we are particularly interested in the subsequent periods because differences add up exponentially.
 Do the two groups remain similar?
@@
 ggplot(data = R1[treatment != "noPunish15"],
-       mapping = aes(x = ownContribution, fill = treatment)) +
+       mapping = aes(x = ownContribution, fill = treatment, lty = treatment)) +
   geom_density(alpha = 0.5) +
@@
                     labels = c("Original Sample", "Replication Sample")) +
+  guides(lty = "none") +
+  geom_vline(xintercept = R1[treatment == "replication", 
+                             mean(ownContribution)],
+             col = "#FFFFFF",
+             lty = 2) +
+  geom_vline(xintercept = R1[treatment == "noPunish10", 
+                             mean(ownContribution)],
+             col = "#FFFFFF",
+             lty = 1) +
     labs(title = "Individual contributions to the dynamic public good in the first period", 
-       y = "", x = "Contributrions (Tokens)") +
+       y = "", x = "Contributrions (Tokens)",
+       caption = "White lines indicate means (dashed line = replication sample).") +
   layout +
@@
 
-```{r firstRoundSummary, results = "asis", warning = FALSE, fig.cap = "test", eval = FALSE}
+```{r firstRoundSummary}
+#| results: asis
+#| warning: false
+#| fig.cap: "test"
+#| eval: false
 
@@
 
-## Provision of the public good
-
-We proceed by further discussing contributions over time on a group level.
-The left panel in Figure 1 shows the average amount of tokens groups contributed over time.
-Contributions are clearly non-zero and are increasing over the course of the first eight periods.
-While contributions flatten in the replication, the GMTV data exhibit a notable drop in the last round.
+In particular, do the two samples' contributions follow the same pattern over time?
+The answer is _no_.
+Figure 2 illustrates that the samples make similar contributions at the beginning and the end of the game but behave differently in between.
+More precisely, the left panel--depicting the average contributions in absolute terms--shows that the original sample contributed substantially more than the replication sample _in all but the first and last rounds_.
+For this reason, the original sample's behavior differs from the replication sample's behavior in two aspects: it contributes more and exhibits a considerable drop in the last period (whereas the replication sample's contributions flatten).
+Note that increasing contributions over time imply increasing endowments over time.
+Hence, increasing absolute contributions do not necessarily imply that participants contribute increasing shares of their endowments.
+The right panel in Figure 1 shows the share of overall endowments contributed over time where both samples exhibit a similar pattern: they decline and do not stabilize.
+The original sample's behavior differs from the replication sample's behavior in one aspect: it declined slower (to the same level in the last period).
 
@@
 
-upperLimit <- SUM$contribution %>% max() %>% round() + 10
+SUM[,
+    contribution := contribution/4]
+
+upperLimit <- SUM$contribution %>% max() %>% round() + 5
 
@@
   labs(y = "Average Amount of Tokens contributed") +
-  scale_color_manual(values = c(cPrimary, cSecondary)) + 
+  scale_color_manual(values = c(cPrimary, cSecondary),
+                     labels = c("Original Sample", "Replication Sample")) + 
+  guides(fill = "none") +
   theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
@@
 
-```{r plotShareOfContributions, fig.cap = "The average amount of tokens contributed over time in treatments."}
+```{r plotShareOfContributions}
+#| fig.cap: "The average amount of tokens contributed over time in treatments."
 
@@
   labs(y = "Share of Current Endowment contributed") +
-  scale_color_manual(values = c(cPrimary, cSecondary))
-
-p1 + p2 + plot_layout(guides = "collect") & theme(legend.position = "bottom")
-
-rm(list = c("p1", "p2"))
-```
-
-Note that increasing contributions over time imply that groups have increasing endowments over time.
-Hence, increasing contributions do not necessarily imply that groups contribute increasing shares of their endowments.
-The right panel in Figure 1 shows the share of overall endowments contributed over time.
-In the original data, groups contribute around `r SHARE[round == 1 & treatment == "noPunish10", round(share*100)]`% of their endowment in round 1.
-This amount steadily decreases to `r SHARE[round == 10 & treatment == "noPunish10", round(share*100)]`%.
-The replication data exhibit a similar pattern with shares ranging from `r SHARE[round == 1 & treatment == "replication", round(share*100)]`% to `r SHARE[round == 10 & treatment == "replication", round(share*100)]`%.
-`r rm("SHARE")`
-
-Taken together, our replication partly mirrors the results of GMTV.
-Absolute contributions tended to be higher in @GMTV2017 but end up at around the same level as in the replication due to a stark decline in contributions in the last round.
-In terms of shares contributed both data sources exhibit a similar pattern: they decline and do not stabilize.
-Even though the share of current endowments contributed in the last round is quite similar, the share declined a little faster in our data, however.
+  scale_color_manual(values = c(cPrimary, cSecondary),
+                     labels = c("Original Sample", "Replication Sample")) +
+  guides(fill = "none")
+
+p1 + p2 + plot_layout(guides = "collect") & 
+  theme(legend.position = "bottom")
+
+# rm(list = c("p1", "p2"))
+```
+
+Moreover, both samples' contributions resemble contributions participants usually make in the standard game with partner matching.^[The right panel is thus, comparable to the visualizations _and results_ in the standard game.
+See, for instance, Figure 1B in @fehrgaechter2000 (p.986).] In the dynamic game presented here, different paths lead to different levels of wealth -- even if they share the same start- and end-points.
+We are thus, more interested in the implications contributions have for wealth generation and growth.
+So, how do the samples compare with respect to wealth/income/endowments/stock?
 
@@
 
-Possibly of more interest are the implications contributions have for wealth generation and growth.
-To measure growth, we define a variable called _stock_ which sums the endowments of all participants in a given group at the end of the round (that is, after the contributions have been made, multiplied and redistributed).
-@GMTV2017 refer to that variable as "wealth" so we will do the same in what follows.
-Before the start of round 1, wealth will be 80 in all groups by construction.
-The maximal wealth that can be reached in round 10 (if each group member contributes their entire endowment in each round) is approximately `r (80*1.5^10) %>% trunc()` tokens or `r (80*1.5^10 /20) %>% trunc()` Euro per group.
-
-Table 3 shows some summary statistics regarding wealth at the end of the last period.
-While there is clearly growth, groups do not realize the maximal potential efficiency as the replication groups reach on average a level of `r main[treatment == "replication" & round == 10, mean(stock)] %>% trunc()` tokens out of `r (80*1.5^10) %>% trunc()` maximally possible or `r main[treatment == "replication" & round == 10, mean(stock)/(80*1.5^10)*100] %>% round(digits=1)`%.
-As in the original data, there is large heterogeneity with the richest group reaching `r main[treatment == "replication" & round == 10, max(stock)]` tokens whereas the poorest group ends up with `r main[treatment == "replication" & round == 10, min(stock)]` tokens.
-
-```{r summary1, results = "asis", warning = FALSE, fig.cap = "test"}
+```{r summary1}
+#| results: asis
+#| warning: false
+#| fig.cap: "test"
 
@@
 
-stargazer(temp,
-          summary.stat = c("mean", "median","sd", "max", "min", "n"),
-          type = type, 
-          flip = TRUE, 
-          header=FALSE)
+# stargazer(temp,
+#           summary.stat = c("mean", "median","sd", "max", "min", "n"),
+#           type = type, 
+#           flip = TRUE, 
+#           header=FALSE)
 
@@
 
+How do the different contribution-paths translate to wealth?^[To measure growth, we define a variable called _stock_ which sums the endowments of all participants in a given group at the end of the round (that is, after the contributions have been made, multiplied and redistributed).] Given that the original sample contributed more in most of the periods, one would expect the respective groups to be considerably more wealthy.
+Figure 3 indicates that they tend to be insignificantly^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean stock in last round of the game.] richer.
+
+```{r stockDistributionViz}
+originalWealth    <- main[treatment == "noPunish10" & round == 10, mean(stock)]
+replicationWealth <- main[treatment == "replication" & round == 10, mean(stock)]
+
+ggplot(data = main,
+       mapping = aes(x = stock, fill = treatment, lty = treatment)) +
+  geom_density(alpha = 0.5) +
+  scale_x_continuous(limits = c(0, NA),
+                       expand = c(0, NA)) +
+  scale_y_continuous(limits = c(0, NA),
+                       expand = c(0, NA)) +
+  scale_fill_manual(values = c(cPrimary, cSecondary),
+                    labels = c("Original Sample", "Replication Sample")) +
+  guides(lty = "none") +
+  geom_vline(xintercept = replicationWealth,
+             col = "#000000", alpha = 0.5,
+             lty = 2) +
+  geom_vline(xintercept = originalWealth,
+             col = "#000000", alpha = 0.5,
+             lty = 1) +
+    labs(title = "Groups' income at the end of the game", 
+       y = "", x = "Stock",
+       caption = "Grey lines indicate means (dashed line = replication sample).") +
+  layout +
+  theme(legend.position = "bottom")
+```
+
+As the grey lines indicate, an average group in the original sample accumulated about `r round(originalWealth)` tokens.
+In contrast, an average group in the replication sample accumulated about `r round(replicationWealth)` tokens.
+However, none of the groups were efficient: the maximal wealth that can be reached in round 10 under full cooperation is approximately `r (80*1.5^10) %>% trunc()` tokens or `r (80*1.5^10 /20) %>% trunc()` Euro per group.
+
+```{r growthHeterogeneityViz}
+maxPath <- data.table(x = 1:10)
+maxPath[, y := 80*1.5^x]
+maxPath[, groupID := 42]
+ggplot(data = main,
+       mapping = aes(x = round, y = stock, color = treatment, by = groupID)) +
+  layout +
+  theme(legend.position="bottom") +
+  geom_line(alpha = 0.5) +
+  scale_x_continuous(breaks = 1:10) +
+  scale_y_continuous(limits = c(0, 4700),
+                       expand = c(0, NA)) +
+  scale_color_manual(values = c(cPrimary, cSecondary),
+                     labels = c("Original Sample", "Replication Sample")) +
+  geom_point(mapping = aes(x = 10, y = 4613), col = "#b5b5b5") +
+  annotate("text", x = 9.7, y = 4630,
+  label = "max", col = "#b5b5b5") +
+  geom_line(data = maxPath, mapping = aes(x = x, y =y), col = "#b5b5b5", lty = 2)
+```
+
+While there is clearly growth, groups do not realize the potential efficiency as the replication groups reach on average a level of `r main[treatment == "replication" & round == 10, mean(stock)] %>% trunc()` tokens out of `r (80*1.5^10) %>% trunc()` maximally possible or `r main[treatment == "replication" & round == 10, mean(stock)/(80*1.5^10)*100] %>% round(digits=1)`%.
+As in the original data, there is large heterogeneity with the richest group reaching `r main[treatment == "replication" & round == 10, max(stock)]` tokens whereas the poorest group ends up with `r main[treatment == "replication" & round == 10, min(stock)]` tokens.
+
 We thus, observe growth even for the poorest group and spot heterogeneity even within data sources.
 
-Figure 2 shows the dynamics of wealth over time.
-The left panel focuses on all groups, the upper right panel on those with above median wealth after round 10 (“successful” groups) and the lower left panel on those with below median wealth after round 10 (“unsuccessful” groups).
-
-```{r plotStock, fig.cap = "Average wealth over time across treatments."}
+Figure 2 shows the dynamics of wealth over time.^[Unlike GMTV I present no median split but only the main results.]
+
+```{r plotStock}
+#| fig.cap: "Average wealth over time across treatments."
 STOCK <- main[,
@@
           scale_x_continuous(name="",  breaks = 1:10) +
-          scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
+          scale_y_continuous(limits = c(0, 600), expand = c(0, 0)) +
           labs(y = "Wealth") +
-          scale_color_manual(values = colors) + 
+          scale_color_manual(values = c(cPrimary, cSecondary),
+                     labels = c("Original Sample", "Replication Sample")) +
+          guides(fill = "none") +
           theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
+
+p1
+```
+
+```{r plotStockLikeGMTV}
+#| eval: false
 
@@
 
-```{r tableStock, results = "asis", warning = FALSE}
+```{r tableStock}
+#| results: asis
+#| warning: false
 
@@
 As such, our results look familiar to GMTV's findings, where poor groups grew ever so slightly, while only rich groups experienced growth (that became exponential only after the 10th round).
-
-## Inequality
-
-In this subsection, we focus on the degree of inequality created endogenously in our setting.
-The smallest possible value the Gini coefficient takes is zero (if all four group members own one fourth of the wealth) and the largest possible value it takes is one (if one group member holds the entire wealth).
-Table 4 shows some summary statistics regarding the Gini coefficient.
-
-The round 10 Gini coefficient ranges between `r main[treatment == "replication" & round == 10, gini %>% min()] %>% round(digits = 3)` and `r main[treatment == "replication" & round == 10, gini %>% max()] %>% round(digits = 3)` in our data with a median of `r main[treatment == "replication" & round == 10, gini %>% median()] %>% round(digits = 3)`.
-
-```{r summary2, results = "asis", warning = FALSE}
-
-if(knitr::is_html_output()){
-  type <- "html"
-} else {
-  type = "latex"
-}
-
-replication <- main[treatment == "replication" & round == 10, gini]
-GMTV    <- main[treatment == "noPunish10" & round == 10, gini]
-
-rows <- sapply(X = list(replication, GMTV), FUN = NROW) %>% max()
-temp <- data.frame(replication = c(replication, rep(NA, rows - NROW(replication))),
-                   GMTV = c(GMTV, rep(NA, rows - NROW(GMTV))))
-
-stargazer(temp,
-          summary.stat = c("mean", "median","sd", "max", "min", "n"),
-          type = type, 
-          flip = TRUE, 
-          header=FALSE)
-
-rs2 <- wilcox.test(replication, 
-                   GMTV,
-                   exact = FALSE)$p.value %>% 
-  round(digits = 4) %>% 
-  formatC(format = "f", 
-          digits = 4)
-
-```
-
-The two-sided rank sum test yields a p-Value of `r rs2` for the mean ```gini``` during the last round of the game.
-
-Figure 3 illustrates the dynamics of the Gini coefficient (at the end of each round) over time and shows that inequality increases slightly.
-
-```{r plotInequality, fig.cap = "Average Gini coefficient over time across treatments."}
-GINI <- main[,
-             lapply(.SD, mean, na.rm = TRUE),
-             by = c("round", "treatment"),
-             .SDcols = "gini"]
-
-GINIr <- main[rich == TRUE,
-              lapply(.SD, mean, na.rm = TRUE),
-              by = c("round", "treatment"),
-              .SDcols = "gini"]
-
-GINIp <- main[rich == FALSE,
-              lapply(.SD, mean, na.rm = TRUE),
-              by = c("round", "treatment"),
-              .SDcols = "gini"]
-
-upperLimit <- GINI$gini %>% max() %>% round(digits = 1) + 0.15
-
-p1 <- ggplot(data = GINI, 
-       aes(x = round, y = gini, fill = treatment, color = treatment, lty = treatment)) +
-          layout +
-          theme(legend.position="bottom") +
-          # geom_vline(xintercept = 10, alpha = 0.66) +
-          geom_line(show.legend=FALSE) +
-          geom_point() +
-          scale_x_continuous(name="",  breaks = 1:10) +
-          scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-          labs(y = "Gini Coefficient") +
-          scale_color_manual(values = colors) + 
-          theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
-
-p2 <- ggplot(data = GINIr, 
-       aes(x = round, y = gini, fill = treatment, color = treatment, lty = treatment)) +
-          layout +
-          theme(legend.position="bottom") +
-          # geom_vline(xintercept = 10, alpha = 0.66) +
-          geom_line(show.legend=FALSE) +
-          geom_point() +
-          scale_x_continuous(name="",  breaks = 1:10) +
-          scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-          labs(y = "Gini (Rich)") +
-          scale_color_manual(values = colors)
-
-p3 <- ggplot(data = GINIp, 
-       aes(x = round, y = gini, fill = treatment, color = treatment, lty = treatment)) +
-          layout +
-          theme(legend.position="bottom") +
-          # geom_vline(xintercept = 10, alpha = 0.66) +
-          geom_line(show.legend=FALSE) +
-          geom_point() +
-          scale_x_continuous(name="",  breaks = 1:10) +
-          scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-          labs(y = "Gini (Poor)") +
-          scale_color_manual(values = colors)
-
-(p1 | (p2 / p3)) + plot_layout(guides = "collect") & theme(legend.position = "bottom")
-
-rm(list = c("GINI", "GINIp", "GINIr", "p1", "p2", "p3"))
-```
-
-### Inequality Differences between Data Sources
-
-Once more, we consider whether we were able to replicate GMTV's results with our data.
-
-The following table shows a simple OLS regression to illustrate differences in the 10th round's Gini coefficient between the replication's data and GMTV's data.
-Mean Gini coefficients are similar across data sources and there are no statistically significant differences in mean Gini coefficients.
-
-```{r tableGINI, results = "asis", warning = FALSE}
-
-# create subsets
-main_all  <- main[round == 10]
-main_poor <- main[round == 10 & rich == FALSE]
-main_rich <- main[round == 10 & rich == TRUE]
-
-# create table
-if(knitr::is_html_output()){
-  type <- "html"
-} else {
-  type = "latex"
-}
-
-m1 <- lm(formula = gini ~ treatment, data = main_all)
-m2 <- lm(formula = gini ~ treatment, data = main_poor)
-m3 <- lm(formula = gini ~ treatment, data = main_rich)
-
-stargazer(m1, m2, m3,
-
-          column.labels = c("All", "Below median", "Above median"),
-          model.numbers = FALSE,
-          dep.var.labels = "Gini",
-          header=FALSE,
-          covariate.labels = c("Replication"),
-
-          type = type, digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
-          )
-```
-
-# Online Methodology
-
-## Time Spent
-
-Participants spent approximately `r duration[, completion_time %>% unique() %>% mean()] %/% 60 + 1` minutes completing the experiment.
-Reading the instructions and answering the comprehension questions took the most time, that is, `r duration[page_name == "Intro_Instructions", time_spent %>% unique() %>% mean()] %/% 60 + 1` minutes.
-The public goods game required `r duration[app_name == "dPGG", time_spent %>% sum(), by = c("session_code", "participant_code")][,V1] %>% mean(na.rm = TRUE) %/% 60` minutes of the participants' time.
-
-```{r plotTime, fig.cap = "Average Time Spent for each Contribution per Round."}
-N <- duration[, participant_code %>% unique() %>% length()]
-plotDT <- duration[app_name == "dPGG" & page_name == "dPGG_Decision",
-                   .(time_spent = time_spent %>% sum()),
-                   by = c("session_code", "participant_code", "page_index", "page_name")]
-
-plotDT[, round := seq(from = 1, to = 10), by = c("participant_code")]
-
-upperLimit <- plotDT[, time_spent %>% mean(), by = c("round")] %>% max()
-
-ggplot(data = summarySE(data = plotDT,
-                        measurevar = "time_spent",
-                        groupvars=c("round"),
-                        na.rm = FALSE,
-                        conf.interval = 0.95,
-                        .drop = TRUE),
-       mapping = aes(x = round, y = time_spent)) +
-  layout +
-  theme(legend.position="bottom") +
-  geom_line(show.legend=FALSE, color = cSecondary, lty=2) +
-  geom_errorbar(aes(ymin=time_spent-ci, ymax=time_spent+ci), width=.25, alpha = 0.5, color = cSecondary) +
-  geom_point(color = cSecondary) +
-  scale_x_continuous(name="",  breaks = 1:10) +
-  scale_y_continuous(limits = c(0, upperLimit + 10), expand = c(0, 0)) +
-  labs(y = "Time Passed in Seconds", caption = "Bars indicate 95% confidence intervals.") +
-  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
-```
-
-Figure 4 illustrates the time participants needed to make each of their contributions during the replication.
-One can see that the initial as well as most of the other contributions take about 20 seconds of time.
-Interestingly, the second contribution takes (on average) about 50% more time than the first one - presumably because this is the first time participants' learn their respective group members' actions.
-The third contribution is a little faster and all subsequent contributions stabilize at `r plotDT[round > 3, time_spent %>% mean()] %>% ceiling()` seconds.
-
-Given that no participant dropped out after answering the comprehension questions correctly and given that participants need less than 20 seconds to make their contributions, more than 10 rounds are feasible.
-
-# Exporatory: Generalizability
-
-The following figure gives a first overview over the distribution of contributions across the two sorts of contributions.
-The density-plots in the top panel show the fraction of the initial endowment contributed in the first round of the experiment.
-The two plots in the bottom panel show contribution behavior in the VCA, that is, donations to climate change mitigation.
-The left panels depict the general population's behavior while the right panelshows the students' behavior.
-All contributions are relative to the maximum amount a participant could have contributed.
-
-Means are indicated by vertical dashed lines and are positive in both settings across samples.^[While the medians are similar in the bottom panel, that is, the experiment's contributions, they are smaller in the taop panel and zero in the student sample.] Overall contributions in the VCA setting are smaller than in the experiment's first round.
-
-```{r vizGeneralizability}
-R1covs <- covs[, .(participant.code,
-                   donation = donation * 20 ,
-                   donationShare = (donation * 20) / payoff * 100,
-                   payoff)]
-temp <- R1[R1covs, on = .(participant.code = participant.code)][treatment == "replication"]
-temp[, contributionShare := ownContribution/20 * 100]
-
-# viz wrapper
-plotShares <- function(stud = FALSE,
-                       var  = "donationShare",
-                       col  = cPrimary,
-                       xlab = "",
-                       ylab = ""){
-
-  dt <- temp[student == stud, .(x = get(var))]
-
-  ggplot(data = dt,
-         mapping = aes(x = x)) +
-    geom_density(alpha = 1,
-                 fill = col) +
-    scale_x_continuous(limits = c(0, 100),
-                       expand = c(0, NA)) +
-    scale_y_continuous(limits = c(0, NA),
-                       expand = c(0, NA)) +
-    geom_vline(xintercept = dt[,mean(x, na.rm = TRUE)],
-               lty = 2) +
-    labs(x = xlab,
-         y = ylab) +
-  layout
-}
-
-p1 <- plotShares(stud = FALSE, col = cPrimary,   var = "donationShare", ylab = "Density in VCA")
-p2 <- plotShares(stud = FALSE, col = cPrimary,   var = "contributionShare", 
-                 xlab = "Share of general pop. contributions", ylab = "Density in Experiment (round 1)")
-p3 <- plotShares(stud = TRUE,  col = cSecondary, var = "donationShare")
-p4 <- plotShares(stud = TRUE,  col = cSecondary, var = "contributionShare", xlab = "Share of students' contributions")
-
-(p1 / p2) | (p3 / p4)
-
-rm(list = c("R1covs", "p1", "p2", "p3", "p4"))
-```
-
-lorem ipsum.
-
-```{r}
-ggplot(data = temp[, 
-                   .(vca = donation / payoff * 100,
-                     dpgg = ownContribution / 20 * 100)],
-       mapping = aes(y = vca, x = dpgg)) +
-  annotate("segment", x = 0, xend = 100,
-                   y = 0,
-                   yend = 100,
-                   colour = "black", lty = 2, alpha = 0.5) +
-  geom_point(alpha = 0.33, col = cSecondary, size = 2) +
-  scale_x_continuous(limits = c(0, 105),
-                     expand = c(0, NA)) +
-  scale_y_continuous(limits = c(0, 105),
-                     expand = c(0, NA)) +
-  labs(y = "VCA: Percentage of endowment donated",
-       x = "Experiment: Percentage of endowment contributed in round 1") +
-  layout
-```
-A visual inspection of the scatter plot (where the saturation of the points is proportional to the frequency of a pair of contribution choices) does not hint at an association between the two sorts of contributions.
-
-## To do
-
-- explain similarities and differences to @GKLS2020 setup and how they came to be
-- compare samples across tasks
-- who generalizes (better)?
-- who is more heterogeneous and what does that mean?
-- How do the results compare to @GKLS2020
-
-# Conclusion

### 2022-10-08 analysis/quarto/paper.tex
added "quarto" and "paper" (already deprecated) + no clue what happened otherwise. Its been a long time

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  authoryear,
  preprint,
  3p]{elsarticle}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\journal{Journal of Behavioral and Experimental Economics}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Growth and inequality in public good provision \textbar{} an extended replication},
  pdfauthor={Hauke Roggenkamp},
  pdfkeywords={Replication study, Non-convenience sample, Open
science, Dynamic public good game, Online experiment, Generalizability},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\setlength{\parindent}{6pt}
\begin{document}

\begin{frontmatter}
\title{Growth and inequality in public good provision \textbar{} an
extended replication}
\author[1,2]{Hauke Roggenkamp%
%
}
 \ead{hauke.roggenkamp@unisg.ch}

\affiliation[1]{organization={Helmut Schmidt
University},addressline={Holstenhofweg
85},city={Hamburg},postcode={22043}}
\affiliation[2]{organization={University of
St.~Gallen},addressline={Torstrasse
25},city={St.~Gallen},postcode={9000}}

\cortext[cor1]{Corresponding author}

\begin{abstract}
This is the abstract. Lorem ipsum dolor sit amet, consectetur adipiscing
elit. Vestibulum augue turpis, dictum non malesuada a, volutpat eget
velit. Nam placerat turpis purus, eu tristique ex tincidunt et. Mauris
sed augue eget turpis ultrices tincidunt. Sed et mi in leo porta
egestas. Aliquam non laoreet velit. Nunc quis ex vitae eros aliquet
auctor nec ac libero. Duis laoreet sapien eu mi luctus, in bibendum leo
molestie. Sed hendrerit diam diam, ac dapibus nisl volutpat vitae.
Aliquam bibendum varius libero, eu efficitur justo rutrum at. Sed at
tempus elit.
\end{abstract}

\begin{keyword}
    Replication study \sep Non-convenience sample \sep Open
science \sep Dynamic public good game \sep Online experiment \sep 
    Generalizability
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, sharp corners, enhanced]}{\end{tcolorbox}}\fi

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\textbf{Hintergrund:} Ich habe diesen
\href{https://groups.google.com/g/esa-announce/c/-_2OmbkdxEk}{post}
gesehen und überlege meine Replikation entsprechend
\href{https://www.sciencedirect.com/journal/journal-of-behavioral-and-experimental-economics/about/call-for-papers\#transparency-reproducibility-and-generalizability-of-behavioral-economics-experiments}{hier}
einzureichen. Ist das realistisch? Wenn ja, wie soll man die Story
aufziehen? Soll man denen mal schreiben und fragen, ob noch Platz ist?

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\begin{quote}
``There are two possible articles you can write: (a) the article you
planned to write when you designed your study or (b) the article that
makes the most sense now that you have seen the results. They are rarely
the same, and the correct answer is (b).'' \citep[p.~171]{bemwriting}
\end{quote}

\hypertarget{pre-registered-gmtv-replication}{%
\section{Pre-registered GMTV
Replication}\label{pre-registered-gmtv-replication}}

\hypertarget{provision-of-the-public-good}{%
\subsection{Provision of the public
good}\label{provision-of-the-public-good}}

First, we ask whether the samples differ with respect to their initial
contributions to the public good. Is our replication sample more
pro-social than the original sample? Figure 1 reveals, that it is not.
The distributions of both samples look fairly similar. Both samples
contributed 10 tokens, that is, 50\% of their endowments on average
(median and mean).\footnote{The two-sided rank sum test (comparing
  differences between samples) yields a p-Value of 0.3926 for the mean
  contribution in first round of the game.} Moreover, both samples'
initial contributions resemble initial contributions participants
usually make in the standard game with partner matching.\footnote{See
  Figure 3B in \citet{fehrgaechter2000} (p.989), for instance.} In the
dynamic game presented here, we are particularly interested in the
subsequent periods because differences add up exponentially. Do the two
groups remain similar?

\includegraphics{paper_files/figure-pdf/firstRoundViz-1.pdf}

In particular, do the two samples' contributions follow the same pattern
over time? The answer is \emph{no}. Figure 2 illustrates that the
samples make similar contributions at the beginning and the end of the
game but behave differently in between. More precisely, the left
panel--depicting the average contributions in absolute terms--shows that
the original sample contributed substantially more than the replication
sample \emph{in all but the first and last rounds}. For this reason, the
original sample's behavior differs from the replication sample's
behavior in two aspects: it contributes more and exhibits a considerable
drop in the last period (whereas the replication sample's contributions
flatten). Note that increasing contributions over time imply increasing
endowments over time. Hence, increasing absolute contributions do not
necessarily imply that participants contribute increasing shares of
their endowments. The right panel in Figure 1 shows the share of overall
endowments contributed over time where both samples exhibit a similar
pattern: they decline and do not stabilize. The original sample's
behavior differs from the replication sample's behavior in one aspect:
it declined slower (to the same level in the last period).

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/plotShareOfContributions-1.pdf}

}

\caption{The average amount of tokens contributed over time in
treatments.}

\end{figure}

Moreover, both samples' contributions resemble contributions
participants usually make in the standard game with partner
matching.\footnote{The right panel is thus, comparable to the
  visualizations \emph{and results} in the standard game. See, for
  instance, Figure 1B in \citet{fehrgaechter2000} (p.986).} In the
dynamic game presented here, different paths lead to different levels of
wealth -- even if they share the same start- and end-points. We are
thus, more interested in the implications contributions have for wealth
generation and growth. So, how do the samples compare with respect to
wealth/income/endowments/stock?

\hypertarget{wealth-creation}{%
\subsection{Wealth Creation}\label{wealth-creation}}

How do the different contribution-paths translate to wealth?\footnote{To
  measure growth, we define a variable called \emph{stock} which sums
  the endowments of all participants in a given group at the end of the
  round (that is, after the contributions have been made, multiplied and
  redistributed).} Given that the original sample contributed more in
most of the periods, one would expect the respective groups to be
considerably more wealthy. Figure 3 indicates that they tend to be
insignificantly\footnote{The two-sided rank sum test (comparing
  differences between samples) yields a p-Value of 0.1356 for the mean
  stock in last round of the game.} richer.

\includegraphics{paper_files/figure-pdf/stockDistributionViz-1.pdf}

As the grey lines indicate, an average group in the original sample
accumulated about 478 tokens. In contrast, an average group in the
replication sample accumulated about 380 tokens. However, none of the
groups were efficient: the maximal wealth that can be reached in round
10 under full cooperation is approximately 4613 tokens or 230 Euro per
group.

\includegraphics{paper_files/figure-pdf/growthHeterogeneityViz-1.pdf}

While there is clearly growth, groups do not realize the potential
efficiency as the replication groups reach on average a level of 379
tokens out of 4613 maximally possible or 8.2\%. As in the original data,
there is large heterogeneity with the richest group reaching 1425 tokens
whereas the poorest group ends up with 92 tokens.

We thus, observe growth even for the poorest group and spot
heterogeneity even within data sources.

Figure 2 shows the dynamics of wealth over time.\footnote{Unlike GMTV I
  present no median split but only the main results.}

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/plotStock-1.pdf}

}

\caption{Average wealth over time across treatments.}

\end{figure}

The Figure illustrates that (in both data sources) growth was continuous
and surprisingly linear, given the exponential character of the game's
design.

To sum up, our groups also tend to be poorer, and median wealth is
higher in GMTV. The difference in mean ranks is not significant
according to a two-sided ranksum test\footnote{The two-sided rank sum
  test (comparing differences between data sources) yields a p-Value of
  0.1356 for the mean wealth after the last round of the game.},
however.

To further assess the statistical significance of differences in means,
we run OLS regressions where we regress wealth on a treatment dummy for
\emph{Replication} (Table 3). These regressions show that differences in
means are only significant for below median groups. This implies that
the poor groups in our data are even less wealthy than GMTV's poor
groups.

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & \multicolumn{3}{c}{Wealth} \\ 
 & All & Below median & Above median \\ 
\hline \\[-1.8ex] 
 Replication & $-$98.26 & $-$59.41$^{***}$ & $-$138.21 \\ 
  & (101.21) & (18.32) & (166.67) \\ 
  & & & \\ 
 Constant & 478.09$^{***}$ & 234.70$^{***}$ & 731.00$^{***}$ \\ 
  & (75.58) & (13.99) & (124.73) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 52 & 24 & 25 \\ 
R$^{2}$ & 0.02 & 0.32 & 0.03 \\ 
Residual Std. Error & 362.49 & 44.24 & 413.67 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

As such, our results look familiar to GMTV's findings, where poor groups
grew ever so slightly, while only rich groups experienced growth (that
became exponential only after the 10th round).

  \bibliography{../biblio.bib}

\end{document}

### 2022-10-08 analysis/reports/00_reproduction.Rmd
added "quarto" and "paper" (already deprecated) + no clue what happened otherwise. Its been a long time

@@
 
-In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree].
+In an attempt to incorporate uncertainty to @GMTV2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree].
 The first experiment will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances).
@@
 
-This document explores the data provided by @GACHTER2017 and finds that some of the variables are a little off.
+This document explores the data provided by @GMTV2017 and finds that some of the variables are a little off.
 In addition, it fails to replicate the orginal article's figures.

### 2022-10-08 analysis/reports/prettyReports/04_Analyses.tex
added "quarto" and "paper" (already deprecated) + no clue what happened otherwise. Its been a long time

% https://github.com/svmiller/svm-r-markdown-templates

\documentclass[11pt,]{article}
\usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{libertine}

  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}

\usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center

\renewenvironment{abstract}
 {{%
    \setlength{\leftmargin}{0mm}
    \setlength{\rightmargin}{\leftmargin}%
  }%
  \relax}
 {\endlist}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother

\setcounter{secnumdepth}{0}

\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}

\title{Analysis Plan: Replicating Growth and Inequality in Public Good
Provision \thanks{Further replication files are available on the
author's Github account (\url{http://github.com/howquez}).
\textbf{Current version}: February 01, 2022; \textbf{Corresponding
author}:
\href{mailto:roggenkh@hsu-hh.de}{\nolinkurl{roggenkh@hsu-hh.de}}.}  }

\author{\Large Hauke
Roggenkamp\vspace{0.05in} \newline\normalsize\emph{Helmut-Schmidt-University}   \and \Large Stefan
Traub\vspace{0.05in} \newline\normalsize\emph{Helmut-Schmidt-University}   \and \Large Michael
Berlemann\vspace{0.05in} \newline\normalsize\emph{Helmut-Schmidt-University}  }

\date{}

\usepackage{titlesec}

\titleformat*{\section}{\normalsize\bfseries}
\titleformat*{\subsection}{\normalsize\itshape}
\titleformat*{\subsubsection}{\normalsize\itshape}
\titleformat*{\paragraph}{\normalsize\itshape}
\titleformat*{\subparagraph}{\normalsize\itshape}

\usepackage{natbib}
\bibliographystyle{apsr}
\usepackage[strings]{underscore} % protect underscores in most circumstances

\newtheorem{hypothesis}{Hypothesis}
\usepackage{setspace}

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{hyperref}
\usepackage{array}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[table]{xcolor}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{calc}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage[para,online,flushleft]{threeparttable}

% move the hyperref stuff down here, after header-includes, to allow for - \usepackage{hyperref}

\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \PassOptionsToPackage{hyphens}{url}\usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \PassOptionsToPackage{hyphens}{url}\usepackage[draft,unicode=true]{hyperref}
\fi
}

\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Hauke
Roggenkamp (Helmut-Schmidt-University) and Stefan
Traub (Helmut-Schmidt-University) and Michael
Berlemann (Helmut-Schmidt-University)},
             pdfkeywords = {dynamic public goods game, inequality,
cooperation, growth},  
            pdftitle={Analysis Plan: Replicating Growth and Inequality
in Public Good Provision},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

% Add an option for endnotes. -----

% add tightlist ----------
\providecommand{\tightlist}{%
\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% add some other packages ----------

% \usepackage{multicol}
% This should regulate where figures float
% See: https://tex.stackexchange.com/questions/2275/keeping-tables-figures-close-to-where-they-are-mentioned
\usepackage[section]{placeins}

\begin{document}

% \pagenumbering{arabic}% resets `page` counter to 1 
%

% \maketitle

{% \usefont{T1}{pnc}{m}{n}
\setlength{\parindent}{0pt}
\thispagestyle{plain}
{\fontsize{18}{20}\selectfont\raggedright 
\maketitle  % title \par

}

{
   \vskip 13.5pt\relax \normalsize\fontsize{11}{12} 
\textbf{\authorfont Hauke
Roggenkamp} \hskip 15pt \emph{\small Helmut-Schmidt-University}   \par \textbf{\authorfont Stefan
Traub} \hskip 15pt \emph{\small Helmut-Schmidt-University}   \par \textbf{\authorfont Michael
Berlemann} \hskip 15pt \emph{\small Helmut-Schmidt-University}

}

}

\begin{abstract}

    \hbox{\vrule height .2pt width 39.14pc}

    \vskip 8.5pt % \small

\noindent We replicate a public goods experiment with dynamic
interdependency and find similar results as GMTV. Absolute contributions
increase over time. Just as in static public goods experiments, the
share of endowments contributed decreases over time. The richest groups
earn fifteen times more than the poorest groups. While there clearly is
growth, groups do not realize the maximal potential efficiency and earn
just a fraction of what is possible. Even though we conducted the
experiment online and remotely, dropouts are no concern. Participants
make relatively fast decisions which makes longer games feasible in the
future. Taken together with inefficient growth and the lack of dropouts,
additional rounds are fairly cheap.

\vskip 8.5pt \noindent \emph{Keywords}: dynamic public goods game,
inequality, cooperation, growth \par

    \hbox{\vrule height .2pt width 39.14pc}

\end{abstract}

\vskip -8.5pt

 % removetitleabstract

\noindent

\hypertarget{background}{%
\section{Background}\label{background}}

In an attempt to incorporate uncertainty to \citet{GMTV2017}'s dynamic
public goods game (DPGG), I plan to run a series of remote online
experiments using oTree \citep{oTree}. This experiment replicated
Gächter et al.'s NOPUNISH 10-round treatment arm as close as possible
(given the remote circumstances). The current demo version of the
experiment can be found \href{https://cliccs.herokuapp.com/}{here}.
Click \href{https://github.com/Howquez/coopUncertainty}{here} to visit
the corresponding Github repository.

\href{https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd/03_dataAnalyses.Rmd}{This
report} is the third in a series of reports covering this project. It
reads the data prepared in the previous reports and analyzes them. The
whole replication project is registered in the AEA RCT Registry and the
unique identifying number is:
\href{https://doi.org/10.1257/rct.7902-2.0}{AEARCTR-0007902}
\citep{preregistration}.

\hypertarget{data}{%
\section{Data}\label{data}}

I'll refer to the data \citet{GMTV2017} provided as \emph{GMTV} or
\emph{noPunish10} in what follows. GMTV conducted most of their sessions
in late 2012. All of these sessions ran in Nottingham using a student
sample. collected They 23 observations in their NOPUNISH 10 treatment
arm. Our data, refered to as \emph{replication} is more recent, gathered
remotely in Hamburg using a different tech stack as well as a different
sample.

We conducted a series a 4 sessions in between Thursday, July 01 to
Friday, July 23 2021 and collected 29 observations (from 116
participants) in total. 35 additional participants could not be matched
with other group members or failed to answer the comprehension
questions. These participants are labeled as dropouts. None of them
dropped out during the session such that attrition is no problem here.

Two of these sessions were special: The first (jyf8xd0s) as well as the
last one (d6jrsxnr). The first session suffered technical problems such
that the risk elicitation task was omitted. The last session (almost
exclusively) relied on a student sample as our non-student sample was
exhausted after the first three sessions. As a consequence, the last
session was conducted with 59 students while all others were conducted
without any students. I'll therefore create a boolean \texttt{student}
variable.

All participants were recruited in by the University of Hamburg's WISO
Research Lab using HROOT \citep{hroot}.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{first-round}{%
\subsection{First Round}\label{first-round}}

We start by discussing initial contributions which assume the full range
between 0 and 20 as Table 1 illustrates. Both the median as well as the
mean are about 10 tokens, that is, 50\% of the initial endowment in both
data sources. This is comparable to initial contributions in the
standard game with partner matching.\footnote{See Figure 3B in
  \citet{fehrgaechter2000}, for instance.}

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & replication & GMTV \\ 
\hline \\[-1.8ex] 
Mean & 10.017 & 10.685 \\ 
Median & 10 & 10.000 \\ 
St. Dev. & 6.340 & 5.881 \\ 
Max & 20 & 20.000 \\ 
Min & 0 & 0.000 \\ 
N & 116 & 92 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

The two-sided rank sum test (comparing differences between data sources)
yields a p-Value of 0.3926 for the mean contribution in first round of
the game.

\hypertarget{provision-of-the-public-good}{%
\subsection{Provision of the public
good}\label{provision-of-the-public-good}}

We proceed by further discussing contributions. The left panel in Figure
1 shows the average amount of tokens participants contributed over time.
Contributions are clearly non-zero and are increasing over time in the
replication treatment.\footnote{Participants contribute about 10 tokens
  in the first round} While contributions flatten in the replication,
the GMTV data exhibit a drop in the last round. Note that increasing
contributions over time imply that participants have increasing
endowments over time. Hence, increasing contributions do not necessarily
imply that participants contribute increasing shares of their
endowments. The right panel in Figure 1 shows the share of overall
endowments contributed over time. In the original data, participants
contribute around 53\% of their endowment in round 1. This amount
steadily decreases. The replication exhibits a similar pattern with an
initial average contributions of 50\%. Both treatments resemble the
results from the standard game: Just as in \citet{fehrgaechter2000}
contributions start at a level of around 50-60\% of endowments and
decrease to around 10\% of endowments in round 10.

\begin{figure}
\centering
\includegraphics{/Users/hauke.roggenkamp/Documents/dev/coopUncertainty/analysis/reports/prettyReports/04_Analyses_files/figure-latex/plotShareOfContributions-1.pdf}
\caption{The average amount of tokens contributed over time in
treatments.}
\end{figure}

\hypertarget{wealth-creation}{%
\subsection{Wealth Creation}\label{wealth-creation}}

Possibly of more interest are the implications contributions have for
wealth generation and growth. To measure growth, we define a variable
\emph{stock} which sums the endowments of all participants in a given
group at the end of the round (that is, after the contributions have
been made, multiplied and redistributed). \citet{GMTV2017} refer to that
variable as ``wealth'' so we will do the same in what follows. Before
the start of round 1, wealth will be 80 in all groups by construction.
The maximal wealth that can be reached in round 10 (if everyone
contributes their entire endowment in each round) is approximately 4613
tokens or 230 Euro per group. Table 3 shows some summary statistics
regarding wealth. Groups do achieve growth on average. While there is
clearly growth, groups do not realize the maximal potential efficiency
as the replication groups reach on average a level of 379 tokens out of
4613 maximally possible or 8.2\%. As in the original data, there is
large heterogeneity with the richest group reaching 1425 tokens whereas
the poorest group ends up with 92 tokens.

\begin{figure}
\centering
\includegraphics{/Users/hauke.roggenkamp/Documents/dev/coopUncertainty/analysis/reports/prettyReports/04_Analyses_files/figure-latex/plotStock-1.pdf}
\caption{Average wealth over time across treatments.}
\end{figure}

Figure 2 shows the dynamics of wealth over time. The left panel focuses
on all groups, the upper right panel on those with above median wealth
after round 10 (``successful'' groups) and the lower left panel on those
with below median wealth after round 10 (``unsuccessful'' groups). The
average wealth is increasing across rounds and is substantially above 80
once round 10 was played as Table 2 illustrates.

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & replication & GMTV \\ 
\hline \\[-1.8ex] 
Mean & 379.828 & 478.087 \\ 
Median & 262 & 304.000 \\ 
St. Dev. & 336.059 & 393.575 \\ 
Max & 1,425 & 1,792.000 \\ 
Min & 92 & 161.000 \\ 
N & 29 & 23 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

The two-sided rank sum test (comparing differences between data sources)
yields a p-Value of 0.1356 for the mean wealth after the last round of
the game.

\hypertarget{wealth-differences-between-data-sources}{%
\subsubsection{Wealth Differences between Data
Sources}\label{wealth-differences-between-data-sources}}

We next consider whether we were able to replicate GMTV's results with
our data. Absolute contributions tended to be higher in \citet{GMTV2017}
but end up at around the same level as in the replication due to a stark
decline in contributions on the last round. In terms of shares
contributed both data sources exhibit a similar pattern: they decline
and do not stabilize. Even though the share of current endowments
contributed in the last round is quite similar, the share declined a
little faster in our data.

Our groups also tend to be poorer. Median wealth is higher in GMTV. This
difference in mean ranks is not significant according to a two-sided
ranksum test, however. To assess the statistical significance of
differences in means, we run OLS regressions where we regress wealth on
a treatment dummy for \emph{Replication} (Table 3). These regressions
show that differences in means are only significant for below median
groups.

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & \multicolumn{3}{c}{Wealth} \\ 
 & All & Below median & Above median \\ 
\hline \\[-1.8ex] 
 Replication & $-$98.26 & $-$59.41$^{***}$ & $-$138.21 \\ 
  & (101.21) & (18.32) & (166.67) \\ 
  & & & \\ 
 Constant & 478.09$^{***}$ & 234.70$^{***}$ & 731.00$^{***}$ \\ 
  & (75.58) & (13.99) & (124.73) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 52 & 24 & 25 \\ 
R$^{2}$ & 0.02 & 0.32 & 0.03 \\ 
Residual Std. Error & 362.49 & 44.24 & 413.67 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\hypertarget{inequality}{%
\subsection{Inequality}\label{inequality}}

In this subsection, we focus on the amount of inequality created
endogenously in our setting. The smallest possible value the Gini
coefficient takes is zero (if all four group members own one fourth of
the wealth) and the largest possible value it takes is one (if one group
member holds the entire wealth). Table 4 shows some summary statistics
regarding the Gini coefficient.

The round 10 Gini coefficient ranges between 0.035 and 0.52 in our data
with a median of 0.218.

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & replication & GMTV \\ 
\hline \\[-1.8ex] 
Mean & 0.218 & 0.246 \\ 
Median & 0.218 & 0.245 \\ 
St. Dev. & 0.123 & 0.131 \\ 
Max & 0.520 & 0.479 \\ 
Min & 0.035 & 0.044 \\ 
N & 29 & 23 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

The two-sided rank sum test yields a p-Value of 0.4176 for the mean
\texttt{gini} during the last round of the game.

Figure 3 illustrates the dynamics of the Gini coefficient (at the end of
each round) over time and shows that inequality increases slightly.

\begin{figure}
\centering
\includegraphics{/Users/hauke.roggenkamp/Documents/dev/coopUncertainty/analysis/reports/prettyReports/04_Analyses_files/figure-latex/plotInequality-1.pdf}
\caption{Average Gini coefficient over time across treatments.}
\end{figure}

\hypertarget{inequality-differences-between-data-sources}{%
\subsubsection{Inequality Differences between Data
Sources}\label{inequality-differences-between-data-sources}}

Once more, we consider whether we were able to replicate GMTV's results
with our data.

The following table shows a simple OLS regression to illustrate
differences in the 10th round's Gini coefficient between the
replication's data and GMTV's data. Mean Gini coefficients are similar
across data sources and there are no statistically significant
differences in mean Gini coefficients.

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & \multicolumn{3}{c}{Gini} \\ 
 & All & Below median & Above median \\ 
\hline \\[-1.8ex] 
 Replication & $-$0.03 & $-$0.05 & 0.002 \\ 
  & (0.04) & (0.06) & (0.05) \\ 
  & & & \\ 
 Constant & 0.25$^{***}$ & 0.26$^{***}$ & 0.23$^{***}$ \\ 
  & (0.03) & (0.04) & (0.04) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 52 & 24 & 25 \\ 
R$^{2}$ & 0.01 & 0.03 & 0.0001 \\ 
Residual Std. Error & 0.13 & 0.13 & 0.13 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\hypertarget{time-spent}{%
\section{Time Spent}\label{time-spent}}

Participants spent approximately 24 minutes completing the experiment.
Reading the instructions and answering the comprehension questions took
the most time, that is, 12 minutes. The public goods game required 7
minutes of the participants' time.

\begin{figure}
\centering
\includegraphics{/Users/hauke.roggenkamp/Documents/dev/coopUncertainty/analysis/reports/prettyReports/04_Analyses_files/figure-latex/plotTime-1.pdf}
\caption{Average Time Spent for each Contribution per Round.}
\end{figure}

Figure 4 illustrates the time participants needed to make each of their
contributions during the replication. One can see that the initial as
well as most of the other contributions take about 20 seconds of time.
Interestingly, the second contribution takes (on average) about 50\%
more time than the first one - presumably because this is the first time
participants' learn their respective group members' actions. The third
contribution is a little faster and all subsequent contributions
stabilize at 19 seconds.

Given that no participant dropped out after answering the comprehension
questions correctly and given that participants need less than 20
seconds to make their contributions, more than 10 rounds are feasible.

\hypertarget{sample-properties}{%
\section{Sample Properties}\label{sample-properties}}

\% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard
University. E-mail: hlavac at fas.harvard.edu \% Date and time: Tue, Feb
01, 2022 - 13:44:37

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
\hline \\[-1.8ex] 
gender & 116 & 0.526 & 0.501 & 0 & 0 & 1 & 1 \\ 
age & 116 & 35.767 & 15.663 & 9 & 24 & 49.2 & 73 \\ 
switching\_row & 78 & 6.154 & 2.151 & 1.000 & 6.000 & 7.000 & 12.000 \\ 
education & 116 & 6.241 & 0.966 & 3 & 6 & 7 & 8 \\ 
donation & 116 & 0.931 & 1.672 & 0.000 & 0.000 & 1.000 & 11.050 \\ 
pq01 & 116 & 4.302 & 1.144 & 1 & 3.8 & 5 & 6 \\ 
pq02 & 116 & 2.681 & 1.702 & 0 & 1 & 4 & 6 \\ 
pq03 & 116 & 3.759 & 1.184 & 1 & 3 & 5 & 6 \\ 
pq04 & 116 & 1.853 & 1.551 & 0 & 1 & 2 & 6 \\ 
pq05 & 116 & 4.284 & 1.207 & 1 & 4 & 5 & 6 \\ 
pq06 & 116 & 3.672 & 1.525 & 0 & 3 & 5 & 6 \\ 
pq07 & 116 & 4.879 & 1.463 & 0 & 4 & 6 & 6 \\ 
pq08 & 116 & 4.647 & 1.385 & 1 & 4 & 6 & 6 \\ 
pq09 & 116 & 1.560 & 2.006 & 0 & 0 & 3 & 6 \\ 
pq10 & 116 & 3.009 & 1.639 & 0 & 2 & 4 & 6 \\ 
pq11 & 116 & 3.586 & 1.358 & 0 & 3 & 5 & 6 \\ 
pq12 & 116 & 3.914 & 1.564 & 0 & 3 & 5 & 6 \\ 
pq13 & 116 & 3.836 & 1.480 & 0 & 3 & 5 & 6 \\ 
pq14 & 116 & 4.241 & 1.618 & 0 & 3 & 6 & 6 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
 & female & age & risk & donations \\ 
\hline \\[-1.8ex] 
 Replication & 0.15$^{**}$ & 5.04$^{***}$ & $-$0.28 & 0.25 \\ 
  & (0.07) & (1.65) & (0.27) & (0.23) \\ 
  & & & & \\ 
 Constant & 0.38$^{***}$ & 30.73$^{***}$ & 6.44$^{***}$ & 0.68$^{***}$ \\ 
  & (0.05) & (1.23) & (0.19) & (0.17) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 208 & 208 & 165 & 208 \\ 
R$^{2}$ & 0.02 & 0.04 & 0.01 & 0.01 \\ 
Residual Std. Error & 0.50 & 11.83 & 1.76 & 1.66 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{5}{c}{\textit{Dependent variable:}} \\ 
\cline{2-6} 
 & quick thinker & easily offended & very satisfied & very dependent & generally happy \\ 
\hline \\[-1.8ex] 
 Replication & $-$0.77$^{***}$ & $-$1.03$^{***}$ & $-$1.23$^{***}$ & $-$0.94$^{***}$ & $-$1.36$^{***}$ \\ 
  & (0.17) & (0.23) & (0.17) & (0.20) & (0.16) \\ 
  & & & & & \\ 
 Constant & 5.08$^{***}$ & 3.71$^{***}$ & 4.99$^{***}$ & 2.79$^{***}$ & 5.64$^{***}$ \\ 
  & (0.13) & (0.17) & (0.13) & (0.15) & (0.12) \\ 
  & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 208 & 208 & 208 & 208 & 208 \\ 
R$^{2}$ & 0.09 & 0.09 & 0.21 & 0.09 & 0.26 \\ 
Residual Std. Error & 1.20 & 1.66 & 1.21 & 1.46 & 1.15 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{5}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{5}{c}{\textit{Dependent variable:}} \\ 
\cline{2-6} 
 & work important & family important & friends important & religion important & politics important \\ 
\hline \\[-1.8ex] 
 Replication & $-$1.04$^{***}$ & $-$0.61$^{***}$ & $-$1.30$^{***}$ & $-$0.87$^{***}$ & $-$0.69$^{***}$ \\ 
  & (0.20) & (0.21) & (0.18) & (0.26) & (0.22) \\ 
  & & & & & \\ 
 Constant & 4.72$^{***}$ & 5.49$^{***}$ & 5.95$^{***}$ & 2.43$^{***}$ & 3.70$^{***}$ \\ 
  & (0.15) & (0.16) & (0.13) & (0.20) & (0.16) \\ 
  & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 208 & 208 & 208 & 208 & 208 \\ 
R$^{2}$ & 0.11 & 0.04 & 0.20 & 0.05 & 0.05 \\ 
Residual Std. Error & 1.46 & 1.51 & 1.28 & 1.88 & 1.58 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{5}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
 & most people trusted & hard work better & government responsible & incomes equal \\ 
\hline \\[-1.8ex] 
 Replication & $-$0.28 & $-$1.52$^{***}$ & $-$0.48$^{**}$ & 0.42$^{*}$ \\ 
  & (0.19) & (0.21) & (0.20) & (0.23) \\ 
  & & & & \\ 
 Constant & 3.87$^{***}$ & 5.43$^{***}$ & 4.32$^{***}$ & 3.83$^{***}$ \\ 
  & (0.14) & (0.16) & (0.15) & (0.17) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 208 & 208 & 208 & 208 \\ 
R$^{2}$ & 0.01 & 0.20 & 0.03 & 0.02 \\ 
Residual Std. Error & 1.36 & 1.52 & 1.42 & 1.63 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
 & \multicolumn{2}{c}{Wealth} & \multicolumn{2}{c}{Gini} \\ 
\hline \\[-1.8ex] 
 female & $-$30.63 & $-$65.02 & 0.02 & 0.02 \\ 
  & (88.07) & (83.80) & (0.03) & (0.03) \\ 
  & & & & \\ 
 age & 7.05$^{*}$ & 9.00$^{**}$ & $-$0.001 & $-$0.001 \\ 
  & (3.82) & (3.60) & (0.001) & (0.001) \\ 
  & & & & \\ 
 risk & 27.21 & 10.98 & $-$0.01 & $-$0.01 \\ 
  & (22.65) & (19.45) & (0.01) & (0.01) \\ 
  & & & & \\ 
 quick thinker & $-$55.19 &  & 0.02 &  \\ 
  & (45.52) &  & (0.02) &  \\ 
  & & & & \\ 
 easily offended & $-$26.52 &  & 0.01 &  \\ 
  & (31.48) &  & (0.01) &  \\ 
  & & & & \\ 
 very satisfied & $-$2.62 &  & 0.001 &  \\ 
  & (42.60) &  & (0.02) &  \\ 
  & & & & \\ 
 very dependent & $-$22.41 &  & 0.0003 &  \\ 
  & (30.47) &  & (0.01) &  \\ 
  & & & & \\ 
 generally happy & 70.06 &  & 0.004 &  \\ 
  & (42.99) &  & (0.02) &  \\ 
  & & & & \\ 
 work important & $-$64.01 &  & $-$0.01 &  \\ 
  & (39.13) &  & (0.02) &  \\ 
  & & & & \\ 
 family important & 11.99 &  & $-$0.01 &  \\ 
  & (38.05) &  & (0.01) &  \\ 
  & & & & \\ 
 friends important & $-$24.05 &  & $-$0.004 &  \\ 
  & (37.94) &  & (0.01) &  \\ 
  & & & & \\ 
 religion important & $-$20.48 &  & 0.02$^{*}$ &  \\ 
  & (26.15) &  & (0.01) &  \\ 
  & & & & \\ 
 politics important & 86.94$^{***}$ &  & $-$0.01 &  \\ 
  & (30.79) &  & (0.01) &  \\ 
  & & & & \\ 
 most people trusted & $-$0.49 &  & $-$0.001 &  \\ 
  & (31.94) &  & (0.01) &  \\ 
  & & & & \\ 
 hard work better & 35.38 &  & $-$0.03$^{*}$ &  \\ 
  & (34.46) &  & (0.01) &  \\ 
  & & & & \\ 
 government responsible & $-$47.38 &  & $-$0.03$^{*}$ &  \\ 
  & (39.54) &  & (0.02) &  \\ 
  & & & & \\ 
 incomes equal & $-$9.13 &  & 0.01 &  \\ 
  & (33.79) &  & (0.01) &  \\ 
  & & & & \\ 
 Constant & 278.16 & 100.12 & 0.39$^{***}$ & 0.28$^{***}$ \\ 
  & (377.35) & (180.67) & (0.14) & (0.07) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 78 & 78 & 78 & 78 \\ 
R$^{2}$ & 0.28 & 0.10 & 0.21 & 0.02 \\ 
Residual Std. Error & 357.69 & 360.58 & 0.14 & 0.14 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{4}{r}{Robust standard errors in parentheses, clustered by group ID.} \\ 
\end{tabular} 
\end{table}

\hypertarget{hamburg-how-do-students-compare-to-non-students}{%
\section{Hamburg: How do Students compare to
non-Students?}\label{hamburg-how-do-students-compare-to-non-students}}

This section considers the replication data only. Doing so, we'll
exploit the circumstance that we recruited from both the convenience or
``student'' sample as well as the non-convenience sample \emph{(Hamburg
Panel)} and analyze the differences between the two.

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & Students & HH.panel \\ 
\hline \\[-1.8ex] 
Mean & 10.172 & 9.827 \\ 
Median & 10 & 10.000 \\ 
St. Dev. & 6.470 & 6.233 \\ 
Max & 20 & 20.000 \\ 
Min & 0 & 0.000 \\ 
N & 64 & 52 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

We start by looking at the initial contributions. As Table 5
illustrates, there is no difference in averages, standard deviation or
the range. The two-sided rank sum test (comparing differences between
data sources) yields a p-Value of 0.8902 for the mean contribution in
first round of the game.

While the initial contributions are on average quite similar between the
two sample, the subsequent contributions differ. In both absolute and
relative terms, the Hamburg-Panel tends to contribute more than the
student sample as the following Figure shows.

\includegraphics{/Users/hauke.roggenkamp/Documents/dev/coopUncertainty/analysis/reports/prettyReports/04_Analyses_files/figure-latex/sampleContributions-1.pdf}

Differences in contributions lead to differences in wealth. The
Hamburg-Panel therefore earned more during the public goods game than
the student sample. This can be seen in the following figure as well as
in the subsequent table:

\begin{figure}
\centering
\includegraphics{/Users/hauke.roggenkamp/Documents/dev/coopUncertainty/analysis/reports/prettyReports/04_Analyses_files/figure-latex/sampleStock-1.pdf}
\caption{Average wealth over time across samples.}
\end{figure}

\newpage
\singlespacing 
\bibliography{../biblio.bib}

\end{document}

### 2022-10-08 analysis/reports/rmd/01_dataGMTV.Rmd
post data collection
added "quarto" and "paper" (already deprecated) + no clue what happened otherwise. Its been a long time

@@
 # calculate gini based on stock (i.e. end of period earnings)
-noPunish10[, stock0 := tokens - putin + sum/4]
-noPunish10[, stock1 := other1 - pu1 + sum/4]
-noPunish10[, stock2 := other2 - pu2 + sum/4]
-noPunish10[, stock3 := other3 - pu3 + sum/4]
+noPunish10[, stock0 := (tokens - putin + 1.5*sum/4) %>% ceiling()]
+noPunish10[, stock1 := (other1 - pu1 + 1.5*sum/4) %>% ceiling()]
+noPunish10[, stock2 := (other2 - pu2 + 1.5*sum/4) %>% ceiling()]
+noPunish10[, stock3 := (other3 - pu3 + 1.5*sum/4) %>% ceiling()]
 
@@
 
+```
+
+Unfortunately, I made a misstake calculating the ```share```. For this reason, it will be recalculated here:
+
+```{r recalcShare}
+GMTV[, share := contribution/endowment]
 ```

### 2022-10-08 analysis/reports/rmd/04_prettyAnalyses.Rmd
added "quarto" and "paper" (already deprecated) + no clue what happened otherwise. Its been a long time

--- 2021-08-11 analysis/reports/rmd/03_dataAnalyses.Rmd
@@
 ---
-title: "3. Analysis Plan"
-description: |
-  Analyze and compare data
+output: 
+  pdf_document:
+    citation_package: natbib
+    keep_tex: true
+    fig_caption: true
+    latex_engine: pdflatex
+    template: ../prettyReports/svm.tex
+bibliography: ../biblio.bib
+header-includes:
+  -  \usepackage{hyperref}
+  - \usepackage{array}   
+  - \usepackage{caption}
+  - \usepackage{graphicx}
+  - \usepackage{siunitx}
+  - \usepackage[table]{xcolor}
+  - \usepackage{multirow}
+  - \usepackage{hhline}
+  - \usepackage{calc}
+  - \usepackage{tabularx}
+  - \usepackage{fontawesome}
+  - \usepackage[para,online,flushleft]{threeparttable}
+biblio-style: apsr
+title: "Analysis Plan: Replicating Growth and Inequality in Public Good Provision"
+thanks: "Further replication files are available on the author's Github account (http://github.com/howquez).
+**Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: roggenkh@hsu-hh.de."
 author:
 - name: Hauke Roggenkamp
-    url: https://github.com/Howquez
-    affiliation: CLICCS
-    affiliation_url: https://www.cliccs.uni-hamburg.de/
-date: "`r Sys.Date()`"
-bibliography: ../biblio.bib
-output:
-  distill::distill_article:
-    toc: true
-    toc_depth: 2
-    toc_float: false
+  affiliation: Helmut-Schmidt-University
+- name: Stefan Traub
+  affiliation: Helmut-Schmidt-University
+- name: Michael Berlemann
+  affiliation: Helmut-Schmidt-University
+abstract: "We replicate a public goods experiment with dynamic interdependency and find similar results as GMTV.
+Absolute contributions increase over time.
+Just as in static public goods experiments, the share of endowments contributed decreases over time.
+The richest groups earn fifteen times more than the poorest groups.
+While there clearly is growth, groups do not realize the maximal potential efficiency and earn just a fraction of what is possible.
+Even though we conducted the experiment online and remotely, dropouts are no concern.
+Participants make relatively fast decisions which makes longer games feasible in the future.
+Taken together with inefficient growth and the lack of dropouts, additional rounds are fairly cheap."
+keywords: "dynamic public goods game, inequality, cooperation, growth"
+date: "`r format(Sys.time(), '%B %d, %Y')`"
+geometry: margin=1in
+fontfamily: libertine
+fontsize: 11pt
+# spacing: double
+endnote: no
 ---
@@
   knitr::opts_chunk$set(echo = FALSE)
+  evalKable <- TRUE
 }else{
-  knitr::opts_chunk$set(echo = TRUE)
+  knitr::opts_chunk$set(echo = FALSE)
+  evalKable <- FALSE
 }
@@
 library(stargazer)
+library(Rmisc)
 ```
@@
 
-# Key Takeaways
-
-- We replicate a public goods experiment with dynamic interdependency and find similar results as @GACHTER2017.
-- Absolute contributions increase over time.
-- Just as in _static_ public goods experiments, the share of endowments contributed decreases over time.
-- The richest groups earn fifteen times more than the poorest groups.
-- While there clearly is growth, groups do not realize the maximal potential efficiency and earn just over `r main[treatment == "replication" & round == 10, mean(stock)/(80*1.5^10)*100] %>% round(digits=1)`% of what is possible.
-- Even though we conducted the experiment online and remotely, dropouts (or "attrition") are no concern.
-- Relying on an inexperienced non-convenience sample, `r trunc((R1[comprehension > 1] %>% NROW() / R1[!(is.na(comprehension))] %>% NROW())*100)`% of all participants stated that they understood the game.
-- Participants make relatively fast decisions which makes longer games feasible in the future.^[Taken together with inefficient growth and the lack of dropouts, additional rounds are fairly cheap.]
-
 # Background
 
-In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree].
+In an attempt to incorporate uncertainty to @GMTV2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree].
 This experiment  replicated Gächter et al.'s NOPUNISH 10-round treatment arm as close as possible (given the remote circumstances).
@@
 
-I'll refer to the data @GACHTER2017 provided as _GMTV_ or _noPunish10_ in what follows.
+I'll refer to the data @GMTV2017 provided as _GMTV_ or _noPunish10_ in what follows.
 GMTV conducted most of their sessions in late 2012.
@@
 
-```{r meta}
+```{r meta, eval = evalKable}
 meta %>% kable()
@@
 
-### Hm..?
-
-The plot above puzzles me a little as the right panel visualizes the mean `share==contribution/endowment` by treatment and round.
-This yields a different result than the mean of the sum of contributions divided by the sum of endowments per treatment and round as the following table illustrates.
-
-```{r}
-main[round == 10, 
-     .(contribution = mean(contribution), 
-       endowment = mean(endowment), 
-       # share = mean(share), # same thing as the following line
-       share = mean(contribution/endowment),
-       sumContBySumEndo = mean(sum(contribution)/sum(endowment))), 
-     by = c("treatment", "round")] %>% 
-  kable()
-```
-
-```{r plotContributionsStudents, eval = FALSE}
-SUM <- main[treatment == "replication",
-            lapply(.SD, mean, na.rm = TRUE),
-            by = c("round", "student"),
-            .SDcols = "contribution"]
-
-SUM[,
-    sum := round(contribution/4)]
-
-upperLimit <- SUM$contribution %>% max() %>% round() + 10
-
-p1 <- ggplot(data = SUM, 
-             aes(x = round, y = contribution, fill = student, color = student, lty = student)) +
-  layout +
-  theme(legend.position="bottom") +
-  geom_line(show.legend=FALSE) +
-  geom_point() +
-  scale_x_continuous(name="",  breaks = 1:15) +
-  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-  labs(y = "Average Amount of Tokens contributed") +
-  scale_color_manual(values = colors) + 
-  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
-
-rm(list = c("SUM"))
-```
-
 ## Wealth Creation
@@
 To measure growth, we define a variable _stock_ which sums the endowments of all participants in a given group at the end of the round (that is, after the contributions have been made, multiplied and redistributed).
-@GACHTER2017 refer to that variable as "wealth" so we will do the same in what follows.
+@GMTV2017 refer to that variable as "wealth" so we will do the same in what follows.
 Before the start of round 1, wealth will be 80 in all groups by construction.
@@
 We next consider whether we were able to replicate GMTV's results with our data.
-Absolute contributions tended to be higher in @GACHTER2017 but end up at around the same level as in the replication due to a stark decline in contributions on the last round.
+Absolute contributions tended to be higher in @GMTV2017 but end up at around the same level as in the replication due to a stark decline in contributions on the last round.
 In terms of shares contributed both data sources exhibit a similar pattern: they decline and do not stabilize.
@@
 
-```{r summary3, results = "asis"}
+```{r summary3, results = "asis", warning = FALSE}
 
@@
 
-```{r}
+```{r eval = evalKable}
 main[treatment == "replication" & round == 10, 

### 2022-10-08 analysis/reports/rmd/Re-Calculation.Rmd
added "quarto" and "paper" (already deprecated) + no clue what happened otherwise. Its been a long time

---
title: "GMTV Data Preparation"
author:
  - name: Hauke Roggenkamp 
    url: https://github.com/Howquez
    affiliation: CLICCS
    affiliation_url: https://www.cliccs.uni-hamburg.de/
date: "`r Sys.Date()`"
bibliography: ../biblio.bib
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: false
    code_folding: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE)
```

# Objective

This document (re-)calculates some of the variables provided in @GMTV2017's online Appendix, namely:

- `WEALTH`, the variable used to measure growth,
- `MEAN`, the share of current endowments contributed and
- `GINI`, the group-level gini coefficient.

It also documents some examples to explain, why a (re-)calculation is needed.

# Setup

To do so, the following packages have to be installed and loaded. If the packages are not yet installed, you can do so using the command `install.packages("package_name")` for the respective packages before loading them in the following chunk.

```{r packages}
library(knitr)       # dynamic report generation (and tables via kable())
library(haven)       # read_dta
library(magrittr)    # pipe operator
library(data.table)  # fast and memory efficient data frames
library(DescTools)   # gini coefficient
```

Afterwards, the data needs to be loaded. This requires you to adjust the path to your personal directory.

```{r readData}
path <- "../../../data/gaechteretal/GMTV-data.dta" # adjust this

DT <- read_dta(path) %>% data.table()
```

Having loaded the data, you should have a data.table called `DT` with `r DT[, .N]` rows and `r DT %>% names() %>% length()` variables in your global environment. Because this document focuses on the first ten experiments, a new data.table called `GMTV` is defined as a subset of `DT`:

```{r subsetData}
GMTV <- DT[exp_num <= 10]
```

`GMTV` consists of `r GMTV[, .N]` rows and `r GMTV %>% names() %>% length()` columns.

# Wealth

The most important variable is used to measure growth shall be called `WEALTH`. This variable sums the endowments of all participants in a given group at the beginning of the following period. The data provided in the article's online appendix does not provide that variable.

This variable cannot be defined as the lag of endowments (`gpd`), because this would return a `NA` for the last period. For this reason, one needs to define the subjects' earnings within a period. These will be called `stock[0-3]` where `stock0` refers to a subject's own earnings and `stock[1-3]` reports the group members' earnings. These variables have to be calculated differently for punishment and no-punishment treatments.

```{r wealth1}
GMTV[punish == FALSE, stock0 := (tokens - putin + 1.5*sum/4) %>% ceiling()]
GMTV[punish == FALSE, stock1 := (other1 - pu1 + 1.5*sum/4) %>% ceiling()]
GMTV[punish == FALSE, stock2 := (other2 - pu2 + 1.5*sum/4) %>% ceiling()]
GMTV[punish == FALSE, stock3 := (other3 - pu3 + 1.5*sum/4) %>% ceiling()]
```

```{r wealth2}
GMTV[punish == TRUE, stock0 := (tokens - putin + 1.5*sum/4 - totallost) %>% ceiling()]
GMTV[punish == TRUE, stock1 := (other1 - pu1 + 1.5*sum/4 - totallost) %>% ceiling()]
GMTV[punish == TRUE, stock2 := (other2 - pu2 + 1.5*sum/4 - totallost) %>% ceiling()]
GMTV[punish == TRUE, stock3 := (other3 - pu3 + 1.5*sum/4 - totallost) %>% ceiling()]
```

Because subjects cannot run into debt, earnings < 0 need to be adjusted accordingly.

```{r wealth3}
GMTV[stock0 < 0, stock0 := 0]
GMTV[stock1 < 0, stock1 := 0]
GMTV[stock2 < 0, stock2 := 0]
GMTV[stock3 < 0, stock3 := 0]
```

With all group members' earnings, one can now calculate the group's `WEALTH` as follows:

```{r wealth4}
GMTV[, WEALTH := stock0 + stock1 + stock2 + stock3]
```

# Share of Current Endowment Contributed

The data provided in the article's online appendix provides a wrong measure of a subject's share of current endowment contributed called `mean` as it relies on a lagged endowment. To calculate the mean, the following STAT code was applied:

```
*tsset subj_id per
*gen mean=sum/l.gdp
```

The following table reports subject 111 in group 101 in ex experiment 1 over three periods. Both the `gdp` (that is, the sum of the group's endowments at the beginning of the period) as well as the sum (that is, the sum of the group's contributions) are group-level variables. Calculating the share `mean=sum/gdp` should yield $18/126=0.143$ in period 5 instead of $0.155$.

To get a subject's share of _current_ endowment contributed (that is, `MEAN`), one just has to calculate the corresponding fraction as follows:

```{r shareOfEndowmentsContributed}
GMTV[, MEAN := sum/gdp]
```

```{r tableMean, echo = FALSE}
GMTV[exp_num == 1 & gr_id == 101 & (per == 4 | per == 5 | per == 6) & subj_id == 111,
     .(exp_num,
       gr_id,
       per,
       subj_id,
       gdp,
       sum,
       mean = round(mean, digits = 3),
       MEAN = round(MEAN, digits = 3))] %>% 
  knitr::kable()
```

# Gini Coefficient

The gini coefficient provided in the original data relies on the subjects' endowments while it should rely on their earnings as the following table illustrates. It shows subject 111 once again over the course of the first three periods.

```{r tableGini1, echo = FALSE}

GMTV[exp_num == 1 & gr_id == 101 & per <=3 & subj_id == 111, # (per == 5 | per == 6 | per == 7)
     .(exp_num, 
       gr_id,
       per,
       subj_id,
       tokens,
       other1,
       other2,
       other3,
       gini = round(gini, digits = 3))] %>% 
  knitr::kable()
```

The Gini coefficient reported in the first row equals $0$ even though it should equal $0.168$. The second period's Gini coefficient should equal $0.146$ but is $0.168$ and so on.

Moreover, the Gini coefficient is a group-level variable and should be the same for all group members in a given period. The next table shows group 101 in period 5 and documents that the Gini coefficient differs among group members.

```{r tableGini2, echo = FALSE}
GMTV[exp_num == 1 & gr_id == 101 & per == 5,
     .(exp_num,
       gr_id,
       per,
       subj_id,
       tokens,
       other1,
       other2,
       other3,
       gini = round(gini, digits = 3))] %>% 
  knitr::kable()
```

For these reasons, the Gini coefficient needs to be re-calculated using  the `stock` variables calculated above (that is, each group member's earnings at the end of a period).

```{r gini}
GMTV[, 
     GINI := Gini(c(stock0, stock1, stock2, stock3)),
     by = .(exp_num, gr_id, subj_id, per)]
```

# Save Data

The updated `GMTV` now consists of `r GMTV[, .N]` rows and `r GMTV %>% names() %>% length()` columns. Some of them are displayed in the following table. The capitalized variables are the ones that were (re-)calculated in this document.

```{r showData, echo = FALSE}
GMTV[,
     .(WEALTH,
       gini = round(gini, digits = 3),
       GINI = round(GINI, digits = 3),
       gdp,
       sum,
       mean = round(mean, digits = 3),
       MEAN = round(MEAN, digits = 3)),
     keyby = c("exp_num",
               "gr_id",
               "per",
               "subj_id")] %>% 
  head(10) %>%
  knitr::kable()
```

You can store the data in your directory using the following code chunk:

```{r saveData}
# you may want to adjust the path to your directory

write.csv(GMTV,
          file = "../../../data/processed/GMTV-update.csv",
          fileEncoding = "UTF-8")

save(GMTV, 
     file = "../../../data/processed/GMTV-update.rda")
```

# References

### 2022-10-08 analysis/reports/rmd/createRooms.Rmd
added "quarto" and "paper" (already deprecated) + no clue what happened otherwise. Its been a long time

---
title: "Create Rooms for oTree Sessions"
description: |
  A new article created using the Distill format.
author:
  - name: Hauke Roggenkamp 
    url: https://github.com/Howquez
    affiliation: CLICCS
    affiliation_url: https://www.cliccs.uni-hamburg.de/
date: "`r Sys.Date()`"
bibliography: ../biblio.bib
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(stringi)
library(magrittr)
library(data.table)
```

This little script aims to write some random tokens that can be used to generate oTree [ROOMS](https://otree.readthedocs.io/en/latest/rooms.html) with persistent identifiers. These can be used to merge payoffs with participants.

```{r}
strings <- stri_rand_strings(n = 200,
                  length = 8,
                  pattern = "[A-Za-z0-9]") %>%
  data.table()

write.table(strings,
          file = "../../../oTree/_rooms/test.txt",
          col.names = FALSE,
          row.names = FALSE,
          quote = FALSE)
```

### 2022-10-08 analysis/R/renderPDF.R

@@ -14,4 +14,9 @@ rmarkdown::render(input = "reports/rmd/03_dataAnalyses.Rmd",
                   output_dir = "reports/pdf/",
                   output_file = "03_Analyses")
 
+rmarkdown::render(input = "reports/rmd/04_prettyAnalyses.Rmd",
+                  output_format = "pdf_document",
+                  output_dir = "reports/prettyReports/",
+                  output_file = "04_Analyses")
+
 print("PDFs rendered. You can find them in analysis/reports/pdf/. The processed data is stored in data/processed/.")

### 2022-10-09 analysis/quarto/paper.qmd
write results:replication

@@
                 axis.ticks = element_line(size = 0.25),
-                plot.caption = element_text(colour = "#555555"),
+                axis.title = element_text(size = 8),
+                legend.text = element_text(size = 8),
+                plot.caption = element_text(size = 6,
+                                            colour = "#555555"),
                 legend.title = element_blank()
@@
 
-***
-
-**Hintergrund:** Ich habe diesen [post](https://groups.google.com/g/esa-announce/c/-_2OmbkdxEk) gesehen und überlege meine Replikation entsprechend [hier](https://www.sciencedirect.com/journal/journal-of-behavioral-and-experimental-economics/about/call-for-papers#transparency-reproducibility-and-generalizability-of-behavioral-economics-experiments) einzureichen.
-Ist das realistisch?
-Wenn ja, wie soll man die Story aufziehen?
-Soll man denen mal schreiben und fragen, ob noch Platz ist?
-
-***
-
+# Introduction
 > "There are two possible articles you can write: (a) the article you planned to write when you designed your study or (b) the article that makes the most sense now that you have seen the results.
@@
 
-# Pre-registered GMTV Replication
-
-## Provision of the public good
+# Methodology
+
+In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific replication_ of one treatment arm of @GMTV2017's dynamic public good game.
+The pure replication re-analyzes the original data.
+[Appendix A](#A:-Pure-Replication) documents [errors I identified]() in the original paper.
+The scientific replication, where I utilize a different sample drawn from a different population in a different situation, is described in this section.
+
+## Procedure
+
+Participants entered the experiment at appointed times remotely from home.
+They first saw a welcome screen.
+After agreeing to the privacy policy, they could proceed to the instructions individually.
+Having read these instructions, each participant has also seen a demo-screen explaining the user interface.
+Before proceeding, they had to answer six comprehension questions correctly.
+Subsequently, they saw a waiting screen until they could be matched with three other participants, who have answered the comprehension questions correctly.
+Once matched, they were exposed to the decision screen over ten periods.
+At the end of the last period, participants saw results of all periods.
+Subsequently, they were exposed to a voluntary climate action, where they could donate (some of) their earnings to offset carbon dioxide.
+Subsequently, I elicited risk preferences [@HoltLaury2002] and finished with @GMTV2017's questionnaire.
+
+## Experimental Design
+
+As in the NOPUNISH 10 Period treatment arm of @GMTV2017, I ran sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of $N_i^1 = 20$ tokens, $T=10$ rounds, a private account with a return of $1$ and a group account with a return of $1.5$ ($\Rightarrow$ MPCR$\equiv \frac{1.5}{4}$), such that:
+
+$$
+N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
+$$
+Instead of receiving fresh endowments every period, participants receive one initial endowment only at the beginning of the first period.
+A participant's subsequent endowment equals her profit from the current period such that a decision in one period has consequences on her future endowments.
+For this reason, the game is described as a _dynamic_ public good game
+
+## Sample
+
+I recruited the participants from the so called _[HamburgPanel](https://www.wiso.uni-hamburg.de/forschung/forschungslabor/umfragelabor/aktuelle-umfragen/hamburgpanel.html)_ using HROOT [@hroot].
+The panel is provided by the University of Hamburg's Research Laboratory, which used a randomized last digits approach to build the panel while drawing from the population of citizens from Hamburg, Germany.
+
+Describe sample properties here.
+
+## Software
+
+The experiment was created using oTree [@oTree] and can be found on [GitHub](https://github.com/Howquez/coopUncertainty).
+
+# Results
+
+## Online Feasibility
+
+How did the participants, who have never participated in a online group experiment before, cope with the situation?
+
+```{r plotTime}
+#| fig.cap: Average Time Spent for each Contribution per Period
+
+N <- duration[, participant_code %>% unique() %>% length()]
+plotDT <- duration[app_name == "dPGG" & page_name == "dPGG_Decision",
+                   .(time_spent = time_spent %>% sum()),
+                   by = c("session_code", "participant_code", "page_index", "page_name")]
+
+plotDT[, round := seq(from = 1, to = 10), by = c("participant_code")]
+
+upperLimit <- plotDT[, time_spent %>% mean(), by = c("round")] %>% max()
+
+ggplot(data = summarySE(data = plotDT,
+                        measurevar = "time_spent",
+                        groupvars=c("round"),
+                        na.rm = FALSE,
+                        conf.interval = 0.95,
+                        .drop = TRUE),
+       mapping = aes(x = round, y = time_spent)) +
+  layout +
+  theme(legend.position="bottom") +
+  geom_line(show.legend=FALSE, color = cSecondary, lty=2) +
+  geom_errorbar(aes(ymin=time_spent-ci, ymax=time_spent+ci), width=.25, alpha = 0.5, color = cSecondary) +
+  geom_point(color = cSecondary) +
+  scale_x_continuous(name="",  breaks = 1:10) +
+  scale_y_continuous(limits = c(0, upperLimit + 10), expand = c(0, 0)) +
+  labs(y = "Time Passed in Seconds", caption = "Bars indicate 95% confidence intervals.") +
+  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
+```
+
+## Pre-registered GMTV Replication
+
+**Result 1.** _The `NOPUNISH 10` treatment of @GMTV2017 can be replicated because the replication data resemble the original data with respect to initial and final contributions, wealth and growth as well as inequality between and within groups._
+
+This is remarkable given the different sample and language, the different software and user interface  as well as the online setting during the COVID19 pandemic.
+
+### Contributions
 
@@
 
-First, we ask whether the samples differ with respect to their initial contributions to the public good.
+First, I ask whether the samples differ with respect to their initial contributions to the public good.
 Is our replication sample more pro-social than the original sample?
-Figure 1 reveals, that it is not.
+Figure 1 reveals that it is not.
 The distributions of both samples look fairly similar.
-Both samples contributed 10 tokens, that is, 50% of their endowments on average (median and mean).^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean contribution in first round of the game.] Moreover, both samples' initial contributions resemble initial contributions participants usually make in the standard game with partner matching.^[See Figure 3B in @fehrgaechter2000 (p.989), for instance.] In the dynamic game presented here, we are particularly interested in the subsequent periods because differences add up exponentially.
-Do the two groups remain similar?
+Both samples contributed 10 tokens, that is, 50% of their endowments on average (median and mean).^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean contribution in first round of the game.] Moreover, both samples' initial contributions resemble initial contributions participants usually make in the standard game with partner matching.^[See Figure 3B in @fehrgaechter2000 (p.989), for instance.] However, in the dynamic game presented here, we are particularly interested in the subsequent periods because differences add up exponentially.
+Do the two groups remain similar over the course of time?
 
 ```{r firstRoundViz}
+#| fig.cap: Individual contributions to the dynamic public good in the first period
+
 ggplot(data = R1[treatment != "noPunish15"],
@@
              lty = 1) +
-    labs(title = "Individual contributions to the dynamic public good in the first period", 
-       y = "", x = "Contributrions (Tokens)",
+    labs(title = "", 
+       y = "", x = "Initially Contributed Tokens",
        caption = "White lines indicate means (dashed line = replication sample).") +
   layout +
-  theme(legend.position = "bottom")
+  theme(legend.position = "top")
 ```
@@
 
-In particular, do the two samples' contributions follow the same pattern over time?
+In particular, do the two samples' contributions follow the same path over the 10 periods they played?
 The answer is _no_.
 Figure 2 illustrates that the samples make similar contributions at the beginning and the end of the game but behave differently in between.
-More precisely, the left panel--depicting the average contributions in absolute terms--shows that the original sample contributed substantially more than the replication sample _in all but the first and last rounds_.
+More precisely, the left panel--depicting the average contributions in absolute terms--shows that the original sample contributed substantially more than the replication sample _in all but the first and last periods_.
 For this reason, the original sample's behavior differs from the replication sample's behavior in two aspects: it contributes more and exhibits a considerable drop in the last period (whereas the replication sample's contributions flatten).
+
 Note that increasing contributions over time imply increasing endowments over time.
-Hence, increasing absolute contributions do not necessarily imply that participants contribute increasing shares of their endowments.
-The right panel in Figure 1 shows the share of overall endowments contributed over time where both samples exhibit a similar pattern: they decline and do not stabilize.
-The original sample's behavior differs from the replication sample's behavior in one aspect: it declined slower (to the same level in the last period).
+Hence, absolute contributions do not us much about the willingness to cooperate.
+For this reason, the right panel in Figure 2 shows the average _share of endowments contributed_ over time.
+Both samples exhibit a similar pattern: they decline and do not stabilize.
+However, both samples also differ with respect to one aspect: the replication sample's share of contributions declines faster.
 
@@
   layout +
-  theme(legend.position="bottom") +
+  theme(legend.position="top") +
   geom_line(show.legend=FALSE) +
@@
 p1 + p2 + plot_layout(guides = "collect") & 
-  theme(legend.position = "bottom")
+  theme(legend.position = "top")
 
@@
 
-Moreover, both samples' contributions resemble contributions participants usually make in the standard game with partner matching.^[The right panel is thus, comparable to the visualizations _and results_ in the standard game.
-See, for instance, Figure 1B in @fehrgaechter2000 (p.986).] In the dynamic game presented here, different paths lead to different levels of wealth -- even if they share the same start- and end-points.
-We are thus, more interested in the implications contributions have for wealth generation and growth.
-So, how do the samples compare with respect to wealth/income/endowments/stock?
-
-## Wealth Creation
-
-```{r summary1}
+Again, both samples' behavior resembles the contributions participants usually make in the standard game with partner matching: contributions equal approximately half of endowments in the very first period and decrease to around 10% of endowments by the last period.^[The right panel is thus, comparable to the visualizations _and results_ in the standard game.
+See, for instance, Figure 1B in @fehrgaechter2000 (p.986).] In the dynamic game presented here, however, different paths lead to different levels of wealth -- even if they share the same start- and end-points.
+I am thus, more interested in the contributions' implications for wealth generation and growth.
+
+### Wealth Creation
+
+```{r summaryWealth}
 #| results: asis
@@
 GMTV    <- main[treatment == "noPunish10" & round == 10, stock]
-
-rows <- sapply(X = list(replication, GMTV), FUN = NROW) %>% max()
-temp <- data.frame(replication = c(replication, rep(NA, rows - NROW(replication))),
-                   GMTV = c(GMTV, rep(NA, rows - NROW(GMTV))))
-
-# stargazer(temp,
-#           summary.stat = c("mean", "median","sd", "max", "min", "n"),
-#           type = type, 
-#           flip = TRUE, 
-#           header=FALSE)
 
@@
 
-How do the different contribution-paths translate to wealth?^[To measure growth, we define a variable called _stock_ which sums the endowments of all participants in a given group at the end of the round (that is, after the contributions have been made, multiplied and redistributed).] Given that the original sample contributed more in most of the periods, one would expect the respective groups to be considerably more wealthy.
-Figure 3 indicates that they tend to be insignificantly^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean stock in last round of the game.] richer.
-
-```{r stockDistributionViz}
+```{r wealthVariables}
 originalWealth    <- main[treatment == "noPunish10" & round == 10, mean(stock)]
 replicationWealth <- main[treatment == "replication" & round == 10, mean(stock)]
+```
+
+How do the different contribution-paths translate into wealth?^[To measure wealth and growth, I define a variable called _stock_ which sums the endowments of all participants in a given group at the end of the round (that is, after the contributions have been made, multiplied and redistributed).] Given that the original sample contributed more in most of the periods, one would expect the respective groups to be considerably more wealthy.
+Figure 3 indicates just that.
+The grey lines show that an average group in the original sample accumulated about `r round(originalWealth)` tokens.
+In contrast, an average group in the replication sample accumulated about `r round(replicationWealth)` tokens.
+This difference is insignificant at conventional levels^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean stock in last round of the game.] though.
+
+```{r stockDistributionViz}
+#| fig.cap: Groups' income at the end of the game
 
@@
              lty = 1) +
-    labs(title = "Groups' income at the end of the game", 
+    labs(title = "", 
        y = "", x = "Stock",
@@
   layout +
-  theme(legend.position = "bottom")
-```
-
-As the grey lines indicate, an average group in the original sample accumulated about `r round(originalWealth)` tokens.
-In contrast, an average group in the replication sample accumulated about `r round(replicationWealth)` tokens.
-However, none of the groups were efficient: the maximal wealth that can be reached in round 10 under full cooperation is approximately `r (80*1.5^10) %>% trunc()` tokens or `r (80*1.5^10 /20) %>% trunc()` Euro per group.
-
-```{r growthHeterogeneityViz}
-maxPath <- data.table(x = 1:10)
-maxPath[, y := 80*1.5^x]
-maxPath[, groupID := 42]
-ggplot(data = main,
-       mapping = aes(x = round, y = stock, color = treatment, by = groupID)) +
-  layout +
-  theme(legend.position="bottom") +
-  geom_line(alpha = 0.5) +
-  scale_x_continuous(breaks = 1:10) +
-  scale_y_continuous(limits = c(0, 4700),
-                       expand = c(0, NA)) +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("Original Sample", "Replication Sample")) +
-  geom_point(mapping = aes(x = 10, y = 4613), col = "#b5b5b5") +
-  annotate("text", x = 9.7, y = 4630,
-  label = "max", col = "#b5b5b5") +
-  geom_line(data = maxPath, mapping = aes(x = x, y =y), col = "#b5b5b5", lty = 2)
-```
-
-While there is clearly growth, groups do not realize the potential efficiency as the replication groups reach on average a level of `r main[treatment == "replication" & round == 10, mean(stock)] %>% trunc()` tokens out of `r (80*1.5^10) %>% trunc()` maximally possible or `r main[treatment == "replication" & round == 10, mean(stock)/(80*1.5^10)*100] %>% round(digits=1)`%.
-As in the original data, there is large heterogeneity with the richest group reaching `r main[treatment == "replication" & round == 10, max(stock)]` tokens whereas the poorest group ends up with `r main[treatment == "replication" & round == 10, min(stock)]` tokens.
-
-We thus, observe growth even for the poorest group and spot heterogeneity even within data sources.
-
-Figure 2 shows the dynamics of wealth over time.^[Unlike GMTV I present no median split but only the main results.]
-
-```{r plotStock}
-#| fig.cap: "Average wealth over time across treatments."
+  theme(legend.position = "top")
+```
+
+```{r overallGinis}
+rG <- main[round == 10 & treatment == "replication",
+           .(stock = sum(stock)),
+           by = groupID][, Gini(stock)] %>% round(digits = 2)
+
+oG <- main[round == 10 & treatment == "noPunish10",
+           .(stock = sum(stock)),
+           by = groupID][, Gini(stock)] %>% round(digits = 2)
+
+rSD <- main[round == 10 & treatment == "replication",
+            .(stock = sum(stock)),
+            by = groupID][, sd(stock)] %>% round(digits = 2)
+
+oSD <- main[round == 10 & treatment == "noPunish10",
+            .(stock = sum(stock)),
+            by = groupID][, sd(stock)] %>% round(digits = 2)
+```
+
+Although there clearly is growth, groups do not realize the maximal potential efficiency: under full cooperation, a group can accumulate at least `r (80*1.5^10) %>% trunc()` tokens or EUR `r (80*1.5^10 /20) %>% trunc()`.
+This is depicted in the left panel of Figure 4, where one can see the average wealth over time by sample.
+The panel illustrates for both samples that growth was continuous and surprisingly linear, given the exponential character of the game's design.
+To sum up, the contribution behavior differed between samples.
+In contrast, neither the eventual wealth nor the corresponding growth paths differed.
+Differences in contribution behavior did, thus, not translate in significantly different wealth outcomes.
+
+Why?
+Perhaps because the heterogeneity within samples and across groups has been too large to _detect_ a significant difference.
+The right panel of Figure 4 depicts heterogeneity: In the replication sample, the richest group earned `r a <- main[treatment == "replication" & round == 10, max(stock)]; a` tokens (which is about `r round(a/80, digits = 2)*100`% of the initial endowment) whereas the poorest group ends up with `r b <- main[treatment == "replication" & round == 10, min(stock)]; b` tokens (`r round(b/80, digits = 2)*100`%).
+More broadly, the replication sample is characterized by inequality between groups ($SD_{Replication} =$ `r rSD`).
+The same holds true for the original sample ($SD_{Original} =$ `r oSD`).
+Hence, the heterogeneity across groups does not differ between samples, which is remarkable because the replication sample was drawn from a more heterogeneous (non-convenience sample).
+Does it differ within groups?
+
+<!-- doch lieber Gini? statt SD reporten? -->
+
+```{r plotStock .column-page}
+
+# data
 STOCK <- main[,
@@
 
-upperLimit <- STOCKr$stock %>% max() %>% round() + 20
-
+# annotation
+maxPath <- data.table(x = 1:10)
+maxPath[, y := 80*1.5^x]
+maxPath[, treatment := "replication"]
+maxPath[, groupID := 42]
+
+# plot
 p1 <- ggplot(data = STOCK, 
              aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
-          layout +
-          theme(legend.position="bottom") +
-          # geom_vline(xintercept = 10, alpha = 0.66) +
-          geom_line(show.legend=FALSE) +
+  geom_line() +
   geom_point() +
-          # annotate("segment", x = 1, xend = 10, 
-          #          y = STOCK[round == 1 & treatment == "replication", stock],
-          #          yend = STOCK[round == 10 & treatment == "replication", stock],
-          #          colour = "black", lty = 2, alpha = 0.5) +
-          # annotate("segment", x = 1, xend = 10, 
-          #          y = STOCK[round == 1 & treatment == "noPunish10", stock],
-          #          yend = STOCK[round == 10 & treatment == "noPunish10", stock],
-          #          colour = "black", lty = 2, alpha = 0.5) +
-          scale_x_continuous(name="",  breaks = 1:10) +
-          scale_y_continuous(limits = c(0, 600), expand = c(0, 0)) +
-          labs(y = "Wealth") +
+  scale_x_continuous(breaks = 1:10) +
+  scale_y_continuous(limits = c(0, 4700), expand = c(0, 0)) +
+  labs(y = "Wealth", x = "Period") +
   scale_color_manual(values = c(cPrimary, cSecondary),
                      labels = c("Original Sample", "Replication Sample")) +
+  geom_point(mapping = aes(x = 10, y = 4613), col = "#b5b5b5") +
+  annotate("text", x = 9, y = 4630, size = 3,
+           label = "max", col = "#b5b5b5") +
+  geom_line(data = maxPath, mapping = aes(x = x, y =y), col = "#b5b5b5", lty = 2) +
   guides(fill = "none") +
-          theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
-
-p1
-```
-
-```{r plotStockLikeGMTV}
-#| eval: false
-
-p2 <- ggplot(data = STOCKr, 
-       aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
   layout +
-          theme(legend.position="bottom") +
-          # geom_vline(xintercept = 10, alpha = 0.66) +
-          geom_line(show.legend=FALSE) +
-          geom_point() +
-          scale_x_continuous(name="",  breaks = 1:10) +
-          scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-          labs(y = "Wealth (Rich)") +
-          scale_color_manual(values = colors)
-
-p3 <- ggplot(data = STOCKp, 
-       aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
+  theme(legend.position = "top") +
+  guides(lty = "none")
+```
+
+```{r growthHeterogeneityViz}
+#| fig.cap: Average wealth over time across samples.
+
+# plot
+p2 <- ggplot(data = main,
+       mapping = aes(x = round, y = stock, color = treatment, by = groupID)) +
+  geom_line(alpha = 0.5) +
+  scale_x_continuous(breaks = 1:10) +
+  scale_y_continuous(limits = c(0, 2000),
+                       expand = c(0, NA)) +
+  scale_color_manual(values = c(cPrimary, cSecondary),
+                     labels = c("Original Sample", "Replication Sample")) +
+  labs(y = "", x = "Period") +
   layout +
-          theme(legend.position="bottom") +
-          # geom_vline(xintercept = 10, alpha = 0.66) +
-          geom_line(show.legend=FALSE) +
-          geom_point() +
-          scale_x_continuous(name="",  breaks = 1:10) +
-          scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-          labs(y = "Wealth (Poor)") +
-          scale_color_manual(values = colors)
-
-(p1 | (p2 / p3)) + plot_layout(guides = "collect") & theme(legend.position = "bottom")
-
-rm(list = c("STOCK", "STOCKr", "STOCKp", "p1", "p2", "p3"))
-```
-
-The Figure illustrates that (in both data sources) growth was continuous and surprisingly linear, given the exponential character of the game's design.
-
-To sum up, our groups also tend to be poorer, and median wealth is higher in GMTV.
-The difference in mean ranks is not significant according to a two-sided ranksum test^[The two-sided rank sum test (comparing differences between data sources) yields a p-Value of `r rs1` for the mean wealth after the last round of the game.], however.
-
-To further assess the statistical significance of differences in means, we run OLS regressions where we regress wealth on a treatment dummy for _Replication_ (Table 3).
-These regressions show that differences in means are only significant for below median groups.
-This implies that the poor groups in our data are even less wealthy than GMTV's poor groups.
-
-```{r tableStock}
+  guides(col = "none")
+
+# assembling
+p1 + p2 + plot_layout(guides = "collect") & theme(legend.position = "top")
+```
+
+### Inequality
+
+```{r summaryGini}
 #| results: asis
 #| warning: false
-
-# create subsets
-main_all  <- main[round == 10]
-main_poor <- main[round == 10 & rich == FALSE]
-main_rich <- main[round == 10 & rich == TRUE]
-
-# create table
+#| fig.cap: "test"
+
 if(knitr::is_html_output()){
@@
 
-m1 <- lm(formula = stock ~ treatment, data = main_all)
-m2 <- lm(formula = stock ~ treatment, data = main_poor)
-m3 <- lm(formula = stock ~ treatment, data = main_rich)
-
-stargazer(m1, m2, m3,
-
-          column.labels = c("All", "Below median", "Above median"),
-          model.numbers = FALSE,
-          dep.var.labels = "Wealth",
-          header = FALSE,
-          covariate.labels = c("Replication"),
-
-          type = type, digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
-          )
-```
-
-As such, our results look familiar to GMTV's findings, where poor groups grew ever so slightly, while only rich groups experienced growth (that became exponential only after the 10th round).
+replication <- main[treatment == "replication" & round == 10, gini]
+GMTV    <- main[treatment == "noPunish10" & round == 10, gini]
+
+rs1 <- wilcox.test(replication, 
+                   GMTV,
+                   exact = FALSE)$p.value %>% 
+  round(digits = 4) %>% 
+  formatC(format = "f", 
+          digits = 4)
+
+```
+
+```{r giniVariables}
+originalGini    <- main[treatment == "noPunish10" & round == 10, mean(gini)] %>% round(digits = 2)
+replicationGini <- main[treatment == "replication" & round == 10, mean(gini)] %>% round(digits = 2)
+```
+
+Given the different samples and the possibility of endogenous growth--which essentially is the main feature of the game--I ask whether and how the inequality grows _within_ groups.
+Figure 5 illustrates that inequality did grow: at the end of the game, the original and the replication groups exhibit an average Gini coefficient of `r originalGini` and `r replicationGini`, respectively.^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean Gini coefficient in last round of the game.] Because every participant started with the same initial endowment (in _Period 0_, so to speak), every group started equally--with a Gini coefficient equaling zero.
+
+Figure 6 shows that this initial state of equality ended with the first period already: both samples exhibit a stark incline in inequality before the second period started.
+From then on, the respective Gini coefficients grew slowly but continuously -- for both samples.
+
+```{r giniDistributionViz}
+#| fig.cap: Groups' Gini coefficients (within groups) at the end of the game
+
+ggplot(data = main,
+       mapping = aes(x = gini, fill = treatment, lty = treatment)) +
+  geom_density(alpha = 0.5) +
+  scale_x_continuous(limits = c(0, 1),
+                       expand = c(0, NA)) +
+  scale_y_continuous(limits = c(0, NA),
+                       expand = c(0, NA)) +
+  scale_fill_manual(values = c(cPrimary, cSecondary),
+                    labels = c("Original Sample", "Replication Sample")) +
+  guides(lty = "none") +
+  geom_vline(xintercept = replicationGini,
+             col = "#000000", alpha = 0.5,
+             lty = 2) +
+  geom_vline(xintercept = originalGini,
+             col = "#000000", alpha = 0.5,
+             lty = 1) +
+    labs(title = "", 
+       y = "", x = "Stock",
+       caption = "Grey lines indicate means (dashed line = replication sample).") +
+  layout +
+  theme(legend.position = "top")
+```
+
+```{r}
+#| fig.cap: Average Gini coefficient (within groups) over time across samples
+#| 
+tmp <- main[,
+            lapply(.SD, mean, na.rm = TRUE),
+            by = c("round", "treatment"),
+            .SDcols = "gini"]
+
+GINI <- rbind(tmp, list(0, "replication", 0), list(0, "noPunish10", 0))
+
+ggplot(data = GINI, 
+             aes(x = round, y = gini, fill = treatment, color = treatment, lty = treatment)) +
+  geom_line() +
+  geom_point() +
+  scale_x_continuous(breaks = 0:10) +
+  scale_y_continuous(limits = c(0, 0.25), expand = c(0, 0)) +
+  labs(y = "Wealth", x = "Period") +
+  scale_color_manual(values = c(cPrimary, cSecondary),
+                     labels = c("Original Sample", "Replication Sample")) +
+  guides(fill = "none") +
+  layout +
+  theme(legend.position = "top") +
+  guides(lty = "none")
+```
+
+## Generalizability
+
+# Conclusion
+
+# Appendix
+
+## A: Pure Replication
+
+## B: Growth _and_ Inequality (exploratory)
+
+In contrast to @GMTV2017, I did not ask how rich and poor groups differ.
+Instead, I was wondering, whether equal groups are wealthier.
+More precisely, does the Gini coefficient correlate with growth and wealth creation?
+To answer that question, Figure 7 applies a median split showing equal and unequal groups' wealth over time.
+
+```{r plotStockByGini}
+#| fig.cap: Average wealth over time across treatments.
+
+# create equality indicator (just as highgdp in original data)
+median <- main[round == 10,
+               median(gini)]
+
+equalGroups <- main[round == 10 & gini > median,
+                    unique(groupID)]
+
+unequalGroups <- main[round == 10 & gini < median,
+                      unique(groupID)]
+
+main[groupID %in% equalGroups,
+     equal := TRUE]
+
+main[groupID %in% unequalGroups,
+     equal := FALSE]
+
+STOCKe <- main[equal == TRUE,
+               lapply(.SD, mean, na.rm = TRUE),
+               by = c("round", "treatment"),
+               .SDcols = "stock"]
+
+STOCKu <- main[equal == FALSE,
+               lapply(.SD, mean, na.rm = TRUE),
+               by = c("round", "treatment"),
+               .SDcols = "stock"]
+
+upperLimit <- 700
+
+p1 <- ggplot(data = STOCKe, 
+             aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
+  layout +
+  theme(legend.position="bottom") +
+  # geom_vline(xintercept = 10, alpha = 0.66) +
+  geom_line() +
+  geom_point() +
+  guides(lty = "none", fill = "none") +
+  scale_x_continuous(name="",  breaks = 1:10) +
+  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
+  labs(y = "Wealth (Equality)", x = "Period") +
+  scale_color_manual(values = c(cPrimary, cSecondary),
+                     labels = c("Original Sample", "Replication Sample"))
+
+p2 <- ggplot(data = STOCKu, 
+             aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
+  layout +
+  theme(legend.position="bottom") +
+  # geom_vline(xintercept = 10, alpha = 0.66) +
+  geom_line() +
+  geom_point() +
+  guides(lty = "none", fill = "none") +
+  scale_x_continuous(name="",  breaks = 1:10) +
+  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
+  labs(y = "Wealth (Inequality)", x = "Period") +
+  scale_color_manual(values = c(cPrimary, cSecondary),
+                     labels = c("Original Sample", "Replication Sample"))
+
+p1 + p2 + plot_layout(guides = "collect") & theme(legend.position = "bottom")
+
+rm(list = c("STOCKe", "STOCKu", "p1", "p2"))
+```

### 2022-10-09 analysis/quarto/paper.tex
write results:replication

@@
 \end{keyword}
-\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, sharp corners, enhanced]}{\end{tcolorbox}}\fi
+\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, frame hidden, breakable, sharp corners, enhanced, interior hidden]}{\end{tcolorbox}}\fi
 
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-\textbf{Hintergrund:} Ich habe diesen
-\href{https://groups.google.com/g/esa-announce/c/-_2OmbkdxEk}{post}
-gesehen und überlege meine Replikation entsprechend
-\href{https://www.sciencedirect.com/journal/journal-of-behavioral-and-experimental-economics/about/call-for-papers\#transparency-reproducibility-and-generalizability-of-behavioral-economics-experiments}{hier}
-einzureichen. Ist das realistisch? Wenn ja, wie soll man die Story
-aufziehen? Soll man denen mal schreiben und fragen, ob noch Platz ist?
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
@@
 
+\hypertarget{methodology}{%
+\section{Methodology}\label{methodology}}
+
+In the terminology of \citet{Hamermesh2007}, I ran both a \emph{pure} as
+well as a \emph{scientific replication} of one treatment arm of
+\citet{GMTV2017}'s dynamic public good game. The pure replication
+re-analyzes the original data.
+\protect\hyperlink{A:-Pure-Replication}{Appendix A} documents
+\href{}{errors I identified} in the original paper. The scientific
+replication, where I utilize a different sample drawn from a different
+population in a different situation, is described in this section.
+
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
+
+Participants entered the experiment at appointed times remotely from
+home. They first saw a welcome screen. After agreeing to the privacy
+policy, they could proceed to the instructions individually. Having read
+these instructions, each participant has also seen a demo-screen
+explaining the user interface. Before proceeding, they had to answer six
+comprehension questions correctly. Subsequently, they saw a waiting
+screen until they could be matched with three other participants, who
+have answered the comprehension questions correctly. Once matched, they
+were exposed to the decision screen over ten periods. At the end of the
+last period, participants saw results of all periods. Subsequently, they
+were exposed to a voluntary climate action, where they could donate
+(some of) their earnings to offset carbon dioxide. Subsequently, I
+elicited risk preferences \citep{HoltLaury2002} and finished with
+\citet{GMTV2017}'s questionnaire.
+
+\hypertarget{experimental-design}{%
+\subsection{Experimental Design}\label{experimental-design}}
+
+As in the NOPUNISH 10 Period treatment arm of \citet{GMTV2017}, I ran
+sessions with groups of four (\(i \in I=\{1,2,3,4\}\)), an initial
+endowment of \(N_i^1 = 20\) tokens, \(T=10\) rounds, a private account
+with a return of \(1\) and a group account with a return of \(1.5\)
+(\(\Rightarrow\) MPCR\(\equiv \frac{1.5}{4}\)), such that:
+
+\[
+N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
+\] Instead of receiving fresh endowments every period, participants
+receive one initial endowment only at the beginning of the first period.
+A participant's subsequent endowment equals her profit from the current
+period such that a decision in one period has consequences on her future
+endowments. For this reason, the game is described as a \emph{dynamic}
+public good game
+
+\hypertarget{sample}{%
+\subsection{Sample}\label{sample}}
+
+I recruited the participants from the so called
+\emph{\href{https://www.wiso.uni-hamburg.de/forschung/forschungslabor/umfragelabor/aktuelle-umfragen/hamburgpanel.html}{HamburgPanel}}
+using HROOT \citep{hroot}. The panel is provided by the University of
+Hamburg's Research Laboratory, which used a randomized last digits
+approach to build the panel while drawing from the population of
+citizens from Hamburg, Germany.
+
+Describe sample properties here.
+
+\hypertarget{software}{%
+\subsection{Software}\label{software}}
+
+The experiment was created using oTree \citep{oTree} and can be found on
+\href{https://github.com/Howquez/coopUncertainty}{GitHub}.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+\hypertarget{online-feasibility}{%
+\subsection{Online Feasibility}\label{online-feasibility}}
+
+How did the participants, who have never participated in a online group
+experiment before, cope with the situation?
+
+\begin{figure}
+
+{\centering \includegraphics{paper_files/figure-pdf/plotTime-1.pdf}
+
+}
+
+\caption{Average Time Spent for each Contribution per Period}
+
+\end{figure}
+
 \hypertarget{pre-registered-gmtv-replication}{%
-\section{Pre-registered GMTV
+\subsection{Pre-registered GMTV
 Replication}\label{pre-registered-gmtv-replication}}
 
-\hypertarget{provision-of-the-public-good}{%
-\subsection{Provision of the public
-good}\label{provision-of-the-public-good}}
+\textbf{Result 1.} \emph{The \texttt{NOPUNISH\ 10} treatment of
+\citet{GMTV2017} can be replicated because the replication data resemble
+the original data with respect to initial and final contributions,
+wealth and growth as well as inequality between and within groups.}
 
-First, we ask whether the samples differ with respect to their initial
+This is remarkable given the different sample and language, the
+different software and user interface as well as the online setting
+during the COVID19 pandemic.
+
+\hypertarget{contributions}{%
+\subsubsection{Contributions}\label{contributions}}
+
+First, I ask whether the samples differ with respect to their initial
 contributions to the public good. Is our replication sample more
-pro-social than the original sample? Figure 1 reveals, that it is not.
+pro-social than the original sample? Figure 1 reveals that it is not.
 The distributions of both samples look fairly similar. Both samples
@@
 usually make in the standard game with partner matching.\footnote{See
-  Figure 3B in \citet{fehrgaechter2000} (p.989), for instance.} In the
-dynamic game presented here, we are particularly interested in the
-subsequent periods because differences add up exponentially. Do the two
-groups remain similar?
+  Figure 3B in \citet{fehrgaechter2000} (p.989), for instance.} However,
+in the dynamic game presented here, we are particularly interested in
+the subsequent periods because differences add up exponentially. Do the
+two groups remain similar over the course of time?
 
-\includegraphics{paper_files/figure-pdf/firstRoundViz-1.pdf}
+\begin{figure}
 
-In particular, do the two samples' contributions follow the same pattern
-over time? The answer is \emph{no}. Figure 2 illustrates that the
-samples make similar contributions at the beginning and the end of the
-game but behave differently in between. More precisely, the left
-panel--depicting the average contributions in absolute terms--shows that
-the original sample contributed substantially more than the replication
-sample \emph{in all but the first and last rounds}. For this reason, the
-original sample's behavior differs from the replication sample's
-behavior in two aspects: it contributes more and exhibits a considerable
-drop in the last period (whereas the replication sample's contributions
-flatten). Note that increasing contributions over time imply increasing
-endowments over time. Hence, increasing absolute contributions do not
-necessarily imply that participants contribute increasing shares of
-their endowments. The right panel in Figure 1 shows the share of overall
-endowments contributed over time where both samples exhibit a similar
-pattern: they decline and do not stabilize. The original sample's
-behavior differs from the replication sample's behavior in one aspect:
-it declined slower (to the same level in the last period).
+{\centering \includegraphics{paper_files/figure-pdf/firstRoundViz-1.pdf}
+
+}
+
+\caption{Individual contributions to the dynamic public good in the
+first period}
+
+\end{figure}
+
+In particular, do the two samples' contributions follow the same path
+over the 10 periods they played? The answer is \emph{no}. Figure 2
+illustrates that the samples make similar contributions at the beginning
+and the end of the game but behave differently in between. More
+precisely, the left panel--depicting the average contributions in
+absolute terms--shows that the original sample contributed substantially
+more than the replication sample \emph{in all but the first and last
+periods}. For this reason, the original sample's behavior differs from
+the replication sample's behavior in two aspects: it contributes more
+and exhibits a considerable drop in the last period (whereas the
+replication sample's contributions flatten).
+
+Note that increasing contributions over time imply increasing endowments
+over time. Hence, absolute contributions do not us much about the
+willingness to cooperate. For this reason, the right panel in Figure 2
+shows the average \emph{share of endowments contributed} over time. Both
+samples exhibit a similar pattern: they decline and do not stabilize.
+However, both samples also differ with respect to one aspect: the
+replication sample's share of contributions declines faster.
 
@@
 
-Moreover, both samples' contributions resemble contributions
-participants usually make in the standard game with partner
-matching.\footnote{The right panel is thus, comparable to the
-  visualizations \emph{and results} in the standard game. See, for
-  instance, Figure 1B in \citet{fehrgaechter2000} (p.986).} In the
-dynamic game presented here, different paths lead to different levels of
-wealth -- even if they share the same start- and end-points. We are
-thus, more interested in the implications contributions have for wealth
-generation and growth. So, how do the samples compare with respect to
-wealth/income/endowments/stock?
+Again, both samples' behavior resembles the contributions participants
+usually make in the standard game with partner matching: contributions
+equal approximately half of endowments in the very first period and
+decrease to around 10\% of endowments by the last period.\footnote{The
+  right panel is thus, comparable to the visualizations \emph{and
+  results} in the standard game. See, for instance, Figure 1B in
+  \citet{fehrgaechter2000} (p.986).} In the dynamic game presented here,
+however, different paths lead to different levels of wealth -- even if
+they share the same start- and end-points. I am thus, more interested in
+the contributions' implications for wealth generation and growth.
 
 \hypertarget{wealth-creation}{%
-\subsection{Wealth Creation}\label{wealth-creation}}
+\subsubsection{Wealth Creation}\label{wealth-creation}}
 
-How do the different contribution-paths translate to wealth?\footnote{To
-  measure growth, we define a variable called \emph{stock} which sums
-  the endowments of all participants in a given group at the end of the
-  round (that is, after the contributions have been made, multiplied and
-  redistributed).} Given that the original sample contributed more in
-most of the periods, one would expect the respective groups to be
-considerably more wealthy. Figure 3 indicates that they tend to be
-insignificantly\footnote{The two-sided rank sum test (comparing
-  differences between samples) yields a p-Value of 0.1356 for the mean
-  stock in last round of the game.} richer.
-
-\includegraphics{paper_files/figure-pdf/stockDistributionViz-1.pdf}
-
-As the grey lines indicate, an average group in the original sample
-accumulated about 478 tokens. In contrast, an average group in the
-replication sample accumulated about 380 tokens. However, none of the
-groups were efficient: the maximal wealth that can be reached in round
-10 under full cooperation is approximately 4613 tokens or 230 Euro per
-group.
-
-\includegraphics{paper_files/figure-pdf/growthHeterogeneityViz-1.pdf}
-
-While there is clearly growth, groups do not realize the potential
-efficiency as the replication groups reach on average a level of 379
-tokens out of 4613 maximally possible or 8.2\%. As in the original data,
-there is large heterogeneity with the richest group reaching 1425 tokens
-whereas the poorest group ends up with 92 tokens.
-
-We thus, observe growth even for the poorest group and spot
-heterogeneity even within data sources.
-
-Figure 2 shows the dynamics of wealth over time.\footnote{Unlike GMTV I
-  present no median split but only the main results.}
+How do the different contribution-paths translate into
+wealth?\footnote{To measure wealth and growth, I define a variable
+  called \emph{stock} which sums the endowments of all participants in a
+  given group at the end of the round (that is, after the contributions
+  have been made, multiplied and redistributed).} Given that the
+original sample contributed more in most of the periods, one would
+expect the respective groups to be considerably more wealthy. Figure 3
+indicates just that. The grey lines show that an average group in the
+original sample accumulated about 478 tokens. In contrast, an average
+group in the replication sample accumulated about 380 tokens. This
+difference is insignificant at conventional levels\footnote{The
+  two-sided rank sum test (comparing differences between samples) yields
+  a p-Value of 0.1356 for the mean stock in last round of the game.}
+though.
 
@@
 
-{\centering \includegraphics{paper_files/figure-pdf/plotStock-1.pdf}
+{\centering \includegraphics{paper_files/figure-pdf/stockDistributionViz-1.pdf}
+
+}
+
+\caption{Groups' income at the end of the game}
+
+\end{figure}
+
+Although there clearly is growth, groups do not realize the maximal
+potential efficiency: under full cooperation, a group can accumulate at
+least 4613 tokens or EUR 230. This is depicted in the left panel of
+Figure 4, where one can see the average wealth over time by sample. The
+panel illustrates for both samples that growth was continuous and
+surprisingly linear, given the exponential character of the game's
+design. To sum up, the contribution behavior differed between samples.
+In contrast, neither the eventual wealth nor the corresponding growth
+paths differed. Differences in contribution behavior did, thus, not
+translate in significantly different wealth outcomes.
+
+Why? Perhaps because the heterogeneity within samples and across groups
+has been too large to \emph{detect} a significant difference. The right
+panel of Figure 4 depicts heterogeneity: In the replication sample, the
+richest group earned 1425 tokens (which is about 1781\% of the initial
+endowment) whereas the poorest group ends up with 92 tokens (115\%).
+More broadly, the replication sample is characterized by inequality
+between groups (\(SD_{Replication} =\) 336.06). The same holds true for
+the original sample (\(SD_{Original} =\) 393.58). Hence, the
+heterogeneity across groups does not differ between samples, which is
+remarkable because the replication sample was drawn from a more
+heterogeneous (non-convenience sample). Does it differ within groups?
+
+\begin{figure}
+
+{\centering \includegraphics{paper_files/figure-pdf/growthHeterogeneityViz-1.pdf}
+
+}
+
+\caption{Average wealth over time across samples.}
+
+\end{figure}
+
+\hypertarget{inequality}{%
+\subsubsection{Inequality}\label{inequality}}
+
+Given the different samples and the possibility of endogenous
+growth--which essentially is the main feature of the game--I ask whether
+and how the inequality grows \emph{within} groups. Figure 5 illustrates
+that inequality did grow: at the end of the game, the original and the
+replication groups exhibit an average Gini coefficient of 0.23 and 0.22,
+respectively.\footnote{The two-sided rank sum test (comparing
+  differences between samples) yields a p-Value of 0.6059 for the mean
+  Gini coefficient in last round of the game.} Because every participant
+started with the same initial endowment (in \emph{Period 0}, so to
+speak), every group started equally--with a Gini coefficient equaling
+zero.
+
+Figure 6 shows that this initial state of equality ended with the first
+period already: both samples exhibit a stark incline in inequality
+before the second period started. From then on, the respective Gini
+coefficients grew slowly but continuously -- for both samples.
+
+\begin{figure}
+
+{\centering \includegraphics{paper_files/figure-pdf/giniDistributionViz-1.pdf}
+
+}
+
+\caption{Groups' Gini coefficients (within groups) at the end of the
+game}
+
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics{paper_files/figure-pdf/unnamed-chunk-1-1.pdf}
+
+}
+
+\caption{Average Gini coefficient (within groups) over time across
+samples}
+
+\end{figure}
+
+\hypertarget{generalizability}{%
+\subsection{Generalizability}\label{generalizability}}
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
+
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
+\hypertarget{a-pure-replication}{%
+\subsection{A: Pure Replication}\label{a-pure-replication}}
+
+\hypertarget{b-growth-and-inequality-exploratory}{%
+\subsection{\texorpdfstring{B: Growth \emph{and} Inequality
+(exploratory)}{B: Growth and Inequality (exploratory)}}\label{b-growth-and-inequality-exploratory}}
+
+In contrast to \citet{GMTV2017}, I did not ask how rich and poor groups
+differ. Instead, I was wondering, whether equal groups are wealthier.
+More precisely, does the Gini coefficient correlate with growth and
+wealth creation? To answer that question, Figure 7 applies a median
+split showing equal and unequal groups' wealth over time.
+
+\begin{figure}
+
+{\centering \includegraphics{paper_files/figure-pdf/plotStockByGini-1.pdf}
 
@@
 
-The Figure illustrates that (in both data sources) growth was continuous
-and surprisingly linear, given the exponential character of the game's
-design.
-
-To sum up, our groups also tend to be poorer, and median wealth is
-higher in GMTV. The difference in mean ranks is not significant
-according to a two-sided ranksum test\footnote{The two-sided rank sum
-  test (comparing differences between data sources) yields a p-Value of
-  0.1356 for the mean wealth after the last round of the game.},
-however.
-
-To further assess the statistical significance of differences in means,
-we run OLS regressions where we regress wealth on a treatment dummy for
-\emph{Replication} (Table 3). These regressions show that differences in
-means are only significant for below median groups. This implies that
-the poor groups in our data are even less wealthy than GMTV's poor
-groups.
-
-\begin{table}[!htbp] \centering 
-  \caption{} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-4} 
-\\[-1.8ex] & \multicolumn{3}{c}{Wealth} \\ 
- & All & Below median & Above median \\ 
-\hline \\[-1.8ex] 
- Replication & $-$98.26 & $-$59.41$^{***}$ & $-$138.21 \\ 
-  & (101.21) & (18.32) & (166.67) \\ 
-  & & & \\ 
- Constant & 478.09$^{***}$ & 234.70$^{***}$ & 731.00$^{***}$ \\ 
-  & (75.58) & (13.99) & (124.73) \\ 
-  & & & \\ 
-\hline \\[-1.8ex] 
-Observations & 52 & 24 & 25 \\ 
-R$^{2}$ & 0.02 & 0.32 & 0.03 \\ 
-Residual Std. Error & 362.49 & 44.24 & 413.67 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
-
-As such, our results look familiar to GMTV's findings, where poor groups
-grew ever so slightly, while only rich groups experienced growth (that
-became exponential only after the 10th round).
-
   \bibliography{../biblio.bib}

### 2022-11-03 analysis/quarto/paper.qmd
many things happened here...

@@
 ---
-title: Growth and inequality in public good provision | an extended replication
+title: Growth and inequality in public good provision --- an extended replication
 author:
@@
 abstract: |
-  This is the abstract.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Vestibulum augue turpis, dictum non malesuada a, volutpat eget velit.
-Nam placerat turpis purus, eu tristique ex tincidunt et.
-Mauris sed augue eget turpis ultrices tincidunt.
-Sed et mi in leo porta egestas.
-Aliquam non laoreet velit.
-Nunc quis ex vitae eros aliquet auctor nec ac libero.
-Duis laoreet sapien eu mi luctus, in bibendum leo molestie.
-Sed hendrerit diam diam, ac dapibus nisl volutpat vitae.
-Aliquam bibendum varius libero, eu efficitur justo rutrum at.
-Sed at tempus elit.
+  You can find the most recent version of this paper [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.pdf). The abstract follows at later point.
 keywords: 
@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE, fig.width = 10, fig.height = 4)
+```
+
+```{r locale}
+#| include: false
+#| warning: false
+#| eval: false
+
+Sys.setlocale("LC_TIME","English United States")
 ```
@@
 pacman::p_load(magrittr, data.table, stringr, lubridate, glue, DescTools, haven,
-               stargazer, ggplot2, patchwork, MetBrewer, Rmisc)
+               stargazer, ggplot2, patchwork, MetBrewer, Rmisc, knitr)
 ```
@@
 colors <- met.brewer(name="Tam",n=7,type="discrete")
-cPrimary = "#ffd353"
-cSecondary = "#9f2d55"
-cInfo = "#34168"
+colors <- c("#F3B05C", "#1E4A75", "#65B5C0", "#AD5E21")
+# cPrimary = "#ffd353"
+# cSecondary = "#9f2d55"
+# cInfo = "#34168"
+cPrimary = "#F3B05C"
+cSecondary = "#1E4A75"
+cInfo = "#36BFA2"
 ```
@@
                     participant.time_started,
+                    participant._index_in_pages,
                     dPGG.1.player.contribution)]
@@
                   .(date = date %>% unique(),
+                    # weekday = date %>% unique() %>% lubridate::wday(label = TRUE),
                     time = hour %>% unique() %>% paste("00", sep = ":"),
                     showups = participant.time_started %>% length(),
-                    dropouts = dPGG.1.player.contribution %>% is.na() %>% sum(na.rm = FALSE)),
+                    dropouts = sum(participant._index_in_pages == 2),
+                    residuals = sum(is.na(dPGG.1.player.contribution) & participant._index_in_pages == 77)),
                   by = session.code]
@@
 meta[,
-     `:=`(participants = showups - dropouts,
-          observations = (showups - dropouts)/4)]
+     `:=`(participants = showups - dropouts - residuals,
+          observations = (showups - dropouts - residuals)/4)]
 
@@
 
-rm(list = c("full", "meta_long"))
+rm(list = c("meta_long"))
 ```
@@
 # create new data table with selected columns
-duration <- timeSpent[participant_code %in% DT$participant.code,
+duration <- timeSpent[session_code %in% meta$session.code, # participant_code %in% DT$participant.code,
                       .(
@@
 rm(list = c("CT", "DT", "GMTV", "GMTVCovariates", "GMTVFirstRound", 
-            "invitedStudents", "noPunish", "replication", "replicationCovariates",
+            "noPunish", "replication", "replicationCovariates",
             "replicationFirstRound", "subset"))
@@
 main[session.code == "d6jrsxnr" | treatment == "noPunish10",
+     student := TRUE]
+
+covs[, student := FALSE]
+covs[session.code == "d6jrsxnr" | treatment == "noPunish10",
      student := TRUE]
@@
 
-# Introduction
-> "There are two possible articles you can write: (a) the article you planned to write when you designed your study or (b) the article that makes the most sense now that you have seen the results.
-They are rarely the same, and the correct answer is (b)." [@bemwriting, p.
-171]
-
-# Methodology
-
-In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific replication_ of one treatment arm of @GMTV2017's dynamic public good game.
+# Introduction {#sec-intro}
+
+Today's actions are tomorrow's result.
+There are many settings in which current decisions affect future outcomes and with it, future decision spaces.
+Opting for environmental friendly policies today not only reduces carbon dioxide omissions but also helps us to reach the Paris climate targets tomorrow.
+Deferring these policies, the targets can be reached as well---but with less flexibility.
+Hence, today's actions (or the omission thereof) not only affect intermediate results but also the number of paths one can choose to reach certain goals.
+
+Standard public good games---although often intended to inform climate policies^[See @GKLS2020 [p.
+1] for numerous references.]---miss these temporal interdependencies because participants have the same set of actions in each period.
+A game implemented by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017] (hereafter, GMTV) as well as Stefan Große (2011, unpublished) incorporated interdependencies into a _dynamic_ public good game with students in Nottingham, England and Erfurt, Germany.
+
+Because their setting is more realistic, one wonders whether it is better suited to inform public policy.
+To answer this question, I replicated parts of GMTV's experiment with different samples.
+In addition, I observed the participant's behavior in voluntary climate actions (VCA).
+This yielded a setting similar to @GKLS2020's which allows me to analyze how behavior in the abstract game translates into real-world action across samples.
+
+I utilized an inexperienced sample that has not been exposed to interactive experiments before.
+Furthermore, I conducted the experiment online.
+This required me to make the experiment's software robust to minimize attrition.
+Because I observed metrics to assess the fluency and feasibility of online experiments, this study also serves as a case study like the one of @AGM2018.
+
+Taken together, this study makes three contributions.
+First, it replicates parts of GMTV's original experiment and highlights the importance of pure replications.
+Second, it shows that logistically complex online experiments are feasible for samples other than students or clickworkers.
+Third, it shows that findings from abstract games do not generalize well and even worse with the representative sample.
+After reporting the methods, this paper is organized along these findings.
+
+# Methodology {#sec-methods}
+
+In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific replication_ of one treatment of GMTV's dynamic public good game.
 The pure replication re-analyzes the original data.
 [Appendix A](#A:-Pure-Replication) documents [errors I identified]() in the original paper.
-The scientific replication, where I utilize a different sample drawn from a different population in a different situation, is described in this section.
-
-## Procedure
+The scientific replication, where I utilize a different sample drawn from a different population in a different situation, is described in the following sections.
+
+## Experimental Design {#sec-design}
+
+As in the NOPUNISH 10 Period treatment of GMTV, I ran sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of $N_i^1 = 20$ tokens, $T=10$ periods, a private account with a return of $1$ and a group account with a return of $1.5$ ($\Rightarrow$ MPCR$\equiv \frac{1.5}{4}$), such that:
+
+$$
+N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
+$$
+What makes the game _dynamic_?
+Instead of receiving fresh endowments every period, participants received one endowment only at the beginning of the first period.
+A participant's endowment in the second period is the wealth he or she accumulated in the first period.
+A participant's endowment in the third period is the wealth he or she accumulated in the first two periods.
+And so on.
+Hence, a decision in one period has consequences on future endowments and, ultimately, growth paths.
+For this reason, the game is described as a _dynamic_ public good game
+
+## Sample {#sec-sample}
+
+I recruited the participants from the so called _[HamburgPanel](https://www.wiso.uni-hamburg.de/forschung/forschungslabor/umfragelabor/aktuelle-umfragen/hamburgpanel.html)_ using HROOT [@hroot].
+The panel is provided by the University of Hamburg's Research Laboratory, which used a randomized last digits approach to build the panel while drawing from the population of citizens from Hamburg, Germany.
+Because the sample was exhausted at one point, I also recruited students from the University of Hamburg.
+
+At the time I conducted the experiment, the representative sample was not familiar with interactive experiments.
+In fact, I ran the first interactive group experiment with this sample.
+The students, in contrast, are used to this kind of experiments.
+Recruiting them, I excluded those who have participated in a public goods game before.
+As a consequence, nonnaiveté is unlikely to affect the validity of my experiment [@GoodmanPaolacci2017 p.
+204].
+
+Throughout this paper, I will compare results of my experiment with the results of GMTV's NOPUNISH 10 Period treatments.
+I am thus, referring to three different samples utilized at two points in time: the University of Nottingham's students (in late 2012), Hamburg's citizens and the University Hamburg's students (both in July 2021).
+@tbl-sample-properties shows how they compare with respect to a few properties.
+
+```{r sampleDifferences1, results = "asis", warning = FALSE}
+#| label: tbl-sample-properties
+#| tbl-cap: Sample Properties
+
+covs[, sample := "Nottingham Students"]
+covs[treatment == "replication" & student == TRUE, sample := "Hamburg Students"]
+covs[treatment == "replication" & student == FALSE, sample := "Hamburg Citizens"]
+covs[, sample := as.factor(sample)]
+# covs[, sample := ordered(sample, levels = c("Nottingham Students", "Hamburg Students", "Hamburg Citizens"))]
+
+m1 <- lm(formula = gender ~ sample, data = covs)
+m2 <- lm(formula = age ~ sample, data = covs)
+m3 <- lm(formula = switching_row ~ sample, data = covs)
+m4 <- lm(formula = donation ~ sample, data = covs)
+m5 <- lm(formula = pq11 ~ sample, data = covs)
+m6 <- lm(formula = pq12 ~ sample, data = covs)
+m7 <- lm(formula = pq13 ~ sample, data = covs)
+m8 <- lm(formula = pq14 ~ sample, data = covs)
+
+stargazer(m1, m2, m5, m6, m7, m8,
+
+          column.labels = c("female", "age",
+                            "trust", "meritocracy", "government", "equality") %>% str_to_title(),
+          model.numbers = FALSE,
+          dep.var.labels.include = FALSE,
+          header=FALSE,
+          intercept.bottom = FALSE,
+          covariate.labels = c("Hamburg Citizens", "Hamburg Students", "Nottingham Students"),
+
+          type = "latex", digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
+          )
+```
+
+```{r}
+# covs[, sample := ordered(sample, levels = c("Nottingham Students", "Hamburg Students", "Hamburg Citizens"))]
+```
+
+Describe sample properties here.
+
+## Software {#sec-software}
+
+The experiment was logistically complex for several reasons.
+First, the sample was inexperienced.
+Second, the experiment was interactive and synchronous.
+Third, the underlying game was dynamic and interdependent.
+This makes dropouts not only more likely, but also more expensive which is why dropouts were a major concern implementing the experiment.
+
+I chose oTree [@oTree] to implement the experiment because it is open-source, well documented and very flexible.
+Its [Bootstrap](https://getbootstrap.com/) (a powerful frontend toolkit) integration allowed me to make the graphical user interface interactive, appealing and easy to navigate.
+The [Highcharts library](https://www.highcharts.com/) made it easy to visualize results and to communicate dynamics.
+The oTree code snippets made it possible to handle dropouts, for instance, by replacing them with artificial bots (and informing the rest of the group thereof).
+Insofar, oTree served a good tool to consider the participants' user experience and thus, to make dropouts less likely.
+
+The experiment's source code be found on [GitHub](https://github.com/Howquez/coopUncertainty).^[https://github.com/Howquez/coopUncertainty]
+
+## Procedure {#sec-procedure}
 
@@
 Subsequently, they were exposed to a voluntary climate action, where they could donate (some of) their earnings to offset carbon dioxide.
-Subsequently, I elicited risk preferences [@HoltLaury2002] and finished with @GMTV2017's questionnaire.
-
-## Experimental Design
-
-As in the NOPUNISH 10 Period treatment arm of @GMTV2017, I ran sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of $N_i^1 = 20$ tokens, $T=10$ rounds, a private account with a return of $1$ and a group account with a return of $1.5$ ($\Rightarrow$ MPCR$\equiv \frac{1.5}{4}$), such that:
-
-$$
-N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
-$$
-Instead of receiving fresh endowments every period, participants receive one initial endowment only at the beginning of the first period.
-A participant's subsequent endowment equals her profit from the current period such that a decision in one period has consequences on her future endowments.
-For this reason, the game is described as a _dynamic_ public good game
-
-## Sample
-
-I recruited the participants from the so called _[HamburgPanel](https://www.wiso.uni-hamburg.de/forschung/forschungslabor/umfragelabor/aktuelle-umfragen/hamburgpanel.html)_ using HROOT [@hroot].
-The panel is provided by the University of Hamburg's Research Laboratory, which used a randomized last digits approach to build the panel while drawing from the population of citizens from Hamburg, Germany.
-
-Describe sample properties here.
-
-## Software
-
-The experiment was created using oTree [@oTree] and can be found on [GitHub](https://github.com/Howquez/coopUncertainty).
-
-# Results
-
-## Online Feasibility
-
-How did the participants, who have never participated in a online group experiment before, cope with the situation?
-
-```{r plotTime}
-#| fig.cap: Average Time Spent for each Contribution per Period
-
-N <- duration[, participant_code %>% unique() %>% length()]
-plotDT <- duration[app_name == "dPGG" & page_name == "dPGG_Decision",
-                   .(time_spent = time_spent %>% sum()),
-                   by = c("session_code", "participant_code", "page_index", "page_name")]
-
-plotDT[, round := seq(from = 1, to = 10), by = c("participant_code")]
-
-upperLimit <- plotDT[, time_spent %>% mean(), by = c("round")] %>% max()
-
-ggplot(data = summarySE(data = plotDT,
-                        measurevar = "time_spent",
-                        groupvars=c("round"),
-                        na.rm = FALSE,
-                        conf.interval = 0.95,
-                        .drop = TRUE),
-       mapping = aes(x = round, y = time_spent)) +
-  layout +
-  theme(legend.position="bottom") +
-  geom_line(show.legend=FALSE, color = cSecondary, lty=2) +
-  geom_errorbar(aes(ymin=time_spent-ci, ymax=time_spent+ci), width=.25, alpha = 0.5, color = cSecondary) +
-  geom_point(color = cSecondary) +
-  scale_x_continuous(name="",  breaks = 1:10) +
-  scale_y_continuous(limits = c(0, upperLimit + 10), expand = c(0, 0)) +
-  labs(y = "Time Passed in Seconds", caption = "Bars indicate 95% confidence intervals.") +
-  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
-```
-
-## Pre-registered GMTV Replication
-
-**Result 1.** _The `NOPUNISH 10` treatment of @GMTV2017 can be replicated because the replication data resemble the original data with respect to initial and final contributions, wealth and growth as well as inequality between and within groups._
-
-This is remarkable given the different sample and language, the different software and user interface  as well as the online setting during the COVID19 pandemic.
-
-### Contributions
+Subsequently, I elicited risk preferences [@HoltLaury2002] and finished with GMTV's questionnaire.
+
+While I tried to stick to GMTV's protocol as close as possible, I deviated in a few aspects.
+First, the instructions were German and also covered topics inherent to the online setting (dropouts and bots, for instance).
+Second, I used another software (oTree instead of zTree).
+Third, GMTV gave participants the opportunity to donate to _Doctors without Borders_ whereas we offered carbon dioxide offsets.
+Fourth, the graphical user interface looked different.
+
+# Results {#sec-results}
+
+## Pre-registered GMTV Replication {#sec-replication}
+
+The analyses in this section were pre-registered [@preregistration].
+I also pre-registered a RMarkdown file with the exact code I intended to use [here](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.] Even though I had to adjust a few lines of code, the main findings in the following section can also be replicated using the pre-registered code.
+
+### Contribution Behavior {#sec-contributions}
 
@@
 Is our replication sample more pro-social than the original sample?
-Figure 1 reveals that it is not.
+@fig-first-round reveals that it is not.
 The distributions of both samples look fairly similar.
@@
 ```{r firstRoundViz}
-#| fig.cap: Individual contributions to the dynamic public good in the first period
+#| fig-cap: Individual contributions to the dynamic public good in the first period
+#| label: fig-first-round
 
@@
 The answer is _no_.
-Figure 2 illustrates that the samples make similar contributions at the beginning and the end of the game but behave differently in between.
-More precisely, the left panel--depicting the average contributions in absolute terms--shows that the original sample contributed substantially more than the replication sample _in all but the first and last periods_.
+@fig-share-of-contributions illustrates that the samples make similar contributions at the beginning and the end of the game but behave differently in between.
+More precisely, the left panel--depicting the average contributions in absolute terms--shows that the original sample contributed substantially more than the replication sample _in all but the first and last period_.
 For this reason, the original sample's behavior differs from the replication sample's behavior in two aspects: it contributes more and exhibits a considerable drop in the last period (whereas the replication sample's contributions flatten).
@@
 Hence, absolute contributions do not us much about the willingness to cooperate.
-For this reason, the right panel in Figure 2 shows the average _share of endowments contributed_ over time.
-Both samples exhibit a similar pattern: they decline and do not stabilize.
+For this reason, the right panel in @fig-share-of-contributions shows the average _share of endowments contributed_ over time.
+Both samples exhibit a similar pattern: their share of endowments contributed declined and did not stabilize.
 However, both samples also differ with respect to one aspect: the replication sample's share of contributions declines faster.
@@
 ```{r plotShareOfContributions}
-#| fig.cap: "The average amount of tokens contributed over time in treatments."
+#| fig-cap: "The average amount of tokens contributed over time in treatments."
+#| label: fig-share-of-contributions
 
@@
 
-### Wealth Creation
+### Wealth Creation {#sec-wealth}
 
@@
 How do the different contribution-paths translate into wealth?^[To measure wealth and growth, I define a variable called _stock_ which sums the endowments of all participants in a given group at the end of the round (that is, after the contributions have been made, multiplied and redistributed).] Given that the original sample contributed more in most of the periods, one would expect the respective groups to be considerably more wealthy.
-Figure 3 indicates just that.
+@fig-stock-distribution indicates just that.
 The grey lines show that an average group in the original sample accumulated about `r round(originalWealth)` tokens.
@@
 ```{r stockDistributionViz}
-#| fig.cap: Groups' income at the end of the game
+#| fig-cap: Groups' income at the end of the game
+#| label: fig-stock-distribution
 
@@
 Although there clearly is growth, groups do not realize the maximal potential efficiency: under full cooperation, a group can accumulate at least `r (80*1.5^10) %>% trunc()` tokens or EUR `r (80*1.5^10 /20) %>% trunc()`.
-This is depicted in the left panel of Figure 4, where one can see the average wealth over time by sample.
+This is depicted in the left panel of @fig-growth-heterogeneity, where one can see the average wealth over time by sample.
 The panel illustrates for both samples that growth was continuous and surprisingly linear, given the exponential character of the game's design.
@@
 In contrast, neither the eventual wealth nor the corresponding growth paths differed.
-Differences in contribution behavior did, thus, not translate in significantly different wealth outcomes.
+Differences in contribution behavior did, thus, not translate to significantly different wealth outcomes.
 
@@
 Perhaps because the heterogeneity within samples and across groups has been too large to _detect_ a significant difference.
-The right panel of Figure 4 depicts heterogeneity: In the replication sample, the richest group earned `r a <- main[treatment == "replication" & round == 10, max(stock)]; a` tokens (which is about `r round(a/80, digits = 2)*100`% of the initial endowment) whereas the poorest group ends up with `r b <- main[treatment == "replication" & round == 10, min(stock)]; b` tokens (`r round(b/80, digits = 2)*100`%).
+The right panel of @fig-growth-heterogeneity depicts heterogeneity: In the replication sample, the richest group earned `r a <- main[treatment == "replication" & round == 10, max(stock)]; a` tokens (which is about `r round(a/80, digits = 2)*100`% of the initial endowment) whereas the poorest group ends up with `r b <- main[treatment == "replication" & round == 10, min(stock)]; b` tokens (`r round(b/80, digits = 2)*100`%).
 More broadly, the replication sample is characterized by inequality between groups ($SD_{Replication} =$ `r rSD`).
@@
 ```{r growthHeterogeneityViz}
-#| fig.cap: Average wealth over time across samples.
+#| fig-cap: Average wealth over time across samples.
+#| label: fig-growth-heterogeneity
 
@@
 
-### Inequality
+### Inequality {#sec-inequality}
 
@@
 Given the different samples and the possibility of endogenous growth--which essentially is the main feature of the game--I ask whether and how the inequality grows _within_ groups.
-Figure 5 illustrates that inequality did grow: at the end of the game, the original and the replication groups exhibit an average Gini coefficient of `r originalGini` and `r replicationGini`, respectively.^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean Gini coefficient in last round of the game.] Because every participant started with the same initial endowment (in _Period 0_, so to speak), every group started equally--with a Gini coefficient equaling zero.
-
-Figure 6 shows that this initial state of equality ended with the first period already: both samples exhibit a stark incline in inequality before the second period started.
+@fig-gini-distribution illustrates that inequality did grow: at the end of the game, the original and the replication groups exhibit an average Gini coefficient of `r originalGini` and `r replicationGini`, respectively.^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean Gini coefficient in last round of the game.] Because every participant started with the same initial endowment (in _Period 0_, so to speak), every group started equally--with a Gini coefficient equaling zero.
+
+@fig-ginit-time-series shows that this initial state of equality ended with the first period already: both samples exhibit a stark incline in inequality before the second period started.
 From then on, the respective Gini coefficients grew slowly but continuously -- for both samples.
@@
 ```{r giniDistributionViz}
-#| fig.cap: Groups' Gini coefficients (within groups) at the end of the game
+#| fig-cap: Groups' Gini coefficients (within groups) at the end of the game
+#| label: fig-gini-distribution
 
@@
     labs(title = "", 
-       y = "", x = "Stock",
+       y = "", x = "Gini Coefficient",
        caption = "Grey lines indicate means (dashed line = replication sample).") +
@@
 
-```{r}
-#| fig.cap: Average Gini coefficient (within groups) over time across samples
-#| 
+```{r giniOverTime}
+#| fig-cap: Average Gini coefficient (within groups) over time across samples
+#| label: fig-ginit-time-series
+
 tmp <- main[,
@@
 
-## Generalizability
-
-# Conclusion
-
-# Appendix
-
-## A: Pure Replication
-
-## B: Growth _and_ Inequality (exploratory)
-
-In contrast to @GMTV2017, I did not ask how rich and poor groups differ.
+**Result 1.** _The `NOPUNISH 10` treatment of GMTV can be replicated because the replication data resemble the original data with respect to initial and final contributions, wealth and growth as well as inequality._
+
+This is remarkable given the different sample and language, the different software and user interface as well as the online setting during the COVID19 pandemic.
+The result suggests that, by and large, the sum of these factors did not affect people’s preferences towards cooperation.
+
+## Online Feasibility {#sec-feasibility}
+
+How did the participants, who have never participated in an online group experiment before, cope with the situation?
+Moreover, did participants understand the unfamiliar setting they found themselves in?
+While the answer to the former question requires more thought, the answer to the latter simply is _yes_: `r 67` out of `r 44 + 67 + 5` answered with _"yes"_ when I asked them.
+Another `r 44` answered with _"rather yes"_ while nobody indicated that he or she did not understand the situation at all.
+To analyze how participants coped with the situation, I consider three additional metrics: selection into the experiment,  attrition as well as the time spent on each page.
+
+I first comment on the selection into the experiment: It was difficult to recruit the sample.
+The panel counted 1.209 non-students of which we were able to recruit `r main[student == FALSE, .N]` participants who finished the experiment---even though we varied the weekdays and timing of the sessions (which were conducted during a nation-wide lockdown with home office regime).
+For this reason, we also recruited students in the last session which explains the relatively large number of showups in @tbl-meta.
+Although I intended to refrain from the recruitment of students initially, this particular sub sample enabled me to investigate the generalizability of my results as I will discuss in  @sec-generalizability.
+Alternatively, I also could have contacted a market research institute to recruit additional participants within a week.
+I refrained from doing so to contrast students and the general population sample, however.
+
+```{r showMeta}
+#| label: tbl-meta
+#| tbl-cap: The Experimental Sessions' Meta Data
+
+meta %>% kable(col.names = names(meta) %>% 
+                 str_replace_all(pattern = "\\.",
+                                 replacement = " ") %>% 
+                 str_to_title()) #, caption = 'A table of the first 10 rows of the mtcars data.')
+```
+
+```{r plotTimeData}
+N <- duration[, participant_code %>% unique() %>% length()]
+plotDT <- duration[app_name == "dPGG" & page_name == "dPGG_Decision",
+                   .(time_spent = time_spent %>% sum()),
+                   by = c("session_code", "participant_code", "page_index", "page_name")]
+
+plotDT[, round := seq(from = 1, to = 10), by = c("participant_code")]
+
+upperLimit <- plotDT[, time_spent %>% mean(), by = c("round")] %>% max()
+
+tmp <- summarySE(data = plotDT,
+                 measurevar = "time_spent",
+                 groupvars=c("round"),
+                 na.rm = FALSE,
+                 conf.interval = 0.95,
+                 .drop = TRUE) %>% 
+  data.table()
+
+```
+
+Turning to the time spent on each page, I focus on the decision times in the dynamic public goods game as @Anderhub2001 did.
+How many seconds did the participants need to make a decision in each period of the game?
+Not too many.
+@fig-time-spent illustrates an intuitive pattern: The first decision took about `r tmp[round == 1, round(time_spent)]` seconds.
+The second decision--where participants first learned about the other group members' previous decisions--took longer (about `r tmp[round == 2, round(time_spent)]` seconds).
+Subsequently, decision times first declined and stabilized at `r tmp[round > 3, round(mean(time_spent))]` seconds.
+Importantly, decision times were so short that crosstalk, that is, communication through private channels--a common concern^[See, for instance, the discussion section in @AGM2018 [p.
+119].] in online experiments--was unlikely, especially because it would require the identification of other group members.^[There were only `r plotDT[page_index == 12 & time_spent > 60, .N]` participants (from all four sessions) who needed more than 60 seconds to make the second decision.]
+
+```{r plotTime}
+#| fig-cap: Average Time Spent for each Contribution per Period
+#| label: fig-time-spent
+
+ggplot(data = tmp,
+       mapping = aes(x = round, y = time_spent)) +
+  layout +
+  theme(legend.position="bottom") +
+  geom_line(show.legend=FALSE, color = cInfo, lty=2) +
+  geom_errorbar(aes(ymin=time_spent-ci, ymax=time_spent+ci), width=.25, alpha = 0.5, color = cInfo) +
+  geom_point(color = cInfo) +
+  scale_x_continuous(name="",  breaks = 1:10) +
+  scale_y_continuous(limits = c(0, upperLimit + 10), expand = c(0, 0)) +
+  labs(y = "Time Passed in Seconds", caption = "Bars indicate 95% confidence intervals.") +
+  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
+```
+
+Considering attrition, I find that it did not affect the interactive experiment at all.
+To elaborate, I differentiate between dropouts and residuals:  Participants who could not be matched to other group members are called residuals.
+Participants who intentionally left the experiment are called dropouts.
+Residuals did not participate in the experiment _by design_.
+Dropouts did not participate in the experiment _by choice_.
+Out of `r meta[, sum(showups)]` people who showed up, I count `r meta[, sum(residuals)]` residuals and `r meta[, sum(dropouts)]` dropouts.
+All of the residuals waited to be matched to a group unsuccessfully before they got paid one Euro for their patience.
+In contrast, all of the dropouts left while reading the instructions and before being matched to other group members.
+Moreover, they got no payment at all.
+Hence, attrition was no concern considering the dynamic public goods game or the expenses.
+
+**Result 2.** _Given the decision times and the fluent procedure, attrition was as negligible as it is in physical laboratories---where (a) not every invited person shows up and (b) a number of participants divisible by the group size is required as well._
+
+## Generalizability {#sec-generalizability}
+
+<!--
+> "There are two possible articles you can write: (a) the article you planned to write when you designed your study or (b) the article that makes the most sense now that you have seen the results.
+They are rarely the same, and the correct answer is (b)." [@bemwriting, p.
+171]
+-->
+
+```{r}
+R1covs <- covs[, .(participant.code,
+                   donation = donation * 20 ,
+                   donationShare = (donation * 20) / payoff * 100,
+                   payoff)]
+temp <- R1[R1covs, on = .(participant.code = participant.code)][treatment == "replication"]
+temp[, contributionShare := ownContribution/20 * 100]
+```
+
+@GKLS2020 asked how much can we learn about voluntary climate action from the behavior in public goods games.
+Using a similar strategy, I answer the question for _dynamic_ public goods games: _Not much_.
+Overall, there seems to be no association between choices in the voluntary climate action and the first period in the dynamic public goods game.
+@fig-scatter-generalizability shows a scatter plot of realized choices, with the percentage of endowment spent by each participant in the first period of the game on the x-axis and that spent in the VCA on the y-axis.
+In addition, the figure contains a fitted line of a linear model whose slope is indistinguishable from zero.
+No matter how much the participants contributed in the first round, they spent, on average, about `r temp[, round(mean(donationShare))]`% of their income on the VCA.
+
+```{r}
+#| fig-cap: Scatter plot of average contributions in the dPGG and real giving task.
+#| label: fig-scatter-generalizability
+#| fig.height: 6
+
+p1 <- ggplot(data = temp[, 
+                   .(vca = donation / payoff * 100,
+                     dpgg = ownContribution / 20 * 100)],
+       mapping = aes(y = vca, x = dpgg)) +
+  annotate("segment", x = 0, xend = 100,
+                   y = 0,
+                   yend = 100,
+                   colour = "black", lty = 2, alpha = 0.5) +
+  geom_point(alpha = 0.5, col = cInfo, size = 2) +
+  geom_smooth(method = "lm", formula = y~x, se = FALSE,
+              col = cInfo) +
+  scale_x_continuous(limits = c(0, 105),
+                     expand = c(0, NA)) +
+  scale_y_continuous(limits = c(0, 105),
+                     expand = c(0, NA)) +
+  labs(y = "VCA: Percentage of endowment donated",
+       x = "Percentage of endowment contributed in period 1") +
+  layout
+
+p2 <- ggplot(data = temp[student == FALSE, 
+                   .(vca = donation / payoff * 100,
+                     dpgg = ownContribution / 20 * 100)],
+       mapping = aes(y = vca, x = dpgg)) +
+  annotate("segment", x = 0, xend = 100,
+                   y = 0,
+                   yend = 100,
+                   colour = "black", lty = 2, alpha = 0.5) +
+  geom_point(alpha = 0.5, col = cInfo, size = 2) +
+  geom_smooth(method = "lm", formula = y~x, se = FALSE,
+              col = cInfo) +
+  scale_x_continuous(limits = c(0, 105),
+                     expand = c(0, NA)) +
+  scale_y_continuous(limits = c(0, 105),
+                     expand = c(0, NA)) +
+  labs(y = "VCA: Percentage of endowment donated",
+       x = "General pop.: Percentage of endowment contributed in period 1") +
+  layout
+
+p3 <- ggplot(data = temp[student == TRUE, 
+                   .(vca = donation / payoff * 100,
+                     dpgg = ownContribution / 20 * 100)],
+       mapping = aes(y = vca, x = dpgg)) +
+  annotate("segment", x = 0, xend = 100,
+                   y = 0,
+                   yend = 100,
+                   colour = "black", lty = 2, alpha = 0.5) +
+  geom_point(alpha = 0.5, col = cInfo, size = 2) +
+  geom_smooth(method = "lm", formula = y~x, se = FALSE,
+              col = cInfo) +
+  scale_x_continuous(limits = c(0, 105),
+                     expand = c(0, NA)) +
+  scale_y_continuous(limits = c(0, 105),
+                     expand = c(0, NA)) +
+  labs(y = "VCA: Percentage of endowment donated",
+       x = "Students: Percentage of endowment contributed in period 1") +
+  layout
+
+p1 / (p2 + p3)
+```
+
+Does this result hold true if one zooms in and inspects the two samples separately?
+Yes.
+Even though the general population sample is a little more consistent than the student sample, both are contributing more in the abstract game than in the VCA.
+@fig-kernel-generalizability shows distributions of contributions across both choices for both samples.
+The left panels illustrate the behavior of the general population sample.
+The right panels illustrate the behavior of the general population sample.
+The top panels show the behavior in the VCA.
+The bottom panels show the behavior in first period of the game.
+A visual inspection shows that (a) both samples behaved similarly in the first period of the game but (b) different (p =
+`r summary(lm(formula = donationShare ~ student, data = temp))$coefficients[2,4] %>% round(digits = 2)`) in the VCA.
+Furthermore, (c) the behavior in the first period of the experiment predicts the general population sample's behavior in the VCA worse than student sample's behavior (p =
+`r summary(lm(formula = contributionShare ~ donationShare + student + donationShare*student, data = temp))$coefficients[4,4] %>% round(digits = 2)`).
+Finally, (4) contributions in the abstract public good game are higher than contributions to the real public good of climate change mitigation.
+
+```{r vizGeneralizability}
+#| fig-cap: Kernel distributions of contributions across tasks and subject pools.
+#| label: fig-kernel-generalizability
+#| fig.height: 6
+
+# viz wrapper
+plotShares <- function(stud = FALSE,
+                       var  = "donationShare",
+                       col  = cPrimary,
+                       xlab = "",
+                       ylab = ""){
+
+  dt <- temp[student == stud, .(x = get(var))]
+
+  model <- lm(x ~ 1, dt)
+  ci1 <- confint(model, level=0.95)[1]
+  ci2 <- confint(model, level=0.95)[2]
+
+  ggplot(data = dt,
+         mapping = aes(x = x)) +
+    annotate("rect", 
+             xmin = ci1, xmax = ci2, 
+             ymin  =0, ymax = Inf, 
+             alpha = 0.33) +
+    geom_density(alpha = 0.75,
+                 fill = col) +
+    scale_x_continuous(limits = c(0, 100),
+                       expand = c(0, NA)) +
+    scale_y_continuous(limits = c(0, NA),
+                       expand = c(0, NA)) +
+    geom_vline(xintercept = dt[,mean(x, na.rm = TRUE)],
+               lty = 2) +
+    labs(x = xlab,
+         y = ylab) +
+  layout
+}
+
+p1 <- plotShares(stud = FALSE, col = cPrimary,   var = "donationShare", ylab = "Density in VCA")
+p2 <- plotShares(stud = FALSE, col = cPrimary,   var = "contributionShare", 
+                 xlab = "Share of general pop. contributions", ylab = "Density in Experiment (round 1)")
+p3 <- plotShares(stud = TRUE,  col = cSecondary, var = "donationShare")
+p4 <- plotShares(stud = TRUE,  col = cSecondary, var = "contributionShare", xlab = "Share of students' contributions")
+
+patchwork <- (p1 / p2) | (p3 / p4)
+patchwork + plot_annotation(caption = "Dashed vertical lines indicate the respective means.\nShaded areas indicate 95% confidence intervals.")
+
+rm(list = c("R1covs", "p1", "p2", "p3", "p4", "patchwork"))
+```
+
+**Result 3.** _Existing evidence overestimates the willingness to contribute to real public goods. This holds true for more representative samples and---to a lower degree---for student samples._
+
+# Conclusion {#sec-conclusion}
+
+The goal of the experiment was to replicate specific experiments of GMTV in an online setting using a general population sample.
+The results suggest that it is important to replicate experiments---both purely and scientifically [@Hamermesh2007 p.
+716]---before drawing conclusions about generalizability.
+
+The three most important findings are as follows: First, the contribution behavior in my experiment is statistically similar to the behavior reported in the original study.
+Consequently, the outcomes growth and inequality are similar as well.
+Second, the online experiment proceeded fluently such that dropouts were no concern.
+Third, contribution behavior in my abstract setting is, if anything, only weakly linked to behavior in the real world.
+This lack of generalizability can be counteracted, but not be solved, by the use of more representative samples.
+
+The significance of the first result is that similar procedures led to replicable findings under different circumstances across two different samples.
+The second result is of methodological importance: It highlights that even logistically complex experiments can be conducted online with---not only with clickworkers but also with a true general population sample.
+The third result questions whether recruiting from more representative samples is worth the efforts because it decreases transferability of results to the real world---at least, a little.
+
+{{< pagebreak >}}
+
+# A: Pure Replication {.appendix}
+
+This section comments on two errors as well as a misconception I found in the original data.^[The data can be found in the supplementary materials they provide in their [online appendix](https://www.sciencedirect.com/science/article/pii/S0047272717300361#s0115).] Before I proceed to explain this in more detail I would like to say that the results of the original paper still hold after the error is fixed and that the authors responded kindly and quickly, showing an interest in solving the issue.
+In fact, some explanations in this section stem from input provided by the authors.
+
+### Error 1: The Gini coefficient
+
+The Gini coefficient is wrongly computed in some periods for some group members.
+The authors found that this happened whenever two group members had exactly the same endowment because the program failed to rank these group members for further calculations.
+
+```{r readGMTVagain}
+GMTV <- read_dta(file="../../data/gaechteretal/GMTV-data.dta") %>% data.table()
+noPunish10 <- GMTV[exp_num == 5 | exp_num == 8 | exp_num == 9]
+# noPunish10 <- GMTV[longgame == 0 & punish == 0 & exp_num <= 10]
+```
+
+@tbl-gini-error illustrates this problem.
+It shows group 101 in period 5 and documents that the Gini coefficient differs among group members.
+According to the authors, the Gini coefficient should equal `GINI=``r GINI <- GMTV[exp_num == 1 & gr_id == 101 & per == 5, tokens %>% Gini() %>% round(digits = 3)]; GINI` for all subjects in the group.
+Instead, participant `112` and `113` who have an equal endowment deviate from that value.
+Importantly, the `DescTools::Gini()` function in the statistical software `R` does not yield this error, which is why I use that function for my calculations using both my as well as the original data.
+
+```{r}
+#| label: tbl-gini-error
+#| tbl-cap: Subset of Data illustrating the Gini Coefficient's Error
+
+GMTV[exp_num == 1 & gr_id == 101 & per == 5,
+     .(exp_num,
+       gr_id,
+       per,
+       subj_id,
+       tokens,
+       other1,
+       other2,
+       other3,
+       gini = round(gini, digits = 3),
+       GINI = GINI
+       )] %>% 
+  knitr::kable()
+```
+
+### Error 2: The share of endowments contributed
+
+The original data provides a wrong measure of the share of endowments contributed (`mean`) because it relies on a lagged endowment (`gdp`).
+More precisely, the authors used the following STATA code for their calculations:
+
+```
+*tsset subj_id per
+*gen mean=sum/l.gdp
+```
+
+@tbl-mean-error reports participant 111 in group 101 in experiment 1 over three periods.
+Both the `gdp` (that is, the sum of the group’s endowments at the beginning of the period) as well as the `sum` (that is, the sum of the group’s contributions) are group-level variables.
+
+```{r}
+#| label: tbl-mean-error
+#| tbl-cap: Subset of Data illustrating the Means's Error
+
+GMTV[, MEAN := sum/gdp]
+
+GMTV[exp_num == 1 & gr_id == 101 & (per == 4 | per == 5 | per == 6) & subj_id == 111,
+     .(exp_num,
+       gr_id,
+       per,
+       subj_id,
+       gdp,
+       sum,
+       mean = round(mean, digits = 3),
+       MEAN = round(MEAN, digits = 3)
+       )] %>% 
+  knitr::kable()
+```
+
+Calculating the share as `MEAN=sum/gdp` solves the problem and yields $\frac{18}{126}=0.143$ in period 5.
+I thus, used this proposed definition for all my calculations using both my as well as the original data.
+
+### The misconception: Timing
+
+The authors wrote a note stating that the Gini coefficient as well as the wealth in the paper always refer to the situation at the start of a period and that they clarify this because the paper (last paragraph at the bottom of page 5), says that wealth is defined as the endowment at the beginning of the following period.
+Furthermore, they write that this error came about as they switched between these two definitions during the course of revising the paper.
+
+I argue that it makes more sense to calculate the variables as they state in the paper.
+More precisely, I think that the wealth at the _beginning_ of a period is less interesting than the wealth at the _end_ of a period for two reasons: First, there is no need for such a variable because it already exists (the endowment).
+Second, this definition yields a value that is determined by the design of the game but misses an important outcome at the end of the game.
+To illustrate this, note that the wealth would be defined as four times the initial endowment in period 1.
+Also note that the very last value would equal the wealth at the beginning of the last period and says nothing about the outcome of that period.
+Because the contributions often drop in the last period, this outcome is of particular interest (yet, not represented in the data).
+Moreover, this definition of wealth yields more informative values to calculate the Gini coefficient for the same reasons: We know that the Gini coefficient is zero _before_ the participants made any decision by design.
+We do no know the inequality at the very end of the game---and the current definition does not tell us.
+
+For these reasons, I define wealth and inequality measures as the outcomes of a period for all of my calculations using both my as well as the original data.^[Accordingly, the definition of `GINI` I provide in @tbl-gini-error is not the definition I used to calculate the current period's Gini coefficient but the previous period's Gini coefficient.]
+
+{{< pagebreak >}}
+
+<!--
+# B: TITLE (exploratory) {.appendix}
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Donec suscipit eleifend felis et faucibus.
+Curabitur nisl risus, tincidunt ut hendrerit sed, sollicitudin eget tortor.
+Curabitur tortor elit, finibus a commodo eget, auctor vel dui.
+Ut convallis, felis in commodo bibendum, ligula neque hendrerit eros, eu eleifend libero ligula pretium dui.
+Nullam blandit a tellus vitae suscipit.
+Donec ac justo vehicula elit tincidunt mollis nec ac lectus.
+Nunc dignissim sem eu felis consequat, id euismod ante imperdiet.
+Mauris quis ex ante.
+
+Nulla elementum laoreet libero nec consequat.
+Donec blandit, tellus id feugiat viverra, lectus tellus sollicitudin ipsum, ut venenatis nunc mauris ut arcu.
+Donec mi eros, ullamcorper aliquet varius non, cursus vel lorem.
+Integer feugiat dui sapien, ac porta lacus porta sit amet.
+Aliquam interdum dictum tempor.
+Quisque bibendum feugiat scelerisque.
+Sed eu purus eu est ullamcorper bibendum.
+
+Donec efficitur magna malesuada tortor feugiat tristique.
+Sed porttitor, quam at vulputate placerat, elit magna posuere est, a eleifend lacus magna ac nunc.
+Quisque sit amet arcu mattis, malesuada mauris et, aliquam libero.
+Fusce viverra sed dolor a ullamcorper.
+Aliquam in ligula neque.
+In maximus nisl id ante vehicula, et euismod ante feugiat.
+Suspendisse et dui lectus.
+Ut euismod ultrices mi eu lacinia.
+
+```{r firstRoundVizAppendix}
+
+d1 <- ggplot(data = R1[treatment == "replication"],
+       mapping = aes(x = ownContribution, fill = student, lty = student)) +
+  geom_density(alpha = 0.5) +
+  scale_x_continuous(limits = c(0, 20),
+                       expand = c(0, NA)) +
+  scale_y_continuous(limits = c(0, 0.1),
+                       expand = c(0, NA)) +
+  scale_fill_manual(values = c(cPrimary, cSecondary),
+                    labels = c("General Population Sample", "Student Sample")) +
+  guides(lty = "none") +
+  geom_vline(xintercept = R1[treatment == "replication", 
+                             mean(ownContribution)],
+             col = "#FFFFFF",
+             lty = 2) +
+  geom_vline(xintercept = R1[treatment == "noPunish10", 
+                             mean(ownContribution)],
+             col = "#FFFFFF",
+             lty = 1) +
+    labs(title = "", 
+       y = "", x = "Initially Contributed Tokens") +
+  layout +
+  theme(legend.position = "top")
+```
+
+```{r stockDistributionVizAppendix}
+
+populationWealth <- main[treatment == "replication" & student == FALSE & round == 10,
+                         mean(stock)]
+studentWealth    <- main[treatment == "replication" & student == TRUE & round == 10,
+                         mean(stock)]
+
+d2 <- ggplot(data = main[treatment == "replication"],
+       mapping = aes(x = stock, fill = student, lty = student)) +
+  geom_density(alpha = 0.5) +
+  scale_x_continuous(limits = c(0, NA),
+                       expand = c(0, NA)) +
+  scale_y_continuous(limits = c(0, NA),
+                       expand = c(0, NA)) +
+  scale_fill_manual(values = c(cPrimary, cSecondary),
+                    labels = c("General Population Sample", "Student Sample")) +
+  guides(lty = "none") +
+  geom_vline(xintercept = studentWealth,
+             col = "#000000", alpha = 0.5,
+             lty = 2) +
+  geom_vline(xintercept = populationWealth,
+             col = "#000000", alpha = 0.5,
+             lty = 1) +
+    labs(title = "", 
+       y = "", x = "Stock") +
+  layout +
+  theme(legend.position = "top")
+```
+
+```{r giniDistributionVizAppendix}
+
+populationGini    <- main[treatment == "replication" & student == FALSE & round == 10,
+                        mean(gini)] %>% round(digits = 2)
+studentGini <- main[treatment == "replication" & student == TRUE & round == 10,
+                        mean(gini)] %>% round(digits = 2)
+
+d3 <- ggplot(data = main[treatment == "replication"],
+       mapping = aes(x = gini, fill = student, lty = student)) +
+  geom_density(alpha = 0.5) +
+  scale_x_continuous(limits = c(0, 1),
+                       expand = c(0, NA)) +
+  scale_y_continuous(limits = c(0, NA),
+                       expand = c(0, NA)) +
+  scale_fill_manual(values = c(cPrimary, cSecondary),
+                    labels = c("General Population Sample", "Student Sample")) +
+  guides(lty = "none") +
+  geom_vline(xintercept = studentGini,
+             col = "#000000", alpha = 0.5,
+             lty = 2) +
+  geom_vline(xintercept = populationGini,
+             col = "#000000", alpha = 0.5,
+             lty = 1) +
+    labs(title = "", 
+       y = "", x = "Gini Coefficient") +
+  layout +
+  theme(legend.position = "top")
+```
+
+```{r assembleAppendixPlots}
+#| fig-cap: Kernel Density Plots
+#| label: fig-multiple-distributions
+
+patchwork <- d1 + d2 + d3 + plot_layout(guides = "collect") &  theme(legend.position = "top") 
+patchwork + plot_annotation(caption = "Vertical lines indicate means (dashed line = student sample).")
+```
+
+```{r plotContributionsAppendix}
+#| include: false
+
+SUM <- main[treatment == "replication",
+            lapply(.SD, mean, na.rm = TRUE),
+            by = c("round", "student"),
+            .SDcols = "contribution"]
+
+SUM[,
+    sum := round(contribution)]
+
+SUM[,
+    contribution := contribution/4]
+
+upperLimit <- SUM$contribution %>% max() %>% round() + 5
+
+p1 <- ggplot(data = SUM, 
+             aes(x = round, y = contribution, fill = student, color = student, lty = student)) +
+  layout +
+  theme(legend.position="top") +
+  geom_line(show.legend=FALSE) +
+  geom_point() +
+  scale_x_continuous(name="",  breaks = 1:15) +
+  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
+  labs(y = "Average Amount of Tokens contributed") +
+  scale_color_manual(values = c(cPrimary, cSecondary),
+                     labels = c("General Population Sample", "Student Sample")) + 
+  guides(fill = "none") +
+  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
+
+rm(list = c("SUM"))
+```
+
+```{r plotShareOfContributionsAppendix}
+#| fig.cap: "The average amount of tokens contributed over time in treatments."
+#| include: false
+
+SHARE <- main[treatment == "replication",
+            lapply(.SD, mean, na.rm = TRUE),
+            by = c("round", "student"),
+            .SDcols = "share"]
+
+# SHARE <- main[,
+#             .(share = sum(contribution)/sum(endowment)),
+#             by = c("round", "treatment")]
+
+upperLimit <- 0.75
+
+p2 <- ggplot(data = SHARE, 
+             aes(x = round, y = share, fill = student, color = student, lty = student)) +
+  layout +
+  theme(legend.position="bottom") +
+  geom_line(show.legend=FALSE) +
+  geom_point() +
+  scale_x_continuous(name="",  breaks = 1:15) +
+  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
+  labs(y = "Share of Current Endowment contributed") +
+  scale_color_manual(values = c(cPrimary, cSecondary),
+                     labels = c("General Population Sample", "Student Sample")) +
+  guides(fill = "none")
+
+p1 + p2 + plot_layout(guides = "collect") & 
+  theme(legend.position = "top")
+
+# rm(list = c("p1", "p2"))
+```
+
+```{r plotStockAppendix}
+#| include: false
+
+# data
+STOCK <- main[treatment == "replication",
+              lapply(.SD, mean, na.rm = TRUE),
+              by = c("round", "student"),
+              .SDcols = "stock"]
+
+# annotation
+maxPath <- data.table(x = 1:10)
+maxPath[, y := 80*1.5^x]
+maxPath[, student := "replication"]
+maxPath[, groupID := 42]
+
+# plot
+p1 <- ggplot(data = STOCK, 
+             aes(x = round, y = stock, fill = student, color = student, lty = student)) +
+  geom_line() +
+  geom_point() +
+  scale_x_continuous(breaks = 1:10) +
+  scale_y_continuous(limits = c(0, 4700), expand = c(0, 0)) +
+  labs(y = "Wealth", x = "Period") +
+  scale_color_manual(values = c(cPrimary, cSecondary),
+                     labels = c("General Population Sample", "Student Sample")) +
+  geom_point(mapping = aes(x = 10, y = 4613), col = "#b5b5b5") +
+  annotate("text", x = 9, y = 4630, size = 3,
+           label = "max", col = "#b5b5b5") +
+  geom_line(data = maxPath, mapping = aes(x = x, y = y), col = "#b5b5b5", lty = 2) +
+  guides(fill = "none") +
+  layout +
+  theme(legend.position = "top") +
+  guides(lty = "none")
+```
+
+```{r growthHeterogeneityVizAppendix}
+#| fig.cap: Average wealth over time across samples.
+#| include: false
+
+# plot
+p2 <- ggplot(data = main[treatment == "replication"],
+       mapping = aes(x = round, y = stock, color = student, by = groupID)) +
+  geom_line(alpha = 0.5) +
+  scale_x_continuous(breaks = 1:10) +
+  scale_y_continuous(limits = c(0, 2000),
+                       expand = c(0, NA)) +
+  scale_color_manual(values = c(cPrimary, cSecondary),
+                     labels = c("General Population Sample", "Student Sample")) +
+  labs(y = "", x = "Period") +
+  layout +
+  guides(col = "none")
+
+# assembling
+p1 + p2 + plot_layout(guides = "collect") & theme(legend.position = "top")
+```
+
+```{r}
+#| fig.cap: Average Gini coefficient (within groups) over time across samples
+#| include: false
+
+tmp <- main[treatment == "replication",
+            lapply(.SD, mean, na.rm = TRUE),
+            by = c("round", "student"),
+            .SDcols = "gini"]
+
+GINI <- rbind(tmp, list(0, TRUE, 0), list(0, FALSE, 0))
+
+ggplot(data = GINI, 
+             aes(x = round, y = gini, fill = student, color = student, lty = student)) +
+  geom_line() +
+  geom_point() +
+  scale_x_continuous(breaks = 0:10) +
+  scale_y_continuous(limits = c(0, 0.25), expand = c(0, 0)) +
+  labs(y = "Wealth", x = "Period") +
+  scale_color_manual(values = c(cPrimary, cSecondary),
+                     labels = c("General Population Sample", "Student Sample")) +
+  guides(fill = "none") +
+  layout +
+  theme(legend.position = "top") +
+  guides(lty = "none")
+```
+
+# C: Growth _and_ Inequality (exploratory) {.appendix}
+
+In contrast to GMTV, I did not ask how rich and poor groups differ.
 Instead, I was wondering, whether equal groups are wealthier.
 More precisely, does the Gini coefficient correlate with growth and wealth creation?
-To answer that question, Figure 7 applies a median split showing equal and unequal groups' wealth over time.
+To answer that question, @fig-stock-by-gini applies a median split showing equal and unequal groups' wealth over time.
 
 ```{r plotStockByGini}
-#| fig.cap: Average wealth over time across treatments.
+#| fig-cap: Average wealth over time across treatments.
+#| label: fig-stock-by-gini
 
@@
 ```
+-->

### 2022-11-03 analysis/quarto/paper.tex
many things happened here...

@@
 \hypersetup{
-  pdftitle={Growth and inequality in public good provision \textbar{} an extended replication},
+  pdftitle={Growth and inequality in public good provision --- an extended replication},
   pdfauthor={Hauke Roggenkamp},
@@
 \begin{frontmatter}
-\title{Growth and inequality in public good provision \textbar{} an
-extended replication}
+\title{Growth and inequality in public good provision --- an extended
+replication}
 \author[1,2]{Hauke Roggenkamp%
@@
 \begin{abstract}
-This is the abstract. Lorem ipsum dolor sit amet, consectetur adipiscing
-elit. Vestibulum augue turpis, dictum non malesuada a, volutpat eget
-velit. Nam placerat turpis purus, eu tristique ex tincidunt et. Mauris
-sed augue eget turpis ultrices tincidunt. Sed et mi in leo porta
-egestas. Aliquam non laoreet velit. Nunc quis ex vitae eros aliquet
-auctor nec ac libero. Duis laoreet sapien eu mi luctus, in bibendum leo
-molestie. Sed hendrerit diam diam, ac dapibus nisl volutpat vitae.
-Aliquam bibendum varius libero, eu efficitur justo rutrum at. Sed at
-tempus elit.
+You can find the most recent version of this paper
+\href{https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.pdf}{here}.
+The abstract follows at later point.
 \end{abstract}
@@
 \end{keyword}
-\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, frame hidden, breakable, sharp corners, enhanced, interior hidden]}{\end{tcolorbox}}\fi
+\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, sharp corners, frame hidden, boxrule=0pt, breakable, enhanced, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\hypertarget{sec-intro}{%
+\section{Introduction}\label{sec-intro}}
 
-\begin{quote}
-``There are two possible articles you can write: (a) the article you
-planned to write when you designed your study or (b) the article that
-makes the most sense now that you have seen the results. They are rarely
-the same, and the correct answer is (b).'' \citep[p.~171]{bemwriting}
-\end{quote}
+Today's actions are tomorrow's result. There are many settings in which
+current decisions affect future outcomes and with it, future decision
+spaces. Opting for environmental friendly policies today not only
+reduces carbon dioxide omissions but also helps us to reach the Paris
+climate targets tomorrow. Deferring these policies, the targets can be
+reached as well---but with less flexibility. Hence, today's actions (or
+the omission thereof) not only affect intermediate results but also the
+number of paths one can choose to reach certain goals.
 
-\hypertarget{methodology}{%
-\section{Methodology}\label{methodology}}
+Standard public good games---although often intended to inform climate
+policies\footnote{See \citet[p.~1]{GKLS2020} for numerous references.}---miss
+these temporal interdependencies because participants have the same set
+of actions in each period. A game implemented by Gächter, Mengel, Tsakas
+\& Vostroknutov \citeyearpar{GMTV2017} (hereafter, GMTV) as well as
+Stefan Große (2011, unpublished) incorporated interdependencies into a
+\emph{dynamic} public good game with students in Nottingham, England and
+Erfurt, Germany.
+
+Because their setting is more realistic, one wonders whether it is
+better suited to inform public policy. To answer this question, I
+replicated parts of GMTV's experiment with different samples. In
+addition, I observed the participant's behavior in voluntary climate
+actions (VCA). This yielded a setting similar to \citet{GKLS2020}'s
+which allows me to analyze how behavior in the abstract game translates
+into real-world action across samples.
+
+I utilized an inexperienced sample that has not been exposed to
+interactive experiments before. Furthermore, I conducted the experiment
+online. This required me to make the experiment's software robust to
+minimize attrition. Because I observed metrics to assess the fluency and
+feasibility of online experiments, this study also serves as a case
+study like the one of \citet{AGM2018}.
+
+Taken together, this study makes three contributions. First, it
+replicates parts of GMTV's original experiment and highlights the
+importance of pure replications. Second, it shows that logistically
+complex online experiments are feasible for samples other than students
+or clickworkers. Third, it shows that findings from abstract games do
+not generalize well and even worse with the representative sample. After
+reporting the methods, this paper is organized along these findings.
+
+\hypertarget{sec-methods}{%
+\section{Methodology}\label{sec-methods}}
 
 In the terminology of \citet{Hamermesh2007}, I ran both a \emph{pure} as
-well as a \emph{scientific replication} of one treatment arm of
-\citet{GMTV2017}'s dynamic public good game. The pure replication
-re-analyzes the original data.
-\protect\hyperlink{A:-Pure-Replication}{Appendix A} documents
+well as a \emph{scientific replication} of one treatment of GMTV's
+dynamic public good game. The pure replication re-analyzes the original
+data. \protect\hyperlink{A:-Pure-Replication}{Appendix A} documents
 \href{}{errors I identified} in the original paper. The scientific
 replication, where I utilize a different sample drawn from a different
-population in a different situation, is described in this section.
+population in a different situation, is described in the following
+sections.
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+\hypertarget{sec-design}{%
+\subsection{Experimental Design}\label{sec-design}}
+
+As in the NOPUNISH 10 Period treatment of GMTV, I ran sessions with
+groups of four (\(i \in I=\{1,2,3,4\}\)), an initial endowment of
+\(N_i^1 = 20\) tokens, \(T=10\) periods, a private account with a return
+of \(1\) and a group account with a return of \(1.5\) (\(\Rightarrow\)
+MPCR\(\equiv \frac{1.5}{4}\)), such that:
+
+\[
+N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
+\] What makes the game \emph{dynamic}? Instead of receiving fresh
+endowments every period, participants received one endowment only at the
+beginning of the first period. A participant's endowment in the second
+period is the wealth he or she accumulated in the first period. A
+participant's endowment in the third period is the wealth he or she
+accumulated in the first two periods. And so on. Hence, a decision in
+one period has consequences on future endowments and, ultimately, growth
+paths. For this reason, the game is described as a \emph{dynamic} public
+good game
+
+\hypertarget{sec-sample}{%
+\subsection{Sample}\label{sec-sample}}
+
+I recruited the participants from the so called
+\emph{\href{https://www.wiso.uni-hamburg.de/forschung/forschungslabor/umfragelabor/aktuelle-umfragen/hamburgpanel.html}{HamburgPanel}}
+using HROOT \citep{hroot}. The panel is provided by the University of
+Hamburg's Research Laboratory, which used a randomized last digits
+approach to build the panel while drawing from the population of
+citizens from Hamburg, Germany. Because the sample was exhausted at one
+point, I also recruited students from the University of Hamburg.
+
+At the time I conducted the experiment, the representative sample was
+not familiar with interactive experiments. In fact, I ran the first
+interactive group experiment with this sample. The students, in
+contrast, are used to this kind of experiments. Recruiting them, I
+excluded those who have participated in a public goods game before. As a
+consequence, nonnaiveté is unlikely to affect the validity of my
+experiment \citep[ p.~204]{GoodmanPaolacci2017}.
+
+Throughout this paper, I will compare results of my experiment with the
+results of GMTV's NOPUNISH 10 Period treatments. I am thus, referring to
+three different samples utilized at two points in time: the University
+of Nottingham's students (in late 2012), Hamburg's citizens and the
+University Hamburg's students (both in July 2021).
+Table~\ref{tbl-sample-properties} shows how they compare with respect to
+a few properties.
+
+\hypertarget{tbl-sample-properties}{}
+\begin{table}[!htbp] \centering 
+  \caption{\label{tbl-sample-properties}Sample Properties } 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-7} 
+ & Female & Age & Trust & Meritocracy & Government & Equality \\ 
+\hline \\[-1.8ex] 
+ Hamburg Citizens & 0.48$^{***}$ & 47.58$^{***}$ & 3.90$^{***}$ & 3.79$^{***}$ & 3.44$^{***}$ & 4.17$^{***}$ \\ 
+  & (0.07) & (1.21) & (0.19) & (0.21) & (0.19) & (0.23) \\ 
+  & & & & & & \\ 
+ Hamburg Students & 0.08 & $-$21.41$^{***}$ & $-$0.58$^{**}$ & 0.23 & 0.71$^{***}$ & 0.12 \\ 
+  & (0.09) & (1.63) & (0.25) & (0.28) & (0.26) & (0.30) \\ 
+  & & & & & & \\ 
+ Nottingham Students & $-$0.10 & $-$15.85$^{***}$ & $-$0.03 & 1.65$^{***}$ & 0.87$^{***}$ & $-$0.35 \\ 
+  & (0.09) & (1.52) & (0.23) & (0.26) & (0.24) & (0.28) \\ 
+  & & & & & & \\ 
+\hline \\[-1.8ex] 
+Observations & 208 & 208 & 208 & 208 & 208 & 208 \\ 
+R$^{2}$ & 0.02 & 0.47 & 0.04 & 0.20 & 0.06 & 0.02 \\ 
+Residual Std. Error & 0.50 & 8.75 & 1.35 & 1.52 & 1.40 & 1.63 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+Describe sample properties here.
+
+\hypertarget{sec-software}{%
+\subsection{Software}\label{sec-software}}
+
+The experiment was logistically complex for several reasons. First, the
+sample was inexperienced. Second, the experiment was interactive and
+synchronous. Third, the underlying game was dynamic and interdependent.
+This makes dropouts not only more likely, but also more expensive which
+is why dropouts were a major concern implementing the experiment.
+
+I chose oTree \citep{oTree} to implement the experiment because it is
+open-source, well documented and very flexible. Its
+\href{https://getbootstrap.com/}{Bootstrap} (a powerful frontend
+toolkit) integration allowed me to make the graphical user interface
+interactive, appealing and easy to navigate. The
+\href{https://www.highcharts.com/}{Highcharts library} made it easy to
+visualize results and to communicate dynamics. The oTree code snippets
+made it possible to handle dropouts, for instance, by replacing them
+with artificial bots (and informing the rest of the group thereof).
+Insofar, oTree served a good tool to consider the participants' user
+experience and thus, to make dropouts less likely.
+
+The experiment's source code be found on
+\href{https://github.com/Howquez/coopUncertainty}{GitHub}.\footnote{https://github.com/Howquez/coopUncertainty}
+
+\hypertarget{sec-procedure}{%
+\subsection{Procedure}\label{sec-procedure}}
 
@@
 (some of) their earnings to offset carbon dioxide. Subsequently, I
-elicited risk preferences \citep{HoltLaury2002} and finished with
-\citet{GMTV2017}'s questionnaire.
+elicited risk preferences \citep{HoltLaury2002} and finished with GMTV's
+questionnaire.
 
-\hypertarget{experimental-design}{%
-\subsection{Experimental Design}\label{experimental-design}}
+While I tried to stick to GMTV's protocol as close as possible, I
+deviated in a few aspects. First, the instructions were German and also
+covered topics inherent to the online setting (dropouts and bots, for
+instance). Second, I used another software (oTree instead of zTree).
+Third, GMTV gave participants the opportunity to donate to \emph{Doctors
+without Borders} whereas we offered carbon dioxide offsets. Fourth, the
+graphical user interface looked different.
 
-As in the NOPUNISH 10 Period treatment arm of \citet{GMTV2017}, I ran
-sessions with groups of four (\(i \in I=\{1,2,3,4\}\)), an initial
-endowment of \(N_i^1 = 20\) tokens, \(T=10\) rounds, a private account
-with a return of \(1\) and a group account with a return of \(1.5\)
-(\(\Rightarrow\) MPCR\(\equiv \frac{1.5}{4}\)), such that:
+\hypertarget{sec-results}{%
+\section{Results}\label{sec-results}}
 
-\[
-N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
-\] Instead of receiving fresh endowments every period, participants
-receive one initial endowment only at the beginning of the first period.
-A participant's subsequent endowment equals her profit from the current
-period such that a decision in one period has consequences on her future
-endowments. For this reason, the game is described as a \emph{dynamic}
-public good game
+\hypertarget{sec-replication}{%
+\subsection{Pre-registered GMTV Replication}\label{sec-replication}}
 
-\hypertarget{sample}{%
-\subsection{Sample}\label{sample}}
+The analyses in this section were pre-registered
+\citep{preregistration}. I also pre-registered a RMarkdown file with the
+exact code I intended to use
+\href{https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd}{here}.\footnote{https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd
+  to run the code, you need to executed the .Rmd files in this
+  repository in the order that is indicated by its file names.} Even
+though I had to adjust a few lines of code, the main findings in the
+following section can also be replicated using the pre-registered code.
 
-I recruited the participants from the so called
-\emph{\href{https://www.wiso.uni-hamburg.de/forschung/forschungslabor/umfragelabor/aktuelle-umfragen/hamburgpanel.html}{HamburgPanel}}
-using HROOT \citep{hroot}. The panel is provided by the University of
-Hamburg's Research Laboratory, which used a randomized last digits
-approach to build the panel while drawing from the population of
-citizens from Hamburg, Germany.
+\hypertarget{sec-contributions}{%
+\subsubsection{Contribution Behavior}\label{sec-contributions}}
 
-Describe sample properties here.
-
-\hypertarget{software}{%
-\subsection{Software}\label{software}}
-
-The experiment was created using oTree \citep{oTree} and can be found on
-\href{https://github.com/Howquez/coopUncertainty}{GitHub}.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{online-feasibility}{%
-\subsection{Online Feasibility}\label{online-feasibility}}
-
-How did the participants, who have never participated in a online group
-experiment before, cope with the situation?
+First, I ask whether the samples differ with respect to their initial
+contributions to the public good. Is our replication sample more
+pro-social than the original sample? Figure~\ref{fig-first-round}
+reveals that it is not. The distributions of both samples look fairly
+similar. Both samples contributed 10 tokens, that is, 50\% of their
+endowments on average (median and mean).\footnote{The two-sided rank sum
+  test (comparing differences between samples) yields a p-Value of
+  0.3926 for the mean contribution in first round of the game.}
+Moreover, both samples' initial contributions resemble initial
+contributions participants usually make in the standard game with
+partner matching.\footnote{See Figure 3B in \citet{fehrgaechter2000}
+  (p.989), for instance.} However, in the dynamic game presented here,
+we are particularly interested in the subsequent periods because
+differences add up exponentially. Do the two groups remain similar over
+the course of time?
 
@@
 
-{\centering \includegraphics{paper_files/figure-pdf/plotTime-1.pdf}
+{\centering \includegraphics{paper_files/figure-pdf/fig-first-round-1.pdf}
 
@@
 
-\caption{Average Time Spent for each Contribution per Period}
-
-\end{figure}
-
-\hypertarget{pre-registered-gmtv-replication}{%
-\subsection{Pre-registered GMTV
-Replication}\label{pre-registered-gmtv-replication}}
-
-\textbf{Result 1.} \emph{The \texttt{NOPUNISH\ 10} treatment of
-\citet{GMTV2017} can be replicated because the replication data resemble
-the original data with respect to initial and final contributions,
-wealth and growth as well as inequality between and within groups.}
-
-This is remarkable given the different sample and language, the
-different software and user interface as well as the online setting
-during the COVID19 pandemic.
-
-\hypertarget{contributions}{%
-\subsubsection{Contributions}\label{contributions}}
-
-First, I ask whether the samples differ with respect to their initial
-contributions to the public good. Is our replication sample more
-pro-social than the original sample? Figure 1 reveals that it is not.
-The distributions of both samples look fairly similar. Both samples
-contributed 10 tokens, that is, 50\% of their endowments on average
-(median and mean).\footnote{The two-sided rank sum test (comparing
-  differences between samples) yields a p-Value of 0.3926 for the mean
-  contribution in first round of the game.} Moreover, both samples'
-initial contributions resemble initial contributions participants
-usually make in the standard game with partner matching.\footnote{See
-  Figure 3B in \citet{fehrgaechter2000} (p.989), for instance.} However,
-in the dynamic game presented here, we are particularly interested in
-the subsequent periods because differences add up exponentially. Do the
-two groups remain similar over the course of time?
-
-\begin{figure}
-
-{\centering \includegraphics{paper_files/figure-pdf/firstRoundViz-1.pdf}
-
-}
-
-\caption{Individual contributions to the dynamic public good in the
-first period}
+\caption{\label{fig-first-round}Individual contributions to the dynamic
+public good in the first period}
 
@@
 In particular, do the two samples' contributions follow the same path
-over the 10 periods they played? The answer is \emph{no}. Figure 2
-illustrates that the samples make similar contributions at the beginning
-and the end of the game but behave differently in between. More
-precisely, the left panel--depicting the average contributions in
-absolute terms--shows that the original sample contributed substantially
-more than the replication sample \emph{in all but the first and last
-periods}. For this reason, the original sample's behavior differs from
-the replication sample's behavior in two aspects: it contributes more
-and exhibits a considerable drop in the last period (whereas the
-replication sample's contributions flatten).
+over the 10 periods they played? The answer is \emph{no}.
+Figure~\ref{fig-share-of-contributions} illustrates that the samples
+make similar contributions at the beginning and the end of the game but
+behave differently in between. More precisely, the left panel--depicting
+the average contributions in absolute terms--shows that the original
+sample contributed substantially more than the replication sample
+\emph{in all but the first and last period}. For this reason, the
+original sample's behavior differs from the replication sample's
+behavior in two aspects: it contributes more and exhibits a considerable
+drop in the last period (whereas the replication sample's contributions
+flatten).
 
@@
 over time. Hence, absolute contributions do not us much about the
-willingness to cooperate. For this reason, the right panel in Figure 2
-shows the average \emph{share of endowments contributed} over time. Both
-samples exhibit a similar pattern: they decline and do not stabilize.
-However, both samples also differ with respect to one aspect: the
-replication sample's share of contributions declines faster.
+willingness to cooperate. For this reason, the right panel in
+Figure~\ref{fig-share-of-contributions} shows the average \emph{share of
+endowments contributed} over time. Both samples exhibit a similar
+pattern: their share of endowments contributed declined and did not
+stabilize. However, both samples also differ with respect to one aspect:
+the replication sample's share of contributions declines faster.
 
@@
 
-{\centering \includegraphics{paper_files/figure-pdf/plotShareOfContributions-1.pdf}
+{\centering \includegraphics{paper_files/figure-pdf/fig-share-of-contributions-1.pdf}
 
@@
 
-\caption{The average amount of tokens contributed over time in
-treatments.}
+\caption{\label{fig-share-of-contributions}The average amount of tokens
+contributed over time in treatments.}
 
@@
 
-\hypertarget{wealth-creation}{%
-\subsubsection{Wealth Creation}\label{wealth-creation}}
+\hypertarget{sec-wealth}{%
+\subsubsection{Wealth Creation}\label{sec-wealth}}
 
@@
 original sample contributed more in most of the periods, one would
-expect the respective groups to be considerably more wealthy. Figure 3
-indicates just that. The grey lines show that an average group in the
-original sample accumulated about 478 tokens. In contrast, an average
-group in the replication sample accumulated about 380 tokens. This
-difference is insignificant at conventional levels\footnote{The
-  two-sided rank sum test (comparing differences between samples) yields
-  a p-Value of 0.1356 for the mean stock in last round of the game.}
-though.
+expect the respective groups to be considerably more wealthy.
+Figure~\ref{fig-stock-distribution} indicates just that. The grey lines
+show that an average group in the original sample accumulated about 478
+tokens. In contrast, an average group in the replication sample
+accumulated about 380 tokens. This difference is insignificant at
+conventional levels\footnote{The two-sided rank sum test (comparing
+  differences between samples) yields a p-Value of 0.1356 for the mean
+  stock in last round of the game.} though.
 
@@
 
-{\centering \includegraphics{paper_files/figure-pdf/stockDistributionViz-1.pdf}
+{\centering \includegraphics{paper_files/figure-pdf/fig-stock-distribution-1.pdf}
 
@@
 
-\caption{Groups' income at the end of the game}
+\caption{\label{fig-stock-distribution}Groups' income at the end of the
+game}
 
@@
 least 4613 tokens or EUR 230. This is depicted in the left panel of
-Figure 4, where one can see the average wealth over time by sample. The
-panel illustrates for both samples that growth was continuous and
-surprisingly linear, given the exponential character of the game's
-design. To sum up, the contribution behavior differed between samples.
-In contrast, neither the eventual wealth nor the corresponding growth
-paths differed. Differences in contribution behavior did, thus, not
-translate in significantly different wealth outcomes.
+Figure~\ref{fig-growth-heterogeneity}, where one can see the average
+wealth over time by sample. The panel illustrates for both samples that
+growth was continuous and surprisingly linear, given the exponential
+character of the game's design. To sum up, the contribution behavior
+differed between samples. In contrast, neither the eventual wealth nor
+the corresponding growth paths differed. Differences in contribution
+behavior did, thus, not translate to significantly different wealth
+outcomes.
 
@@
 has been too large to \emph{detect} a significant difference. The right
-panel of Figure 4 depicts heterogeneity: In the replication sample, the
-richest group earned 1425 tokens (which is about 1781\% of the initial
-endowment) whereas the poorest group ends up with 92 tokens (115\%).
-More broadly, the replication sample is characterized by inequality
-between groups (\(SD_{Replication} =\) 336.06). The same holds true for
-the original sample (\(SD_{Original} =\) 393.58). Hence, the
-heterogeneity across groups does not differ between samples, which is
-remarkable because the replication sample was drawn from a more
-heterogeneous (non-convenience sample). Does it differ within groups?
+panel of Figure~\ref{fig-growth-heterogeneity} depicts heterogeneity: In
+the replication sample, the richest group earned 1425 tokens (which is
+about 1781\% of the initial endowment) whereas the poorest group ends up
+with 92 tokens (115\%). More broadly, the replication sample is
+characterized by inequality between groups (\(SD_{Replication} =\)
+336.06). The same holds true for the original sample
+(\(SD_{Original} =\) 393.58). Hence, the heterogeneity across groups
+does not differ between samples, which is remarkable because the
+replication sample was drawn from a more heterogeneous (non-convenience
+sample). Does it differ within groups?
 
@@
 
-{\centering \includegraphics{paper_files/figure-pdf/growthHeterogeneityViz-1.pdf}
+{\centering \includegraphics{paper_files/figure-pdf/fig-growth-heterogeneity-1.pdf}
 
@@
 
-\caption{Average wealth over time across samples.}
+\caption{\label{fig-growth-heterogeneity}Average wealth over time across
+samples.}
 
@@
 
-\hypertarget{inequality}{%
-\subsubsection{Inequality}\label{inequality}}
+\hypertarget{sec-inequality}{%
+\subsubsection{Inequality}\label{sec-inequality}}
 
@@
 growth--which essentially is the main feature of the game--I ask whether
-and how the inequality grows \emph{within} groups. Figure 5 illustrates
-that inequality did grow: at the end of the game, the original and the
-replication groups exhibit an average Gini coefficient of 0.23 and 0.22,
-respectively.\footnote{The two-sided rank sum test (comparing
-  differences between samples) yields a p-Value of 0.6059 for the mean
-  Gini coefficient in last round of the game.} Because every participant
-started with the same initial endowment (in \emph{Period 0}, so to
-speak), every group started equally--with a Gini coefficient equaling
-zero.
+and how the inequality grows \emph{within} groups.
+Figure~\ref{fig-gini-distribution} illustrates that inequality did grow:
+at the end of the game, the original and the replication groups exhibit
+an average Gini coefficient of 0.23 and 0.22, respectively.\footnote{The
+  two-sided rank sum test (comparing differences between samples) yields
+  a p-Value of 0.6059 for the mean Gini coefficient in last round of the
+  game.} Because every participant started with the same initial
+endowment (in \emph{Period 0}, so to speak), every group started
+equally--with a Gini coefficient equaling zero.
 
-Figure 6 shows that this initial state of equality ended with the first
-period already: both samples exhibit a stark incline in inequality
-before the second period started. From then on, the respective Gini
-coefficients grew slowly but continuously -- for both samples.
+Figure~\ref{fig-ginit-time-series} shows that this initial state of
+equality ended with the first period already: both samples exhibit a
+stark incline in inequality before the second period started. From then
+on, the respective Gini coefficients grew slowly but continuously -- for
+both samples.
 
@@
 
-{\centering \includegraphics{paper_files/figure-pdf/giniDistributionViz-1.pdf}
+{\centering \includegraphics{paper_files/figure-pdf/fig-gini-distribution-1.pdf}
 
@@
 
-\caption{Groups' Gini coefficients (within groups) at the end of the
-game}
+\caption{\label{fig-gini-distribution}Groups' Gini coefficients (within
+groups) at the end of the game}
 
@@
 
-{\centering \includegraphics{paper_files/figure-pdf/unnamed-chunk-1-1.pdf}
+{\centering \includegraphics{paper_files/figure-pdf/fig-ginit-time-series-1.pdf}
 
@@
 
-\caption{Average Gini coefficient (within groups) over time across
-samples}
+\caption{\label{fig-ginit-time-series}Average Gini coefficient (within
+groups) over time across samples}
 
@@
 
-\hypertarget{generalizability}{%
-\subsection{Generalizability}\label{generalizability}}
+\textbf{Result 1.} \emph{The \texttt{NOPUNISH\ 10} treatment of GMTV can
+be replicated because the replication data resemble the original data
+with respect to initial and final contributions, wealth and growth as
+well as inequality.}
 
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
+This is remarkable given the different sample and language, the
+different software and user interface as well as the online setting
+during the COVID19 pandemic. The result suggests that, by and large, the
+sum of these factors did not affect people's preferences towards
+cooperation.
 
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
+\hypertarget{sec-feasibility}{%
+\subsection{Online Feasibility}\label{sec-feasibility}}
 
-\hypertarget{a-pure-replication}{%
-\subsection{A: Pure Replication}\label{a-pure-replication}}
+How did the participants, who have never participated in an online group
+experiment before, cope with the situation? Moreover, did participants
+understand the unfamiliar setting they found themselves in? While the
+answer to the former question requires more thought, the answer to the
+latter simply is \emph{yes}: 67 out of 116 answered with \emph{``yes''}
+when I asked them. Another 44 answered with \emph{``rather yes''} while
+nobody indicated that he or she did not understand the situation at all.
+To analyze how participants coped with the situation, I consider three
+additional metrics: selection into the experiment, attrition as well as
+the time spent on each page.
 
-\hypertarget{b-growth-and-inequality-exploratory}{%
-\subsection{\texorpdfstring{B: Growth \emph{and} Inequality
-(exploratory)}{B: Growth and Inequality (exploratory)}}\label{b-growth-and-inequality-exploratory}}
+I first comment on the selection into the experiment: It was difficult
+to recruit the sample. The panel counted 1.209 non-students of which we
+were able to recruit 130 participants who finished the experiment---even
+though we varied the weekdays and timing of the sessions (which were
+conducted during a nation-wide lockdown with home office regime). For
+this reason, we also recruited students in the last session which
+explains the relatively large number of showups in Table~\ref{tbl-meta}.
+Although I intended to refrain from the recruitment of students
+initially, this particular sub sample enabled me to investigate the
+generalizability of my results as I will discuss in
+Section~\ref{sec-generalizability}. Alternatively, I also could have
+contacted a market research institute to recruit additional participants
+within a week. I refrained from doing so to contrast students and the
+general population sample, however.
 
-In contrast to \citet{GMTV2017}, I did not ask how rich and poor groups
-differ. Instead, I was wondering, whether equal groups are wealthier.
-More precisely, does the Gini coefficient correlate with growth and
-wealth creation? To answer that question, Figure 7 applies a median
-split showing equal and unequal groups' wealth over time.
+\hypertarget{tbl-meta}{}
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1566}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1325}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0723}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0964}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1084}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1205}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1566}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1566}}@{}}
+\caption{\label{tbl-meta}The Experimental Sessions' Meta
+Data}\tabularnewline
+\toprule()
+\begin{minipage}[b]{\linewidth}\raggedright
+Session Code
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Date
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Time
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Showups
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Dropouts
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Residuals
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Participants
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Observations
+\end{minipage} \\
+\midrule()
+\endfirsthead
+\toprule()
+\begin{minipage}[b]{\linewidth}\raggedright
+Session Code
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Date
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Time
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Showups
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Dropouts
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Residuals
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Participants
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Observations
+\end{minipage} \\
+\midrule()
+\endhead
+jyf8xd0s & 2021-07-01 & 15:00 & 35 & 4 & 3 & 28 & 7 \\
+vggk2gh1 & 2021-07-03 & 13:00 & 20 & 8 & 0 & 12 & 3 \\
+8gi7c8xg & 2021-07-09 & 13:00 & 21 & 5 & 4 & 12 & 3 \\
+d6jrsxnr & 2021-07-23 & 14:00 & 75 & 8 & 3 & 64 & 16 \\
+\bottomrule()
+\end{longtable}
+
+Turning to the time spent on each page, I focus on the decision times in
+the dynamic public goods game as \citet{Anderhub2001} did. How many
+seconds did the participants need to make a decision in each period of
+the game? Not too many. Figure~\ref{fig-time-spent} illustrates an
+intuitive pattern: The first decision took about 22 seconds. The second
+decision--where participants first learned about the other group
+members' previous decisions--took longer (about 33 seconds).
+Subsequently, decision times first declined and stabilized at 19
+seconds. Importantly, decision times were so short that crosstalk, that
+is, communication through private channels--a common concern\footnote{See,
+  for instance, the discussion section in \citet[p.~119]{AGM2018}.} in
+online experiments--was unlikely, especially because it would require
+the identification of other group members.\footnote{There were only 9
+  participants (from all four sessions) who needed more than 60 seconds
+  to make the second decision.}
 
@@
 
-{\centering \includegraphics{paper_files/figure-pdf/plotStockByGini-1.pdf}
+{\centering \includegraphics{paper_files/figure-pdf/fig-time-spent-1.pdf}
 
@@
 
-\caption{Average wealth over time across treatments.}
+\caption{\label{fig-time-spent}Average Time Spent for each Contribution
+per Period}
 
 \end{figure}
+
+Considering attrition, I find that it did not affect the interactive
+experiment at all. To elaborate, I differentiate between dropouts and
+residuals: Participants who could not be matched to other group members
+are called residuals. Participants who intentionally left the experiment
+are called dropouts. Residuals did not participate in the experiment
+\emph{by design}. Dropouts did not participate in the experiment
+\emph{by choice}. Out of 151 people who showed up, I count 10 residuals
+and 25 dropouts. All of the residuals waited to be matched to a group
+unsuccessfully before they got paid one Euro for their patience. In
+contrast, all of the dropouts left while reading the instructions and
+before being matched to other group members. Moreover, they got no
+payment at all. Hence, attrition was no concern considering the dynamic
+public goods game or the expenses.
+
+\textbf{Result 2.} \emph{Given the decision times and the fluent
+procedure, attrition was as negligible as it is in physical
+laboratories---where (a) not every invited person shows up and (b) a
+number of participants divisible by the group size is required as well.}
+
+\hypertarget{sec-generalizability}{%
+\subsection{Generalizability}\label{sec-generalizability}}
+
+\citet{GKLS2020} asked how much can we learn about voluntary climate
+action from the behavior in public goods games. Using a similar
+strategy, I answer the question for \emph{dynamic} public goods games:
+\emph{Not much}. Overall, there seems to be no association between
+choices in the voluntary climate action and the first period in the
+dynamic public goods game. Figure~\ref{fig-scatter-generalizability}
+shows a scatter plot of realized choices, with the percentage of
+endowment spent by each participant in the first period of the game on
+the x-axis and that spent in the VCA on the y-axis. In addition, the
+figure contains a fitted line of a linear model whose slope is
+indistinguishable from zero. No matter how much the participants
+contributed in the first round, they spent, on average, about 21\% of
+their income on the VCA.
+
+\begin{figure}
+
+{\centering \includegraphics{paper_files/figure-pdf/fig-scatter-generalizability-1.pdf}
+
+}
+
+\caption{\label{fig-scatter-generalizability}Scatter plot of average
+contributions in the dPGG and real giving task.}
+
+\end{figure}
+
+Does this result hold true if one zooms in and inspects the two samples
+separately? Yes. Even though the general population sample is a little
+more consistent than the student sample, both are contributing more in
+the abstract game than in the VCA.
+Figure~\ref{fig-kernel-generalizability} shows distributions of
+contributions across both choices for both samples. The left panels
+illustrate the behavior of the general population sample. The right
+panels illustrate the behavior of the general population sample. The top
+panels show the behavior in the VCA. The bottom panels show the behavior
+in first period of the game. A visual inspection shows that (a) both
+samples behaved similarly in the first period of the game but (b)
+different (p = 0.03) in the VCA. Furthermore, (c) the behavior in the
+first period of the experiment predicts the general population sample's
+behavior in the VCA worse than student sample's behavior (p = 0.07).
+Finally, (4) contributions in the abstract public good game are higher
+than contributions to the real public good of climate change mitigation.
+
+\begin{figure}
+
+{\centering \includegraphics{paper_files/figure-pdf/fig-kernel-generalizability-1.pdf}
+
+}
+
+\caption{\label{fig-kernel-generalizability}Kernel distributions of
+contributions across tasks and subject pools.}
+
+\end{figure}
+
+\textbf{Result 3.} \emph{Existing evidence overestimates the willingness
+to contribute to real public goods. This holds true for more
+representative samples and---to a lower degree---for student samples.}
+
+\hypertarget{sec-conclusion}{%
+\section{Conclusion}\label{sec-conclusion}}
+
+The goal of the experiment was to replicate specific experiments of GMTV
+in an online setting using a general population sample. The results
+suggest that it is important to replicate experiments---both purely and
+scientifically \citep[ p.~716]{Hamermesh2007}---before drawing
+conclusions about generalizability.
+
+The three most important findings are as follows: First, the
+contribution behavior in my experiment is statistically similar to the
+behavior reported in the original study. Consequently, the outcomes
+growth and inequality are similar as well. Second, the online experiment
+proceeded fluently such that dropouts were no concern. Third,
+contribution behavior in my abstract setting is, if anything, only
+weakly linked to behavior in the real world. This lack of
+generalizability can be counteracted, but not be solved, by the use of
+more representative samples.
+
+The significance of the first result is that similar procedures led to
+replicable findings under different circumstances across two different
+samples. The second result is of methodological importance: It
+highlights that even logistically complex experiments can be conducted
+online with---not only with clickworkers but also with a true general
+population sample. The third result questions whether recruiting from
+more representative samples is worth the efforts because it decreases
+transferability of results to the real world---at least, a little.
+
+\newpage{}
+
+\hypertarget{a-pure-replication}{%
+\section{A: Pure Replication}\label{a-pure-replication}}
+
+This section comments on two errors as well as a misconception I found
+in the original data.\footnote{The data can be found in the
+  supplementary materials they provide in their
+  \href{https://www.sciencedirect.com/science/article/pii/S0047272717300361\#s0115}{online
+  appendix}.} Before I proceed to explain this in more detail I would
+like to say that the results of the original paper still hold after the
+error is fixed and that the authors responded kindly and quickly,
+showing an interest in solving the issue. In fact, some explanations in
+this section stem from input provided by the authors.
+
+\hypertarget{error-1-the-gini-coefficient}{%
+\subsubsection{Error 1: The Gini
+coefficient}\label{error-1-the-gini-coefficient}}
+
+The Gini coefficient is wrongly computed in some periods for some group
+members. The authors found that this happened whenever two group members
+had exactly the same endowment because the program failed to rank these
+group members for further calculations.
+
+Table~\ref{tbl-gini-error} illustrates this problem. It shows group 101
+in period 5 and documents that the Gini coefficient differs among group
+members. According to the authors, the Gini coefficient should equal
+\texttt{GINI=}0.127 for all subjects in the group. Instead, participant
+\texttt{112} and \texttt{113} who have an equal endowment deviate from
+that value. Importantly, the \texttt{DescTools::Gini()} function in the
+statistical software \texttt{R} does not yield this error, which is why
+I use that function for my calculations using both my as well as the
+original data.
+
+\hypertarget{tbl-gini-error}{}
+\begin{longtable}[]{@{}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1212}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0909}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0606}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1212}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1061}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1061}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1061}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1061}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0909}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0909}}@{}}
+\caption{\label{tbl-gini-error}Subset of Data illustrating the Gini
+Coefficient's Error}\tabularnewline
+\toprule()
+\begin{minipage}[b]{\linewidth}\raggedleft
+exp\_num
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+gr\_id
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+per
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+subj\_id
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+tokens
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+other1
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+other2
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+other3
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+gini
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+GINI
+\end{minipage} \\
+\midrule()
+\endfirsthead
+\toprule()
+\begin{minipage}[b]{\linewidth}\raggedleft
+exp\_num
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+gr\_id
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+per
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+subj\_id
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+tokens
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+other1
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+other2
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+other3
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+gini
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+GINI
+\end{minipage} \\
+\midrule()
+\endhead
+1 & 101 & 5 & 111 & 42 & 27 & 27 & 30 & 0.127 & 0.127 \\
+1 & 101 & 5 & 112 & 27 & 42 & 27 & 30 & 0.111 & 0.127 \\
+1 & 101 & 5 & 113 & 27 & 42 & 27 & 30 & 0.111 & 0.127 \\
+1 & 101 & 5 & 114 & 30 & 42 & 27 & 27 & 0.127 & 0.127 \\
+\bottomrule()
+\end{longtable}
+
+\hypertarget{error-2-the-share-of-endowments-contributed}{%
+\subsubsection{Error 2: The share of endowments
+contributed}\label{error-2-the-share-of-endowments-contributed}}
+
+The original data provides a wrong measure of the share of endowments
+contributed (\texttt{mean}) because it relies on a lagged endowment
+(\texttt{gdp}). More precisely, the authors used the following STATA
+code for their calculations:
+
+\begin{verbatim}
+*tsset subj_id per
+*gen mean=sum/l.gdp
+\end{verbatim}
+
+Table~\ref{tbl-mean-error} reports participant 111 in group 101 in
+experiment 1 over three periods. Both the \texttt{gdp} (that is, the sum
+of the group's endowments at the beginning of the period) as well as the
+\texttt{sum} (that is, the sum of the group's contributions) are
+group-level variables.
+
+\hypertarget{tbl-mean-error}{}
+\begin{longtable}[]{@{}rrrrrrrr@{}}
+\caption{\label{tbl-mean-error}Subset of Data illustrating the Means's
+Error}\tabularnewline
+\toprule()
+exp\_num & gr\_id & per & subj\_id & gdp & sum & mean & MEAN \\
+\midrule()
+\endfirsthead
+\toprule()
+exp\_num & gr\_id & per & subj\_id & gdp & sum & mean & MEAN \\
+\midrule()
+\endhead
+1 & 101 & 4 & 111 & 116 & 18 & 0.168 & 0.155 \\
+1 & 101 & 5 & 111 & 126 & 18 & 0.155 & 0.143 \\
+1 & 101 & 6 & 111 & 136 & 17 & 0.135 & 0.125 \\
+\bottomrule()
+\end{longtable}
+
+Calculating the share as \texttt{MEAN=sum/gdp} solves the problem and
+yields \(\frac{18}{126}=0.143\) in period 5. I thus, used this proposed
+definition for all my calculations using both my as well as the original
+data.
+
+\hypertarget{the-misconception-timing}{%
+\subsubsection{The misconception:
+Timing}\label{the-misconception-timing}}
+
+The authors wrote a note stating that the Gini coefficient as well as
+the wealth in the paper always refer to the situation at the start of a
+period and that they clarify this because the paper (last paragraph at
+the bottom of page 5), says that wealth is defined as the endowment at
+the beginning of the following period. Furthermore, they write that this
+error came about as they switched between these two definitions during
+the course of revising the paper.
+
+I argue that it makes more sense to calculate the variables as they
+state in the paper. More precisely, I think that the wealth at the
+\emph{beginning} of a period is less interesting than the wealth at the
+\emph{end} of a period for two reasons: First, there is no need for such
+a variable because it already exists (the endowment). Second, this
+definition yields a value that is determined by the design of the game
+but misses an important outcome at the end of the game. To illustrate
+this, note that the wealth would be defined as four times the initial
+endowment in period 1. Also note that the very last value would equal
+the wealth at the beginning of the last period and says nothing about
+the outcome of that period. Because the contributions often drop in the
+last period, this outcome is of particular interest (yet, not
+represented in the data). Moreover, this definition of wealth yields
+more informative values to calculate the Gini coefficient for the same
+reasons: We know that the Gini coefficient is zero \emph{before} the
+participants made any decision by design. We do no know the inequality
+at the very end of the game---and the current definition does not tell
+us.
+
+For these reasons, I define wealth and inequality measures as the
+outcomes of a period for all of my calculations using both my as well as
+the original data.\footnote{Accordingly, the definition of \texttt{GINI}
+  I provide in Table~\ref{tbl-gini-error} is not the definition I used
+  to calculate the current period's Gini coefficient but the previous
+  period's Gini coefficient.}
+
+\newpage{}
 

### 2022-11-03 analysis/reports/rmd/originalAnalysis.Rmd
many things happened here...

--- 2021-07-30 analysis/reports/rmd/03_dataAnalyses.Rmd
@@
 
-The table above displays summary statistics for the 10th period's ```stock``` a.k.a _Wealth_. The rank sum test yields a p-Value of `r rs1` for the mean wealth during the last period of the game.
-
-The following table shows a simple regression to illustrate differences in the 10th period's wealth between the replication's data and GMTV's data.
+The rank sum test yields a p-Value of `r rs1` for the mean ```stock``` a.k.a _Wealth_ during the last period of the game.
 
@@
 
-stargazer(lm(formula = stock ~ treatment, data = main_all),
-          lm(formula = stock ~ treatment, data = main_poor),
-          lm(formula = stock ~ treatment, data = main_rich),
+m1 <- lm(formula = stock ~ treatment, data = main_all)
+m2 <- lm(formula = stock ~ treatment, data = main_poor)
+m3 <- lm(formula = stock ~ treatment, data = main_rich)
+
+stargazer(m1, m2, m3,
 
@@
 ```
-
-These information are also plotted over all periods in the following figure.
 
@@
 
-The following figure plots the Gini-coefficient These over all periods.
-
 ```{r plotInequality, fig.cap = "Average Gini coefficient over time across treatments."}
@@
 
-upperLimit <- GINI$gini %>% max() %>% round(digits = 1) + 0.15
+upperLimit <- GINI$gini %>% max() %>% round(digits = 1) + 0.10
 
@@
 
-The following table shows a simple regression to illustrate differences in the 10th period's Gini coefficient between the replication's data and GMTV's data.
-
 ```{r tableGINI, results = "asis", warning = FALSE}
@@
 
-stargazer(lm(formula = gini ~ treatment, data = main_all),
-          lm(formula = gini ~ treatment, data = main_poor),
-          lm(formula = gini ~ treatment, data = main_rich),
+m1 <- lm(formula = gini ~ treatment, data = main_all)
+m2 <- lm(formula = gini ~ treatment, data = main_poor)
+m3 <- lm(formula = gini ~ treatment, data = main_rich)
+stargazer(m1, m2, m3,
 
@@
 
-The table above displays summary statistics for the 10th period's ```gini``` .
 The rank sum test yields a p-Value of `r rs2` for the mean ```gini``` during the last period of the game.
@@
 
-stargazer(lm(formula = gender ~ treatment, data = covs),
-          lm(formula = age ~ treatment, data = covs),
-          lm(formula = switching_row ~ treatment, data = covs),
-          lm(formula = donation ~ treatment, data = covs),
+m1 <- lm(formula = gender ~ treatment, data = covs)
+m2 <- lm(formula = age ~ treatment, data = covs)
+m3 <- lm(formula = switching_row ~ treatment, data = covs)
+m4 <- lm(formula = donation ~ treatment, data = covs)
+
+stargazer(m1, m2, m3, m4,
 
@@
 
-stargazer(lm(formula = pq01 ~ treatment, data = covs),
-          lm(formula = pq02 ~ treatment, data = covs),
-          lm(formula = pq03 ~ treatment, data = covs),
-          lm(formula = pq04 ~ treatment, data = covs),
-          lm(formula = pq05 ~ treatment, data = covs),
+m1 <- lm(formula = pq01 ~ treatment, data = covs)
+m2 <- lm(formula = pq02 ~ treatment, data = covs)
+m3 <- lm(formula = pq03 ~ treatment, data = covs)
+m4 <- lm(formula = pq04 ~ treatment, data = covs)
+m5 <- lm(formula = pq05 ~ treatment, data = covs)
+
+stargazer(m1, m2, m3, m4, m5,
 
@@
 
-stargazer(lm(formula = pq06 ~ treatment, data = covs),
-          lm(formula = pq07 ~ treatment, data = covs),
-          lm(formula = pq08 ~ treatment, data = covs),
-          lm(formula = pq09 ~ treatment, data = covs),
-          lm(formula = pq10 ~ treatment, data = covs),
+m1 <- lm(formula = pq06 ~ treatment, data = covs)
+m2 <- lm(formula = pq07 ~ treatment, data = covs)
+m3 <- lm(formula = pq08 ~ treatment, data = covs)
+m4 <- lm(formula = pq09 ~ treatment, data = covs)
+m5 <- lm(formula = pq10 ~ treatment, data = covs)
+
+stargazer(m1, m2, m3, m4, m5,
 
@@
 
-stargazer(lm(formula = pq11 ~ treatment, data = covs),
-          lm(formula = pq12 ~ treatment, data = covs),
-          lm(formula = pq13 ~ treatment, data = covs),
-          lm(formula = pq14 ~ treatment, data = covs),
+m1 <- lm(formula = pq11 ~ treatment, data = covs)
+m2 <- lm(formula = pq12 ~ treatment, data = covs)
+m3 <- lm(formula = pq13 ~ treatment, data = covs)
+m4 <- lm(formula = pq14 ~ treatment, data = covs)
+
+stargazer(m1, m2, m3, m4,
 
@@
 
-olsStock1 <- lm(formula = stock ~ gender + age + 
-                  switching_row + 
-                  pq01 + pq02 + pq03 + pq04 + 
+olsStock1 <- lm(formula = stock ~ gender + age + switching_row + pq01 + pq02 + pq03 + pq04 + 
                   pq05 + pq06 + pq07 +pq08 + pq09 + pq10 + pq11 + pq12 + pq13 + pq14, 
@@
                 data = covariates[treatment == "replication"])
-olsGINI1  <- lm(formula = gini ~ gender + age + 
-                  switching_row + 
-                  pq01 + pq02 + pq03 + pq04 +
+olsGINI1  <- lm(formula = gini ~ gender + age + switching_row + pq01 + pq02 + pq03 + pq04 +
                   pq05 + pq06 + pq07 + pq08 + pq09 + pq10 + pq11 + pq12 + pq13 + pq14, 
@@
           header=FALSE,
-          covariate.labels = c("female", "age", 
-                               "risk",
+          covariate.labels = c("female", "age", "risk",
                                "quick thinker",

### 2022-11-03 oTree/HLPL/__init__.py

@@ -1,0 +1,143 @@
+import random
+
+from otree.api import *
+
+
+author = 'Your name here'
+doc = """
+Inspired by https://github.com/felixholzmeister/mpl
+"""
+
+
+class Constants(BaseConstants):
+    name_in_url = 'HLPL'
+    players_per_group = None
+    num_rounds = 1
+    num_choices = 11
+    lottery_price = 100
+
+
+class Subsession(BaseSubsession):
+    pass
+
+
+class Group(BaseGroup):
+    pass
+
+
+class Player(BasePlayer):
+    review_instructions = models.IntegerField(
+        doc="Counts the number of times a player reviews instructions.", initial=0, blank=True
+    )
+    review_contact = models.IntegerField(
+        doc="Counts the number of times a player reviews contact information.",
+        initial=0,
+        blank=True,
+    )
+    for j in range(1, Constants.num_choices + 1):
+        locals()['choice_' + str(j)] = models.StringField()
+    del j
+    random_draw = models.IntegerField()
+    choice_to_pay = models.StringField()
+    option_to_pay = models.StringField()
+    inconsistent = models.IntegerField()
+    switching_row = models.IntegerField()
+
+
+# FUNCTIONS
+def creating_session(subsession: Subsession):
+    n = Constants.num_choices
+    for p in subsession.get_players():
+        indices = [j for j in range(1, n + 1)]
+        # indices.append(n)
+        certainty_equivalents = [(k - 1) * 10 for k in indices]
+        form_fields = ["choice_" + str(k) for k in indices]
+        p.participant.vars["mpl_choices"] = list(zip(indices, form_fields, certainty_equivalents))
+        p.participant.vars["mpl_index_to_pay"] = random.choice(indices)
+        p.participant.vars["mpl_choice_to_pay"] = "choice_" + str(
+            p.participant.vars["mpl_index_to_pay"]
+        )
+        p.participant.vars['mpl_choices_made'] = [None for j in range(1, n + 1)]
+
+
+def set_payoffs(player: Player):
+    player.random_draw = random.randint(0, 100)
+    player.choice_to_pay = player.participant.vars["mpl_choice_to_pay"]
+    player.option_to_pay = getattr(player, player.choice_to_pay)
+    if player.option_to_pay == "lottery":
+        if player.random_draw <= 50:
+            player.payoff = Constants.lottery_price
+        else:
+            player.payoff = 0
+    else:
+        player.payoff = player.participant.vars["mpl_index_to_pay"] * 10
[…]

### 2022-11-03 oTree/HLPL/tests.py

@@ -1,13 +1,13 @@
 from otree.api import Currency as c, currency_range
-from . import pages
-from ._builtin import Bot
-from .models import Constants
+from . import *
+from otree.api import Bot
+
 import random
 
 
 class PlayerBot(Bot):
     def play_round(self):
-        yield pages.HLPL_Decision, dict(choice_1="lottery",
+        yield HLPL_Decision, dict(choice_1="lottery",
                                              choice_2="lottery",
                                              choice_3="lottery",
                                              choice_4="lottery",

### 2022-11-03 oTree/Intro/__init__.py

@@ -1,0 +1,145 @@
+import time
+
+from otree.api import *
+
+
+author = "Hauke Roggenkamp"
+doc = """
+Welcome participants, display instructions and comprehension questions.
+"""
+
+
+class Constants(BaseConstants):
+    name_in_url = "A_Intro"
+    players_per_group = None
+    num_rounds = 1
+    group_size = 4
+    num_others_per_group = group_size - 1
+    initial_endowment = 20
+    efficiency_factor = 1.5  # (MPCR) Marginal Per Capita Return per round
+    rate_of_return = (efficiency_factor - 1) * 100
+
+
+class Subsession(BaseSubsession):
+    pass
+
+
+class Group(BaseGroup):
+    pass
+
+
+class Player(BasePlayer):
+    # Tracking Fields
+    window_width = models.IntegerField(doc="Documents the respondent's browser window's width.")
+    window_height = models.IntegerField(doc="Documents the respondent's browser window's height.")
+    browser = models.StringField(doc="Documents the respondent's browser (incl. its version).")
+    # Wrong Answers
+    wrong_answer1_1 = models.IntegerField(
+        doc="Counts the number of wrong guesses for CQ1_1.", initial=0
+    )
+    wrong_answer1_2 = models.IntegerField(
+        doc="Counts the number of wrong guesses for CQ1_2.", initial=0
+    )
+    wrong_answer2_1 = models.IntegerField(
+        doc="Counts the number of wrong guesses for CQ2_1.", initial=0
+    )
+    wrong_answer2_2 = models.IntegerField(
+        doc="Counts the number of wrong guesses for CQ2_2.", initial=0
+    )
+    wrong_answer3_1 = models.IntegerField(
+        doc="Counts the number of wrong guesses for CQ3_1.", initial=0
+    )
+    wrong_answer3_2 = models.IntegerField(
+        doc="Counts the number of wrong guesses for CQ3_2.", initial=0
+    )
+    CQ1_1 = models.IntegerField(
+        doc="Comprehension Question 1.1",
+        # initial=int(Constants.initial_endowment),
+        blank=True,
+    )
+    CQ1_2 = models.IntegerField(
+        doc="Comprehension Question 1.2",
+        # initial=int(Constants.initial_endowment),
+        blank=True,
+    )
+    CQ2_1 = models.IntegerField(
+        doc="Comprehension Question 2.1",
[…]

### 2022-11-03 oTree/Intro/models.py

@@ -1,107 +1,0 @@
-from otree.api import (
-    models,
-    widgets,
-    BaseConstants,
-    BaseSubsession,
-    BaseGroup,
-    BasePlayer,
-    Currency as c,
-    currency_range,
-)
-
-
-author = "Hauke Roggenkamp"
-
-doc = """
-Welcome participants, display instructions and comprehension questions.
-"""
-
-
-class Constants(BaseConstants):
-    name_in_url = "Intro"
-    players_per_group = None
-    num_rounds = 1
-
-    group_size = 4
-    num_others_per_group = group_size - 1
-    initial_endowment = 20
-    efficiency_factor = 1.5 # (MPCR) Marginal Per Capita Return per round
-    rate_of_return = (efficiency_factor - 1)*100
-
-
-class Subsession(BaseSubsession):
-    pass
-
-
-class Group(BaseGroup):
-    pass
-
-
-class Player(BasePlayer):
-    # Tracking Fields
-    window_width = models.IntegerField(doc="Documents the respondent's browser window's width.")
-    window_height = models.IntegerField(doc="Documents the respondent's browser window's height.")
-    browser = models.StringField(doc="Documents the respondent's browser (incl. its version).")
-
-    # Wrong Answers
-    wrong_answer1_1 = models.IntegerField(doc="Counts the number of wrong guesses for CQ1_1.", initial=0)
-    wrong_answer1_2 = models.IntegerField(doc="Counts the number of wrong guesses for CQ1_2.", initial=0)
-    wrong_answer2_1 = models.IntegerField(doc="Counts the number of wrong guesses for CQ2_1.", initial=0)
-    wrong_answer2_2 = models.IntegerField(doc="Counts the number of wrong guesses for CQ2_2.", initial=0)
-    wrong_answer3_1 = models.IntegerField(doc="Counts the number of wrong guesses for CQ3_1.", initial=0)
-    wrong_answer3_2 = models.IntegerField(doc="Counts the number of wrong guesses for CQ3_2.", initial=0)
-
-
-
-    CQ1_1 = models.IntegerField(doc="Comprehension Question 1.1",
-                                # initial=int(Constants.initial_endowment),
-                                blank = True)
-    def CQ1_1_error_message(self, value):
-        if value != int(Constants.initial_endowment):
-            self.wrong_answer1_1 += 1
-            return "Leider falsch."
-
-    CQ1_2 = models.IntegerField(doc="Comprehension Question 1.2",
[…]

### 2022-11-03 oTree/Intro/tests.py

@@ -1,15 +1,15 @@
 from otree.api import Currency as c, currency_range
-from . import pages
-from ._builtin import Bot
+from . import *
+from otree.api import Bot
 from otree.api import Submission
 
-from .models import Constants
+
 
 
 class PlayerBot(Bot):
     def play_round(self):
-        yield pages.Intro_Welcome, dict(window_width=1, window_height=1, browser="Chrome Canary")
-        yield pages.Intro_Instructions, dict(CQ1_1=int(Constants.initial_endowment),
+        yield Intro_Welcome, dict(window_width=1, window_height=1, browser="Chrome Canary")
+        yield Intro_Instructions, dict(CQ1_1=int(Constants.initial_endowment),
                                              CQ1_2=int(Constants.initial_endowment),
                                              CQ2_1=int(Constants.initial_endowment * Constants.efficiency_factor),
                                              CQ2_2=int(Constants.initial_endowment * Constants.efficiency_factor),

### 2022-11-03 oTree/Outro/__init__.py

@@ -1,0 +1,234 @@
+from otree.api import *
+
+
+author = "Hauke Roggenkamp"
+doc = """
+Elicit covariates and display results
+"""
+
+
+class Constants(BaseConstants):
+    name_in_url = 'Outro'
+    players_per_group = None
+    num_rounds = 1
+
+
+class Subsession(BaseSubsession):
+    pass
+
+
+class Group(BaseGroup):
+    pass
+
+
+class Player(BasePlayer):
+    # Gächter et al's (2017, JPE) Personality Questions
+    PQ01 = models.IntegerField(
+        widget=widgets.RadioSelect,
+        choices=[0, 1, 2, 3, 4, 5, 6],
+        label="Ich kann schnell denken.",
+        doc="I am a quick thinker",
+    )
+    PQ02 = models.IntegerField(
+        widget=widgets.RadioSelect,
+        choices=[0, 1, 2, 3, 4, 5, 6],
+        label="Ich fühle mich schnell angegriffen.",
+        doc="I get easily offended",
+    )
+    PQ03 = models.IntegerField(
+        widget=widgets.RadioSelect,
+        choices=[0, 1, 2, 3, 4, 5, 6],
+        label="Ich bin sehr zufrieden mit mir.",
+        doc="I am very satisfied with myself",
+    )
+    PQ04 = models.IntegerField(
+        widget=widgets.RadioSelect,
+        choices=[0, 1, 2, 3, 4, 5, 6],
+        label="Ich bin sehr auf andere angewiesen.",
+        doc="I am very dependent on others",
+    )
+    PQ05 = models.IntegerField(
+        widget=widgets.RadioSelect,
+        choices=[0, 1, 2, 3, 4, 5, 6],
+        label="Ich bin grundsätzlich glücklich.",
+        doc="Generally speaking, I am happy",
+    )
+    PQ06 = models.IntegerField(
+        widget=widgets.RadioSelect,
+        choices=[0, 1, 2, 3, 4, 5, 6],
+        label="Arbeit spielt eine wichtige Rolle in meinem Leben.",
+        doc="Work plays a very important role in my life",
+    )
+    PQ07 = models.IntegerField(
+        widget=widgets.RadioSelect,
+        choices=[0, 1, 2, 3, 4, 5, 6],
+        label="Familie spielt eine sehr wichtige Rolle in meinem Leben.",
+        doc="Family plays a very important role in my life",
+    )
[…]

### 2022-11-03 oTree/Outro/tests.py

@@ -1,12 +1,12 @@
 from otree.api import Currency as c, currency_range
-from . import pages
-from ._builtin import Bot
-from .models import Constants
+from . import *
+from otree.api import Bot
+
 import random
 
 class PlayerBot(Bot):
     def play_round(self):
-        yield pages.Outro_Personality, dict(PQ01=random.randint(0, 6),
+        yield Outro_Personality, dict(PQ01=random.randint(0, 6),
                                             PQ02=random.randint(0, 6),
                                             PQ03=random.randint(0, 6),
                                             PQ04=random.randint(0, 6),
@@ -20,9 +20,9 @@ class PlayerBot(Bot):
                                             PQ12=random.randint(0, 6),
                                             PQ13=random.randint(0, 6),
                                             PQ14=random.randint(0, 6))
-        yield pages.Outro_Covariates, dict(Age=random.randint(18, 66),
+        yield Outro_Covariates, dict(Age=random.randint(18, 66),
                                            Gender=random.choice(["diverse", "male", "female", "not specified"]),
                                            Education=random.randint(0, 8),
                                            Income=random.randint(0, 5))
-        yield pages.Outro_CLICCS, dict(CLICCS1="lorem ipsum 1", CLICCS2="lorem ipsum 2")
+        yield Outro_CLICCS, dict(CLICCS1="lorem ipsum 1", CLICCS2="lorem ipsum 2")
 

### 2022-11-03 oTree/_REMOVE_SELF_BACKUP/HLPL/tests.py

@@ -1,0 +1,20 @@
+from otree.api import Currency as c, currency_range
+from . import pages
+from ._builtin import Bot
+from .models import Constants
+import random
+
+
+class PlayerBot(Bot):
+    def play_round(self):
+        yield pages.HLPL_Decision, dict(choice_1="lottery",
+                                             choice_2="lottery",
+                                             choice_3="lottery",
+                                             choice_4="lottery",
+                                             choice_5="lottery",
+                                             choice_6= random.choice(["lottery", "certainty"]),
+                                             choice_7="certainty",
+                                             choice_8="certainty",
+                                             choice_9="certainty",
+                                             choice_10="certainty",
+                                             choice_11="certainty")

### 2022-11-03 oTree/_REMOVE_SELF_BACKUP/Intro/models.py

@@ -1,0 +1,107 @@
+from otree.api import (
+    models,
+    widgets,
+    BaseConstants,
+    BaseSubsession,
+    BaseGroup,
+    BasePlayer,
+    Currency as c,
+    currency_range,
+)
+
+
+author = "Hauke Roggenkamp"
+
+doc = """
+Welcome participants, display instructions and comprehension questions.
+"""
+
+
+class Constants(BaseConstants):
+    name_in_url = "A_Intro"
+    players_per_group = None
+    num_rounds = 1
+
+    group_size = 4
+    num_others_per_group = group_size - 1
+    initial_endowment = 20
+    efficiency_factor = 1.5 # (MPCR) Marginal Per Capita Return per round
+    rate_of_return = (efficiency_factor - 1)*100
+
+
+class Subsession(BaseSubsession):
+    pass
+
+
+class Group(BaseGroup):
+    pass
+
+
+class Player(BasePlayer):
+    # Tracking Fields
+    window_width = models.IntegerField(doc="Documents the respondent's browser window's width.")
+    window_height = models.IntegerField(doc="Documents the respondent's browser window's height.")
+    browser = models.StringField(doc="Documents the respondent's browser (incl. its version).")
+
+    # Wrong Answers
+    wrong_answer1_1 = models.IntegerField(doc="Counts the number of wrong guesses for CQ1_1.", initial=0)
+    wrong_answer1_2 = models.IntegerField(doc="Counts the number of wrong guesses for CQ1_2.", initial=0)
+    wrong_answer2_1 = models.IntegerField(doc="Counts the number of wrong guesses for CQ2_1.", initial=0)
+    wrong_answer2_2 = models.IntegerField(doc="Counts the number of wrong guesses for CQ2_2.", initial=0)
+    wrong_answer3_1 = models.IntegerField(doc="Counts the number of wrong guesses for CQ3_1.", initial=0)
+    wrong_answer3_2 = models.IntegerField(doc="Counts the number of wrong guesses for CQ3_2.", initial=0)
+
+
+
+    CQ1_1 = models.IntegerField(doc="Comprehension Question 1.1",
+                                # initial=int(Constants.initial_endowment),
+                                blank = True)
+    def CQ1_1_error_message(self, value):
+        if value != int(Constants.initial_endowment):
+            self.wrong_answer1_1 += 1
+            return "Leider falsch."
+
+    CQ1_2 = models.IntegerField(doc="Comprehension Question 1.2",
[…]

### 2022-11-03 oTree/_REMOVE_SELF_BACKUP/Intro/tests.py

@@ -1,0 +1,18 @@
+from otree.api import Currency as c, currency_range
+from . import pages
+from ._builtin import Bot
+from otree.api import Submission
+
+from .models import Constants
+
+
+class PlayerBot(Bot):
+    def play_round(self):
+        yield pages.Intro_Welcome, dict(window_width=1, window_height=1, browser="Chrome Canary")
+        yield pages.Intro_Instructions, dict(CQ1_1=int(Constants.initial_endowment),
+                                             CQ1_2=int(Constants.initial_endowment),
+                                             CQ2_1=int(Constants.initial_endowment * Constants.efficiency_factor),
+                                             CQ2_2=int(Constants.initial_endowment * Constants.efficiency_factor),
+                                             #MCQ_1=['2', '3'], MCQ_2=['2', '3'],
+                                             CQ3_1=int(30 + Constants.efficiency_factor * 40 / Constants.group_size),
+                                             CQ3_2=True)

### 2022-11-03 oTree/_REMOVE_SELF_BACKUP/Outro/tests.py

@@ -1,0 +1,28 @@
+from otree.api import Currency as c, currency_range
+from . import pages
+from ._builtin import Bot
+from .models import Constants
+import random
+
+class PlayerBot(Bot):
+    def play_round(self):
+        yield pages.Outro_Personality, dict(PQ01=random.randint(0, 6),
+                                            PQ02=random.randint(0, 6),
+                                            PQ03=random.randint(0, 6),
+                                            PQ04=random.randint(0, 6),
+                                            PQ05=random.randint(0, 6),
+                                            PQ06=random.randint(0, 6),
+                                            PQ07=random.randint(0, 6),
+                                            PQ08=random.randint(0, 6),
+                                            PQ09=random.randint(0, 6),
+                                            PQ10=random.randint(0, 6),
+                                            PQ11=random.randint(0, 6),
+                                            PQ12=random.randint(0, 6),
+                                            PQ13=random.randint(0, 6),
+                                            PQ14=random.randint(0, 6))
+        yield pages.Outro_Covariates, dict(Age=random.randint(18, 66),
+                                           Gender=random.choice(["diverse", "male", "female", "not specified"]),
+                                           Education=random.randint(0, 8),
+                                           Income=random.randint(0, 5))
+        yield pages.Outro_CLICCS, dict(CLICCS1="lorem ipsum 1", CLICCS2="lorem ipsum 2")
+

### 2022-11-03 oTree/_REMOVE_SELF_BACKUP/dPGG/models.py

@@ -1,0 +1,237 @@
+from otree.api import (
+    models,
+    widgets,
+    BaseConstants,
+    BaseSubsession,
+    BaseGroup,
+    BasePlayer,
+    Currency as c,
+    currency_range,
+)
+
+import math
+import random
+import time
+
+author = "Hauke Roggenkamp"
+
+doc = """
+Dynamic Public Goods Game where the current round's earnings determine the next round's endowment
+"""
+
+
+class Constants(BaseConstants):
+    name_in_url = "dPGG"
+    players_per_group = 4 # adjust Constants.group_size in A_Intro App when adjusting this
+    num_others_per_group = players_per_group - 1
+    num_rounds = 10
+    initial_endowment = 20
+    efficiency_factor = 1.5 # /4 = (MPCR) Marginal Per Capita Return per round
+    rate_of_return = (efficiency_factor - 1)*100
+
+    safe_rounds = 0 # number of rounds without any risk
+    threshold = 0.5 # fraction of a group's endowment that has to be contributed such that no disaster can occur
+    belief_elicitation_round = 1
+    elicitation_bonus = 30 # points
+    timeout = 4 # minutes
+    patience = 10 # minutes
+    patience_bonus = 20 # points
+
+
+
+class Subsession(BaseSubsession):
+    def creating_session(self):
+        print("lets go")
+        if self.round_number == 1:
+            for p in self.get_players():
+                p.participant.vars["belief_elicitation_round"] = Constants.belief_elicitation_round
+                p.participant.vars["endowments"] = []
+                p.participant.vars["stock"] = []
+                p.participant.vars["euros"] = []
+                p.participant.vars["is_dropout"] = False
+                p.participant.vars["is_residual_player"] = False
+                if not "wait_page_arrival" in p.participant.vars:
+                    p.participant.vars["wait_page_arrival"] = time.time()
+
+    def group_by_arrival_time_method(self, waiting_players):
+        if len(waiting_players) >= Constants.players_per_group:
+            return waiting_players[:Constants.players_per_group]
+        for player in waiting_players:
+            player.wait_time_left = int(math.ceil(Constants.patience - (time.time() - player.participant.vars['wait_page_arrival']) / 60))
+            if player.waiting_too_long():
+                player.participant.vars["is_residual_player"] = True
+                player.group.residual = True
+                # make a single-player group.
+                return [player]
+
+
+
+class Group(BaseGroup):
+
[…]

### 2022-11-03 oTree/_REMOVE_SELF_BACKUP/dPGG/tests.py

@@ -1,0 +1,31 @@
+from otree.api import Currency as c, currency_range
+from . import pages
+from ._builtin import Bot
+from otree.api import Submission
+from .models import Constants
+import random
+
+
+class PlayerBot(Bot):
+    def play_round(self):
+        if self.round_number <= self.session.config["num_rounds"]:
+            if self.round_number == Constants.belief_elicitation_round:
+                if self.session.config["belief_elicitation"]:
+                    yield pages.dPGG_Belief, dict(belief=random.randint(int(self.player.endowment/2),
+                                                                        self.player.endowment)*Constants.num_others_per_group
+                                                  )
+            yield Submission(pages.dPGG_Decision, # in Gächter et al, subjects first contribute around 60%, then 30%
+                             dict(contribution=int(self.player.endowment/2)),
+                             # dict(contribution=int((100 - 6 * self.round_number)/100 * random.randint(int(self.player.endowment/5*2.5), #HI==2.5,LO==2
+                             #                                                                           int(self.player.endowment/5*5))  #HI==5,  LO==3.5
+                             #                       )
+                             #      ),
+                             check_html=False)
+            if self.round_number == self.session.config["num_rounds"]:
+                yield pages.dPGG_Results
+                if random.randint(0, 100) > 90:
+                    a = 0
+                else:
+                    a = random.randint(1, 3)
+                yield pages.dPGG_Comprehension, dict(comprehension=a)
+                yield pages.dPGG_Donation, dict(donation=random.randint(0, int(self.player.endowment/2)))

### 2022-11-03 oTree/dPGG/__init__.py

@@ -1,0 +1,449 @@
+import math
+import random
+import time
+
+from otree.api import *
+
+
+author = "Hauke Roggenkamp"
+doc = """
+Dynamic Public Goods Game where the current round's earnings determine the next round's endowment
+"""
+
+
+class Constants(BaseConstants):
+    name_in_url = "dPGG"
+    players_per_group = 4  # adjust Constants.group_size in A_Intro App when adjusting this
+    num_others_per_group = players_per_group - 1
+    num_rounds = 10
+    initial_endowment = 20
+    efficiency_factor = 1.5  # /4 = (MPCR) Marginal Per Capita Return per round
+    rate_of_return = (efficiency_factor - 1) * 100
+    safe_rounds = 0  # number of rounds without any risk
+    threshold = 0.5  # fraction of a group's endowment that has to be contributed such that no disaster can occur
+    belief_elicitation_round = 1
+    elicitation_bonus = 30  # points
+    timeout = 4  # minutes
+    patience = 10  # minutes
+    patience_bonus = 20  # points
+
+
+class Subsession(BaseSubsession):
+    pass
+
+
+class Group(BaseGroup):
+    residual = models.BooleanField(initial=False, doc="if true, group is incomplete")
+    EWE = models.BooleanField(initial=False, doc="if true, extreme weather event occurred")
+    total_contribution = models.IntegerField(doc="sum of contributions in this round")
+    average_contribution = models.FloatField(doc="average contribution in this round")
+    individual_share = models.IntegerField(
+        doc="individual share each player receives from this round's contributions"
+    )
+    bot_active = models.BooleanField(
+        doc="denotes whether player in group dropped out such that a bot takes over", initial=False
+    )
+    wealth = models.IntegerField(doc="sum of endowments at the beginning of a round")
+
+
+class Player(BasePlayer):
+    comprehension = models.IntegerField(
+        doc="Respondent's understanding of the tasks",
+        label="Haben Sie die Aufgabe gut verstanden?",
+        choices=[[0, "Nein"], [1, "Eher nicht"], [2, "Eher schon"], [3, "Ja"]],
+        widget=widgets.RadioSelect,
+    )
+    donation = models.IntegerField(doc="Participant's donation (in points) for carbon offsetting")
+    review_instructions = models.IntegerField(
+        doc="Counts the number of times a player reviews instructions.", initial=0, blank=True
+    )
+    review_contact = models.IntegerField(
[…]

### 2022-11-03 oTree/dPGG/models.py

@@ -1,236 +1,0 @@
-from otree.api import (
-    models,
-    widgets,
-    BaseConstants,
-    BaseSubsession,
-    BaseGroup,
-    BasePlayer,
-    Currency as c,
-    currency_range,
-)
-
-import math
-import random
-import time
-
-author = "Hauke Roggenkamp"
-
-doc = """
-Dynamic Public Goods Game where the current round's earnings determine the next round's endowment
-"""
-
-
-class Constants(BaseConstants):
-    name_in_url = "dPGG"
-    players_per_group = 4 # adjust Constants.group_size in Intro App when adjusting this
-    num_others_per_group = players_per_group - 1
-    num_rounds = 10
-    initial_endowment = 20
-    efficiency_factor = 1.5 # /4 = (MPCR) Marginal Per Capita Return per round
-    rate_of_return = (efficiency_factor - 1)*100
-
-    safe_rounds = 0 # number of rounds without any risk
-    threshold = 0.5 # fraction of a group's endowment that has to be contributed such that no disaster can occur
-    belief_elicitation_round = 1
-    elicitation_bonus = 30 # points
-    timeout = 4 # minutes
-    patience = 10 # minutes
-    patience_bonus = 20 # points
-
-
-
-class Subsession(BaseSubsession):
-    def creating_session(self):
-        if self.round_number == 1:
-            for p in self.get_players():
-                p.participant.vars["belief_elicitation_round"] = Constants.belief_elicitation_round
-                p.participant.vars["endowments"] = []
-                p.participant.vars["stock"] = []
-                p.participant.vars["euros"] = []
-                p.participant.vars["is_dropout"] = False
-                p.participant.vars["is_residual_player"] = False
-                if not "wait_page_arrival" in p.participant.vars:
-                    p.participant.vars["wait_page_arrival"] = time.time()
-
-    def group_by_arrival_time_method(self, waiting_players):
-        if len(waiting_players) >= Constants.players_per_group:
-            return waiting_players[:Constants.players_per_group]
-        for player in waiting_players:
-            player.wait_time_left = int(math.ceil(Constants.patience - (time.time() - player.participant.vars['wait_page_arrival']) / 60))
-            if player.waiting_too_long():
-                player.participant.vars["is_residual_player"] = True
-                player.group.residual = True
-                # make a single-player group.
-                return [player]
-
-
-
-class Group(BaseGroup):
-
-    residual = models.BooleanField(initial=False, doc="if true, group is incomplete")
[…]

### 2022-11-03 oTree/dPGG/tests.py

@@ -1,8 +1,8 @@
 from otree.api import Currency as c, currency_range
-from . import pages
-from ._builtin import Bot
+from . import *
+from otree.api import Bot
 from otree.api import Submission
-from .models import Constants
+
 import random
 
 
@@ -11,10 +11,10 @@ class PlayerBot(Bot):
         if self.round_number <= self.session.config["num_rounds"]:
             if self.round_number == Constants.belief_elicitation_round:
                 if self.session.config["belief_elicitation"]:
-                    yield pages.dPGG_Belief, dict(belief=random.randint(int(self.player.endowment/2),
+                    yield dPGG_Belief, dict(belief=random.randint(int(self.player.endowment/2),
                                                                         self.player.endowment)*Constants.num_others_per_group
                                                   )
-            yield Submission(pages.dPGG_Decision, # in Gächter et al, subjects first contribute around 60%, then 30%
+            yield Submission(dPGG_Decision, # in Gächter et al, subjects first contribute around 60%, then 30%
                              dict(contribution=int(self.player.endowment/2)),
                              # dict(contribution=int((100 - 6 * self.round_number)/100 * random.randint(int(self.player.endowment/5*2.5), #HI==2.5,LO==2
                              #                                                                           int(self.player.endowment/5*5))  #HI==5,  LO==3.5
@@ -22,10 +22,10 @@ class PlayerBot(Bot):
                              #      ),
                              check_html=False)
             if self.round_number == self.session.config["num_rounds"]:
-                yield pages.dPGG_Results
+                yield dPGG_Results
                 if random.randint(0, 100) > 90:
                     a = 0
                 else:
                     a = random.randint(1, 3)
-                yield pages.dPGG_Comprehension, dict(comprehension=a)
-                yield pages.dPGG_Donation, dict(donation=random.randint(0, int(self.player.endowment/2)))
+                yield dPGG_Comprehension, dict(comprehension=a)
+                yield dPGG_Donation, dict(donation=random.randint(0, int(self.player.endowment/2)))

### 2022-11-03 oTree/settings.py

@@ -2,13 +2,13 @@ from os import environ
 
 SESSION_CONFIGS = [
     dict(
-        name="GMTV",
-        display_name="GMTV Replication",
+        name="B_GMTV",
+        display_name="B_GMTV Replication",
         num_rounds=10,
         num_demo_participants=4,
         risk=0.0,
         belief_elicitation=False,
-        app_sequence=["Intro", "dPGG", "HLPL", "Outro"]
+        app_sequence=["A_Intro", "dPGG", "HLPL", "Outro"]
     ),
     #     dict(
     #     name="HLPL",
@@ -62,8 +62,8 @@ ADMIN_PASSWORD = environ.get('OTREE_ADMIN_PASSWORD')
 
 DEMO_PAGE_INTRO_HTML = """ """
 
-SECRET_KEY = environ.get('OTREE_SECRET_KEY')
-# SECRET_KEY = ""
+# SECRET_KEY = environ.get('OTREE_SECRET_KEY')
+SECRET_KEY = ""
 
 # if an app is included in SESSION_CONFIGS, you don't need to list it here
 INSTALLED_APPS = ['otree']

### 2022-11-03 otreeLite/A_Intro/__init__.py

@@ -13,6 +13,7 @@ class C(BaseConstants):
     NUM_ROUNDS = 1
     EARNINGS_TEMPLATE = "A_Intro/C_Earnings.html"
     SHOCKS_TEMPLATE = "A_Intro/D_Shocks.html"
+    DEMO_TEMPLATE = "A_Intro/E_Demo.html"
 
 
 class Subsession(BaseSubsession):

### 2022-11-04 analysis/quarto/paper.qmd
work on paper and template.

@@
 
+```{r constants}
+SHOW_UP_FEE <- 5
+EXCHANGE_RATE <- 1/20
+```
+
 ```{r design}
@@
 
+```{r earnings}
+
+# This chunk requires raw data
+files <- list.files(path = "../../data/replication/",
+                       recursive = TRUE,
+                       full.names = TRUE)
+csvs <- list()
+
+for(i in files){
+  name <- str_extract(string = i,
+                      pattern = "2021.*")
+
+  temp <- read.csv(i, 
+                   stringsAsFactors = FALSE) %>%
+    data.table()
+
+  csvs[[name]] <- temp
+}
+
+full <- rbindlist(l = csvs,
+                  use.names = TRUE) %>%
+  data.table()
+
+# subset data of participants who have completed the study
+tmp <- full[participant._index_in_pages >= 76 & 
+              participant.time_started != "" & 
+              !(is.na(dPGG.1.player.contribution)) &
+              participant.label != ""]
+
+# calculate total payoff
+tmp[, finalPayoff := (dPGG.10.player.stock - dPGG.10.player.donation + HLPL.1.player.payoff) * EXCHANGE_RATE + SHOW_UP_FEE]
+
+earningsMean <- tmp[, mean(finalPayoff, na.rm = TRUE)]
+earningsSD   <- tmp[, sd(finalPayoff, na.rm = TRUE)]
+```
+
 <!-- PAPER STARTS HERE -->
@@
 
-In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific replication_ of one treatment of GMTV's dynamic public good game.
+In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific replication_^[@Parsons2022 use the term of a _conceptual replication_ which means the same.] of one treatment of GMTV's dynamic public good game.
 The pure replication re-analyzes the original data.
@@
 
-As in the NOPUNISH 10 Period treatment of GMTV, I ran sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of $N_i^1 = 20$ tokens, $T=10$ periods, a private account with a return of $1$ and a group account with a return of $1.5$ ($\Rightarrow$ MPCR$\equiv \frac{1.5}{4}$), such that:
+As in the NOPUNISH 10 Period treatment of GMTV, I ran sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of $N_i^1 = 20$ tokens^[A token was worth `r EXCHANGE_RATE` Euros.], $T=10$ periods, a private account with a return of $1$ and a group account with a return of $1.5$ ($\Rightarrow$ MPCR$\equiv \frac{1.5}{4}$), such that:
 
@@
 
+## Voluntary Climate Action (VCA)
+
+Like GMTV we employ a real giving task after the abstract game.
+In contrast to GMTV and like @GKLS2020, we employed a VCA, where they could donate (some of) their earnings to offset carbon dioxide (that is, by retiring emission permits from the EU ETS).^[Importantly, @GKLS2020 made the VCA decision with a fresh endowment _before_ they played the abstract game.
+I deviate from their procedure to match GMTV's procedure.]
+To ensure that each participant had the same basic level of information about the impact of their decision, I provided some basic information about the mechanism.
+The information also highlighted that the mitigation came into operation on a European level.
+Finally, I informed the participants that the documentation of individual and aggregate contributions were posted immediately after the experiments online.
+To avoid privacy or social image concerns, participants learned their unique and random IDs, which they needed to identify their individual contributions.
+This document certified that their contributions have been used to offset [1.82 tons](https://www.compensators.org/compensatelist/?searchterm=stefan+traub) of carbon dioxide emissions.
+
 ## Sample {#sec-sample}
@@
 
-The experiment's source code be found on [GitHub](https://github.com/Howquez/coopUncertainty).^[https://github.com/Howquez/coopUncertainty]
-
 ## Procedure {#sec-procedure}
@@
 At the end of the last period, participants saw results of all periods.
-Subsequently, they were exposed to a voluntary climate action, where they could donate (some of) their earnings to offset carbon dioxide.
-Subsequently, I elicited risk preferences [@HoltLaury2002] and finished with GMTV's questionnaire.
+Subsequently, they made their VCA decision, before I elicited risk preferences [@HoltLaury2002] and finished with GMTV's questionnaire.
 
@@
 
+```{r totalTimeSpent}
+tmp <- duration[page_index == 1 | page_index == 76, 
+                .(page_index, participant_code, page_submission)]
+tmp[order(participant_code, page_index), 
+    total := page_submission - data.table::shift(x = page_submission,
+                                                 n = 1,
+                                                 type = "lag"),
+    by = participant_code]
+
+total_completion_time <- tmp[!is.na(total), mean(total/ 60) %>% round()]
+```
+
+The experiment lasted around `r total_completion_time` minutes on average.
+The earnings of the average subject were `r earningsMean %>% round(digits = 2)` Euros (sd = `r earningsSD  %>% round(digits = 2)`).^[This values include earnings from the incentivized risk elicitation task that are not part of the analysis.]
+
+## Pre-registration {#sec-registration}
+
+Parts of the analyses are pre-registered [@preregistration].
+In addition, I pre-registered the exact analyses I planned to run when I designed designed the experiment on [GitHub](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.].
+GitHub is a website and cloud-based service where developers---and researchers alike---can store and manage their code.
+The service is based on Git^[Git is a specific open-source version control system developed in 2005.] and designed for version control.
+Importantly, changes are timestamped and can be tracked.
+Moreover, one can create branches, that is, duplicates of code -- either to work collaborative or to archive a certain state.
+Accordingly, I archived my analyses scripts and created a [branch](https://github.com/Howquez/coopUncertainty/tree/July21Replication) a few days _before_ we collected data.
+
+The analysis that makes the most sense now that you have collected the data is a little different, though: Because the more representative subject pool was exhausted earlier than expected, I recruited students unwantedly and changed parts of the scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd] Because the originally planned analysis code is archived and reproducible, these changes are transparent.
+
 # Results {#sec-results}
@@
 ## Pre-registered GMTV Replication {#sec-replication}
-
-The analyses in this section were pre-registered [@preregistration].
-I also pre-registered a RMarkdown file with the exact code I intended to use [here](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.] Even though I had to adjust a few lines of code, the main findings in the following section can also be replicated using the pre-registered code.
 

### 2022-11-04 analysis/quarto/paper.tex
work on paper and template.

@@
 \end{keyword}
-\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, sharp corners, frame hidden, boxrule=0pt, breakable, enhanced, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
+\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, frame hidden, sharp corners, enhanced, breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
 
@@
 In the terminology of \citet{Hamermesh2007}, I ran both a \emph{pure} as
-well as a \emph{scientific replication} of one treatment of GMTV's
-dynamic public good game. The pure replication re-analyzes the original
-data. \protect\hyperlink{A:-Pure-Replication}{Appendix A} documents
+well as a \emph{scientific replication}\footnote{\citet{Parsons2022} use
+  the term of a \emph{conceptual replication} which means the same.} of
+one treatment of GMTV's dynamic public good game. The pure replication
+re-analyzes the original data.
+\protect\hyperlink{A:-Pure-Replication}{Appendix A} documents
 \href{}{errors I identified} in the original paper. The scientific
@@
 groups of four (\(i \in I=\{1,2,3,4\}\)), an initial endowment of
-\(N_i^1 = 20\) tokens, \(T=10\) periods, a private account with a return
-of \(1\) and a group account with a return of \(1.5\) (\(\Rightarrow\)
-MPCR\(\equiv \frac{1.5}{4}\)), such that:
+\(N_i^1 = 20\) tokens\footnote{A token was worth 0.05 Euros.}, \(T=10\)
+periods, a private account with a return of \(1\) and a group account
+with a return of \(1.5\) (\(\Rightarrow\) MPCR\(\equiv \frac{1.5}{4}\)),
+such that:
 
@@
 good game
+
+\hypertarget{voluntary-climate-action-vca}{%
+\subsection{Voluntary Climate Action
+(VCA)}\label{voluntary-climate-action-vca}}
+
+Like GMTV we employ a real giving task after the abstract game. In
+contrast to GMTV and like \citet{GKLS2020}, we employed a VCA, where
+they could donate (some of) their earnings to offset carbon dioxide
+(that is, by retiring emission permits from the EU ETS).\footnote{Importantly,
+  \citet{GKLS2020} made the VCA decision with a fresh endowment
+  \emph{before} they played the abstract game. I deviate from their
+  procedure to match GMTV's procedure.} To ensure that each participant
+had the same basic level of information about the impact of their
+decision, I provided some basic information about the mechanism. The
+information also highlighted that the mitigation came into operation on
+a European level. Finally, I informed the participants that the
+documentation of individual and aggregate contributions were posted
+immediately after the experiments online. To avoid privacy or social
+image concerns, participants learned their unique and random IDs, which
+they needed to identify their individual contributions. This document
+certified that their contributions have been used to offset
+\href{https://www.compensators.org/compensatelist/?searchterm=stefan+traub}{1.82
+tons} of carbon dioxide emissions.
 
@@
 
-The experiment's source code be found on
-\href{https://github.com/Howquez/coopUncertainty}{GitHub}.\footnote{https://github.com/Howquez/coopUncertainty}
-
 \hypertarget{sec-procedure}{%
@@
 last period, participants saw results of all periods. Subsequently, they
-were exposed to a voluntary climate action, where they could donate
-(some of) their earnings to offset carbon dioxide. Subsequently, I
-elicited risk preferences \citep{HoltLaury2002} and finished with GMTV's
-questionnaire.
+made their VCA decision, before I elicited risk preferences
+\citep{HoltLaury2002} and finished with GMTV's questionnaire.
 
@@
 
+The experiment lasted around 25 minutes on average. The earnings of the
+average subject were 11.23 Euros (sd = 4.85).\footnote{This values
+  include earnings from the incentivized risk elicitation task that are
+  not part of the analysis.}
+
+\hypertarget{sec-registration}{%
+\subsection{Pre-registration}\label{sec-registration}}
+
+Parts of the analyses are pre-registered \citep{preregistration}. In
+addition, I pre-registered the exact analyses I planned to run when I
+designed designed the experiment on
+\href{https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd}{GitHub}.\footnote{https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd
+  to run the code, you need to executed the .Rmd files in this
+  repository in the order that is indicated by its file names.}. GitHub
+is a website and cloud-based service where developers---and researchers
+alike---can store and manage their code. The service is based on
+Git\footnote{Git is a specific open-source version control system
+  developed in 2005.} and designed for version control. Importantly,
+changes are timestamped and can be tracked. Moreover, one can create
+branches, that is, duplicates of code -- either to work collaborative or
+to archive a certain state. Accordingly, I archived my analyses scripts
+and created a
+\href{https://github.com/Howquez/coopUncertainty/tree/July21Replication}{branch}
+a few days \emph{before} we collected data.
+
+The analysis that makes the most sense now that you have collected the
+data is a little different, though: Because the more representative
+subject pool was exhausted earlier than expected, I recruited students
+unwantedly and changed parts of the scripts.\footnote{The source code of
+  this document contains the analysis and can be found
+  \href{https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}{here}:
+  https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}
+Because the originally planned analysis code is archived and
+reproducible, these changes are transparent.
+
 \hypertarget{sec-results}{%
@@
 \subsection{Pre-registered GMTV Replication}\label{sec-replication}}
-
-The analyses in this section were pre-registered
-\citep{preregistration}. I also pre-registered a RMarkdown file with the
-exact code I intended to use
-\href{https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd}{here}.\footnote{https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd
-  to run the code, you need to executed the .Rmd files in this
-  repository in the order that is indicated by its file names.} Even
-though I had to adjust a few lines of code, the main findings in the
-following section can also be replicated using the pre-registered code.
 

### 2022-11-05 analysis/quarto/paper.qmd
update paper

@@
 There are many settings in which current decisions affect future outcomes and with it, future decision spaces.
-Opting for environmental friendly policies today not only reduces carbon dioxide omissions but also helps us to reach the Paris climate targets tomorrow.
-Deferring these policies, the targets can be reached as well---but with less flexibility.
-Hence, today's actions (or the omission thereof) not only affect intermediate results but also the number of paths one can choose to reach certain goals.
+Opting for environmental friendly policies today not only reduces carbon dioxide omissions immediately but also helps us to reach the Paris climate targets tomorrow.
+Deferring these policies, may not necessarily prevent us from reaching these targets, but it makes it more difficult in the future.
+Hence, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of paths one can choose to reach certain goals.
 
 Standard public good games---although often intended to inform climate policies^[See @GKLS2020 [p.
-1] for numerous references.]---miss these temporal interdependencies because participants have the same set of actions in each period.
-A game implemented by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017] (hereafter, GMTV) as well as Stefan Große (2011, unpublished) incorporated interdependencies into a _dynamic_ public good game with students in Nottingham, England and Erfurt, Germany.
-
-Because their setting is more realistic, one wonders whether it is better suited to inform public policy.
-To answer this question, I replicated parts of GMTV's experiment with different samples.
-In addition, I observed the participant's behavior in voluntary climate actions (VCA).
+1] for numerous references.]---miss these temporal interdependencies simply because participants have the same set of actions in each period.
+Accordingly, participants' actions in a given period do not affect their number of actions in subsequent periods.
+A game implemented by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017] (hereafter, GMTV) as well as Stefan Große (2011, unpublished) incorporated interdependencies into a _dynamic_ public good game.
+Here, participants' actions in a given period affect their number of actions in subsequent periods.
+Because there is surprisingly little experimental research on these interdependencies^[One exemption are @Moser2019, who built on GMTV's design do investigate leadership.], I replicated one of their treatments.
+
+@GKLS2020 find that standard public good games do not generalize to real-world climate action.
+Because the dynamic setting has a more realistic property, one wonders whether it is better suited to inform public policy.
+To answer this question, I ran the experiment with different samples^[GMTV ran their experiments with students in Nottingham, England.] online, that is, with participants who make their decisions in an environment whcih is more natural than the lab.
+In addition, I observed the participants' behavior in voluntary climate actions (VCA).
 This yielded a setting similar to @GKLS2020's which allows me to analyze how behavior in the abstract game translates into real-world action across samples.
 
-I utilized an inexperienced sample that has not been exposed to interactive experiments before.
-Furthermore, I conducted the experiment online.
-This required me to make the experiment's software robust to minimize attrition.
-Because I observed metrics to assess the fluency and feasibility of online experiments, this study also serves as a case study like the one of @AGM2018.
+@AGM2018 conducted public good games in the lab and on MTurk to draw lessons from online experimentation.
+This study extends this literature [see also @GoodmanPaolacci2017] by focusing on a completely inexperienced sample that has not been exposed to interactive experiments before.
+This required me to design a robust (and thus, more complex) software to minimize attrition.
+In exchange, the online setting allowed me to also collect paradata to assess the fluency and feasibility of the experiment.
+This article reports on both topics: the robust design as well as the feasibility.
 
@@
 
-As in the NOPUNISH 10 Period treatment of GMTV, I ran sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of $N_i^1 = 20$ tokens^[A token was worth `r EXCHANGE_RATE` Euros.], $T=10$ periods, a private account with a return of $1$ and a group account with a return of $1.5$ ($\Rightarrow$ MPCR$\equiv \frac{1.5}{4}$), such that:
+As in the NOPUNISH 10 Period treatment of GMTV, I ran sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of $N_i^1 = 20$ tokens^[A token was worth `r EXCHANGE_RATE` Euros.], $T=10$ periods, a private account with a return of $1$ and a group account with a return of $1.5$ ($\Rightarrow$ MPCR$\equiv \frac{1.5}{4}$).
+With $i$'s contribution in period $t$ being $c_i^t$, the model looks as follows:
 
@@
 $$
+
 What makes the game _dynamic_?
@@
 Like GMTV we employ a real giving task after the abstract game.
-In contrast to GMTV and like @GKLS2020, we employed a VCA, where they could donate (some of) their earnings to offset carbon dioxide (that is, by retiring emission permits from the EU ETS).^[Importantly, @GKLS2020 made the VCA decision with a fresh endowment _before_ they played the abstract game.
+In contrast to GMTV and like @GKLS2020, we employed a VCA, where they could donate any amount their earnings to offset carbon dioxide (that is, retirine emission permits from the EU ETS).^[Importantly, @GKLS2020 made the VCA decision with a fresh endowment _before_ they played the abstract game.
 I deviate from their procedure to match GMTV's procedure.]
@@
 The information also highlighted that the mitigation came into operation on a European level.
-Finally, I informed the participants that the documentation of individual and aggregate contributions were posted immediately after the experiments online.
+Finally, I informed the participants that the documentation of individual and aggregate contributions were to be posted immediately after the experiments online.
 To avoid privacy or social image concerns, participants learned their unique and random IDs, which they needed to identify their individual contributions.
-This document certified that their contributions have been used to offset [1.82 tons](https://www.compensators.org/compensatelist/?searchterm=stefan+traub) of carbon dioxide emissions.
+The document certified that their contributions have been used to offset [1.82 tons](https://www.compensators.org/compensatelist/?searchterm=stefan+traub) of carbon dioxide emissions.
 
@@
 I recruited the participants from the so called _[HamburgPanel](https://www.wiso.uni-hamburg.de/forschung/forschungslabor/umfragelabor/aktuelle-umfragen/hamburgpanel.html)_ using HROOT [@hroot].
-The panel is provided by the University of Hamburg's Research Laboratory, which used a randomized last digits approach to build the panel while drawing from the population of citizens from Hamburg, Germany.
+The panel is provided by the University of Hamburg's Research Laboratory, which used a randomized last digits approach to build the panel while drawing from the population of citizens of Hamburg, Germany.
 Because the sample was exhausted at one point, I also recruited students from the University of Hamburg.
 
-At the time I conducted the experiment, the representative sample was not familiar with interactive experiments.
+At the time I conducted the experiment, the more representative sample was not familiar with interactive experiments.
 In fact, I ran the first interactive group experiment with this sample.
-The students, in contrast, are used to this kind of experiments.
+The students, in contrast, were used to this kind of experiments.
 Recruiting them, I excluded those who have participated in a public goods game before.
-As a consequence, nonnaiveté is unlikely to affect the validity of my experiment [@GoodmanPaolacci2017 p.
+As a consequence, nonnaiveté is unlikely to affect the validity of the experiment [@GoodmanPaolacci2017 p.
 204].
@@
 Third, the underlying game was dynamic and interdependent.
-This makes dropouts not only more likely, but also more expensive which is why dropouts were a major concern implementing the experiment.
+This makes dropouts not only more likely but also more expensive, which is why attrition was a major concern implementing the experiment.
 
@@
 The [Highcharts library](https://www.highcharts.com/) made it easy to visualize results and to communicate dynamics.
-The oTree code snippets made it possible to handle dropouts, for instance, by replacing them with artificial bots (and informing the rest of the group thereof).
-Insofar, oTree served a good tool to consider the participants' user experience and thus, to make dropouts less likely.
+Insofar, oTree served a good tool to enhance the participants' user experience and thus, to make dropouts less likely.
+Furthermore, the oTree code snippets made it possible to handle dropouts.
+
+Which features were required to handle dropouts?
+First, participants had to be matched to form a group _after_ comprehension questions were answered successfully.
+Importantly, participants were grouped by the order they answered these questions to reduce waiting times.
+While waiting for other players to form the group, the participants saw a wait-page informing them that they are waiting for other participants to arrive and that they do not have to wait for longer than 10 minutes.
+The screen also informed them that they would receive a _patience bonus_ of one Euro after the expiration of that time (or what was left of it).
+Second, participants only had 10 minutes to make the first contribution and 4 minutes for the remaining contributions.
+After this time expired, participants were replaced by bots that made random contributions.
+In this case, the remaining group members were informed about the replacement.
+Both features were implemented to limit wait times and boredom for other participants.
+@sec-feasibility shows that the first feature became effective in some cases, wheres the second feature did not.
 
@@
 The experiment lasted around `r total_completion_time` minutes on average.
-The earnings of the average subject were `r earningsMean %>% round(digits = 2)` Euros (sd = `r earningsSD  %>% round(digits = 2)`).^[This values include earnings from the incentivized risk elicitation task that are not part of the analysis.]
+The earnings  averaged `r earningsMean %>% round(digits = 2)` Euros (sd = `r earningsSD  %>% round(digits = 2)`).^[This values include earnings from the incentivized risk elicitation task that is not part of the analysis.]
 
@@
 
-Parts of the analyses are pre-registered [@preregistration].
+Parts of the analyses were pre-registered in the American Economic Association's RCT Registry [@preregistration].
 In addition, I pre-registered the exact analyses I planned to run when I designed designed the experiment on [GitHub](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.].
@@
 
-The analysis that makes the most sense now that you have collected the data is a little different, though: Because the more representative subject pool was exhausted earlier than expected, I recruited students unwantedly and changed parts of the scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd] Because the originally planned analysis code is archived and reproducible, these changes are transparent.
+The analysis that makes the most sense now that I have collected the data is a little different though: Because the more representative subject pool was exhausted earlier than expected, I recruited students unwantedly and changed parts of the scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd] However, because the originally planned analysis code is archived and reproducible, these changes are transparent and easy to assess.
 
@@
 
+```{r reviewInformation}
+#| eval: false
+
+# to see how many people clicked on the popups to review instructions: 
+full[dPGG.1.player.review_instructions !=0, .N]
+full[dPGG.2.player.review_instructions !=0, .N]
+#...
+
+# or for contact information
+full[dPGG.1.player.review_contact !=0, .N]
+full[dPGG.2.player.review_contact !=0, .N]
+# ...
+
+```
+
 How did the participants, who have never participated in an online group experiment before, cope with the situation?
@@
 Another `r 44` answered with _"rather yes"_ while nobody indicated that he or she did not understand the situation at all.
-To analyze how participants coped with the situation, I consider three additional metrics: selection into the experiment,  attrition as well as the time spent on each page.
+There is some behavioral data supporting this finding: The user interface offered a popup to review instructions or contact information.
+I tracked both and find that none of the participants ever opened these popups even though they were clearly visible in the decision screen's header and introduced in the instructions.
+To  further analyze how participants coped with the situation, I consider three additional metrics: selection into the experiment, attrition as well as the time spent on each page.
 
@@
 
-**Result 3.** _Existing evidence overestimates the willingness to contribute to real public goods. This holds true for more representative samples and---to a lower degree---for student samples._
+**Result 3.** _Overall, contribution behavior is uncorrelated with the willingness to contribute to real public goods.
+This holds true for more representative samples and---to a lower degree---for student samples._
 
@@
 Third, contribution behavior in my abstract setting is, if anything, only weakly linked to behavior in the real world.
-This lack of generalizability can be counteracted, but not be solved, by the use of more representative samples.
 
@@
 The second result is of methodological importance: It highlights that even logistically complex experiments can be conducted online with---not only with clickworkers but also with a true general population sample.
-The third result questions whether recruiting from more representative samples is worth the efforts because it decreases transferability of results to the real world---at least, a little.
+The third result questions whether recruiting from more representative samples is worth the efforts because it decreases transferability of results to the real world---at least in this specific case.
 

### 2022-11-05 analysis/quarto/paper.tex
update paper

@@
 \end{keyword}
-\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, frame hidden, sharp corners, enhanced, breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
+\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, frame hidden, interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, breakable]}{\end{tcolorbox}}\fi
 
@@
 spaces. Opting for environmental friendly policies today not only
-reduces carbon dioxide omissions but also helps us to reach the Paris
-climate targets tomorrow. Deferring these policies, the targets can be
-reached as well---but with less flexibility. Hence, today's actions (or
-the omission thereof) not only affect intermediate results but also the
-number of paths one can choose to reach certain goals.
+reduces carbon dioxide omissions immediately but also helps us to reach
+the Paris climate targets tomorrow. Deferring these policies, may not
+necessarily prevent us from reaching these targets, but it makes it more
+difficult in the future. Hence, today's actions (or the omission
+thereof) not only affect intermediate outcomes but also the number of
+paths one can choose to reach certain goals.
 
@@
 policies\footnote{See \citet[p.~1]{GKLS2020} for numerous references.}---miss
-these temporal interdependencies because participants have the same set
-of actions in each period. A game implemented by Gächter, Mengel, Tsakas
-\& Vostroknutov \citeyearpar{GMTV2017} (hereafter, GMTV) as well as
-Stefan Große (2011, unpublished) incorporated interdependencies into a
-\emph{dynamic} public good game with students in Nottingham, England and
-Erfurt, Germany.
-
-Because their setting is more realistic, one wonders whether it is
-better suited to inform public policy. To answer this question, I
-replicated parts of GMTV's experiment with different samples. In
-addition, I observed the participant's behavior in voluntary climate
+these temporal interdependencies simply because participants have the
+same set of actions in each period. Accordingly, participants' actions
+in a given period do not affect their number of actions in subsequent
+periods. A game implemented by Gächter, Mengel, Tsakas \& Vostroknutov
+\citeyearpar{GMTV2017} (hereafter, GMTV) as well as Stefan Große (2011,
+unpublished) incorporated interdependencies into a \emph{dynamic} public
+good game. Here, participants' actions in a given period affect their
+number of actions in subsequent periods. Because there is surprisingly
+little experimental research on these interdependencies\footnote{One
+  exemption are \citet{Moser2019}, who built on GMTV's design do
+  investigate leadership.}, I replicated one of their treatments.
+
+\citet{GKLS2020} find that standard public good games do not generalize
+to real-world climate action. Because the dynamic setting has a more
+realistic property, one wonders whether it is better suited to inform
+public policy. To answer this question, I ran the experiment with
+different samples\footnote{GMTV ran their experiments with students in
+  Nottingham, England.} online, that is, with participants who make
+their decisions in an environment whcih is more natural than the lab. In
+addition, I observed the participants' behavior in voluntary climate
 actions (VCA). This yielded a setting similar to \citet{GKLS2020}'s
@@
 
-I utilized an inexperienced sample that has not been exposed to
-interactive experiments before. Furthermore, I conducted the experiment
-online. This required me to make the experiment's software robust to
-minimize attrition. Because I observed metrics to assess the fluency and
-feasibility of online experiments, this study also serves as a case
-study like the one of \citet{AGM2018}.
+\citet{AGM2018} conducted public good games in the lab and on MTurk to
+draw lessons from online experimentation. This study extends this
+literature \citep[see also][]{GoodmanPaolacci2017} by focusing on a
+completely inexperienced sample that has not been exposed to interactive
+experiments before. This required me to design a robust (and thus, more
+complex) software to minimize attrition. In exchange, the online setting
+allowed me to also collect paradata to assess the fluency and
+feasibility of the experiment. This article reports on both topics: the
+robust design as well as the feasibility.
 
@@
 periods, a private account with a return of \(1\) and a group account
-with a return of \(1.5\) (\(\Rightarrow\) MPCR\(\equiv \frac{1.5}{4}\)),
-such that:
+with a return of \(1.5\) (\(\Rightarrow\) MPCR\(\equiv \frac{1.5}{4}\)).
+With \(i\)'s contribution in period \(t\) being \(c_i^t\), the model
+looks as follows:
 
@@
 N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
-\] What makes the game \emph{dynamic}? Instead of receiving fresh
+\]
+
+What makes the game \emph{dynamic}? Instead of receiving fresh
 endowments every period, participants received one endowment only at the
@@
 contrast to GMTV and like \citet{GKLS2020}, we employed a VCA, where
-they could donate (some of) their earnings to offset carbon dioxide
-(that is, by retiring emission permits from the EU ETS).\footnote{Importantly,
+they could donate any amount their earnings to offset carbon dioxide
+(that is, retirine emission permits from the EU ETS).\footnote{Importantly,
   \citet{GKLS2020} made the VCA decision with a fresh endowment
@@
 a European level. Finally, I informed the participants that the
-documentation of individual and aggregate contributions were posted
-immediately after the experiments online. To avoid privacy or social
-image concerns, participants learned their unique and random IDs, which
-they needed to identify their individual contributions. This document
-certified that their contributions have been used to offset
+documentation of individual and aggregate contributions were to be
+posted immediately after the experiments online. To avoid privacy or
+social image concerns, participants learned their unique and random IDs,
+which they needed to identify their individual contributions. The
+document certified that their contributions have been used to offset
 \href{https://www.compensators.org/compensatelist/?searchterm=stefan+traub}{1.82
@@
 approach to build the panel while drawing from the population of
-citizens from Hamburg, Germany. Because the sample was exhausted at one
+citizens of Hamburg, Germany. Because the sample was exhausted at one
 point, I also recruited students from the University of Hamburg.
 
-At the time I conducted the experiment, the representative sample was
-not familiar with interactive experiments. In fact, I ran the first
+At the time I conducted the experiment, the more representative sample
+was not familiar with interactive experiments. In fact, I ran the first
 interactive group experiment with this sample. The students, in
-contrast, are used to this kind of experiments. Recruiting them, I
+contrast, were used to this kind of experiments. Recruiting them, I
 excluded those who have participated in a public goods game before. As a
-consequence, nonnaiveté is unlikely to affect the validity of my
+consequence, nonnaiveté is unlikely to affect the validity of the
 experiment \citep[ p.~204]{GoodmanPaolacci2017}.
@@
 synchronous. Third, the underlying game was dynamic and interdependent.
-This makes dropouts not only more likely, but also more expensive which
-is why dropouts were a major concern implementing the experiment.
+This makes dropouts not only more likely but also more expensive, which
+is why attrition was a major concern implementing the experiment.
 
@@
 \href{https://www.highcharts.com/}{Highcharts library} made it easy to
-visualize results and to communicate dynamics. The oTree code snippets
-made it possible to handle dropouts, for instance, by replacing them
-with artificial bots (and informing the rest of the group thereof).
-Insofar, oTree served a good tool to consider the participants' user
-experience and thus, to make dropouts less likely.
+visualize results and to communicate dynamics. Insofar, oTree served a
+good tool to enhance the participants' user experience and thus, to make
+dropouts less likely. Furthermore, the oTree code snippets made it
+possible to handle dropouts.
+
+Which features were required to handle dropouts? First, participants had
+to be matched to form a group \emph{after} comprehension questions were
+answered successfully. Importantly, participants were grouped by the
+order they answered these questions to reduce waiting times. While
+waiting for other players to form the group, the participants saw a
+wait-page informing them that they are waiting for other participants to
+arrive and that they do not have to wait for longer than 10 minutes. The
+screen also informed them that they would receive a \emph{patience
+bonus} of one Euro after the expiration of that time (or what was left
+of it). Second, participants only had 10 minutes to make the first
+contribution and 4 minutes for the remaining contributions. After this
+time expired, participants were replaced by bots that made random
+contributions. In this case, the remaining group members were informed
+about the replacement. Both features were implemented to limit wait
+times and boredom for other participants. Section~\ref{sec-feasibility}
+shows that the first feature became effective in some cases, wheres the
+second feature did not.
 
@@
 
-The experiment lasted around 25 minutes on average. The earnings of the
-average subject were 11.23 Euros (sd = 4.85).\footnote{This values
-  include earnings from the incentivized risk elicitation task that are
-  not part of the analysis.}
+The experiment lasted around 25 minutes on average. The earnings
+averaged 11.23 Euros (sd = 4.85).\footnote{This values include earnings
+  from the incentivized risk elicitation task that is not part of the
+  analysis.}
 
@@
 
-Parts of the analyses are pre-registered \citep{preregistration}. In
-addition, I pre-registered the exact analyses I planned to run when I
-designed designed the experiment on
+Parts of the analyses were pre-registered in the American Economic
+Association's RCT Registry \citep{preregistration}. In addition, I
+pre-registered the exact analyses I planned to run when I designed
+designed the experiment on
 \href{https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd}{GitHub}.\footnote{https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd
@@
 
-The analysis that makes the most sense now that you have collected the
-data is a little different, though: Because the more representative
+The analysis that makes the most sense now that I have collected the
+data is a little different though: Because the more representative
 subject pool was exhausted earlier than expected, I recruited students
@@
   https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}
-Because the originally planned analysis code is archived and
-reproducible, these changes are transparent.
+However, because the originally planned analysis code is archived and
+reproducible, these changes are transparent and easy to assess.
 
@@
 nobody indicated that he or she did not understand the situation at all.
-To analyze how participants coped with the situation, I consider three
-additional metrics: selection into the experiment, attrition as well as
-the time spent on each page.
+There is some behavioral data supporting this finding: The user
+interface offered a popup to review instructions or contact information.
+I tracked both and find that none of the participants ever opened these
+popups even though they were clearly visible in the decision screen's
+header and introduced in the instructions. To further analyze how
+participants coped with the situation, I consider three additional
+metrics: selection into the experiment, attrition as well as the time
+spent on each page.
 
@@
 
-\textbf{Result 3.} \emph{Existing evidence overestimates the willingness
-to contribute to real public goods. This holds true for more
-representative samples and---to a lower degree---for student samples.}
+\textbf{Result 3.} \emph{Overall, contribution behavior is uncorrelated
+with the willingness to contribute to real public goods. This holds true
+for more representative samples and---to a lower degree---for student
+samples.}
 
@@
 contribution behavior in my abstract setting is, if anything, only
-weakly linked to behavior in the real world. This lack of
-generalizability can be counteracted, but not be solved, by the use of
-more representative samples.
+weakly linked to behavior in the real world.
 
@@
 more representative samples is worth the efforts because it decreases
-transferability of results to the real world---at least, a little.
+transferability of results to the real world---at least in this specific
+case.
 

### 2022-11-05 otreeLite/settings.py

@@ -5,6 +5,12 @@ SESSION_CONFIGS = [
         name="GMTV",
         app_sequence=["A_Intro", "B_GMTV", "D_Outro"],
         num_demo_participants=2,
+        num_rounds=10,
+        group_size=2,
+        efficiency_factor=1.5,
+        risk=0,
+        damage=0,
+        initial_endowment=20,
     ),
     dict(
         name="Clubs",

### 2022-11-06 analysis/quarto/paper.tex
typo

@@
 \end{keyword}
-\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, frame hidden, interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, breakable]}{\end{tcolorbox}}\fi
+\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, enhanced, breakable, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, sharp corners]}{\end{tcolorbox}}\fi
 
@@
 behavior in the VCA worse than student sample's behavior (p = 0.07).
-Finally, (4) contributions in the abstract public good game are higher
+Finally, (d) contributions in the abstract public good game are higher
 than contributions to the real public good of climate change mitigation.

### 2023-05-16 analysis/quarto/paper.qmd
typo
rewriting

@@
 ---
-title: Growth and inequality in public good provision --- an extended replication
+title: Revisiting 'Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation
 author:
@@
 abstract: |
-  You can find the most recent version of this paper [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.pdf). The abstract follows at later point.
+  I revisit the dynamic public good game by Gächter et al.
+(2017) developed to study cooperation under dynamic interdependencies.
+Collecting data from both students and a general population sample, I not only reproduce some of the author's original observations but also test the game's generalizability.
+Appending a charitable dictator game, I find no correlations between behavior in the abstract game and the charitable context.
+This applies to students and the general population sample alike.
+Studying inexperiend general population samples raises methodological challenges with respect to fatigue and dropouts.
+This paper approaches them and provides simple solutions to run relieable interactive experiments online.
+
+  You can find the most recent version of this paper [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.pdf).
 keywords: 
@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = FALSE, fig.width = 10, fig.height = 4)
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE,
+                      fig.width = 10, fig.height = 4)
 ```
@@
 
-pacman::p_load(magrittr, data.table, stringr, lubridate, glue, DescTools, haven,
-               stargazer, ggplot2, patchwork, MetBrewer, Rmisc, knitr)
+pacman::p_load(magrittr, data.table, stringr, lubridate, glue, DescTools, haven, censReg,
+               stargazer, vtable, ggplot2, patchwork, MetBrewer, Rmisc, knitr)
 ```
@@
                    trust = Outro.1.player.PQ11,
+                   government = Outro.1.player.PQ13,
                    comprehension = dPGG.10.player.comprehension)]
@@
                              trust = NA,
+                             government = NA,
                              comprehension = NA)]
@@
 Hence, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of paths one can choose to reach certain goals.
-
-Standard public good games---although often intended to inform climate policies^[See @GKLS2020 [p.
-1] for numerous references.]---miss these temporal interdependencies simply because participants have the same set of actions in each period.
+This apllies especially to carbon dioxide emissions where its current stock will last for well over a millennium [@Inman2008; @CalzolariEtAl2018].
+
+Public good games---although often intended to inform climate policies (e.g.
+@MilinskiEtAl2006, @TavoniEtAl2011, @Hauser2014, @BrickEtAl2015, @GomezEtAl2018, @CalzolariEtAl2018, @CookEtAl2019)---miss these temporal interdependencies simply because participants have the same set of actions in each period.
 Accordingly, participants' actions in a given period do not affect their number of actions in subsequent periods.
-A game implemented by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017] (hereafter, GMTV) as well as Stefan Große (2011, unpublished) incorporated interdependencies into a _dynamic_ public good game.
+A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017] (hereafter, GMTV) as well as Stefan Große (2011, unpublished) incorporated interdependencies into a _dynamic_ public good game.
 Here, participants' actions in a given period affect their number of actions in subsequent periods.
-Because there is surprisingly little experimental research on these interdependencies^[One exemption are @Moser2019, who built on GMTV's design do investigate leadership.], I replicated one of their treatments.
-
-@GKLS2020 find that standard public good games do not generalize to real-world climate action.
-Because the dynamic setting has a more realistic property, one wonders whether it is better suited to inform public policy.
-To answer this question, I ran the experiment with different samples^[GMTV ran their experiments with students in Nottingham, England.] online, that is, with participants who make their decisions in an environment whcih is more natural than the lab.
-In addition, I observed the participants' behavior in voluntary climate actions (VCA).
+Because there is surprisingly little experimental research on these interdependencies^[One exemption are @Moser2019, who built on GMTV's design to investigate leadership.], I reproduced one of their treatments to compare dynamics across samples.
+
+@GKLS2020 find that standard public good games do not generalize well to real-world climate action.
+They also find that generalizability depends on structural resemblance of the public goods game with the context of climate change mitigation.
+Greater resemblance improves generalizability.
+Because GMTV's dynamic setting has a more realistic property—namely, interdependencies—one wonders whether it is better suited to inform public policy.
+To approach this question, I ran the experiment with different samples^[GMTV ran their experiments with students in Nottingham, England.] and
+<!--, that is, with participants who make their decisions in an environment which is more natural than the lab.-->
+observed the participants' behavior in voluntary climate actions (VCA).
 This yielded a setting similar to @GKLS2020's which allows me to analyze how behavior in the abstract game translates into real-world action across samples.
 
+The VCA is a (charitable) dictator games where each participant is a dictator dividing her budget between herself and some organization linked to the reduction of CO2 emissions.
+@EckelGrossman1996 were the first to implement a charitable dictator game observing contributions of 30% of the endowments.
+Like @GKLS2020, @CarpenterEtAl2008 report that students make lower contributions to charity than community members.
+
 @AGM2018 conducted public good games in the lab and on MTurk to draw lessons from online experimentation.
-This study extends this literature [see also @GoodmanPaolacci2017] by focusing on a completely inexperienced sample that has not been exposed to interactive experiments before.
+This study extends this literature [see also @GoodmanPaolacci2017  @AmirEtAl2012] by focusing on a completely inexperienced sample that has not been exposed to interactive experiments before.
 This required me to design a robust (and thus, more complex) software to minimize attrition.
@@
 Second, it shows that logistically complex online experiments are feasible for samples other than students or clickworkers.
-Third, it shows that findings from abstract games do not generalize well and even worse with the representative sample.
+Third, this paper supports critics arguing that findings from abstract games do not generalize well---not even with a more representative sample.
 After reporting the methods, this paper is organized along these findings.
 
+# Transparency
+
+Well before credibility crises comprised a variety disciplines, @bemwriting [p. 2] indirectly conceded discrepancies between fuzzy research processes and the polished article that results from it:
+
+> _"There are two possible articles you can write: (a) the article you planned to write when you designed your study or (b) the article that makes the most sense now that you have seen the results.
+They are rarely the same, and the correct answer is (b)."_
+
+Now, 20 years later, we accustom ourselves with mechanisms designed to unravel the fuzzy back-and-forth between exploratory and confirmatory research.
+Prominently, pre-registrations were established to tie the researchers' hands when doing confirmatory research--reducing observable discrepancies between (a) and (b).
+Today, researchers can not only choose where to pre-register but also decide about the level of detail they provide.
+More severely, nothing stops researchers from pre-registering multiple hypotheses opposing each other (see e.g.
+@SimmonsEtAl2021 and @PhamEtAl2021 for a discussion).
+
+@WaldronAllen2022 report a wide variety of depth of pre-registrations in the field of Neuropsychopharmacology and document that the label _'pre-registration'_ can be obtained with minimal effort.
+In absence of transparency and scrutiny pre-registrations run into danger to miss the target of making science more credible.
+Even more so, they may have adverse effects as the label _'pre-registered'_ becomes cheap (too) to acquire.
+
+Discussing the costs and benefits of pre-registrations, @Olken2015 stresses the uncertainty of research processes and promotes moderate approaches.
+As @WaldronAllen2022, he argues that pre-registrations not necessarily eliminate  flexibility.
+These 'moderate' or 'flexible' approaches require transparency to reduce concerns of _'data-mining'_ [@Olken2015 p.
+61] by showing (a) the analyses I planned to run, (b) the analysis that made most sense after collecting the data and the transition from (a) to (b).
+Because this is neither incentivized nor easy to verify, we need tools that make transparency convenient to establish and to scrutinize.
+I propose version control (such as Git) as one such tool and illustrate its application on this paper:  GitHub is a website and cloud-based service where developers---and researchers alike---can store and manage their code.
+The service is based on Git^[Git is a specific open-source version control system developed in 2005.] and designed for version control.
+Importantly, changes are time-stamped and can be tracked.
+Moreover, one can create branches, that is, duplicates of code -- either to work collaborative or to archive a certain state.
+
+To sum up, pre-registrations alone are necessary but not sufficient to restore the credibility in experimental sciences.
+Pre-registrations must come with additional emphasis on transparency covering the whole research process as well as with a higher level of scrutiny that looks beyond mere labels.
+
+In fact, the experiment reported in this article qualifies for the label _'pre-registered'_ at a first glance:
+Parts of the analyses were pre-registered in the American Economic Association's RCT Registry [@preregistration].
+In addition, I pre-registered the exact analyses I planned to run when I designed the experiment on [GitHub](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.].
+
+The analysis that made the most sense after having collected the data is a little different though: Because the more representative subject pool was exhausted earlier than expected, I recruited students which opened up a new research direction: assessing generalizability.
+Hence, this article combines both confirmatory as well as exploratory research.
+
+Accordingly, I  changed many of the analysis scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd] However, because the originally planned analysis code is archived and reproducible, these changes are transparent and easy to assess, showcasing (a), (b) and the transition from (a) to (b).
+
+<!--
+I archived detailed analyses scripts and created a [branch](https://github.com/Howquez/coopUncertainty/tree/July21Replication) a few days _before_ we collected data and pre-registered the analysis via the American Economic Association's RCT Registry [@preregistration].
+-->
+
 # Methodology {#sec-methods}
 
-In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific replication_^[@Parsons2022 use the term of a _conceptual replication_ which means the same.] of one treatment of GMTV's dynamic public good game.
-The pure replication re-analyzes the original data.
+In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific_ reproduction^[@Parsons2022 use the term of a _conceptual replication_ which means the same.] of one treatment of GMTV's dynamic public good game.
+The pure reproduction re-analyzes the original data.
 [Appendix A](#A:-Pure-Replication) documents [errors I identified]() in the original paper.
@@
 ## Experimental Design {#sec-design}
+
+The design builds on the workhorse model @Zelmer2003 [p.301] describes in her meta-analysis, where
+
+> _"subjects are divided into groups and play the same game for a finite number of periods.
+Each period, every subject is endowed with an income [...] The subject must then divide this income between a contribution to a private account [...] that yields a constant return to themselves only and a contribution to a public account [...] where consumption benefits accrue to all group members.
+At the end of each period, subjects typically learn the aggregate contribution to the public good by all members of their group and their earnings for the period."_
+
+Considering the design, the only differences between such a _static_ game and GMTV's design are _dynamics_: Instead of receiving fresh endowments every period, participants receive one endowment only at the beginning of the first period.
+A participant's endowment in the second period is the wealth she accumulated in the first period.
+A participant's endowment in the third period is the wealth she accumulated in the first two periods.
+And so on.
+Hence, a decision in one period has consequences on future endowments and, ultimately, growth paths.
+For this reason, the game is described as a _dynamic_ public good game.
 
@@
 
-What makes the game _dynamic_?
-Instead of receiving fresh endowments every period, participants received one endowment only at the beginning of the first period.
-A participant's endowment in the second period is the wealth he or she accumulated in the first period.
-A participant's endowment in the third period is the wealth he or she accumulated in the first two periods.
-And so on.
-Hence, a decision in one period has consequences on future endowments and, ultimately, growth paths.
-For this reason, the game is described as a _dynamic_ public good game
-
 ## Voluntary Climate Action (VCA)
@@
 Like GMTV we employ a real giving task after the abstract game.
-In contrast to GMTV and like @GKLS2020, we employed a VCA, where they could donate any amount their earnings to offset carbon dioxide (that is, retirine emission permits from the EU ETS).^[Importantly, @GKLS2020 made the VCA decision with a fresh endowment _before_ they played the abstract game.
+In contrast to GMTV and like @GKLS2020, we employed a VCA, where participants could donate any amount their earnings to offset carbon dioxide (that is, retire emission permits from the EU ETS).^[Importantly, @GKLS2020 made the VCA decision with a fresh endowment _before_ they played the abstract game.
 I deviate from their procedure to match GMTV's procedure.]
@@
 The information also highlighted that the mitigation came into operation on a European level.
-Finally, I informed the participants that the documentation of individual and aggregate contributions were to be posted immediately after the experiments online.
+Finally, I informed the participants that the documentation of individual and aggregate contributions were to be posted immediately after the concluding the sessions online.
 To avoid privacy or social image concerns, participants learned their unique and random IDs, which they needed to identify their individual contributions.
@@
 
-## Sample {#sec-sample}
+## Recruitment and Sample Characteristics {#sec-sample}
 
@@
 In fact, I ran the first interactive group experiment with this sample.
-The students, in contrast, were used to this kind of experiments.
-Recruiting them, I excluded those who have participated in a public goods game before.
+The students, in contrast, were used to single-player experiments.
+Recruiting them, I excluded those who have participated in interactive experiments such as public goods games before, to keep the two distinct subject pools comparable in terms of their experience.
 As a consequence, nonnaiveté is unlikely to affect the validity of the experiment [@GoodmanPaolacci2017 p.
@@
 I am thus, referring to three different samples utilized at two points in time: the University of Nottingham's students (in late 2012), Hamburg's citizens and the University Hamburg's students (both in July 2021).
-@tbl-sample-properties shows how they compare with respect to a few properties.
-
-```{r sampleDifferences1, results = "asis", warning = FALSE}
-#| label: tbl-sample-properties
-#| tbl-cap: Sample Properties
+@tbl-sample-properties gives an overview.
+
+```{r sampleDifferences1, results = "asis", warning = FALSE, eval=FALSE}
 
@@
 
+```{r sampleProperties}
+#| results: 'asis'
+#| label: tbl-sample-properties
+#| tbl-cap: Sample Properties
+
+covs[, sample := "Nottingham Students"]
+covs[treatment == "replication" & student == TRUE, sample := "Hamburg Students"]
+covs[treatment == "replication" & student == FALSE, sample := "Hamburg Citizens"]
+covs[, sample := as.factor(sample)]
+
+vtable::sumtable(data = covs, 
+                 vars = c('age', 'gender', 'switching_row'),
+                 group = 'sample',
+                 group.test = TRUE,
+                 digits = 2,
+                 labels = c('Age', 'Female', 'Switching Row'),
+                 # note = "Switching Row describes choices in a multiple price list to elicit risk preferences.
+The higher the value, the higher the certainty equivalent.
+Government Responsible is self-reported based on a question adapted from GMTV ('The government should take responsibility that people are better provided for.')",
+                 out = 'latex')
+```
+
 ```{r}
@@
 
-Describe sample properties here.
+Overall, I recruited `r covs[treatment == 'replication', .N]` participants for the experiment.
+The three samples differ significantly with respect to their age.
+The non-student sample is more diverse compared to the two student samples.
 
@@
 Insofar, oTree served a good tool to enhance the participants' user experience and thus, to make dropouts less likely.
-Furthermore, the oTree code snippets made it possible to handle dropouts.
 
@@
 Having read these instructions, each participant has also seen a demo-screen explaining the user interface.
-Before proceeding, they had to answer six comprehension questions correctly.
+Before proceeding, they had to answer six comprehension questions correctly to avoid confusion in later stages [@FerraroVossler2010].
 Subsequently, they saw a waiting screen until they could be matched with three other participants, who have answered the comprehension questions correctly.
@@
 
-While I tried to stick to GMTV's protocol as close as possible, I deviated in a few aspects.
+While I stuck to GMTV's protocol as close as possible, I deviated in a few aspects.
 First, the instructions were German and also covered topics inherent to the online setting (dropouts and bots, for instance).
-Second, I used another software (oTree instead of zTree).
+Second, I used another software (oTree instead of zTree) which also affected the graphical user interface participants were exposed to.
 Third, GMTV gave participants the opportunity to donate to _Doctors without Borders_ whereas we offered carbon dioxide offsets.
-Fourth, the graphical user interface looked different.
 
@@
 
-## Pre-registration {#sec-registration}
-
-Parts of the analyses were pre-registered in the American Economic Association's RCT Registry [@preregistration].
-In addition, I pre-registered the exact analyses I planned to run when I designed designed the experiment on [GitHub](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.].
-GitHub is a website and cloud-based service where developers---and researchers alike---can store and manage their code.
-The service is based on Git^[Git is a specific open-source version control system developed in 2005.] and designed for version control.
-Importantly, changes are timestamped and can be tracked.
-Moreover, one can create branches, that is, duplicates of code -- either to work collaborative or to archive a certain state.
-Accordingly, I archived my analyses scripts and created a [branch](https://github.com/Howquez/coopUncertainty/tree/July21Replication) a few days _before_ we collected data.
-
-The analysis that makes the most sense now that I have collected the data is a little different though: Because the more representative subject pool was exhausted earlier than expected, I recruited students unwantedly and changed parts of the scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd] However, because the originally planned analysis code is archived and reproducible, these changes are transparent and easy to assess.
-
 # Results {#sec-results}
@@
 First, I ask whether the samples differ with respect to their initial contributions to the public good.
-Is our replication sample more pro-social than the original sample?
-@fig-first-round reveals that it is not.
-The distributions of both samples look fairly similar.
-Both samples contributed 10 tokens, that is, 50% of their endowments on average (median and mean).^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean contribution in first round of the game.] Moreover, both samples' initial contributions resemble initial contributions participants usually make in the standard game with partner matching.^[See Figure 3B in @fehrgaechter2000 (p.989), for instance.] However, in the dynamic game presented here, we are particularly interested in the subsequent periods because differences add up exponentially.
+Is the replication sample (consisting of both students and non-students) more pro-social than the original sample?
+A two-sided rank sum test reveals that it is not (p=`r rs1`).
+Both samples contributed 10 tokens, that is, 50% of their endowments on average (median and mean).
+Moreover, both samples' initial contributions resemble initial contributions participants usually make in the static game with partner matching.^[See Figure 3B in @fehrgaechter2000 [p.989], for instance.] However, in the dynamic game presented here, we are particularly interested in the subsequent periods because differences add up exponentially.
 Do the two groups remain similar over the course of time?
@@
 ```{r firstRoundViz}
+#| eval: false
 #| fig-cap: Individual contributions to the dynamic public good in the first period
@@
 
+```{r}
+for(r in 1:10){
+  a <- main[round == r & treatment == 'replication', share]
+  b <- main[round == r & treatment == 'noPunish10', share]
+
+  wilcox.test(a, 
+              b,
+              exact = FALSE)$p.value %>% 
+    round(digits = 4) %>% 
+    formatC(format = "f", 
+            digits = 4)# %>%
+    # print()
+  }
+
+r <- 5
+a <- main[round == r & treatment == 'replication', contribution]
+b <- main[round == r & treatment == 'noPunish10', contribution]
+
+rs2 <- wilcox.test(a, 
+            b,
+            exact = FALSE)$p.value %>% 
+  round(digits = 4) %>% 
+  formatC(format = "f", 
+          digits = 4)
+```
+
 In particular, do the two samples' contributions follow the same path over the 10 periods they played?
@@
 @fig-share-of-contributions illustrates that the samples make similar contributions at the beginning and the end of the game but behave differently in between.
-More precisely, the left panel--depicting the average contributions in absolute terms--shows that the original sample contributed substantially more than the replication sample _in all but the first and last period_.
-For this reason, the original sample's behavior differs from the replication sample's behavior in two aspects: it contributes more and exhibits a considerable drop in the last period (whereas the replication sample's contributions flatten).
+More precisely, the left panel--depicting the average contributions in absolute terms--shows that the original sample contributed more than the replication sample _in all but the first and last period_.^[In period five, this difference is significant: a two-sided rank sum test yields p=`r rs2`.
+] For this reason, the original sample's behavior differs from the replication sample's behavior in two aspects: it contributes more and exhibits a considerable drop in the last period (whereas the replication sample's contributions flatten).
 
 Note that increasing contributions over time imply increasing endowments over time.
-Hence, absolute contributions do not us much about the willingness to cooperate.
+Hence, absolute contributions do not tell much about the willingness to cooperate.
 For this reason, the right panel in @fig-share-of-contributions shows the average _share of endowments contributed_ over time.
@@
 However, both samples also differ with respect to one aspect: the replication sample's share of contributions declines faster.
+This is mirrored by a two-sided rank sum test which is only significant at a five percent level in periods three and four.
 
@@
 
-Again, both samples' behavior resembles the contributions participants usually make in the standard game with partner matching: contributions equal approximately half of endowments in the very first period and decrease to around 10% of endowments by the last period.^[The right panel is thus, comparable to the visualizations _and results_ in the standard game.
-See, for instance, Figure 1B in @fehrgaechter2000 (p.986).] In the dynamic game presented here, however, different paths lead to different levels of wealth -- even if they share the same start- and end-points.
+Again, both samples' behavior resembles the contributions participants usually make in the static game with partner matching: contributions equal approximately half of endowments in the very first period and decrease to around ten percent of endowments by the last period.^[The right panel is thus, comparable to the visualizations _and results_ in the static game.
+See, for instance, Figure 1B in @fehrgaechter2000 [p.986].] In the dynamic game presented here, however, different paths lead to different levels of wealth -- even if they share the same start- and end-points.
 I am thus, more interested in the contributions' implications for wealth generation and growth.
@@
 
-How do the different contribution-paths translate into wealth?^[To measure wealth and growth, I define a variable called _stock_ which sums the endowments of all participants in a given group at the end of the round (that is, after the contributions have been made, multiplied and redistributed).] Given that the original sample contributed more in most of the periods, one would expect the respective groups to be considerably more wealthy.
-@fig-stock-distribution indicates just that.
-The grey lines show that an average group in the original sample accumulated about `r round(originalWealth)` tokens.
+How do the different contribution-paths translate into wealth?^[To measure wealth and growth, I define a variable called _stock_ which sums the endowments of all participants in a given group at the end of the round (that is, after the contributions have been made, multiplied and redistributed).] Given that the original sample contributed more, one would expect the respective groups to be  more wealthy.
+A mere mean comparison indicates just that: An average group in the original sample accumulated about `r round(originalWealth)` tokens.
 In contrast, an average group in the replication sample accumulated about `r round(replicationWealth)` tokens.
-This difference is insignificant at conventional levels^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean stock in last round of the game.] though.
+This difference is insignificant at conventional levels though: A two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean stock in last period of the game.
 
 ```{r stockDistributionViz}
+#| eval: false
 #| fig-cap: Groups' income at the end of the game
@@
 The panel illustrates for both samples that growth was continuous and surprisingly linear, given the exponential character of the game's design.
-To sum up, the contribution behavior differed between samples.
-In contrast, neither the eventual wealth nor the corresponding growth paths differed.
+Despite somewhat differing contribution behavior between samples, neither the eventual wealth nor the corresponding growth paths differed.
 Differences in contribution behavior did, thus, not translate to significantly different wealth outcomes.
@@
 Given the different samples and the possibility of endogenous growth--which essentially is the main feature of the game--I ask whether and how the inequality grows _within_ groups.
-@fig-gini-distribution illustrates that inequality did grow: at the end of the game, the original and the replication groups exhibit an average Gini coefficient of `r originalGini` and `r replicationGini`, respectively.^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean Gini coefficient in last round of the game.] Because every participant started with the same initial endowment (in _Period 0_, so to speak), every group started equally--with a Gini coefficient equaling zero.
-
-@fig-ginit-time-series shows that this initial state of equality ended with the first period already: both samples exhibit a stark incline in inequality before the second period started.
-From then on, the respective Gini coefficients grew slowly but continuously -- for both samples.
+@fig-gini-time-series illustrates that inequality did grow: at the end of the game, the original and the replication groups exhibit an average Gini coefficient of `r originalGini` and `r replicationGini`, respectively.^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean Gini coefficient in last round of the game.] Because every participant started with the same initial endowment (in _Period 0_, so to speak), every group started equally--with a Gini coefficient equaling zero.
+
+@fig-gini-time-series also shows that this initial state of equality ended with the first period already: both samples exhibit a stark incline in inequality before the second period started.
+From then on, the respective Gini coefficients grew slowly but continuously -- for both samples.^[In each and every period, the two-sided rank sum test comparing gini coefficients between both sample yields p-values way over ten percent.]
 
 ```{r giniDistributionViz}
+#| eval: false
 #| fig-cap: Groups' Gini coefficients (within groups) at the end of the game
@@
 #| fig-cap: Average Gini coefficient (within groups) over time across samples
-#| label: fig-ginit-time-series
+#| label: fig-gini-time-series
 
@@
 I first comment on the selection into the experiment: It was difficult to recruit the sample.
-The panel counted 1.209 non-students of which we were able to recruit `r main[student == FALSE, .N]` participants who finished the experiment---even though we varied the weekdays and timing of the sessions (which were conducted during a nation-wide lockdown with home office regime).
-For this reason, we also recruited students in the last session which explains the relatively large number of showups in @tbl-meta.
+The panel counted 1.209 non-students of which I were able to recruit `r main[student == FALSE, .N]` participants who finished the experiment---even though I varied the weekdays and timing of the sessions (which were conducted during a nation-wide lockdown with home office regime).
+For this reason, I also recruited students in the last session which explains the relatively large number of showups in @tbl-meta.
 Although I intended to refrain from the recruitment of students initially, this particular sub sample enabled me to investigate the generalizability of my results as I will discuss in  @sec-generalizability.
-Alternatively, I also could have contacted a market research institute to recruit additional participants within a week.
-I refrained from doing so to contrast students and the general population sample, however.
 
@@
 
-```{r}
+```{r generalizability_prep}
 R1covs <- covs[, .(participant.code,
@@
                    donationShare = (donation * 20) / payoff * 100,
+                   age,
+                   gender,
+                   switching_row,
                    payoff)]
@@
 temp[, contributionShare := ownContribution/20 * 100]
+temp[, consistency := 1 - (contributionShare - donationShare)]
 ```
@@
 @GKLS2020 asked how much can we learn about voluntary climate action from the behavior in public goods games.
-Using a similar strategy, I answer the question for _dynamic_ public goods games: _Not much_.
+Using a similar strategy, I answer the question for a _dynamic_ public good game: _Not much_.
 Overall, there seems to be no association between choices in the voluntary climate action and the first period in the dynamic public goods game.
-@fig-scatter-generalizability shows a scatter plot of realized choices, with the percentage of endowment spent by each participant in the first period of the game on the x-axis and that spent in the VCA on the y-axis.
-In addition, the figure contains a fitted line of a linear model whose slope is indistinguishable from zero.
-No matter how much the participants contributed in the first round, they spent, on average, about `r temp[, round(mean(donationShare))]`% of their income on the VCA.
+
+```{r vca_differences}
+rs1 <- wilcox.test(temp[student == FALSE, donationShare], 
+                   temp[student == TRUE, donationShare],
+                   exact = FALSE)$p.value %>% 
+  round(digits = 4) %>% 
+  formatC(format = "f", 
+          digits = 4)
+```
+
+@fig-kernel-generalizability shows distributions of contributions across both choices for both samples.
+The top panels illustrate the behavior of the general population sample.
+The bottom panels illustrate the behavior of the general population sample.
+The left panels show the behavior in the VCA.
+The right panels show the behavior in first period of the game.
+A visual inspection shows that (a) mean contributions are positive in both tasks for both samples.^[The same holds true for median contributions.] (b) Furthermore, average contributions are lower in the VCA.
+(c) In contrast to @GKLS2020's observation, we do not observe a difference between samples in the abstract game's contribution behavior.
+(d) However, the student's share of income contributed to the VCA is significantly lower than the general population sample's contributions (two-sided rank sum test, p=`r rs1`).
+Taken together, these aggregate results indicate, that the consistency between tasks is higher for the general population than it is for students.
+Or, to put it differently, the general population's behavior in the abstract game better predicts their behavior in real-world mitigation context.
+
+```{r vizGeneralizability}
+#| fig-cap: Kernel distributions of contributions across tasks and subject pools.
+#| label: fig-kernel-generalizability
+#| fig.height: 6
+
+# viz wrapper
+plotShares <- function(stud = FALSE,
+                       var  = "donationShare",
+                       col  = cPrimary,
+                       xlab = "",
+                       ylab = ""){
+
+  dt <- temp[student == stud, .(x = get(var))]
+
+  model <- lm(x ~ 1, dt)
+  ci1 <- confint(model, level=0.95)[1]
+  ci2 <- confint(model, level=0.95)[2]
+
+  ggplot(data = dt,
+         mapping = aes(x = x)) +
+    annotate("rect", 
+             xmin = ci1, xmax = ci2, 
+             ymin  =0, ymax = Inf, 
+             alpha = 0.33) +
+    geom_density(alpha = 0.75,
+                 fill = col) +
+    scale_x_continuous(limits = c(0, 100),
+                       expand = c(0, NA)) +
+    scale_y_continuous(limits = c(0, NA),
+                       expand = c(0, NA)) +
+    geom_vline(xintercept = dt[,mean(x, na.rm = TRUE)],
+               lty = 2) +
+    labs(x = xlab,
+         y = ylab) +
+  layout
+}
+
+p1 <- plotShares(stud = FALSE, 
+                 col = cSecondary,   
+                 var = "donationShare",
+                 xlab = "Share of erarnings the general pop. contributed", 
+                 ylab = "Density in VCA")
+
+p2 <- plotShares(stud = FALSE, 
+                 col = cSecondary,   
+                 var = "contributionShare", 
+                 xlab = "Share of endowment the general pop. contributed", 
+                 ylab = "Density in dPGG Experiment (period 1)")
+
+p3 <- plotShares(stud = TRUE,  col = cPrimary, var = "donationShare",
+                 xlab = "Share of income the students contributed",
+                 ylab = "Density in VCA")
+
+p4 <- plotShares(stud = TRUE,  col = cPrimary, var = "contributionShare", 
+                 xlab = "Share of endowment the students contributed",
+                 ylab = "Density in dPGG Experiment (period 1)")
+
+patchwork <- (p1 / p3) | (p2 / p4)
+patchwork + plot_annotation(caption = "Dashed vertical lines indicate the respective means.\nShaded areas indicate 95% confidence intervals.")
+
+rm(list = c("R1covs", "p1", "p2", "p3", "p4", "patchwork"))
+```
+
+@tbl-tobit-generalizability shows that this is not the case.
+It reports tobit regression results cautioning against transferability from dPGG results to real-world mitigation behavior: The share of endowment contributed in the first period (displayed in the first row) does not predict the share of earnings donated as a VCA.
+The student status negatively affects VCA donations in column two but disappears if one controls for age in column three.
+Importantly, the interaction of student status and first-period contributions is not significant.
+This suggests that the general population sample's transferability is just as bad as the student sample's.
+We thus, find a similar result as @GKLS2020 [p.6].
+
+```{r generalizability_tobit}
+#| results: 'asis'
+#| label: tbl-tobit-generalizability
+#| tbl-cap: Correlations between first-round-dPGG and VCA behavior
+
+to1 <- censReg(formula = donationShare ~ contributionShare, 
+                   data = temp, left = 0, right = 100)
+to2 <- censReg(formula = donationShare ~ contributionShare + student + student * contributionShare, 
+                   data = temp, left = 0, right = 100)
+reg <- lm(formula = donationShare ~ contributionShare + student + student * contributionShare, 
+                   data = temp,)
+to3 <- censReg(formula = donationShare ~ contributionShare + student + student * contributionShare + age + gender, 
+                   data = temp, left = 0, right = 100)
+to4 <- censReg(formula = donationShare ~ contributionShare + student + student * contributionShare + age + gender + switching_row, 
+                   data = temp, left = 0, right = 100)
+
+stargazer(to1, to2, # reg, 
+          to3, # to4,
+
+          model.numbers = TRUE,
+          dep.var.caption  = "Tobit Regression censoring below 0 and above 100",
+          dep.var.labels = "VCA Donation as Share of Earnings",
+          header=FALSE,
+          intercept.bottom = TRUE,
+          order = c(1, 2, 6, 3, 4, 5),
+          covariate.labels = c("First-period contribution in percent", "Student (1 = yes)", "First-period contr. x Student", "Age", "Female (1 = yes)", "Risk Aversion (1-12)"),
+          type = "latex", digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
+          )
+```
 
@@
 #| fig.height: 6
+#| eval: false
 
@@
                    colour = "black", lty = 2, alpha = 0.5) +
-  geom_point(alpha = 0.5, col = cInfo, size = 2) +
+  geom_point(alpha = 0.5, col = cSecondary, size = 2) +
   geom_smooth(method = "lm", formula = y~x, se = FALSE,
-              col = cInfo) +
+              col = cSecondary) +
   scale_x_continuous(limits = c(0, 105),
@@
                    colour = "black", lty = 2, alpha = 0.5) +
-  geom_point(alpha = 0.5, col = cInfo, size = 2) +
+  geom_point(alpha = 0.5, col = cPrimary, size = 2) +
   geom_smooth(method = "lm", formula = y~x, se = FALSE,
-              col = cInfo) +
+              col = cPrimary) +
   scale_x_continuous(limits = c(0, 105),
@@
 
-Does this result hold true if one zooms in and inspects the two samples separately?
-Yes.
-Even though the general population sample is a little more consistent than the student sample, both are contributing more in the abstract game than in the VCA.
-@fig-kernel-generalizability shows distributions of contributions across both choices for both samples.
-The left panels illustrate the behavior of the general population sample.
-The right panels illustrate the behavior of the general population sample.
-The top panels show the behavior in the VCA.
-The bottom panels show the behavior in first period of the game.
-A visual inspection shows that (a) both samples behaved similarly in the first period of the game but (b) different (p =
-`r summary(lm(formula = donationShare ~ student, data = temp))$coefficients[2,4] %>% round(digits = 2)`) in the VCA.
-Furthermore, (c) the behavior in the first period of the experiment predicts the general population sample's behavior in the VCA worse than student sample's behavior (p =
-`r summary(lm(formula = contributionShare ~ donationShare + student + donationShare*student, data = temp))$coefficients[4,4] %>% round(digits = 2)`).
-Finally, (4) contributions in the abstract public good game are higher than contributions to the real public good of climate change mitigation.
-
-```{r vizGeneralizability}
-#| fig-cap: Kernel distributions of contributions across tasks and subject pools.
-#| label: fig-kernel-generalizability
-#| fig.height: 6
-
-# viz wrapper
-plotShares <- function(stud = FALSE,
-                       var  = "donationShare",
-                       col  = cPrimary,
-                       xlab = "",
-                       ylab = ""){
-
-  dt <- temp[student == stud, .(x = get(var))]
-
-  model <- lm(x ~ 1, dt)
-  ci1 <- confint(model, level=0.95)[1]
-  ci2 <- confint(model, level=0.95)[2]
-
-  ggplot(data = dt,
-         mapping = aes(x = x)) +
-    annotate("rect", 
-             xmin = ci1, xmax = ci2, 
-             ymin  =0, ymax = Inf, 
-             alpha = 0.33) +
-    geom_density(alpha = 0.75,
-                 fill = col) +
-    scale_x_continuous(limits = c(0, 100),
-                       expand = c(0, NA)) +
-    scale_y_continuous(limits = c(0, NA),
-                       expand = c(0, NA)) +
-    geom_vline(xintercept = dt[,mean(x, na.rm = TRUE)],
-               lty = 2) +
-    labs(x = xlab,
-         y = ylab) +
-  layout
-}
-
-p1 <- plotShares(stud = FALSE, col = cPrimary,   var = "donationShare", ylab = "Density in VCA")
-p2 <- plotShares(stud = FALSE, col = cPrimary,   var = "contributionShare", 
-                 xlab = "Share of general pop. contributions", ylab = "Density in Experiment (round 1)")
-p3 <- plotShares(stud = TRUE,  col = cSecondary, var = "donationShare")
-p4 <- plotShares(stud = TRUE,  col = cSecondary, var = "contributionShare", xlab = "Share of students' contributions")
-
-patchwork <- (p1 / p2) | (p3 / p4)
-patchwork + plot_annotation(caption = "Dashed vertical lines indicate the respective means.\nShaded areas indicate 95% confidence intervals.")
-
-rm(list = c("R1covs", "p1", "p2", "p3", "p4", "patchwork"))
-```
-
-**Result 3.** _Overall, contribution behavior is uncorrelated with the willingness to contribute to real public goods.
-This holds true for more representative samples and---to a lower degree---for student samples._
+<!--
+@fig-kernel-generalizability also indicates that the general population's contribution behavior is more consistent than the students' behavior.
+Hence, one may conclude that their behavior in the abstract game translates comparably well to the real world.
+This is not the case.
+If anything, the _students'_ behavior in the abstract game is more predictive for their VCA.
+@fig-scatter-generalizability visualizes the within-subjects relationship of both contribution tasks.
+More precisely, it shows a scatter plot of realized choices, with the percentage of endowment spent by each participant in the first period of the game on the x-axis and that spent in the VCA on the y-axis.
+In addition, the figures contains a fitted line of a linear model.
+The upper pannel illustrates overall behavior and exhibits a slope which is indistinguishable from zero.
+No matter how much the participants contributed in the first round, they spent, on average, about `r temp[, round(mean(donationShare))]`% of their income on the VCA.
+The two bottom panels differentiate between both samples with slopes that differ qualitatively.
+However, none of the slopes is significant.
+-->
+
+**Result 3.** _There is no significant correlation between average contributions in the abstract public goods game and contributions to the real public good of climate change mitigation._
 
@@
 
-The goal of the experiment was to replicate specific experiments of GMTV in an online setting using a general population sample.
-The results suggest that it is important to replicate experiments---both purely and scientifically [@Hamermesh2007 p.
+The initial goal of the experiment was to reproduce specific experiments of GMTV in an online setting using a general population sample.
+The results suggest that it is important to reproduce experiments---both purely and scientifically [@Hamermesh2007 p.
 716]---before drawing conclusions about generalizability.
@@
 The three most important findings are as follows: First, the contribution behavior in my experiment is statistically similar to the behavior reported in the original study.
-Consequently, the outcomes growth and inequality are similar as well.
+Consequently, the outcomes growth and inequality are reproducible.
 Second, the online experiment proceeded fluently such that dropouts were no concern.
-Third, contribution behavior in my abstract setting is, if anything, only weakly linked to behavior in the real world.
+Third, contribution behavior in the dynamic abstract setting is not linked to behavior in the real world -- neither for students nor a more representative sample.
 
@@
 The second result is of methodological importance: It highlights that even logistically complex experiments can be conducted online with---not only with clickworkers but also with a true general population sample.
-The third result questions whether recruiting from more representative samples is worth the efforts because it decreases transferability of results to the real world---at least in this specific case.
+The third result questions whether recruiting from more representative samples is worth the efforts because it did not affect transferability of abstract results to the real world.
 

### 2023-05-16 analysis/quarto/paper.tex
rewriting

@@
 
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 \makeatletter
@@
 \hypersetup{
-  pdftitle={Growth and inequality in public good provision --- an extended replication},
+  pdftitle={Revisiting `Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation},
   pdfauthor={Hauke Roggenkamp},
@@
 \begin{frontmatter}
-\title{Growth and inequality in public good provision --- an extended
-replication}
+\title{Revisiting `Growth and Inequality in Public Good Provision'
+---Reproducing and Generalizing Through Inconvenient Online
+Experimentation}
 \author[1,2]{Hauke Roggenkamp%
@@
 \begin{abstract}
+I revisit the dynamic public good game by Gächter et al.~(2017)
+developed to study cooperation under dynamic interdependencies.
+Collecting data from both students and a general population sample, I
+not only reproduce some of the author's original observations but also
+test the game's generalizability. Appending a charitable dictator game,
+I find no correlations between behavior in the abstract game and the
+charitable context. This applies to students and the general population
+sample alike. Studying inexperiend general population samples raises
+methodological challenges with respect to fatigue and dropouts. This
+paper approaches them and provides simple solutions to run relieable
+interactive experiments online.
+
 You can find the most recent version of this paper
 \href{https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.pdf}{here}.
-The abstract follows at later point.
 \end{abstract}
@@
 \end{keyword}
-\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, enhanced, breakable, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, sharp corners]}{\end{tcolorbox}}\fi
+\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, boxrule=0pt, sharp corners, frame hidden]}{\end{tcolorbox}}\fi
 
@@
 thereof) not only affect intermediate outcomes but also the number of
-paths one can choose to reach certain goals.
-
-Standard public good games---although often intended to inform climate
-policies\footnote{See \citet[p.~1]{GKLS2020} for numerous references.}---miss
-these temporal interdependencies simply because participants have the
-same set of actions in each period. Accordingly, participants' actions
-in a given period do not affect their number of actions in subsequent
-periods. A game implemented by Gächter, Mengel, Tsakas \& Vostroknutov
+paths one can choose to reach certain goals. This apllies especially to
+carbon dioxide emissions where its current stock will last for well over
+a millennium \citep{Inman2008, CalzolariEtAl2018}.
+
+Public good games---although often intended to inform climate policies
+(e.g. \citet{MilinskiEtAl2006}, \citet{TavoniEtAl2011},
+\citet{Hauser2014}, \citet{BrickEtAl2015}, \citet{GomezEtAl2018},
+\citet{CalzolariEtAl2018}, \citet{CookEtAl2019})---miss these temporal
+interdependencies simply because participants have the same set of
+actions in each period. Accordingly, participants' actions in a given
+period do not affect their number of actions in subsequent periods. A
+game designed by Gächter, Mengel, Tsakas \& Vostroknutov
 \citeyearpar{GMTV2017} (hereafter, GMTV) as well as Stefan Große (2011,
@@
 little experimental research on these interdependencies\footnote{One
-  exemption are \citet{Moser2019}, who built on GMTV's design do
-  investigate leadership.}, I replicated one of their treatments.
+  exemption are \citet{Moser2019}, who built on GMTV's design to
+  investigate leadership.}, I reproduced one of their treatments to
+compare dynamics across samples.
 
 \citet{GKLS2020} find that standard public good games do not generalize
-to real-world climate action. Because the dynamic setting has a more
-realistic property, one wonders whether it is better suited to inform
-public policy. To answer this question, I ran the experiment with
-different samples\footnote{GMTV ran their experiments with students in
-  Nottingham, England.} online, that is, with participants who make
-their decisions in an environment whcih is more natural than the lab. In
-addition, I observed the participants' behavior in voluntary climate
-actions (VCA). This yielded a setting similar to \citet{GKLS2020}'s
-which allows me to analyze how behavior in the abstract game translates
-into real-world action across samples.
+well to real-world climate action. They also find that generalizability
+depends on structural resemblance of the public goods game with the
+context of climate change mitigation. Greater resemblance improves
+generalizability. Because GMTV's dynamic setting has a more realistic
+property---namely, interdependencies---one wonders whether it is better
+suited to inform public policy. To approach this question, I ran the
+experiment with different samples\footnote{GMTV ran their experiments
+  with students in Nottingham, England.} and observed the participants'
+behavior in voluntary climate actions (VCA). This yielded a setting
+similar to \citet{GKLS2020}'s which allows me to analyze how behavior in
+the abstract game translates into real-world action across samples.
+
+The VCA is a (charitable) dictator games where each participant is a
+dictator dividing her budget between herself and some organization
+linked to the reduction of CO2 emissions. \citet{EckelGrossman1996} were
+the first to implement a charitable dictator game observing
+contributions of 30\% of the endowments. Like \citet{GKLS2020},
+\citet{CarpenterEtAl2008} report that students make lower contributions
+to charity than community members.
 
@@
 draw lessons from online experimentation. This study extends this
-literature \citep[see also][]{GoodmanPaolacci2017} by focusing on a
-completely inexperienced sample that has not been exposed to interactive
-experiments before. This required me to design a robust (and thus, more
-complex) software to minimize attrition. In exchange, the online setting
-allowed me to also collect paradata to assess the fluency and
-feasibility of the experiment. This article reports on both topics: the
-robust design as well as the feasibility.
+literature \citep[see also][ \citet{AmirEtAl2012}]{GoodmanPaolacci2017}
+by focusing on a completely inexperienced sample that has not been
+exposed to interactive experiments before. This required me to design a
+robust (and thus, more complex) software to minimize attrition. In
+exchange, the online setting allowed me to also collect paradata to
+assess the fluency and feasibility of the experiment. This article
+reports on both topics: the robust design as well as the feasibility.
 
@@
 complex online experiments are feasible for samples other than students
-or clickworkers. Third, it shows that findings from abstract games do
-not generalize well and even worse with the representative sample. After
-reporting the methods, this paper is organized along these findings.
+or clickworkers. Third, this paper supports critics arguing that
+findings from abstract games do not generalize well---not even with a
+more representative sample. After reporting the methods, this paper is
+organized along these findings.
+
+\hypertarget{transparency}{%
+\section{Transparency}\label{transparency}}
+
+Well before credibility crises comprised a variety disciplines,
+\citet[p.~2]{bemwriting} indirectly conceded discrepancies between fuzzy
+research processes and the polished article that results from it:
+
+\begin{quote}
+\emph{``There are two possible articles you can write: (a) the article
+you planned to write when you designed your study or (b) the article
+that makes the most sense now that you have seen the results. They are
+rarely the same, and the correct answer is (b).''}
+\end{quote}
+
+Now, 20 years later, we accustom ourselves with mechanisms designed to
+unravel the fuzzy back-and-forth between exploratory and confirmatory
+research. Prominently, pre-registrations were established to tie the
+researchers' hands when doing confirmatory research--reducing observable
+discrepancies between (a) and (b). Today, researchers can not only
+choose where to pre-register but also decide about the level of detail
+they provide. More severely, nothing stops researchers from
+pre-registering multiple hypotheses opposing each other (see e.g.
+\citet{SimmonsEtAl2021} and \citet{PhamEtAl2021} for a discussion).
+
+\citet{WaldronAllen2022} report a wide variety of depth of
+pre-registrations in the field of Neuropsychopharmacology and document
+that the label \emph{`pre-registration'} can be obtained with minimal
+effort. In absence of transparency and scrutiny pre-registrations run
+into danger to miss the target of making science more credible. Even
+more so, they may have adverse effects as the label
+\emph{`pre-registered'} becomes cheap (too) to acquire.
+
+Discussing the costs and benefits of pre-registrations,
+\citet{Olken2015} stresses the uncertainty of research processes and
+promotes moderate approaches. As \citet{WaldronAllen2022}, he argues
+that pre-registrations not necessarily eliminate flexibility. These
+`moderate' or `flexible' approaches require transparency to reduce
+concerns of \emph{`data-mining'} \citep[ p.~61]{Olken2015} by showing
+(a) the analyses I planned to run, (b) the analysis that made most sense
+after collecting the data and the transition from (a) to (b). Because
+this is neither incentivized nor easy to verify, we need tools that make
+transparency convenient to establish and to scrutinize. I propose
+version control (such as Git) as one such tool and illustrate its
+application on this paper: GitHub is a website and cloud-based service
+where developers---and researchers alike---can store and manage their
+code. The service is based on Git\footnote{Git is a specific open-source
+  version control system developed in 2005.} and designed for version
+control. Importantly, changes are time-stamped and can be tracked.
+Moreover, one can create branches, that is, duplicates of code -- either
+to work collaborative or to archive a certain state.
+
+To sum up, pre-registrations alone are necessary but not sufficient to
+restore the credibility in experimental sciences. Pre-registrations must
+come with additional emphasis on transparency covering the whole
+research process as well as with a higher level of scrutiny that looks
+beyond mere labels.
+
+In fact, the experiment reported in this article qualifies for the label
+\emph{`pre-registered'} at a first glance: Parts of the analyses were
+pre-registered in the American Economic Association's RCT Registry
+\citep{preregistration}. In addition, I pre-registered the exact
+analyses I planned to run when I designed the experiment on
+\href{https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd}{GitHub}.\footnote{https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd
+  to run the code, you need to executed the .Rmd files in this
+  repository in the order that is indicated by its file names.}.
+
+The analysis that made the most sense after having collected the data is
+a little different though: Because the more representative subject pool
+was exhausted earlier than expected, I recruited students which opened
+up a new research direction: assessing generalizability. Hence, this
+article combines both confirmatory as well as exploratory research.
+
+Accordingly, I changed many of the analysis scripts.\footnote{The source
+  code of this document contains the analysis and can be found
+  \href{https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}{here}:
+  https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}
+However, because the originally planned analysis code is archived and
+reproducible, these changes are transparent and easy to assess,
+showcasing (a), (b) and the transition from (a) to (b).
 
@@
 In the terminology of \citet{Hamermesh2007}, I ran both a \emph{pure} as
-well as a \emph{scientific replication}\footnote{\citet{Parsons2022} use
-  the term of a \emph{conceptual replication} which means the same.} of
-one treatment of GMTV's dynamic public good game. The pure replication
-re-analyzes the original data.
+well as a \emph{scientific} reproduction\footnote{\citet{Parsons2022}
+  use the term of a \emph{conceptual replication} which means the same.}
+of one treatment of GMTV's dynamic public good game. The pure
+reproduction re-analyzes the original data.
 \protect\hyperlink{A:-Pure-Replication}{Appendix A} documents
@@
 \subsection{Experimental Design}\label{sec-design}}
+
+The design builds on the workhorse model \citet[p.301]{Zelmer2003}
+describes in her meta-analysis, where
+
+\begin{quote}
+\emph{``subjects are divided into groups and play the same game for a
+finite number of periods. Each period, every subject is endowed with an
+income {[}\ldots{]} The subject must then divide this income between a
+contribution to a private account {[}\ldots{]} that yields a constant
+return to themselves only and a contribution to a public account
+{[}\ldots{]} where consumption benefits accrue to all group members. At
+the end of each period, subjects typically learn the aggregate
+contribution to the public good by all members of their group and their
+earnings for the period.''}
+\end{quote}
+
+Considering the design, the only differences between such a
+\emph{static} game and GMTV's design are \emph{dynamics}: Instead of
+receiving fresh endowments every period, participants receive one
+endowment only at the beginning of the first period. A participant's
+endowment in the second period is the wealth she accumulated in the
+first period. A participant's endowment in the third period is the
+wealth she accumulated in the first two periods. And so on. Hence, a
+decision in one period has consequences on future endowments and,
+ultimately, growth paths. For this reason, the game is described as a
+\emph{dynamic} public good game.
 
@@
 
-What makes the game \emph{dynamic}? Instead of receiving fresh
-endowments every period, participants received one endowment only at the
-beginning of the first period. A participant's endowment in the second
-period is the wealth he or she accumulated in the first period. A
-participant's endowment in the third period is the wealth he or she
-accumulated in the first two periods. And so on. Hence, a decision in
-one period has consequences on future endowments and, ultimately, growth
-paths. For this reason, the game is described as a \emph{dynamic} public
-good game
-
 \hypertarget{voluntary-climate-action-vca}{%
@@
 contrast to GMTV and like \citet{GKLS2020}, we employed a VCA, where
-they could donate any amount their earnings to offset carbon dioxide
-(that is, retirine emission permits from the EU ETS).\footnote{Importantly,
+participants could donate any amount their earnings to offset carbon
+dioxide (that is, retire emission permits from the EU ETS).\footnote{Importantly,
   \citet{GKLS2020} made the VCA decision with a fresh endowment
@@
 documentation of individual and aggregate contributions were to be
-posted immediately after the experiments online. To avoid privacy or
-social image concerns, participants learned their unique and random IDs,
-which they needed to identify their individual contributions. The
-document certified that their contributions have been used to offset
+posted immediately after the concluding the sessions online. To avoid
+privacy or social image concerns, participants learned their unique and
+random IDs, which they needed to identify their individual
+contributions. The document certified that their contributions have been
+used to offset
 \href{https://www.compensators.org/compensatelist/?searchterm=stefan+traub}{1.82
@@
 \hypertarget{sec-sample}{%
-\subsection{Sample}\label{sec-sample}}
+\subsection{Recruitment and Sample Characteristics}\label{sec-sample}}
 
@@
 interactive group experiment with this sample. The students, in
-contrast, were used to this kind of experiments. Recruiting them, I
-excluded those who have participated in a public goods game before. As a
-consequence, nonnaiveté is unlikely to affect the validity of the
-experiment \citep[ p.~204]{GoodmanPaolacci2017}.
+contrast, were used to single-player experiments. Recruiting them, I
+excluded those who have participated in interactive experiments such as
+public goods games before, to keep the two distinct subject pools
+comparable in terms of their experience. As a consequence, nonnaiveté is
+unlikely to affect the validity of the experiment \citep[
+p.~204]{GoodmanPaolacci2017}.
 
@@
 University Hamburg's students (both in July 2021).
-Table~\ref{tbl-sample-properties} shows how they compare with respect to
-a few properties.
+Table~\ref{tbl-sample-properties} gives an overview.
 
 \hypertarget{tbl-sample-properties}{}
-\begin{table}[!htbp] \centering 
-  \caption{\label{tbl-sample-properties}Sample Properties } 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-7} 
- & Female & Age & Trust & Meritocracy & Government & Equality \\ 
-\hline \\[-1.8ex] 
- Hamburg Citizens & 0.48$^{***}$ & 47.58$^{***}$ & 3.90$^{***}$ & 3.79$^{***}$ & 3.44$^{***}$ & 4.17$^{***}$ \\ 
-  & (0.07) & (1.21) & (0.19) & (0.21) & (0.19) & (0.23) \\ 
-  & & & & & & \\ 
- Hamburg Students & 0.08 & $-$21.41$^{***}$ & $-$0.58$^{**}$ & 0.23 & 0.71$^{***}$ & 0.12 \\ 
-  & (0.09) & (1.63) & (0.25) & (0.28) & (0.26) & (0.30) \\ 
-  & & & & & & \\ 
- Nottingham Students & $-$0.10 & $-$15.85$^{***}$ & $-$0.03 & 1.65$^{***}$ & 0.87$^{***}$ & $-$0.35 \\ 
-  & (0.09) & (1.52) & (0.23) & (0.26) & (0.24) & (0.28) \\ 
-  & & & & & & \\ 
-\hline \\[-1.8ex] 
-Observations & 208 & 208 & 208 & 208 & 208 & 208 \\ 
-R$^{2}$ & 0.02 & 0.47 & 0.04 & 0.20 & 0.06 & 0.02 \\ 
-Residual Std. Error & 0.50 & 8.75 & 1.35 & 1.52 & 1.40 & 1.63 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\begin{table}[!htbp] \centering \renewcommand*{\arraystretch}{1.1}\caption{\label{tbl-sample-properties}Sample Properties }\resizebox{\textwidth}{!}{
+\begin{tabular}{lrrrrrrrrrl}
+\hline
+\hline
+sample & \multicolumn{3}{c}{Hamburg Citizens} & \multicolumn{3}{c}{Hamburg Students} & \multicolumn{3}{c}{Nottingham Students} &   \\ 
+ Variable & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Test} \\
+\hline
+Age & 52 & 48 & 15 & 64 & 26 & 7.6 & 92 & 33 & 2.6 & F$=88.98^{***}$ \\ 
+Female & 52 & 0.48 & 0.5 & 64 & 0.56 & 0.5 & 92 & 0.38 & 0.49 & F$=2.596^{*}$ \\ 
+Switching Row & 20 & 6.6 & 2.6 & 58 & 6 & 2 & 87 & 6.4 & 1.3 & F$=1.406^{}$\\ 
+\hline
+\hline
+\multicolumn{11}{l}{Statistical significance markers: * p<0.1; ** p<0.05; *** p<0.01}\\ 
 \end{tabular}
+}
 \end{table}
 
-Describe sample properties here.
+Overall, I recruited 116 participants for the experiment. The three
+samples differ significantly with respect to their age. The non-student
+sample is more diverse compared to the two student samples.
 
@@
 good tool to enhance the participants' user experience and thus, to make
-dropouts less likely. Furthermore, the oTree code snippets made it
-possible to handle dropouts.
+dropouts less likely.
 
@@
 explaining the user interface. Before proceeding, they had to answer six
-comprehension questions correctly. Subsequently, they saw a waiting
-screen until they could be matched with three other participants, who
-have answered the comprehension questions correctly. Once matched, they
-were exposed to the decision screen over ten periods. At the end of the
-last period, participants saw results of all periods. Subsequently, they
-made their VCA decision, before I elicited risk preferences
+comprehension questions correctly to avoid confusion in later stages
+\citep{FerraroVossler2010}. Subsequently, they saw a waiting screen
+until they could be matched with three other participants, who have
+answered the comprehension questions correctly. Once matched, they were
+exposed to the decision screen over ten periods. At the end of the last
+period, participants saw results of all periods. Subsequently, they made
+their VCA decision, before I elicited risk preferences
 \citep{HoltLaury2002} and finished with GMTV's questionnaire.
 
-While I tried to stick to GMTV's protocol as close as possible, I
-deviated in a few aspects. First, the instructions were German and also
-covered topics inherent to the online setting (dropouts and bots, for
-instance). Second, I used another software (oTree instead of zTree).
+While I stuck to GMTV's protocol as close as possible, I deviated in a
+few aspects. First, the instructions were German and also covered topics
+inherent to the online setting (dropouts and bots, for instance).
+Second, I used another software (oTree instead of zTree) which also
+affected the graphical user interface participants were exposed to.
 Third, GMTV gave participants the opportunity to donate to \emph{Doctors
-without Borders} whereas we offered carbon dioxide offsets. Fourth, the
-graphical user interface looked different.
+without Borders} whereas we offered carbon dioxide offsets.
 
@@
 
-\hypertarget{sec-registration}{%
-\subsection{Pre-registration}\label{sec-registration}}
-
-Parts of the analyses were pre-registered in the American Economic
-Association's RCT Registry \citep{preregistration}. In addition, I
-pre-registered the exact analyses I planned to run when I designed
-designed the experiment on
-\href{https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd}{GitHub}.\footnote{https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd
-  to run the code, you need to executed the .Rmd files in this
-  repository in the order that is indicated by its file names.}. GitHub
-is a website and cloud-based service where developers---and researchers
-alike---can store and manage their code. The service is based on
-Git\footnote{Git is a specific open-source version control system
-  developed in 2005.} and designed for version control. Importantly,
-changes are timestamped and can be tracked. Moreover, one can create
-branches, that is, duplicates of code -- either to work collaborative or
-to archive a certain state. Accordingly, I archived my analyses scripts
-and created a
-\href{https://github.com/Howquez/coopUncertainty/tree/July21Replication}{branch}
-a few days \emph{before} we collected data.
-
-The analysis that makes the most sense now that I have collected the
-data is a little different though: Because the more representative
-subject pool was exhausted earlier than expected, I recruited students
-unwantedly and changed parts of the scripts.\footnote{The source code of
-  this document contains the analysis and can be found
-  \href{https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}{here}:
-  https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}
-However, because the originally planned analysis code is archived and
-reproducible, these changes are transparent and easy to assess.
-
 \hypertarget{sec-results}{%
@@
 First, I ask whether the samples differ with respect to their initial
-contributions to the public good. Is our replication sample more
-pro-social than the original sample? Figure~\ref{fig-first-round}
-reveals that it is not. The distributions of both samples look fairly
-similar. Both samples contributed 10 tokens, that is, 50\% of their
-endowments on average (median and mean).\footnote{The two-sided rank sum
-  test (comparing differences between samples) yields a p-Value of
-  0.3926 for the mean contribution in first round of the game.}
-Moreover, both samples' initial contributions resemble initial
-contributions participants usually make in the standard game with
-partner matching.\footnote{See Figure 3B in \citet{fehrgaechter2000}
-  (p.989), for instance.} However, in the dynamic game presented here,
-we are particularly interested in the subsequent periods because
-differences add up exponentially. Do the two groups remain similar over
-the course of time?
-
-\begin{figure}
-
-{\centering \includegraphics{paper_files/figure-pdf/fig-first-round-1.pdf}
-
-}
-
-\caption{\label{fig-first-round}Individual contributions to the dynamic
-public good in the first period}
-
-\end{figure}
+contributions to the public good. Is the replication sample (consisting
+of both students and non-students) more pro-social than the original
+sample? A two-sided rank sum test reveals that it is not (p=0.3926).
+Both samples contributed 10 tokens, that is, 50\% of their endowments on
+average (median and mean). Moreover, both samples' initial contributions
+resemble initial contributions participants usually make in the static
+game with partner matching.\footnote{See Figure 3B in
+  \citet[p.989]{fehrgaechter2000}, for instance.} However, in the
+dynamic game presented here, we are particularly interested in the
+subsequent periods because differences add up exponentially. Do the two
+groups remain similar over the course of time?
 
@@
 the average contributions in absolute terms--shows that the original
-sample contributed substantially more than the replication sample
-\emph{in all but the first and last period}. For this reason, the
-original sample's behavior differs from the replication sample's
-behavior in two aspects: it contributes more and exhibits a considerable
-drop in the last period (whereas the replication sample's contributions
-flatten).
+sample contributed more than the replication sample \emph{in all but the
+first and last period}.\footnote{In period five, this difference is
+  significant: a two-sided rank sum test yields p=0.0486.} For this
+reason, the original sample's behavior differs from the replication
+sample's behavior in two aspects: it contributes more and exhibits a
+considerable drop in the last period (whereas the replication sample's
+contributions flatten).
 
 Note that increasing contributions over time imply increasing endowments
-over time. Hence, absolute contributions do not us much about the
+over time. Hence, absolute contributions do not tell much about the
 willingness to cooperate. For this reason, the right panel in
@@
 stabilize. However, both samples also differ with respect to one aspect:
-the replication sample's share of contributions declines faster.
+the replication sample's share of contributions declines faster. This is
+mirrored by a two-sided rank sum test which is only significant at a
+five percent level in periods three and four.
 
@@
 Again, both samples' behavior resembles the contributions participants
-usually make in the standard game with partner matching: contributions
+usually make in the static game with partner matching: contributions
 equal approximately half of endowments in the very first period and
-decrease to around 10\% of endowments by the last period.\footnote{The
-  right panel is thus, comparable to the visualizations \emph{and
-  results} in the standard game. See, for instance, Figure 1B in
-  \citet{fehrgaechter2000} (p.986).} In the dynamic game presented here,
-however, different paths lead to different levels of wealth -- even if
-they share the same start- and end-points. I am thus, more interested in
-the contributions' implications for wealth generation and growth.
+decrease to around ten percent of endowments by the last
+period.\footnote{The right panel is thus, comparable to the
+  visualizations \emph{and results} in the static game. See, for
+  instance, Figure 1B in \citet[p.986]{fehrgaechter2000}.} In the
+dynamic game presented here, however, different paths lead to different
+levels of wealth -- even if they share the same start- and end-points. I
+am thus, more interested in the contributions' implications for wealth
+generation and growth.
 
@@
   have been made, multiplied and redistributed).} Given that the
-original sample contributed more in most of the periods, one would
-expect the respective groups to be considerably more wealthy.
-Figure~\ref{fig-stock-distribution} indicates just that. The grey lines
-show that an average group in the original sample accumulated about 478
-tokens. In contrast, an average group in the replication sample
-accumulated about 380 tokens. This difference is insignificant at
-conventional levels\footnote{The two-sided rank sum test (comparing
-  differences between samples) yields a p-Value of 0.1356 for the mean
-  stock in last round of the game.} though.
-
-\begin{figure}
-
-{\centering \includegraphics{paper_files/figure-pdf/fig-stock-distribution-1.pdf}
-
-}
-
-\caption{\label{fig-stock-distribution}Groups' income at the end of the
-game}
-
-\end{figure}
+original sample contributed more, one would expect the respective groups
+to be more wealthy. A mere mean comparison indicates just that: An
+average group in the original sample accumulated about 478 tokens. In
+contrast, an average group in the replication sample accumulated about
+380 tokens. This difference is insignificant at conventional levels
+though: A two-sided rank sum test (comparing differences between
+samples) yields a p-Value of 0.1356 for the mean stock in last period of
+the game.
 
@@
 growth was continuous and surprisingly linear, given the exponential
-character of the game's design. To sum up, the contribution behavior
-differed between samples. In contrast, neither the eventual wealth nor
-the corresponding growth paths differed. Differences in contribution
+character of the game's design. Despite somewhat differing contribution
+behavior between samples, neither the eventual wealth nor the
+corresponding growth paths differed. Differences in contribution
 behavior did, thus, not translate to significantly different wealth
@@
 and how the inequality grows \emph{within} groups.
-Figure~\ref{fig-gini-distribution} illustrates that inequality did grow:
+Figure~\ref{fig-gini-time-series} illustrates that inequality did grow:
 at the end of the game, the original and the replication groups exhibit
@@
 
-Figure~\ref{fig-ginit-time-series} shows that this initial state of
+Figure~\ref{fig-gini-time-series} also shows that this initial state of
 equality ended with the first period already: both samples exhibit a
@@
 on, the respective Gini coefficients grew slowly but continuously -- for
-both samples.
+both samples.\footnote{In each and every period, the two-sided rank sum
+  test comparing gini coefficients between both sample yields p-values
+  way over ten percent.}
 
@@
 
-{\centering \includegraphics{paper_files/figure-pdf/fig-gini-distribution-1.pdf}
+{\centering \includegraphics{paper_files/figure-pdf/fig-gini-time-series-1.pdf}
 
@@
 
-\caption{\label{fig-gini-distribution}Groups' Gini coefficients (within
-groups) at the end of the game}
-
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics{paper_files/figure-pdf/fig-ginit-time-series-1.pdf}
-
-}
-
-\caption{\label{fig-ginit-time-series}Average Gini coefficient (within
+\caption{\label{fig-gini-time-series}Average Gini coefficient (within
 groups) over time across samples}
@@
 I first comment on the selection into the experiment: It was difficult
-to recruit the sample. The panel counted 1.209 non-students of which we
+to recruit the sample. The panel counted 1.209 non-students of which I
 were able to recruit 130 participants who finished the experiment---even
-though we varied the weekdays and timing of the sessions (which were
+though I varied the weekdays and timing of the sessions (which were
 conducted during a nation-wide lockdown with home office regime). For
-this reason, we also recruited students in the last session which
+this reason, I also recruited students in the last session which
 explains the relatively large number of showups in Table~\ref{tbl-meta}.
@@
 generalizability of my results as I will discuss in
-Section~\ref{sec-generalizability}. Alternatively, I also could have
-contacted a market research institute to recruit additional participants
-within a week. I refrained from doing so to contrast students and the
-general population sample, however.
+Section~\ref{sec-generalizability}.
 
 \hypertarget{tbl-meta}{}
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1566}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1325}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0723}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0964}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1084}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1205}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1566}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1566}}@{}}
-\caption{\label{tbl-meta}The Experimental Sessions' Meta
-Data}\tabularnewline
-\toprule()
-\begin{minipage}[b]{\linewidth}\raggedright
-Session Code
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Date
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Time
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Showups
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Dropouts
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Residuals
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Participants
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Observations
-\end{minipage} \\
-\midrule()
-\endfirsthead
-\toprule()
-\begin{minipage}[b]{\linewidth}\raggedright
-Session Code
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Date
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Time
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Showups
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Dropouts
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Residuals
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Participants
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Observations
-\end{minipage} \\
-\midrule()
-\endhead
-jyf8xd0s & 2021-07-01 & 15:00 & 35 & 4 & 3 & 28 & 7 \\
-vggk2gh1 & 2021-07-03 & 13:00 & 20 & 8 & 0 & 12 & 3 \\
-8gi7c8xg & 2021-07-09 & 13:00 & 21 & 5 & 4 & 12 & 3 \\
-d6jrsxnr & 2021-07-23 & 14:00 & 75 & 8 & 3 & 64 & 16 \\
-\bottomrule()
-\end{longtable}
+\begin{table}
+\caption{\label{tbl-meta}The Experimental Sessions' Meta Data }\tabularnewline
+
+\centering
+\begin{tabular}{l|l|l|r|r|r|r|r}
+\hline
+Session Code & Date & Time & Showups & Dropouts & Residuals & Participants & Observations\\
+\hline
+jyf8xd0s & 2021-07-01 & 15:00 & 35 & 4 & 3 & 28 & 7\\
+\hline
+vggk2gh1 & 2021-07-03 & 13:00 & 20 & 8 & 0 & 12 & 3\\
+\hline
+8gi7c8xg & 2021-07-09 & 13:00 & 21 & 5 & 4 & 12 & 3\\
+\hline
+d6jrsxnr & 2021-07-23 & 14:00 & 75 & 8 & 3 & 64 & 16\\
+\hline
+\end{tabular}
+\end{table}
 
@@
 action from the behavior in public goods games. Using a similar
-strategy, I answer the question for \emph{dynamic} public goods games:
+strategy, I answer the question for a \emph{dynamic} public good game:
 \emph{Not much}. Overall, there seems to be no association between
 choices in the voluntary climate action and the first period in the
-dynamic public goods game. Figure~\ref{fig-scatter-generalizability}
-shows a scatter plot of realized choices, with the percentage of
-endowment spent by each participant in the first period of the game on
-the x-axis and that spent in the VCA on the y-axis. In addition, the
-figure contains a fitted line of a linear model whose slope is
-indistinguishable from zero. No matter how much the participants
-contributed in the first round, they spent, on average, about 21\% of
-their income on the VCA.
-
-\begin{figure}
-
-{\centering \includegraphics{paper_files/figure-pdf/fig-scatter-generalizability-1.pdf}
-
-}
-
-\caption{\label{fig-scatter-generalizability}Scatter plot of average
-contributions in the dPGG and real giving task.}
-
-\end{figure}
-
-Does this result hold true if one zooms in and inspects the two samples
-separately? Yes. Even though the general population sample is a little
-more consistent than the student sample, both are contributing more in
-the abstract game than in the VCA.
+dynamic public goods game.
+
 Figure~\ref{fig-kernel-generalizability} shows distributions of
-contributions across both choices for both samples. The left panels
-illustrate the behavior of the general population sample. The right
-panels illustrate the behavior of the general population sample. The top
-panels show the behavior in the VCA. The bottom panels show the behavior
-in first period of the game. A visual inspection shows that (a) both
-samples behaved similarly in the first period of the game but (b)
-different (p = 0.03) in the VCA. Furthermore, (c) the behavior in the
-first period of the experiment predicts the general population sample's
-behavior in the VCA worse than student sample's behavior (p = 0.07).
-Finally, (d) contributions in the abstract public good game are higher
-than contributions to the real public good of climate change mitigation.
+contributions across both choices for both samples. The top panels
+illustrate the behavior of the general population sample. The bottom
+panels illustrate the behavior of the general population sample. The
+left panels show the behavior in the VCA. The right panels show the
+behavior in first period of the game. A visual inspection shows that (a)
+mean contributions are positive in both tasks for both
+samples.\footnote{The same holds true for median contributions.} (b)
+Furthermore, average contributions are lower in the VCA. (c) In contrast
+to \citet{GKLS2020}'s observation, we do not observe a difference
+between samples in the abstract game's contribution behavior. (d)
+However, the student's share of income contributed to the VCA is
+significantly lower than the general population sample's contributions
+(two-sided rank sum test, p=0.0085). Taken together, these aggregate
+results indicate, that the consistency between tasks is higher for the
+general population than it is for students. Or, to put it differently,
+the general population's behavior in the abstract game better predicts
+their behavior in real-world mitigation context.
 
@@
 
-\textbf{Result 3.} \emph{Overall, contribution behavior is uncorrelated
-with the willingness to contribute to real public goods. This holds true
-for more representative samples and---to a lower degree---for student
-samples.}
+Table~\ref{tbl-tobit-generalizability} shows that this is not the case.
+It reports tobit regression results cautioning against transferability
+from dPGG results to real-world mitigation behavior: The share of
+endowment contributed in the first period (displayed in the first row)
+does not predict the share of earnings donated as a VCA. The student
+status negatively affects VCA donations in column two but disappears if
+one controls for age in column three. Importantly, the interaction of
+student status and first-period contributions is not significant. This
+suggests that the general population sample's transferability is just as
+bad as the student sample's. We thus, find a similar result as
+\citet[p.6]{GKLS2020}.
+
+\hypertarget{tbl-tobit-generalizability}{}
+\begin{table}[!htbp] \centering 
+  \caption{\label{tbl-tobit-generalizability}Correlations between first-round-dPGG and VCA behavior } 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{3}{c}{Tobit Regression censoring below 0 and above 100} \\ 
+\cline{2-4} 
+\\[-1.8ex] & \multicolumn{3}{c}{VCA Donation as Share of Earnings} \\ 
+\\[-1.8ex] & (1) & (2) & (3)\\ 
+\hline \\[-1.8ex] 
+ First-period contribution in percent & 0.07 & $-$0.17 & $-$0.23 \\ 
+  & (0.18) & (0.25) & (0.25) \\ 
+  & & & \\ 
+ Student (1 = yes) &  & $-$48.68$^{**}$ & $-$31.06 \\ 
+  &  & (20.44) & (21.74) \\ 
+  & & & \\ 
+ First-period contr. x Student & 4.00$^{***}$ & 3.96$^{***}$ & 3.94$^{***}$ \\ 
+  & (0.11) & (0.11) & (0.11) \\ 
+  & & & \\ 
+ Age &  &  & 0.92$^{**}$ \\ 
+  &  &  & (0.45) \\ 
+  & & & \\ 
+ Female (1 = yes) &  &  & 4.98 \\ 
+  &  &  & (10.74) \\ 
+  & & & \\ 
+ Risk Aversion (1-12) &  & 0.46 & 0.50 \\ 
+  &  & (0.34) & (0.34) \\ 
+  & & & \\ 
+ Constant & 3.16 & 29.35$^{**}$ & $-$13.93 \\ 
+  & (10.70) & (14.67) & (26.41) \\ 
+  & & & \\ 
+\hline \\[-1.8ex] 
+Observations & 116 & 116 & 116 \\ 
+Log Likelihood & $-$359.78 & $-$356.07 & $-$354.01 \\ 
+Akaike Inf. Crit. & 725.55 & 722.15 & 722.02 \\ 
+Bayesian Inf. Crit. & 733.82 & 735.91 & 741.29 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+\textbf{Result 3.} \emph{There is no significant correlation between
+average contributions in the abstract public goods game and
+contributions to the real public good of climate change mitigation.}
 
@@
 
-The goal of the experiment was to replicate specific experiments of GMTV
-in an online setting using a general population sample. The results
-suggest that it is important to replicate experiments---both purely and
-scientifically \citep[ p.~716]{Hamermesh2007}---before drawing
-conclusions about generalizability.
+The initial goal of the experiment was to reproduce specific experiments
+of GMTV in an online setting using a general population sample. The
+results suggest that it is important to reproduce experiments---both
+purely and scientifically \citep[ p.~716]{Hamermesh2007}---before
+drawing conclusions about generalizability.
 
@@
 behavior reported in the original study. Consequently, the outcomes
-growth and inequality are similar as well. Second, the online experiment
+growth and inequality are reproducible. Second, the online experiment
 proceeded fluently such that dropouts were no concern. Third,
-contribution behavior in my abstract setting is, if anything, only
-weakly linked to behavior in the real world.
+contribution behavior in the dynamic abstract setting is not linked to
+behavior in the real world -- neither for students nor a more
+representative sample.
 
@@
 population sample. The third result questions whether recruiting from
-more representative samples is worth the efforts because it decreases
-transferability of results to the real world---at least in this specific
-case.
+more representative samples is worth the efforts because it did not
+affect transferability of abstract results to the real world.
 
@@
 \hypertarget{tbl-gini-error}{}
-\begin{longtable}[]{@{}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1212}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0909}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0606}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1212}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1061}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1061}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1061}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1061}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0909}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0909}}@{}}
-\caption{\label{tbl-gini-error}Subset of Data illustrating the Gini
-Coefficient's Error}\tabularnewline
-\toprule()
-\begin{minipage}[b]{\linewidth}\raggedleft
-exp\_num
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-gr\_id
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-per
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-subj\_id
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-tokens
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-other1
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-other2
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-other3
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-gini
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-GINI
-\end{minipage} \\
-\midrule()
-\endfirsthead
-\toprule()
-\begin{minipage}[b]{\linewidth}\raggedleft
-exp\_num
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-gr\_id
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-per
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-subj\_id
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-tokens
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-other1
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-other2
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-other3
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-gini
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-GINI
-\end{minipage} \\
-\midrule()
-\endhead
-1 & 101 & 5 & 111 & 42 & 27 & 27 & 30 & 0.127 & 0.127 \\
-1 & 101 & 5 & 112 & 27 & 42 & 27 & 30 & 0.111 & 0.127 \\
-1 & 101 & 5 & 113 & 27 & 42 & 27 & 30 & 0.111 & 0.127 \\
-1 & 101 & 5 & 114 & 30 & 42 & 27 & 27 & 0.127 & 0.127 \\
-\bottomrule()
-\end{longtable}
+\begin{table}
+\caption{\label{tbl-gini-error}Subset of Data illustrating the Gini Coefficient's Error }\tabularnewline
+
+\centering
+\begin{tabular}{r|r|r|r|r|r|r|r|r|r}
+\hline
+exp\_num & gr\_id & per & subj\_id & tokens & other1 & other2 & other3 & gini & GINI\\
+\hline
+1 & 101 & 5 & 111 & 42 & 27 & 27 & 30 & 0.127 & 0.127\\
+\hline
+1 & 101 & 5 & 112 & 27 & 42 & 27 & 30 & 0.111 & 0.127\\
+\hline
+1 & 101 & 5 & 113 & 27 & 42 & 27 & 30 & 0.111 & 0.127\\
+\hline
+1 & 101 & 5 & 114 & 30 & 42 & 27 & 27 & 0.127 & 0.127\\
+\hline
+\end{tabular}
+\end{table}
 
@@
 \hypertarget{tbl-mean-error}{}
-\begin{longtable}[]{@{}rrrrrrrr@{}}
-\caption{\label{tbl-mean-error}Subset of Data illustrating the Means's
-Error}\tabularnewline
-\toprule()
-exp\_num & gr\_id & per & subj\_id & gdp & sum & mean & MEAN \\
-\midrule()
-\endfirsthead
-\toprule()
-exp\_num & gr\_id & per & subj\_id & gdp & sum & mean & MEAN \\
-\midrule()
-\endhead
-1 & 101 & 4 & 111 & 116 & 18 & 0.168 & 0.155 \\
-1 & 101 & 5 & 111 & 126 & 18 & 0.155 & 0.143 \\
-1 & 101 & 6 & 111 & 136 & 17 & 0.135 & 0.125 \\
-\bottomrule()
-\end{longtable}
+\begin{table}
+\caption{\label{tbl-mean-error}Subset of Data illustrating the Means's Error }\tabularnewline
+
+\centering
+\begin{tabular}{r|r|r|r|r|r|r|r}
+\hline
+exp\_num & gr\_id & per & subj\_id & gdp & sum & mean & MEAN\\
+\hline
+1 & 101 & 4 & 111 & 116 & 18 & 0.168 & 0.155\\
+\hline
+1 & 101 & 5 & 111 & 126 & 18 & 0.155 & 0.143\\
+\hline
+1 & 101 & 6 & 111 & 136 & 17 & 0.135 & 0.125\\
+\hline
+\end{tabular}
+\end{table}
 

### 2023-05-16 analysis/slides/CLICCS.qmd
rewriting

--- 2022-11-04 analysis/quarto/paper.qmd
@@
 ---
-title: Growth and inequality in public good provision --- an extended replication
-author:
-  - name: Hauke Roggenkamp
-    email: hauke.roggenkamp@unisg.ch
-    affiliations:
-        - id: HSU
-          name: Helmut Schmidt University
-          department: Department of Economics
-          address:  Holstenhofweg 85
-          city: Hamburg
-          state: Germany
-          postal-code: 22043
-        - id: HSG
-          name: University of St. Gallen
-          department: Institute for Behavioral Science and Technology
-          address: Torstrasse 25
-          city: St. Gallen
-          state: Switzerland
-          postal-code: 9000
-    # attributes:
-    #     corresponding: true
-    # note: This is the first author footnote.
-abstract: |
-  You can find the most recent version of this paper [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.pdf). The abstract follows at later point.
-keywords: 
-  - Replication study
-  - Non-convenience sample
-  - Open science
-  - Dynamic public good game
-  - Online experiment
-  - Generalizability
-date: last-modified
+title: "Growth and inequality in public good provision"
+author: Hauke Roggenkamp, Stefan Traub and Michael Berlemann
+date: "`r Sys.Date()`"
 bibliography: ../biblio.bib
 format: 
-  elsevier-pdf:
-    keep-tex: true
-    journal:
-      name: Journal of Behavioral and Experimental Economics
-      formatting: preprint
-      model: 3p
-      cite-style: authoryear
+  revealjs: 
+    footer: "[CLICCS B5 | Nov 2022](https://www.cliccs.uni-hamburg.de/research/theme-b/b5.html)"
+    preview-links: true
 ---
@@
 
-<!-- PAPER STARTS HERE -->
-
-<!-- 
-# Key Takeaways
-
-- We **[replicate](#gmtv-replication)** a public goods experiment with dynamic inter-dependencies and find similar results as @GMTV2017. 
-    + Absolute contributions increase over time.
-    + Just as in _static_ public goods experiments, the share of endowments contributed decreases over time.
-    + The richest groups earn fifteen times more than the poorest groups.
-    + While there clearly is growth, groups do not realize the maximal potential efficiency and earn just over `r main[treatment == "replication" & round == 10, mean(stock)/(80*1.5^10)*100] %>% round(digits=1)`% of what is possible.
-- Varying the subject pool and including a voluntary climate action (VCA), we have a setup similar to @GKLS2020, which allows us to assess **[generalizability](#generalizability)**.^[Note that one can easily model the VCA as a dictator game, which relates to a literature summarized by @cartwright2022.]
-- Studying a general population sample online, synchronously and over the course of multiple periods, we find that classic **[lab procedures](online-methodology)** can be applied outside of the lab too.
-    + Even though we conducted the experiment online and remotely, dropouts (or "attrition") are no concern.
-    + Relying on an inexperienced non-convenience sample that cannot interact with experimenters, `r trunc((R1[comprehension > 1] %>% NROW() / R1[!(is.na(comprehension))] %>% NROW())*100)`% of all participants stated that they understood the game.
-    + Participants make relatively fast decisions which makes longer games feasible in the future.^[Taken together with inefficient growth and the lack of dropouts, additional rounds are fairly cheap.]
-
--->
-
-# Introduction {#sec-intro}
-
-Today's actions are tomorrow's result.
-There are many settings in which current decisions affect future outcomes and with it, future decision spaces.
-Opting for environmental friendly policies today not only reduces carbon dioxide omissions but also helps us to reach the Paris climate targets tomorrow.
-Deferring these policies, the targets can be reached as well---but with less flexibility.
-Hence, today's actions (or the omission thereof) not only affect intermediate results but also the number of paths one can choose to reach certain goals.
-
-Standard public good games---although often intended to inform climate policies^[See @GKLS2020 [p.
-1] for numerous references.]---miss these temporal interdependencies because participants have the same set of actions in each period.
-A game implemented by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017] (hereafter, GMTV) as well as Stefan Große (2011, unpublished) incorporated interdependencies into a _dynamic_ public good game with students in Nottingham, England and Erfurt, Germany.
-
-Because their setting is more realistic, one wonders whether it is better suited to inform public policy.
-To answer this question, I replicated parts of GMTV's experiment with different samples.
-In addition, I observed the participant's behavior in voluntary climate actions (VCA).
-This yielded a setting similar to @GKLS2020's which allows me to analyze how behavior in the abstract game translates into real-world action across samples.
-
-I utilized an inexperienced sample that has not been exposed to interactive experiments before.
-Furthermore, I conducted the experiment online.
-This required me to make the experiment's software robust to minimize attrition.
-Because I observed metrics to assess the fluency and feasibility of online experiments, this study also serves as a case study like the one of @AGM2018.
-
-Taken together, this study makes three contributions.
-First, it replicates parts of GMTV's original experiment and highlights the importance of pure replications.
-Second, it shows that logistically complex online experiments are feasible for samples other than students or clickworkers.
-Third, it shows that findings from abstract games do not generalize well and even worse with the representative sample.
-After reporting the methods, this paper is organized along these findings.
-
-# Methodology {#sec-methods}
-
-In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific replication_^[@Parsons2022 use the term of a _conceptual replication_ which means the same.] of one treatment of GMTV's dynamic public good game.
-The pure replication re-analyzes the original data.
-[Appendix A](#A:-Pure-Replication) documents [errors I identified]() in the original paper.
-The scientific replication, where I utilize a different sample drawn from a different population in a different situation, is described in the following sections.
-
-## Experimental Design {#sec-design}
-
-As in the NOPUNISH 10 Period treatment of GMTV, I ran sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of $N_i^1 = 20$ tokens^[A token was worth `r EXCHANGE_RATE` Euros.], $T=10$ periods, a private account with a return of $1$ and a group account with a return of $1.5$ ($\Rightarrow$ MPCR$\equiv \frac{1.5}{4}$), such that:
+# Background
+
+We would like to submit to JBEE's special issue: [Transparency, Reproducibility, and Generalizability of Behavioral Economics Experiments](https://www.sciencedirect.com/journal/journal-of-behavioral-and-experimental-economics/about/call-for-papers#transparency-reproducibility-and-generalizability-of-behavioral-economics-experiments)
+
+# Outline {.smaller}
+
+**Transparency**: We preregistered our (initially intended) analysis [@preregistration] and [version control](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd) is public on GitHub.
+
+**Reproducibility**: We ran a pure as well as a scientific (yet partial) replication of @GMTV2017.
+
+**Generalizability**: We ended up in a setting similar to @GKLS2020.
+
+**Online Feasibility**: Because the experiment was logistically complex, we provide a case study similar to @AGM2018.
+
+# Replication: @GMTV2017
+
+## Idea
+
+- Opting for necessary climate policies tomorrow does not render it impossible to reach targets --- but it makes it increasingly more difficult.
+- We can describe this as temporal interdependencies where timing and paths matter.
+- Even though public good games are often interpreted in climate policy contexts, they do not capture these dynamics.
+- Gächter and colleagues designed a _dynamic_ public game that captures just that.
+
+## Dynamic Public Good Game
+
+We conducted their 10-period treatment without punishing.
 
 $$
-N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
+E_i^{t+1}=E_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
 $$
-What makes the game _dynamic_?
-Instead of receiving fresh endowments every period, participants received one endowment only at the beginning of the first period.
-A participant's endowment in the second period is the wealth he or she accumulated in the first period.
-A participant's endowment in the third period is the wealth he or she accumulated in the first two periods.
-And so on.
-Hence, a decision in one period has consequences on future endowments and, ultimately, growth paths.
-For this reason, the game is described as a _dynamic_ public good game
-
-## Voluntary Climate Action (VCA)
-
-Like GMTV we employ a real giving task after the abstract game.
-In contrast to GMTV and like @GKLS2020, we employed a VCA, where they could donate (some of) their earnings to offset carbon dioxide (that is, by retiring emission permits from the EU ETS).^[Importantly, @GKLS2020 made the VCA decision with a fresh endowment _before_ they played the abstract game.
-I deviate from their procedure to match GMTV's procedure.]
-To ensure that each participant had the same basic level of information about the impact of their decision, I provided some basic information about the mechanism.
-The information also highlighted that the mitigation came into operation on a European level.
-Finally, I informed the participants that the documentation of individual and aggregate contributions were posted immediately after the experiments online.
-To avoid privacy or social image concerns, participants learned their unique and random IDs, which they needed to identify their individual contributions.
-This document certified that their contributions have been used to offset [1.82 tons](https://www.compensators.org/compensatelist/?searchterm=stefan+traub) of carbon dioxide emissions.
-
-## Sample {#sec-sample}
-
-I recruited the participants from the so called _[HamburgPanel](https://www.wiso.uni-hamburg.de/forschung/forschungslabor/umfragelabor/aktuelle-umfragen/hamburgpanel.html)_ using HROOT [@hroot].
-The panel is provided by the University of Hamburg's Research Laboratory, which used a randomized last digits approach to build the panel while drawing from the population of citizens from Hamburg, Germany.
-Because the sample was exhausted at one point, I also recruited students from the University of Hamburg.
-
-At the time I conducted the experiment, the representative sample was not familiar with interactive experiments.
-In fact, I ran the first interactive group experiment with this sample.
-The students, in contrast, are used to this kind of experiments.
-Recruiting them, I excluded those who have participated in a public goods game before.
-As a consequence, nonnaiveté is unlikely to affect the validity of my experiment [@GoodmanPaolacci2017 p.
-204].
-
-Throughout this paper, I will compare results of my experiment with the results of GMTV's NOPUNISH 10 Period treatments.
-I am thus, referring to three different samples utilized at two points in time: the University of Nottingham's students (in late 2012), Hamburg's citizens and the University Hamburg's students (both in July 2021).
-@tbl-sample-properties shows how they compare with respect to a few properties.
-
-```{r sampleDifferences1, results = "asis", warning = FALSE}
-#| label: tbl-sample-properties
-#| tbl-cap: Sample Properties
-
-covs[, sample := "Nottingham Students"]
-covs[treatment == "replication" & student == TRUE, sample := "Hamburg Students"]
-covs[treatment == "replication" & student == FALSE, sample := "Hamburg Citizens"]
-covs[, sample := as.factor(sample)]
-# covs[, sample := ordered(sample, levels = c("Nottingham Students", "Hamburg Students", "Hamburg Citizens"))]
-
-m1 <- lm(formula = gender ~ sample, data = covs)
-m2 <- lm(formula = age ~ sample, data = covs)
-m3 <- lm(formula = switching_row ~ sample, data = covs)
-m4 <- lm(formula = donation ~ sample, data = covs)
-m5 <- lm(formula = pq11 ~ sample, data = covs)
-m6 <- lm(formula = pq12 ~ sample, data = covs)
-m7 <- lm(formula = pq13 ~ sample, data = covs)
-m8 <- lm(formula = pq14 ~ sample, data = covs)
-
-stargazer(m1, m2, m5, m6, m7, m8,
-
-          column.labels = c("female", "age",
-                            "trust", "meritocracy", "government", "equality") %>% str_to_title(),
-          model.numbers = FALSE,
-          dep.var.labels.include = FALSE,
-          header=FALSE,
-          intercept.bottom = FALSE,
-          covariate.labels = c("Hamburg Citizens", "Hamburg Students", "Nottingham Students"),
-
-          type = "latex", digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
-          )
-```
-
-```{r}
-# covs[, sample := ordered(sample, levels = c("Nottingham Students", "Hamburg Students", "Hamburg Citizens"))]
-```
-
-Describe sample properties here.
-
-## Software {#sec-software}
-
-The experiment was logistically complex for several reasons.
-First, the sample was inexperienced.
-Second, the experiment was interactive and synchronous.
-Third, the underlying game was dynamic and interdependent.
-This makes dropouts not only more likely, but also more expensive which is why dropouts were a major concern implementing the experiment.
-
-I chose oTree [@oTree] to implement the experiment because it is open-source, well documented and very flexible.
-Its [Bootstrap](https://getbootstrap.com/) (a powerful frontend toolkit) integration allowed me to make the graphical user interface interactive, appealing and easy to navigate.
-The [Highcharts library](https://www.highcharts.com/) made it easy to visualize results and to communicate dynamics.
-The oTree code snippets made it possible to handle dropouts, for instance, by replacing them with artificial bots (and informing the rest of the group thereof).
-Insofar, oTree served a good tool to consider the participants' user experience and thus, to make dropouts less likely.
-
-## Procedure {#sec-procedure}
-
-Participants entered the experiment at appointed times remotely from home.
-They first saw a welcome screen.
-After agreeing to the privacy policy, they could proceed to the instructions individually.
-Having read these instructions, each participant has also seen a demo-screen explaining the user interface.
-Before proceeding, they had to answer six comprehension questions correctly.
-Subsequently, they saw a waiting screen until they could be matched with three other participants, who have answered the comprehension questions correctly.
-Once matched, they were exposed to the decision screen over ten periods.
-At the end of the last period, participants saw results of all periods.
-Subsequently, they made their VCA decision, before I elicited risk preferences [@HoltLaury2002] and finished with GMTV's questionnaire.
-
-While I tried to stick to GMTV's protocol as close as possible, I deviated in a few aspects.
-First, the instructions were German and also covered topics inherent to the online setting (dropouts and bots, for instance).
-Second, I used another software (oTree instead of zTree).
-Third, GMTV gave participants the opportunity to donate to _Doctors without Borders_ whereas we offered carbon dioxide offsets.
-Fourth, the graphical user interface looked different.
-
-```{r totalTimeSpent}
-tmp <- duration[page_index == 1 | page_index == 76, 
-                .(page_index, participant_code, page_submission)]
-tmp[order(participant_code, page_index), 
-    total := page_submission - data.table::shift(x = page_submission,
-                                                 n = 1,
-                                                 type = "lag"),
-    by = participant_code]
-
-total_completion_time <- tmp[!is.na(total), mean(total/ 60) %>% round()]
-```
-
-The experiment lasted around `r total_completion_time` minutes on average.
-The earnings of the average subject were `r earningsMean %>% round(digits = 2)` Euros (sd = `r earningsSD  %>% round(digits = 2)`).^[This values include earnings from the incentivized risk elicitation task that are not part of the analysis.]
-
-## Pre-registration {#sec-registration}
-
-Parts of the analyses are pre-registered [@preregistration].
-In addition, I pre-registered the exact analyses I planned to run when I designed designed the experiment on [GitHub](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.].
-GitHub is a website and cloud-based service where developers---and researchers alike---can store and manage their code.
-The service is based on Git^[Git is a specific open-source version control system developed in 2005.] and designed for version control.
-Importantly, changes are timestamped and can be tracked.
-Moreover, one can create branches, that is, duplicates of code -- either to work collaborative or to archive a certain state.
-Accordingly, I archived my analyses scripts and created a [branch](https://github.com/Howquez/coopUncertainty/tree/July21Replication) a few days _before_ we collected data.
-
-The analysis that makes the most sense now that you have collected the data is a little different, though: Because the more representative subject pool was exhausted earlier than expected, I recruited students unwantedly and changed parts of the scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd] Because the originally planned analysis code is archived and reproducible, these changes are transparent.
-
-# Results {#sec-results}
-
-## Pre-registered GMTV Replication {#sec-replication}
-
-### Contribution Behavior {#sec-contributions}
-
-```{r prepFirstSummary}
-replication <- R1[treatment == "replication", ownContribution]
-GMTV    <- R1[treatment == "noPunish10", ownContribution]
-
-rows <- sapply(X = list(replication, GMTV), FUN = NROW) %>% max()
-temp <- data.frame(replication = c(replication, rep(NA, rows - NROW(replication))),
-                   GMTV = c(GMTV, rep(NA, rows - NROW(GMTV))))
-
-rs1 <- wilcox.test(replication, 
-                   GMTV,
-                   exact = FALSE)$p.value %>% 
-  round(digits = 4) %>% 
-  formatC(format = "f", 
-          digits = 4)
-```
-
-First, I ask whether the samples differ with respect to their initial contributions to the public good.
-Is our replication sample more pro-social than the original sample?
-@fig-first-round reveals that it is not.
-The distributions of both samples look fairly similar.
-Both samples contributed 10 tokens, that is, 50% of their endowments on average (median and mean).^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean contribution in first round of the game.] Moreover, both samples' initial contributions resemble initial contributions participants usually make in the standard game with partner matching.^[See Figure 3B in @fehrgaechter2000 (p.989), for instance.] However, in the dynamic game presented here, we are particularly interested in the subsequent periods because differences add up exponentially.
-Do the two groups remain similar over the course of time?
+
+- Groups of four players receive an initial endowment of $E_i^{1}=20$ tokens each. 
+- Their contributions $c_i^t$ are pooled, multiplied and divided by all players.
+- Today's actions are tomorrow's result: $E_i^{t+1}$ is the current period's outcome.
+- The game ends after period 10 and participants earn $E_i^{10}$.
+
+## Methods {.smaller}
+
+We ran a _scientific_ replication (different sample drawn from a different population in a different situation).
+
+- We recruited a non-convenience sample from Hamburg^[The so called _[HamburgPanel](https://www.wiso.uni-hamburg.de/forschung/forschungslabor/umfragelabor/aktuelle-umfragen/hamburgpanel.html)_.] that was completely inexperienced in interactive multi-player experiments at that time.
+- We conducted a synchronous online experiment using oTree [@oTree] with a different (probably more appealing) User Interface.
+- After the game, participants could donate to retire emission permits from the EU ETS (instead of doctors without borders).
+- Four sessions in July 2021. Importantly, the subject pool was exhausted, so we had to invite additional students.
+- N = `r R1[treatment == 'replication', .N]`
+
+## Initial Contributions
 
@@
 
-```{r firstRoundSummary}
-#| results: asis
-#| warning: false
-#| fig.cap: "test"
-#| eval: false
-
-if(knitr::is_html_output()){
-  type <- "html"
-} else {
-  type = "latex"
-}
-
-stargazer(temp,
-          summary.stat = c("mean", "median","sd", "max", "min", "n"),
-          type = type, 
-          flip = TRUE, 
-          header=FALSE)
-```
-
-In particular, do the two samples' contributions follow the same path over the 10 periods they played?
-The answer is _no_.
-@fig-share-of-contributions illustrates that the samples make similar contributions at the beginning and the end of the game but behave differently in between.
-More precisely, the left panel--depicting the average contributions in absolute terms--shows that the original sample contributed substantially more than the replication sample _in all but the first and last period_.
-For this reason, the original sample's behavior differs from the replication sample's behavior in two aspects: it contributes more and exhibits a considerable drop in the last period (whereas the replication sample's contributions flatten).
-
-Note that increasing contributions over time imply increasing endowments over time.
-Hence, absolute contributions do not us much about the willingness to cooperate.
-For this reason, the right panel in @fig-share-of-contributions shows the average _share of endowments contributed_ over time.
-Both samples exhibit a similar pattern: their share of endowments contributed declined and did not stabilize.
-However, both samples also differ with respect to one aspect: the replication sample's share of contributions declines faster.
+## Contributions over Time
 
@@
 
-Again, both samples' behavior resembles the contributions participants usually make in the standard game with partner matching: contributions equal approximately half of endowments in the very first period and decrease to around 10% of endowments by the last period.^[The right panel is thus, comparable to the visualizations _and results_ in the standard game.
-See, for instance, Figure 1B in @fehrgaechter2000 (p.986).] In the dynamic game presented here, however, different paths lead to different levels of wealth -- even if they share the same start- and end-points.
-I am thus, more interested in the contributions' implications for wealth generation and growth.
-
-### Wealth Creation {#sec-wealth}
-
-```{r summaryWealth}
-#| results: asis
-#| warning: false
-#| fig.cap: "test"
-
-if(knitr::is_html_output()){
-  type <- "html"
-} else {
-  type = "latex"
-}
-
-replication <- main[treatment == "replication" & round == 10, stock]
-GMTV    <- main[treatment == "noPunish10" & round == 10, stock]
-
-rs1 <- wilcox.test(replication, 
-                   GMTV,
-                   exact = FALSE)$p.value %>% 
-  round(digits = 4) %>% 
-  formatC(format = "f", 
-          digits = 4)
-
-```
+## Wealth Creation
 
@@
 ```
-
-How do the different contribution-paths translate into wealth?^[To measure wealth and growth, I define a variable called _stock_ which sums the endowments of all participants in a given group at the end of the round (that is, after the contributions have been made, multiplied and redistributed).] Given that the original sample contributed more in most of the periods, one would expect the respective groups to be considerably more wealthy.
-@fig-stock-distribution indicates just that.
-The grey lines show that an average group in the original sample accumulated about `r round(originalWealth)` tokens.
-In contrast, an average group in the replication sample accumulated about `r round(replicationWealth)` tokens.
-This difference is insignificant at conventional levels^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean stock in last round of the game.] though.
 
@@
 
-```{r overallGinis}
-rG <- main[round == 10 & treatment == "replication",
-           .(stock = sum(stock)),
-           by = groupID][, Gini(stock)] %>% round(digits = 2)
-
-oG <- main[round == 10 & treatment == "noPunish10",
-           .(stock = sum(stock)),
-           by = groupID][, Gini(stock)] %>% round(digits = 2)
-
-rSD <- main[round == 10 & treatment == "replication",
-            .(stock = sum(stock)),
-            by = groupID][, sd(stock)] %>% round(digits = 2)
-
-oSD <- main[round == 10 & treatment == "noPunish10",
-            .(stock = sum(stock)),
-            by = groupID][, sd(stock)] %>% round(digits = 2)
-```
-
-Although there clearly is growth, groups do not realize the maximal potential efficiency: under full cooperation, a group can accumulate at least `r (80*1.5^10) %>% trunc()` tokens or EUR `r (80*1.5^10 /20) %>% trunc()`.
-This is depicted in the left panel of @fig-growth-heterogeneity, where one can see the average wealth over time by sample.
-The panel illustrates for both samples that growth was continuous and surprisingly linear, given the exponential character of the game's design.
-To sum up, the contribution behavior differed between samples.
-In contrast, neither the eventual wealth nor the corresponding growth paths differed.
-Differences in contribution behavior did, thus, not translate to significantly different wealth outcomes.
-
-Why?
-Perhaps because the heterogeneity within samples and across groups has been too large to _detect_ a significant difference.
-The right panel of @fig-growth-heterogeneity depicts heterogeneity: In the replication sample, the richest group earned `r a <- main[treatment == "replication" & round == 10, max(stock)]; a` tokens (which is about `r round(a/80, digits = 2)*100`% of the initial endowment) whereas the poorest group ends up with `r b <- main[treatment == "replication" & round == 10, min(stock)]; b` tokens (`r round(b/80, digits = 2)*100`%).
-More broadly, the replication sample is characterized by inequality between groups ($SD_{Replication} =$ `r rSD`).
-The same holds true for the original sample ($SD_{Original} =$ `r oSD`).
-Hence, the heterogeneity across groups does not differ between samples, which is remarkable because the replication sample was drawn from a more heterogeneous (non-convenience sample).
-Does it differ within groups?
-
-<!-- doch lieber Gini? statt SD reporten? -->
+## Wealth Creation
 
@@
 
-### Inequality {#sec-inequality}
-
-```{r summaryGini}
-#| results: asis
-#| warning: false
-#| fig.cap: "test"
-
-if(knitr::is_html_output()){
-  type <- "html"
-} else {
-  type = "latex"
-}
-
-replication <- main[treatment == "replication" & round == 10, gini]
-GMTV    <- main[treatment == "noPunish10" & round == 10, gini]
-
-rs1 <- wilcox.test(replication, 
-                   GMTV,
-                   exact = FALSE)$p.value %>% 
-  round(digits = 4) %>% 
-  formatC(format = "f", 
-          digits = 4)
-
-```
-
-```{r giniVariables}
-originalGini    <- main[treatment == "noPunish10" & round == 10, mean(gini)] %>% round(digits = 2)
-replicationGini <- main[treatment == "replication" & round == 10, mean(gini)] %>% round(digits = 2)
-```
-
-Given the different samples and the possibility of endogenous growth--which essentially is the main feature of the game--I ask whether and how the inequality grows _within_ groups.
-@fig-gini-distribution illustrates that inequality did grow: at the end of the game, the original and the replication groups exhibit an average Gini coefficient of `r originalGini` and `r replicationGini`, respectively.^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean Gini coefficient in last round of the game.] Because every participant started with the same initial endowment (in _Period 0_, so to speak), every group started equally--with a Gini coefficient equaling zero.
-
-@fig-ginit-time-series shows that this initial state of equality ended with the first period already: both samples exhibit a stark incline in inequality before the second period started.
-From then on, the respective Gini coefficients grew slowly but continuously -- for both samples.
-
-```{r giniDistributionViz}
-#| fig-cap: Groups' Gini coefficients (within groups) at the end of the game
-#| label: fig-gini-distribution
-
-ggplot(data = main,
-       mapping = aes(x = gini, fill = treatment, lty = treatment)) +
-  geom_density(alpha = 0.5) +
-  scale_x_continuous(limits = c(0, 1),
-                       expand = c(0, NA)) +
-  scale_y_continuous(limits = c(0, NA),
-                       expand = c(0, NA)) +
-  scale_fill_manual(values = c(cPrimary, cSecondary),
-                    labels = c("Original Sample", "Replication Sample")) +
-  guides(lty = "none") +
-  geom_vline(xintercept = replicationGini,
-             col = "#000000", alpha = 0.5,
-             lty = 2) +
-  geom_vline(xintercept = originalGini,
-             col = "#000000", alpha = 0.5,
-             lty = 1) +
-    labs(title = "", 
-       y = "", x = "Gini Coefficient",
-       caption = "Grey lines indicate means (dashed line = replication sample).") +
-  layout +
-  theme(legend.position = "top")
-```
+## Inequality
 
@@
 
-**Result 1.** _The `NOPUNISH 10` treatment of GMTV can be replicated because the replication data resemble the original data with respect to initial and final contributions, wealth and growth as well as inequality._
-
-This is remarkable given the different sample and language, the different software and user interface as well as the online setting during the COVID19 pandemic.
-The result suggests that, by and large, the sum of these factors did not affect people’s preferences towards cooperation.
-
-## Online Feasibility {#sec-feasibility}
-
-How did the participants, who have never participated in an online group experiment before, cope with the situation?
-Moreover, did participants understand the unfamiliar setting they found themselves in?
-While the answer to the former question requires more thought, the answer to the latter simply is _yes_: `r 67` out of `r 44 + 67 + 5` answered with _"yes"_ when I asked them.
-Another `r 44` answered with _"rather yes"_ while nobody indicated that he or she did not understand the situation at all.
-To analyze how participants coped with the situation, I consider three additional metrics: selection into the experiment,  attrition as well as the time spent on each page.
-
-I first comment on the selection into the experiment: It was difficult to recruit the sample.
-The panel counted 1.209 non-students of which we were able to recruit `r main[student == FALSE, .N]` participants who finished the experiment---even though we varied the weekdays and timing of the sessions (which were conducted during a nation-wide lockdown with home office regime).
-For this reason, we also recruited students in the last session which explains the relatively large number of showups in @tbl-meta.
-Although I intended to refrain from the recruitment of students initially, this particular sub sample enabled me to investigate the generalizability of my results as I will discuss in  @sec-generalizability.
-Alternatively, I also could have contacted a market research institute to recruit additional participants within a week.
-I refrained from doing so to contrast students and the general population sample, however.
-
-```{r showMeta}
-#| label: tbl-meta
-#| tbl-cap: The Experimental Sessions' Meta Data
-
-meta %>% kable(col.names = names(meta) %>% 
-                 str_replace_all(pattern = "\\.",
-                                 replacement = " ") %>% 
-                 str_to_title()) #, caption = 'A table of the first 10 rows of the mtcars data.')
-```
-
-```{r plotTimeData}
-N <- duration[, participant_code %>% unique() %>% length()]
-plotDT <- duration[app_name == "dPGG" & page_name == "dPGG_Decision",
-                   .(time_spent = time_spent %>% sum()),
-                   by = c("session_code", "participant_code", "page_index", "page_name")]
-
-plotDT[, round := seq(from = 1, to = 10), by = c("participant_code")]
-
-upperLimit <- plotDT[, time_spent %>% mean(), by = c("round")] %>% max()
-
-tmp <- summarySE(data = plotDT,
-                 measurevar = "time_spent",
-                 groupvars=c("round"),
-                 na.rm = FALSE,
-                 conf.interval = 0.95,
-                 .drop = TRUE) %>% 
-  data.table()
-
-```
-
-Turning to the time spent on each page, I focus on the decision times in the dynamic public goods game as @Anderhub2001 did.
-How many seconds did the participants need to make a decision in each period of the game?
-Not too many.
-@fig-time-spent illustrates an intuitive pattern: The first decision took about `r tmp[round == 1, round(time_spent)]` seconds.
-The second decision--where participants first learned about the other group members' previous decisions--took longer (about `r tmp[round == 2, round(time_spent)]` seconds).
-Subsequently, decision times first declined and stabilized at `r tmp[round > 3, round(mean(time_spent))]` seconds.
-Importantly, decision times were so short that crosstalk, that is, communication through private channels--a common concern^[See, for instance, the discussion section in @AGM2018 [p.
-119].] in online experiments--was unlikely, especially because it would require the identification of other group members.^[There were only `r plotDT[page_index == 12 & time_spent > 60, .N]` participants (from all four sessions) who needed more than 60 seconds to make the second decision.]
-
-```{r plotTime}
-#| fig-cap: Average Time Spent for each Contribution per Period
-#| label: fig-time-spent
-
-ggplot(data = tmp,
-       mapping = aes(x = round, y = time_spent)) +
-  layout +
-  theme(legend.position="bottom") +
-  geom_line(show.legend=FALSE, color = cInfo, lty=2) +
-  geom_errorbar(aes(ymin=time_spent-ci, ymax=time_spent+ci), width=.25, alpha = 0.5, color = cInfo) +
-  geom_point(color = cInfo) +
-  scale_x_continuous(name="",  breaks = 1:10) +
-  scale_y_continuous(limits = c(0, upperLimit + 10), expand = c(0, 0)) +
-  labs(y = "Time Passed in Seconds", caption = "Bars indicate 95% confidence intervals.") +
-  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
-```
-
-Considering attrition, I find that it did not affect the interactive experiment at all.
-To elaborate, I differentiate between dropouts and residuals:  Participants who could not be matched to other group members are called residuals.
-Participants who intentionally left the experiment are called dropouts.
-Residuals did not participate in the experiment _by design_.
-Dropouts did not participate in the experiment _by choice_.
-Out of `r meta[, sum(showups)]` people who showed up, I count `r meta[, sum(residuals)]` residuals and `r meta[, sum(dropouts)]` dropouts.
-All of the residuals waited to be matched to a group unsuccessfully before they got paid one Euro for their patience.
-In contrast, all of the dropouts left while reading the instructions and before being matched to other group members.
-Moreover, they got no payment at all.
-Hence, attrition was no concern considering the dynamic public goods game or the expenses.
-
-**Result 2.** _Given the decision times and the fluent procedure, attrition was as negligible as it is in physical laboratories---where (a) not every invited person shows up and (b) a number of participants divisible by the group size is required as well._
-
-## Generalizability {#sec-generalizability}
-
-<!--
-> "There are two possible articles you can write: (a) the article you planned to write when you designed your study or (b) the article that makes the most sense now that you have seen the results.
-They are rarely the same, and the correct answer is (b)." [@bemwriting, p.
-171]
--->
+## Replication: @GMTV2017
+
+We also downloaded their data to run a _pure_ replication. That is, we tried to reproduce their results using their data.
+
+- Doing so, we found two errors
+    - calculating the Gini coefficient and
+    - calculating the share of endowments contributed.
+- In addition, we found a misconception as they report the endowments at the beginning of each period. Hence, the outcome of the last period is pruned.
+
+# Generalizability: @GKLS2020
+
+## Idea
+
+## Observed Behavior
 
@@
 
-@GKLS2020 asked how much can we learn about voluntary climate action from the behavior in public goods games.
-Using a similar strategy, I answer the question for _dynamic_ public goods games: _Not much_.
-Overall, there seems to be no association between choices in the voluntary climate action and the first period in the dynamic public goods game.
-@fig-scatter-generalizability shows a scatter plot of realized choices, with the percentage of endowment spent by each participant in the first period of the game on the x-axis and that spent in the VCA on the y-axis.
-In addition, the figure contains a fitted line of a linear model whose slope is indistinguishable from zero.
-No matter how much the participants contributed in the first round, they spent, on average, about `r temp[, round(mean(donationShare))]`% of their income on the VCA.
+```{r vizGeneralizability}
+#| fig-cap: Kernel distributions of contributions across tasks and subject pools.
+#| label: fig-kernel-generalizability
+#| fig.height: 6
+
+# viz wrapper
+plotShares <- function(stud = FALSE,
+                       var  = "donationShare",
+                       col  = cPrimary,
+                       xlab = "",
+                       ylab = ""){
+
+  dt <- temp[student == stud, .(x = get(var))]
+
+  model <- lm(x ~ 1, dt)
+  ci1 <- confint(model, level=0.95)[1]
+  ci2 <- confint(model, level=0.95)[2]
+
+  ggplot(data = dt,
+         mapping = aes(x = x)) +
+    annotate("rect", 
+             xmin = ci1, xmax = ci2, 
+             ymin  =0, ymax = Inf, 
+             alpha = 0.33) +
+    geom_density(alpha = 0.75,
+                 fill = col) +
+    scale_x_continuous(limits = c(0, 100),
+                       expand = c(0, NA)) +
+    scale_y_continuous(limits = c(0, NA),
+                       expand = c(0, NA)) +
+    geom_vline(xintercept = dt[,mean(x, na.rm = TRUE)],
+               lty = 2) +
+    labs(x = xlab,
+         y = ylab) +
+  layout
+}
+
+p1 <- plotShares(stud = FALSE, col = cSecondary,   var = "donationShare", ylab = "Density in VCA")
+p2 <- plotShares(stud = FALSE, col = cSecondary,   var = "contributionShare", 
+                 xlab = "Share of general pop. contributions", ylab = "Density in Experiment (round 1)")
+p3 <- plotShares(stud = TRUE,  col = cPrimary, var = "donationShare")
+p4 <- plotShares(stud = TRUE,  col = cPrimary, var = "contributionShare", xlab = "Share of students' contributions")
+
+patchwork <- (p1 / p2) | (p3 / p4)
+patchwork + plot_annotation(caption = "Dashed vertical lines indicate the respective means.\nShaded areas indicate 95% confidence intervals.")
+
+rm(list = c("R1covs", "p1", "p2", "p3", "p4", "patchwork"))
+```
+
+## Individual Behavior
 
@@
 
-Does this result hold true if one zooms in and inspects the two samples separately?
-Yes.
-Even though the general population sample is a little more consistent than the student sample, both are contributing more in the abstract game than in the VCA.
-@fig-kernel-generalizability shows distributions of contributions across both choices for both samples.
-The left panels illustrate the behavior of the general population sample.
-The right panels illustrate the behavior of the general population sample.
-The top panels show the behavior in the VCA.
-The bottom panels show the behavior in first period of the game.
-A visual inspection shows that (a) both samples behaved similarly in the first period of the game but (b) different (p =
-`r summary(lm(formula = donationShare ~ student, data = temp))$coefficients[2,4] %>% round(digits = 2)`) in the VCA.
-Furthermore, (c) the behavior in the first period of the experiment predicts the general population sample's behavior in the VCA worse than student sample's behavior (p =
-`r summary(lm(formula = contributionShare ~ donationShare + student + donationShare*student, data = temp))$coefficients[4,4] %>% round(digits = 2)`).
-Finally, (4) contributions in the abstract public good game are higher than contributions to the real public good of climate change mitigation.
-
-```{r vizGeneralizability}
-#| fig-cap: Kernel distributions of contributions across tasks and subject pools.
-#| label: fig-kernel-generalizability
-#| fig.height: 6
-
-# viz wrapper
-plotShares <- function(stud = FALSE,
-                       var  = "donationShare",
-                       col  = cPrimary,
-                       xlab = "",
-                       ylab = ""){
-
-  dt <- temp[student == stud, .(x = get(var))]
-
-  model <- lm(x ~ 1, dt)
-  ci1 <- confint(model, level=0.95)[1]
-  ci2 <- confint(model, level=0.95)[2]
-
-  ggplot(data = dt,
-         mapping = aes(x = x)) +
-    annotate("rect", 
-             xmin = ci1, xmax = ci2, 
-             ymin  =0, ymax = Inf, 
-             alpha = 0.33) +
-    geom_density(alpha = 0.75,
-                 fill = col) +
-    scale_x_continuous(limits = c(0, 100),
-                       expand = c(0, NA)) +
-    scale_y_continuous(limits = c(0, NA),
-                       expand = c(0, NA)) +
-    geom_vline(xintercept = dt[,mean(x, na.rm = TRUE)],
-               lty = 2) +
-    labs(x = xlab,
-         y = ylab) +
-  layout
-}
-
-p1 <- plotShares(stud = FALSE, col = cPrimary,   var = "donationShare", ylab = "Density in VCA")
-p2 <- plotShares(stud = FALSE, col = cPrimary,   var = "contributionShare", 
-                 xlab = "Share of general pop. contributions", ylab = "Density in Experiment (round 1)")
-p3 <- plotShares(stud = TRUE,  col = cSecondary, var = "donationShare")
-p4 <- plotShares(stud = TRUE,  col = cSecondary, var = "contributionShare", xlab = "Share of students' contributions")
-
-patchwork <- (p1 / p2) | (p3 / p4)
-patchwork + plot_annotation(caption = "Dashed vertical lines indicate the respective means.\nShaded areas indicate 95% confidence intervals.")
-
-rm(list = c("R1covs", "p1", "p2", "p3", "p4", "patchwork"))
-```
-
-**Result 3.** _Existing evidence overestimates the willingness to contribute to real public goods. This holds true for more representative samples and---to a lower degree---for student samples._
-
-# Conclusion {#sec-conclusion}
-
-The goal of the experiment was to replicate specific experiments of GMTV in an online setting using a general population sample.
-The results suggest that it is important to replicate experiments---both purely and scientifically [@Hamermesh2007 p.
-716]---before drawing conclusions about generalizability.
-
-The three most important findings are as follows: First, the contribution behavior in my experiment is statistically similar to the behavior reported in the original study.
-Consequently, the outcomes growth and inequality are similar as well.
-Second, the online experiment proceeded fluently such that dropouts were no concern.
-Third, contribution behavior in my abstract setting is, if anything, only weakly linked to behavior in the real world.
-This lack of generalizability can be counteracted, but not be solved, by the use of more representative samples.
-
-The significance of the first result is that similar procedures led to replicable findings under different circumstances across two different samples.
-The second result is of methodological importance: It highlights that even logistically complex experiments can be conducted online with---not only with clickworkers but also with a true general population sample.
-The third result questions whether recruiting from more representative samples is worth the efforts because it decreases transferability of results to the real world---at least, a little.
-
-{{< pagebreak >}}
-
-# A: Pure Replication {.appendix}
-
-This section comments on two errors as well as a misconception I found in the original data.^[The data can be found in the supplementary materials they provide in their [online appendix](https://www.sciencedirect.com/science/article/pii/S0047272717300361#s0115).] Before I proceed to explain this in more detail I would like to say that the results of the original paper still hold after the error is fixed and that the authors responded kindly and quickly, showing an interest in solving the issue.
-In fact, some explanations in this section stem from input provided by the authors.
-
-### Error 1: The Gini coefficient
-
-The Gini coefficient is wrongly computed in some periods for some group members.
-The authors found that this happened whenever two group members had exactly the same endowment because the program failed to rank these group members for further calculations.
-
-```{r readGMTVagain}
-GMTV <- read_dta(file="../../data/gaechteretal/GMTV-data.dta") %>% data.table()
-noPunish10 <- GMTV[exp_num == 5 | exp_num == 8 | exp_num == 9]
-# noPunish10 <- GMTV[longgame == 0 & punish == 0 & exp_num <= 10]
-```
-
-@tbl-gini-error illustrates this problem.
-It shows group 101 in period 5 and documents that the Gini coefficient differs among group members.
-According to the authors, the Gini coefficient should equal `GINI=``r GINI <- GMTV[exp_num == 1 & gr_id == 101 & per == 5, tokens %>% Gini() %>% round(digits = 3)]; GINI` for all subjects in the group.
-Instead, participant `112` and `113` who have an equal endowment deviate from that value.
-Importantly, the `DescTools::Gini()` function in the statistical software `R` does not yield this error, which is why I use that function for my calculations using both my as well as the original data.
-
-```{r}
-#| label: tbl-gini-error
-#| tbl-cap: Subset of Data illustrating the Gini Coefficient's Error
-
-GMTV[exp_num == 1 & gr_id == 101 & per == 5,
-     .(exp_num,
-       gr_id,
-       per,
-       subj_id,
-       tokens,
-       other1,
-       other2,
-       other3,
-       gini = round(gini, digits = 3),
-       GINI = GINI
-       )] %>% 
-  knitr::kable()
-```
-
-### Error 2: The share of endowments contributed
-
-The original data provides a wrong measure of the share of endowments contributed (`mean`) because it relies on a lagged endowment (`gdp`).
-More precisely, the authors used the following STATA code for their calculations:
-
-```
-*tsset subj_id per
-*gen mean=sum/l.gdp
-```
-
-@tbl-mean-error reports participant 111 in group 101 in experiment 1 over three periods.
-Both the `gdp` (that is, the sum of the group’s endowments at the beginning of the period) as well as the `sum` (that is, the sum of the group’s contributions) are group-level variables.
-
-```{r}
-#| label: tbl-mean-error
-#| tbl-cap: Subset of Data illustrating the Means's Error
-
-GMTV[, MEAN := sum/gdp]
-
-GMTV[exp_num == 1 & gr_id == 101 & (per == 4 | per == 5 | per == 6) & subj_id == 111,
-     .(exp_num,
-       gr_id,
-       per,
-       subj_id,
-       gdp,
-       sum,
-       mean = round(mean, digits = 3),
-       MEAN = round(MEAN, digits = 3)
-       )] %>% 
-  knitr::kable()
-```
-
-Calculating the share as `MEAN=sum/gdp` solves the problem and yields $\frac{18}{126}=0.143$ in period 5.
-I thus, used this proposed definition for all my calculations using both my as well as the original data.
-
-### The misconception: Timing
-
-The authors wrote a note stating that the Gini coefficient as well as the wealth in the paper always refer to the situation at the start of a period and that they clarify this because the paper (last paragraph at the bottom of page 5), says that wealth is defined as the endowment at the beginning of the following period.
-Furthermore, they write that this error came about as they switched between these two definitions during the course of revising the paper.
-
-I argue that it makes more sense to calculate the variables as they state in the paper.
-More precisely, I think that the wealth at the _beginning_ of a period is less interesting than the wealth at the _end_ of a period for two reasons: First, there is no need for such a variable because it already exists (the endowment).
-Second, this definition yields a value that is determined by the design of the game but misses an important outcome at the end of the game.
-To illustrate this, note that the wealth would be defined as four times the initial endowment in period 1.
-Also note that the very last value would equal the wealth at the beginning of the last period and says nothing about the outcome of that period.
-Because the contributions often drop in the last period, this outcome is of particular interest (yet, not represented in the data).
-Moreover, this definition of wealth yields more informative values to calculate the Gini coefficient for the same reasons: We know that the Gini coefficient is zero _before_ the participants made any decision by design.
-We do no know the inequality at the very end of the game---and the current definition does not tell us.
-
-For these reasons, I define wealth and inequality measures as the outcomes of a period for all of my calculations using both my as well as the original data.^[Accordingly, the definition of `GINI` I provide in @tbl-gini-error is not the definition I used to calculate the current period's Gini coefficient but the previous period's Gini coefficient.]
-
-{{< pagebreak >}}
-
-<!--
-# B: TITLE (exploratory) {.appendix}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Donec suscipit eleifend felis et faucibus.
-Curabitur nisl risus, tincidunt ut hendrerit sed, sollicitudin eget tortor.
-Curabitur tortor elit, finibus a commodo eget, auctor vel dui.
-Ut convallis, felis in commodo bibendum, ligula neque hendrerit eros, eu eleifend libero ligula pretium dui.
-Nullam blandit a tellus vitae suscipit.
-Donec ac justo vehicula elit tincidunt mollis nec ac lectus.
-Nunc dignissim sem eu felis consequat, id euismod ante imperdiet.
-Mauris quis ex ante.
-
-Nulla elementum laoreet libero nec consequat.
-Donec blandit, tellus id feugiat viverra, lectus tellus sollicitudin ipsum, ut venenatis nunc mauris ut arcu.
-Donec mi eros, ullamcorper aliquet varius non, cursus vel lorem.
-Integer feugiat dui sapien, ac porta lacus porta sit amet.
-Aliquam interdum dictum tempor.
-Quisque bibendum feugiat scelerisque.
-Sed eu purus eu est ullamcorper bibendum.
-
-Donec efficitur magna malesuada tortor feugiat tristique.
-Sed porttitor, quam at vulputate placerat, elit magna posuere est, a eleifend lacus magna ac nunc.
-Quisque sit amet arcu mattis, malesuada mauris et, aliquam libero.
-Fusce viverra sed dolor a ullamcorper.
-Aliquam in ligula neque.
-In maximus nisl id ante vehicula, et euismod ante feugiat.
-Suspendisse et dui lectus.
-Ut euismod ultrices mi eu lacinia.
-
-```{r firstRoundVizAppendix}
-
-d1 <- ggplot(data = R1[treatment == "replication"],
-       mapping = aes(x = ownContribution, fill = student, lty = student)) +
-  geom_density(alpha = 0.5) +
-  scale_x_continuous(limits = c(0, 20),
-                       expand = c(0, NA)) +
-  scale_y_continuous(limits = c(0, 0.1),
-                       expand = c(0, NA)) +
-  scale_fill_manual(values = c(cPrimary, cSecondary),
-                    labels = c("General Population Sample", "Student Sample")) +
-  guides(lty = "none") +
-  geom_vline(xintercept = R1[treatment == "replication", 
-                             mean(ownContribution)],
-             col = "#FFFFFF",
-             lty = 2) +
-  geom_vline(xintercept = R1[treatment == "noPunish10", 
-                             mean(ownContribution)],
-             col = "#FFFFFF",
-             lty = 1) +
-    labs(title = "", 
-       y = "", x = "Initially Contributed Tokens") +
-  layout +
-  theme(legend.position = "top")
-```
-
-```{r stockDistributionVizAppendix}
-
-populationWealth <- main[treatment == "replication" & student == FALSE & round == 10,
-                         mean(stock)]
-studentWealth    <- main[treatment == "replication" & student == TRUE & round == 10,
-                         mean(stock)]
-
-d2 <- ggplot(data = main[treatment == "replication"],
-       mapping = aes(x = stock, fill = student, lty = student)) +
-  geom_density(alpha = 0.5) +
-  scale_x_continuous(limits = c(0, NA),
-                       expand = c(0, NA)) +
-  scale_y_continuous(limits = c(0, NA),
-                       expand = c(0, NA)) +
-  scale_fill_manual(values = c(cPrimary, cSecondary),
-                    labels = c("General Population Sample", "Student Sample")) +
-  guides(lty = "none") +
-  geom_vline(xintercept = studentWealth,
-             col = "#000000", alpha = 0.5,
-             lty = 2) +
-  geom_vline(xintercept = populationWealth,
-             col = "#000000", alpha = 0.5,
-             lty = 1) +
-    labs(title = "", 
-       y = "", x = "Stock") +
-  layout +
-  theme(legend.position = "top")
-```
-
-```{r giniDistributionVizAppendix}
-
-populationGini    <- main[treatment == "replication" & student == FALSE & round == 10,
-                        mean(gini)] %>% round(digits = 2)
-studentGini <- main[treatment == "replication" & student == TRUE & round == 10,
-                        mean(gini)] %>% round(digits = 2)
-
-d3 <- ggplot(data = main[treatment == "replication"],
-       mapping = aes(x = gini, fill = student, lty = student)) +
-  geom_density(alpha = 0.5) +
-  scale_x_continuous(limits = c(0, 1),
-                       expand = c(0, NA)) +
-  scale_y_continuous(limits = c(0, NA),
-                       expand = c(0, NA)) +
-  scale_fill_manual(values = c(cPrimary, cSecondary),
-                    labels = c("General Population Sample", "Student Sample")) +
-  guides(lty = "none") +
-  geom_vline(xintercept = studentGini,
-             col = "#000000", alpha = 0.5,
-             lty = 2) +
-  geom_vline(xintercept = populationGini,
-             col = "#000000", alpha = 0.5,
-             lty = 1) +
-    labs(title = "", 
-       y = "", x = "Gini Coefficient") +
-  layout +
-  theme(legend.position = "top")
-```
-
-```{r assembleAppendixPlots}
-#| fig-cap: Kernel Density Plots
-#| label: fig-multiple-distributions
-
-patchwork <- d1 + d2 + d3 + plot_layout(guides = "collect") &  theme(legend.position = "top") 
-patchwork + plot_annotation(caption = "Vertical lines indicate means (dashed line = student sample).")
-```
-
-```{r plotContributionsAppendix}
-#| include: false
-
-SUM <- main[treatment == "replication",
-            lapply(.SD, mean, na.rm = TRUE),
-            by = c("round", "student"),
-            .SDcols = "contribution"]
-
-SUM[,
-    sum := round(contribution)]
-
-SUM[,
-    contribution := contribution/4]
-
-upperLimit <- SUM$contribution %>% max() %>% round() + 5
-
-p1 <- ggplot(data = SUM, 
-             aes(x = round, y = contribution, fill = student, color = student, lty = student)) +
-  layout +
-  theme(legend.position="top") +
-  geom_line(show.legend=FALSE) +
-  geom_point() +
-  scale_x_continuous(name="",  breaks = 1:15) +
-  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-  labs(y = "Average Amount of Tokens contributed") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("General Population Sample", "Student Sample")) + 
-  guides(fill = "none") +
-  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
-
-rm(list = c("SUM"))
-```
-
-```{r plotShareOfContributionsAppendix}
-#| fig.cap: "The average amount of tokens contributed over time in treatments."
-#| include: false
-
-SHARE <- main[treatment == "replication",
-            lapply(.SD, mean, na.rm = TRUE),
-            by = c("round", "student"),
-            .SDcols = "share"]
-
-# SHARE <- main[,
-#             .(share = sum(contribution)/sum(endowment)),
-#             by = c("round", "treatment")]
-
-upperLimit <- 0.75
-
-p2 <- ggplot(data = SHARE, 
-             aes(x = round, y = share, fill = student, color = student, lty = student)) +
+# Online Feasibility: @AGM2018
+
+## Idea
+
+Accept the loss of control in online experiments and make use of (para) data to better describe it. For instance,
+
+- Provide instructions in pop-up windows and measure the time they were opened.
+- Track wrong answers in comprehension questions.
+- Note that it is fairly simple to implement a chat-with-experimenter-widget.
+- Measure the time spent on each page.
+
+## Time Spent
+
+```{r plotTimeData}
+N <- duration[, participant_code %>% unique() %>% length()]
+plotDT <- duration[app_name == "dPGG" & page_name == "dPGG_Decision",
+                   .(time_spent = time_spent %>% sum()),
+                   by = c("session_code", "participant_code", "page_index", "page_name")]
+
+plotDT[, round := seq(from = 1, to = 10), by = c("participant_code")]
+
+upperLimit <- plotDT[, time_spent %>% mean(), by = c("round")] %>% max()
+
+tmp <- summarySE(data = plotDT,
+                 measurevar = "time_spent",
+                 groupvars=c("round"),
+                 na.rm = FALSE,
+                 conf.interval = 0.95,
+                 .drop = TRUE) %>% 
+  data.table()
+
+```
+
+```{r plotTime}
+#| fig-cap: Average Time Spent for each Contribution per Period
+#| label: fig-time-spent
+
+ggplot(data = tmp,
+       mapping = aes(x = round, y = time_spent)) +
   layout +
   theme(legend.position="bottom") +
-  geom_line(show.legend=FALSE) +
-  geom_point() +
-  scale_x_continuous(name="",  breaks = 1:15) +
-  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-  labs(y = "Share of Current Endowment contributed") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("General Population Sample", "Student Sample")) +
-  guides(fill = "none")
-
-p1 + p2 + plot_layout(guides = "collect") & 
-  theme(legend.position = "top")
-
-# rm(list = c("p1", "p2"))
-```
-
-```{r plotStockAppendix}
-#| include: false
-
-# data
-STOCK <- main[treatment == "replication",
-              lapply(.SD, mean, na.rm = TRUE),
-              by = c("round", "student"),
-              .SDcols = "stock"]
-
-# annotation
-maxPath <- data.table(x = 1:10)
-maxPath[, y := 80*1.5^x]
-maxPath[, student := "replication"]
-maxPath[, groupID := 42]
-
-# plot
-p1 <- ggplot(data = STOCK, 
-             aes(x = round, y = stock, fill = student, color = student, lty = student)) +
-  geom_line() +
-  geom_point() +
-  scale_x_continuous(breaks = 1:10) +
-  scale_y_continuous(limits = c(0, 4700), expand = c(0, 0)) +
-  labs(y = "Wealth", x = "Period") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("General Population Sample", "Student Sample")) +
-  geom_point(mapping = aes(x = 10, y = 4613), col = "#b5b5b5") +
-  annotate("text", x = 9, y = 4630, size = 3,
-           label = "max", col = "#b5b5b5") +
-  geom_line(data = maxPath, mapping = aes(x = x, y = y), col = "#b5b5b5", lty = 2) +
-  guides(fill = "none") +
-  layout +
-  theme(legend.position = "top") +
-  guides(lty = "none")
-```
-
-```{r growthHeterogeneityVizAppendix}
-#| fig.cap: Average wealth over time across samples.
-#| include: false
-
-# plot
-p2 <- ggplot(data = main[treatment == "replication"],
-       mapping = aes(x = round, y = stock, color = student, by = groupID)) +
-  geom_line(alpha = 0.5) +
-  scale_x_continuous(breaks = 1:10) +
-  scale_y_continuous(limits = c(0, 2000),
-                       expand = c(0, NA)) +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("General Population Sample", "Student Sample")) +
-  labs(y = "", x = "Period") +
-  layout +
-  guides(col = "none")
-
-# assembling
-p1 + p2 + plot_layout(guides = "collect") & theme(legend.position = "top")
-```
-
-```{r}
-#| fig.cap: Average Gini coefficient (within groups) over time across samples
-#| include: false
-
-tmp <- main[treatment == "replication",
-            lapply(.SD, mean, na.rm = TRUE),
-            by = c("round", "student"),
-            .SDcols = "gini"]
-
-GINI <- rbind(tmp, list(0, TRUE, 0), list(0, FALSE, 0))
-
-ggplot(data = GINI, 
-             aes(x = round, y = gini, fill = student, color = student, lty = student)) +
-  geom_line() +
-  geom_point() +
-  scale_x_continuous(breaks = 0:10) +
-  scale_y_continuous(limits = c(0, 0.25), expand = c(0, 0)) +
-  labs(y = "Wealth", x = "Period") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("General Population Sample", "Student Sample")) +
-  guides(fill = "none") +
-  layout +
-  theme(legend.position = "top") +
-  guides(lty = "none")
-```
-
-# C: Growth _and_ Inequality (exploratory) {.appendix}
-
-In contrast to GMTV, I did not ask how rich and poor groups differ.
-Instead, I was wondering, whether equal groups are wealthier.
-More precisely, does the Gini coefficient correlate with growth and wealth creation?
-To answer that question, @fig-stock-by-gini applies a median split showing equal and unequal groups' wealth over time.
-
-```{r plotStockByGini}
-#| fig-cap: Average wealth over time across treatments.
-#| label: fig-stock-by-gini
-
-# create equality indicator (just as highgdp in original data)
-median <- main[round == 10,
-               median(gini)]
-
-equalGroups <- main[round == 10 & gini > median,
-                    unique(groupID)]
-
-unequalGroups <- main[round == 10 & gini < median,
-                      unique(groupID)]
-
-main[groupID %in% equalGroups,
-     equal := TRUE]
-
-main[groupID %in% unequalGroups,
-     equal := FALSE]
-
-STOCKe <- main[equal == TRUE,
-               lapply(.SD, mean, na.rm = TRUE),
-               by = c("round", "treatment"),
-               .SDcols = "stock"]
-
-STOCKu <- main[equal == FALSE,
-               lapply(.SD, mean, na.rm = TRUE),
-               by = c("round", "treatment"),
-               .SDcols = "stock"]
-
-upperLimit <- 700
-
-p1 <- ggplot(data = STOCKe, 
-             aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
-  layout +
-  theme(legend.position="bottom") +
-  # geom_vline(xintercept = 10, alpha = 0.66) +
-  geom_line() +
-  geom_point() +
-  guides(lty = "none", fill = "none") +
+  geom_line(show.legend=FALSE, color = cInfo, lty=2) +
+  geom_errorbar(aes(ymin=time_spent-ci, ymax=time_spent+ci), width=.25, alpha = 0.5, color = cInfo) +
+  geom_point(color = cInfo) +
   scale_x_continuous(name="",  breaks = 1:10) +
-  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-  labs(y = "Wealth (Equality)", x = "Period") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("Original Sample", "Replication Sample"))
-
-p2 <- ggplot(data = STOCKu, 
-             aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
-  layout +
-  theme(legend.position="bottom") +
-  # geom_vline(xintercept = 10, alpha = 0.66) +
-  geom_line() +
-  geom_point() +
-  guides(lty = "none", fill = "none") +
-  scale_x_continuous(name="",  breaks = 1:10) +
-  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-  labs(y = "Wealth (Inequality)", x = "Period") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("Original Sample", "Replication Sample"))
-
-p1 + p2 + plot_layout(guides = "collect") & theme(legend.position = "bottom")
-
-rm(list = c("STOCKe", "STOCKu", "p1", "p2"))
-```
--->
+  scale_y_continuous(limits = c(0, upperLimit + 10), expand = c(0, 0)) +
+  labs(y = "Time Passed in Seconds", caption = "Bars indicate 95% confidence intervals.") +
+  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
+```
+
+## Handle Dropouts
+
+- Match participants into groups after they have successfully answered the comprehension questions.
+- Define a rule for participants who could not form a group (timer and patience bonus).
+- Set a reasonable time limit for decisions to keep the rest of the group engaged
+- In case of Dropouts, either define bots or let players finish the game in smaller groups.
+
+## {.smaller}
+
+```{r showMeta}
+#| label: tbl-meta
+#| tbl-cap: The Experimental Sessions' Meta Data
+
+tmp <- meta[, .(date, time, showups, dropouts, residuals, participants, observations)] 
+tmp %>% 
+  kable(col.names = names(tmp) %>%
+          str_replace_all(pattern = "\\.",
+                          replacement = " ") %>% 
+          str_to_title()) #, caption = 'A table of the first 10 rows of the mtcars data.')
+```
+
+Dropouts don't get paid and _Residuals_^[Overbooked participants.] are cheaper as in the lab.
+
+# Thank you
+
+![](img/QR.png)
+
+## References
+
+::: {#refs}
+:::
+
+```{python}
+#| eval: false
+import random
+
+TASKS = ['A', 'B', 'C']
+NUM_ROUNDS = len(TASKS)
+round_numbers = list(range(1, NUM_ROUNDS + 1))
+random.shuffle(round_numbers)
+task_rounds = dict(zip(TASKS, round_numbers))
+```

### 2023-05-19 analysis/quarto/paper.qmd
work on transpercy section

@@
 Hence, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of paths one can choose to reach certain goals.
-This apllies especially to carbon dioxide emissions where its current stock will last for well over a millennium [@Inman2008; @CalzolariEtAl2018].
+This applies especially to carbon dioxide emissions where its current stock will last for well over a millennium [@Inman2008; @CalzolariEtAl2018].
 
@@
 Taken together, this study makes three contributions.
-First, it replicates parts of GMTV's original experiment and highlights the importance of pure replications.
+First, it reproduces parts of GMTV's original experiment and highlights the importance of pure replications.
 Second, it shows that logistically complex online experiments are feasible for samples other than students or clickworkers.
@@
 Parts of the analyses were pre-registered in the American Economic Association's RCT Registry [@preregistration].
-In addition, I pre-registered the exact analyses I planned to run when I designed the experiment on [GitHub](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.].
-
-The analysis that made the most sense after having collected the data is a little different though: Because the more representative subject pool was exhausted earlier than expected, I recruited students which opened up a new research direction: assessing generalizability.
+In addition, I pre-registered the exact analyses I planned to run when I designed the experiment on [GitHub](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.]
+
+At a second glance, the analysis that made the most sense after having collected the data and that is reported here is a little different though: Because the more representative subject pool was exhausted earlier than expected, I recruited students which opened up a new research direction: assessing generalizability.
 Hence, this article combines both confirmatory as well as exploratory research.
 
-Accordingly, I  changed many of the analysis scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd] However, because the originally planned analysis code is archived and reproducible, these changes are transparent and easy to assess, showcasing (a), (b) and the transition from (a) to (b).
+Accordingly, I  changed many of the analysis scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd] However, because the originally planned analysis code is archived and reproducible, these changes are transparent.
+Importantly, I followed a literate programming approach [@Knuth_1984; @AkhtarYe_2023].
+Hence, all documents needed to analyze the data and write the report stem from the same source.
+This establishes consistence between the commands one tells the statistical software to do and the explanation one tells human beings one told the statistical software to do.
+As such, (a), (b) and the transition from (a) to (b) are not only transparent but also comprehensible.
 
@@
 [Appendix A](#A:-Pure-Replication) documents [errors I identified]() in the original paper.
-The scientific replication, where I utilize a different sample drawn from a different population in a different situation, is described in the following sections.
+The scientific reproduction, where I utilize a different sample drawn from a different population in a different situation, is described in the following sections.
 
@@
 
-## Pre-registered GMTV Replication {#sec-replication}
+## Pre-registered GMTV Reproduction {#sec-replication}
 
@@
 First, I ask whether the samples differ with respect to their initial contributions to the public good.
-Is the replication sample (consisting of both students and non-students) more pro-social than the original sample?
+Is the reproduction sample (consisting of both students and non-students) more pro-social than the original sample?
 A two-sided rank sum test reveals that it is not (p=`r rs1`).
@@
   scale_fill_manual(values = c(cPrimary, cSecondary),
-                    labels = c("Original Sample", "Replication Sample")) +
+                    labels = c("Original Sample", "Reproduction Sample")) +
   guides(lty = "none") +
@@
        y = "", x = "Initially Contributed Tokens",
-       caption = "White lines indicate means (dashed line = replication sample).") +
+       caption = "White lines indicate means (dashed line = reproduction sample).") +
   layout +
@@
 @fig-share-of-contributions illustrates that the samples make similar contributions at the beginning and the end of the game but behave differently in between.
-More precisely, the left panel--depicting the average contributions in absolute terms--shows that the original sample contributed more than the replication sample _in all but the first and last period_.^[In period five, this difference is significant: a two-sided rank sum test yields p=`r rs2`.
-] For this reason, the original sample's behavior differs from the replication sample's behavior in two aspects: it contributes more and exhibits a considerable drop in the last period (whereas the replication sample's contributions flatten).
+More precisely, the left panel--depicting the average contributions in absolute terms--shows that the original sample contributed more than the reproduction sample _in all but the first and last period_.^[In period five, this difference is significant: a two-sided rank sum test yields p=`r rs2`.
+] For this reason, the original sample's behavior differs from the reproduction sample's behavior in two aspects: it contributes more and exhibits a considerable drop in the last period (whereas the reproduction sample's contributions flatten).
 
@@
 Both samples exhibit a similar pattern: their share of endowments contributed declined and did not stabilize.
-However, both samples also differ with respect to one aspect: the replication sample's share of contributions declines faster.
+However, both samples also differ with respect to one aspect: the reproduction sample's share of contributions declines faster.
 This is mirrored by a two-sided rank sum test which is only significant at a five percent level in periods three and four.
@@
   scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("Original Sample", "Replication Sample")) + 
+                     labels = c("Original Sample", "Reproduction Sample")) + 
   guides(fill = "none") +
@@
   scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("Original Sample", "Replication Sample")) +
+                     labels = c("Original Sample", "Reproduction Sample")) +
   guides(fill = "none")
@@
 A mere mean comparison indicates just that: An average group in the original sample accumulated about `r round(originalWealth)` tokens.
-In contrast, an average group in the replication sample accumulated about `r round(replicationWealth)` tokens.
+In contrast, an average group in the reproduction sample accumulated about `r round(replicationWealth)` tokens.
 This difference is insignificant at conventional levels though: A two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean stock in last period of the game.
@@
        y = "", x = "Stock",
-       caption = "Grey lines indicate means (dashed line = replication sample).") +
+       caption = "Grey lines indicate means (dashed line = reproduction sample).") +
   layout +
@@
 Perhaps because the heterogeneity within samples and across groups has been too large to _detect_ a significant difference.
-The right panel of @fig-growth-heterogeneity depicts heterogeneity: In the replication sample, the richest group earned `r a <- main[treatment == "replication" & round == 10, max(stock)]; a` tokens (which is about `r round(a/80, digits = 2)*100`% of the initial endowment) whereas the poorest group ends up with `r b <- main[treatment == "replication" & round == 10, min(stock)]; b` tokens (`r round(b/80, digits = 2)*100`%).
-More broadly, the replication sample is characterized by inequality between groups ($SD_{Replication} =$ `r rSD`).
+The right panel of @fig-growth-heterogeneity depicts heterogeneity: In the reproduction sample, the richest group earned `r a <- main[treatment == "replication" & round == 10, max(stock)]; a` tokens (which is about `r round(a/80, digits = 2)*100`% of the initial endowment) whereas the poorest group ends up with `r b <- main[treatment == "replication" & round == 10, min(stock)]; b` tokens (`r round(b/80, digits = 2)*100`%).
+More broadly, the reproduction sample is characterized by inequality between groups ($SD_{Replication} =$ `r rSD`).
 The same holds true for the original sample ($SD_{Original} =$ `r oSD`).
-Hence, the heterogeneity across groups does not differ between samples, which is remarkable because the replication sample was drawn from a more heterogeneous (non-convenience sample).
+Hence, the heterogeneity across groups does not differ between samples, which is remarkable because the reproduction sample was drawn from a more heterogeneous (non-convenience sample).
 Does it differ within groups?
@@
   scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("Original Sample", "Replication Sample")) +
+                     labels = c("Original Sample", "Reproduction Sample")) +
   geom_point(mapping = aes(x = 10, y = 4613), col = "#b5b5b5") +
@@
   scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("Original Sample", "Replication Sample")) +
+                     labels = c("Original Sample", "Reproduction Sample")) +
   labs(y = "", x = "Period") +
@@
        y = "", x = "Gini Coefficient",
-       caption = "Grey lines indicate means (dashed line = replication sample).") +
+       caption = "Grey lines indicate means (dashed line = reproduction sample).") +
   layout +
@@
   scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("Original Sample", "Replication Sample")) +
+                     labels = c("Original Sample", "Reproduction Sample")) +
   guides(fill = "none") +
@@
 The top panels illustrate the behavior of the general population sample.
-The bottom panels illustrate the behavior of the general population sample.
+The bottom panels illustrate the behavior of the student sample.
 The left panels show the behavior in the VCA.
@@
 In addition, the figures contains a fitted line of a linear model.
-The upper pannel illustrates overall behavior and exhibits a slope which is indistinguishable from zero.
+The upper panel illustrates overall behavior and exhibits a slope which is indistinguishable from zero.
 No matter how much the participants contributed in the first round, they spent, on average, about `r temp[, round(mean(donationShare))]`% of their income on the VCA.
@@
   scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("Original Sample", "Replication Sample"))
+                     labels = c("Original Sample", "Reproduction Sample"))
 

### 2023-05-19 analysis/quarto/paper.tex
work on transpercy section

@@
 \end{keyword}
-\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, boxrule=0pt, sharp corners, frame hidden]}{\end{tcolorbox}}\fi
+\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, enhanced, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, frame hidden, sharp corners]}{\end{tcolorbox}}\fi
 
@@
 thereof) not only affect intermediate outcomes but also the number of
-paths one can choose to reach certain goals. This apllies especially to
+paths one can choose to reach certain goals. This applies especially to
 carbon dioxide emissions where its current stock will last for well over
@@
 Taken together, this study makes three contributions. First, it
-replicates parts of GMTV's original experiment and highlights the
+reproduces parts of GMTV's original experiment and highlights the
 importance of pure replications. Second, it shows that logistically
@@
   to run the code, you need to executed the .Rmd files in this
-  repository in the order that is indicated by its file names.}.
-
-The analysis that made the most sense after having collected the data is
-a little different though: Because the more representative subject pool
-was exhausted earlier than expected, I recruited students which opened
-up a new research direction: assessing generalizability. Hence, this
-article combines both confirmatory as well as exploratory research.
+  repository in the order that is indicated by its file names.}
+
+At a second glance, the analysis that made the most sense after having
+collected the data and that is reported here is a little different
+though: Because the more representative subject pool was exhausted
+earlier than expected, I recruited students which opened up a new
+research direction: assessing generalizability. Hence, this article
+combines both confirmatory as well as exploratory research.
 
@@
 However, because the originally planned analysis code is archived and
-reproducible, these changes are transparent and easy to assess,
-showcasing (a), (b) and the transition from (a) to (b).
+reproducible, these changes are transparent. Importantly, I followed a
+literate programming approach \citep{Knuth_1984, AkhtarYe_2023}. Hence,
+all documents needed to analyze the data and write the report stem from
+the same source. This establishes consistence between the commands one
+tells the statistical software to do and the explanation one tells human
+beings one told the statistical software to do. As such, (a), (b) and
+the transition from (a) to (b) are not only transparent but also
+comprehensible.
 
@@
 \href{}{errors I identified} in the original paper. The scientific
-replication, where I utilize a different sample drawn from a different
+reproduction, where I utilize a different sample drawn from a different
 population in a different situation, is described in the following
@@
 \hypertarget{sec-replication}{%
-\subsection{Pre-registered GMTV Replication}\label{sec-replication}}
+\subsection{Pre-registered GMTV Reproduction}\label{sec-replication}}
 
@@
 First, I ask whether the samples differ with respect to their initial
-contributions to the public good. Is the replication sample (consisting
+contributions to the public good. Is the reproduction sample (consisting
 of both students and non-students) more pro-social than the original
@@
 the average contributions in absolute terms--shows that the original
-sample contributed more than the replication sample \emph{in all but the
-first and last period}.\footnote{In period five, this difference is
+sample contributed more than the reproduction sample \emph{in all but
+the first and last period}.\footnote{In period five, this difference is
   significant: a two-sided rank sum test yields p=0.0486.} For this
-reason, the original sample's behavior differs from the replication
+reason, the original sample's behavior differs from the reproduction
 sample's behavior in two aspects: it contributes more and exhibits a
-considerable drop in the last period (whereas the replication sample's
+considerable drop in the last period (whereas the reproduction sample's
 contributions flatten).
@@
 stabilize. However, both samples also differ with respect to one aspect:
-the replication sample's share of contributions declines faster. This is
-mirrored by a two-sided rank sum test which is only significant at a
+the reproduction sample's share of contributions declines faster. This
+is mirrored by a two-sided rank sum test which is only significant at a
 five percent level in periods three and four.
@@
 average group in the original sample accumulated about 478 tokens. In
-contrast, an average group in the replication sample accumulated about
+contrast, an average group in the reproduction sample accumulated about
 380 tokens. This difference is insignificant at conventional levels
@@
 panel of Figure~\ref{fig-growth-heterogeneity} depicts heterogeneity: In
-the replication sample, the richest group earned 1425 tokens (which is
+the reproduction sample, the richest group earned 1425 tokens (which is
 about 1781\% of the initial endowment) whereas the poorest group ends up
-with 92 tokens (115\%). More broadly, the replication sample is
+with 92 tokens (115\%). More broadly, the reproduction sample is
 characterized by inequality between groups (\(SD_{Replication} =\)
@@
 does not differ between samples, which is remarkable because the
-replication sample was drawn from a more heterogeneous (non-convenience
+reproduction sample was drawn from a more heterogeneous (non-convenience
 sample). Does it differ within groups?
@@
 illustrate the behavior of the general population sample. The bottom
-panels illustrate the behavior of the general population sample. The
-left panels show the behavior in the VCA. The right panels show the
-behavior in first period of the game. A visual inspection shows that (a)
-mean contributions are positive in both tasks for both
-samples.\footnote{The same holds true for median contributions.} (b)
-Furthermore, average contributions are lower in the VCA. (c) In contrast
-to \citet{GKLS2020}'s observation, we do not observe a difference
-between samples in the abstract game's contribution behavior. (d)
-However, the student's share of income contributed to the VCA is
-significantly lower than the general population sample's contributions
-(two-sided rank sum test, p=0.0085). Taken together, these aggregate
-results indicate, that the consistency between tasks is higher for the
-general population than it is for students. Or, to put it differently,
-the general population's behavior in the abstract game better predicts
-their behavior in real-world mitigation context.
+panels illustrate the behavior of the student sample. The left panels
+show the behavior in the VCA. The right panels show the behavior in
+first period of the game. A visual inspection shows that (a) mean
+contributions are positive in both tasks for both samples.\footnote{The
+  same holds true for median contributions.} (b) Furthermore, average
+contributions are lower in the VCA. (c) In contrast to
+\citet{GKLS2020}'s observation, we do not observe a difference between
+samples in the abstract game's contribution behavior. (d) However, the
+student's share of income contributed to the VCA is significantly lower
+than the general population sample's contributions (two-sided rank sum
+test, p=0.0085). Taken together, these aggregate results indicate, that
+the consistency between tasks is higher for the general population than
+it is for students. Or, to put it differently, the general population's
+behavior in the abstract game better predicts their behavior in
+real-world mitigation context.
 

### 2023-05-19 analysis/quarto/paper.qmd
work on introduction

@@
 This yielded a setting similar to @GKLS2020's which allows me to analyze how behavior in the abstract game translates into real-world action across samples.
+The article shows that the dynamic setting _does not_ add any advances with respect to generalizability of results.
 
@@
 @AGM2018 conducted public good games in the lab and on MTurk to draw lessons from online experimentation.
-This study extends this literature [see also @GoodmanPaolacci2017  @AmirEtAl2012] by focusing on a completely inexperienced sample that has not been exposed to interactive experiments before.
+This study extends this literature [see also @GoodmanPaolacci2017  @AmirEtAl2012] by focusing on an inconvenient sample: one that is completely inexperienced sample that has not been exposed to interactive experiments before.
 This required me to design a robust (and thus, more complex) software to minimize attrition.
@@
 Third, this paper supports critics arguing that findings from abstract games do not generalize well---not even with a more representative sample.
-After reporting the methods, this paper is organized along these findings.
-
-# Transparency
+
+After commenting on transparent research practices and reporting the methods in @sec-transparency and @sec-methods, this paper is organized along these findings: The confirmatory reproduction is reported in @sec-replication, the online feasibility in @sec-feasibility and the generalizability in @sec-generalizability.
+@sec-conclusion concludes.
+
+# Transparency {#sec-transparency}
 
@@
 Importantly, I followed a literate programming approach [@Knuth_1984; @AkhtarYe_2023].
-Hence, all documents needed to analyze the data and write the report stem from the same source.
+Hence, all documents needed to analyze the data and to write the report stem from the same source.
 This establishes consistence between the commands one tells the statistical software to do and the explanation one tells human beings one told the statistical software to do.
@@
 
+Limitations?
+
 {{< pagebreak >}}

### 2023-05-19 analysis/quarto/paper.tex
work on introduction

@@
 \end{keyword}
-\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, enhanced, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, frame hidden, sharp corners]}{\end{tcolorbox}}\fi
+\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, sharp corners, borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi
 
@@
 similar to \citet{GKLS2020}'s which allows me to analyze how behavior in
-the abstract game translates into real-world action across samples.
+the abstract game translates into real-world action across samples. The
+article shows that the dynamic setting \emph{does not} add any advances
+with respect to generalizability of results.
 
@@
 literature \citep[see also][ \citet{AmirEtAl2012}]{GoodmanPaolacci2017}
-by focusing on a completely inexperienced sample that has not been
-exposed to interactive experiments before. This required me to design a
-robust (and thus, more complex) software to minimize attrition. In
-exchange, the online setting allowed me to also collect paradata to
-assess the fluency and feasibility of the experiment. This article
-reports on both topics: the robust design as well as the feasibility.
+by focusing on an inconvenient sample: one that is completely
+inexperienced sample that has not been exposed to interactive
+experiments before. This required me to design a robust (and thus, more
+complex) software to minimize attrition. In exchange, the online setting
+allowed me to also collect paradata to assess the fluency and
+feasibility of the experiment. This article reports on both topics: the
+robust design as well as the feasibility.
 
@@
 findings from abstract games do not generalize well---not even with a
-more representative sample. After reporting the methods, this paper is
-organized along these findings.
-
-\hypertarget{transparency}{%
-\section{Transparency}\label{transparency}}
+more representative sample.
+
+After commenting on transparent research practices and reporting the
+methods in Section~\ref{sec-transparency} and Section~\ref{sec-methods},
+this paper is organized along these findings: The confirmatory
+reproduction is reported in Section~\ref{sec-replication}, the online
+feasibility in Section~\ref{sec-feasibility} and the generalizability in
+Section~\ref{sec-generalizability}. Section~\ref{sec-conclusion}
+concludes.
+
+\hypertarget{sec-transparency}{%
+\section{Transparency}\label{sec-transparency}}
 
@@
 literate programming approach \citep{Knuth_1984, AkhtarYe_2023}. Hence,
-all documents needed to analyze the data and write the report stem from
-the same source. This establishes consistence between the commands one
-tells the statistical software to do and the explanation one tells human
-beings one told the statistical software to do. As such, (a), (b) and
-the transition from (a) to (b) are not only transparent but also
+all documents needed to analyze the data and to write the report stem
+from the same source. This establishes consistence between the commands
+one tells the statistical software to do and the explanation one tells
+human beings one told the statistical software to do. As such, (a), (b)
+and the transition from (a) to (b) are not only transparent but also
 comprehensible.
@@
 
+Limitations?
+
 \newpage{}

### 2023-05-22 analysis/quarto/paper.qmd
add sample sizes to results sections

@@
 
+```{r}
+N_r <- R1[treatment == "replication", .N]
+N_o <- R1[treatment == "noPunish10", .N]
+```
+
+Throughout this section, I pool data from both the citizens as well as the students from Hamburg and compare it with the students GMTV recruited in Nottingham.
+I refer to the two samples as the _reproduction sample_ ($N_r$ = `r N_r`) and the _original sample_ ($N_o$ = `r N_o`), respectively.
+
 ### Contribution Behavior {#sec-contributions}
@@
 Given the different samples and the possibility of endogenous growth--which essentially is the main feature of the game--I ask whether and how the inequality grows _within_ groups.
-@fig-gini-time-series illustrates that inequality did grow: at the end of the game, the original and the replication groups exhibit an average Gini coefficient of `r originalGini` and `r replicationGini`, respectively.^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean Gini coefficient in last round of the game.] Because every participant started with the same initial endowment (in _Period 0_, so to speak), every group started equally--with a Gini coefficient equaling zero.
+@fig-gini-time-series illustrates that inequality did grow: at the end of the game, the original and the replication groups exhibit an average Gini coefficient of `r originalGini` and `r replicationGini`, respectively.^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean Gini coefficient in last round of the game.] Because every participant started with the same initial endowment (in _period 0_, so to speak), every group started equally--with a Gini coefficient equaling zero.
 
@@
 
+```{r}
+N <- duration[, participant_code %>% unique() %>% length()]
+```
+
+Throughout this section, I do not consider GMTV's data and pool data I gathered from the citizens as well as the students from Hamburg (N = `r N`).
+
 ```{r reviewInformation}
@@
 
-<!--
-> "There are two possible articles you can write: (a) the article you planned to write when you designed your study or (b) the article that makes the most sense now that you have seen the results.
-They are rarely the same, and the correct answer is (b)." [@bemwriting, p.
-171]
--->
-
 ```{r generalizability_prep}
@@
 temp[, consistency := 1 - (contributionShare - donationShare)]
-```
+
+N_s <- temp[student == TRUE, .N]
+N_g <- temp[student == FALSE, .N]
+```
+
+As before, I do not consider GMTVs' data in this section.
+Instead, I will differentiate between data from the citizens and the students from Hamburg.
+I refer to the two samples as the _students_ ($N_s$ = `r N_s`) and the _general population sample_ ($N_g$ = `r N_g`), respectively.
 

### 2023-05-22 analysis/quarto/paper.tex
add sample sizes to results sections

@@
 \end{keyword}
-\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, sharp corners, borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi
+\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, boxrule=0pt, frame hidden, enhanced, interior hidden, breakable, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
 
@@
 
+Throughout this section, I pool data from both the citizens as well as
+the students from Hamburg and compare it with the students GMTV
+recruited in Nottingham. I refer to the two samples as the
+\emph{reproduction sample} (\(N_r\) = 116) and the \emph{original
+sample} (\(N_o\) = 92), respectively.
+
 \hypertarget{sec-contributions}{%
@@
   game.} Because every participant started with the same initial
-endowment (in \emph{Period 0}, so to speak), every group started
+endowment (in \emph{period 0}, so to speak), every group started
 equally--with a Gini coefficient equaling zero.
@@
 \subsection{Online Feasibility}\label{sec-feasibility}}
+
+Throughout this section, I do not consider GMTV's data and pool data I
+gathered from the citizens as well as the students from Hamburg (N =
+151).
 
@@
 \subsection{Generalizability}\label{sec-generalizability}}
+
+As before, I do not consider GMTVs' data in this section. Instead, I
+will differentiate between data from the citizens and the students from
+Hamburg. I refer to the two samples as the \emph{students} (\(N_s\) =
+64) and the \emph{general population sample} (\(N_g\) = 52),
+respectively.
 

### 2023-05-22 analysis/quarto/paper.qmd
rewrite intro & positioning

@@
 (2017) developed to study cooperation under dynamic interdependencies.
-Collecting data from both students and a general population sample, I not only reproduce some of the author's original observations but also test the game's generalizability.
-Appending a charitable dictator game, I find no correlations between behavior in the abstract game and the charitable context.
+Collecting data from both a convenient (students) and an inconvenient (general population) sample, I not only reproduce some of the author's original observations but also test their novel game's generalizability.
+Appending a charitable dictator game, I find no correlations between behavior in the charitable context and the dynamic game.
 This applies to students and the general population sample alike.
-Studying inexperiend general population samples raises methodological challenges with respect to fatigue and dropouts.
-This paper approaches them and provides simple solutions to run relieable interactive experiments online.
+Because the study of inexperiend general population samples raises methodological challenges, such as fatigue and dropouts, this research approaches them.
+Doing so, I and provide simple solutions to run relieable interactive experiments online.
 
@@
 Opting for environmental friendly policies today not only reduces carbon dioxide omissions immediately but also helps us to reach the Paris climate targets tomorrow.
-Deferring these policies, may not necessarily prevent us from reaching these targets, but it makes it more difficult in the future.
-Hence, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of paths one can choose to reach certain goals.
-This applies especially to carbon dioxide emissions where its current stock will last for well over a millennium [@Inman2008; @CalzolariEtAl2018].
-
-Public good games---although often intended to inform climate policies (e.g.
+Deferring these policies, may not necessarily prevent us from reaching these targets, but it requires more effort in the future compared to a path that includes immediate action.
+Aiming at certain goals, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of paths one can choose from that lead to that specific goal.
+
+Public good (or public bad) games---although often intended to inform climate policies (e.g.
 @MilinskiEtAl2006, @TavoniEtAl2011, @Hauser2014, @BrickEtAl2015, @GomezEtAl2018, @CalzolariEtAl2018, @CookEtAl2019)---miss these temporal interdependencies simply because participants have the same set of actions in each period.
 Accordingly, participants' actions in a given period do not affect their number of actions in subsequent periods.
-A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017] (hereafter, GMTV) as well as Stefan Große (2011, unpublished) incorporated interdependencies into a _dynamic_ public good game.
-Here, participants' actions in a given period affect their number of actions in subsequent periods.
-Because there is surprisingly little experimental research on these interdependencies^[One exemption are @Moser2019, who built on GMTV's design to investigate leadership.], I reproduced one of their treatments to compare dynamics across samples.
-
-@GKLS2020 find that standard public good games do not generalize well to real-world climate action.
-They also find that generalizability depends on structural resemblance of the public goods game with the context of climate change mitigation.
-Greater resemblance improves generalizability.
-Because GMTV's dynamic setting has a more realistic property—namely, interdependencies—one wonders whether it is better suited to inform public policy.
-To approach this question, I ran the experiment with different samples^[GMTV ran their experiments with students in Nottingham, England.] and
+To see the lack of realism, consider carbon dioxide emissions, where the current stock will last for well over a millennium [@Inman2008; @CalzolariEtAl2018].
+Playing with fresh endowments in each period is as if one could just undo carbon dioxide emissions at no cost.
+
+A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017 hereafter, GMTV] as well as Stefan Große (2011, unpublished) shows that it is fairly simple to remedy that flaw.
+They incorporated interdependencies into a _dynamic_ public good game by defining endowments as the income of previous periods.
+To put it differently, participants' actions in a given period affect their number of actions in subsequent periods: the more (less) they earn now, the more (less) they can contribute in the next period.
+Importantly, this modification qualitatively yields the same rational predictions as the static game (i.e.
+free-riding and the under-provision of the public good).
+It is thus, equally well suited to study dilemma situations.
+
+Because there is surprisingly little experimental research on interdependencies^[One exemption are @Moser2019, who built on GMTV's design to investigate leadership.], I reproduced one of GMTV's treatments to compare dynamics across (in)experienced samples to investigate its generalizability.
+@GKLS2020 find that static public good games do not generalize well to real-world climate action.
+They also find that generalizability depends on structural resemblance of the public goods game with the context of climate change mitigation: Greater resemblance improves generalizability.
+Because GMTV's dynamic setting has a more realistic property—namely, interdependencies—one would expect it to be better suited to inform public policy.
+To test this intuition, I not only ran the experiment with different samples but also
 <!--, that is, with participants who make their decisions in an environment which is more natural than the lab.-->
-observed the participants' behavior in voluntary climate actions (VCA).
-This yielded a setting similar to @GKLS2020's which allows me to analyze how behavior in the abstract game translates into real-world action across samples.
-The article shows that the dynamic setting _does not_ add any advances with respect to generalizability of results.
-
-The VCA is a (charitable) dictator games where each participant is a dictator dividing her budget between herself and some organization linked to the reduction of CO2 emissions.
+observed the participants' behavior in voluntary climate actions (VCA).^[The VCA is a (charitable) dictator games where each participant is a dictator dividing her budget between herself and some organization linked to the reduction of CO2 emissions.
 @EckelGrossman1996 were the first to implement a charitable dictator game observing contributions of 30% of the endowments.
-Like @GKLS2020, @CarpenterEtAl2008 report that students make lower contributions to charity than community members.
-
-@AGM2018 conducted public good games in the lab and on MTurk to draw lessons from online experimentation.
-This study extends this literature [see also @GoodmanPaolacci2017  @AmirEtAl2012] by focusing on an inconvenient sample: one that is completely inexperienced sample that has not been exposed to interactive experiments before.
+Like @GKLS2020, @CarpenterEtAl2008 report that students make lower contributions to charity than community members.] This yielded a setting similar to @GKLS2020's which allows me to analyze how behavior in the abstract game translates into real-world action across samples.
+This research shows that the dynamic setting _does not_ add any advances with respect to generalizability of results.
+
+@AGM2018 conducted static public good games in the lab and on MTurk to draw lessons from online experimentation.
+This study extends this literature [see also @GoodmanPaolacci2017  @AmirEtAl2012] by focusing on an _inconvenient_ sample (i.e.
+one that is completely inexperienced sample that has not been exposed to interactive experiments before) playing a computationally more complex game.
 This required me to design a robust (and thus, more complex) software to minimize attrition.
-In exchange, the online setting allowed me to also collect paradata to assess the fluency and feasibility of the experiment.
-This article reports on both topics: the robust design as well as the feasibility.
+I collected paradata to assess the desired fluency and feasibility of the experiment.
+This research reports on the robust design that made the dynamic game feasible.
 
@@
 Now, 20 years later, we accustom ourselves with mechanisms designed to unravel the fuzzy back-and-forth between exploratory and confirmatory research.
-Prominently, pre-registrations were established to tie the researchers' hands when doing confirmatory research--reducing observable discrepancies between (a) and (b).
+Prominently, pre-registrations were established to tie the researchers' hands when doing confirmatory research--reducing observable discrepancies between Daryl Bem's above-mentioned (a) and (b).
 Today, researchers can not only choose where to pre-register but also decide about the level of detail they provide.
@@
 
-@WaldronAllen2022 report a wide variety of depth of pre-registrations in the field of Neuropsychopharmacology and document that the label _'pre-registration'_ can be obtained with minimal effort.
+@WaldronAllen2022 report a wide variety of depth of pre-registrations in the field of Neuropsychopharmacology and document that the _'pre-registered'_ label can be obtained with minimal effort.
 In absence of transparency and scrutiny pre-registrations run into danger to miss the target of making science more credible.
-Even more so, they may have adverse effects as the label _'pre-registered'_ becomes cheap (too) to acquire.
+Even more so, they may have adverse effects as the _'pre-registered'_ label becomes cheap (too) to acquire.
 
@@
 
-In fact, the experiment reported in this article qualifies for the label _'pre-registered'_ at a first glance:
-Parts of the analyses were pre-registered in the American Economic Association's RCT Registry [@preregistration].
-In addition, I pre-registered the exact analyses I planned to run when I designed the experiment on [GitHub](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.]
+In fact, the experiment reported in this article qualifies for the _'pre-registered'_ label at a first glance:
+The analysis was pre-registered in the American Economic Association's RCT Registry [@preregistration].
+Further, I pre-registered the exact analyses I planned to run when I designed the experiment on [GitHub](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.]
 
@@
 
-Considering the design, the only differences between such a _static_ game and GMTV's design are _dynamics_: Instead of receiving fresh endowments every period, participants receive one endowment only at the beginning of the first period.
+Considering the design, the only differences between such a _static_ game (with partner matching) and GMTV's design are _dynamics_: Instead of receiving fresh endowments every period, participants receive one endowment only at the beginning of the first period.
 A participant's endowment in the second period is the wealth she accumulated in the first period.

### 2023-05-22 analysis/quarto/paper.tex
rewrite intro & positioning

@@
 developed to study cooperation under dynamic interdependencies.
-Collecting data from both students and a general population sample, I
-not only reproduce some of the author's original observations but also
-test the game's generalizability. Appending a charitable dictator game,
-I find no correlations between behavior in the abstract game and the
-charitable context. This applies to students and the general population
-sample alike. Studying inexperiend general population samples raises
-methodological challenges with respect to fatigue and dropouts. This
-paper approaches them and provides simple solutions to run relieable
-interactive experiments online.
+Collecting data from both a convenient (students) and an inconvenient
+(general population) sample, I not only reproduce some of the author's
+original observations but also test their novel game's generalizability.
+Appending a charitable dictator game, I find no correlations between
+behavior in the charitable context and the dynamic game. This applies to
+students and the general population sample alike. Because the study of
+inexperiend general population samples raises methodological challenges,
+such as fatigue and dropouts, this research approaches them. Doing so, I
+and provide simple solutions to run relieable interactive experiments
+online.
 
@@
 \end{keyword}
-\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, boxrule=0pt, frame hidden, enhanced, interior hidden, breakable, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
+\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, frame hidden, boxrule=0pt, breakable, enhanced, sharp corners]}{\end{tcolorbox}}\fi
 
@@
 the Paris climate targets tomorrow. Deferring these policies, may not
-necessarily prevent us from reaching these targets, but it makes it more
-difficult in the future. Hence, today's actions (or the omission
-thereof) not only affect intermediate outcomes but also the number of
-paths one can choose to reach certain goals. This applies especially to
-carbon dioxide emissions where its current stock will last for well over
-a millennium \citep{Inman2008, CalzolariEtAl2018}.
-
-Public good games---although often intended to inform climate policies
-(e.g. \citet{MilinskiEtAl2006}, \citet{TavoniEtAl2011},
+necessarily prevent us from reaching these targets, but it requires more
+effort in the future compared to a path that includes immediate action.
+Aiming at certain goals, today's actions (or the omission thereof) not
+only affect intermediate outcomes but also the number of paths one can
+choose from that lead to that specific goal.
+
+Public good (or public bad) games---although often intended to inform
+climate policies (e.g. \citet{MilinskiEtAl2006}, \citet{TavoniEtAl2011},
 \citet{Hauser2014}, \citet{BrickEtAl2015}, \citet{GomezEtAl2018},
@@
 actions in each period. Accordingly, participants' actions in a given
-period do not affect their number of actions in subsequent periods. A
-game designed by Gächter, Mengel, Tsakas \& Vostroknutov
-\citeyearpar{GMTV2017} (hereafter, GMTV) as well as Stefan Große (2011,
-unpublished) incorporated interdependencies into a \emph{dynamic} public
-good game. Here, participants' actions in a given period affect their
-number of actions in subsequent periods. Because there is surprisingly
-little experimental research on these interdependencies\footnote{One
-  exemption are \citet{Moser2019}, who built on GMTV's design to
-  investigate leadership.}, I reproduced one of their treatments to
-compare dynamics across samples.
-
-\citet{GKLS2020} find that standard public good games do not generalize
-well to real-world climate action. They also find that generalizability
-depends on structural resemblance of the public goods game with the
-context of climate change mitigation. Greater resemblance improves
-generalizability. Because GMTV's dynamic setting has a more realistic
-property---namely, interdependencies---one wonders whether it is better
-suited to inform public policy. To approach this question, I ran the
-experiment with different samples\footnote{GMTV ran their experiments
-  with students in Nottingham, England.} and observed the participants'
-behavior in voluntary climate actions (VCA). This yielded a setting
-similar to \citet{GKLS2020}'s which allows me to analyze how behavior in
-the abstract game translates into real-world action across samples. The
-article shows that the dynamic setting \emph{does not} add any advances
-with respect to generalizability of results.
-
-The VCA is a (charitable) dictator games where each participant is a
-dictator dividing her budget between herself and some organization
-linked to the reduction of CO2 emissions. \citet{EckelGrossman1996} were
-the first to implement a charitable dictator game observing
-contributions of 30\% of the endowments. Like \citet{GKLS2020},
-\citet{CarpenterEtAl2008} report that students make lower contributions
-to charity than community members.
-
-\citet{AGM2018} conducted public good games in the lab and on MTurk to
-draw lessons from online experimentation. This study extends this
-literature \citep[see also][ \citet{AmirEtAl2012}]{GoodmanPaolacci2017}
-by focusing on an inconvenient sample: one that is completely
-inexperienced sample that has not been exposed to interactive
-experiments before. This required me to design a robust (and thus, more
-complex) software to minimize attrition. In exchange, the online setting
-allowed me to also collect paradata to assess the fluency and
-feasibility of the experiment. This article reports on both topics: the
-robust design as well as the feasibility.
+period do not affect their number of actions in subsequent periods. To
+see the lack of realism, consider carbon dioxide emissions, where the
+current stock will last for well over a millennium
+\citep{Inman2008, CalzolariEtAl2018}. Playing with fresh endowments in
+each period is as if one could just undo carbon dioxide emissions at no
+cost.
+
+A game designed by Gächter, Mengel, Tsakas \& Vostroknutov \citeyearpar[
+hereafter, GMTV]{GMTV2017} as well as Stefan Große (2011, unpublished)
+shows that it is fairly simple to remedy that flaw. They incorporated
+interdependencies into a \emph{dynamic} public good game by defining
+endowments as the income of previous periods. To put it differently,
+participants' actions in a given period affect their number of actions
+in subsequent periods: the more (less) they earn now, the more (less)
+they can contribute in the next period. Importantly, this modification
+qualitatively yields the same rational predictions as the static game
+(i.e.~free-riding and the under-provision of the public good). It is
+thus, equally well suited to study dilemma situations.
+
+Because there is surprisingly little experimental research on
+interdependencies\footnote{One exemption are \citet{Moser2019}, who
+  built on GMTV's design to investigate leadership.}, I reproduced one
+of GMTV's treatments to compare dynamics across (in)experienced samples
+to investigate its generalizability. \citet{GKLS2020} find that static
+public good games do not generalize well to real-world climate action.
+They also find that generalizability depends on structural resemblance
+of the public goods game with the context of climate change mitigation:
+Greater resemblance improves generalizability. Because GMTV's dynamic
+setting has a more realistic property---namely, interdependencies---one
+would expect it to be better suited to inform public policy. To test
+this intuition, I not only ran the experiment with different samples but
+also observed the participants' behavior in voluntary climate actions
+(VCA).\footnote{The VCA is a (charitable) dictator games where each
+  participant is a dictator dividing her budget between herself and some
+  organization linked to the reduction of CO2 emissions.
+  \citet{EckelGrossman1996} were the first to implement a charitable
+  dictator game observing contributions of 30\% of the endowments. Like
+  \citet{GKLS2020}, \citet{CarpenterEtAl2008} report that students make
+  lower contributions to charity than community members.} This yielded a
+setting similar to \citet{GKLS2020}'s which allows me to analyze how
+behavior in the abstract game translates into real-world action across
+samples. This research shows that the dynamic setting \emph{does not}
+add any advances with respect to generalizability of results.
+
+\citet{AGM2018} conducted static public good games in the lab and on
+MTurk to draw lessons from online experimentation. This study extends
+this literature \citep[see also][
+\citet{AmirEtAl2012}]{GoodmanPaolacci2017} by focusing on an
+\emph{inconvenient} sample (i.e.~one that is completely inexperienced
+sample that has not been exposed to interactive experiments before)
+playing a computationally more complex game. This required me to design
+a robust (and thus, more complex) software to minimize attrition. I
+collected paradata to assess the desired fluency and feasibility of the
+experiment. This research reports on the robust design that made the
+dynamic game feasible.
 
@@
 researchers' hands when doing confirmatory research--reducing observable
-discrepancies between (a) and (b). Today, researchers can not only
-choose where to pre-register but also decide about the level of detail
-they provide. More severely, nothing stops researchers from
-pre-registering multiple hypotheses opposing each other (see e.g.
-\citet{SimmonsEtAl2021} and \citet{PhamEtAl2021} for a discussion).
+discrepancies between Daryl Bem's above-mentioned (a) and (b). Today,
+researchers can not only choose where to pre-register but also decide
+about the level of detail they provide. More severely, nothing stops
+researchers from pre-registering multiple hypotheses opposing each other
+(see e.g. \citet{SimmonsEtAl2021} and \citet{PhamEtAl2021} for a
+discussion).
 
@@
 pre-registrations in the field of Neuropsychopharmacology and document
-that the label \emph{`pre-registration'} can be obtained with minimal
+that the \emph{`pre-registered'} label can be obtained with minimal
 effort. In absence of transparency and scrutiny pre-registrations run
 into danger to miss the target of making science more credible. Even
-more so, they may have adverse effects as the label
-\emph{`pre-registered'} becomes cheap (too) to acquire.
+more so, they may have adverse effects as the \emph{`pre-registered'}
+label becomes cheap (too) to acquire.
 
@@
 
-In fact, the experiment reported in this article qualifies for the label
-\emph{`pre-registered'} at a first glance: Parts of the analyses were
+In fact, the experiment reported in this article qualifies for the
+\emph{`pre-registered'} label at a first glance: The analysis was
 pre-registered in the American Economic Association's RCT Registry
-\citep{preregistration}. In addition, I pre-registered the exact
-analyses I planned to run when I designed the experiment on
+\citep{preregistration}. Further, I pre-registered the exact analyses I
+planned to run when I designed the experiment on
 \href{https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd}{GitHub}.\footnote{https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd
@@
 Considering the design, the only differences between such a
-\emph{static} game and GMTV's design are \emph{dynamics}: Instead of
-receiving fresh endowments every period, participants receive one
-endowment only at the beginning of the first period. A participant's
-endowment in the second period is the wealth she accumulated in the
-first period. A participant's endowment in the third period is the
-wealth she accumulated in the first two periods. And so on. Hence, a
-decision in one period has consequences on future endowments and,
-ultimately, growth paths. For this reason, the game is described as a
-\emph{dynamic} public good game.
+\emph{static} game (with partner matching) and GMTV's design are
+\emph{dynamics}: Instead of receiving fresh endowments every period,
+participants receive one endowment only at the beginning of the first
+period. A participant's endowment in the second period is the wealth she
+accumulated in the first period. A participant's endowment in the third
+period is the wealth she accumulated in the first two periods. And so
+on. Hence, a decision in one period has consequences on future
+endowments and, ultimately, growth paths. For this reason, the game is
+described as a \emph{dynamic} public good game.
 

### 2023-05-24 analysis/quarto/paper.qmd
incorporate comments on citation, style and punctuation

@@
 abstract: |
-  I revisit the dynamic public good game by Gächter et al.
+  I revisit the dynamic public goods game by Gächter et al.
 (2017) developed to study cooperation under dynamic interdependencies.
@@
 Because the study of inexperiend general population samples raises methodological challenges, such as fatigue and dropouts, this research approaches them.
-Doing so, I and provide simple solutions to run relieable interactive experiments online.
+Doing so, I provide simple solutions to run relieable interactive experiments online.
 
@@
   - Open science
-  - Dynamic public good game
+  - Dynamic public goods game
   - Online experiment
@@
 @MilinskiEtAl2006, @TavoniEtAl2011, @Hauser2014, @BrickEtAl2015, @GomezEtAl2018, @CalzolariEtAl2018, @CookEtAl2019)---miss these temporal interdependencies simply because participants have the same set of actions in each period.
-Accordingly, participants' actions in a given period do not affect their number of actions in subsequent periods.
+Accordingly, participants' actions in a given period do not affect their action space in subsequent periods.
 To see the lack of realism, consider carbon dioxide emissions, where the current stock will last for well over a millennium [@Inman2008; @CalzolariEtAl2018].
@@
 
-A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017 hereafter, GMTV] as well as Stefan Große (2011, unpublished) shows that it is fairly simple to remedy that flaw.
-They incorporated interdependencies into a _dynamic_ public good game by defining endowments as the income of previous periods.
+A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017 hereafter, GMTV] as well as Stefan Große (2011, unpublished) shows that it is fairly simple to remedy that limitation.
+They incorporated interdependencies into a _dynamic_ public goods game by defining endowments as the income of previous periods.
 To put it differently, participants' actions in a given period affect their number of actions in subsequent periods: the more (less) they earn now, the more (less) they can contribute in the next period.
@@
 Because there is surprisingly little experimental research on interdependencies^[One exemption are @Moser2019, who built on GMTV's design to investigate leadership.], I reproduced one of GMTV's treatments to compare dynamics across (in)experienced samples to investigate its generalizability.
-@GKLS2020 find that static public good games do not generalize well to real-world climate action.
+@GKLS2020 find that static public goods games do not generalize well to real-world climate action.
 They also find that generalizability depends on structural resemblance of the public goods game with the context of climate change mitigation: Greater resemblance improves generalizability.
@@
 <!--, that is, with participants who make their decisions in an environment which is more natural than the lab.-->
-observed the participants' behavior in voluntary climate actions (VCA).^[The VCA is a (charitable) dictator games where each participant is a dictator dividing her budget between herself and some organization linked to the reduction of CO2 emissions.
+observed the participants' behavior in voluntary climate actions (VCA).^[The VCA is a (charitable) dictator game where each participant is a dictator dividing her budget between herself and some organization linked to the reduction of CO2 emissions.
 @EckelGrossman1996 were the first to implement a charitable dictator game observing contributions of 30% of the endowments.
@@
 
-@AGM2018 conducted static public good games in the lab and on MTurk to draw lessons from online experimentation.
-This study extends this literature [see also @GoodmanPaolacci2017  @AmirEtAl2012] by focusing on an _inconvenient_ sample (i.e.
+@AGM2018 conducted static public goods games in the lab and on MTurk to draw lessons from online experimentation.
+This study extends this literature [see @GoodmanPaolacci2017; also  @AmirEtAl2012] by focusing on an _inconvenient_ sample (i.e.
 one that is completely inexperienced sample that has not been exposed to interactive experiments before) playing a computationally more complex game.
@@
 @sec-conclusion concludes.
+Because I observed some differences in reproducing GMTV's analysis using their data, I report these in the [Appendix](@sec-appendix).
 
@@
 
-> _"There are two possible articles you can write: (a) the article you planned to write when you designed your study or (b) the article that makes the most sense now that you have seen the results.
-They are rarely the same, and the correct answer is (b)."_
+> _There are two possible articles you can write: (a) the article you planned to write when you designed your study or (b) the article that makes the most sense now that you have seen the results.
+They are rarely the same, and the correct answer is (b)._
 
@@
 Today, researchers can not only choose where to pre-register but also decide about the level of detail they provide.
-More severely, nothing stops researchers from pre-registering multiple hypotheses opposing each other (see e.g.
-@SimmonsEtAl2021 and @PhamEtAl2021 for a discussion).
+More severely, nothing stops researchers from pre-registering multiple hypotheses opposing each other (see, e.g., @SimmonsEtAl2021 and @PhamEtAl2021 for a discussion).
 
@@
 Importantly, changes are time-stamped and can be tracked.
-Moreover, one can create branches, that is, duplicates of code -- either to work collaborative or to archive a certain state.
+Moreover, one can create branches, that is, duplicates of code either to work collaboratively or to archive a certain state.
 
@@
 
-In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific_ reproduction^[@Parsons2022 use the term of a _conceptual replication_ which means the same.] of one treatment of GMTV's dynamic public good game.
+In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific_ reproduction^[@Parsons2022 use the term of a _conceptual replication_ which means the same.] of one treatment of GMTV's dynamic public goods game.
 The pure reproduction re-analyzes the original data.
@@
 
-> _"subjects are divided into groups and play the same game for a finite number of periods.
+> _subjects are divided into groups and play the same game for a finite number of periods.
 Each period, every subject is endowed with an income [...] The subject must then divide this income between a contribution to a private account [...] that yields a constant return to themselves only and a contribution to a public account [...] where consumption benefits accrue to all group members.
-At the end of each period, subjects typically learn the aggregate contribution to the public good by all members of their group and their earnings for the period."_
+At the end of each period, subjects typically learn the aggregate contribution to the public good by all members of their group and their earnings for the period._
 
@@
 Hence, a decision in one period has consequences on future endowments and, ultimately, growth paths.
-For this reason, the game is described as a _dynamic_ public good game.
+For this reason, the game is described as a _dynamic_ public goods game.
 
@@
 
-Like GMTV we employ a real giving task after the abstract game.
-In contrast to GMTV and like @GKLS2020, we employed a VCA, where participants could donate any amount their earnings to offset carbon dioxide (that is, retire emission permits from the EU ETS).^[Importantly, @GKLS2020 made the VCA decision with a fresh endowment _before_ they played the abstract game.
+Like GMTV I employ a real giving task after the abstract game.
+Specifically, I employed a (charitable) dictator game where each participant is a dictator dividing her budget between herself and some organization.
+Whereas GMTV chose _Doctors without Borders_ as a receiver, I chose another organization in another context: like @GKLS2020, I employed a VCA, where participants could donate any amount their earnings to offset carbon dioxide (that is, retire emission permits from the EU ETS).^[Importantly, @GKLS2020 made the VCA decision with a fresh endowment _before_ they played the abstract game.
 I deviate from their procedure to match GMTV's procedure.]
@@
 Second, I used another software (oTree instead of zTree) which also affected the graphical user interface participants were exposed to.
-Third, GMTV gave participants the opportunity to donate to _Doctors without Borders_ whereas we offered carbon dioxide offsets.
+Third, GMTV gave participants the opportunity to donate to _Doctors without Borders_ whereas I offered carbon dioxide offsets.
 
@@
 Both samples contributed 10 tokens, that is, 50% of their endowments on average (median and mean).
-Moreover, both samples' initial contributions resemble initial contributions participants usually make in the static game with partner matching.^[See Figure 3B in @fehrgaechter2000 [p.989], for instance.] However, in the dynamic game presented here, we are particularly interested in the subsequent periods because differences add up exponentially.
+Moreover, both samples' initial contributions resemble initial contributions participants usually make in the static game with partner matching.^[See Figure 3B in @fehrgaechter2000 [p.989], for instance.] However, in the dynamic game presented here, I are particularly interested in the subsequent periods because differences add up exponentially.
 Do the two groups remain similar over the course of time?
@@
 In contrast, an average group in the reproduction sample accumulated about `r round(replicationWealth)` tokens.
-This difference is insignificant at conventional levels though: A two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean stock in last period of the game.
+This difference is insignificant at conventional levels though: A two-sided rank sum test (comparing differences between samples) yields p=`r rs1` for the mean stock in last period of the game.
 
@@
 Given the different samples and the possibility of endogenous growth--which essentially is the main feature of the game--I ask whether and how the inequality grows _within_ groups.
-@fig-gini-time-series illustrates that inequality did grow: at the end of the game, the original and the replication groups exhibit an average Gini coefficient of `r originalGini` and `r replicationGini`, respectively.^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean Gini coefficient in last round of the game.] Because every participant started with the same initial endowment (in _period 0_, so to speak), every group started equally--with a Gini coefficient equaling zero.
+@fig-gini-time-series illustrates that inequality did grow: at the end of the game, the original and the replication groups exhibit an average Gini coefficient of `r originalGini` and `r replicationGini`, respectively.^[The two-sided rank sum test (comparing differences between samples) yields p=`r rs1` for the mean Gini coefficient in last round of the game.] Because every participant started with the same initial endowment (in _period 0_, so to speak), every group started equally--with a Gini coefficient equaling zero.
 
@@
   scale_y_continuous(limits = c(0, 0.25), expand = c(0, 0)) +
-  labs(y = "Wealth", x = "Period") +
+  labs(y = "Gini coefficient", x = "Period") +
   scale_color_manual(values = c(cPrimary, cSecondary),
@@
 @GKLS2020 asked how much can we learn about voluntary climate action from the behavior in public goods games.
-Using a similar strategy, I answer the question for a _dynamic_ public good game: _Not much_.
+Using a similar strategy, I answer the question for a _dynamic_ public goods game: _Not much_.
 Overall, there seems to be no association between choices in the voluntary climate action and the first period in the dynamic public goods game.
@@
 A visual inspection shows that (a) mean contributions are positive in both tasks for both samples.^[The same holds true for median contributions.] (b) Furthermore, average contributions are lower in the VCA.
-(c) In contrast to @GKLS2020's observation, we do not observe a difference between samples in the abstract game's contribution behavior.
+(c) In contrast to @GKLS2020's observation, I do not observe a difference between samples in the abstract game's contribution behavior.
 (d) However, the student's share of income contributed to the VCA is significantly lower than the general population sample's contributions (two-sided rank sum test, p=`r rs1`).
@@
                  var = "donationShare",
-                 xlab = "Share of erarnings the general pop. contributed", 
+                 xlab = "Share of income the general pop. contributed", 
                  ylab = "Density in VCA")
@@
 This suggests that the general population sample's transferability is just as bad as the student sample's.
-We thus, find a similar result as @GKLS2020 [p.6].
+I thus, find a similar result as @GKLS2020 [p.6].
 

### 2023-05-24 analysis/quarto/paper.tex
incorporate comments on citation, style and punctuation

@@
   pdfkeywords={Replication study, Non-convenience sample, Open
-science, Dynamic public good game, Online experiment, Generalizability},
+science, Dynamic public goods game, Online
+experiment, Generalizability},
   colorlinks=true,
@@
 \begin{abstract}
-I revisit the dynamic public good game by Gächter et al.~(2017)
+I revisit the dynamic public goods game by Gächter et al.~(2017)
 developed to study cooperation under dynamic interdependencies.
@@
 such as fatigue and dropouts, this research approaches them. Doing so, I
-and provide simple solutions to run relieable interactive experiments
+provide simple solutions to run relieable interactive experiments
 online.
@@
     Replication study \sep Non-convenience sample \sep Open
-science \sep Dynamic public good game \sep Online experiment \sep 
+science \sep Dynamic public goods game \sep Online experiment \sep 
     Generalizability
 \end{keyword}
-\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, frame hidden, boxrule=0pt, breakable, enhanced, sharp corners]}{\end{tcolorbox}}\fi
+\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, breakable, interior hidden, boxrule=0pt, enhanced, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi
 
@@
 actions in each period. Accordingly, participants' actions in a given
-period do not affect their number of actions in subsequent periods. To
-see the lack of realism, consider carbon dioxide emissions, where the
+period do not affect their action space in subsequent periods. To see
+the lack of realism, consider carbon dioxide emissions, where the
 current stock will last for well over a millennium
@@
 hereafter, GMTV]{GMTV2017} as well as Stefan Große (2011, unpublished)
-shows that it is fairly simple to remedy that flaw. They incorporated
-interdependencies into a \emph{dynamic} public good game by defining
-endowments as the income of previous periods. To put it differently,
-participants' actions in a given period affect their number of actions
-in subsequent periods: the more (less) they earn now, the more (less)
-they can contribute in the next period. Importantly, this modification
-qualitatively yields the same rational predictions as the static game
-(i.e.~free-riding and the under-provision of the public good). It is
-thus, equally well suited to study dilemma situations.
+shows that it is fairly simple to remedy that limitation. They
+incorporated interdependencies into a \emph{dynamic} public goods game
+by defining endowments as the income of previous periods. To put it
+differently, participants' actions in a given period affect their number
+of actions in subsequent periods: the more (less) they earn now, the
+more (less) they can contribute in the next period. Importantly, this
+modification qualitatively yields the same rational predictions as the
+static game (i.e.~free-riding and the under-provision of the public
+good). It is thus, equally well suited to study dilemma situations.
 
@@
 to investigate its generalizability. \citet{GKLS2020} find that static
-public good games do not generalize well to real-world climate action.
+public goods games do not generalize well to real-world climate action.
 They also find that generalizability depends on structural resemblance
@@
 also observed the participants' behavior in voluntary climate actions
-(VCA).\footnote{The VCA is a (charitable) dictator games where each
+(VCA).\footnote{The VCA is a (charitable) dictator game where each
   participant is a dictator dividing her budget between herself and some
@@
 
-\citet{AGM2018} conducted static public good games in the lab and on
+\citet{AGM2018} conducted static public goods games in the lab and on
 MTurk to draw lessons from online experimentation. This study extends
-this literature \citep[see also][
-\citet{AmirEtAl2012}]{GoodmanPaolacci2017} by focusing on an
-\emph{inconvenient} sample (i.e.~one that is completely inexperienced
-sample that has not been exposed to interactive experiments before)
-playing a computationally more complex game. This required me to design
-a robust (and thus, more complex) software to minimize attrition. I
-collected paradata to assess the desired fluency and feasibility of the
-experiment. This research reports on the robust design that made the
-dynamic game feasible.
+this literature
+\citetext{\citealp[see][]{GoodmanPaolacci2017}; \citealp[also][]{AmirEtAl2012}}
+by focusing on an \emph{inconvenient} sample (i.e.~one that is
+completely inexperienced sample that has not been exposed to interactive
+experiments before) playing a computationally more complex game. This
+required me to design a robust (and thus, more complex) software to
+minimize attrition. I collected paradata to assess the desired fluency
+and feasibility of the experiment. This research reports on the robust
+design that made the dynamic game feasible.
 
@@
 Section~\ref{sec-generalizability}. Section~\ref{sec-conclusion}
-concludes.
+concludes. Because I observed some differences in reproducing GMTV's
+analysis using their data, I report these in the
+\href{@sec-appendix}{Appendix}.
 
@@
 \begin{quote}
-\emph{``There are two possible articles you can write: (a) the article
-you planned to write when you designed your study or (b) the article
-that makes the most sense now that you have seen the results. They are
-rarely the same, and the correct answer is (b).''}
+\emph{There are two possible articles you can write: (a) the article you
+planned to write when you designed your study or (b) the article that
+makes the most sense now that you have seen the results. They are rarely
+the same, and the correct answer is (b).}
 \end{quote}
@@
 researchers from pre-registering multiple hypotheses opposing each other
-(see e.g. \citet{SimmonsEtAl2021} and \citet{PhamEtAl2021} for a
+(see, e.g., \citet{SimmonsEtAl2021} and \citet{PhamEtAl2021} for a
 discussion).
@@
 control. Importantly, changes are time-stamped and can be tracked.
-Moreover, one can create branches, that is, duplicates of code -- either
-to work collaborative or to archive a certain state.
+Moreover, one can create branches, that is, duplicates of code either to
+work collaboratively or to archive a certain state.
 
@@
   use the term of a \emph{conceptual replication} which means the same.}
-of one treatment of GMTV's dynamic public good game. The pure
+of one treatment of GMTV's dynamic public goods game. The pure
 reproduction re-analyzes the original data.
@@
 \begin{quote}
-\emph{``subjects are divided into groups and play the same game for a
+\emph{subjects are divided into groups and play the same game for a
 finite number of periods. Each period, every subject is endowed with an
@@
 contribution to the public good by all members of their group and their
-earnings for the period.''}
+earnings for the period.}
 \end{quote}
@@
 endowments and, ultimately, growth paths. For this reason, the game is
-described as a \emph{dynamic} public good game.
+described as a \emph{dynamic} public goods game.
 
@@
 
-Like GMTV we employ a real giving task after the abstract game. In
-contrast to GMTV and like \citet{GKLS2020}, we employed a VCA, where
-participants could donate any amount their earnings to offset carbon
-dioxide (that is, retire emission permits from the EU ETS).\footnote{Importantly,
-  \citet{GKLS2020} made the VCA decision with a fresh endowment
-  \emph{before} they played the abstract game. I deviate from their
-  procedure to match GMTV's procedure.} To ensure that each participant
-had the same basic level of information about the impact of their
-decision, I provided some basic information about the mechanism. The
-information also highlighted that the mitigation came into operation on
-a European level. Finally, I informed the participants that the
-documentation of individual and aggregate contributions were to be
-posted immediately after the concluding the sessions online. To avoid
-privacy or social image concerns, participants learned their unique and
-random IDs, which they needed to identify their individual
-contributions. The document certified that their contributions have been
-used to offset
+Like GMTV I employ a real giving task after the abstract game.
+Specifically, I employed a (charitable) dictator game where each
+participant is a dictator dividing her budget between herself and some
+organization. Whereas GMTV chose \emph{Doctors without Borders} as a
+receiver, I chose another organization in another context: like
+\citet{GKLS2020}, I employed a VCA, where participants could donate any
+amount their earnings to offset carbon dioxide (that is, retire emission
+permits from the EU ETS).\footnote{Importantly, \citet{GKLS2020} made
+  the VCA decision with a fresh endowment \emph{before} they played the
+  abstract game. I deviate from their procedure to match GMTV's
+  procedure.} To ensure that each participant had the same basic level
+of information about the impact of their decision, I provided some basic
+information about the mechanism. The information also highlighted that
+the mitigation came into operation on a European level. Finally, I
+informed the participants that the documentation of individual and
+aggregate contributions were to be posted immediately after the
+concluding the sessions online. To avoid privacy or social image
+concerns, participants learned their unique and random IDs, which they
+needed to identify their individual contributions. The document
+certified that their contributions have been used to offset
 \href{https://www.compensators.org/compensatelist/?searchterm=stefan+traub}{1.82
@@
 Third, GMTV gave participants the opportunity to donate to \emph{Doctors
-without Borders} whereas we offered carbon dioxide offsets.
+without Borders} whereas I offered carbon dioxide offsets.
 
@@
   \citet[p.989]{fehrgaechter2000}, for instance.} However, in the
-dynamic game presented here, we are particularly interested in the
+dynamic game presented here, I are particularly interested in the
 subsequent periods because differences add up exponentially. Do the two
@@
 though: A two-sided rank sum test (comparing differences between
-samples) yields a p-Value of 0.1356 for the mean stock in last period of
-the game.
+samples) yields p=0.1356 for the mean stock in last period of the game.
 
@@
   two-sided rank sum test (comparing differences between samples) yields
-  a p-Value of 0.6059 for the mean Gini coefficient in last round of the
-  game.} Because every participant started with the same initial
-endowment (in \emph{period 0}, so to speak), every group started
-equally--with a Gini coefficient equaling zero.
+  p=0.6059 for the mean Gini coefficient in last round of the game.}
+Because every participant started with the same initial endowment (in
+\emph{period 0}, so to speak), every group started equally--with a Gini
+coefficient equaling zero.
 
@@
 action from the behavior in public goods games. Using a similar
-strategy, I answer the question for a \emph{dynamic} public good game:
+strategy, I answer the question for a \emph{dynamic} public goods game:
 \emph{Not much}. Overall, there seems to be no association between
@@
 contributions are lower in the VCA. (c) In contrast to
-\citet{GKLS2020}'s observation, we do not observe a difference between
+\citet{GKLS2020}'s observation, I do not observe a difference between
 samples in the abstract game's contribution behavior. (d) However, the
@@
 suggests that the general population sample's transferability is just as
-bad as the student sample's. We thus, find a similar result as
+bad as the student sample's. I thus, find a similar result as
 \citet[p.6]{GKLS2020}.

### 2023-05-24 analysis/quarto/PageTimes.qmd
incorporate another set of comments and calculate overall page times for cost estimation

--- 2023-05-22 analysis/quarto/paper.qmd
@@
 ---
-title: Revisiting 'Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation
-author:
-  - name: Hauke Roggenkamp
-    email: hauke.roggenkamp@unisg.ch
-    affiliations:
-        - id: HSU
-          name: Helmut Schmidt University
-          department: Department of Economics
-          address:  Holstenhofweg 85
-          city: Hamburg
-          state: Germany
-          postal-code: 22043
-        - id: HSG
-          name: University of St. Gallen
-          department: Institute for Behavioral Science and Technology
-          address: Torstrasse 25
-          city: St. Gallen
-          state: Switzerland
-          postal-code: 9000
-    # attributes:
-    #     corresponding: true
-    # note: This is the first author footnote.
-abstract: |
-  I revisit the dynamic public good game by Gächter et al.
-(2017) developed to study cooperation under dynamic interdependencies.
-Collecting data from both students and a general population sample, I not only reproduce some of the author's original observations but also test the game's generalizability.
-Appending a charitable dictator game, I find no correlations between behavior in the abstract game and the charitable context.
-This applies to students and the general population sample alike.
-Studying inexperiend general population samples raises methodological challenges with respect to fatigue and dropouts.
-This paper approaches them and provides simple solutions to run relieable interactive experiments online.
-
-  You can find the most recent version of this paper [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.pdf).
-keywords: 
-  - Replication study
-  - Non-convenience sample
-  - Open science
-  - Dynamic public good game
-  - Online experiment
-  - Generalizability
-date: last-modified
-bibliography:  ../biblio.bib
-format:
-  elsevier-pdf:
-    keep-tex: true
-    journal:
-      name: Journal of Behavioral and Experimental Economics
-      formatting: preprint
-      model: 3p
-      cite-style: authoryear
+title: "Page Times"
+format: html
 ---
-
-```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = FALSE,
-                      fig.width = 10, fig.height = 4)
-```
-
-```{r locale}
-#| include: false
-#| warning: false
-#| eval: false
-
-Sys.setlocale("LC_TIME","English United States")
-```
 
@@
                stargazer, vtable, ggplot2, patchwork, MetBrewer, Rmisc, knitr)
-```
-
-```{r constants}
-SHOW_UP_FEE <- 5
-EXCHANGE_RATE <- 1/20
 ```
@@
 
-<!-- OUR DATA -->
-
 ```{r readAllData}
 # identify files of all sessions
-files <- list.files(path = "../../data/replication/",
+files <- list.files(path = "../../data/pageTimes/",
                        recursive = TRUE,
@@
 
-# ignore observations who have not made it to the first contribution
-DT <- full[participant._index_in_pages > 2 & 
-             participant.time_started != "" & 
-             participant.label != "" &
-             !(is.na(dPGG.1.player.contribution))]
+# participants who made it to the last page
+full_obs <- full[page_index == max(page_index), participant_code]
+
+DT <- full[participant_code %in% full_obs & (page_index == max(page_index) | page_index == min(page_index)) & session_code != '5mm1nf75']
+
+setorder(DT, session_code, participant_code, page_index)
 
 # tidy up
-rm(list = c("files", "csvs", "i", "name", "temp"))
+rm(list = c("files", "csvs", "i", "name", "temp", "full_obs"))
 ```
 
-```{r metaData}
-# aggregate each session's meta data
-meta_long <- full[participant.time_started != "" & 
-                    participant.label != "",
-                  .(session.code,
-                    participant.label,
-                    participant.time_started,
-                    participant._index_in_pages,
-                    dPGG.1.player.contribution)]
+```{r}
+DT[, seconds_spent := epoch_time - shift(epoch_time, n = 1, type = 'lag'), by = participant_code]
 
-# reformat time stamp in new variables
-meta_long[, `:=`(date = participant.time_started %>% ymd_hms() %>% date(),
-                 hour = participant.time_started %>% ymd_hms() %>% hour())]
+DT[, median(seconds_spent, na.rm = TRUE) %>% seconds_to_period()]
+DT[, mean(seconds_spent, na.rm = TRUE) %>% seconds_to_period()]
+DT[, min(seconds_spent, na.rm = TRUE) %>% seconds_to_period()]
+DT[, max(seconds_spent, na.rm = TRUE) %>% seconds_to_period()]
 
-# aggregate and count 
-meta <- meta_long[,
-                  .(date = date %>% unique(),
-                    # weekday = date %>% unique() %>% lubridate::wday(label = TRUE),
-                    time = hour %>% unique() %>% paste("00", sep = ":"),
-                    showups = participant.time_started %>% length(),
-                    dropouts = sum(participant._index_in_pages == 2),
-                    residuals = sum(is.na(dPGG.1.player.contribution) & participant._index_in_pages == 77)),
-                  by = session.code]
-
-# get number of participants and observations (groups of 4)
-meta[,
-     `:=`(participants = showups - dropouts - residuals,
-          observations = (showups - dropouts - residuals)/4)]
-
-# save data
-fileName <- "replication2021"
-save(meta, file = paste0("../../data/processed/rda/", fileName, "_meta", ".rda"))
-write.csv(meta, file = paste0("../../data/processed/csv/", fileName, "_meta", ".csv"))
-
-rm(list = c("meta_long"))
-```
-
-```{r identifyStudents}
-# we had to invite students as the general population sample was exhausted, unfortunately. let's identify them:
-invitedStudents <- read.table(file = "../../data/sample/invited_students.txt", col.names = c("participant.label")) %>%
-  data.table()
-# note that these students participated in the ultimate session
-```
-
-```{r focusOnFirstRound}
-# create data table 
-replicationFirstRound <- DT[,
-                 .(participant.code,
-                   treatment = "replication",
-                   session.code,
-                   groupID = paste(session.code, dPGG.1.group.id_in_subsession, sep = "_"),
-                   othersContribution = dPGG.1.group.total_contribution - dPGG.1.player.contribution,
-                   ownContribution = dPGG.1.player.contribution,
-                   trust = Outro.1.player.PQ11,
-                   government = Outro.1.player.PQ13,
-                   comprehension = dPGG.10.player.comprehension)]
-
-# save data
-save(replicationFirstRound, file = paste0("../../data/processed/rda/", fileName, "_R1", ".rda"))
-write.csv(replicationFirstRound, file = paste0("../../data/processed/csv/", fileName, "_R1", ".csv"))
-```
-
-```{r subsetData}
-
-# identify most relevant variables
-mRegex <- "participant\\.code$|session\\.code$|dPGG\\.1\\.group\\.id_in_subsession|^dPGG.1.player.id_in_group$|\\.1\\.player.belief|endowment|contribution|stock|gain$|bot_active|10.player.comprehension|10.player.donation"
-mainVariables <- str_subset(string = names(DT), pattern = mRegex)
-
-# prune all other variables
-subset <- DT[, ..mainVariables]
-
-# tidy up
-rm(list = c("mRegex", "mainVariables"))
-```
-
-```{r addNewVariables}
-# refactor groupID such that it eventually contains treatment-info
-subset[, groupID := paste(session.code, 
-                          dPGG.1.group.id_in_subsession,
-                          sep = "_")]
-
-# add share as contribution/endowment
-for(round in 1:10){
-  contribution <- glue("dPGG.{round}.player.contribution")
-  endowment <- glue("dPGG.{round}.player.endowment")
-  subset[, glue("dPGG.{round}.player.share") := subset[[contribution]]/subset[[endowment]] ]
-}
-
-# add treatment variable
-subset[,
-       treatment := "replication"]
-```
-
-```{r calculateAggregates}
-# we need to aggregate some outcomes on a groupID level (per sessions per treatment)
-# we'll do so using a loop
-# this will yield a list of data tables that will be merged to a list eventually.
-cluster <- c("treatment", "session.code", "groupID")
-outcomes <- c("contribution", "endowment", "stock", "gain", "bot_active")
-
-DTs <- list()
-for(outcome in outcomes){
-  if(outcome == "bot_active"){
-    var = names(subset) %>% str_subset(pattern = glue("group\\.{outcome}$"))
-  } else {
-    var = names(subset) %>% str_subset(pattern = glue("player\\.{outcome}$"))
-  }
-
-  # calculate either averages or the sum per round per group
-  aggregates = subset[, lapply(.SD, sum, na.rm=TRUE), 
-                      by = cluster, 
-                      .SDcols=var]
-
-  # transform from wide to long
-  meltedAggregates <- melt(aggregates, id.vars = cluster, measure.vars = var)
-  DTname <- glue("{str_to_title(outcome)}")
-  DTs[[DTname]] <- meltedAggregates
-  rm(list = c("DTname", "meltedAggregates", "aggregates", "var", "outcome"))
-}
-```
-
-```{r renameVariables}
-# each data table in that list has the same column names.
-# the outcomes are all named "value", for instance.
-# now, we"ll infer the round number (contained in the variable name)
-for(i in 1:length(outcomes)){
-  DTs[[i]] <- DTs[[i]][,
-                       .(treatment,
-                         session.code,
-                         groupID,
-                         round = str_replace_all(string = variable,
-                                                 pattern = "\\D", 
-                                                 replacement="") %>% as.integer(),
-                         value # to be renamed afterwards
-                       )
-  ]
-  # rename "value" to outcome variable
-  setnames(DTs[[i]], old = "value", new = outcomes[i])
-}
-
-# tidy up
-rm("i")
-```
-
-```{r calculateGini}
-# repeat everything for the gini
-var = names(subset) %>% str_subset(pattern = "player\\.stock$")
-gini = subset[,
-              lapply(.SD, Gini, na.rm=TRUE), 
-                by = cluster, 
-                .SDcols=var
-              ]
-Gini <- melt(gini, id.vars = cluster, measure.vars = var)
-
-DTs[["Gini"]] <- Gini[,
-                    .(treatment,
-                      session.code,
-                      groupID,
-                      round = str_replace_all(string = variable,
-                                              pattern = "\\D", 
-                                              replacement="") %>% as.integer(),
-                      gini = value
-                       )]
-rm(list = c("var", "gini", "Gini"))
-
-# note that GMTV used start of period earnnings, i.e. endowments. We use end of period earnings, i.e. stock.
-# this adjustment has been considered in our processing of GMTVs data.
-```
-
-```{r mergerEverything4FinalData}
-# now merge every table in the list to one final data table called "replication"
-replication <- Reduce(function(...) merge(..., by=c(cluster, "round"), all = TRUE), DTs)
-
-# tidy up
-rm(list = c("cluster", "contribution", "endowment", "round", "DTs", "outcomes"))
-```
-
-```{r calculateShare}
-# define the share (one of the main outcome variables) as 
-# the sum of contributions devided by the sum of endowments
-replication[, share := contribution/endowment]
-```
-
-```{r defineRichGroups}
-# use the median to differentiate between poor and rich groups (as GMTV did)
-median <- replication[round == 10,
-                      median(stock)]
-
-# find the groups that end up rich or poor
-richGroups <- replication[round == 10 & stock > median,
-                          unique(groupID)]
-
-poorGroups <- replication[round == 10 & stock < median,
-                          unique(groupID)]
-
-# mark these groups for each period
-replication[groupID %in% richGroups,
-            rich := TRUE]
-
-replication[groupID %in% poorGroups,
-            rich := FALSE]
-
-# tidy up
-rm(list = c("median", "poorGroups", "richGroups"))
+tmp <- DT[!is.na(seconds_spent)]
 
@@
 
-```{r misc}
-# flag observations where at least one participant did not understand the game
-noComp <- subset[dPGG.10.player.comprehension == 0,
-                 groupID] %>% unique()
-replication[,
-     noComprehension := 0]
-replication[groupID %in% noComp,
-     noComprehension := 1]
+```{r}
 
-# drop observations (i.e. groups in rounds) with dropouts (bot_active == 1) and
-# where round > 10
-replication <- replication[bot_active == 0 & round <= 10]
+ggplot(data = tmp,
+       mapping = aes(x = seconds_spent/60)) +
+  geom_density(col = cPrimary, fill = NA, alpha = 0.66) +
+  scale_x_continuous(limits = c(0, NA),
+                       expand = c(0, NA)) +
+  scale_y_continuous(limits = c(0, 0.075),
+                       expand = c(0, NA)) +
+  geom_vline(xintercept = tmp[, median(seconds_spent/60, na.rm = TRUE)],
+             col = "#999999",
+             lty = 2) +
+    labs(title = "", 
+       y = "", x = "Minutes Spent in Experiment") +
+  layout
 
-# tidy up
-rm("noComp")
-```
-
-```{r saveData}
-save(replication, file = paste0("../../data/processed/rda/", fileName, ".rda"))
-write.csv(replication, file = paste0("../../data/processed/csv/", fileName, ".csv"))
-```
-
-```{r createCovariates}
-
-# so far, I neglected many variables in what happened before. The following few lines
-# deal with some of these variables in a similar procedure
-
-# add variables
-DT[, treatment := "replication"]
-DT[, groupID := paste(session.code, dPGG.1.group.id_in_subsession, 
-                    sep = "_")]
-
-# subset
-cRegex <- "participant.code|session.code|treatment|groupID|Outro.1.player|10.player.donation|10.player.stock|switching_row|inconsistent"
-covariates <- str_subset(string = names(DT),
-                            pattern = cRegex)
-CT <- DT[, ..covariates]
-
-# rename
-names(CT) <- names(CT) %>% 
-  str_replace_all(pattern =".*player\\.",
-                  replacement = "") %>%
-  str_to_lower()
-names(CT)[names(CT) == "groupid"] <- "groupID"
-
-# refactor
-CT[, donation := donation/20] # exchange rate tokens to real world currency 1/20
-CT[donation %>% is.na, donation := 0]
-CT[, gender := ifelse(test = gender == "female",
-                      yes  = 1,
-                      no   = 0)]
-CT[, inconsistent := as.logical(inconsistent)]
-
-# reassign payoff (with stock of the last period)
-CT[, payoff := stock]
-CT[, stock := NULL]
-
-# write data
-replicationCovariates <- CT
-save(replicationCovariates, 
-     file = paste0("../../data/processed/rda/", fileName, "_COVS", ".rda"))
-write.csv(replicationCovariates, 
-          file = paste0("../../data/processed/csv/", fileName, "_COVS", ".csv"))
-
-# tidy up
-rm(list = c("CT", "cRegex", "covariates"))
-```
-
-```{r readTime}
-# as before, we need to read a list of files (measuring the time spent per page)
-
-# identify files
-files <- list.files(path = "../../data/pageTimes/",
-                       recursive = TRUE,
-                       full.names = TRUE)
-
-# loop
-csvs <- list()
-for(i in files){
-  name <- str_extract(string = i,
-                      pattern = "2021.*")
-
-  temp <- read.csv(i, 
-                   stringsAsFactors = FALSE) %>%
-    data.table()
-
-  csvs[[name]] <- temp
-}
-
-# bind files list to data.table
-timeSpent <- rbindlist(l = csvs,
-                       use.names = TRUE) %>%
-  data.table()
-
-# set oder
-setorder(timeSpent, session_code, participant_code, epoch_time)
-
-# tidy up
-rm(list = c("files", "i", "name", "temp"))
-```
-
-```{r calcDuration}
-# shift rows to calculate this duration (per page) as the distance between
-# the current and the next time stamp
-timeSpent[,
-          lag := shift(epoch_time, fill = NA, type = "lag"),
-          by = c("session_code", "participant_code")]
-
-timeSpent[,
-          duration := epoch_time - lag,
-          by = c("session_code", "participant_code")]
-
-# calculate overall time spent as the difference between the min and max time stamp
-timeSpent[,
-          completion := epoch_time %>% max() - epoch_time %>% min(),
-          by = c("session_code", "participant_code")]
-
-# create new data table with selected columns
-duration <- timeSpent[session_code %in% meta$session.code, # participant_code %in% DT$participant.code,
-                      .(
-                        session_code,
-                        participant_code,
-                        app_name,
-                        page_name,
-                        page_index,
-                        page_submission = epoch_time,
-                        time_spent = duration,
-                        completion_time = completion
-                      )]
-
-# save data
-save(duration, file = paste0("../../data/processed/rda/", fileName, "_timeSpent", ".rda"))
-write.csv(duration, file = paste0("../../data/processed/csv/", fileName, "_timeSpent", ".csv"))
-
-# tidy up
-rm(list = c("timeSpent", "csvs", "DT"))
-```
-
-<!-- ORIGINAL (GMTV) DATA -->
-
-```{r readGMTV}
-# having done all that, we need to prepare the original data and bind it to ours
-# I'll thus, start by reading the orginal data
-
-DT <- read_dta(file="../../data/gaechteretal/GMTV-data.dta") %>% data.table()
-CT <- read_dta(file="../../data/gaechteretal/GMTV-questionnaire-data.dta") %>% data.table()
-```
-
-```{r subsetGMTV}
-# because we only replicate one of their treatments, I subset accordingly
-# noPunish10 <- DT[exp_num == 5 | exp_num == 8 | exp_num == 9]
-noPunish10 <- DT[longgame == 0 & punish == 0 & exp_num <= 10]
-```
-
-```{r newVariablsGMTV}
-# calculate the share of endowments contributed
-noPunish10[,
-           share := sum/gdp,
-           by = .(subj_id, per)]
-
-# calculate gini based on endowments (as GMTV did)
-noPunish10[,
-           gini2 := Gini(c(tokens, other1, other2, other3)),
-           by = .(subj_id, per)]
-
-# calculate gini based on stock (i.e. end of period earnings)
-noPunish10[, stock0 := (tokens - putin + 1.5*sum/4) %>% ceiling()]
-noPunish10[, stock1 := (other1 - pu1 + 1.5*sum/4) %>% ceiling()]
-noPunish10[, stock2 := (other2 - pu2 + 1.5*sum/4) %>% ceiling()]
-noPunish10[, stock3 := (other3 - pu3 + 1.5*sum/4) %>% ceiling()]
-noPunish10[, 
-           gini3 := Gini(c(stock0, stock1, stock2, stock3)),
-           by = .(subj_id, per)]
-```
-
-```{r createGMTVtable}
-# select columns we are interested in and rename a few to match our data
-
-GMTV <- noPunish10[order(gr_id, per),
-           .(treatment = "noPunish10", 
-             session.code = exp_num,
-             groupID = gr_id, 
-             round = per,
-             contribution = sum,
-             endowment = gdp,
-             share,
-             stock = (gdp + ceiling(sum/4*1.5)*4-sum),
-             gain = (ceiling(sum/4*1.5)*4-sum),
-             gini = gini3,
-             bot_active = 0,
-             noComprehension = NA)] %>% unique()
-
-# tidy up
-rm(list = c("noPunish10"))
-```
-
-```{r richPoorGMTV}
- # create rich indicator (just as highgdp in original data)
-median <- GMTV[round == 10,
-                   median(stock)]
-
-richGroups <- GMTV[round == 10 & stock > median,
-                       unique(groupID)]
-
-poorGroups <- GMTV[round == 10 & stock < median,
-                       unique(groupID)]
-
-GMTV[groupID %in% richGroups,
-         rich := TRUE]
-
-GMTV[groupID %in% poorGroups,
-         rich := FALSE]
-
-# tidy up
-rm(list = c("median", "richGroups", "poorGroups", "fileName"))
-```
-
-```{r saveGMTV}
-fileName <- "GMTV2017"
-# save data
-save(GMTV, file = paste0("../../data/processed/rda/", fileName, ".rda"))
-write.csv(GMTV, file = paste0("../../data/processed/rda/", fileName, ".csv"))
-```
-
-```{r calcSwitchingPoint}
-# GMTV gathered some risk data that I'll process in a separate DT and merge it
-# with other covariates later on
-
-GMTVRisk <- CT[exp_num == 5 | exp_num == 8 | exp_num == 9,
-               .(participant.code = subj_id,
-                 e10, e20, e30, e40, e50, e60, e70,
-                 inconsistent = ifelse(test = e60 < e70 | e50 < e60 | e40 < e50 | e30 < e40 | e20 < e30 | e10 < e20,
-                                       yes  = TRUE,
-                                       no   = FALSE)
-                 )]
-
-GMTVRisk[,
-         switching_row := ifelse(test = inconsistent == TRUE,
-                                yes  = NA,
-                                no   = e10 + e20 + e30 + e40 + e50 + e60 + e70 + 1 + 2) # because GMTV used a 7-point-likert scale
-         ]
-```
-
-```{r subsetCovariates}
-# subset covariate data and rename+refactor some variables
-temp <- CT[exp_num == 5 | exp_num == 8 | exp_num == 9,
-                         .(treatment = "noPunish10",
-                           session.code = exp_num,
-                           groupID = gr_id,
-                           participant.code = subj_id,
-                           gender,
-                           age = Sys.Date() %>% lubridate::year() - age,
-                           pq01 = q1,
-                           pq02 = q2,
-                           pq03 = q3,
-                           pq04 = q4,
-                           pq05 = q5,
-                           pq06 = q6,
-                           pq07 = q7,
-                           pq08 = q8,
-                           pq09 = q9,
-                           pq10 = q10,
-                           pq11 = q11,
-                           pq12 = q12,
-                           pq13 = q13,
-                           pq14 = q14,
-                           donation = don
-                           )]
-
-temp[donation %>% is.na, donation := 0]
-
-```
-
-```{r mergeAndWrite}
-
-GMTVCovariates <- data.table::merge.data.table(x = temp,
-                                               y = GMTVRisk[, .(participant.code, inconsistent, switching_row)],
-                                               by = c("participant.code"))
-
-# write data
-save(GMTVCovariates, 
-     file = paste0("../../data/processed/rda/", fileName, "_COVS", ".rda"))
-write.csv(GMTVCovariates, 
-          file = paste0("../../data/processed/csv/", fileName, "_COVS", ".csv"))
-
-# tidy up
-rm(list = c("temp", "GMTVRisk"))
-```
-
-```{r firstRound}
-noPunish <- DT[exp_num == 1 | exp_num == 3 | # noPunish15
-                 exp_num == 5 | exp_num == 8 | exp_num == 9] # noPunish10
-
-temp <- noPunish[per == 1]
-temp <- temp[,
-             treatment := "noPunish10"]
-temp <- temp[exp_num == 1 | exp_num == 3,
-             treatment := "noPunish15"]
-
-GMTVFirstRound <- temp[,
-                           .(participant.code = subj_id,
-                             treatment,
-                             session.code = exp_num,
-                             groupID = gr_id,
-                             othersContribution = sumputin - putin,
-                             ownContribution = putin,
-                             trust = NA,
-                             government = NA,
-                             comprehension = NA)]
-
-# save data
-save(GMTVFirstRound, 
-     file = paste0("../../data/processed/rda/", fileName, "_R1", ".rda"))
-write.csv(GMTVFirstRound, 
-          file = paste0("../../data/processed/csv/", fileName, "_R1", ".csv"))
-
-rm(list = c("temp", "fileName"))
-```
-
-<!-- MERGE & TUNE DATA -->
-
-```{r rbindOursAndGMTV, eval = TRUE}
-main <- rbindlist(list(replication, GMTV), 
-                  use.names = TRUE)
-
-R1   <- rbindlist(list(replicationFirstRound, GMTVFirstRound), 
-                  use.names = TRUE)
-
-covs <- rbindlist(list(replicationCovariates, GMTVCovariates), 
-                  use.names = TRUE,
-                  fill = TRUE)
-
-rm(list = c("CT", "DT", "GMTV", "GMTVCovariates", "GMTVFirstRound", 
-            "noPunish", "replication", "replicationCovariates",
-            "replicationFirstRound", "subset"))
-```
-
-```{r treatmentAsFactor}
-main[, treatment := as.factor(treatment)]
-R1[, treatment := as.factor(treatment)]
-covs[, treatment := as.factor(treatment)]
-```
-
-```{r studentSample}
-
-# Two of these sessions were special: The first (`r meta[1, session.code]`) as well as the last one (`r meta[, session.code %>% tail(n=1)]`).
-The first session suffered technical problems such that the risk elicitation task was omitted.
-The last session (almost exclusively) relied on a student sample as our non-student sample was exhausted after the first three sessions.
-As a consequence, the last session was conducted with 59 students while all others were conducted without any students.
-I'll therefore create a boolean `student` variable.
-Becaue all of the original experiments were conducted with students, `student` also equals 1 in the "noPunish10" treatments
-
-main[, student := FALSE]
-main[session.code == "d6jrsxnr" | treatment == "noPunish10",
-     student := TRUE]
-
-covs[, student := FALSE]
-covs[session.code == "d6jrsxnr" | treatment == "noPunish10",
-     student := TRUE]
-
-R1[, student := FALSE]
-R1[session.code == "d6jrsxnr" | treatment == "noPunish10",
-   student := TRUE]
-```
-
-```{r earnings}
-
-# This chunk requires raw data
-files <- list.files(path = "../../data/replication/",
-                       recursive = TRUE,
-                       full.names = TRUE)
-csvs <- list()
-
-for(i in files){
-  name <- str_extract(string = i,
-                      pattern = "2021.*")
-
-  temp <- read.csv(i, 
-                   stringsAsFactors = FALSE) %>%
-    data.table()
-
-  csvs[[name]] <- temp
-}
-
-full <- rbindlist(l = csvs,
-                  use.names = TRUE) %>%
-  data.table()
-
-# subset data of participants who have completed the study
-tmp <- full[participant._index_in_pages >= 76 & 
-              participant.time_started != "" & 
-              !(is.na(dPGG.1.player.contribution)) &
-              participant.label != ""]
-
-# calculate total payoff
-tmp[, finalPayoff := (dPGG.10.player.stock - dPGG.10.player.donation + HLPL.1.player.payoff) * EXCHANGE_RATE + SHOW_UP_FEE]
-
-earningsMean <- tmp[, mean(finalPayoff, na.rm = TRUE)]
-earningsSD   <- tmp[, sd(finalPayoff, na.rm = TRUE)]
-```
-
-<!-- PAPER STARTS HERE -->
-
-<!-- 
-# Key Takeaways
-
-- We **[replicate](#gmtv-replication)** a public goods experiment with dynamic inter-dependencies and find similar results as @GMTV2017. 
-    + Absolute contributions increase over time.
-    + Just as in _static_ public goods experiments, the share of endowments contributed decreases over time.
-    + The richest groups earn fifteen times more than the poorest groups.
-    + While there clearly is growth, groups do not realize the maximal potential efficiency and earn just over `r main[treatment == "replication" & round == 10, mean(stock)/(80*1.5^10)*100] %>% round(digits=1)`% of what is possible.
-- Varying the subject pool and including a voluntary climate action (VCA), we have a setup similar to @GKLS2020, which allows us to assess **[generalizability](#generalizability)**.^[Note that one can easily model the VCA as a dictator game, which relates to a literature summarized by @cartwright2022.]
-- Studying a general population sample online, synchronously and over the course of multiple periods, we find that classic **[lab procedures](online-methodology)** can be applied outside of the lab too.
-    + Even though we conducted the experiment online and remotely, dropouts (or "attrition") are no concern.
-    + Relying on an inexperienced non-convenience sample that cannot interact with experimenters, `r trunc((R1[comprehension > 1] %>% NROW() / R1[!(is.na(comprehension))] %>% NROW())*100)`% of all participants stated that they understood the game.
-    + Participants make relatively fast decisions which makes longer games feasible in the future.^[Taken together with inefficient growth and the lack of dropouts, additional rounds are fairly cheap.]
-
--->
-
-# Introduction {#sec-intro}
-
-Today's actions are tomorrow's result.
-There are many settings in which current decisions affect future outcomes and with it, future decision spaces.
-Opting for environmental friendly policies today not only reduces carbon dioxide omissions immediately but also helps us to reach the Paris climate targets tomorrow.
-Deferring these policies, may not necessarily prevent us from reaching these targets, but it makes it more difficult in the future.
-Hence, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of paths one can choose to reach certain goals.
-This applies especially to carbon dioxide emissions where its current stock will last for well over a millennium [@Inman2008; @CalzolariEtAl2018].
-
-Public good games---although often intended to inform climate policies (e.g.
-@MilinskiEtAl2006, @TavoniEtAl2011, @Hauser2014, @BrickEtAl2015, @GomezEtAl2018, @CalzolariEtAl2018, @CookEtAl2019)---miss these temporal interdependencies simply because participants have the same set of actions in each period.
-Accordingly, participants' actions in a given period do not affect their number of actions in subsequent periods.
-A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017] (hereafter, GMTV) as well as Stefan Große (2011, unpublished) incorporated interdependencies into a _dynamic_ public good game.
-Here, participants' actions in a given period affect their number of actions in subsequent periods.
-Because there is surprisingly little experimental research on these interdependencies^[One exemption are @Moser2019, who built on GMTV's design to investigate leadership.], I reproduced one of their treatments to compare dynamics across samples.
-
-@GKLS2020 find that standard public good games do not generalize well to real-world climate action.
-They also find that generalizability depends on structural resemblance of the public goods game with the context of climate change mitigation.
-Greater resemblance improves generalizability.
-Because GMTV's dynamic setting has a more realistic property—namely, interdependencies—one wonders whether it is better suited to inform public policy.
-To approach this question, I ran the experiment with different samples^[GMTV ran their experiments with students in Nottingham, England.] and
-<!--, that is, with participants who make their decisions in an environment which is more natural than the lab.-->
-observed the participants' behavior in voluntary climate actions (VCA).
-This yielded a setting similar to @GKLS2020's which allows me to analyze how behavior in the abstract game translates into real-world action across samples.
-The article shows that the dynamic setting _does not_ add any advances with respect to generalizability of results.
-
-The VCA is a (charitable) dictator games where each participant is a dictator dividing her budget between herself and some organization linked to the reduction of CO2 emissions.
-@EckelGrossman1996 were the first to implement a charitable dictator game observing contributions of 30% of the endowments.
-Like @GKLS2020, @CarpenterEtAl2008 report that students make lower contributions to charity than community members.
-
-@AGM2018 conducted public good games in the lab and on MTurk to draw lessons from online experimentation.
-This study extends this literature [see also @GoodmanPaolacci2017  @AmirEtAl2012] by focusing on an inconvenient sample: one that is completely inexperienced sample that has not been exposed to interactive experiments before.
-This required me to design a robust (and thus, more complex) software to minimize attrition.
-In exchange, the online setting allowed me to also collect paradata to assess the fluency and feasibility of the experiment.
-This article reports on both topics: the robust design as well as the feasibility.
-
-Taken together, this study makes three contributions.
-First, it reproduces parts of GMTV's original experiment and highlights the importance of pure replications.
-Second, it shows that logistically complex online experiments are feasible for samples other than students or clickworkers.
-Third, this paper supports critics arguing that findings from abstract games do not generalize well---not even with a more representative sample.
-
-After commenting on transparent research practices and reporting the methods in @sec-transparency and @sec-methods, this paper is organized along these findings: The confirmatory reproduction is reported in @sec-replication, the online feasibility in @sec-feasibility and the generalizability in @sec-generalizability.
-@sec-conclusion concludes.
-
-# Transparency {#sec-transparency}
-
-Well before credibility crises comprised a variety disciplines, @bemwriting [p. 2] indirectly conceded discrepancies between fuzzy research processes and the polished article that results from it:
-
-> _"There are two possible articles you can write: (a) the article you planned to write when you designed your study or (b) the article that makes the most sense now that you have seen the results.
-They are rarely the same, and the correct answer is (b)."_
-
-Now, 20 years later, we accustom ourselves with mechanisms designed to unravel the fuzzy back-and-forth between exploratory and confirmatory research.
-Prominently, pre-registrations were established to tie the researchers' hands when doing confirmatory research--reducing observable discrepancies between (a) and (b).
-Today, researchers can not only choose where to pre-register but also decide about the level of detail they provide.
-More severely, nothing stops researchers from pre-registering multiple hypotheses opposing each other (see e.g.
-@SimmonsEtAl2021 and @PhamEtAl2021 for a discussion).
-
-@WaldronAllen2022 report a wide variety of depth of pre-registrations in the field of Neuropsychopharmacology and document that the label _'pre-registration'_ can be obtained with minimal effort.
-In absence of transparency and scrutiny pre-registrations run into danger to miss the target of making science more credible.
-Even more so, they may have adverse effects as the label _'pre-registered'_ becomes cheap (too) to acquire.
-
-Discussing the costs and benefits of pre-registrations, @Olken2015 stresses the uncertainty of research processes and promotes moderate approaches.
-As @WaldronAllen2022, he argues that pre-registrations not necessarily eliminate  flexibility.
-These 'moderate' or 'flexible' approaches require transparency to reduce concerns of _'data-mining'_ [@Olken2015 p.
-61] by showing (a) the analyses I planned to run, (b) the analysis that made most sense after collecting the data and the transition from (a) to (b).
-Because this is neither incentivized nor easy to verify, we need tools that make transparency convenient to establish and to scrutinize.
-I propose version control (such as Git) as one such tool and illustrate its application on this paper:  GitHub is a website and cloud-based service where developers---and researchers alike---can store and manage their code.
-The service is based on Git^[Git is a specific open-source version control system developed in 2005.] and designed for version control.
-Importantly, changes are time-stamped and can be tracked.
-Moreover, one can create branches, that is, duplicates of code -- either to work collaborative or to archive a certain state.
-
-To sum up, pre-registrations alone are necessary but not sufficient to restore the credibility in experimental sciences.
-Pre-registrations must come with additional emphasis on transparency covering the whole research process as well as with a higher level of scrutiny that looks beyond mere labels.
-
-In fact, the experiment reported in this article qualifies for the label _'pre-registered'_ at a first glance:
-Parts of the analyses were pre-registered in the American Economic Association's RCT Registry [@preregistration].
-In addition, I pre-registered the exact analyses I planned to run when I designed the experiment on [GitHub](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.]
-
-At a second glance, the analysis that made the most sense after having collected the data and that is reported here is a little different though: Because the more representative subject pool was exhausted earlier than expected, I recruited students which opened up a new research direction: assessing generalizability.
-Hence, this article combines both confirmatory as well as exploratory research.
-
-Accordingly, I  changed many of the analysis scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd] However, because the originally planned analysis code is archived and reproducible, these changes are transparent.
-Importantly, I followed a literate programming approach [@Knuth_1984; @AkhtarYe_2023].
-Hence, all documents needed to analyze the data and to write the report stem from the same source.
-This establishes consistence between the commands one tells the statistical software to do and the explanation one tells human beings one told the statistical software to do.
-As such, (a), (b) and the transition from (a) to (b) are not only transparent but also comprehensible.
-
-<!--
-I archived detailed analyses scripts and created a [branch](https://github.com/Howquez/coopUncertainty/tree/July21Replication) a few days _before_ we collected data and pre-registered the analysis via the American Economic Association's RCT Registry [@preregistration].
--->
-
-# Methodology {#sec-methods}
-
-In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific_ reproduction^[@Parsons2022 use the term of a _conceptual replication_ which means the same.] of one treatment of GMTV's dynamic public good game.
-The pure reproduction re-analyzes the original data.
-[Appendix A](#A:-Pure-Replication) documents [errors I identified]() in the original paper.
-The scientific reproduction, where I utilize a different sample drawn from a different population in a different situation, is described in the following sections.
-
-## Experimental Design {#sec-design}
-
-The design builds on the workhorse model @Zelmer2003 [p.301] describes in her meta-analysis, where
-
-> _"subjects are divided into groups and play the same game for a finite number of periods.
-Each period, every subject is endowed with an income [...] The subject must then divide this income between a contribution to a private account [...] that yields a constant return to themselves only and a contribution to a public account [...] where consumption benefits accrue to all group members.
-At the end of each period, subjects typically learn the aggregate contribution to the public good by all members of their group and their earnings for the period."_
-
-Considering the design, the only differences between such a _static_ game and GMTV's design are _dynamics_: Instead of receiving fresh endowments every period, participants receive one endowment only at the beginning of the first period.
-A participant's endowment in the second period is the wealth she accumulated in the first period.
-A participant's endowment in the third period is the wealth she accumulated in the first two periods.
-And so on.
-Hence, a decision in one period has consequences on future endowments and, ultimately, growth paths.
-For this reason, the game is described as a _dynamic_ public good game.
-
- As in the NOPUNISH 10 Period treatment of GMTV, I ran sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of $N_i^1 = 20$ tokens^[A token was worth `r EXCHANGE_RATE` Euros.], $T=10$ periods, a private account with a return of $1$ and a group account with a return of $1.5$ ($\Rightarrow$ MPCR$\equiv \frac{1.5}{4}$).
-With $i$'s contribution in period $t$ being $c_i^t$, the model looks as follows:
-
-$$
-N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
-$$
-
-## Voluntary Climate Action (VCA)
-
-Like GMTV we employ a real giving task after the abstract game.
-In contrast to GMTV and like @GKLS2020, we employed a VCA, where participants could donate any amount their earnings to offset carbon dioxide (that is, retire emission permits from the EU ETS).^[Importantly, @GKLS2020 made the VCA decision with a fresh endowment _before_ they played the abstract game.
-I deviate from their procedure to match GMTV's procedure.]
-To ensure that each participant had the same basic level of information about the impact of their decision, I provided some basic information about the mechanism.
-The information also highlighted that the mitigation came into operation on a European level.
-Finally, I informed the participants that the documentation of individual and aggregate contributions were to be posted immediately after the concluding the sessions online.
-To avoid privacy or social image concerns, participants learned their unique and random IDs, which they needed to identify their individual contributions.
-The document certified that their contributions have been used to offset [1.82 tons](https://www.compensators.org/compensatelist/?searchterm=stefan+traub) of carbon dioxide emissions.
-
-## Recruitment and Sample Characteristics {#sec-sample}
-
-I recruited the participants from the so called _[HamburgPanel](https://www.wiso.uni-hamburg.de/forschung/forschungslabor/umfragelabor/aktuelle-umfragen/hamburgpanel.html)_ using HROOT [@hroot].
-The panel is provided by the University of Hamburg's Research Laboratory, which used a randomized last digits approach to build the panel while drawing from the population of citizens of Hamburg, Germany.
-Because the sample was exhausted at one point, I also recruited students from the University of Hamburg.
-
-At the time I conducted the experiment, the more representative sample was not familiar with interactive experiments.
-In fact, I ran the first interactive group experiment with this sample.
-The students, in contrast, were used to single-player experiments.
-Recruiting them, I excluded those who have participated in interactive experiments such as public goods games before, to keep the two distinct subject pools comparable in terms of their experience.
-As a consequence, nonnaiveté is unlikely to affect the validity of the experiment [@GoodmanPaolacci2017 p.
-204].
-
-Throughout this paper, I will compare results of my experiment with the results of GMTV's NOPUNISH 10 Period treatments.
-I am thus, referring to three different samples utilized at two points in time: the University of Nottingham's students (in late 2012), Hamburg's citizens and the University Hamburg's students (both in July 2021).
-@tbl-sample-properties gives an overview.
-
-```{r sampleDifferences1, results = "asis", warning = FALSE, eval=FALSE}
-
-covs[, sample := "Nottingham Students"]
-covs[treatment == "replication" & student == TRUE, sample := "Hamburg Students"]
-covs[treatment == "replication" & student == FALSE, sample := "Hamburg Citizens"]
-covs[, sample := as.factor(sample)]
-# covs[, sample := ordered(sample, levels = c("Nottingham Students", "Hamburg Students", "Hamburg Citizens"))]
-
-m1 <- lm(formula = gender ~ sample, data = covs)
-m2 <- lm(formula = age ~ sample, data = covs)
-m3 <- lm(formula = switching_row ~ sample, data = covs)
-m4 <- lm(formula = donation ~ sample, data = covs)
-m5 <- lm(formula = pq11 ~ sample, data = covs)
-m6 <- lm(formula = pq12 ~ sample, data = covs)
-m7 <- lm(formula = pq13 ~ sample, data = covs)
-m8 <- lm(formula = pq14 ~ sample, data = covs)
-
-stargazer(m1, m2, m5, m6, m7, m8,
-
-          column.labels = c("female", "age",
-                            "trust", "meritocracy", "government", "equality") %>% str_to_title(),
-          model.numbers = FALSE,
-          dep.var.labels.include = FALSE,
-          header=FALSE,
-          intercept.bottom = FALSE,
-          covariate.labels = c("Hamburg Citizens", "Hamburg Students", "Nottingham Students"),
-
-          type = "latex", digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
-          )
-```
-
-```{r sampleProperties}
-#| results: 'asis'
-#| label: tbl-sample-properties
-#| tbl-cap: Sample Properties
-
-covs[, sample := "Nottingham Students"]
-covs[treatment == "replication" & student == TRUE, sample := "Hamburg Students"]
-covs[treatment == "replication" & student == FALSE, sample := "Hamburg Citizens"]
-covs[, sample := as.factor(sample)]
-
-vtable::sumtable(data = covs, 
-                 vars = c('age', 'gender', 'switching_row'),
-                 group = 'sample',
-                 group.test = TRUE,
-                 digits = 2,
-                 labels = c('Age', 'Female', 'Switching Row'),
-                 # note = "Switching Row describes choices in a multiple price list to elicit risk preferences.
-The higher the value, the higher the certainty equivalent.
-Government Responsible is self-reported based on a question adapted from GMTV ('The government should take responsibility that people are better provided for.')",
-                 out = 'latex')
-```
-
-```{r}
-# covs[, sample := ordered(sample, levels = c("Nottingham Students", "Hamburg Students", "Hamburg Citizens"))]
-```
-
-Overall, I recruited `r covs[treatment == 'replication', .N]` participants for the experiment.
-The three samples differ significantly with respect to their age.
-The non-student sample is more diverse compared to the two student samples.
-
-## Software {#sec-software}
-
-The experiment was logistically complex for several reasons.
-First, the sample was inexperienced.
-Second, the experiment was interactive and synchronous.
-Third, the underlying game was dynamic and interdependent.
-This makes dropouts not only more likely but also more expensive, which is why attrition was a major concern implementing the experiment.
-
-I chose oTree [@oTree] to implement the experiment because it is open-source, well documented and very flexible.
-Its [Bootstrap](https://getbootstrap.com/) (a powerful frontend toolkit) integration allowed me to make the graphical user interface interactive, appealing and easy to navigate.
-The [Highcharts library](https://www.highcharts.com/) made it easy to visualize results and to communicate dynamics.
-Insofar, oTree served a good tool to enhance the participants' user experience and thus, to make dropouts less likely.
-
-Which features were required to handle dropouts?
-First, participants had to be matched to form a group _after_ comprehension questions were answered successfully.
-Importantly, participants were grouped by the order they answered these questions to reduce waiting times.
-While waiting for other players to form the group, the participants saw a wait-page informing them that they are waiting for other participants to arrive and that they do not have to wait for longer than 10 minutes.
-The screen also informed them that they would receive a _patience bonus_ of one Euro after the expiration of that time (or what was left of it).
-Second, participants only had 10 minutes to make the first contribution and 4 minutes for the remaining contributions.
-After this time expired, participants were replaced by bots that made random contributions.
-In this case, the remaining group members were informed about the replacement.
-Both features were implemented to limit wait times and boredom for other participants.
-@sec-feasibility shows that the first feature became effective in some cases, wheres the second feature did not.
-
-## Procedure {#sec-procedure}
-
-Participants entered the experiment at appointed times remotely from home.
-They first saw a welcome screen.
-After agreeing to the privacy policy, they could proceed to the instructions individually.
-Having read these instructions, each participant has also seen a demo-screen explaining the user interface.
-Before proceeding, they had to answer six comprehension questions correctly to avoid confusion in later stages [@FerraroVossler2010].
-Subsequently, they saw a waiting screen until they could be matched with three other participants, who have answered the comprehension questions correctly.
-Once matched, they were exposed to the decision screen over ten periods.
-At the end of the last period, participants saw results of all periods.
-Subsequently, they made their VCA decision, before I elicited risk preferences [@HoltLaury2002] and finished with GMTV's questionnaire.
-
-While I stuck to GMTV's protocol as close as possible, I deviated in a few aspects.
-First, the instructions were German and also covered topics inherent to the online setting (dropouts and bots, for instance).
-Second, I used another software (oTree instead of zTree) which also affected the graphical user interface participants were exposed to.
-Third, GMTV gave participants the opportunity to donate to _Doctors without Borders_ whereas we offered carbon dioxide offsets.
-
-```{r totalTimeSpent}
-tmp <- duration[page_index == 1 | page_index == 76, 
-                .(page_index, participant_code, page_submission)]
-tmp[order(participant_code, page_index), 
-    total := page_submission - data.table::shift(x = page_submission,
-                                                 n = 1,
-                                                 type = "lag"),
-    by = participant_code]
-
-total_completion_time <- tmp[!is.na(total), mean(total/ 60) %>% round()]
-```
-
-The experiment lasted around `r total_completion_time` minutes on average.
-The earnings  averaged `r earningsMean %>% round(digits = 2)` Euros (sd = `r earningsSD  %>% round(digits = 2)`).^[This values include earnings from the incentivized risk elicitation task that is not part of the analysis.]
-
-# Results {#sec-results}
-
-## Pre-registered GMTV Reproduction {#sec-replication}
-
-```{r}
-N_r <- R1[treatment == "replication", .N]
-N_o <- R1[treatment == "noPunish10", .N]
-```
-
-Throughout this section, I pool data from both the citizens as well as the students from Hamburg and compare it with the students GMTV recruited in Nottingham.
-I refer to the two samples as the _reproduction sample_ ($N_r$ = `r N_r`) and the _original sample_ ($N_o$ = `r N_o`), respectively.
-
-### Contribution Behavior {#sec-contributions}
-
-```{r prepFirstSummary}
-replication <- R1[treatment == "replication", ownContribution]
-GMTV    <- R1[treatment == "noPunish10", ownContribution]
-
-rows <- sapply(X = list(replication, GMTV), FUN = NROW) %>% max()
-temp <- data.frame(replication = c(replication, rep(NA, rows - NROW(replication))),
-                   GMTV = c(GMTV, rep(NA, rows - NROW(GMTV))))
-
-rs1 <- wilcox.test(replication, 
-                   GMTV,
-                   exact = FALSE)$p.value %>% 
-  round(digits = 4) %>% 
-  formatC(format = "f", 
-          digits = 4)
-```
-
-First, I ask whether the samples differ with respect to their initial contributions to the public good.
-Is the reproduction sample (consisting of both students and non-students) more pro-social than the original sample?
-A two-sided rank sum test reveals that it is not (p=`r rs1`).
-Both samples contributed 10 tokens, that is, 50% of their endowments on average (median and mean).
-Moreover, both samples' initial contributions resemble initial contributions participants usually make in the static game with partner matching.^[See Figure 3B in @fehrgaechter2000 [p.989], for instance.] However, in the dynamic game presented here, we are particularly interested in the subsequent periods because differences add up exponentially.
-Do the two groups remain similar over the course of time?
-
-```{r firstRoundViz}
-#| eval: false
-#| fig-cap: Individual contributions to the dynamic public good in the first period
-#| label: fig-first-round
-
-ggplot(data = R1[treatment != "noPunish15"],
-       mapping = aes(x = ownContribution, fill = treatment, lty = treatment)) +
-  geom_density(alpha = 0.5) +
-  scale_x_continuous(limits = c(0, 20),
-                       expand = c(0, NA)) +
-  scale_y_continuous(limits = c(0, 0.1),
-                       expand = c(0, NA)) +
-  scale_fill_manual(values = c(cPrimary, cSecondary),
-                    labels = c("Original Sample", "Reproduction Sample")) +
-  guides(lty = "none") +
-  geom_vline(xintercept = R1[treatment == "replication", 
-                             mean(ownContribution)],
-             col = "#FFFFFF",
-             lty = 2) +
-  geom_vline(xintercept = R1[treatment == "noPunish10", 
-                             mean(ownContribution)],
-             col = "#FFFFFF",
-             lty = 1) +
-    labs(title = "", 
-       y = "", x = "Initially Contributed Tokens",
-       caption = "White lines indicate means (dashed line = reproduction sample).") +
-  layout +
-  theme(legend.position = "top")
-```
-
-```{r firstRoundSummary}
-#| results: asis
-#| warning: false
-#| fig.cap: "test"
-#| eval: false
-
-if(knitr::is_html_output()){
-  type <- "html"
-} else {
-  type = "latex"
-}
-
-stargazer(temp,
-          summary.stat = c("mean", "median","sd", "max", "min", "n"),
-          type = type, 
-          flip = TRUE, 
-          header=FALSE)
-```
-
-```{r}
-for(r in 1:10){
-  a <- main[round == r & treatment == 'replication', share]
-  b <- main[round == r & treatment == 'noPunish10', share]
-
-  wilcox.test(a, 
-              b,
-              exact = FALSE)$p.value %>% 
-    round(digits = 4) %>% 
-    formatC(format = "f", 
-            digits = 4)# %>%
-    # print()
-  }
-
-r <- 5
-a <- main[round == r & treatment == 'replication', contribution]
-b <- main[round == r & treatment == 'noPunish10', contribution]
-
-rs2 <- wilcox.test(a, 
-            b,
-            exact = FALSE)$p.value %>% 
-  round(digits = 4) %>% 
-  formatC(format = "f", 
-          digits = 4)
-```
-
-In particular, do the two samples' contributions follow the same path over the 10 periods they played?
-The answer is _no_.
-@fig-share-of-contributions illustrates that the samples make similar contributions at the beginning and the end of the game but behave differently in between.
-More precisely, the left panel--depicting the average contributions in absolute terms--shows that the original sample contributed more than the reproduction sample _in all but the first and last period_.^[In period five, this difference is significant: a two-sided rank sum test yields p=`r rs2`.
-] For this reason, the original sample's behavior differs from the reproduction sample's behavior in two aspects: it contributes more and exhibits a considerable drop in the last period (whereas the reproduction sample's contributions flatten).
-
-Note that increasing contributions over time imply increasing endowments over time.
-Hence, absolute contributions do not tell much about the willingness to cooperate.
-For this reason, the right panel in @fig-share-of-contributions shows the average _share of endowments contributed_ over time.
-Both samples exhibit a similar pattern: their share of endowments contributed declined and did not stabilize.
-However, both samples also differ with respect to one aspect: the reproduction sample's share of contributions declines faster.
-This is mirrored by a two-sided rank sum test which is only significant at a five percent level in periods three and four.
-
-```{r plotContributions}
-
-SUM <- main[,
-            lapply(.SD, mean, na.rm = TRUE),
-            by = c("round", "treatment"),
-            .SDcols = "contribution"]
-
-SUM[,
-    sum := round(contribution)]
-
-SUM[,
-    contribution := contribution/4]
-
-upperLimit <- SUM$contribution %>% max() %>% round() + 5
-
-p1 <- ggplot(data = SUM, 
-             aes(x = round, y = contribution, fill = treatment, color = treatment, lty = treatment)) +
-  layout +
-  theme(legend.position="top") +
-  geom_line(show.legend=FALSE) +
-  geom_point() +
-  scale_x_continuous(name="",  breaks = 1:15) +
-  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-  labs(y = "Average Amount of Tokens contributed") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("Original Sample", "Reproduction Sample")) + 
-  guides(fill = "none") +
-  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
-
-rm(list = c("SUM"))
-```
-
-```{r plotShareOfContributions}
-#| fig-cap: "The average amount of tokens contributed over time in treatments."
-#| label: fig-share-of-contributions
-
-SHARE <- main[,
-            lapply(.SD, mean, na.rm = TRUE),
-            by = c("round", "treatment"),
-            .SDcols = "share"]
-
-# SHARE <- main[,
-#             .(share = sum(contribution)/sum(endowment)),
-#             by = c("round", "treatment")]
-
-upperLimit <- 0.75
-
-p2 <- ggplot(data = SHARE, 
-             aes(x = round, y = share, fill = treatment, color = treatment, lty = treatment)) +
-  layout +
-  theme(legend.position="bottom") +
-  geom_line(show.legend=FALSE) +
-  geom_point() +
-  scale_x_continuous(name="",  breaks = 1:15) +
-  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-  labs(y = "Share of Current Endowment contributed") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("Original Sample", "Reproduction Sample")) +
-  guides(fill = "none")
-
-p1 + p2 + plot_layout(guides = "collect") & 
-  theme(legend.position = "top")
-
-# rm(list = c("p1", "p2"))
-```
-
-Again, both samples' behavior resembles the contributions participants usually make in the static game with partner matching: contributions equal approximately half of endowments in the very first period and decrease to around ten percent of endowments by the last period.^[The right panel is thus, comparable to the visualizations _and results_ in the static game.
-See, for instance, Figure 1B in @fehrgaechter2000 [p.986].] In the dynamic game presented here, however, different paths lead to different levels of wealth -- even if they share the same start- and end-points.
-I am thus, more interested in the contributions' implications for wealth generation and growth.
-
-### Wealth Creation {#sec-wealth}
-
-```{r summaryWealth}
-#| results: asis
-#| warning: false
-#| fig.cap: "test"
-
-if(knitr::is_html_output()){
-  type <- "html"
-} else {
-  type = "latex"
-}
-
-replication <- main[treatment == "replication" & round == 10, stock]
-GMTV    <- main[treatment == "noPunish10" & round == 10, stock]
-
-rs1 <- wilcox.test(replication, 
-                   GMTV,
-                   exact = FALSE)$p.value %>% 
-  round(digits = 4) %>% 
-  formatC(format = "f", 
-          digits = 4)
-
-```
-
-```{r wealthVariables}
-originalWealth    <- main[treatment == "noPunish10" & round == 10, mean(stock)]
-replicationWealth <- main[treatment == "replication" & round == 10, mean(stock)]
-```
-
-How do the different contribution-paths translate into wealth?^[To measure wealth and growth, I define a variable called _stock_ which sums the endowments of all participants in a given group at the end of the round (that is, after the contributions have been made, multiplied and redistributed).] Given that the original sample contributed more, one would expect the respective groups to be  more wealthy.
-A mere mean comparison indicates just that: An average group in the original sample accumulated about `r round(originalWealth)` tokens.
-In contrast, an average group in the reproduction sample accumulated about `r round(replicationWealth)` tokens.
-This difference is insignificant at conventional levels though: A two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean stock in last period of the game.
-
-```{r stockDistributionViz}
-#| eval: false
-#| fig-cap: Groups' income at the end of the game
-#| label: fig-stock-distribution
-
-ggplot(data = main,
-       mapping = aes(x = stock, fill = treatment, lty = treatment)) +
+ggplot(data = tmp[!is.na(seconds_spent)],
+       mapping = aes(x = seconds_spent/60, fill = session_code)) +
   geom_density(alpha = 0.5) +
@@
                        expand = c(0, NA)) +
-  scale_fill_manual(values = c(cPrimary, cSecondary),
-                    labels = c("Original Sample", "Reproduction Sample")) +
-  guides(lty = "none") +
-  geom_vline(xintercept = replicationWealth,
-             col = "#000000", alpha = 0.5,
-             lty = 2) +
-  geom_vline(xintercept = originalWealth,
-             col = "#000000", alpha = 0.5,
-             lty = 1) +
     labs(title = "", 
-       y = "", x = "Stock",
-       caption = "Grey lines indicate means (dashed line = reproduction sample).") +
-  layout +
-  theme(legend.position = "top")
+       y = "", x = "Minutes Spent in Experiment") +
+  layout
 ```
-
-```{r overallGinis}
-rG <- main[round == 10 & treatment == "replication",
-           .(stock = sum(stock)),
-           by = groupID][, Gini(stock)] %>% round(digits = 2)
-
-oG <- main[round == 10 & treatment == "noPunish10",
-           .(stock = sum(stock)),
-           by = groupID][, Gini(stock)] %>% round(digits = 2)
-
-rSD <- main[round == 10 & treatment == "replication",
-            .(stock = sum(stock)),
-            by = groupID][, sd(stock)] %>% round(digits = 2)
-
-oSD <- main[round == 10 & treatment == "noPunish10",
-            .(stock = sum(stock)),
-            by = groupID][, sd(stock)] %>% round(digits = 2)
-```
-
-Although there clearly is growth, groups do not realize the maximal potential efficiency: under full cooperation, a group can accumulate at least `r (80*1.5^10) %>% trunc()` tokens or EUR `r (80*1.5^10 /20) %>% trunc()`.
-This is depicted in the left panel of @fig-growth-heterogeneity, where one can see the average wealth over time by sample.
-The panel illustrates for both samples that growth was continuous and surprisingly linear, given the exponential character of the game's design.
-Despite somewhat differing contribution behavior between samples, neither the eventual wealth nor the corresponding growth paths differed.
-Differences in contribution behavior did, thus, not translate to significantly different wealth outcomes.
-
-Why?
-Perhaps because the heterogeneity within samples and across groups has been too large to _detect_ a significant difference.
-The right panel of @fig-growth-heterogeneity depicts heterogeneity: In the reproduction sample, the richest group earned `r a <- main[treatment == "replication" & round == 10, max(stock)]; a` tokens (which is about `r round(a/80, digits = 2)*100`% of the initial endowment) whereas the poorest group ends up with `r b <- main[treatment == "replication" & round == 10, min(stock)]; b` tokens (`r round(b/80, digits = 2)*100`%).
-More broadly, the reproduction sample is characterized by inequality between groups ($SD_{Replication} =$ `r rSD`).
-The same holds true for the original sample ($SD_{Original} =$ `r oSD`).
-Hence, the heterogeneity across groups does not differ between samples, which is remarkable because the reproduction sample was drawn from a more heterogeneous (non-convenience sample).
-Does it differ within groups?
-
-<!-- doch lieber Gini? statt SD reporten? -->
-
-```{r plotStock .column-page}
-
-# data
-STOCK <- main[,
-              lapply(.SD, mean, na.rm = TRUE),
-              by = c("round", "treatment"),
-              .SDcols = "stock"]
-
-STOCKr <- main[rich == TRUE,
-               lapply(.SD, mean, na.rm = TRUE),
-               by = c("round", "treatment"),
-               .SDcols = "stock"]
-
-STOCKp <- main[rich == FALSE,
-               lapply(.SD, mean, na.rm = TRUE),
-               by = c("round", "treatment"),
-               .SDcols = "stock"]
-
-# annotation
-maxPath <- data.table(x = 1:10)
-maxPath[, y := 80*1.5^x]
-maxPath[, treatment := "replication"]
-maxPath[, groupID := 42]
-
-# plot
-p1 <- ggplot(data = STOCK, 
-             aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
-  geom_line() +
-  geom_point() +
-  scale_x_continuous(breaks = 1:10) +
-  scale_y_continuous(limits = c(0, 4700), expand = c(0, 0)) +
-  labs(y = "Wealth", x = "Period") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("Original Sample", "Reproduction Sample")) +
-  geom_point(mapping = aes(x = 10, y = 4613), col = "#b5b5b5") +
-  annotate("text", x = 9, y = 4630, size = 3,
-           label = "max", col = "#b5b5b5") +
-  geom_line(data = maxPath, mapping = aes(x = x, y =y), col = "#b5b5b5", lty = 2) +
-  guides(fill = "none") +
-  layout +
-  theme(legend.position = "top") +
-  guides(lty = "none")
-```
-
-```{r growthHeterogeneityViz}
-#| fig-cap: Average wealth over time across samples.
-#| label: fig-growth-heterogeneity
-
-# plot
-p2 <- ggplot(data = main,
-       mapping = aes(x = round, y = stock, color = treatment, by = groupID)) +
-  geom_line(alpha = 0.5) +
-  scale_x_continuous(breaks = 1:10) +
-  scale_y_continuous(limits = c(0, 2000),
-                       expand = c(0, NA)) +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("Original Sample", "Reproduction Sample")) +
-  labs(y = "", x = "Period") +
-  layout +
-  guides(col = "none")
-
-# assembling
-p1 + p2 + plot_layout(guides = "collect") & theme(legend.position = "top")
-```
-
-### Inequality {#sec-inequality}
-
-```{r summaryGini}
-#| results: asis
-#| warning: false
-#| fig.cap: "test"
-
-if(knitr::is_html_output()){
-  type <- "html"
-} else {
-  type = "latex"
-}
-
-replication <- main[treatment == "replication" & round == 10, gini]
-GMTV    <- main[treatment == "noPunish10" & round == 10, gini]
-
-rs1 <- wilcox.test(replication, 
-                   GMTV,
-                   exact = FALSE)$p.value %>% 
-  round(digits = 4) %>% 
-  formatC(format = "f", 
-          digits = 4)
-
-```
-
-```{r giniVariables}
-originalGini    <- main[treatment == "noPunish10" & round == 10, mean(gini)] %>% round(digits = 2)
-replicationGini <- main[treatment == "replication" & round == 10, mean(gini)] %>% round(digits = 2)
-```
-
-Given the different samples and the possibility of endogenous growth--which essentially is the main feature of the game--I ask whether and how the inequality grows _within_ groups.
-@fig-gini-time-series illustrates that inequality did grow: at the end of the game, the original and the replication groups exhibit an average Gini coefficient of `r originalGini` and `r replicationGini`, respectively.^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean Gini coefficient in last round of the game.] Because every participant started with the same initial endowment (in _period 0_, so to speak), every group started equally--with a Gini coefficient equaling zero.
-
-@fig-gini-time-series also shows that this initial state of equality ended with the first period already: both samples exhibit a stark incline in inequality before the second period started.
-From then on, the respective Gini coefficients grew slowly but continuously -- for both samples.^[In each and every period, the two-sided rank sum test comparing gini coefficients between both sample yields p-values way over ten percent.]
-
-```{r giniDistributionViz}
-#| eval: false
-#| fig-cap: Groups' Gini coefficients (within groups) at the end of the game
-#| label: fig-gini-distribution
-
-ggplot(data = main,
-       mapping = aes(x = gini, fill = treatment, lty = treatment)) +
-  geom_density(alpha = 0.5) +
-  scale_x_continuous(limits = c(0, 1),
-                       expand = c(0, NA)) +
-  scale_y_continuous(limits = c(0, NA),
-                       expand = c(0, NA)) +
-  scale_fill_manual(values = c(cPrimary, cSecondary),
-                    labels = c("Original Sample", "Reproduction Sample")) +
-  guides(lty = "none") +
-  geom_vline(xintercept = replicationGini,
-             col = "#000000", alpha = 0.5,
-             lty = 2) +
-  geom_vline(xintercept = originalGini,
-             col = "#000000", alpha = 0.5,
-             lty = 1) +
-    labs(title = "", 
-       y = "", x = "Gini Coefficient",
-       caption = "Grey lines indicate means (dashed line = reproduction sample).") +
-  layout +
-  theme(legend.position = "top")
-```
-
-```{r giniOverTime}
-#| fig-cap: Average Gini coefficient (within groups) over time across samples
-#| label: fig-gini-time-series
-
-tmp <- main[,
-            lapply(.SD, mean, na.rm = TRUE),
-            by = c("round", "treatment"),
-            .SDcols = "gini"]
-
-GINI <- rbind(tmp, list(0, "replication", 0), list(0, "noPunish10", 0))
-
-ggplot(data = GINI, 
-             aes(x = round, y = gini, fill = treatment, color = treatment, lty = treatment)) +
-  geom_line() +
-  geom_point() +
-  scale_x_continuous(breaks = 0:10) +
-  scale_y_continuous(limits = c(0, 0.25), expand = c(0, 0)) +
-  labs(y = "Wealth", x = "Period") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("Original Sample", "Reproduction Sample")) +
-  guides(fill = "none") +
-  layout +
-  theme(legend.position = "top") +
-  guides(lty = "none")
-```
-
-**Result 1.** _The `NOPUNISH 10` treatment of GMTV can be replicated because the replication data resemble the original data with respect to initial and final contributions, wealth and growth as well as inequality._
-
-This is remarkable given the different sample and language, the different software and user interface as well as the online setting during the COVID19 pandemic.
-The result suggests that, by and large, the sum of these factors did not affect people’s preferences towards cooperation.
-
-## Online Feasibility {#sec-feasibility}
-
-```{r}
-N <- duration[, participant_code %>% unique() %>% length()]
-```
-
-Throughout this section, I do not consider GMTV's data and pool data I gathered from the citizens as well as the students from Hamburg (N = `r N`).
-
-```{r reviewInformation}
-#| eval: false
-
-# to see how many people clicked on the popups to review instructions: 
-full[dPGG.1.player.review_instructions !=0, .N]
-full[dPGG.2.player.review_instructions !=0, .N]
-#...
-
-# or for contact information
-full[dPGG.1.player.review_contact !=0, .N]
-full[dPGG.2.player.review_contact !=0, .N]
-# ...
-
-```
-
-How did the participants, who have never participated in an online group experiment before, cope with the situation?
-Moreover, did participants understand the unfamiliar setting they found themselves in?
-While the answer to the former question requires more thought, the answer to the latter simply is _yes_: `r 67` out of `r 44 + 67 + 5` answered with _"yes"_ when I asked them.
-Another `r 44` answered with _"rather yes"_ while nobody indicated that he or she did not understand the situation at all.
-There is some behavioral data supporting this finding: The user interface offered a popup to review instructions or contact information.
-I tracked both and find that none of the participants ever opened these popups even though they were clearly visible in the decision screen's header and introduced in the instructions.
-To further analyze how participants coped with the situation, I consider three additional metrics: selection into the experiment, attrition as well as the time spent on each page.
-
-I first comment on the selection into the experiment: It was difficult to recruit the sample.
-The panel counted 1.209 non-students of which I were able to recruit `r main[student == FALSE, .N]` participants who finished the experiment---even though I varied the weekdays and timing of the sessions (which were conducted during a nation-wide lockdown with home office regime).
-For this reason, I also recruited students in the last session which explains the relatively large number of showups in @tbl-meta.
-Although I intended to refrain from the recruitment of students initially, this particular sub sample enabled me to investigate the generalizability of my results as I will discuss in  @sec-generalizability.
-
-```{r showMeta}
-#| label: tbl-meta
-#| tbl-cap: The Experimental Sessions' Meta Data
-
-meta %>% kable(col.names = names(meta) %>% 
-                 str_replace_all(pattern = "\\.",
-                                 replacement = " ") %>% 
-                 str_to_title()) #, caption = 'A table of the first 10 rows of the mtcars data.')
-```
-
-```{r plotTimeData}
-N <- duration[, participant_code %>% unique() %>% length()]
-plotDT <- duration[app_name == "dPGG" & page_name == "dPGG_Decision",
-                   .(time_spent = time_spent %>% sum()),
-                   by = c("session_code", "participant_code", "page_index", "page_name")]
-
-plotDT[, round := seq(from = 1, to = 10), by = c("participant_code")]
-
-upperLimit <- plotDT[, time_spent %>% mean(), by = c("round")] %>% max()
-
-tmp <- summarySE(data = plotDT,
-                 measurevar = "time_spent",
-                 groupvars=c("round"),
-                 na.rm = FALSE,
-                 conf.interval = 0.95,
-                 .drop = TRUE) %>% 
-  data.table()
-
-```
-
-Turning to the time spent on each page, I focus on the decision times in the dynamic public goods game as @Anderhub2001 did.
-How many seconds did the participants need to make a decision in each period of the game?
-Not too many.
-@fig-time-spent illustrates an intuitive pattern: The first decision took about `r tmp[round == 1, round(time_spent)]` seconds.
-The second decision--where participants first learned about the other group members' previous decisions--took longer (about `r tmp[round == 2, round(time_spent)]` seconds).
-Subsequently, decision times first declined and stabilized at `r tmp[round > 3, round(mean(time_spent))]` seconds.
-Importantly, decision times were so short that crosstalk, that is, communication through private channels--a common concern^[See, for instance, the discussion section in @AGM2018 [p.
-119].] in online experiments--was unlikely, especially because it would require the identification of other group members.^[There were only `r plotDT[page_index == 12 & time_spent > 60, .N]` participants (from all four sessions) who needed more than 60 seconds to make the second decision.]
-
-```{r plotTime}
-#| fig-cap: Average Time Spent for each Contribution per Period
-#| label: fig-time-spent
-
-ggplot(data = tmp,
-       mapping = aes(x = round, y = time_spent)) +
-  layout +
-  theme(legend.position="bottom") +
-  geom_line(show.legend=FALSE, color = cInfo, lty=2) +
-  geom_errorbar(aes(ymin=time_spent-ci, ymax=time_spent+ci), width=.25, alpha = 0.5, color = cInfo) +
-  geom_point(color = cInfo) +
-  scale_x_continuous(name="",  breaks = 1:10) +
-  scale_y_continuous(limits = c(0, upperLimit + 10), expand = c(0, 0)) +
-  labs(y = "Time Passed in Seconds", caption = "Bars indicate 95% confidence intervals.") +
-  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
-```
-
-Considering attrition, I find that it did not affect the interactive experiment at all.
-To elaborate, I differentiate between dropouts and residuals:  Participants who could not be matched to other group members are called residuals.
-Participants who intentionally left the experiment are called dropouts.
-Residuals did not participate in the experiment _by design_.
-Dropouts did not participate in the experiment _by choice_.
-Out of `r meta[, sum(showups)]` people who showed up, I count `r meta[, sum(residuals)]` residuals and `r meta[, sum(dropouts)]` dropouts.
-All of the residuals waited to be matched to a group unsuccessfully before they got paid one Euro for their patience.
-In contrast, all of the dropouts left while reading the instructions and before being matched to other group members.
-Moreover, they got no payment at all.
-Hence, attrition was no concern considering the dynamic public goods game or the expenses.
-
-**Result 2.** _Given the decision times and the fluent procedure, attrition was as negligible as it is in physical laboratories---where (a) not every invited person shows up and (b) a number of participants divisible by the group size is required as well._
-
-## Generalizability {#sec-generalizability}
-
-```{r generalizability_prep}
-R1covs <- covs[, .(participant.code,
-                   donation = donation * 20 ,
-                   donationShare = (donation * 20) / payoff * 100,
-                   age,
-                   gender,
-                   switching_row,
-                   payoff)]
-temp <- R1[R1covs, on = .(participant.code = participant.code)][treatment == "replication"]
-temp[, contributionShare := ownContribution/20 * 100]
-temp[, consistency := 1 - (contributionShare - donationShare)]
-
-N_s <- temp[student == TRUE, .N]
-N_g <- temp[student == FALSE, .N]
-```
-
-As before, I do not consider GMTVs' data in this section.
-Instead, I will differentiate between data from the citizens and the students from Hamburg.
-I refer to the two samples as the _students_ ($N_s$ = `r N_s`) and the _general population sample_ ($N_g$ = `r N_g`), respectively.
-
-@GKLS2020 asked how much can we learn about voluntary climate action from the behavior in public goods games.
-Using a similar strategy, I answer the question for a _dynamic_ public good game: _Not much_.
-Overall, there seems to be no association between choices in the voluntary climate action and the first period in the dynamic public goods game.
-
-```{r vca_differences}
-rs1 <- wilcox.test(temp[student == FALSE, donationShare], 
-                   temp[student == TRUE, donationShare],
-                   exact = FALSE)$p.value %>% 
-  round(digits = 4) %>% 
-  formatC(format = "f", 
-          digits = 4)
-```
-
-@fig-kernel-generalizability shows distributions of contributions across both choices for both samples.
-The top panels illustrate the behavior of the general population sample.
-The bottom panels illustrate the behavior of the student sample.
-The left panels show the behavior in the VCA.
-The right panels show the behavior in first period of the game.
-A visual inspection shows that (a) mean contributions are positive in both tasks for both samples.^[The same holds true for median contributions.] (b) Furthermore, average contributions are lower in the VCA.
-(c) In contrast to @GKLS2020's observation, we do not observe a difference between samples in the abstract game's contribution behavior.
-(d) However, the student's share of income contributed to the VCA is significantly lower than the general population sample's contributions (two-sided rank sum test, p=`r rs1`).
-Taken together, these aggregate results indicate, that the consistency between tasks is higher for the general population than it is for students.
-Or, to put it differently, the general population's behavior in the abstract game better predicts their behavior in real-world mitigation context.
-
-```{r vizGeneralizability}
-#| fig-cap: Kernel distributions of contributions across tasks and subject pools.
-#| label: fig-kernel-generalizability
-#| fig.height: 6
-
-# viz wrapper
-plotShares <- function(stud = FALSE,
-                       var  = "donationShare",
-                       col  = cPrimary,
-                       xlab = "",
-                       ylab = ""){
-
-  dt <- temp[student == stud, .(x = get(var))]
-
-  model <- lm(x ~ 1, dt)
-  ci1 <- confint(model, level=0.95)[1]
-  ci2 <- confint(model, level=0.95)[2]
-
-  ggplot(data = dt,
-         mapping = aes(x = x)) +
-    annotate("rect", 
-             xmin = ci1, xmax = ci2, 
-             ymin  =0, ymax = Inf, 
-             alpha = 0.33) +
-    geom_density(alpha = 0.75,
-                 fill = col) +
-    scale_x_continuous(limits = c(0, 100),
-                       expand = c(0, NA)) +
-    scale_y_continuous(limits = c(0, NA),
-                       expand = c(0, NA)) +
-    geom_vline(xintercept = dt[,mean(x, na.rm = TRUE)],
-               lty = 2) +
-    labs(x = xlab,
-         y = ylab) +
-  layout
-}
-
-p1 <- plotShares(stud = FALSE, 
-                 col = cSecondary,   
-                 var = "donationShare",
-                 xlab = "Share of erarnings the general pop. contributed", 
-                 ylab = "Density in VCA")
-
-p2 <- plotShares(stud = FALSE, 
-                 col = cSecondary,   
-                 var = "contributionShare", 
-                 xlab = "Share of endowment the general pop. contributed", 
-                 ylab = "Density in dPGG Experiment (period 1)")
-
-p3 <- plotShares(stud = TRUE,  col = cPrimary, var = "donationShare",
-                 xlab = "Share of income the students contributed",
-                 ylab = "Density in VCA")
-
-p4 <- plotShares(stud = TRUE,  col = cPrimary, var = "contributionShare", 
-                 xlab = "Share of endowment the students contributed",
-                 ylab = "Density in dPGG Experiment (period 1)")
-
-patchwork <- (p1 / p3) | (p2 / p4)
-patchwork + plot_annotation(caption = "Dashed vertical lines indicate the respective means.\nShaded areas indicate 95% confidence intervals.")
-
-rm(list = c("R1covs", "p1", "p2", "p3", "p4", "patchwork"))
-```
-
-@tbl-tobit-generalizability shows that this is not the case.
-It reports tobit regression results cautioning against transferability from dPGG results to real-world mitigation behavior: The share of endowment contributed in the first period (displayed in the first row) does not predict the share of earnings donated as a VCA.
-The student status negatively affects VCA donations in column two but disappears if one controls for age in column three.
-Importantly, the interaction of student status and first-period contributions is not significant.
-This suggests that the general population sample's transferability is just as bad as the student sample's.
-We thus, find a similar result as @GKLS2020 [p.6].
-
-```{r generalizability_tobit}
-#| results: 'asis'
-#| label: tbl-tobit-generalizability
-#| tbl-cap: Correlations between first-round-dPGG and VCA behavior
-
-to1 <- censReg(formula = donationShare ~ contributionShare, 
-                   data = temp, left = 0, right = 100)
-to2 <- censReg(formula = donationShare ~ contributionShare + student + student * contributionShare, 
-                   data = temp, left = 0, right = 100)
-reg <- lm(formula = donationShare ~ contributionShare + student + student * contributionShare, 
-                   data = temp,)
-to3 <- censReg(formula = donationShare ~ contributionShare + student + student * contributionShare + age + gender, 
-                   data = temp, left = 0, right = 100)
-to4 <- censReg(formula = donationShare ~ contributionShare + student + student * contributionShare + age + gender + switching_row, 
-                   data = temp, left = 0, right = 100)
-
-stargazer(to1, to2, # reg, 
-          to3, # to4,
-
-          model.numbers = TRUE,
-          dep.var.caption  = "Tobit Regression censoring below 0 and above 100",
-          dep.var.labels = "VCA Donation as Share of Earnings",
-          header=FALSE,
-          intercept.bottom = TRUE,
-          order = c(1, 2, 6, 3, 4, 5),
-          covariate.labels = c("First-period contribution in percent", "Student (1 = yes)", "First-period contr. x Student", "Age", "Female (1 = yes)", "Risk Aversion (1-12)"),
-          type = "latex", digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
-          )
-```
-
-```{r}
-#| fig-cap: Scatter plot of average contributions in the dPGG and real giving task.
-#| label: fig-scatter-generalizability
-#| fig.height: 6
-#| eval: false
-
-p1 <- ggplot(data = temp[, 
-                   .(vca = donation / payoff * 100,
-                     dpgg = ownContribution / 20 * 100)],
-       mapping = aes(y = vca, x = dpgg)) +
-  annotate("segment", x = 0, xend = 100,
-                   y = 0,
-                   yend = 100,
-                   colour = "black", lty = 2, alpha = 0.5) +
-  geom_point(alpha = 0.5, col = cInfo, size = 2) +
-  geom_smooth(method = "lm", formula = y~x, se = FALSE,
-              col = cInfo) +
-  scale_x_continuous(limits = c(0, 105),
-                     expand = c(0, NA)) +
-  scale_y_continuous(limits = c(0, 105),
-                     expand = c(0, NA)) +
-  labs(y = "VCA: Percentage of endowment donated",
-       x = "Percentage of endowment contributed in period 1") +
-  layout
-
-p2 <- ggplot(data = temp[student == FALSE, 
-                   .(vca = donation / payoff * 100,
-                     dpgg = ownContribution / 20 * 100)],
-       mapping = aes(y = vca, x = dpgg)) +
-  annotate("segment", x = 0, xend = 100,
-                   y = 0,
-                   yend = 100,
-                   colour = "black", lty = 2, alpha = 0.5) +
-  geom_point(alpha = 0.5, col = cSecondary, size = 2) +
-  geom_smooth(method = "lm", formula = y~x, se = FALSE,
-              col = cSecondary) +
-  scale_x_continuous(limits = c(0, 105),
-                     expand = c(0, NA)) +
-  scale_y_continuous(limits = c(0, 105),
-                     expand = c(0, NA)) +
-  labs(y = "VCA: Percentage of endowment donated",
-       x = "General pop.: Percentage of endowment contributed in period 1") +
-  layout
-
-p3 <- ggplot(data = temp[student == TRUE, 
-                   .(vca = donation / payoff * 100,
-                     dpgg = ownContribution / 20 * 100)],
-       mapping = aes(y = vca, x = dpgg)) +
-  annotate("segment", x = 0, xend = 100,
-                   y = 0,
-                   yend = 100,
-                   colour = "black", lty = 2, alpha = 0.5) +
-  geom_point(alpha = 0.5, col = cPrimary, size = 2) +
-  geom_smooth(method = "lm", formula = y~x, se = FALSE,
-              col = cPrimary) +
-  scale_x_continuous(limits = c(0, 105),
-                     expand = c(0, NA)) +
-  scale_y_continuous(limits = c(0, 105),
-                     expand = c(0, NA)) +
-  labs(y = "VCA: Percentage of endowment donated",
-       x = "Students: Percentage of endowment contributed in period 1") +
-  layout
-
-p1 / (p2 + p3)
-```
-
-<!--
-@fig-kernel-generalizability also indicates that the general population's contribution behavior is more consistent than the students' behavior.
-Hence, one may conclude that their behavior in the abstract game translates comparably well to the real world.
-This is not the case.
-If anything, the _students'_ behavior in the abstract game is more predictive for their VCA.
-@fig-scatter-generalizability visualizes the within-subjects relationship of both contribution tasks.
-More precisely, it shows a scatter plot of realized choices, with the percentage of endowment spent by each participant in the first period of the game on the x-axis and that spent in the VCA on the y-axis.
-In addition, the figures contains a fitted line of a linear model.
-The upper panel illustrates overall behavior and exhibits a slope which is indistinguishable from zero.
-No matter how much the participants contributed in the first round, they spent, on average, about `r temp[, round(mean(donationShare))]`% of their income on the VCA.
-The two bottom panels differentiate between both samples with slopes that differ qualitatively.
-However, none of the slopes is significant.
--->
-
-**Result 3.** _There is no significant correlation between average contributions in the abstract public goods game and contributions to the real public good of climate change mitigation._
-
-# Conclusion {#sec-conclusion}
-
-The initial goal of the experiment was to reproduce specific experiments of GMTV in an online setting using a general population sample.
-The results suggest that it is important to reproduce experiments---both purely and scientifically [@Hamermesh2007 p.
-716]---before drawing conclusions about generalizability.
-
-The three most important findings are as follows: First, the contribution behavior in my experiment is statistically similar to the behavior reported in the original study.
-Consequently, the outcomes growth and inequality are reproducible.
-Second, the online experiment proceeded fluently such that dropouts were no concern.
-Third, contribution behavior in the dynamic abstract setting is not linked to behavior in the real world -- neither for students nor a more representative sample.
-
-The significance of the first result is that similar procedures led to replicable findings under different circumstances across two different samples.
-The second result is of methodological importance: It highlights that even logistically complex experiments can be conducted online with---not only with clickworkers but also with a true general population sample.
-The third result questions whether recruiting from more representative samples is worth the efforts because it did not affect transferability of abstract results to the real world.
-
-Limitations?
-
-{{< pagebreak >}}
-
-# A: Pure Replication {.appendix}
-
-This section comments on two errors as well as a misconception I found in the original data.^[The data can be found in the supplementary materials they provide in their [online appendix](https://www.sciencedirect.com/science/article/pii/S0047272717300361#s0115).] Before I proceed to explain this in more detail I would like to say that the results of the original paper still hold after the error is fixed and that the authors responded kindly and quickly, showing an interest in solving the issue.
-In fact, some explanations in this section stem from input provided by the authors.
-
-### Error 1: The Gini coefficient
-
-The Gini coefficient is wrongly computed in some periods for some group members.
-The authors found that this happened whenever two group members had exactly the same endowment because the program failed to rank these group members for further calculations.
-
-```{r readGMTVagain}
-GMTV <- read_dta(file="../../data/gaechteretal/GMTV-data.dta") %>% data.table()
-noPunish10 <- GMTV[exp_num == 5 | exp_num == 8 | exp_num == 9]
-# noPunish10 <- GMTV[longgame == 0 & punish == 0 & exp_num <= 10]
-```
-
-@tbl-gini-error illustrates this problem.
-It shows group 101 in period 5 and documents that the Gini coefficient differs among group members.
-According to the authors, the Gini coefficient should equal `GINI=``r GINI <- GMTV[exp_num == 1 & gr_id == 101 & per == 5, tokens %>% Gini() %>% round(digits = 3)]; GINI` for all subjects in the group.
-Instead, participant `112` and `113` who have an equal endowment deviate from that value.
-Importantly, the `DescTools::Gini()` function in the statistical software `R` does not yield this error, which is why I use that function for my calculations using both my as well as the original data.
-
-```{r}
-#| label: tbl-gini-error
-#| tbl-cap: Subset of Data illustrating the Gini Coefficient's Error
-
-GMTV[exp_num == 1 & gr_id == 101 & per == 5,
-     .(exp_num,
-       gr_id,
-       per,
-       subj_id,
-       tokens,
-       other1,
-       other2,
-       other3,
-       gini = round(gini, digits = 3),
-       GINI = GINI
-       )] %>% 
-  knitr::kable()
-```
-
-### Error 2: The share of endowments contributed
-
-The original data provides a wrong measure of the share of endowments contributed (`mean`) because it relies on a lagged endowment (`gdp`).
-More precisely, the authors used the following STATA code for their calculations:
-
-```
-*tsset subj_id per
-*gen mean=sum/l.gdp
-```
-
-@tbl-mean-error reports participant 111 in group 101 in experiment 1 over three periods.
-Both the `gdp` (that is, the sum of the group’s endowments at the beginning of the period) as well as the `sum` (that is, the sum of the group’s contributions) are group-level variables.
-
-```{r}
-#| label: tbl-mean-error
-#| tbl-cap: Subset of Data illustrating the Means's Error
-
-GMTV[, MEAN := sum/gdp]
-
-GMTV[exp_num == 1 & gr_id == 101 & (per == 4 | per == 5 | per == 6) & subj_id == 111,
-     .(exp_num,
-       gr_id,
-       per,
-       subj_id,
-       gdp,
-       sum,
-       mean = round(mean, digits = 3),
-       MEAN = round(MEAN, digits = 3)
-       )] %>% 
-  knitr::kable()
-```
-
-Calculating the share as `MEAN=sum/gdp` solves the problem and yields $\frac{18}{126}=0.143$ in period 5.
-I thus, used this proposed definition for all my calculations using both my as well as the original data.
-
-### The misconception: Timing
-
-The authors wrote a note stating that the Gini coefficient as well as the wealth in the paper always refer to the situation at the start of a period and that they clarify this because the paper (last paragraph at the bottom of page 5), says that wealth is defined as the endowment at the beginning of the following period.
-Furthermore, they write that this error came about as they switched between these two definitions during the course of revising the paper.
-
-I argue that it makes more sense to calculate the variables as they state in the paper.
-More precisely, I think that the wealth at the _beginning_ of a period is less interesting than the wealth at the _end_ of a period for two reasons: First, there is no need for such a variable because it already exists (the endowment).
-Second, this definition yields a value that is determined by the design of the game but misses an important outcome at the end of the game.
-To illustrate this, note that the wealth would be defined as four times the initial endowment in period 1.
-Also note that the very last value would equal the wealth at the beginning of the last period and says nothing about the outcome of that period.
-Because the contributions often drop in the last period, this outcome is of particular interest (yet, not represented in the data).
-Moreover, this definition of wealth yields more informative values to calculate the Gini coefficient for the same reasons: We know that the Gini coefficient is zero _before_ the participants made any decision by design.
-We do no know the inequality at the very end of the game---and the current definition does not tell us.
-
-For these reasons, I define wealth and inequality measures as the outcomes of a period for all of my calculations using both my as well as the original data.^[Accordingly, the definition of `GINI` I provide in @tbl-gini-error is not the definition I used to calculate the current period's Gini coefficient but the previous period's Gini coefficient.]
-
-{{< pagebreak >}}
-
-<!--
-# B: TITLE (exploratory) {.appendix}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Donec suscipit eleifend felis et faucibus.
-Curabitur nisl risus, tincidunt ut hendrerit sed, sollicitudin eget tortor.
-Curabitur tortor elit, finibus a commodo eget, auctor vel dui.
-Ut convallis, felis in commodo bibendum, ligula neque hendrerit eros, eu eleifend libero ligula pretium dui.
-Nullam blandit a tellus vitae suscipit.
-Donec ac justo vehicula elit tincidunt mollis nec ac lectus.
-Nunc dignissim sem eu felis consequat, id euismod ante imperdiet.
-Mauris quis ex ante.
-
-Nulla elementum laoreet libero nec consequat.
-Donec blandit, tellus id feugiat viverra, lectus tellus sollicitudin ipsum, ut venenatis nunc mauris ut arcu.
-Donec mi eros, ullamcorper aliquet varius non, cursus vel lorem.
-Integer feugiat dui sapien, ac porta lacus porta sit amet.
-Aliquam interdum dictum tempor.
-Quisque bibendum feugiat scelerisque.
-Sed eu purus eu est ullamcorper bibendum.
-
-Donec efficitur magna malesuada tortor feugiat tristique.
-Sed porttitor, quam at vulputate placerat, elit magna posuere est, a eleifend lacus magna ac nunc.
-Quisque sit amet arcu mattis, malesuada mauris et, aliquam libero.
-Fusce viverra sed dolor a ullamcorper.
-Aliquam in ligula neque.
-In maximus nisl id ante vehicula, et euismod ante feugiat.
-Suspendisse et dui lectus.
-Ut euismod ultrices mi eu lacinia.
-
-```{r firstRoundVizAppendix}
-
-d1 <- ggplot(data = R1[treatment == "replication"],
-       mapping = aes(x = ownContribution, fill = student, lty = student)) +
-  geom_density(alpha = 0.5) +
-  scale_x_continuous(limits = c(0, 20),
-                       expand = c(0, NA)) +
-  scale_y_continuous(limits = c(0, 0.1),
-                       expand = c(0, NA)) +
-  scale_fill_manual(values = c(cPrimary, cSecondary),
-                    labels = c("General Population Sample", "Student Sample")) +
-  guides(lty = "none") +
-  geom_vline(xintercept = R1[treatment == "replication", 
-                             mean(ownContribution)],
-             col = "#FFFFFF",
-             lty = 2) +
-  geom_vline(xintercept = R1[treatment == "noPunish10", 
-                             mean(ownContribution)],
-             col = "#FFFFFF",
-             lty = 1) +
-    labs(title = "", 
-       y = "", x = "Initially Contributed Tokens") +
-  layout +
-  theme(legend.position = "top")
-```
-
-```{r stockDistributionVizAppendix}
-
-populationWealth <- main[treatment == "replication" & student == FALSE & round == 10,
-                         mean(stock)]
-studentWealth    <- main[treatment == "replication" & student == TRUE & round == 10,
-                         mean(stock)]
-
-d2 <- ggplot(data = main[treatment == "replication"],
-       mapping = aes(x = stock, fill = student, lty = student)) +
-  geom_density(alpha = 0.5) +
-  scale_x_continuous(limits = c(0, NA),
-                       expand = c(0, NA)) +
-  scale_y_continuous(limits = c(0, NA),
-                       expand = c(0, NA)) +
-  scale_fill_manual(values = c(cPrimary, cSecondary),
-                    labels = c("General Population Sample", "Student Sample")) +
-  guides(lty = "none") +
-  geom_vline(xintercept = studentWealth,
-             col = "#000000", alpha = 0.5,
-             lty = 2) +
-  geom_vline(xintercept = populationWealth,
-             col = "#000000", alpha = 0.5,
-             lty = 1) +
-    labs(title = "", 
-       y = "", x = "Stock") +
-  layout +
-  theme(legend.position = "top")
-```
-
-```{r giniDistributionVizAppendix}
-
-populationGini    <- main[treatment == "replication" & student == FALSE & round == 10,
-                        mean(gini)] %>% round(digits = 2)
-studentGini <- main[treatment == "replication" & student == TRUE & round == 10,
-                        mean(gini)] %>% round(digits = 2)
-
-d3 <- ggplot(data = main[treatment == "replication"],
-       mapping = aes(x = gini, fill = student, lty = student)) +
-  geom_density(alpha = 0.5) +
-  scale_x_continuous(limits = c(0, 1),
-                       expand = c(0, NA)) +
-  scale_y_continuous(limits = c(0, NA),
-                       expand = c(0, NA)) +
-  scale_fill_manual(values = c(cPrimary, cSecondary),
-                    labels = c("General Population Sample", "Student Sample")) +
-  guides(lty = "none") +
-  geom_vline(xintercept = studentGini,
-             col = "#000000", alpha = 0.5,
-             lty = 2) +
-  geom_vline(xintercept = populationGini,
-             col = "#000000", alpha = 0.5,
-             lty = 1) +
-    labs(title = "", 
-       y = "", x = "Gini Coefficient") +
-  layout +
-  theme(legend.position = "top")
-```
-
-```{r assembleAppendixPlots}
-#| fig-cap: Kernel Density Plots
-#| label: fig-multiple-distributions
-
-patchwork <- d1 + d2 + d3 + plot_layout(guides = "collect") &  theme(legend.position = "top") 
-patchwork + plot_annotation(caption = "Vertical lines indicate means (dashed line = student sample).")
-```
-
-```{r plotContributionsAppendix}
-#| include: false
-
-SUM <- main[treatment == "replication",
-            lapply(.SD, mean, na.rm = TRUE),
-            by = c("round", "student"),
-            .SDcols = "contribution"]
-
-SUM[,
-    sum := round(contribution)]
-
-SUM[,
-    contribution := contribution/4]
-
-upperLimit <- SUM$contribution %>% max() %>% round() + 5
-
-p1 <- ggplot(data = SUM, 
-             aes(x = round, y = contribution, fill = student, color = student, lty = student)) +
-  layout +
-  theme(legend.position="top") +
-  geom_line(show.legend=FALSE) +
-  geom_point() +
-  scale_x_continuous(name="",  breaks = 1:15) +
-  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-  labs(y = "Average Amount of Tokens contributed") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("General Population Sample", "Student Sample")) + 
-  guides(fill = "none") +
-  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
-
-rm(list = c("SUM"))
-```
-
-```{r plotShareOfContributionsAppendix}
-#| fig.cap: "The average amount of tokens contributed over time in treatments."
-#| include: false
-
-SHARE <- main[treatment == "replication",
-            lapply(.SD, mean, na.rm = TRUE),
-            by = c("round", "student"),
-            .SDcols = "share"]
-
-# SHARE <- main[,
-#             .(share = sum(contribution)/sum(endowment)),
-#             by = c("round", "treatment")]
-
-upperLimit <- 0.75
-
-p2 <- ggplot(data = SHARE, 
-             aes(x = round, y = share, fill = student, color = student, lty = student)) +
-  layout +
-  theme(legend.position="bottom") +
-  geom_line(show.legend=FALSE) +
-  geom_point() +
-  scale_x_continuous(name="",  breaks = 1:15) +
-  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-  labs(y = "Share of Current Endowment contributed") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("General Population Sample", "Student Sample")) +
-  guides(fill = "none")
-
-p1 + p2 + plot_layout(guides = "collect") & 
-  theme(legend.position = "top")
-
-# rm(list = c("p1", "p2"))
-```
-
-```{r plotStockAppendix}
-#| include: false
-
-# data
-STOCK <- main[treatment == "replication",
-              lapply(.SD, mean, na.rm = TRUE),
-              by = c("round", "student"),
-              .SDcols = "stock"]
-
-# annotation
-maxPath <- data.table(x = 1:10)
-maxPath[, y := 80*1.5^x]
-maxPath[, student := "replication"]
-maxPath[, groupID := 42]
-
-# plot
-p1 <- ggplot(data = STOCK, 
-             aes(x = round, y = stock, fill = student, color = student, lty = student)) +
-  geom_line() +
-  geom_point() +
-  scale_x_continuous(breaks = 1:10) +
-  scale_y_continuous(limits = c(0, 4700), expand = c(0, 0)) +
-  labs(y = "Wealth", x = "Period") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("General Population Sample", "Student Sample")) +
-  geom_point(mapping = aes(x = 10, y = 4613), col = "#b5b5b5") +
-  annotate("text", x = 9, y = 4630, size = 3,
-           label = "max", col = "#b5b5b5") +
-  geom_line(data = maxPath, mapping = aes(x = x, y = y), col = "#b5b5b5", lty = 2) +
-  guides(fill = "none") +
-  layout +
-  theme(legend.position = "top") +
-  guides(lty = "none")
-```
-
-```{r growthHeterogeneityVizAppendix}
-#| fig.cap: Average wealth over time across samples.
-#| include: false
-
-# plot
-p2 <- ggplot(data = main[treatment == "replication"],
-       mapping = aes(x = round, y = stock, color = student, by = groupID)) +
-  geom_line(alpha = 0.5) +
-  scale_x_continuous(breaks = 1:10) +
-  scale_y_continuous(limits = c(0, 2000),
-                       expand = c(0, NA)) +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("General Population Sample", "Student Sample")) +
-  labs(y = "", x = "Period") +
-  layout +
-  guides(col = "none")
-
-# assembling
-p1 + p2 + plot_layout(guides = "collect") & theme(legend.position = "top")
-```
-
-```{r}
-#| fig.cap: Average Gini coefficient (within groups) over time across samples
-#| include: false
-
-tmp <- main[treatment == "replication",
-            lapply(.SD, mean, na.rm = TRUE),
-            by = c("round", "student"),
-            .SDcols = "gini"]
-
-GINI <- rbind(tmp, list(0, TRUE, 0), list(0, FALSE, 0))
-
-ggplot(data = GINI, 
-             aes(x = round, y = gini, fill = student, color = student, lty = student)) +
-  geom_line() +
-  geom_point() +
-  scale_x_continuous(breaks = 0:10) +
-  scale_y_continuous(limits = c(0, 0.25), expand = c(0, 0)) +
-  labs(y = "Wealth", x = "Period") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("General Population Sample", "Student Sample")) +
-  guides(fill = "none") +
-  layout +
-  theme(legend.position = "top") +
-  guides(lty = "none")
-```
-
-# C: Growth _and_ Inequality (exploratory) {.appendix}
-
-In contrast to GMTV, I did not ask how rich and poor groups differ.
-Instead, I was wondering, whether equal groups are wealthier.
-More precisely, does the Gini coefficient correlate with growth and wealth creation?
-To answer that question, @fig-stock-by-gini applies a median split showing equal and unequal groups' wealth over time.
-
-```{r plotStockByGini}
-#| fig-cap: Average wealth over time across treatments.
-#| label: fig-stock-by-gini
-
-# create equality indicator (just as highgdp in original data)
-median <- main[round == 10,
-               median(gini)]
-
-equalGroups <- main[round == 10 & gini > median,
-                    unique(groupID)]
-
-unequalGroups <- main[round == 10 & gini < median,
-                      unique(groupID)]
-
-main[groupID %in% equalGroups,
-     equal := TRUE]
-
-main[groupID %in% unequalGroups,
-     equal := FALSE]
-
-STOCKe <- main[equal == TRUE,
-               lapply(.SD, mean, na.rm = TRUE),
-               by = c("round", "treatment"),
-               .SDcols = "stock"]
-
-STOCKu <- main[equal == FALSE,
-               lapply(.SD, mean, na.rm = TRUE),
-               by = c("round", "treatment"),
-               .SDcols = "stock"]
-
-upperLimit <- 700
-
-p1 <- ggplot(data = STOCKe, 
-             aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
-  layout +
-  theme(legend.position="bottom") +
-  # geom_vline(xintercept = 10, alpha = 0.66) +
-  geom_line() +
-  geom_point() +
-  guides(lty = "none", fill = "none") +
-  scale_x_continuous(name="",  breaks = 1:10) +
-  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-  labs(y = "Wealth (Equality)", x = "Period") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("Original Sample", "Reproduction Sample"))
-
-p2 <- ggplot(data = STOCKu, 
-             aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
-  layout +
-  theme(legend.position="bottom") +
-  # geom_vline(xintercept = 10, alpha = 0.66) +
-  geom_line() +
-  geom_point() +
-  guides(lty = "none", fill = "none") +
-  scale_x_continuous(name="",  breaks = 1:10) +
-  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-  labs(y = "Wealth (Inequality)", x = "Period") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("Original Sample", "Reproduction Sample"))
-
-p1 + p2 + plot_layout(guides = "collect") & theme(legend.position = "bottom")
-
-rm(list = c("STOCKe", "STOCKu", "p1", "p2"))
-```
--->

### 2023-05-24 analysis/quarto/paper.qmd
incorporate another set of comments and calculate overall page times for cost estimation

@@
 abstract: |
-  I revisit the dynamic public goods game by Gächter et al.
-(2017) developed to study cooperation under dynamic interdependencies.
+  I revisit the dynamic public goods game developed by Gächter et al.
+(2017) to study cooperation under dynamic interdependencies.
 Collecting data from both a convenient (students) and an inconvenient (general population) sample, I not only reproduce some of the author's original observations but also test their novel game's generalizability.
@@
 
-Public good (or public bad) games---although often intended to inform climate policies (e.g.
-@MilinskiEtAl2006, @TavoniEtAl2011, @Hauser2014, @BrickEtAl2015, @GomezEtAl2018, @CalzolariEtAl2018, @CookEtAl2019)---miss these temporal interdependencies simply because participants have the same set of actions in each period.
+Public good (or public bad) games---although often intended to inform climate policies [e.g.
+@MilinskiEtAl2006; @TavoniEtAl2011; @Hauser2014; @BrickEtAl2015; @GomezEtAl2018; @CalzolariEtAl2018; @CookEtAl2019]---miss these temporal interdependencies simply because participants have the same set of actions in each period.
 Accordingly, participants' actions in a given period do not affect their action space in subsequent periods.
@@
 A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017 hereafter, GMTV] as well as Stefan Große (2011, unpublished) shows that it is fairly simple to remedy that limitation.
-They incorporated interdependencies into a _dynamic_ public goods game by defining endowments as the income of previous periods.
+They incorporated interdependencies into a _dynamic_ public goods game (dPGG) by defining endowments as the income of previous periods.
 To put it differently, participants' actions in a given period affect their number of actions in subsequent periods: the more (less) they earn now, the more (less) they can contribute in the next period.
@@
 @AGM2018 conducted static public goods games in the lab and on MTurk to draw lessons from online experimentation.
-This study extends this literature [see @GoodmanPaolacci2017; also  @AmirEtAl2012] by focusing on an _inconvenient_ sample (i.e.
+This study extends this literature [see, e.g., @SnowbergYariv_2021; @GuptaRigottiWilson_2021; @GoodmanPaolacci2017; @AmirEtAl2012] by focusing on an _inconvenient_ sample (i.e.
 one that is completely inexperienced sample that has not been exposed to interactive experiments before) playing a computationally more complex game.
@@
 Today, researchers can not only choose where to pre-register but also decide about the level of detail they provide.
-More severely, nothing stops researchers from pre-registering multiple hypotheses opposing each other (see, e.g., @SimmonsEtAl2021 and @PhamEtAl2021 for a discussion).
+More severely, nothing stops researchers from pre-registering multiple hypotheses opposing each other [see, e.g., @SimmonsEtAl2021; and @PhamEtAl2021 for a discussion].
 
@@
 The analysis was pre-registered in the American Economic Association's RCT Registry [@preregistration].
-Further, I pre-registered the exact analyses I planned to run when I designed the experiment on [GitHub](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.]
+Further, I pre-registered the exact analyses I planned to run when I designed the experiment on [GitHub](https://shorturl.at/bAGKY).^[https://shorturl.at/bAGKY to run the code, you need to execute the .Rmd files in this repository in the order that is indicated by file names.]
 
@@
 
-Accordingly, I  changed many of the analysis scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd] However, because the originally planned analysis code is archived and reproducible, these changes are transparent.
+Accordingly, I edited many of the analyses scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://shorturl.at/ilpAG] However, because the originally planned analysis code is archived and reproducible, these changes are transparent.
 Importantly, I followed a literate programming approach [@Knuth_1984; @AkhtarYe_2023].
@@
 
-**Result 3.** _There is no significant correlation between average contributions in the abstract public goods game and contributions to the real public good of climate change mitigation._
+**Result 3.** _There is no significant correlation between average contributions in the abstract public goods game and contributions to the real public good of climate change mitigation---for none of the samples._
 

### 2023-05-24 analysis/quarto/paper.tex
incorporate another set of comments and calculate overall page times for cost estimation

@@
 \begin{abstract}
-I revisit the dynamic public goods game by Gächter et al.~(2017)
-developed to study cooperation under dynamic interdependencies.
+I revisit the dynamic public goods game developed by Gächter et
+al.~(2017) to study cooperation under dynamic interdependencies.
 Collecting data from both a convenient (students) and an inconvenient
@@
 \end{keyword}
-\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, breakable, interior hidden, boxrule=0pt, enhanced, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi
+\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable, boxrule=0pt, interior hidden, sharp corners, frame hidden]}{\end{tcolorbox}}\fi
 
@@
 Public good (or public bad) games---although often intended to inform
-climate policies (e.g. \citet{MilinskiEtAl2006}, \citet{TavoniEtAl2011},
-\citet{Hauser2014}, \citet{BrickEtAl2015}, \citet{GomezEtAl2018},
-\citet{CalzolariEtAl2018}, \citet{CookEtAl2019})---miss these temporal
-interdependencies simply because participants have the same set of
-actions in each period. Accordingly, participants' actions in a given
-period do not affect their action space in subsequent periods. To see
-the lack of realism, consider carbon dioxide emissions, where the
-current stock will last for well over a millennium
+climate policies
+\citep[e.g.][]{MilinskiEtAl2006, TavoniEtAl2011, Hauser2014, BrickEtAl2015, GomezEtAl2018, CalzolariEtAl2018, CookEtAl2019}---miss
+these temporal interdependencies simply because participants have the
+same set of actions in each period. Accordingly, participants' actions
+in a given period do not affect their action space in subsequent
+periods. To see the lack of realism, consider carbon dioxide emissions,
+where the current stock will last for well over a millennium
 \citep{Inman2008, CalzolariEtAl2018}. Playing with fresh endowments in
@@
 incorporated interdependencies into a \emph{dynamic} public goods game
-by defining endowments as the income of previous periods. To put it
-differently, participants' actions in a given period affect their number
-of actions in subsequent periods: the more (less) they earn now, the
-more (less) they can contribute in the next period. Importantly, this
-modification qualitatively yields the same rational predictions as the
-static game (i.e.~free-riding and the under-provision of the public
+(dPGG) by defining endowments as the income of previous periods. To put
+it differently, participants' actions in a given period affect their
+number of actions in subsequent periods: the more (less) they earn now,
+the more (less) they can contribute in the next period. Importantly,
+this modification qualitatively yields the same rational predictions as
+the static game (i.e.~free-riding and the under-provision of the public
 good). It is thus, equally well suited to study dilemma situations.
@@
 MTurk to draw lessons from online experimentation. This study extends
-this literature
-\citetext{\citealp[see][]{GoodmanPaolacci2017}; \citealp[also][]{AmirEtAl2012}}
+this literature \citep[see,
+e.g.,][]{SnowbergYariv_2021, GuptaRigottiWilson_2021, GoodmanPaolacci2017, AmirEtAl2012}
 by focusing on an \emph{inconvenient} sample (i.e.~one that is
@@
 researchers from pre-registering multiple hypotheses opposing each other
-(see, e.g., \citet{SimmonsEtAl2021} and \citet{PhamEtAl2021} for a
-discussion).
+\citetext{\citealp[see, e.g.,][]{SimmonsEtAl2021}; \citealp[and][ for a
+discussion]{PhamEtAl2021}}.
 
@@
 planned to run when I designed the experiment on
-\href{https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd}{GitHub}.\footnote{https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd
-  to run the code, you need to executed the .Rmd files in this
-  repository in the order that is indicated by its file names.}
+\href{https://shorturl.at/bAGKY}{GitHub}.\footnote{https://shorturl.at/bAGKY
+  to run the code, you need to execute the .Rmd files in this repository
+  in the order that is indicated by file names.}
 
@@
 
-Accordingly, I changed many of the analysis scripts.\footnote{The source
+Accordingly, I edited many of the analyses scripts.\footnote{The source
   code of this document contains the analysis and can be found
   \href{https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}{here}:
-  https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}
-However, because the originally planned analysis code is archived and
-reproducible, these changes are transparent. Importantly, I followed a
-literate programming approach \citep{Knuth_1984, AkhtarYe_2023}. Hence,
-all documents needed to analyze the data and to write the report stem
-from the same source. This establishes consistence between the commands
-one tells the statistical software to do and the explanation one tells
-human beings one told the statistical software to do. As such, (a), (b)
-and the transition from (a) to (b) are not only transparent but also
-comprehensible.
+  https://shorturl.at/ilpAG} However, because the originally planned
+analysis code is archived and reproducible, these changes are
+transparent. Importantly, I followed a literate programming approach
+\citep{Knuth_1984, AkhtarYe_2023}. Hence, all documents needed to
+analyze the data and to write the report stem from the same source. This
+establishes consistence between the commands one tells the statistical
+software to do and the explanation one tells human beings one told the
+statistical software to do. As such, (a), (b) and the transition from
+(a) to (b) are not only transparent but also comprehensible.
 
@@
 average contributions in the abstract public goods game and
-contributions to the real public good of climate change mitigation.}
+contributions to the real public good of climate change mitigation---for
+none of the samples.}
 

### 2023-06-12 analysis/quarto/paper.qmd
June2023 State

@@
 (2017) to study cooperation under dynamic interdependencies.
-Collecting data from both a convenient (students) and an inconvenient (general population) sample, I not only reproduce some of the author's original observations but also test their novel game's generalizability.
+Collecting data from both a convenient (students) and an inconvenient (general population) sample, I not only reproduce some of the authors' original observations but also test their novel game's generalizability.
 Appending a charitable dictator game, I find no correlations between behavior in the charitable context and the dynamic game.
 This applies to students and the general population sample alike.
-Because the study of inexperiend general population samples raises methodological challenges, such as fatigue and dropouts, this research approaches them.
-Doing so, I provide simple solutions to run relieable interactive experiments online.
-
-  You can find the most recent version of this paper [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.pdf).
+Because the study of inexperienced general population samples raises methodological challenges, such as fatigue and dropouts, this research approaches them.
+Doing so, I provide simple solutions to run reliable interactive experiments online.
+
 keywords: 
-  - Replication study
-  - Non-convenience sample
-  - Open science
-  - Dynamic public goods game
-  - Online experiment
+  - Public goods
+  - Dynamic games
+  - Reproducibility
   - Generalizability
+  - Online Experiment
+  - Climate change mitigation
 date: last-modified
@@
       name: Journal of Behavioral and Experimental Economics
-      formatting: preprint
+      formatting: review
       model: 3p
+      layout: onecolumn
       cite-style: authoryear
+      highlights:
+        - Highlight 1
+        - Highlight 2 
+        - Highlight 3
 ---
@@
 
-Today's actions are tomorrow's result.
-There are many settings in which current decisions affect future outcomes and with it, future decision spaces.
+Today's actions are tomorrow's result. There are many settings in which current decisions affect future outcomes and with it, future decision spaces. 
+<!-- Think of lifetime consumption‐smoothing and save more tomorrow -->
 Opting for environmental friendly policies today not only reduces carbon dioxide omissions immediately but also helps us to reach the Paris climate targets tomorrow.
-Deferring these policies, may not necessarily prevent us from reaching these targets, but it requires more effort in the future compared to a path that includes immediate action.
+Deferring these policies, may not necessarily prevent us from reaching these targets, but it requires more effort in the future compared to a path that includes immediate action @HaenselEtAl2022.
 Aiming at certain goals, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of paths one can choose from that lead to that specific goal.
@@
 
-A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017 hereafter, GMTV] as well as Stefan Große (2011, unpublished) shows that it is fairly simple to remedy that limitation.
-They incorporated interdependencies into a _dynamic_ public goods game (dPGG) by defining endowments as the income of previous periods.
-To put it differently, participants' actions in a given period affect their number of actions in subsequent periods: the more (less) they earn now, the more (less) they can contribute in the next period.
+A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017 hereafter, GMTV] as well as Stefan Große (unpublished) shows that it is fairly simple to add this element of realism.
+They incorporate interdependencies into a _dynamic_ public goods game (dPGG) by defining endowments as the income of previous periods.
+Consequently, participants' actions in a given period affect their number of actions in subsequent periods: the more (less) they earn now, the more (less) they can contribute in the next period.
 Importantly, this modification qualitatively yields the same rational predictions as the static game (i.e.
@@
 
-Because there is surprisingly little experimental research on interdependencies^[One exemption are @Moser2019, who built on GMTV's design to investigate leadership.], I reproduced one of GMTV's treatments to compare dynamics across (in)experienced samples to investigate its generalizability.
+Because there is surprisingly little experimental research on interdependencies^[One exemption are @Moser2019, who built on GMTVs' design to investigate leadership.], I reproduced one of GMTVs' treatments to compare dynamics across (in)experienced samples to investigate its generalizability.
 @GKLS2020 find that static public goods games do not generalize well to real-world climate action.
 They also find that generalizability depends on structural resemblance of the public goods game with the context of climate change mitigation: Greater resemblance improves generalizability.
-Because GMTV's dynamic setting has a more realistic property—namely, interdependencies—one would expect it to be better suited to inform public policy.
+Because GMTVs' dynamic setting has a more realistic property—namely, interdependencies—one would expect it to be better suited to inform public policy.
 To test this intuition, I not only ran the experiment with different samples but also
@@
 @EckelGrossman1996 were the first to implement a charitable dictator game observing contributions of 30% of the endowments.
-Like @GKLS2020, @CarpenterEtAl2008 report that students make lower contributions to charity than community members.] This yielded a setting similar to @GKLS2020's which allows me to analyze how behavior in the abstract game translates into real-world action across samples.
+Like @GKLS2020, @CarpenterEtAl2008 report that students make lower contributions to charity than community members.] This yielded a setting similar to the one of @GKLS2020, which allows me to analyze how behavior in the abstract game translates into real-world action across samples.
 This research shows that the dynamic setting _does not_ add any advances with respect to generalizability of results.
 
-@AGM2018 conducted static public goods games in the lab and on MTurk to draw lessons from online experimentation.
+@AGM2018 conducted static public goods games in the lab and on MTurk to draw (and report) lessons from online experimentation.
 This study extends this literature [see, e.g., @SnowbergYariv_2021; @GuptaRigottiWilson_2021; @GoodmanPaolacci2017; @AmirEtAl2012] by focusing on an _inconvenient_ sample (i.e.
@@
 This required me to design a robust (and thus, more complex) software to minimize attrition.
-I collected paradata to assess the desired fluency and feasibility of the experiment.
-This research reports on the robust design that made the dynamic game feasible.
+I collected paradata---which captures screen time and survey navigation, for instance---to assess the desired fluency and feasibility of the experiment.
+Like @AGM2018, this research is of practical relevance as it reports on the robust design that made the dynamic game feasible.
 
 Taken together, this study makes three contributions.
-First, it reproduces parts of GMTV's original experiment and highlights the importance of pure replications.
+First, it reproduces parts of GMTVs' original experiment and highlights the importance of pure replications.
 Second, it shows that logistically complex online experiments are feasible for samples other than students or clickworkers.
@@
 @sec-conclusion concludes.
-Because I observed some differences in reproducing GMTV's analysis using their data, I report these in the [Appendix](@sec-appendix).
+Because I observed some (qualitatively inconsequential) differences in reproducing GMTVs' analysis using their data, I report these in the [Appendix](@sec-appendix).
 
@@
 
-In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific_ reproduction^[@Parsons2022 use the term of a _conceptual replication_ which means the same.] of one treatment of GMTV's dynamic public goods game.
+In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific_ reproduction^[@Parsons2022 use the term of a _conceptual replication_ which means the same.] of one treatment of GMTVs' dynamic public goods game.
 The pure reproduction re-analyzes the original data.
@@
 
-Considering the design, the only differences between such a _static_ game (with partner matching) and GMTV's design are _dynamics_: Instead of receiving fresh endowments every period, participants receive one endowment only at the beginning of the first period.
+Considering the design, the only differences between such a _static_ game (with partner matching) and GMTVs' design are _dynamics_: Instead of receiving fresh endowments every period, participants receive one endowment only at the beginning of the first period.
 A participant's endowment in the second period is the wealth she accumulated in the first period.
@@
 Specifically, I employed a (charitable) dictator game where each participant is a dictator dividing her budget between herself and some organization.
-Whereas GMTV chose _Doctors without Borders_ as a receiver, I chose another organization in another context: like @GKLS2020, I employed a VCA, where participants could donate any amount their earnings to offset carbon dioxide (that is, retire emission permits from the EU ETS).^[Importantly, @GKLS2020 made the VCA decision with a fresh endowment _before_ they played the abstract game.
-I deviate from their procedure to match GMTV's procedure.]
+Whereas GMTV chose _Doctors without Borders_ as a receiver, I chose another organization in another context: like @GKLS2020, I employed a VCA, where participants could donate any amount of their earnings to offset carbon dioxide (that is, retire emission permits from the EU ETS).^[Importantly, @GKLS2020 made the VCA decision with a fresh endowment _before_ they played the abstract game.
+I deviate from their procedure to match GMTVs' procedure.]
 To ensure that each participant had the same basic level of information about the impact of their decision, I provided some basic information about the mechanism.
@@
 
-Throughout this paper, I will compare results of my experiment with the results of GMTV's NOPUNISH 10 Period treatments.
+Throughout this paper, I will compare results of my experiment with the results of GMTVs' NOPUNISH 10 Period treatments.
 I am thus, referring to three different samples utilized at two points in time: the University of Nottingham's students (in late 2012), Hamburg's citizens and the University Hamburg's students (both in July 2021).
@@
                  digits = 2,
-                 labels = c('Age', 'Female', 'Switching Row'),
+                 labels = c('Age', 'Female', 'Risk Aversion (1-12)'),
                  # note = "Switching Row describes choices in a multiple price list to elicit risk preferences.
@@
 At the end of the last period, participants saw results of all periods.
-Subsequently, they made their VCA decision, before I elicited risk preferences [@HoltLaury2002] and finished with GMTV's questionnaire.
-
-While I stuck to GMTV's protocol as close as possible, I deviated in a few aspects.
+Subsequently, they made their VCA decision, before I elicited risk preferences [@HoltLaury2002] and finished with GMTVs' questionnaire.
+
+While I stuck to GMTVs' protocol as close as possible, I deviated in a few aspects.
 First, the instructions were German and also covered topics inherent to the online setting (dropouts and bots, for instance).
@@
                    exact = FALSE)$p.value %>% 
-  round(digits = 4) %>% 
+  round(digits = 3) %>% 
   formatC(format = "f", 
-          digits = 4)
+          digits = 3)
 ```
@@
 ```{r}
-for(r in 1:10){
-  a <- main[round == r & treatment == 'replication', share]
-  b <- main[round == r & treatment == 'noPunish10', share]
-
-  wilcox.test(a, 
-              b,
-              exact = FALSE)$p.value %>% 
-    round(digits = 4) %>% 
-    formatC(format = "f", 
-            digits = 4)# %>%
-    # print()
-  }
-
 r <- 5
@@
 ```{r plotShareOfContributions}
-#| fig-cap: "The average amount of tokens contributed over time in treatments."
+#| fig-cap: "The average amount of tokens contributed over time across samples."
 #| label: fig-share-of-contributions
@@
                    exact = FALSE)$p.value %>% 
-  round(digits = 4) %>% 
+  round(digits = 3) %>% 
   formatC(format = "f", 
-          digits = 4)
+          digits = 3)
 
@@
 
-Although there clearly is growth, groups do not realize the maximal potential efficiency: under full cooperation, a group can accumulate at least `r (80*1.5^10) %>% trunc()` tokens or EUR `r (80*1.5^10 /20) %>% trunc()`.
+Although there clearly is growth, groups do not realize the maximal potential efficiency: under full cooperation, a group can accumulate at maximum `r (80*1.5^10) %>% trunc()` tokens or EUR `r (80*1.5^10 /20) %>% trunc()`.
 This is depicted in the left panel of @fig-growth-heterogeneity, where one can see the average wealth over time by sample.
@@
 
-Throughout this section, I do not consider GMTV's data and pool data I gathered from the citizens as well as the students from Hamburg (N = `r N`).
+Throughout this section, I do not consider GMTVs' data and pool data I gathered from the citizens as well as the students from Hamburg (N = `r N`).
 
@@
 There is some behavioral data supporting this finding: The user interface offered a popup to review instructions or contact information.
-I tracked both and find that none of the participants ever opened these popups even though they were clearly visible in the decision screen's header and introduced in the instructions.
+I tracked both and find that none of the participants ever opened these popups even though they were clearly visible in the decision screens' header and introduced in the instructions.
 To further analyze how participants coped with the situation, I consider three additional metrics: selection into the experiment, attrition as well as the time spent on each page.
@@
 @GKLS2020 asked how much can we learn about voluntary climate action from the behavior in public goods games.
-Using a similar strategy, I answer the question for a _dynamic_ public goods game: _Not much_.
+Using a similar strategy, I answer the question for a _dynamic_ public goods game: _Not too much_.
 Overall, there seems to be no association between choices in the voluntary climate action and the first period in the dynamic public goods game.
@@
 A visual inspection shows that (a) mean contributions are positive in both tasks for both samples.^[The same holds true for median contributions.] (b) Furthermore, average contributions are lower in the VCA.
-(c) In contrast to @GKLS2020's observation, I do not observe a difference between samples in the abstract game's contribution behavior.
+(c) In contrast to the observation of @GKLS2020, I do not observe a difference between samples in the abstract game's contribution behavior.
 (d) However, the student's share of income contributed to the VCA is significantly lower than the general population sample's contributions (two-sided rank sum test, p=`r rs1`).
@@
 The initial goal of the experiment was to reproduce specific experiments of GMTV in an online setting using a general population sample. 
-The results suggest that it is important to reproduce experiments---both purely and scientifically [@Hamermesh2007 p.
-716]---before drawing conclusions about generalizability.
-
+<!--The results suggest that it is important to reproduce experiments---both purely and scientifically [@Hamermesh2007 p. 716]---before drawing conclusions about generalizability.
+-->
 The three most important findings are as follows: First, the contribution behavior in my experiment is statistically similar to the behavior reported in the original study.
-Consequently, the outcomes growth and inequality are reproducible.
+Consequently, the outcomes growth and inequality are reproducible in both meanings: they are _purely_ (despite minor differences one can re-analyze the original data and reach the same conclusions) and _scientifically_ (one can gather new data drawn from a different population in a different situation and find similar patterns) reproducible.
 Second, the online experiment proceeded fluently such that dropouts were no concern.
@@
 
-Limitations?
+Taken together the results answer the questions whether GMTVs' dynamic paradigm is reproducible  across samples (yes) and whether it is feasible employ it online (also yes).
+The question that is _not_ answered is, whether GMTVs' treatment effects replicate well because I did not focus on treatments and treatment effects.
+It thus, remains an open question, whether the causal effect of GMTVs' treatments replicate well.
+Further, we do not know whether their treatments affect real-world behavior.
+How generalizable are treatment effects in public goods games in general?
+Albeit this study does not address these questions, it provides methods suited to investigate them---even with inconvenient samples.
+
+# Acknowledgements
+
+I gratefully acknowledge support by the German Research Foundation (DFG) under Germany’s Excellence Strategy, cluster EXC 2037 “Climate, Climatic Change, and Society” (project 390683824).
+I thank Stefan Traub and participants of the CLICCS B5 group for helpful discussions.
 
@@
 
-<!--
-# B: TITLE (exploratory) {.appendix}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Donec suscipit eleifend felis et faucibus.
-Curabitur nisl risus, tincidunt ut hendrerit sed, sollicitudin eget tortor.
-Curabitur tortor elit, finibus a commodo eget, auctor vel dui.
-Ut convallis, felis in commodo bibendum, ligula neque hendrerit eros, eu eleifend libero ligula pretium dui.
-Nullam blandit a tellus vitae suscipit.
-Donec ac justo vehicula elit tincidunt mollis nec ac lectus.
-Nunc dignissim sem eu felis consequat, id euismod ante imperdiet.
-Mauris quis ex ante.
-
-Nulla elementum laoreet libero nec consequat.
-Donec blandit, tellus id feugiat viverra, lectus tellus sollicitudin ipsum, ut venenatis nunc mauris ut arcu.
-Donec mi eros, ullamcorper aliquet varius non, cursus vel lorem.
-Integer feugiat dui sapien, ac porta lacus porta sit amet.
-Aliquam interdum dictum tempor.
-Quisque bibendum feugiat scelerisque.
-Sed eu purus eu est ullamcorper bibendum.
-
-Donec efficitur magna malesuada tortor feugiat tristique.
-Sed porttitor, quam at vulputate placerat, elit magna posuere est, a eleifend lacus magna ac nunc.
-Quisque sit amet arcu mattis, malesuada mauris et, aliquam libero.
-Fusce viverra sed dolor a ullamcorper.
-Aliquam in ligula neque.
-In maximus nisl id ante vehicula, et euismod ante feugiat.
-Suspendisse et dui lectus.
-Ut euismod ultrices mi eu lacinia.
-
-```{r firstRoundVizAppendix}
-
-d1 <- ggplot(data = R1[treatment == "replication"],
-       mapping = aes(x = ownContribution, fill = student, lty = student)) +
-  geom_density(alpha = 0.5) +
-  scale_x_continuous(limits = c(0, 20),
-                       expand = c(0, NA)) +
-  scale_y_continuous(limits = c(0, 0.1),
-                       expand = c(0, NA)) +
-  scale_fill_manual(values = c(cPrimary, cSecondary),
-                    labels = c("General Population Sample", "Student Sample")) +
-  guides(lty = "none") +
-  geom_vline(xintercept = R1[treatment == "replication", 
-                             mean(ownContribution)],
-             col = "#FFFFFF",
-             lty = 2) +
-  geom_vline(xintercept = R1[treatment == "noPunish10", 
-                             mean(ownContribution)],
-             col = "#FFFFFF",
-             lty = 1) +
-    labs(title = "", 
-       y = "", x = "Initially Contributed Tokens") +
-  layout +
-  theme(legend.position = "top")
-```
-
-```{r stockDistributionVizAppendix}
-
-populationWealth <- main[treatment == "replication" & student == FALSE & round == 10,
-                         mean(stock)]
-studentWealth    <- main[treatment == "replication" & student == TRUE & round == 10,
-                         mean(stock)]
-
-d2 <- ggplot(data = main[treatment == "replication"],
-       mapping = aes(x = stock, fill = student, lty = student)) +
-  geom_density(alpha = 0.5) +
-  scale_x_continuous(limits = c(0, NA),
-                       expand = c(0, NA)) +
-  scale_y_continuous(limits = c(0, NA),
-                       expand = c(0, NA)) +
-  scale_fill_manual(values = c(cPrimary, cSecondary),
-                    labels = c("General Population Sample", "Student Sample")) +
-  guides(lty = "none") +
-  geom_vline(xintercept = studentWealth,
-             col = "#000000", alpha = 0.5,
-             lty = 2) +
-  geom_vline(xintercept = populationWealth,
-             col = "#000000", alpha = 0.5,
-             lty = 1) +
-    labs(title = "", 
-       y = "", x = "Stock") +
-  layout +
-  theme(legend.position = "top")
-```
-
-```{r giniDistributionVizAppendix}
-
-populationGini    <- main[treatment == "replication" & student == FALSE & round == 10,
-                        mean(gini)] %>% round(digits = 2)
-studentGini <- main[treatment == "replication" & student == TRUE & round == 10,
-                        mean(gini)] %>% round(digits = 2)
-
-d3 <- ggplot(data = main[treatment == "replication"],
-       mapping = aes(x = gini, fill = student, lty = student)) +
-  geom_density(alpha = 0.5) +
-  scale_x_continuous(limits = c(0, 1),
-                       expand = c(0, NA)) +
-  scale_y_continuous(limits = c(0, NA),
-                       expand = c(0, NA)) +
-  scale_fill_manual(values = c(cPrimary, cSecondary),
-                    labels = c("General Population Sample", "Student Sample")) +
-  guides(lty = "none") +
-  geom_vline(xintercept = studentGini,
-             col = "#000000", alpha = 0.5,
-             lty = 2) +
-  geom_vline(xintercept = populationGini,
-             col = "#000000", alpha = 0.5,
-             lty = 1) +
-    labs(title = "", 
-       y = "", x = "Gini Coefficient") +
-  layout +
-  theme(legend.position = "top")
-```
-
-```{r assembleAppendixPlots}
-#| fig-cap: Kernel Density Plots
-#| label: fig-multiple-distributions
-
-patchwork <- d1 + d2 + d3 + plot_layout(guides = "collect") &  theme(legend.position = "top") 
-patchwork + plot_annotation(caption = "Vertical lines indicate means (dashed line = student sample).")
-```
-
-```{r plotContributionsAppendix}
-#| include: false
-
-SUM <- main[treatment == "replication",
-            lapply(.SD, mean, na.rm = TRUE),
-            by = c("round", "student"),
-            .SDcols = "contribution"]
-
-SUM[,
-    sum := round(contribution)]
-
-SUM[,
-    contribution := contribution/4]
-
-upperLimit <- SUM$contribution %>% max() %>% round() + 5
-
-p1 <- ggplot(data = SUM, 
-             aes(x = round, y = contribution, fill = student, color = student, lty = student)) +
-  layout +
-  theme(legend.position="top") +
-  geom_line(show.legend=FALSE) +
-  geom_point() +
-  scale_x_continuous(name="",  breaks = 1:15) +
-  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-  labs(y = "Average Amount of Tokens contributed") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("General Population Sample", "Student Sample")) + 
-  guides(fill = "none") +
-  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
-
-rm(list = c("SUM"))
-```
-
-```{r plotShareOfContributionsAppendix}
-#| fig.cap: "The average amount of tokens contributed over time in treatments."
-#| include: false
-
-SHARE <- main[treatment == "replication",
-            lapply(.SD, mean, na.rm = TRUE),
-            by = c("round", "student"),
-            .SDcols = "share"]
-
-# SHARE <- main[,
-#             .(share = sum(contribution)/sum(endowment)),
-#             by = c("round", "treatment")]
-
-upperLimit <- 0.75
-
-p2 <- ggplot(data = SHARE, 
-             aes(x = round, y = share, fill = student, color = student, lty = student)) +
-  layout +
-  theme(legend.position="bottom") +
-  geom_line(show.legend=FALSE) +
-  geom_point() +
-  scale_x_continuous(name="",  breaks = 1:15) +
-  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-  labs(y = "Share of Current Endowment contributed") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("General Population Sample", "Student Sample")) +
-  guides(fill = "none")
-
-p1 + p2 + plot_layout(guides = "collect") & 
-  theme(legend.position = "top")
-
-# rm(list = c("p1", "p2"))
-```
-
-```{r plotStockAppendix}
-#| include: false
-
-# data
-STOCK <- main[treatment == "replication",
-              lapply(.SD, mean, na.rm = TRUE),
-              by = c("round", "student"),
-              .SDcols = "stock"]
-
-# annotation
-maxPath <- data.table(x = 1:10)
-maxPath[, y := 80*1.5^x]
-maxPath[, student := "replication"]
-maxPath[, groupID := 42]
-
-# plot
-p1 <- ggplot(data = STOCK, 
-             aes(x = round, y = stock, fill = student, color = student, lty = student)) +
-  geom_line() +
-  geom_point() +
-  scale_x_continuous(breaks = 1:10) +
-  scale_y_continuous(limits = c(0, 4700), expand = c(0, 0)) +
-  labs(y = "Wealth", x = "Period") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("General Population Sample", "Student Sample")) +
-  geom_point(mapping = aes(x = 10, y = 4613), col = "#b5b5b5") +
-  annotate("text", x = 9, y = 4630, size = 3,
-           label = "max", col = "#b5b5b5") +
-  geom_line(data = maxPath, mapping = aes(x = x, y = y), col = "#b5b5b5", lty = 2) +
-  guides(fill = "none") +
-  layout +
-  theme(legend.position = "top") +
-  guides(lty = "none")
-```
-
-```{r growthHeterogeneityVizAppendix}
-#| fig.cap: Average wealth over time across samples.
-#| include: false
-
-# plot
-p2 <- ggplot(data = main[treatment == "replication"],
-       mapping = aes(x = round, y = stock, color = student, by = groupID)) +
-  geom_line(alpha = 0.5) +
-  scale_x_continuous(breaks = 1:10) +
-  scale_y_continuous(limits = c(0, 2000),
-                       expand = c(0, NA)) +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("General Population Sample", "Student Sample")) +
-  labs(y = "", x = "Period") +
-  layout +
-  guides(col = "none")
-
-# assembling
-p1 + p2 + plot_layout(guides = "collect") & theme(legend.position = "top")
-```
+# B: Tables
 
 ```{r}
-#| fig.cap: Average Gini coefficient (within groups) over time across samples
-#| include: false
-
-tmp <- main[treatment == "replication",
-            lapply(.SD, mean, na.rm = TRUE),
-            by = c("round", "student"),
-            .SDcols = "gini"]
-
-GINI <- rbind(tmp, list(0, TRUE, 0), list(0, FALSE, 0))
-
-ggplot(data = GINI, 
-             aes(x = round, y = gini, fill = student, color = student, lty = student)) +
-  geom_line() +
-  geom_point() +
-  scale_x_continuous(breaks = 0:10) +
-  scale_y_continuous(limits = c(0, 0.25), expand = c(0, 0)) +
-  labs(y = "Wealth", x = "Period") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("General Population Sample", "Student Sample")) +
-  guides(fill = "none") +
-  layout +
-  theme(legend.position = "top") +
-  guides(lty = "none")
-```
-
-# C: Growth _and_ Inequality (exploratory) {.appendix}
-
-In contrast to GMTV, I did not ask how rich and poor groups differ.
-Instead, I was wondering, whether equal groups are wealthier.
-More precisely, does the Gini coefficient correlate with growth and wealth creation?
-To answer that question, @fig-stock-by-gini applies a median split showing equal and unequal groups' wealth over time.
-
-```{r plotStockByGini}
-#| fig-cap: Average wealth over time across treatments.
-#| label: fig-stock-by-gini
-
-# create equality indicator (just as highgdp in original data)
-median <- main[round == 10,
-               median(gini)]
-
-equalGroups <- main[round == 10 & gini > median,
-                    unique(groupID)]
-
-unequalGroups <- main[round == 10 & gini < median,
-                      unique(groupID)]
-
-main[groupID %in% equalGroups,
-     equal := TRUE]
-
-main[groupID %in% unequalGroups,
-     equal := FALSE]
-
-STOCKe <- main[equal == TRUE,
-               lapply(.SD, mean, na.rm = TRUE),
-               by = c("round", "treatment"),
-               .SDcols = "stock"]
-
-STOCKu <- main[equal == FALSE,
-               lapply(.SD, mean, na.rm = TRUE),
-               by = c("round", "treatment"),
-               .SDcols = "stock"]
-
-upperLimit <- 700
-
-p1 <- ggplot(data = STOCKe, 
-             aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
-  layout +
-  theme(legend.position="bottom") +
-  # geom_vline(xintercept = 10, alpha = 0.66) +
-  geom_line() +
-  geom_point() +
-  guides(lty = "none", fill = "none") +
-  scale_x_continuous(name="",  breaks = 1:10) +
-  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-  labs(y = "Wealth (Equality)", x = "Period") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("Original Sample", "Reproduction Sample"))
-
-p2 <- ggplot(data = STOCKu, 
-             aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
-  layout +
-  theme(legend.position="bottom") +
-  # geom_vline(xintercept = 10, alpha = 0.66) +
-  geom_line() +
-  geom_point() +
-  guides(lty = "none", fill = "none") +
-  scale_x_continuous(name="",  breaks = 1:10) +
-  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-  labs(y = "Wealth (Inequality)", x = "Period") +
-  scale_color_manual(values = c(cPrimary, cSecondary),
-                     labels = c("Original Sample", "Reproduction Sample"))
-
-p1 + p2 + plot_layout(guides = "collect") & theme(legend.position = "bottom")
-
-rm(list = c("STOCKe", "STOCKu", "p1", "p2"))
-```
--->
+#| label: tbl-contribution-periods
+#| tbl-cap: The average amount of tokens contributed over time across samples.
+
+p <- data.table(round = 1:10)
+for(r in 1:10){
+  a <- main[round == r & treatment == 'replication', contribution]
+  b <- main[round == r & treatment == 'noPunish10', contribution]
+
+  p[round == r, `p-value` := wilcox.test(a, b, exact = FALSE)$p.value %>% 
+      round(digits = 3) %>% 
+      formatC(format = "f", digits = 3)]
+}
+
+tmp <- main[, 
+            .(Mean = mean(contribution, na.rm = TRUE) %>% formatC(format = "f", digits = 3),
+              CI = t.test(contribution, conf.level = 0.95)$conf.int[c(1,2)] %>% formatC(format = "f", digits = 3) %>% paste(collapse = " - ")),
+            by = c('treatment', 'round')] %>%
+  data.table::dcast(formula = round ~ treatment,
+                    value.var = c('Mean', 'CI'))
+
+tmp <- tmp[, c(1,2,4,3,5)]
+
+tmp[p, on = .(round = round)] %>%
+  kable(col.names = c('Period', 
+                      'Mean: Original', '95%-CI: Original',
+                      'Mean: Reproduction', '95%-CI: Reproduction',
+                      'p-Value'))
+
+```
+
+```{r}
+#| label: tbl-share-periods
+#| tbl-cap: The average share of current endowments contributed over time across samples.
+
+p <- data.table(round = 1:10)
+for(r in 1:10){
+  a <- main[round == r & treatment == 'replication', share]
+  b <- main[round == r & treatment == 'noPunish10', share]
+
+  p[round == r, `p-value` := wilcox.test(a, b, exact = FALSE)$p.value %>% 
+      round(digits = 3) %>% 
+      formatC(format = "f", digits = 3)]
+}
+
+tmp <- main[, 
+            .(Mean = mean(share, na.rm = TRUE) %>% formatC(format = "f", digits = 3),
+              CI = t.test(share, conf.level = 0.95)$conf.int[c(1,2)] %>% formatC(format = "f", digits = 3) %>% paste(collapse = " - ")),
+            by = c('treatment', 'round')] %>%
+  data.table::dcast(formula = round ~ treatment,
+                    value.var = c('Mean', 'CI'))
+
+tmp <- tmp[, c(1,2,4,3,5)]
+
+tmp[p, on = .(round = round)] %>%
+  kable(col.names = c('Period', 
+                      'Mean: Original', '95%-CI: Original',
+                      'Mean: Reproduction', '95%-CI: Reproduction',
+                      'p-Value'))
+
+```
+
+```{r}
+#| label: tbl-wealth-periods
+#| tbl-cap: The average wealth over time across samples.
+
+p <- data.table(round = 1:10)
+for(r in 1:10){
+  a <- main[round == r & treatment == 'replication', stock]
+  b <- main[round == r & treatment == 'noPunish10', stock]
+
+  p[round == r, `p-value` := wilcox.test(a, b, exact = FALSE)$p.value %>% 
+      round(digits = 3) %>% 
+      formatC(format = "f", digits = 3)]
+}
+
+tmp <- main[, 
+            .(Mean = mean(stock, na.rm = TRUE) %>% formatC(format = "f", digits = 3),
+              CI = t.test(stock, conf.level = 0.95)$conf.int[c(1,2)] %>% formatC(format = "f", digits = 3) %>% paste(collapse = " - ")),
+            by = c('treatment', 'round')] %>%
+  data.table::dcast(formula = round ~ treatment,
+                    value.var = c('Mean', 'CI'))
+
+tmp <- tmp[, c(1,2,4,3,5)]
+
+tmp[p, on = .(round = round)] %>%
+  kable(col.names = c('Period', 
+                      'Mean: Original', '95%-CI: Original',
+                      'Mean: Reproduction', '95%-CI: Reproduction',
+                      'p-Value'))
+
+```
+
+```{r}
+#| label: tbl-gini-periods
+#| tbl-cap: The average Gini coefficient over time across samples.
+
+p <- data.table(round = 1:10)
+for(r in 1:10){
+  a <- main[round == r & treatment == 'replication', gini]
+  b <- main[round == r & treatment == 'noPunish10', gini]
+
+  p[round == r, `p-value` := wilcox.test(a, b, exact = FALSE)$p.value %>% 
+      round(digits = 3) %>% 
+      formatC(format = "f", digits = 3)]
+}
+
+tmp <- main[, 
+            .(Mean = mean(gini, na.rm = TRUE) %>% formatC(format = "f", digits = 3),
+              CI = t.test(gini, conf.level = 0.95)$conf.int[c(1,2)] %>% formatC(format = "f", digits = 3) %>% paste(collapse = " - ")),
+            by = c('treatment', 'round')] %>%
+  data.table::dcast(formula = round ~ treatment,
+                    value.var = c('Mean', 'CI'))
+
+tmp <- tmp[, c(1,2,4,3,5)]
+
+tmp[p, on = .(round = round)] %>%
+  kable(col.names = c('Period', 
+                      'Mean: Original', '95%-CI: Original',
+                      'Mean: Reproduction', '95%-CI: Reproduction',
+                      'p-Value'))
+
+```
+
+{{< pagebreak >}}

### 2023-06-12 otreeLite/settings.py

@@ -36,7 +36,7 @@ SESSION_CONFIGS = [
 # e.g. self.session.config['participation_fee']
 
 SESSION_CONFIG_DEFAULTS = dict(
-    real_world_currency_per_point=0.10,
+    real_world_currency_per_point=0.02,
     participation_fee=2.00,
     doc=""
 )

### 2023-06-12 analysis/article/paper.tex
disentangle projects

--- 2023-05-24 analysis/quarto/paper.tex
@@
   authoryear,
-  preprint,
-  3p]{elsarticle}
+  review,
+  3p,
+  onecolumn]{elsarticle}
 
@@
   pdfauthor={Hauke Roggenkamp},
-  pdfkeywords={Replication study, Non-convenience sample, Open
-science, Dynamic public goods game, Online
-experiment, Generalizability},
+  pdfkeywords={Public goods, Dynamic
+games, Reproducibility, Generalizability, Online Experiment, Climate
+change mitigation},
   colorlinks=true,
@@
 Collecting data from both a convenient (students) and an inconvenient
-(general population) sample, I not only reproduce some of the author's
+(general population) sample, I not only reproduce some of the authors'
 original observations but also test their novel game's generalizability.
@@
 students and the general population sample alike. Because the study of
-inexperiend general population samples raises methodological challenges,
-such as fatigue and dropouts, this research approaches them. Doing so, I
-provide simple solutions to run relieable interactive experiments
-online.
-
-You can find the most recent version of this paper
-\href{https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.pdf}{here}.
+inexperienced general population samples raises methodological
+challenges, such as fatigue and dropouts, this research approaches them.
+Doing so, I provide simple solutions to run reliable interactive
+experiments online.
 \end{abstract}
 
+\begin{highlights}
+\item Highlight 1\item Highlight 2\item Highlight 3
+\end{highlights}
+
 \begin{keyword}
-    Replication study \sep Non-convenience sample \sep Open
-science \sep Dynamic public goods game \sep Online experiment \sep 
-    Generalizability
+    Public goods \sep Dynamic
+games \sep Reproducibility \sep Generalizability \sep Online
+Experiment \sep 
+    Climate change mitigation
 \end{keyword}
-\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable, boxrule=0pt, interior hidden, sharp corners, frame hidden]}{\end{tcolorbox}}\fi
+\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, enhanced, breakable, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, boxrule=0pt]}{\end{tcolorbox}}\fi
 
@@
 A game designed by Gächter, Mengel, Tsakas \& Vostroknutov \citeyearpar[
-hereafter, GMTV]{GMTV2017} as well as Stefan Große (2011, unpublished)
-shows that it is fairly simple to remedy that limitation. They
+hereafter, GMTV]{GMTV2017} as well as Stefan Große (unpublished) shows
+that it is fairly simple to add this element of realism. They
 incorporated interdependencies into a \emph{dynamic} public goods game
@@
 interdependencies\footnote{One exemption are \citet{Moser2019}, who
-  built on GMTV's design to investigate leadership.}, I reproduced one
-of GMTV's treatments to compare dynamics across (in)experienced samples
+  built on GMTVs' design to investigate leadership.}, I reproduced one
+of GMTVs' treatments to compare dynamics across (in)experienced samples
 to investigate its generalizability. \citet{GKLS2020} find that static
@@
 of the public goods game with the context of climate change mitigation:
-Greater resemblance improves generalizability. Because GMTV's dynamic
+Greater resemblance improves generalizability. Because GMTVs' dynamic
 setting has a more realistic property---namely, interdependencies---one
@@
   lower contributions to charity than community members.} This yielded a
-setting similar to \citet{GKLS2020}'s which allows me to analyze how
-behavior in the abstract game translates into real-world action across
-samples. This research shows that the dynamic setting \emph{does not}
-add any advances with respect to generalizability of results.
+setting similar to the one of \citet{GKLS2020}, which allows me to
+analyze how behavior in the abstract game translates into real-world
+action across samples. This research shows that the dynamic setting
+\emph{does not} add any advances with respect to generalizability of
+results.
 
@@
 required me to design a robust (and thus, more complex) software to
-minimize attrition. I collected paradata to assess the desired fluency
-and feasibility of the experiment. This research reports on the robust
+minimize attrition. I collected paradata---which captures screen time
+and survey navigation, for instance---to assess the desired fluency and
+feasibility of the experiment. This research reports on the robust
 design that made the dynamic game feasible.
@@
 Taken together, this study makes three contributions. First, it
-reproduces parts of GMTV's original experiment and highlights the
+reproduces parts of GMTVs' original experiment and highlights the
 importance of pure replications. Second, it shows that logistically
@@
 Section~\ref{sec-generalizability}. Section~\ref{sec-conclusion}
-concludes. Because I observed some differences in reproducing GMTV's
-analysis using their data, I report these in the
-\href{@sec-appendix}{Appendix}.
+concludes. Because I observed some (qualitatively inconsequential)
+differences in reproducing GMTVs' analysis using their data, I report
+these in the \href{@sec-appendix}{Appendix}.
 
@@
   use the term of a \emph{conceptual replication} which means the same.}
-of one treatment of GMTV's dynamic public goods game. The pure
+of one treatment of GMTVs' dynamic public goods game. The pure
 reproduction re-analyzes the original data.
@@
 Considering the design, the only differences between such a
-\emph{static} game (with partner matching) and GMTV's design are
+\emph{static} game (with partner matching) and GMTVs' design are
 \emph{dynamics}: Instead of receiving fresh endowments every period,
@@
 \citet{GKLS2020}, I employed a VCA, where participants could donate any
-amount their earnings to offset carbon dioxide (that is, retire emission
-permits from the EU ETS).\footnote{Importantly, \citet{GKLS2020} made
-  the VCA decision with a fresh endowment \emph{before} they played the
-  abstract game. I deviate from their procedure to match GMTV's
-  procedure.} To ensure that each participant had the same basic level
-of information about the impact of their decision, I provided some basic
-information about the mechanism. The information also highlighted that
-the mitigation came into operation on a European level. Finally, I
-informed the participants that the documentation of individual and
-aggregate contributions were to be posted immediately after the
-concluding the sessions online. To avoid privacy or social image
-concerns, participants learned their unique and random IDs, which they
-needed to identify their individual contributions. The document
-certified that their contributions have been used to offset
+amount of their earnings to offset carbon dioxide (that is, retire
+emission permits from the EU ETS).\footnote{Importantly,
+  \citet{GKLS2020} made the VCA decision with a fresh endowment
+  \emph{before} they played the abstract game. I deviate from their
+  procedure to match GMTVs' procedure.} To ensure that each participant
+had the same basic level of information about the impact of their
+decision, I provided some basic information about the mechanism. The
+information also highlighted that the mitigation came into operation on
+a European level. Finally, I informed the participants that the
+documentation of individual and aggregate contributions were to be
+posted immediately after the concluding the sessions online. To avoid
+privacy or social image concerns, participants learned their unique and
+random IDs, which they needed to identify their individual
+contributions. The document certified that their contributions have been
+used to offset
 \href{https://www.compensators.org/compensatelist/?searchterm=stefan+traub}{1.82
@@
 Throughout this paper, I will compare results of my experiment with the
-results of GMTV's NOPUNISH 10 Period treatments. I am thus, referring to
+results of GMTVs' NOPUNISH 10 Period treatments. I am thus, referring to
 three different samples utilized at two points in time: the University
@@
 Female & 52 & 0.48 & 0.5 & 64 & 0.56 & 0.5 & 92 & 0.38 & 0.49 & F$=2.596^{*}$ \\ 
-Switching Row & 20 & 6.6 & 2.6 & 58 & 6 & 2 & 87 & 6.4 & 1.3 & F$=1.406^{}$\\ 
+Risk Aversion (1-12) & 20 & 6.6 & 2.6 & 58 & 6 & 2 & 87 & 6.4 & 1.3 & F$=1.406^{}$\\ 
 \hline
@@
 their VCA decision, before I elicited risk preferences
-\citep{HoltLaury2002} and finished with GMTV's questionnaire.
-
-While I stuck to GMTV's protocol as close as possible, I deviated in a
+\citep{HoltLaury2002} and finished with GMTVs' questionnaire.
+
+While I stuck to GMTVs' protocol as close as possible, I deviated in a
 few aspects. First, the instructions were German and also covered topics
@@
 of both students and non-students) more pro-social than the original
-sample? A two-sided rank sum test reveals that it is not (p=0.3926).
-Both samples contributed 10 tokens, that is, 50\% of their endowments on
+sample? A two-sided rank sum test reveals that it is not (p=0.393). Both
+samples contributed 10 tokens, that is, 50\% of their endowments on
 average (median and mean). Moreover, both samples' initial contributions
@@
 \caption{\label{fig-share-of-contributions}The average amount of tokens
-contributed over time in treatments.}
+contributed over time across samples.}
 
@@
 though: A two-sided rank sum test (comparing differences between
-samples) yields p=0.1356 for the mean stock in last period of the game.
+samples) yields p=0.136 for the mean stock in last period of the game.
 
@@
 potential efficiency: under full cooperation, a group can accumulate at
-least 4613 tokens or EUR 230. This is depicted in the left panel of
+maximum 4613 tokens or EUR 230. This is depicted in the left panel of
 Figure~\ref{fig-growth-heterogeneity}, where one can see the average
@@
   two-sided rank sum test (comparing differences between samples) yields
-  p=0.6059 for the mean Gini coefficient in last round of the game.}
+  p=0.606 for the mean Gini coefficient in last round of the game.}
 Because every participant started with the same initial endowment (in
@@
 
-Throughout this section, I do not consider GMTV's data and pool data I
+Throughout this section, I do not consider GMTVs' data and pool data I
 gathered from the citizens as well as the students from Hamburg (N =
@@
 I tracked both and find that none of the participants ever opened these
-popups even though they were clearly visible in the decision screen's
+popups even though they were clearly visible in the decision screens'
 header and introduced in the instructions. To further analyze how
@@
 strategy, I answer the question for a \emph{dynamic} public goods game:
-\emph{Not much}. Overall, there seems to be no association between
+\emph{Not too much}. Overall, there seems to be no association between
 choices in the voluntary climate action and the first period in the
@@
   same holds true for median contributions.} (b) Furthermore, average
-contributions are lower in the VCA. (c) In contrast to
-\citet{GKLS2020}'s observation, I do not observe a difference between
-samples in the abstract game's contribution behavior. (d) However, the
-student's share of income contributed to the VCA is significantly lower
-than the general population sample's contributions (two-sided rank sum
-test, p=0.0085). Taken together, these aggregate results indicate, that
-the consistency between tasks is higher for the general population than
-it is for students. Or, to put it differently, the general population's
+contributions are lower in the VCA. (c) In contrast to the observation
+of \citet{GKLS2020}, I do not observe a difference between samples in
+the abstract game's contribution behavior. (d) However, the student's
+share of income contributed to the VCA is significantly lower than the
+general population sample's contributions (two-sided rank sum test,
+p=0.009). Taken together, these aggregate results indicate, that the
+consistency between tasks is higher for the general population than it
+is for students. Or, to put it differently, the general population's
 behavior in the abstract game better predicts their behavior in
@@
 of GMTV in an online setting using a general population sample. The
-results suggest that it is important to reproduce experiments---both
-purely and scientifically \citep[ p.~716]{Hamermesh2007}---before
-drawing conclusions about generalizability.
-
-The three most important findings are as follows: First, the
-contribution behavior in my experiment is statistically similar to the
-behavior reported in the original study. Consequently, the outcomes
-growth and inequality are reproducible. Second, the online experiment
+three most important findings are as follows: First, the contribution
+behavior in my experiment is statistically similar to the behavior
+reported in the original study. Consequently, the outcomes growth and
+inequality are reproducible in both meanings: they are \emph{purely}
+(despite minor differences one can re-analyze the original data and
+reach the same conclusions) and \emph{scientifically} (one can gather
+new data drawn from a different population in a different situation and
+find similar patterns) reproducible. Second, the online experiment
 proceeded fluently such that dropouts were no concern. Third,
@@
 
-Limitations?
+Taken together the results answer the questions whether GMTVs' dynamic
+paradigm is reproducible across samples (yes) and whether it is feasible
+employ it online (also yes). The question that is \emph{not} answered
+is, whether GMTVs' treatment effects replicate well because I did not
+focus on treatments and treatment effects. It thus, remains an open
+question, whether the causal effect of GMTVs' treatments replicate well.
+Further, we do not know whether their treatments affect real-world
+behavior. How generalizable are treatment effects in public goods games
+in general? Albeit this study does not address these questions, it
+provides methods suited to investigate them---even with inconvenient
+samples.
+
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
+
+I gratefully acknowledge support by the German Research Foundation (DFG)
+under Germany's Excellence Strategy, cluster EXC 2037 ``Climate,
+Climatic Change, and Society'' (project 390683824). I thank Stefan Traub
+and participants of the CLICCS B5 group for helpful discussions.
 
@@
 
+\hypertarget{b-tables}{%
+\section{B: Tables}\label{b-tables}}
+
+\hypertarget{tbl-contribution-periods}{}
+\begin{table}
+\caption{\label{tbl-contribution-periods}The average amount of tokens contributed over time across samples. }\tabularnewline
+
+\centering
+\begin{tabular}{r|l|l|l|l|l}
+\hline
+Period & Mean: Original & 95\%-CI: Original & Mean: Reproduction & 95\%-CI: Reproduction & p-Value\\
+\hline
+1 & 42.739 & 38.367 - 47.111 & 40.069 & 34.406 - 45.732 & 0.561\\
+\hline
+2 & 50.826 & 42.775 - 58.877 & 40.138 & 31.557 - 48.719 & 0.061\\
+\hline
+3 & 59.348 & 45.916 - 72.780 & 43.207 & 30.815 - 55.599 & 0.067\\
+\hline
+4 & 71.565 & 53.030 - 90.100 & 46.414 & 29.930 - 62.898 & 0.014\\
+\hline
+5 & 82.348 & 55.398 - 109.298 & 55.931 & 33.101 - 78.761 & 0.049\\
+\hline
+6 & 87.435 & 45.735 - 129.135 & 62.448 & 31.121 - 93.776 & 0.191\\
+\hline
+7 & 91.652 & 36.859 - 146.446 & 68.966 & 33.626 - 104.305 & 0.740\\
+\hline
+8 & 103.087 & 30.382 - 175.792 & 69.759 & 29.621 - 109.896 & 0.507\\
+\hline
+9 & 98.804 & 20.125 - 177.483 & 70.448 & 22.055 - 118.841 & 0.747\\
+\hline
+10 & 73.609 & 20.019 - 127.198 & 70.793 & 15.116 - 126.470 & 0.606\\
+\hline
+\end{tabular}
+\end{table}
+
+\hypertarget{tbl-share-periods}{}
+\begin{table}
+\caption{\label{tbl-share-periods}The average share of current endowments contributed over time across
+samples. }\tabularnewline
+
+\centering
+\begin{tabular}{r|l|l|l|l|l}
+\hline
+Period & Mean: Original & 95\%-CI: Original & Mean: Reproduction & 95\%-CI: Reproduction & p-Value\\
+\hline
+1 & 0.534 & 0.480 - 0.589 & 0.501 & 0.430 - 0.572 & 0.561\\
+\hline
+2 & 0.487 & 0.418 - 0.557 & 0.383 & 0.309 - 0.457 & 0.051\\
+\hline
+3 & 0.441 & 0.358 - 0.524 & 0.325 & 0.245 - 0.406 & 0.046\\
+\hline
+4 & 0.418 & 0.338 - 0.497 & 0.278 & 0.202 - 0.354 & 0.009\\
+\hline
+5 & 0.377 & 0.285 - 0.470 & 0.270 & 0.190 - 0.349 & 0.063\\
+\hline
+6 & 0.300 & 0.194 - 0.407 & 0.234 & 0.153 - 0.315 & 0.277\\
+\hline
+7 & 0.240 & 0.143 - 0.337 & 0.217 & 0.150 - 0.285 & 0.934\\
+\hline
+8 & 0.214 & 0.122 - 0.306 & 0.176 & 0.111 - 0.240 & 0.593\\
+\hline
+9 & 0.165 & 0.081 - 0.249 & 0.149 & 0.087 - 0.212 & 0.949\\
+\hline
+10 & 0.115 & 0.049 - 0.181 & 0.121 & 0.067 - 0.175 & 0.450\\
+\hline
+\end{tabular}
+\end{table}
+
+\hypertarget{tbl-wealth-periods}{}
+\begin{table}
+\caption{\label{tbl-wealth-periods}The average wealth over time across samples. }\tabularnewline
+
+\centering
+\begin{tabular}{r|l|l|l|l|l}
+\hline
+Period & Mean: Original & 95\%-CI: Original & Mean: Reproduction & 95\%-CI: Reproduction & p-Value\\
+\hline
+1 & 103.348 & 100.966 - 105.729 & 101.724 & 98.806 - 104.642 & 0.605\\
+\hline
+2 & 130.435 & 124.592 - 136.277 & 123.517 & 116.597 - 130.437 & 0.099\\
+\hline
+3 & 161.696 & 149.708 - 173.683 & 146.517 & 133.780 - 159.255 & 0.061\\
+\hline
+4 & 199.522 & 178.632 - 220.412 & 171.000 & 150.455 - 191.545 & 0.033\\
+\hline
+5 & 242.217 & 208.842 - 275.593 & 200.586 & 169.020 - 232.152 & 0.033\\
+\hline
+6 & 288.174 & 235.294 - 341.054 & 233.448 & 186.751 - 280.146 & 0.047\\
+\hline
+7 & 335.478 & 256.590 - 414.367 & 269.586 & 205.759 - 333.413 & 0.072\\
+\hline
+8 & 388.739 & 275.392 - 502.086 & 305.897 & 223.488 - 388.305 & 0.107\\
+\hline
+9 & 439.674 & 290.308 - 589.040 & 342.759 & 239.624 - 445.893 & 0.124\\
+\hline
+10 & 478.087 & 307.892 - 648.282 & 379.828 & 251.997 - 507.658 & 0.136\\
+\hline
+\end{tabular}
+\end{table}
+
+\hypertarget{tbl-gini-periods}{}
+\begin{table}
+\caption{\label{tbl-gini-periods}The average Gini coefficient over time across samples. }\tabularnewline
+
+\centering
+\begin{tabular}{r|l|l|l|l|l}
+\hline
+Period & Mean: Original & 95\%-CI: Original & Mean: Reproduction & 95\%-CI: Reproduction & p-Value\\
+\hline
+1 & 0.134 & 0.111 - 0.157 & 0.131 & 0.111 - 0.151 & 0.825\\
+\hline
+2 & 0.150 & 0.118 - 0.182 & 0.165 & 0.139 - 0.192 & 0.733\\
+\hline
+3 & 0.171 & 0.133 - 0.210 & 0.186 & 0.153 - 0.219 & 0.495\\
+\hline
+4 & 0.183 & 0.137 - 0.230 & 0.188 & 0.150 - 0.226 & 0.768\\
+\hline
+5 & 0.192 & 0.141 - 0.243 & 0.200 & 0.159 - 0.241 & 0.606\\
+\hline
+6 & 0.193 & 0.139 - 0.248 & 0.194 & 0.149 - 0.239 & 0.825\\
+\hline
+7 & 0.207 & 0.153 - 0.260 & 0.211 & 0.165 - 0.256 & 0.905\\
+\hline
+8 & 0.214 & 0.160 - 0.268 & 0.216 & 0.170 - 0.261 & 0.985\\
+\hline
+9 & 0.223 & 0.171 - 0.275 & 0.220 & 0.173 - 0.266 & 0.726\\
+\hline
+10 & 0.232 & 0.179 - 0.285 & 0.218 & 0.171 - 0.265 & 0.606\\
+\hline
+\end{tabular}
+\end{table}
+
+\newpage{}
+
   \bibliography{../biblio.bib}

### 2023-06-12 analysis/slides/WIP_GMTV_Data.Rmd
disentangle projects

---
title: "Growth and inequality in public good provision"
author: "Hauke Roggenkamp"
date: "`r Sys.Date()`"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(plm)         # robust standard errors
library(lmtest)      # robust standard errors
library(haven)       # read_dta
library(here)        # file paths
library(magrittr)    # pipe operator
library(data.table)  # great data objects
library(knitr)       # print tables
library(stargazer)   # regression Tables
library(DescTools)   # gini coefficient
library(ggplot2)     # viz
library(wesanderson) # color palette
library(patchwork)   # plot arrangements

layout <- theme(panel.background = element_rect(fill = "white"),
                panel.grid = element_blank(),
                panel.grid.major.y = element_line(colour="gray", size=0.25),
                legend.key = element_rect(fill = "white"),
                axis.line.x.bottom = element_line(size = 0.25),
                axis.line.y.left = element_line(size = 0.25),
                # plot.margin = unit(c(1,1,1,1), "cm"),
                legend.title = element_blank()
                )

```

```{r preperation}

# regressions 
gdp_ols <- function(DT, var = "gdp", output = "plm"){
  p.df <- DT %>% pdata.frame(index = c("gr_id"))
  plm <- plm(get(var) ~ punish, data = p.df, model = "pooling")
  # plm
  G <- length(unique(p.df$gr_id))
  N <- length(p.df$gr_id)
  dfa <- (G/(G - 1)) * (N - 1) / plm$df.residual
  group_c_vcov <- dfa * vcovHC(plm, type = "HC0", cluster = "group", adjust = T)
  # coeftest(plm, vcov = group_c_vcov)
  se <- sqrt(diag(group_c_vcov))
  # se

  if (output == "plm") {
    plm
  } else {
    se
  }

}

layout <- theme(panel.background = element_rect(fill = "white"),
                panel.grid = element_blank(),
                panel.grid.major.y = element_line(colour="gray", size=0.25),
                legend.key = element_rect(fill = "white"),
                axis.line.x.bottom = element_line(size = 0.25),
                axis.line.y.left = element_line(size = 0.25),
                # plot.margin = unit(c(1,1,1,1), "cm"),
                legend.title = element_blank()
                )

```

## Original Data

The following five slides report a subset of the original data. More specifically, I focus on experiment 1, group 101 and subjects 111, 112, 113 and 114 in periods 1 to 7. These subjects played the long game without punishment.

There is no specific reason I focus on this particular group.

With this example at hand, I will show that the definition of Wealth, the Share of Endowment Contributed as well as the Gini Coefficient is processed erroneously.

## Original Data: Variables

Among several identifiers and treatment variables, the data (as downloaded from the online appendix) contains the following information:

-   `exp_num` is a session identifier
-   `per` denotes the period
-   `gr_id` is a group identifier (carrying treatment information)
-   `subj_id` is a subject identifier
-   `tokens` reports a subject's endowment.
-   `other[1-3]` report the other group members' endowments.
-   `gdp` equals the sum of endowments of a group.
-   `putin` reports a subject's contribution.
-   `pu[1-3]` report the other group members' contributions
-   `sum` equals the sum of contributions of a group.
-   `gini` shall report a group's Gini coefficient.
-   `mean` shall report the sum of endowments contributed of a group.

```{r readData}
DT <- read_dta(here("..", "data", "gaechteretal", "GMTV-data.dta")) %>% data.table()

GMTV <- DT[order(exp_num, treat, gr_id, per),
           .(treat, punish = as.logical(punish), longgame = as.logical(longgame),        # treatment vars
             exp_num, gr_id, per, subj_id,              # IDs
             tokens, other1, other2, other3, gdp,       # endowments
             putin, pu1, pu2, pu3, sum, mean,           # contributions
             gini,                                      # ginis
             totallost,                                 # punishment var
             highgdp
             )]

```

## Original Data: Wealth

One of the main variables of the paper is called _Wealth_ . This variable is said to _sum the endowments of all participants in a given group at the beginning of the following period_.

As the reproduction of Table 2 will show, however, _Wealth_ is defined as `gdp`. The following Table shows that the _gdp_ is defined as the sum of endowments of the current period as $42+27+27+30=126$ & $45+29+29+33=136$.

```{r}
GMTV[exp_num == 1 & gr_id == 101 & (per == 5 | per == 6) & subj_id == 111,
     .(gr_id,
       per,
       subj_id,
       tokens,
       other1,
       other2,
       other3,
       gdp)] %>% 
  knitr::kable()
```

## Original Data: Share of Income Contributed

The `mean` is intended report the share of a group's income that is contributed to the public good. According to the following STATA code snipet that Friederike provided, it calculates she share of the group's previous income that is contributed in this period.

```
*tsset subj_id per
*gen mean=sum/l.gdp
```

This is also in line with subject 111's `mean` in the table below as it should equal $18/126=0.143$ in period 5 but is $0.155=18/116$.

```{r}
GMTV[exp_num == 1 & gr_id == 101 & (per == 4 | per == 5 | per == 6) & subj_id == 111,
     .(gr_id,
       per,
       subj_id,
       gdp,
       sum,
       mean = round(mean, digits = 3))] %>% 
  knitr::kable()
```

## Original Data: Gini

The following table displays the whole group 101 of experiment 1 in period 5.

```{r}
GMTV[exp_num == 1 & gr_id == 101 & per == 5,
     .(gr_id,
       per,
       subj_id,
       tokens,
       other1,
       other2,
       other3,
       gini = round(gini, digits = 3))] %>% 
  knitr::kable()
```

Because the Gini coefficient expresses the inequality within a group, it _should_ be the same for all group members. The table above illustrates an example where this is not the case.

## Original Data: Gini

In addition, the `gini` definition has another (probably a related) flaw that is similar to the definition of Wealth: It reports the inequality of endowments instead of earnings -- at least sometimes.

The following Table shows subject 111's data once again. The Gini coefficient reported in period 1 should equal $0.168$ but equals $0$. The second period's Gini coefficient should equal $0.146$ but is $0.168$ and so on.

```{r Gini2}

GMTV[exp_num == 1 & gr_id == 101 & per <=3 & subj_id == 111, # (per == 5 | per == 6 | per == 7)
     .(gr_id,
       per,
       subj_id,
       tokens,
       other1,
       other2,
       other3,
       gini = round(gini, digits = 3))] %>% 
  knitr::kable()
```

## Original Data: Reproduction of Tables

To demonstrate that these data were used to create the Figures and Tables that were published, I reproduce Table 2 (using `gdp` as a measure for _Wealth_) and 4.

Please excuse the tables' format and their misleading captions.

## Original Data: Reproduction of Table 2

```{r regressionSubsets}
# subsets for regression tables
GMTV_short_all  <- GMTV[longgame == 0 & treat < 3 & per == 10]
GMTV_short_poor <- GMTV[longgame == 0 & treat < 3 & per == 10 & highgdp == 0]
GMTV_short_rich <- GMTV[longgame == 0 & treat < 3 & per == 10 & highgdp == 1]
GMTV_long_all   <- GMTV[longgame == 1 & treat > 100 & per == 15]
GMTV_long_poor  <- GMTV[longgame == 1 & treat > 100 & per == 15 & highgdp == 0]
GMTV_long_rich  <- GMTV[longgame == 1 & treat > 100 & per == 15 & highgdp == 1]
```

```{r reproductionTable2.1, results = "asis"}
stargazer(gdp_ols(GMTV_short_all),
          gdp_ols(GMTV_short_poor),
          gdp_ols(GMTV_short_rich),

          se = list(gdp_ols(GMTV_short_all,  output = "se"),
                    gdp_ols(GMTV_short_poor, output = "se"),
                    gdp_ols(GMTV_short_rich, output = "se")),

          add.lines = list(c("Long Game?", "No", "No", "No")),

          column.labels = rep(c("All", "Below median", "Above median"), 2),
          model.numbers = FALSE,
          dep.var.labels = "Wealth (Table 2)",
          notes = "Robust standard errors in parentheses",

          header=FALSE,
          no.space = TRUE,
          columns.sep.width = "3pt",
          font.size = "small",

          type = "latex", digits = 2, omit.stat = c("adj.rsq", "f")
          )
```

## Original Data: Reproduction of Table 4

```{r reproductionTable4.1, results = "asis"}
stargazer(gdp_ols(GMTV_short_all, var = "gini"),
          gdp_ols(GMTV_short_poor, var = "gini"),
          gdp_ols(GMTV_short_rich, var = "gini"),

          se = list(gdp_ols(GMTV_short_all,  output = "se", var = "gini"),
                    gdp_ols(GMTV_short_poor, output = "se", var = "gini"),
                    gdp_ols(GMTV_short_rich, output = "se", var = "gini")),

          add.lines = list(c("Long Game?", "No", "No", "No")),

          column.labels = rep(c("All", "Below median", "Above median"), 2),
          model.numbers = FALSE,
          dep.var.labels = "Gini (Table 4)",
          notes = "Robust standard errors in parentheses",

          header=FALSE,
          no.space = TRUE,
          columns.sep.width = "3pt",
          font.size = "small",

          type = "latex", digits = 3, omit.stat = c("adj.rsq", "f")
          )
```

## Original Data: Reproduction of Table 4

```{r reproductionTable4.2, results = "asis"}
stargazer(gdp_ols(GMTV_long_all, var = "gini"),
          gdp_ols(GMTV_long_poor, var = "gini"),
          gdp_ols(GMTV_long_rich, var = "gini"),

          se = list(gdp_ols(GMTV_long_all,  output = "se", var = "gini"),
                    gdp_ols(GMTV_long_poor, output = "se", var = "gini"),
                    gdp_ols(GMTV_long_rich, output = "se", var = "gini")),

          add.lines = list(c("Long Game?", "Yes", "Yes", "Yes")),

          column.labels = rep(c("All", "Below median", "Above median"), 2),
          model.numbers = FALSE,
          dep.var.labels = "Gini (Table 4)",
          notes = "Robust standard errors in parentheses",

          header=FALSE,
          no.space = TRUE,
          columns.sep.width = "3pt",
          font.size = "small",

          type = "latex", digits = 3, omit.stat = c("adj.rsq", "f")
          )
```

## Re-processed Data

```{r reProcessData}
# Wealth
GMTV[, stock0 := (tokens - putin + 1.5*sum/4) %>% ceiling()]
GMTV[, stock1 := (other1 - pu1 + 1.5*sum/4) %>% ceiling()]
GMTV[, stock2 := (other2 - pu2 + 1.5*sum/4) %>% ceiling()]
GMTV[, stock3 := (other3 - pu3 + 1.5*sum/4) %>% ceiling()]

GMTV[!is.na(totallost), stock0 := (tokens - putin + 1.5*sum/4 - totallost) %>% ceiling()]
GMTV[!is.na(totallost), stock1 := (other1 - pu1 + 1.5*sum/4 - totallost) %>% ceiling()]
GMTV[!is.na(totallost), stock2 := (other2 - pu2 + 1.5*sum/4 - totallost) %>% ceiling()]
GMTV[!is.na(totallost), stock3 := (other3 - pu3 + 1.5*sum/4 - totallost) %>% ceiling()]

GMTV[stock0 < 0, stock0 := 0]
GMTV[stock1 < 0, stock1 := 0]
GMTV[stock2 < 0, stock2 := 0]
GMTV[stock3 < 0, stock3 := 0]

GMTV[, gdp2 := stock0 + stock1 + stock2 + stock3]

# Mean
GMTV[,
     mean2 := sum/gdp,
     by = .(exp_num, subj_id, per)]

# Gini 
GMTV[,
     gini2 := Gini(c(stock0, stock1, stock2, stock3)),
     by = .(exp_num, subj_id, per)]
```

```{r eval = FALSE}
x <- GMTV[exp_num <= 10,
     .(treat,
       exp_num,
       punish,
       longgame,
       gr_id,
       per,
       subj_id,
       tokens,
       putin,
       sum,
       multi = ceiling(sum * 1.5),
       totallost,
       calculated = stock0,
       reported = shift(tokens, n = 1, fill = NA, type = "lead"),
       diff = shift(tokens, n = 1, fill = NA, type = "lead") - stock0),
     by = subj_id]

x[punish == TRUE] %>% View()

x[punish == TRUE & diff < 0, .N]

```

The following Table shows the same experiment, group and round as displayed above. The only difference is, that the the Wealth meassure, the Share of Endowments Contributed and the Gini coefficient are re-processed.

## Re-processed Data: Wealth

Re-processing _Wealth_ is problematic for the punish-treatments as the original data does report how much a subject punishes her group members. It provides the variable `totallost` which reports the punishment received by others, apperently. The following code therefore exceeds each subject's individual _Wealth_ as the following table illustrates.

```
wealth <- ceiling(tokens-putin+1.5*sum/4-totallost)
```

```{r}
GMTV[subj_id == 441,
     .(# exp_num,
       per,
       subj_id,
       tokens,
       putin,
       sum,
       totallost,
       wealth = shift(tokens, n = 1, fill = NA, type = "lead"),
       wealth2 = (tokens - putin + 1.5 * sum / 4 - totallost) %>% ceiling())] %>% 
  head(2) %>%
  knitr::kable()
```

`wealth` is a lagged variable reporting the next period's endowments (`tokens`) and `wealth2` is the recalculated variable (using the code displayed above). The first period's difference between the two variables cannot be explained with the available data.

## Re-processed Data: Wealth

Remember: The `gdp` reported in the data describes the group's _Wealth_ at the beginning of a period and I want to calculate the _Wealth_ at the end of a period. This is quite easy for the no-punish-treatments (because the data provides all the information I need) as well as for all but the last period of the punish-treatments (because I can rely on the next-period's `tokens` or `gdp`).

To reproduce the tables, however, I need the final period's outcome in the punish-treatments.

Looking at the zTree code it appears as if I need the variables called `pun1`, `pun2`, `pun3` to do so.

## Re-processed Data Share of Income Contributed

Subject 111's `mean` in the table below now equals $18/126=$ `r round(18/126, digits = 3)` in period 5 and $18/116=$ `r round(18/116, digits = 3)` in period 4.

```{r}
GMTV[exp_num == 1 & gr_id == 101 & (per == 4 | per == 5 | per == 6) & subj_id == 111,
     .(gr_id,
       per,
       subj_id,
       gdp,
       sum,
       mean = round(mean2, digits = 3))] %>% 
  knitr::kable()
```

## Re-processed Data: Gini

These two tables illustrate the example from above. One can see that the Gini coefficient is constant within the group and that it relies on a period's outcomes instead of the endowments.

```{r}
GMTV[exp_num == 1 & gr_id == 101 & per == 5,
     .(gr_id,
       per,
       subj_id,
       tokens,
       other1,
       other2,
       other3,
       gini = round(gini2, digits = 3))] %>% 
  knitr::kable()
```

```{r}

GMTV[exp_num == 1 & gr_id == 101 & per <=3 & subj_id == 111, # (per == 5 | per == 6 | per == 7)
     .(gr_id,
       per,
       subj_id,
       tokens,
       other1,
       other2,
       other3,
       gini = round(gini2, digits = 3))] %>% 
  knitr::kable()
```

## Re-processed Data: Gini

Note: Because I cannot calculate the individuals' wealth in the last punishment periods, I also cannot calculate the corresponding Gini coefficient.

## Re-processed Data:Reproduction of Table 2

Not possible.

## Re-processed Data:Reproduction of Table 4

Not possible.

## Re-processed Data: Figure 1 a

```{r}

GMTV[punish == 0 & longgame == 0, # exp_num == 5 | exp_num == 8 | exp_num == 9,
     treatment := "noPunish10"]

GMTV[punish == 0 & longgame == 1, # exp_num == 1 | exp_num == 3,
     treatment := "noPunish15"]

GMTV[punish == 1 & longgame == 0, # exp_num == 4 | exp_num == 6 | exp_num == 10,
     treatment := "Punish10"]

GMTV[punish == 1 & longgame == 1, # exp_num == 2 | exp_num == 7,
     treatment := "Punish15"]

# remove duplicate rows while subsetting only group level variables
GMTVgroups <- GMTV[exp_num <= 10,
                   .(treatment,
                     treat,
                     punish = as.logical(punish),
                     longgame = as.logical(longgame),
                     exp_num,
                     gr_id,
                     per,
                     sum,
                     gdp,
                     gdp2,
                     mean,
                     mean2,
                     gini,
                     gini2,
                     highgdp = as.logical(highgdp))] %>% unique()
```

Even though I have not manipulated the `sum`, that is, a group's contributions, my reproduction of Figure 1a looks a little different -- although qualitatively similar.

```{r plotContributionsA}

SUM <- GMTVgroups[, 
                    lapply(.SD, mean, na.rm = TRUE),
                    by = c("per", "treatment", "punish", "longgame"),
                    .SDcols = "sum"]

SUM[,
    sum := round(sum/4)]

ggplot(data = SUM, aes(x = per, y = sum, fill = treatment, color = treatment, lty = punish)) +
          layout +
          theme(legend.position="bottom") +
          geom_vline(xintercept = 10, alpha = 0.66) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="",  breaks = 1:15) +
          scale_y_continuous(breaks = seq(0, 150, by = 50), limits = c(0, 170), expand = c(0, 0)) +
          labs(y = "Average Amount of Tokens contributed") +
          scale_color_manual(values = wes_palette("Zissou1"))

```

## Re-processed Data: Figure 1 b

The left panel shows my reproduction of Figure 1 b using the original data, which does not look like the original. The right panel shows my take on Figure 1 b using the re-processed `mean`. That one does not look like the original either.

```{r plotContributionsB1}

MEANS <- GMTVgroups[,
                    lapply(.SD, mean, na.rm = TRUE),
                    by = c("per", "treatment", "punish", "longgame"),
                    .SDcols = c("mean", "mean2")]

MEANS2 <- GMTV[exp_num <= 10,
               lapply(.SD, mean, na.rm = TRUE),
               by = c("per", "treatment", "punish", "longgame"),
               .SDcols = c("mean", "mean2")]

mean <- ggplot(data = MEANS, aes(x = per, y = mean, fill = treatment, color = treatment, lty = punish)) +
          layout +
          theme(legend.position="none") +
          geom_vline(xintercept = 10, alpha = 0.66, size = 0.25) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="",  breaks = 1:15) +
          scale_y_continuous(breaks = seq(0, 1.2, by = 0.2), limits = c(0, 1.25), expand = c(0, 0)) +
          labs(y = "Share of past Endowment contributed") +
          scale_color_manual(values = wes_palette("Zissou1"))

mean2 <- ggplot(data = MEANS, aes(x = per, y = mean2, fill = treatment, color = treatment, lty = punish)) +
          layout +
          theme(legend.position="none") +
          geom_vline(xintercept = 10, alpha = 0.66, size = 0.25) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="", breaks = 1:15) +
          scale_y_continuous(breaks = seq(0, 1.2, by = 0.2), limits = c(0, 1.25), expand = c(0, 0)) +
          labs(y = "Share of current Endowment contributed") +
          scale_color_manual(values = wes_palette("Zissou1"))

patchwork <- mean + mean2 & theme(legend.position = "bottom")
patchwork <- patchwork + plot_layout(guides = "collect")
patchwork

```

## Re-processed Data: Figure 1 b

These two figures are essentially the same as above but are calculating by averageing over individuals instead of groups.

```{r plotContributionsB2}

MEANS2 <- GMTV[exp_num <= 10,
               lapply(.SD, mean, na.rm = TRUE),
               by = c("per", "treatment", "punish", "longgame"),
               .SDcols = c("mean", "mean2")]

mean <- ggplot(data = MEANS2, aes(x = per, y = mean, fill = treatment, color = treatment, lty = punish)) +
          layout +
          theme(legend.position="none") +
          geom_vline(xintercept = 10, alpha = 0.66, size = 0.25) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="",  breaks = 1:15) +
          scale_y_continuous(breaks = seq(0, 1.2, by = 0.2), limits = c(0, 1.25), expand = c(0, 0)) +
          labs(y = "Share of past Endowment contributed") +
          scale_color_manual(values = wes_palette("Zissou1"))

mean2 <- ggplot(data = MEANS2, aes(x = per, y = mean2, fill = treatment, color = treatment, lty = punish)) +
          layout +
          theme(legend.position="none") +
          geom_vline(xintercept = 10, alpha = 0.66, size = 0.25) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="", breaks = 1:15) +
          scale_y_continuous(breaks = seq(0, 1.2, by = 0.2), limits = c(0, 1.25), expand = c(0, 0)) +
          labs(y = "Share of current Endowment contributed") +
          scale_color_manual(values = wes_palette("Zissou1"))

patchwork <- mean + mean2 & theme(legend.position = "bottom")
patchwork <- patchwork + plot_layout(guides = "collect")
patchwork

```

## Re-processed Data: Figure 1

I cannot reproduce Figure 1. Neither using the original data, nor my re-processed data.

This implies either that

- I made a mistake in creating the Figure (using a subset of the data where `exp_num <= 10`)
- the Figures have been created with data that was not provided in the online appendix (which would be weird as the tables have been created with that data)

## Re-processed Data: Figure 2 a

The following figures show my take on Figure 2 a. The left panel calculated group averages of wealth while the right panel calculated individual average. Both are using the original data

```{r plotWealthA}

STOCK <- GMTVgroups[, 
                    lapply(.SD, mean, na.rm = TRUE),
                    by = c("per", "treatment", "punish", "longgame"),
                    .SDcols = "gdp"]

STOCK2 <- GMTV[exp_num <= 10,
               lapply(.SD, mean, na.rm = TRUE),
               by = c("per", "treatment", "punish", "longgame"),
               .SDcols = "gdp"]

p1 <- ggplot(data = STOCK, aes(x = per, y = gdp, fill = treatment, color = treatment, lty = punish)) +
          layout +
          theme(legend.position="bottom") +
          geom_vline(xintercept = 10, alpha = 0.66) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="",  breaks = 1:15) +
          scale_y_continuous(breaks = seq(0, 1500, by = 500), limits = c(0, 1700), expand = c(0, 0)) +
          labs(y = "Wealth (group average)") +
          scale_color_manual(values = wes_palette("Zissou1"))

p2 <- ggplot(data = STOCK2, aes(x = per, y = gdp, fill = treatment, color = treatment, lty = punish)) +
          layout +
          theme(legend.position="bottom") +
          geom_vline(xintercept = 10, alpha = 0.66) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="",  breaks = 1:15) +
          scale_y_continuous(breaks = seq(0, 1500, by = 500), limits = c(0, 1700), expand = c(0, 0)) +
          labs(y = "Wealth (individual average)") +
          scale_color_manual(values = wes_palette("Zissou1"))

patchwork <- p1 + p2 & theme(legend.position = "bottom")
patchwork <- patchwork + plot_layout(guides = "collect")
patchwork

```

## Re-processed Data: Figure 2 a

The following figures show my take on Figure 2 a. The left panel calculated group averages of wealth while the right panel calculated individual average. Both are using the original data

```{r plotWealthB}

STOCK  <- GMTV[exp_num <= 10,
               lapply(.SD, mean, na.rm = TRUE),
               by = c("per", "treatment", "punish", "longgame"),
               .SDcols = c("gdp", "gdp2")]

p1 <- ggplot(data = STOCK, aes(x = per, y = gdp, fill = treatment, color = treatment, lty = punish)) +
          layout +
          theme(legend.position="bottom") +
          geom_vline(xintercept = 10, alpha = 0.66) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="",  breaks = 1:15) +
          scale_y_continuous(breaks = seq(0, 1500, by = 500), limits = c(0, 1700), expand = c(0, 0)) +
          labs(y = "Wealth (original data)") +
          scale_color_manual(values = wes_palette("Zissou1"))

p2 <- ggplot(data = STOCK, aes(x = per, y = gdp2, fill = treatment, color = treatment, lty = punish)) +
          layout +
          theme(legend.position="bottom") +
          geom_vline(xintercept = 10, alpha = 0.66) +
          geom_line(show.legend=FALSE) +
          geom_point() +
          scale_x_continuous(name="",  breaks = 1:15) +
          scale_y_continuous(breaks = seq(0, 1500, by = 500), limits = c(0, 1700), expand = c(0, 0)) +
          labs(y = "Wealth (reprocessed data)") +
          scale_color_manual(values = wes_palette("Zissou1"))

patchwork <- p1 + p2 & theme(legend.position = "bottom")
patchwork <- patchwork + plot_layout(guides = "collect")
patchwork

```

### 2023-06-12 oTree/HLPL/__init__.py

@@ -1,143 +1,0 @@
-import random
-
-from otree.api import *
-
-
-author = 'Your name here'
-doc = """
-Inspired by https://github.com/felixholzmeister/mpl
-"""
-
-
-class Constants(BaseConstants):
-    name_in_url = 'HLPL'
-    players_per_group = None
-    num_rounds = 1
-    num_choices = 11
-    lottery_price = 100
-
-
-class Subsession(BaseSubsession):
-    pass
-
-
-class Group(BaseGroup):
-    pass
-
-
-class Player(BasePlayer):
-    review_instructions = models.IntegerField(
-        doc="Counts the number of times a player reviews instructions.", initial=0, blank=True
-    )
-    review_contact = models.IntegerField(
-        doc="Counts the number of times a player reviews contact information.",
-        initial=0,
-        blank=True,
-    )
-    for j in range(1, Constants.num_choices + 1):
-        locals()['choice_' + str(j)] = models.StringField()
-    del j
-    random_draw = models.IntegerField()
-    choice_to_pay = models.StringField()
-    option_to_pay = models.StringField()
-    inconsistent = models.IntegerField()
-    switching_row = models.IntegerField()
-
-
-# FUNCTIONS
-def creating_session(subsession: Subsession):
-    n = Constants.num_choices
-    for p in subsession.get_players():
-        indices = [j for j in range(1, n + 1)]
-        # indices.append(n)
-        certainty_equivalents = [(k - 1) * 10 for k in indices]
-        form_fields = ["choice_" + str(k) for k in indices]
-        p.participant.vars["mpl_choices"] = list(zip(indices, form_fields, certainty_equivalents))
-        p.participant.vars["mpl_index_to_pay"] = random.choice(indices)
-        p.participant.vars["mpl_choice_to_pay"] = "choice_" + str(
-            p.participant.vars["mpl_index_to_pay"]
-        )
-        p.participant.vars['mpl_choices_made'] = [None for j in range(1, n + 1)]
-
-
-def set_payoffs(player: Player):
-    player.random_draw = random.randint(0, 100)
-    player.choice_to_pay = player.participant.vars["mpl_choice_to_pay"]
-    player.option_to_pay = getattr(player, player.choice_to_pay)
-    if player.option_to_pay == "lottery":
-        if player.random_draw <= 50:
-            player.payoff = Constants.lottery_price
-        else:
-            player.payoff = 0
-    else:
-        player.payoff = player.participant.vars["mpl_index_to_pay"] * 10
[…]

### 2023-06-12 oTree/HLPL/tests.py

@@ -1,20 +1,0 @@
-from otree.api import Currency as c, currency_range
-from . import *
-from otree.api import Bot
-
-import random
-
-
-class PlayerBot(Bot):
-    def play_round(self):
-        yield HLPL_Decision, dict(choice_1="lottery",
-                                             choice_2="lottery",
-                                             choice_3="lottery",
-                                             choice_4="lottery",
-                                             choice_5="lottery",
-                                             choice_6= random.choice(["lottery", "certainty"]),
-                                             choice_7="certainty",
-                                             choice_8="certainty",
-                                             choice_9="certainty",
-                                             choice_10="certainty",
-                                             choice_11="certainty")

### 2023-06-12 oTree/Intro/__init__.py

@@ -1,145 +1,0 @@
-import time
-
-from otree.api import *
-
-
-author = "Hauke Roggenkamp"
-doc = """
-Welcome participants, display instructions and comprehension questions.
-"""
-
-
-class Constants(BaseConstants):
-    name_in_url = "A_Intro"
-    players_per_group = None
-    num_rounds = 1
-    group_size = 4
-    num_others_per_group = group_size - 1
-    initial_endowment = 20
-    efficiency_factor = 1.5  # (MPCR) Marginal Per Capita Return per round
-    rate_of_return = (efficiency_factor - 1) * 100
-
-
-class Subsession(BaseSubsession):
-    pass
-
-
-class Group(BaseGroup):
-    pass
-
-
-class Player(BasePlayer):
-    # Tracking Fields
-    window_width = models.IntegerField(doc="Documents the respondent's browser window's width.")
-    window_height = models.IntegerField(doc="Documents the respondent's browser window's height.")
-    browser = models.StringField(doc="Documents the respondent's browser (incl. its version).")
-    # Wrong Answers
-    wrong_answer1_1 = models.IntegerField(
-        doc="Counts the number of wrong guesses for CQ1_1.", initial=0
-    )
-    wrong_answer1_2 = models.IntegerField(
-        doc="Counts the number of wrong guesses for CQ1_2.", initial=0
-    )
-    wrong_answer2_1 = models.IntegerField(
-        doc="Counts the number of wrong guesses for CQ2_1.", initial=0
-    )
-    wrong_answer2_2 = models.IntegerField(
-        doc="Counts the number of wrong guesses for CQ2_2.", initial=0
-    )
-    wrong_answer3_1 = models.IntegerField(
-        doc="Counts the number of wrong guesses for CQ3_1.", initial=0
-    )
-    wrong_answer3_2 = models.IntegerField(
-        doc="Counts the number of wrong guesses for CQ3_2.", initial=0
-    )
-    CQ1_1 = models.IntegerField(
-        doc="Comprehension Question 1.1",
-        # initial=int(Constants.initial_endowment),
-        blank=True,
-    )
-    CQ1_2 = models.IntegerField(
-        doc="Comprehension Question 1.2",
-        # initial=int(Constants.initial_endowment),
-        blank=True,
-    )
-    CQ2_1 = models.IntegerField(
-        doc="Comprehension Question 2.1",
[…]

### 2023-06-12 oTree/Intro/tests.py

@@ -1,18 +1,0 @@
-from otree.api import Currency as c, currency_range
-from . import *
-from otree.api import Bot
-from otree.api import Submission
-
-
-
-
-class PlayerBot(Bot):
-    def play_round(self):
-        yield Intro_Welcome, dict(window_width=1, window_height=1, browser="Chrome Canary")
-        yield Intro_Instructions, dict(CQ1_1=int(Constants.initial_endowment),
-                                             CQ1_2=int(Constants.initial_endowment),
-                                             CQ2_1=int(Constants.initial_endowment * Constants.efficiency_factor),
-                                             CQ2_2=int(Constants.initial_endowment * Constants.efficiency_factor),
-                                             #MCQ_1=['2', '3'], MCQ_2=['2', '3'],
-                                             CQ3_1=int(30 + Constants.efficiency_factor * 40 / Constants.group_size),
-                                             CQ3_2=True)

### 2023-06-12 oTree/Outro/__init__.py

@@ -1,234 +1,0 @@
-from otree.api import *
-
-
-author = "Hauke Roggenkamp"
-doc = """
-Elicit covariates and display results
-"""
-
-
-class Constants(BaseConstants):
-    name_in_url = 'Outro'
-    players_per_group = None
-    num_rounds = 1
-
-
-class Subsession(BaseSubsession):
-    pass
-
-
-class Group(BaseGroup):
-    pass
-
-
-class Player(BasePlayer):
-    # Gächter et al's (2017, JPE) Personality Questions
-    PQ01 = models.IntegerField(
-        widget=widgets.RadioSelect,
-        choices=[0, 1, 2, 3, 4, 5, 6],
-        label="Ich kann schnell denken.",
-        doc="I am a quick thinker",
-    )
-    PQ02 = models.IntegerField(
-        widget=widgets.RadioSelect,
-        choices=[0, 1, 2, 3, 4, 5, 6],
-        label="Ich fühle mich schnell angegriffen.",
-        doc="I get easily offended",
-    )
-    PQ03 = models.IntegerField(
-        widget=widgets.RadioSelect,
-        choices=[0, 1, 2, 3, 4, 5, 6],
-        label="Ich bin sehr zufrieden mit mir.",
-        doc="I am very satisfied with myself",
-    )
-    PQ04 = models.IntegerField(
-        widget=widgets.RadioSelect,
-        choices=[0, 1, 2, 3, 4, 5, 6],
-        label="Ich bin sehr auf andere angewiesen.",
-        doc="I am very dependent on others",
-    )
-    PQ05 = models.IntegerField(
-        widget=widgets.RadioSelect,
-        choices=[0, 1, 2, 3, 4, 5, 6],
-        label="Ich bin grundsätzlich glücklich.",
-        doc="Generally speaking, I am happy",
-    )
-    PQ06 = models.IntegerField(
-        widget=widgets.RadioSelect,
-        choices=[0, 1, 2, 3, 4, 5, 6],
-        label="Arbeit spielt eine wichtige Rolle in meinem Leben.",
-        doc="Work plays a very important role in my life",
-    )
-    PQ07 = models.IntegerField(
-        widget=widgets.RadioSelect,
-        choices=[0, 1, 2, 3, 4, 5, 6],
-        label="Familie spielt eine sehr wichtige Rolle in meinem Leben.",
-        doc="Family plays a very important role in my life",
-    )
[…]

### 2023-06-12 oTree/Outro/tests.py

@@ -1,28 +1,0 @@
-from otree.api import Currency as c, currency_range
-from . import *
-from otree.api import Bot
-
-import random
-
-class PlayerBot(Bot):
-    def play_round(self):
-        yield Outro_Personality, dict(PQ01=random.randint(0, 6),
-                                            PQ02=random.randint(0, 6),
-                                            PQ03=random.randint(0, 6),
-                                            PQ04=random.randint(0, 6),
-                                            PQ05=random.randint(0, 6),
-                                            PQ06=random.randint(0, 6),
-                                            PQ07=random.randint(0, 6),
-                                            PQ08=random.randint(0, 6),
-                                            PQ09=random.randint(0, 6),
-                                            PQ10=random.randint(0, 6),
-                                            PQ11=random.randint(0, 6),
-                                            PQ12=random.randint(0, 6),
-                                            PQ13=random.randint(0, 6),
-                                            PQ14=random.randint(0, 6))
-        yield Outro_Covariates, dict(Age=random.randint(18, 66),
-                                           Gender=random.choice(["diverse", "male", "female", "not specified"]),
-                                           Education=random.randint(0, 8),
-                                           Income=random.randint(0, 5))
-        yield Outro_CLICCS, dict(CLICCS1="lorem ipsum 1", CLICCS2="lorem ipsum 2")
-

### 2023-06-12 oTree/_REMOVE_SELF_BACKUP/HLPL/models.py

@@ -1,114 +1,0 @@
-from otree.api import (
-    models,
-    widgets,
-    BaseConstants,
-    BaseSubsession,
-    BaseGroup,
-    BasePlayer,
-    Currency as c,
-    currency_range,
-)
-
-import random
-
-author = 'Your name here'
-
-doc = """
-Inspired by https://github.com/felixholzmeister/mpl
-"""
-
-
-class Constants(BaseConstants):
-    name_in_url = 'HLPL'
-    players_per_group = None
-    num_rounds = 1
-    num_choices = 11
-    lottery_price = 100
-
-
-
-class Subsession(BaseSubsession):
-    def creating_session(self):
-        n = Constants.num_choices
-        for p in self.get_players():
-
-            indices = [j for j in range(1, n + 1)]
-            # indices.append(n)
-            certainty_equivalents = [(k-1)*10 for k in indices]
-
-            form_fields = ["choice_" + str(k) for k in indices]
-
-            p.participant.vars["mpl_choices"] = list(
-                zip(indices, form_fields, certainty_equivalents)
-            )
-
-            p.participant.vars["mpl_index_to_pay"] = random.choice(indices)
-            p.participant.vars["mpl_choice_to_pay"] = "choice_" + str(p.participant.vars["mpl_index_to_pay"])
-
-            p.participant.vars['mpl_choices_made'] = [None for j in range(1, n + 1)]
-
-
-class Group(BaseGroup):
-    pass
-
-
-class Player(BasePlayer):
-
-
-    review_instructions = models.IntegerField(doc="Counts the number of times a player reviews instructions.",
-                                              initial=0,
-                                              blank=True)
-    review_contact = models.IntegerField(doc="Counts the number of times a player reviews contact information.",
-                                         initial=0,
-                                         blank=True)
-
-
-
-
-    for j in range(1, Constants.num_choices + 1):
-        locals()['choice_' + str(j)] = models.StringField()
-    del j
-
-    random_draw = models.IntegerField()
-    choice_to_pay = models.StringField()
-    option_to_pay = models.StringField()
-    inconsistent = models.IntegerField()
-    switching_row = models.IntegerField()
-
-    def set_payoffs(self):
-        self.random_draw = random.randint(0, 100)
-        self.choice_to_pay = self.participant.vars["mpl_choice_to_pay"]
-        self.option_to_pay = getattr(self, self.choice_to_pay)
-
-        if self.option_to_pay == "lottery":
[…]

### 2023-06-12 oTree/_REMOVE_SELF_BACKUP/HLPL/pages.py

@@ -1,48 +1,0 @@
-from otree.api import Currency as c, currency_range
-from ._builtin import Page, WaitPage
-from .models import Constants
-
-
-class HLPL_Decision(Page):
-    form_model = "player"
-
-    def is_displayed(self):
-        if not self.participant.vars["is_residual_player"]:
-            return True
-
-    def get_form_fields(self):
-        # unzip list of form_fields from <mpl_choices> list
-        form_fields = [list(t) for t in zip(*self.participant.vars['mpl_choices'])][1]
-        form_fields.extend(["review_instructions", "review_contact"])
-        return form_fields
-
-    def vars_for_template(self):
-        return dict(
-            choices=self.player.participant.vars["mpl_choices"]
-        )
-
-    def js_vars(self):
-        return dict(
-            template="risk",
-        )
-
-    def get_timeout_seconds(self):
-        if self.participant.vars.get("is_dropout"):
-            return 1  # instant timeout, 1 second
-
-    def before_next_page(self):
-        form_fields = [list(t) for t in zip(*self.participant.vars['mpl_choices'])][1]
-        indices = [list(t) for t in zip(*self.participant.vars['mpl_choices'])][0]
-
-        for j, choice in zip(indices, form_fields):
-            choice_i = getattr(self.player, choice)
-            self.participant.vars['mpl_choices_made'][j - 1] = choice_i
-
-        # set payoff
-        self.player.set_payoffs()
-        # determine consistency
-        self.player.set_consistency()
-        # set switching row
-        self.player.set_switching_row()
-
-page_sequence = [HLPL_Decision]

### 2023-06-12 oTree/_REMOVE_SELF_BACKUP/HLPL/tests.py

@@ -1,20 +1,0 @@
-from otree.api import Currency as c, currency_range
-from . import pages
-from ._builtin import Bot
-from .models import Constants
-import random
-
-
-class PlayerBot(Bot):
-    def play_round(self):
-        yield pages.HLPL_Decision, dict(choice_1="lottery",
-                                             choice_2="lottery",
-                                             choice_3="lottery",
-                                             choice_4="lottery",
-                                             choice_5="lottery",
-                                             choice_6= random.choice(["lottery", "certainty"]),
-                                             choice_7="certainty",
-                                             choice_8="certainty",
-                                             choice_9="certainty",
-                                             choice_10="certainty",
-                                             choice_11="certainty")

### 2023-06-12 oTree/_REMOVE_SELF_BACKUP/Intro/models.py

@@ -1,107 +1,0 @@
-from otree.api import (
-    models,
-    widgets,
-    BaseConstants,
-    BaseSubsession,
-    BaseGroup,
-    BasePlayer,
-    Currency as c,
-    currency_range,
-)
-
-
-author = "Hauke Roggenkamp"
-
-doc = """
-Welcome participants, display instructions and comprehension questions.
-"""
-
-
-class Constants(BaseConstants):
-    name_in_url = "A_Intro"
-    players_per_group = None
-    num_rounds = 1
-
-    group_size = 4
-    num_others_per_group = group_size - 1
-    initial_endowment = 20
-    efficiency_factor = 1.5 # (MPCR) Marginal Per Capita Return per round
-    rate_of_return = (efficiency_factor - 1)*100
-
-
-class Subsession(BaseSubsession):
-    pass
-
-
-class Group(BaseGroup):
-    pass
-
-
-class Player(BasePlayer):
-    # Tracking Fields
-    window_width = models.IntegerField(doc="Documents the respondent's browser window's width.")
-    window_height = models.IntegerField(doc="Documents the respondent's browser window's height.")
-    browser = models.StringField(doc="Documents the respondent's browser (incl. its version).")
-
-    # Wrong Answers
-    wrong_answer1_1 = models.IntegerField(doc="Counts the number of wrong guesses for CQ1_1.", initial=0)
-    wrong_answer1_2 = models.IntegerField(doc="Counts the number of wrong guesses for CQ1_2.", initial=0)
-    wrong_answer2_1 = models.IntegerField(doc="Counts the number of wrong guesses for CQ2_1.", initial=0)
-    wrong_answer2_2 = models.IntegerField(doc="Counts the number of wrong guesses for CQ2_2.", initial=0)
-    wrong_answer3_1 = models.IntegerField(doc="Counts the number of wrong guesses for CQ3_1.", initial=0)
-    wrong_answer3_2 = models.IntegerField(doc="Counts the number of wrong guesses for CQ3_2.", initial=0)
-
-
-
-    CQ1_1 = models.IntegerField(doc="Comprehension Question 1.1",
-                                # initial=int(Constants.initial_endowment),
-                                blank = True)
-    def CQ1_1_error_message(self, value):
-        if value != int(Constants.initial_endowment):
-            self.wrong_answer1_1 += 1
-            return "Leider falsch."
-
-    CQ1_2 = models.IntegerField(doc="Comprehension Question 1.2",
[…]

### 2023-06-12 oTree/_REMOVE_SELF_BACKUP/Intro/pages.py

@@ -1,25 +1,0 @@
-from otree.api import Currency as c, currency_range
-from ._builtin import Page, WaitPage
-from .models import Constants
-import time
-
-
-class Intro_Welcome(Page):
-    form_model = "player"
-    form_fields = ["window_width", "window_height", "browser"]
-
-
-class Intro_Instructions(Page):
-    form_model = "player"
-    form_fields = ["CQ1_1", "CQ1_2", "CQ2_1", "CQ2_2", "CQ3_1", "CQ3_2"]
-
-    def js_vars(self):
-        return dict(
-            template="instructions",
-        )
-
-
-    def before_next_page(self):
-        self.participant.vars['wait_page_arrival'] = time.time()
-
-page_sequence = [Intro_Welcome, Intro_Instructions]

### 2023-06-12 oTree/_REMOVE_SELF_BACKUP/Intro/tests.py

@@ -1,18 +1,0 @@
-from otree.api import Currency as c, currency_range
-from . import pages
-from ._builtin import Bot
-from otree.api import Submission
-
-from .models import Constants
-
-
-class PlayerBot(Bot):
-    def play_round(self):
-        yield pages.Intro_Welcome, dict(window_width=1, window_height=1, browser="Chrome Canary")
-        yield pages.Intro_Instructions, dict(CQ1_1=int(Constants.initial_endowment),
-                                             CQ1_2=int(Constants.initial_endowment),
-                                             CQ2_1=int(Constants.initial_endowment * Constants.efficiency_factor),
-                                             CQ2_2=int(Constants.initial_endowment * Constants.efficiency_factor),
-                                             #MCQ_1=['2', '3'], MCQ_2=['2', '3'],
-                                             CQ3_1=int(30 + Constants.efficiency_factor * 40 / Constants.group_size),
-                                             CQ3_2=True)

### 2023-06-12 oTree/_REMOVE_SELF_BACKUP/Outro/models.py

@@ -1,107 +1,0 @@
-from otree.api import (
-    models,
-    widgets,
-    BaseConstants,
-    BaseSubsession,
-    BaseGroup,
-    BasePlayer,
-    Currency as c,
-    currency_range,
-)
-
-
-author = "Hauke Roggenkamp"
-
-doc = """
-Elicit covariates and display results
-"""
-
-
-class Constants(BaseConstants):
-    name_in_url = 'Outro'
-    players_per_group = None
-    num_rounds = 1
-
-
-class Subsession(BaseSubsession):
-    pass
-
-
-class Group(BaseGroup):
-    pass
-
-
-class Player(BasePlayer):
-
-    # Gächter et al's (2017, JPE) Personality Questions
-    PQ01 = models.IntegerField(widget=widgets.RadioSelect, choices=[0, 1, 2, 3, 4, 5, 6], label="Ich kann schnell denken.", doc="I am a quick thinker")
-    PQ02 = models.IntegerField(widget=widgets.RadioSelect, choices=[0, 1, 2, 3, 4, 5, 6], label="Ich fühle mich schnell angegriffen.", doc="I get easily offended")
-    PQ03 = models.IntegerField(widget=widgets.RadioSelect, choices=[0, 1, 2, 3, 4, 5, 6], label="Ich bin sehr zufrieden mit mir.", doc="I am very satisfied with myself")
-    PQ04 = models.IntegerField(widget=widgets.RadioSelect, choices=[0, 1, 2, 3, 4, 5, 6], label="Ich bin sehr auf andere angewiesen.", doc="I am very dependent on others")
-    PQ05 = models.IntegerField(widget=widgets.RadioSelect, choices=[0, 1, 2, 3, 4, 5, 6], label="Ich bin grundsätzlich glücklich.", doc="Generally speaking, I am happy")
-    PQ06 = models.IntegerField(widget=widgets.RadioSelect, choices=[0, 1, 2, 3, 4, 5, 6], label="Arbeit spielt eine wichtige Rolle in meinem Leben.", doc="Work plays a very important role in my life")
-    PQ07 = models.IntegerField(widget=widgets.RadioSelect, choices=[0, 1, 2, 3, 4, 5, 6], label="Familie spielt eine sehr wichtige Rolle in meinem Leben.", doc="Family plays a very important role in my life")
[…]

### 2023-06-12 oTree/_REMOVE_SELF_BACKUP/Outro/pages.py

@@ -1,51 +1,0 @@
-from otree.api import Currency as c, currency_range
-from ._builtin import Page, WaitPage
-from .models import Constants
-
-
-class Outro_Personality(Page):
-    form_model = "player"
-    form_fields = ["PQ01", "PQ02", "PQ03", "PQ04", "PQ05",
-                   "PQ06", "PQ07", "PQ08", "PQ09", "PQ10",
-                   "PQ11", "PQ12", "PQ13", "PQ14"]
-
-    def vars_for_template(self):
-        return dict(
-            choices=[0, 1, 2, 3, 4, 5, 6],
-        )
-
-class Outro_Covariates(Page):
-    form_model = "player"
-    form_fields = ["Age", "Gender", "Education", "Income"]
-
-
-class Outro_CLICCS(Page):
-    form_model = "player"
-    form_fields = ["CLICCS1", "CLICCS2"]
-
-
-
-class Outro_Final(Page):
-    form_model = "player"
-
-    def vars_for_template(self):
-        return dict(
-            is_residual_player=self.participant.vars["is_residual_player"],
-            final_payoff=self.participant.payoff_plus_participation_fee().to_real_world_currency(self.session),
-            payment_data_survey_link='https://www.limesurvey.uni-hamburg.de/index.php/162819?token=' + str(
-                self.participant.label)
-
-        )
-
-    def js_vars(self):
-        return dict(
-            flat_fee=self.session.config["participation_fee"],
-            exchange_rate=self.session.config["real_world_currency_per_point"],
-            template="final",
-            current_round=self.session.config["num_rounds"],
-            euros=self.participant.vars["euros"],
-            num_rounds=self.session.config["num_rounds"],
-        )
-
-
-page_sequence = [Outro_Personality, Outro_Covariates, Outro_CLICCS, Outro_Final]

### 2023-06-12 oTree/_REMOVE_SELF_BACKUP/Outro/tests.py

@@ -1,28 +1,0 @@
-from otree.api import Currency as c, currency_range
-from . import pages
-from ._builtin import Bot
-from .models import Constants
-import random
-
-class PlayerBot(Bot):
-    def play_round(self):
-        yield pages.Outro_Personality, dict(PQ01=random.randint(0, 6),
-                                            PQ02=random.randint(0, 6),
-                                            PQ03=random.randint(0, 6),
-                                            PQ04=random.randint(0, 6),
-                                            PQ05=random.randint(0, 6),
-                                            PQ06=random.randint(0, 6),
-                                            PQ07=random.randint(0, 6),
-                                            PQ08=random.randint(0, 6),
-                                            PQ09=random.randint(0, 6),
-                                            PQ10=random.randint(0, 6),
-                                            PQ11=random.randint(0, 6),
-                                            PQ12=random.randint(0, 6),
-                                            PQ13=random.randint(0, 6),
-                                            PQ14=random.randint(0, 6))
-        yield pages.Outro_Covariates, dict(Age=random.randint(18, 66),
-                                           Gender=random.choice(["diverse", "male", "female", "not specified"]),
-                                           Education=random.randint(0, 8),
-                                           Income=random.randint(0, 5))
-        yield pages.Outro_CLICCS, dict(CLICCS1="lorem ipsum 1", CLICCS2="lorem ipsum 2")
-

### 2023-06-12 oTree/_REMOVE_SELF_BACKUP/dPGG/models.py

@@ -1,237 +1,0 @@
-from otree.api import (
-    models,
-    widgets,
-    BaseConstants,
-    BaseSubsession,
-    BaseGroup,
-    BasePlayer,
-    Currency as c,
-    currency_range,
-)
-
-import math
-import random
-import time
-
-author = "Hauke Roggenkamp"
-
-doc = """
-Dynamic Public Goods Game where the current round's earnings determine the next round's endowment
-"""
-
-
-class Constants(BaseConstants):
-    name_in_url = "dPGG"
-    players_per_group = 4 # adjust Constants.group_size in A_Intro App when adjusting this
-    num_others_per_group = players_per_group - 1
-    num_rounds = 10
-    initial_endowment = 20
-    efficiency_factor = 1.5 # /4 = (MPCR) Marginal Per Capita Return per round
-    rate_of_return = (efficiency_factor - 1)*100
-
-    safe_rounds = 0 # number of rounds without any risk
-    threshold = 0.5 # fraction of a group's endowment that has to be contributed such that no disaster can occur
-    belief_elicitation_round = 1
-    elicitation_bonus = 30 # points
-    timeout = 4 # minutes
-    patience = 10 # minutes
-    patience_bonus = 20 # points
-
-
-
-class Subsession(BaseSubsession):
-    def creating_session(self):
-        print("lets go")
-        if self.round_number == 1:
-            for p in self.get_players():
-                p.participant.vars["belief_elicitation_round"] = Constants.belief_elicitation_round
-                p.participant.vars["endowments"] = []
-                p.participant.vars["stock"] = []
-                p.participant.vars["euros"] = []
-                p.participant.vars["is_dropout"] = False
-                p.participant.vars["is_residual_player"] = False
-                if not "wait_page_arrival" in p.participant.vars:
-                    p.participant.vars["wait_page_arrival"] = time.time()
-
-    def group_by_arrival_time_method(self, waiting_players):
-        if len(waiting_players) >= Constants.players_per_group:
-            return waiting_players[:Constants.players_per_group]
-        for player in waiting_players:
-            player.wait_time_left = int(math.ceil(Constants.patience - (time.time() - player.participant.vars['wait_page_arrival']) / 60))
-            if player.waiting_too_long():
-                player.participant.vars["is_residual_player"] = True
-                player.group.residual = True
-                # make a single-player group.
-                return [player]
-
-
-
-class Group(BaseGroup):
-
[…]

### 2023-06-12 oTree/_REMOVE_SELF_BACKUP/dPGG/pages.py

@@ -1,184 +1,0 @@
-from otree.api import Currency as c, currency_range
-from ._builtin import Page, WaitPage
-from .models import Constants
-import random
-
-class dPGG_InitialWaitPage(WaitPage):
-    template_name = 'dPGG/dPGG_InitialWaitPage.html'
-    group_by_arrival_time = True
-
-    def is_displayed(self):
-        if self.round_number == 1:
-            return True
-
-
-class dPGG_Belief(Page):
-    form_model = "player"
-    form_fields = ["review_instructions", "review_contact", "belief"]
-
-    timeout_seconds = Constants.timeout * 60
-
-    def is_displayed(self):
-        if not self.participant.vars["is_residual_player"]:
-            if self.session.config["belief_elicitation"]:
-                if self.round_number == Constants.belief_elicitation_round:
-                    return True
-
-    def js_vars(self):
-        return dict(
-            timeout=Constants.timeout,
-            template="decision",
-            current_round=self.round_number,
-            endowments=self.participant.vars["endowments"],
-            num_rounds=self.session.config["num_rounds"],
-        )
-
-    def before_next_page(self):
-        if self.timeout_happened:
-            self.player.belief = 0
-            self.participant.vars["is_dropout"] = True
-            self.player.is_dropout = True
-            self.group.bot_active = True
-
-
-class dPGG_Decision(Page):
-    form_model = "player"
-    form_fields = ["review_instructions", "review_contact", "contribution"]
-
-    def get_timeout_seconds(self):
-        if self.participant.vars.get("is_dropout"):
-            return 1  # instant timeout, 1 second
-        else:
-            if self.round_number == 1:
-                return 2.5 * Constants.timeout * 60
-            else:
-                return Constants.timeout * 60
-
-    def before_next_page(self):
-        if self.timeout_happened:
-            self.player.contribution = random.randint(0, self.player.endowment)
-            self.participant.vars["is_dropout"] = True
-            self.player.is_dropout = True
-            self.group.bot_active = True
-
-
-    def is_displayed(self):
-        if not self.participant.vars["is_residual_player"]:
-            if self.round_number <= self.session.config["num_rounds"]:
-                return True
-
-    def vars_for_template(self):
-        EWE = 0
-        diff = 0
-        bot_active = False
-        if self.round_number > 1:
-            EWE = self.group.in_round(self.round_number - 1).EWE
[…]

### 2023-06-12 oTree/_REMOVE_SELF_BACKUP/dPGG/tests.py

@@ -1,31 +1,0 @@
-from otree.api import Currency as c, currency_range
-from . import pages
-from ._builtin import Bot
-from otree.api import Submission
-from .models import Constants
-import random
-
-
-class PlayerBot(Bot):
-    def play_round(self):
-        if self.round_number <= self.session.config["num_rounds"]:
-            if self.round_number == Constants.belief_elicitation_round:
-                if self.session.config["belief_elicitation"]:
-                    yield pages.dPGG_Belief, dict(belief=random.randint(int(self.player.endowment/2),
-                                                                        self.player.endowment)*Constants.num_others_per_group
-                                                  )
-            yield Submission(pages.dPGG_Decision, # in Gächter et al, subjects first contribute around 60%, then 30%
-                             dict(contribution=int(self.player.endowment/2)),
-                             # dict(contribution=int((100 - 6 * self.round_number)/100 * random.randint(int(self.player.endowment/5*2.5), #HI==2.5,LO==2
-                             #                                                                           int(self.player.endowment/5*5))  #HI==5,  LO==3.5
-                             #                       )
-                             #      ),
-                             check_html=False)
-            if self.round_number == self.session.config["num_rounds"]:
-                yield pages.dPGG_Results
-                if random.randint(0, 100) > 90:
-                    a = 0
-                else:
-                    a = random.randint(1, 3)
-                yield pages.dPGG_Comprehension, dict(comprehension=a)
-                yield pages.dPGG_Donation, dict(donation=random.randint(0, int(self.player.endowment/2)))

### 2023-06-12 oTree/dPGG/__init__.py

@@ -1,449 +1,0 @@
-import math
-import random
-import time
-
-from otree.api import *
-
-
-author = "Hauke Roggenkamp"
-doc = """
-Dynamic Public Goods Game where the current round's earnings determine the next round's endowment
-"""
-
-
-class Constants(BaseConstants):
-    name_in_url = "dPGG"
-    players_per_group = 4  # adjust Constants.group_size in A_Intro App when adjusting this
-    num_others_per_group = players_per_group - 1
-    num_rounds = 10
-    initial_endowment = 20
-    efficiency_factor = 1.5  # /4 = (MPCR) Marginal Per Capita Return per round
-    rate_of_return = (efficiency_factor - 1) * 100
-    safe_rounds = 0  # number of rounds without any risk
-    threshold = 0.5  # fraction of a group's endowment that has to be contributed such that no disaster can occur
-    belief_elicitation_round = 1
-    elicitation_bonus = 30  # points
-    timeout = 4  # minutes
-    patience = 10  # minutes
-    patience_bonus = 20  # points
-
-
-class Subsession(BaseSubsession):
-    pass
-
-
-class Group(BaseGroup):
-    residual = models.BooleanField(initial=False, doc="if true, group is incomplete")
-    EWE = models.BooleanField(initial=False, doc="if true, extreme weather event occurred")
-    total_contribution = models.IntegerField(doc="sum of contributions in this round")
-    average_contribution = models.FloatField(doc="average contribution in this round")
-    individual_share = models.IntegerField(
-        doc="individual share each player receives from this round's contributions"
-    )
-    bot_active = models.BooleanField(
-        doc="denotes whether player in group dropped out such that a bot takes over", initial=False
-    )
-    wealth = models.IntegerField(doc="sum of endowments at the beginning of a round")
-
-
-class Player(BasePlayer):
-    comprehension = models.IntegerField(
-        doc="Respondent's understanding of the tasks",
-        label="Haben Sie die Aufgabe gut verstanden?",
-        choices=[[0, "Nein"], [1, "Eher nicht"], [2, "Eher schon"], [3, "Ja"]],
-        widget=widgets.RadioSelect,
-    )
-    donation = models.IntegerField(doc="Participant's donation (in points) for carbon offsetting")
-    review_instructions = models.IntegerField(
-        doc="Counts the number of times a player reviews instructions.", initial=0, blank=True
-    )
-    review_contact = models.IntegerField(
[…]

### 2023-06-12 oTree/dPGG/tests.py

@@ -1,31 +1,0 @@
-from otree.api import Currency as c, currency_range
-from . import *
-from otree.api import Bot
-from otree.api import Submission
-
-import random
-
-
-class PlayerBot(Bot):
-    def play_round(self):
-        if self.round_number <= self.session.config["num_rounds"]:
-            if self.round_number == Constants.belief_elicitation_round:
-                if self.session.config["belief_elicitation"]:
-                    yield dPGG_Belief, dict(belief=random.randint(int(self.player.endowment/2),
-                                                                        self.player.endowment)*Constants.num_others_per_group
-                                                  )
-            yield Submission(dPGG_Decision, # in Gächter et al, subjects first contribute around 60%, then 30%
-                             dict(contribution=int(self.player.endowment/2)),
-                             # dict(contribution=int((100 - 6 * self.round_number)/100 * random.randint(int(self.player.endowment/5*2.5), #HI==2.5,LO==2
-                             #                                                                           int(self.player.endowment/5*5))  #HI==5,  LO==3.5
-                             #                       )
-                             #      ),
-                             check_html=False)
-            if self.round_number == self.session.config["num_rounds"]:
-                yield dPGG_Results
-                if random.randint(0, 100) > 90:
-                    a = 0
-                else:
-                    a = random.randint(1, 3)
-                yield dPGG_Comprehension, dict(comprehension=a)
-                yield dPGG_Donation, dict(donation=random.randint(0, int(self.player.endowment/2)))

### 2023-06-12 oTree/settings.py

@@ -1,69 +1,0 @@
-from os import environ
-
-SESSION_CONFIGS = [
-    dict(
-        name="B_GMTV",
-        display_name="B_GMTV Replication",
-        num_rounds=10,
-        num_demo_participants=4,
-        risk=0.0,
-        belief_elicitation=False,
-        app_sequence=["A_Intro", "dPGG", "HLPL", "Outro"]
-    ),
-    #     dict(
-    #     name="HLPL",
-    #     display_name="Hault & Laury Price List",
-    #     num_rounds=10,
-    #     num_demo_participants=1,
-    #     app_sequence=["HLPL"]
-    # )
-]
-
-# if you set a property in SESSION_CONFIG_DEFAULTS, it will be inherited by all configs
-# in SESSION_CONFIGS, except those that explicitly override it.
-# the session config can be accessed from methods in your apps as self.session.config,
-# e.g. self.session.config['participation_fee']
-
-SESSION_CONFIG_DEFAULTS = dict(
-    real_world_currency_per_point=0.05,
-    participation_fee=5.00,
-    doc=""
-)
-
-# ISO-639 code
-# for example: de, fr, ja, ko, zh-hans
-LANGUAGE_CODE = "de"
-
-# e.g. EUR, GBP, CNY, JPY
-REAL_WORLD_CURRENCY_CODE = "EUR"
-USE_POINTS = True
-
-ROOMS = [
-    {
-        'name': '2021_07_01_17_00',
-        'display_name': '2021_07_01_17_00',
-        'participant_label_file': '_rooms/2021_07_01_17_00.txt',
-    },
-    {
-        'name': '2021_07_03_15_00',
-        'display_name': '2021_07_03_15_00',
-        'participant_label_file': '_rooms/2021_07_03_15_00.txt',
-    },
-    {
-        'name': '2021_07_09_15_00',
-        'display_name': '2021_07_09_15_00',
-        'participant_label_file': '_rooms/2021_07_09_15_00.txt',
-    }
-]
-
-ADMIN_USERNAME = 'admin'
-# for security, best to set admin password in an environment variable
-ADMIN_PASSWORD = environ.get('OTREE_ADMIN_PASSWORD')
-
-DEMO_PAGE_INTRO_HTML = """ """
-
-# SECRET_KEY = environ.get('OTREE_SECRET_KEY')
-SECRET_KEY = ""
-
-# if an app is included in SESSION_CONFIGS, you don't need to list it here
-INSTALLED_APPS = ['otree']

### 2023-06-12 otreeLite/B_Clubs/__init__.py

@@ -1,246 +1,0 @@
-from otree.api import *
-import time
-import math
-
-doc = """
-Public Bads Game
-"""
-
-
-class C(BaseConstants):
-    NAME_IN_URL = "Clubs"
-    PLAYERS_PER_GROUP = 2
-    NUM_ROUNDS = 10
-    PATIENCE = 1
-    PATIENCE_BONUS = 20
-    ENDOWMENT = 60
-    EFFICIENCY_FACTOR = 1
-    TIMEOUT = 4
-    MEMBER_ROLE = "Member"
-    OUTSIDER_ROLE = "Outsider"
-
-
-
-class Subsession(BaseSubsession):
-    pass
-
-
-class Group(BaseGroup):
-    residual = models.BooleanField(initial=False, doc="if true, group is incomplete")
-    threshold_investment = models.IntegerField(doc="maximum investment allowed to stay in the club", initial = 10)
-    total_investment = models.IntegerField(doc="sum of all investments in this period")
-    average_investment = models.FloatField(doc="average investment in this round")
-
-    club_size = models.IntegerField(doc="number of club members", initial = 0)
-    club_investment = models.IntegerField(doc="sum of club members' investments in this period", initial = 0)
-    average_club_investment = models.IntegerField(doc="average of club members' investments in this period", initial = 0)
-    average_club_payoff = models.IntegerField(doc="average of club members' payoff in this period", initial = 0)
-
-    outsiders_size = models.IntegerField(doc="number of outsiders", initial = 0)
-    outsiders_investment = models.IntegerField(doc="sum of outsiders' investments in this period", initial = 0)
-    average_outsider_investment = models.IntegerField(doc="average of outsiders' investments in this period", initial = 0)
-    average_outsider_payoff = models.IntegerField(doc="average of outsiders' payoff in this period", initial = 0)
-
-
-wealth = models.IntegerField(doc="sum of endowments at the beginning of a round")
-
-
-
-class Player(BasePlayer):
-    payoff_int = models.IntegerField(doc="payoffs as integers")
-    wait_time_left = models.IntegerField(doc="denotes the time a player has to wait for others to arrive on WaitPage")
-    join = models.StringField(doc="whether the player wants to join the club", initial = "", blank = True)
-    member = models.BooleanField(doc="whether the player is a member the club", initial = False, blank = True)
-    investment = models.IntegerField(min=0, max=C.ENDOWMENT, doc="the player's investment in this round")
[…]

### 2023-06-12 otreeLite/B_EWE/__init__.py

@@ -1,242 +1,0 @@
-from otree.api import *
-import math
-import time
-import random
-
-
-
-doc = """
-Your app description
-"""
-
-# MODELS
-class C(BaseConstants):
-    NAME_IN_URL = 'EWE'
-    PLAYERS_PER_GROUP = 3
-    NUM_ROUNDS = 10
-    EARNINGS_TEMPLATE = "A_Intro/C_Earnings.html"
-    SHOCKS_TEMPLATE = "A_Intro/D_Shocks.html"
-    PATIENCE = 1
-    PATIENCE_BONUS = 20
-    # INITIAL_ENDOWMENT = 20 called initial_endowment in session configs
-    EFFICIENCY_FACTOR = 1.5
-    TIMEOUT = 4
-    # extreme weather constants
-    # DANGER = 0.2 called risk in session configs
-    DAMAGE = 0.5
-
-
-class Subsession(BaseSubsession):
-    pass
-
-
-class Group(BaseGroup):
-    residual = models.BooleanField(initial=False, doc="if true, group is incomplete")
-    total_contribution = models.IntegerField(doc="sum of contributions in this round")
-    average_contribution = models.FloatField(doc="average contribution in this round")
-    individual_share = models.IntegerField(doc="individual share each player receives from this round's contributions")
-    wealth = models.IntegerField(doc="sum of endowments at the beginning of a round")
-    # extreme weather variables
-    EWE = models.BooleanField(initial=False, doc="if true, extreme weather event occurred")
-    damage_factor = models.FloatField(doc="how much of an individual's income will be destroyed by an EWE")
-
-
-class Player(BasePlayer):
-    wait_time_left = models.IntegerField(doc="denotes the time a player has to wait for others to arrive on WaitPage")
-    endowment = models.IntegerField(doc="the player's endowment in this round (equals her stock of last round)")
-    contribution = models.IntegerField(min=0, doc="the player's contribution in this round")
-    stock = models.IntegerField(doc="accumulated earnings of played rounds")
-    gain = models.IntegerField(doc="a round's earnings.")
-    returns = models.IntegerField(initial=0, doc="earnings if there was no ewe")
-    total_damage = models.IntegerField(initial=0, doc="damage caused by the ewe")
-    MPCR = models.FloatField(doc="marginal per capita return")
-
-    formula_shown = models.BooleanField(doc="True if participant wanted to see the formula that explains earnings.",
-                                        initial=False)
[…]

### 2023-06-14 analysis/R/04_rmd/01_dataGMTV.Rmd
improve reproducability

--- 2022-10-08 analysis/reports/rmd/01_dataGMTV.Rmd
@@
 
-Having replicated Gaechter et al.'s main figures (more or less) the next step is to prepare the data we obtain in our experiment for the analysis.
-This will be done in the second report using simulated data.^[Eventually, one can use that report and apply it to the actual data.]
+Having replicated Gächter et al.'s main figures (more or less) the next step is to prepare the data we obtain in our experiment for the analysis. This will be done in the second report using my data.

### 2023-06-14 analysis/R/04_rmd/03_dataAnalyses.Rmd
improve reproducability

--- 2021-08-11 analysis/reports/rmd/03_dataAnalyses.Rmd
@@
 
-- We replicate a public goods experiment with dynamic interdependency and find similar results as @GACHTER2017.
+- We replicate a public goods experiment with dynamic interdependency and find similar results as @GMTV2017.
 - Absolute contributions increase over time.
@@
 
-In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree].
+In an attempt to incorporate uncertainty to @GMTV2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree].
 This experiment  replicated Gächter et al.'s NOPUNISH 10-round treatment arm as close as possible (given the remote circumstances).
@@
 
-stargazer(lm(formula = stock ~ treatment, data = main_all),
-          lm(formula = stock ~ treatment, data = main_poor),
-          lm(formula = stock ~ treatment, data = main_rich),
+m1 <- lm(formula = stock ~ treatment, data = main_all)
+m2 <- lm(formula = stock ~ treatment, data = main_poor)
+m3 <- lm(formula = stock ~ treatment, data = main_rich)
+
+stargazer(m1,
+          m2,
+          m3,
 
@@
 
-stargazer(lm(formula = gini ~ treatment, data = main_all),
-          lm(formula = gini ~ treatment, data = main_poor),
-          lm(formula = gini ~ treatment, data = main_rich),
+m1 <- lm(formula = gini ~ treatment, data = main_all)
+m2 <- lm(formula = gini ~ treatment, data = main_poor)
+m3 <- lm(formula = gini ~ treatment, data = main_rich)
+
+stargazer(m1,
+          m2,
+          m3,
 
@@
 
-stargazer(lm(formula = gender ~ treatment, data = covs),
-          lm(formula = age ~ treatment, data = covs),
-          lm(formula = switching_row ~ treatment, data = covs),
-          lm(formula = donation ~ treatment, data = covs),
+m1 <- lm(formula = gender ~ treatment, data = covs)
+m2 <- lm(formula = age ~ treatment, data = covs)
+m3 <- lm(formula = switching_row ~ treatment, data = covs)
+m4 <- lm(formula = donation ~ treatment, data = covs)
+
+stargazer(m1,
+          m2,
+          m3,
+          m4,
 
@@
 
-stargazer(lm(formula = pq01 ~ treatment, data = covs),
-          lm(formula = pq02 ~ treatment, data = covs),
-          lm(formula = pq03 ~ treatment, data = covs),
-          lm(formula = pq04 ~ treatment, data = covs),
-          lm(formula = pq05 ~ treatment, data = covs),
+m5 <- lm(formula = pq01 ~ treatment, data = covs)
+m6 <- lm(formula = pq02 ~ treatment, data = covs)
+m7 <- lm(formula = pq03 ~ treatment, data = covs)
+m8 <- lm(formula = pq04 ~ treatment, data = covs)
+m9 <- lm(formula = pq05 ~ treatment, data = covs)
+
+stargazer(m5,
+          m6,
+          m7,
+          m8,
+          m9,
 
@@
 
-stargazer(lm(formula = pq06 ~ treatment, data = covs),
-          lm(formula = pq07 ~ treatment, data = covs),
-          lm(formula = pq08 ~ treatment, data = covs),
-          lm(formula = pq09 ~ treatment, data = covs),
-          lm(formula = pq10 ~ treatment, data = covs),
+m10 <- lm(formula = pq06 ~ treatment, data = covs)
+m11 <- lm(formula = pq07 ~ treatment, data = covs)
+m12 <- lm(formula = pq08 ~ treatment, data = covs)
+m13 <- lm(formula = pq09 ~ treatment, data = covs)
+m14 <- lm(formula = pq10 ~ treatment, data = covs)
+
+stargazer(m10,
+          m11,
+          m12,
+          m13,
+          m14,
 
@@
 
-stargazer(lm(formula = pq11 ~ treatment, data = covs),
-          lm(formula = pq12 ~ treatment, data = covs),
-          lm(formula = pq13 ~ treatment, data = covs),
-          lm(formula = pq14 ~ treatment, data = covs),
+m15 <- lm(formula = pq11 ~ treatment, data = covs)
+m16 <- lm(formula = pq12 ~ treatment, data = covs)
+m17 <- lm(formula = pq13 ~ treatment, data = covs)
+m18 <- lm(formula = pq14 ~ treatment, data = covs)
+stargazer(m15,
+          m16,
+          m17,
+          m18,
 
@@
 ```
-
-# Hamburg: How do Students compare to non-Students?
-
-This section considers the replication data only.
-Doing so, we'll exploit the circumstance that we recruited from both the convenience or "student" sample as well as the non-convenience sample _(Hamburg Panel)_ and analyze the differences between the two.
-
-```{r sample0, results = "asis", warning = FALSE, fig.cap = "test"}
-
-if(knitr::is_html_output()){
-  type <- "html"
-} else {
-  type = "latex"
-}
-
-students <- R1[treatment == "replication" & student == TRUE, ownContribution]
-HHpanel  <- R1[treatment == "replication" & student == FALSE, ownContribution]
-
-rows <- sapply(X = list(students, HHpanel), FUN = NROW) %>% max()
-temp <- data.frame(Students = c(students, rep(NA, rows - NROW(students))),
-                   `HH-panel` = c(HHpanel, rep(NA, rows - NROW(HHpanel))))
-
-stargazer(temp,
-          summary.stat = c("mean", "median","sd", "max", "min", "n"),
-          type = type, 
-          flip = TRUE, 
-          header=FALSE)
-
-rs1 <- wilcox.test(students, 
-                   HHpanel,
-                   exact = FALSE)$p.value %>% 
-  round(digits = 4) %>% 
-  formatC(format = "f", 
-          digits = 4)
-```
-
-We start by looking at the initial contributions.
-As Table 5 illustrates, there is no difference in averages, standard deviation or the range.
-The two-sided rank sum test (comparing differences between data sources) yields a p-Value of `r rs1` for the mean contribution in first round of the game.
-
-While the initial contributions are on average quite similar between the two sample, the subsequent contributions differ.
-In both absolute and relative terms, the Hamburg-Panel tends to contribute more than the student sample as the following Figure shows.
-
-```{r sampleContributions}
-
-SUM <- main[treatment == "replication",
-            lapply(.SD, mean, na.rm = TRUE),
-            by = c("round", "student"),
-            .SDcols = "contribution"]
-
-SUM[,
-    sum := round(contribution/4)]
-
-upperLimit <- SUM$contribution %>% max() %>% round() + 10
-
-p1 <- ggplot(data = SUM, 
-             aes(x = round, y = contribution, fill = student, color = student, lty = student)) +
-  layout +
-  theme(legend.position="bottom") +
-  geom_line(show.legend=FALSE) +
-  geom_point() +
-  scale_x_continuous(name="",  breaks = 1:15) +
-  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-  labs(y = "Average Amount of Tokens contributed") +
-  scale_color_manual(values = colors, labels = c("Hamburg-Panel", "Students")) + 
-  guides(lty = FALSE, fill = FALSE) +
-  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))
-
-SHARE <- main[treatment == "replication",
-            lapply(.SD, mean, na.rm = TRUE),
-            by = c("round", "student"),
-            .SDcols = "share"]
-
-upperLimit <- 1
-
-p2 <- ggplot(data = SHARE, 
-             aes(x = round, y = share, fill = student, color = student, lty = student)) +
-  layout +
-  theme(legend.position="bottom") +
-  geom_line(show.legend=FALSE) +
-  geom_point() +
-  scale_x_continuous(name="",  breaks = 1:15) +
-  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-  labs(y = "Share of Current Endowment contributed") +
-  guides(lty = FALSE, fill = FALSE) +
-  scale_color_manual(values = colors, labels = c("Hamburg-Panel", "Students"))
-
-p1 + p2 + plot_layout(guides = "collect") & theme(legend.position = "bottom")
-
-rm(list = c("SUM", "SHARE", "p1", "p2"))
-```
-
-Differences in contributions lead to differences in wealth.
-The Hamburg-Panel therefore earned more during the public goods game than the student sample.
-This can be seen in the following figure as well as in the subsequent table:
-
-```{r sampleStock, fig.cap = "Average wealth over time across samples."}
-STOCK <- main[treatment == "replication",
-              lapply(.SD, mean, na.rm = TRUE),
-              by = c("round", "student"),
-              .SDcols = "stock"]
-
-upperLimit <- STOCK$stock %>% max() %>% round() + 20
-
-ggplot(data = STOCK, 
-       aes(x = round, y = stock, fill = student, color = student, lty = student)) +
-  layout +
-  theme(legend.position="bottom") +
-  geom_line(show.legend=FALSE) +
-  geom_point() +
-  scale_x_continuous(name="",  breaks = 1:10) +
-  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
-  labs(y = "Wealth") +
-  guides(lty = FALSE, fill = FALSE) +
-  scale_color_manual(values = colors, labels = c("Hamburg-Panel", "Students"))
-
-rm(list = c("STOCK"))
-```
-
-```{r}
-main[treatment == "replication" & round == 10, 
-     lapply(.SD, mean, na.rm = TRUE), 
-     by = c("round", "student"), 
-     .SDcols = c("contribution", "share", "stock")] %>%
-  kable()
-```

### 2023-06-14 analysis/article/paper.qmd
improve reproducability

--- 2023-06-12 analysis/quarto/paper.qmd
@@
 
-pacman::p_load(magrittr, data.table, stringr, lubridate, glue, DescTools, haven, censReg,
-               stargazer, vtable, ggplot2, patchwork, MetBrewer, Rmisc, knitr)
+pacman::p_load(magrittr, data.table, stringr, lubridate, glue, haven, DescTools, censReg, stargazer, vtable, ggplot2, patchwork, Rmisc, knitr, rang)
+```
+
+```{r system_requirements}
+#| eval: false
+packages <- pacman::p_loaded()
+
+graph <- rang::resolve(pkgs = packages,
+                       snapshot_date = '2023-06-14')
+
+export_rang(graph, '../requirements/article.R')
+save(graph, file = '../requirements/article.rda')
 ```
@@
 # color
-colors <- met.brewer(name="Tam",n=7,type="discrete")
-colors <- c("#F3B05C", "#1E4A75", "#65B5C0", "#AD5E21")
-# cPrimary = "#ffd353"
-# cSecondary = "#9f2d55"
-# cInfo = "#34168"
 cPrimary = "#F3B05C"
@@
 save(GMTV, file = paste0("../../data/processed/rda/", fileName, ".rda"))
-write.csv(GMTV, file = paste0("../../data/processed/rda/", fileName, ".csv"))
+write.csv(GMTV, file = paste0("../../data/processed/csv/", fileName, ".csv"))
 ```

### 2023-06-14 analysis/article/paper.tex
improve reproducability

@@
 \end{keyword}
-\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, enhanced, breakable, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, boxrule=0pt]}{\end{tcolorbox}}\fi
+\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, enhanced, sharp corners, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable]}{\end{tcolorbox}}\fi
 
@@
 necessarily prevent us from reaching these targets, but it requires more
-effort in the future compared to a path that includes immediate action.
-Aiming at certain goals, today's actions (or the omission thereof) not
-only affect intermediate outcomes but also the number of paths one can
-choose from that lead to that specific goal.
+effort in the future compared to a path that includes immediate action
+\citet{HaenselEtAl2022}. Aiming at certain goals, today's actions (or
+the omission thereof) not only affect intermediate outcomes but also the
+number of paths one can choose from that lead to that specific goal.
 
@@
 that it is fairly simple to add this element of realism. They
-incorporated interdependencies into a \emph{dynamic} public goods game
-(dPGG) by defining endowments as the income of previous periods. To put
-it differently, participants' actions in a given period affect their
+incorporate interdependencies into a \emph{dynamic} public goods game
+(dPGG) by defining endowments as the income of previous periods.
+Consequently, participants' actions in a given period affect their
 number of actions in subsequent periods: the more (less) they earn now,
@@
 \citet{AGM2018} conducted static public goods games in the lab and on
-MTurk to draw lessons from online experimentation. This study extends
-this literature \citep[see,
+MTurk to draw (and report) lessons from online experimentation. This
+study extends this literature \citep[see,
 e.g.,][]{SnowbergYariv_2021, GuptaRigottiWilson_2021, GoodmanPaolacci2017, AmirEtAl2012}
@@
 and survey navigation, for instance---to assess the desired fluency and
-feasibility of the experiment. This research reports on the robust
-design that made the dynamic game feasible.
+feasibility of the experiment. Like \citet{AGM2018}, this research is of
+practical relevance as it reports on the robust design that made the
+dynamic game feasible.
 

### 2023-06-14 analysis/R/00_source.R

@@ -1,0 +1,7 @@
+rm(list = ls())
+
+source("R/01_config.R")
+source("R/02_renderHTML.R")
+source("R/03_renderPDF.R")
+
+for(i in pacman::p_loaded()){print(paste0(i, ' (', pacman::p_ver(i), ')'))}

### 2023-06-14 analysis/R/01_config.R

@@ -1,6 +1,7 @@
 # Packages -----
 # see https://rstudio.com/resources/webinars/managing-packages-for-open-source-data-science/
 listOfPackages <- c("renv",          # package management
+                    "rang",          # package management
                     "rmarkdown",
                     "knitr",
                     "distill",       # good looking HTML articles
@@ -36,9 +37,13 @@ for(package in listOfPackages){
   require(package, character.only = TRUE)
 }
 
-# renv::snapshot()
+# create snapshot -----
+# graph <- rang::resolve(pkgs = listOfPackages,
+#                        snapshot_date = '2023-06-14')
+# export_rang(graph, 'requirements/pre-reg.R')
+# save(graph, file = 'requirements/pre-reg.rda')
 
-# read most recent data
+# read most recent data -----
 cFiles <- file.info(list.files(path = "../data/replication",
                                recursive = TRUE,
                                full.names = TRUE,

### 2023-06-14 analysis/R/02_renderHTML.R

@@ -1,0 +1,14 @@
+# Render HTML Report -----
+rmarkdown::render(input = "R/04_rmd/01_dataGMTV.Rmd",
+                  output_dir = "reports/html/",
+                  output_file = "01_GMTV")
+
+rmarkdown::render(input = "R/04_rmd/02_dataProcessing.Rmd",
+                  output_dir = "reports/html/",
+                  output_file = "02_Replication")
+
+rmarkdown::render(input = "R/04_rmd/03_dataAnalyses.Rmd",
+                  output_dir = "reports/html/",
+                  output_file = "03_Analyses")
+
+print("HTMLs rendered. You can find them in analysis/reports/html/. The processed data is stored in data/processed/.")

### 2023-06-14 analysis/R/03_renderPDF.R

@@ -1,0 +1,17 @@
+# Render PDF Report -----
+rmarkdown::render(input = "R/04_rmd/01_dataGMTV.Rmd",
+                  output_format = "pdf_document",
+                  output_dir = "reports/pdf/",
+                  output_file = "01_GMTV")
+
+rmarkdown::render(input = "R/04_rmd/02_dataProcessing.Rmd",
+                  output_format = "pdf_document",
+                  output_dir = "reports/pdf/",
+                  output_file = "02_Replication")
+
+rmarkdown::render(input = "R/04_rmd/03_dataAnalyses.Rmd",
+                  output_format = "pdf_document",
+                  output_dir = "reports/pdf/",
+                  output_file = "03_Analyses")
+
+print("PDFs rendered. You can find them in analysis/reports/pdf/. The processed data is stored in data/processed/.")

### 2023-06-14 analysis/R/renderHTML.R

@@ -1,14 +1,0 @@
-# Render HTML Report -----
-# rmarkdown::render(input = "reports/rmd/01_dataGMTV.Rmd",
-#                   output_dir = "reports/html/",
-#                   output_file = "01_GMTV")
-
-rmarkdown::render(input = "reports/rmd/02_dataProcessing.Rmd",
-                  output_dir = "reports/html/",
-                  output_file = "02_Replication")
-
-rmarkdown::render(input = "reports/rmd/03_dataAnalyses.Rmd",
-                  output_dir = "reports/html/",
-                  output_file = "03_Analyses")
-
-print("PDFs rendered. You can find them in analysis/reports/html/. The processed data is stored in data/processed/.")

### 2023-06-14 analysis/R/renderPDF.R

@@ -1,22 +1,0 @@
-# Render PDF Report -----
-# rmarkdown::render(input = "reports/rmd/01_dataGMTV.Rmd",
-#                   output_format = "pdf_document",
-#                   output_dir = "reports/pdf/",
-#                   output_file = "01_GMTV")
-
-rmarkdown::render(input = "reports/rmd/02_dataProcessing.Rmd",
-                  output_format = "pdf_document",
-                  output_dir = "reports/pdf/",
-                  output_file = "02_Replication")
-
-rmarkdown::render(input = "reports/rmd/03_dataAnalyses.Rmd",
-                  output_format = "pdf_document",
-                  output_dir = "reports/pdf/",
-                  output_file = "03_Analyses")
-
-rmarkdown::render(input = "reports/rmd/04_prettyAnalyses.Rmd",
-                  output_format = "pdf_document",
-                  output_dir = "reports/prettyReports/",
-                  output_file = "04_Analyses")
-
-print("PDFs rendered. You can find them in analysis/reports/pdf/. The processed data is stored in data/processed/.")

### 2023-06-14 analysis/R/source.R

@@ -1,5 +1,0 @@
-rm(list = ls())
-
-source("R/config.R")
-source("R/renderHTML.R")
-source("R/renderPDF.R")

### 2023-06-16 analysis/article/paper.qmd
rewrite transparency chapter

@@
 Because the study of inexperienced general population samples raises methodological challenges, such as fatigue and dropouts, this research approaches them.
-Doing so, I provide simple solutions to run reliable interactive experiments online.
+In doing so, I provide simple solutions to run reliable interactive experiments online.
+Furthermore, this article showcases the use of literate programming and version control which I argue are convenient tools to make pre-registrations more credible and flexible.
 
@@
 <!-- Think of lifetime consumption‐smoothing and save more tomorrow -->
-Opting for environmental friendly policies today not only reduces carbon dioxide omissions immediately but also helps us to reach the Paris climate targets tomorrow.
-Deferring these policies, may not necessarily prevent us from reaching these targets, but it requires more effort in the future compared to a path that includes immediate action @HaenselEtAl2022.
+Opting for environmentally friendly policies today not only reduces carbon dioxide emissions immediately but also helps us to reach the Paris climate targets tomorrow.
+Deferring these policies, may not necessarily prevent us from reaching these targets, but it requires more effort in the future compared to a path that includes immediate action [@HaenselEtAl2022].
 Aiming at certain goals, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of paths one can choose from that lead to that specific goal.
@@
 
-A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017 hereafter, GMTV] as well as Stefan Große (unpublished) shows that it is fairly simple to add this element of realism.
+A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017 hereafter, GMTV] as well as Stefan Große (unpublished), shows that it is fairly simple to add this element of realism.
 They incorporate interdependencies into a _dynamic_ public goods game (dPGG) by defining endowments as the income of previous periods.
@@
 
-Because there is surprisingly little experimental research on interdependencies^[One exemption are @Moser2019, who built on GMTVs' design to investigate leadership.], I reproduced one of GMTVs' treatments to compare dynamics across (in)experienced samples to investigate its generalizability.
+Because there is surprisingly little experimental research on interdependencies^[See e.g.
+@BattagliniEtAl2016, @Rockenbach2017 or @Moser2019.], I reproduced one of GMTVs' treatments to compare dynamics across (in)experienced samples to investigate its generalizability.
 @GKLS2020 find that static public goods games do not generalize well to real-world climate action.
-They also find that generalizability depends on structural resemblance of the public goods game with the context of climate change mitigation: Greater resemblance improves generalizability.
+They also find that generalizability depends on the structural resemblance of the public goods game with the context of climate change mitigation: Greater resemblance improves generalizability.
 Because GMTVs' dynamic setting has a more realistic property—namely, interdependencies—one would expect it to be better suited to inform public policy.
@@
 Like @GKLS2020, @CarpenterEtAl2008 report that students make lower contributions to charity than community members.] This yielded a setting similar to the one of @GKLS2020, which allows me to analyze how behavior in the abstract game translates into real-world action across samples.
-This research shows that the dynamic setting _does not_ add any advances with respect to generalizability of results.
+This research shows that the dynamic setting _does not_ add any advances to the generalizability of results.
 
@@
 This study extends this literature [see, e.g., @SnowbergYariv_2021; @GuptaRigottiWilson_2021; @GoodmanPaolacci2017; @AmirEtAl2012] by focusing on an _inconvenient_ sample (i.e.
-one that is completely inexperienced sample that has not been exposed to interactive experiments before) playing a computationally more complex game.
-This required me to design a robust (and thus, more complex) software to minimize attrition.
-I collected paradata---which captures screen time and survey navigation, for instance---to assess the desired fluency and feasibility of the experiment.
+one that is a completely inexperienced sample that has not been exposed to interactive experiments before) playing a computationally more complex game.
+This required me to design robust (and thus, more complex) software to minimize attrition.
+I collected para data---which capture screen time and survey navigation, for instance---to assess the desired fluency and feasibility of the experiment.
 Like @AGM2018, this research is of practical relevance as it reports on the robust design that made the dynamic game feasible.
@@
 
-After commenting on transparent research practices and reporting the methods in @sec-transparency and @sec-methods, this paper is organized along these findings: The confirmatory reproduction is reported in @sec-replication, the online feasibility in @sec-feasibility and the generalizability in @sec-generalizability.
+After commenting on transparent research practices and reporting the methods in @sec-transparency and @sec-methods, this paper is organized along these findings: The confirmatory reproduction is reported in @sec-replication, the online feasibility in @sec-feasibility, and the generalizability in @sec-generalizability.
 @sec-conclusion concludes.
@@
 
-Well before credibility crises comprised a variety disciplines, @bemwriting [p. 2] indirectly conceded discrepancies between fuzzy research processes and the polished article that results from it:
+Well before credibility crises comprised a variety of disciplines^[See e.g., @CamererEtAl2016; @BrodeurEtAl2016; @BrodeurEtAl2020; @ChristensenMiguel2018; @FerraroShukla2020 who focus on economics.], @bemwriting [p.
+2] indirectly conceded discrepancies between fuzzy research processes and the polished article that results from it:
 
@@
 
-Now, 20 years later, we accustom ourselves with mechanisms designed to unravel the fuzzy back-and-forth between exploratory and confirmatory research.
-Prominently, pre-registrations were established to tie the researchers' hands when doing confirmatory research--reducing observable discrepancies between Daryl Bem's above-mentioned (a) and (b).
-Today, researchers can not only choose where to pre-register but also decide about the level of detail they provide.
-More severely, nothing stops researchers from pre-registering multiple hypotheses opposing each other [see, e.g., @SimmonsEtAl2021; and @PhamEtAl2021 for a discussion].
-
-@WaldronAllen2022 report a wide variety of depth of pre-registrations in the field of Neuropsychopharmacology and document that the _'pre-registered'_ label can be obtained with minimal effort.
-In absence of transparency and scrutiny pre-registrations run into danger to miss the target of making science more credible.
-Even more so, they may have adverse effects as the _'pre-registered'_ label becomes cheap (too) to acquire.
-
-Discussing the costs and benefits of pre-registrations, @Olken2015 stresses the uncertainty of research processes and promotes moderate approaches.
-As @WaldronAllen2022, he argues that pre-registrations not necessarily eliminate  flexibility.
-These 'moderate' or 'flexible' approaches require transparency to reduce concerns of _'data-mining'_ [@Olken2015 p.
-61] by showing (a) the analyses I planned to run, (b) the analysis that made most sense after collecting the data and the transition from (a) to (b).
-Because this is neither incentivized nor easy to verify, we need tools that make transparency convenient to establish and to scrutinize.
-I propose version control (such as Git) as one such tool and illustrate its application on this paper:  GitHub is a website and cloud-based service where developers---and researchers alike---can store and manage their code.
-The service is based on Git^[Git is a specific open-source version control system developed in 2005.] and designed for version control.
-Importantly, changes are time-stamped and can be tracked.
-Moreover, one can create branches, that is, duplicates of code either to work collaboratively or to archive a certain state.
-
-To sum up, pre-registrations alone are necessary but not sufficient to restore the credibility in experimental sciences.
-Pre-registrations must come with additional emphasis on transparency covering the whole research process as well as with a higher level of scrutiny that looks beyond mere labels.
-
-In fact, the experiment reported in this article qualifies for the _'pre-registered'_ label at a first glance:
+Now, 20 years later, we accustom ourselves to mechanisms designed to unravel the fuzzy back-and-forth between exploratory and confirmatory research.
+Prominently, pre-registrations were established to tie the researchers' hands with respect to p-hacking and ex-post theorizing when doing confirmatory research---reducing observable discrepancies between Daryl Bem's above-mentioned (a) and (b).
+
+While pre-registrations could help to make empirical sciences more credible, they come at costs that are discussed by @Olken2015 as well as @Krishna2021, @SimmonsEtAl2021, and @PhamEtAl2021.
+One important concern is that strict pre-registrations may severely discount any additional analysis of the data inspired by surprise results.
+In practice, there are at least two ways to approach that problem: First, one could (and should) add unforeseen analyses to the article but label them as exploratory.
+Second, one could write a minimal pre-registration leaving enough degrees of freedom for the researcher to incorporate such surprises without further notice.
+The key difference between the two approaches is the deliberate omission of transparency.
+
+For the field of neuropsychopharmacology @WaldronAllen2022 document that the depth of pre-registrations differs indeed: it is spanning from notes on hypotheses only to fully specified, detailed experimental protocols with accompanying power analyses and sampling plans.
+Treating all pre-registrations equally may thus lead to an adverse effect: If one can acquire the _'pre-registered'_ label with minimal effort and maximum flexibility, the label itself may run into danger to become worthless and to miss the target of making science more credible.
+
+This erosion of credibility can be avoided by the means of transparency---not because transparency can tighten the ties but also because it facilitates scrutiny, policing [see @AnkelPetersFialaNeubauer2023] and forensics: transparent research practices make it easier for others to track and understand a researcher's reaction to surprises in the data, which, in turn, gives the researcher more flexibility to react to these surprises.
+As additional transparency is associated with additional effort, I propose version control as a natural and easy-to-implement solution augmenting pre-registrations.
+
+Contemporary experimental research is, to a certain degree, a computational science: experiments often require complex software and the analysis thereof can result in complicated scripts.
+In addition, much research is carried out in collaborative efforts.
+For these reasons alone, it makes sense to implement version control systems such as GitHub and GitLab as well as OSF (albeit less powerful) that ensure that files are stored consistently and that changes are tracked.
+When these systems are implemented in the whole research process, one can archive different states of the software and visualize differences between different states.
+For instance, one can archive the analysis before and after the data was collected or the experimental software used in a pilot and the eventual experiment.
+Importantly, one can keep projects private and change their visibility to public only after the corresponding article is accepted for publication.
+Taken together, these features _automatically_ enhance transparency and facilitate scrutiny, policing, and forensics whilst also making software development and collaboration more efficient.
+As a consequence, the implementation and eventual disclosure of version control come not only with meta-scientific but also with organizational benefits.
+
+The experiment reported in this article qualifies for the _'pre-registered'_ label at first glance:
 The analysis was pre-registered in the American Economic Association's RCT Registry [@preregistration].
-Further, I pre-registered the exact analyses I planned to run when I designed the experiment on [GitHub](https://shorturl.at/bAGKY).^[https://shorturl.at/bAGKY to run the code, you need to execute the .Rmd files in this repository in the order that is indicated by file names.]
-
-At a second glance, the analysis that made the most sense after having collected the data and that is reported here is a little different though: Because the more representative subject pool was exhausted earlier than expected, I recruited students which opened up a new research direction: assessing generalizability.
+Further, I pre-registered the exact analyses I planned to run when I designed the experiment on [GitHub](https://github.com/Howquez/GMTV/tree/July21Replication/analysis/R).^[bit.ly/3Pnak5H.
+To run the code, you need to execute the .Rmd files in this repository in the order that is indicated by file names.
+Detailed instructions can be found in the README file accompanying the analysis scripts.]
+
+At second glance, the analysis that made the most sense after having collected the data and that is reported here is a little different though: Because the more representative subject pool was exhausted earlier than expected, I recruited students which opened up a new research direction: assessing generalizability.
 Hence, this article combines both confirmatory as well as exploratory research.
 
-Accordingly, I edited many of the analyses scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://shorturl.at/ilpAG] However, because the originally planned analysis code is archived and reproducible, these changes are transparent.
+Accordingly, I edited many of the analysis scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/GMTV/blob/main/analysis/article/paper.qmd): https://bit.ly/43LCyLw] However, because the originally planned analysis code is archived and reproducible, these changes are transparent.
 Importantly, I followed a literate programming approach [@Knuth_1984; @AkhtarYe_2023].
@@
 This establishes consistence between the commands one tells the statistical software to do and the explanation one tells human beings one told the statistical software to do.
-As such, (a), (b) and the transition from (a) to (b) are not only transparent but also comprehensible.
+As such, (a), (b), and the transition from (a) to (b) are not only transparent but also comprehensible.
 
 <!--
-I archived detailed analyses scripts and created a [branch](https://github.com/Howquez/coopUncertainty/tree/July21Replication) a few days _before_ we collected data and pre-registered the analysis via the American Economic Association's RCT Registry [@preregistration].
+I archived detailed analyses scripts and created a [branch](https://GitHub.com/Howquez/coopUncertainty/tree/July21Replication) a few days _before_ we collected data and pre-registered the analysis via the American Economic Association's RCT Registry [@preregistration].
 -->
@@
 
-In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific_ reproduction^[@Parsons2022 use the term of a _conceptual replication_ which means the same.] of one treatment of GMTVs' dynamic public goods game.
+In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific_ reproduction^[In fact, @Hamermesh2007 uses the term _replication_ instead of _reproduction_.
+The reason I deviate is that I do not compare different treatments with each other to _replicate_ a treatment effect.
+Instead, I _reproduce_ the results of one specific treatment arm.] of one treatment of GMTVs' dynamic public goods game.
 The pure reproduction re-analyzes the original data.
-[Appendix A](#A:-Pure-Replication) documents [errors I identified]() in the original paper.
+[Appendix A](#A:-Pure-Replication) documents [the errors I identified]() in the original paper.
 The scientific reproduction, where I utilize a different sample drawn from a different population in a different situation, is described in the following sections.
@@
 
-Considering the design, the only differences between such a _static_ game (with partner matching) and GMTVs' design are _dynamics_: Instead of receiving fresh endowments every period, participants receive one endowment only at the beginning of the first period.
+Considering the design, the 'only' differences between such a _static_ game (with partner matching) and GMTVs' design are _dynamics_: Instead of receiving fresh endowments every period, participants receive one endowment only at the beginning of the first period.
 A participant's endowment in the second period is the wealth she accumulated in the first period.
@@
 The information also highlighted that the mitigation came into operation on a European level.
-Finally, I informed the participants that the documentation of individual and aggregate contributions were to be posted immediately after the concluding the sessions online.
+Finally, I informed the participants that the documentation of individual and aggregate contributions was to be posted immediately after the conclusion of the sessions online.
 To avoid privacy or social image concerns, participants learned their unique and random IDs, which they needed to identify their individual contributions.
@@
 
-I recruited the participants from the so called _[HamburgPanel](https://www.wiso.uni-hamburg.de/forschung/forschungslabor/umfragelabor/aktuelle-umfragen/hamburgpanel.html)_ using HROOT [@hroot].
+I recruited the participants from the so-called _[HamburgPanel](https://www.wiso.uni-hamburg.de/forschung/forschungslabor/umfragelabor/aktuelle-umfragen/hamburgpanel.html)_ using HROOT [@hroot].
 The panel is provided by the University of Hamburg's Research Laboratory, which used a randomized last digits approach to build the panel while drawing from the population of citizens of Hamburg, Germany.
@@
 
-Throughout this paper, I will compare results of my experiment with the results of GMTVs' NOPUNISH 10 Period treatments.
-I am thus, referring to three different samples utilized at two points in time: the University of Nottingham's students (in late 2012), Hamburg's citizens and the University Hamburg's students (both in July 2021).
+Throughout this paper, I will compare the results of my experiment with the results of GMTVs' NOPUNISH 10 Period treatments.
+I am thus, referring to three different samples utilized at two points in time: the University of Nottingham's students (in late 2012), Hamburg's citizens, and the University of Hamburg's students (both in July 2021).
 @tbl-sample-properties gives an overview.
@@
 Third, the underlying game was dynamic and interdependent.
-This makes dropouts not only more likely but also more expensive, which is why attrition was a major concern implementing the experiment.
-
-I chose oTree [@oTree] to implement the experiment because it is open-source, well documented and very flexible.
-Its [Bootstrap](https://getbootstrap.com/) (a powerful frontend toolkit) integration allowed me to make the graphical user interface interactive, appealing and easy to navigate.
-The [Highcharts library](https://www.highcharts.com/) made it easy to visualize results and to communicate dynamics.
-Insofar, oTree served a good tool to enhance the participants' user experience and thus, to make dropouts less likely.
+This makes dropouts not only more likely but also more expensive, which is why attrition was a major concern in implementing the experiment.
+
+I chose oTree [@oTree] to implement the experiment because it is open-source, well-documented, and very flexible.
+Its [Bootstrap](https://getbootstrap.com/) (a powerful frontend toolkit) integration allowed me to make the graphical user interface interactive, appealing, and easy to navigate.
+The [Highcharts library](https://www.highcharts.com/) made it easy to visualize results and communicate dynamics.
+Insofar, oTree served as a good tool to enhance the participants' user experience and thus, to make dropouts less likely.
 
@@
 Both features were implemented to limit wait times and boredom for other participants.
-@sec-feasibility shows that the first feature became effective in some cases, wheres the second feature did not.
+@sec-feasibility shows that the first feature became effective in some cases, whereas the second feature did not.
 
@@
 Once matched, they were exposed to the decision screen over ten periods.
-At the end of the last period, participants saw results of all periods.
+At the end of the last period, participants saw the results of all periods.
 Subsequently, they made their VCA decision, before I elicited risk preferences [@HoltLaury2002] and finished with GMTVs' questionnaire.
@@
 The experiment lasted around `r total_completion_time` minutes on average.
-The earnings  averaged `r earningsMean %>% round(digits = 2)` Euros (sd = `r earningsSD  %>% round(digits = 2)`).^[This values include earnings from the incentivized risk elicitation task that is not part of the analysis.]
+The earnings  averaged `r earningsMean %>% round(digits = 2)` Euros (sd = `r earningsSD  %>% round(digits = 2)`).^[This value include earnings from the incentivized risk elicitation task that is not part of the analysis.]
 
@@
 
-## Pre-registered GMTV Reproduction {#sec-replication}
+## Reproducibility {#sec-replication}
 
@@
 Both samples contributed 10 tokens, that is, 50% of their endowments on average (median and mean).
-Moreover, both samples' initial contributions resemble initial contributions participants usually make in the static game with partner matching.^[See Figure 3B in @fehrgaechter2000 [p.989], for instance.] However, in the dynamic game presented here, I are particularly interested in the subsequent periods because differences add up exponentially.
+Moreover, both samples' initial contributions resemble the initial contributions participants usually make in the static game with partner matching.^[See Figure 3B in @fehrgaechter2000 [p.989], for instance.] However, in the dynamic game presented here, I am particularly interested in the subsequent periods because differences add up exponentially.
 Do the two groups remain similar over the course of time?
@@
 In particular, do the two samples' contributions follow the same path over the 10 periods they played?
-The answer is _no_.
-@fig-share-of-contributions illustrates that the samples make similar contributions at the beginning and the end of the game but behave differently in between.
+The answer is _yes and no_.
+@fig-share-of-contributions and @tbl-contribution-periods illustrate that the samples make similar contributions at the beginning and the end of the game but behave differently in between.
 More precisely, the left panel--depicting the average contributions in absolute terms--shows that the original sample contributed more than the reproduction sample _in all but the first and last period_.^[In period five, this difference is significant: a two-sided rank sum test yields p=`r rs2`.
@@
 
-Again, both samples' behavior resembles the contributions participants usually make in the static game with partner matching: contributions equal approximately half of endowments in the very first period and decrease to around ten percent of endowments by the last period.^[The right panel is thus, comparable to the visualizations _and results_ in the static game.
-See, for instance, Figure 1B in @fehrgaechter2000 [p.986].] In the dynamic game presented here, however, different paths lead to different levels of wealth -- even if they share the same start- and end-points.
+Again, both samples' behavior resembles the contributions participants usually make in the static game with partner matching: contributions equal approximately half of the endowments in the very first period and decrease to around ten percent of endowments by the last period.^[The right panel is thus, comparable to the visualizations _and results_ in the static game.
+See, for instance, Figure 1B in @fehrgaechter2000 [p.986].] In the dynamic game presented here, however, different paths lead to different levels of wealth -- even if they share the same start- and endpoints.
 I am thus, more interested in the contributions' implications for wealth generation and growth.
@@
 
-How do the different contribution-paths translate into wealth?^[To measure wealth and growth, I define a variable called _stock_ which sums the endowments of all participants in a given group at the end of the round (that is, after the contributions have been made, multiplied and redistributed).] Given that the original sample contributed more, one would expect the respective groups to be  more wealthy.
+How do the different contribution paths translate into wealth?^[To measure wealth and growth, I define a variable called _stock_ which sums the endowments of all participants in a given group at the end of the round (that is, after the contributions have been made, multiplied, and redistributed).] Given that the original sample contributed more, one would expect the respective groups to be  more wealthy.
 A mere mean comparison indicates just that: An average group in the original sample accumulated about `r round(originalWealth)` tokens.
-In contrast, an average group in the reproduction sample accumulated about `r round(replicationWealth)` tokens.
-This difference is insignificant at conventional levels though: A two-sided rank sum test (comparing differences between samples) yields p=`r rs1` for the mean stock in last period of the game.
+In contrast, the average group in the reproduction sample accumulated about `r round(replicationWealth)` tokens.
+This difference is insignificant at conventional levels though: A two-sided rank sum test (comparing differences between samples) yields p=`r rs1` for the mean stock in the last period of the game.
 
@@
 
-Although there clearly is growth, groups do not realize the maximal potential efficiency: under full cooperation, a group can accumulate at maximum `r (80*1.5^10) %>% trunc()` tokens or EUR `r (80*1.5^10 /20) %>% trunc()`.
+Although there clearly is growth, groups do not realize the maximal potential efficiency: under full cooperation, a group can accumulate a maximum of `r (80*1.5^10) %>% trunc()` tokens or EUR `r (80*1.5^10 /20) %>% trunc()`.
 This is depicted in the left panel of @fig-growth-heterogeneity, where one can see the average wealth over time by sample.
@@
 
-Given the different samples and the possibility of endogenous growth--which essentially is the main feature of the game--I ask whether and how the inequality grows _within_ groups.
-@fig-gini-time-series illustrates that inequality did grow: at the end of the game, the original and the replication groups exhibit an average Gini coefficient of `r originalGini` and `r replicationGini`, respectively.^[The two-sided rank sum test (comparing differences between samples) yields p=`r rs1` for the mean Gini coefficient in last round of the game.] Because every participant started with the same initial endowment (in _period 0_, so to speak), every group started equally--with a Gini coefficient equaling zero.
+Given the different samples and the possibility of endogenous growth---which essentially is the main feature of the game---I ask whether and how the inequality grows _within_ groups.
+@fig-gini-time-series illustrates that inequality did grow: at the end of the game, the original and the replication groups exhibit an average Gini coefficient of `r originalGini` and `r replicationGini`, respectively.^[The two-sided rank sum test (comparing differences between samples) yields p=`r rs1` for the mean Gini coefficient in the last round of the game.] Because every participant started with the same initial endowment (in _period 0_, so to speak), every group started equally--with a Gini coefficient equaling zero.
 
@@
 
-**Result 1.** _The `NOPUNISH 10` treatment of GMTV can be replicated because the replication data resemble the original data with respect to initial and final contributions, wealth and growth as well as inequality._
-
-This is remarkable given the different sample and language, the different software and user interface as well as the online setting during the COVID19 pandemic.
-The result suggests that, by and large, the sum of these factors did not affect people’s preferences towards cooperation.
+**Result 1.** _The `NOPUNISH 10` treatment of GMTV can be replicated because the replication data resemble the original data with respect to initial and final contributions, wealth, and growth as well as inequality._
+
+This is remarkable given the different sample and language, the different software and user interface as well as the online setting during the COVID-19 pandemic.
+The result suggests that by and large, the sum of these factors did not affect people’s preferences towards cooperation.
 
@@
 Another `r 44` answered with _"rather yes"_ while nobody indicated that he or she did not understand the situation at all.
-There is some behavioral data supporting this finding: The user interface offered a popup to review instructions or contact information.
+Some behavioral data are supporting this finding: The user interface offered a popup to review instructions or contact information.
 I tracked both and find that none of the participants ever opened these popups even though they were clearly visible in the decision screens' header and introduced in the instructions.
@@
 I first comment on the selection into the experiment: It was difficult to recruit the sample.
-The panel counted 1.209 non-students of which I were able to recruit `r main[student == FALSE, .N]` participants who finished the experiment---even though I varied the weekdays and timing of the sessions (which were conducted during a nation-wide lockdown with home office regime).
+The panel counted 1.209 non-students of which I was able to recruit `r main[student == FALSE, .N]` participants who finished the experiment---even though I varied the weekdays and timing of the sessions (which were conducted during a nationwide lockdown with home office regime).
 For this reason, I also recruited students in the last session which explains the relatively large number of showups in @tbl-meta.
-Although I intended to refrain from the recruitment of students initially, this particular sub sample enabled me to investigate the generalizability of my results as I will discuss in  @sec-generalizability.
+Although I intended to refrain from the recruitment of students initially, this particular sub-sample enabled me to investigate the generalizability of my results as I will discuss in  @sec-generalizability.
 
@@
 Turning to the time spent on each page, I focus on the decision times in the dynamic public goods game as @Anderhub2001 did.
-How many seconds did the participants need to make a decision in each period of the game?
+How many seconds did the participants need to decide in each period of the game?
 Not too many.
 @fig-time-spent illustrates an intuitive pattern: The first decision took about `r tmp[round == 1, round(time_spent)]` seconds.
-The second decision--where participants first learned about the other group members' previous decisions--took longer (about `r tmp[round == 2, round(time_spent)]` seconds).
+The second decision---where participants first learned about the other group members' previous decisions---took longer (about `r tmp[round == 2, round(time_spent)]` seconds).
 Subsequently, decision times first declined and stabilized at `r tmp[round > 3, round(mean(time_spent))]` seconds.
-Importantly, decision times were so short that crosstalk, that is, communication through private channels--a common concern^[See, for instance, the discussion section in @AGM2018 [p.
-119].] in online experiments--was unlikely, especially because it would require the identification of other group members.^[There were only `r plotDT[page_index == 12 & time_spent > 60, .N]` participants (from all four sessions) who needed more than 60 seconds to make the second decision.]
+Importantly, decision times were so short that crosstalk, that is, communication through private channels---a common concern^[See, for instance, the discussion section in @AGM2018 [p.
+119].] in online experiments---was unlikely, especially because it would require the identification of other group members.^[There were only `r plotDT[page_index == 12 & time_spent > 60, .N]` participants (from all four sessions) who needed more than 60 seconds to make the second decision.]
 
 ```{r plotTime}
-#| fig-cap: Average Time Spent for each Contribution per Period
+#| fig-cap: Average Time Spent for Each Contribution per Period
 #| label: fig-time-spent
@@
 
-**Result 2.** _Given the decision times and the fluent procedure, attrition was as negligible as it is in physical laboratories---where (a) not every invited person shows up and (b) a number of participants divisible by the group size is required as well._
+**Result 2.** _Given the decision times and the fluent procedure, attrition was as negligible as it is in physical laboratories---where (a) not every invited person shows up and (b) several participants divisible by the group size are required as well._
 
@@
 The left panels show the behavior in the VCA.
-The right panels show the behavior in first period of the game.
+The right panels show the behavior in the first period of the game.
 A visual inspection shows that (a) mean contributions are positive in both tasks for both samples.^[The same holds true for median contributions.] (b) Furthermore, average contributions are lower in the VCA.
@@
 Taken together, these aggregate results indicate, that the consistency between tasks is higher for the general population than it is for students.
-Or, to put it differently, the general population's behavior in the abstract game better predicts their behavior in real-world mitigation context.
+Or, to put it differently, the general population's behavior in the abstract game better predicts their behavior in a real-world mitigation context.
 
@@
 The student status negatively affects VCA donations in column two but disappears if one controls for age in column three.
-Importantly, the interaction of student status and first-period contributions is not significant.
+Importantly, the interaction between student status and first-period contributions is not significant.
 This suggests that the general population sample's transferability is just as bad as the student sample's.
@@
 Second, the online experiment proceeded fluently such that dropouts were no concern.
-Third, contribution behavior in the dynamic abstract setting is not linked to behavior in the real world -- neither for students nor a more representative sample.
+Third, contribution behavior in the dynamic abstract setting is not linked to behavior in the real world---neither for students nor a more representative sample.
 
 The significance of the first result is that similar procedures led to replicable findings under different circumstances across two different samples.
-The second result is of methodological importance: It highlights that even logistically complex experiments can be conducted online with---not only with clickworkers but also with a true general population sample.
-The third result questions whether recruiting from more representative samples is worth the efforts because it did not affect transferability of abstract results to the real world.
-
-Taken together the results answer the questions whether GMTVs' dynamic paradigm is reproducible  across samples (yes) and whether it is feasible employ it online (also yes).
+The second result is of methodological importance: It highlights that even logistically complex experiments can be conducted online---not only with clickworkers but also with a true general population sample.
+The third result questions whether recruiting from more representative samples is worth the effort because it did not affect the transferability of abstract results to the real world.
+
+Taken together the results answer the questions whether GMTVs' dynamic paradigm is reproducible  across samples (yes) and whether it is feasible to employ it online (also yes).
 The question that is _not_ answered is, whether GMTVs' treatment effects replicate well because I did not focus on treatments and treatment effects.
-It thus, remains an open question, whether the causal effect of GMTVs' treatments replicate well.
+It thus, remains an open question, whether the causal effects of GMTVs' treatments replicate well.
 Further, we do not know whether their treatments affect real-world behavior.
-How generalizable are treatment effects in public goods games in general?
+So, how generalizable are treatment effects in public goods games in general?
 Albeit this study does not address these questions, it provides methods suited to investigate them---even with inconvenient samples.
@@
 I gratefully acknowledge support by the German Research Foundation (DFG) under Germany’s Excellence Strategy, cluster EXC 2037 “Climate, Climatic Change, and Society” (project 390683824).
-I thank Stefan Traub and participants of the CLICCS B5 group for helpful discussions.
+I thank Stefan Traub and the participants of the CLICCS B5 group for helpful discussions.
 
@@
 According to the authors, the Gini coefficient should equal `GINI=``r GINI <- GMTV[exp_num == 1 & gr_id == 101 & per == 5, tokens %>% Gini() %>% round(digits = 3)]; GINI` for all subjects in the group.
-Instead, participant `112` and `113` who have an equal endowment deviate from that value.
+Instead, participants `112` and `113` who have an equal endowment deviate from that value.
 Importantly, the `DescTools::Gini()` function in the statistical software `R` does not yield this error, which is why I use that function for my calculations using both my as well as the original data.

### 2023-06-16 analysis/article/paper.tex
rewrite transparency chapter

@@
 challenges, such as fatigue and dropouts, this research approaches them.
-Doing so, I provide simple solutions to run reliable interactive
-experiments online.
+In doing so, I provide simple solutions to run reliable interactive
+experiments online. Furthermore, this article showcases the use of
+literate programming and version control which I argue are convenient
+tools to make pre-registrations more credible and flexible.
 \end{abstract}
@@
 \end{keyword}
-\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, enhanced, sharp corners, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable]}{\end{tcolorbox}}\fi
+\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced, sharp corners, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi
 
@@
 current decisions affect future outcomes and with it, future decision
-spaces. Opting for environmental friendly policies today not only
-reduces carbon dioxide omissions immediately but also helps us to reach
+spaces. Opting for environmentally friendly policies today not only
+reduces carbon dioxide emissions immediately but also helps us to reach
 the Paris climate targets tomorrow. Deferring these policies, may not
@@
 effort in the future compared to a path that includes immediate action
-\citet{HaenselEtAl2022}. Aiming at certain goals, today's actions (or
+\citep{HaenselEtAl2022}. Aiming at certain goals, today's actions (or
 the omission thereof) not only affect intermediate outcomes but also the
@@
 A game designed by Gächter, Mengel, Tsakas \& Vostroknutov \citeyearpar[
-hereafter, GMTV]{GMTV2017} as well as Stefan Große (unpublished) shows
+hereafter, GMTV]{GMTV2017} as well as Stefan Große (unpublished), shows
 that it is fairly simple to add this element of realism. They
@@
 Because there is surprisingly little experimental research on
-interdependencies\footnote{One exemption are \citet{Moser2019}, who
-  built on GMTVs' design to investigate leadership.}, I reproduced one
-of GMTVs' treatments to compare dynamics across (in)experienced samples
-to investigate its generalizability. \citet{GKLS2020} find that static
+interdependencies\footnote{See e.g. \citet{BattagliniEtAl2016},
+  \citet{Rockenbach2017} or \citet{Moser2019}.}, I reproduced one of
+GMTVs' treatments to compare dynamics across (in)experienced samples to
+investigate its generalizability. \citet{GKLS2020} find that static
 public goods games do not generalize well to real-world climate action.
-They also find that generalizability depends on structural resemblance
-of the public goods game with the context of climate change mitigation:
-Greater resemblance improves generalizability. Because GMTVs' dynamic
-setting has a more realistic property---namely, interdependencies---one
-would expect it to be better suited to inform public policy. To test
-this intuition, I not only ran the experiment with different samples but
-also observed the participants' behavior in voluntary climate actions
-(VCA).\footnote{The VCA is a (charitable) dictator game where each
-  participant is a dictator dividing her budget between herself and some
-  organization linked to the reduction of CO2 emissions.
-  \citet{EckelGrossman1996} were the first to implement a charitable
-  dictator game observing contributions of 30\% of the endowments. Like
-  \citet{GKLS2020}, \citet{CarpenterEtAl2008} report that students make
-  lower contributions to charity than community members.} This yielded a
-setting similar to the one of \citet{GKLS2020}, which allows me to
-analyze how behavior in the abstract game translates into real-world
-action across samples. This research shows that the dynamic setting
-\emph{does not} add any advances with respect to generalizability of
-results.
+They also find that generalizability depends on the structural
+resemblance of the public goods game with the context of climate change
+mitigation: Greater resemblance improves generalizability. Because
+GMTVs' dynamic setting has a more realistic property---namely,
+interdependencies---one would expect it to be better suited to inform
+public policy. To test this intuition, I not only ran the experiment
+with different samples but also observed the participants' behavior in
+voluntary climate actions (VCA).\footnote{The VCA is a (charitable)
+  dictator game where each participant is a dictator dividing her budget
+  between herself and some organization linked to the reduction of CO2
+  emissions. \citet{EckelGrossman1996} were the first to implement a
+  charitable dictator game observing contributions of 30\% of the
+  endowments. Like \citet{GKLS2020}, \citet{CarpenterEtAl2008} report
+  that students make lower contributions to charity than community
+  members.} This yielded a setting similar to the one of
+\citet{GKLS2020}, which allows me to analyze how behavior in the
+abstract game translates into real-world action across samples. This
+research shows that the dynamic setting \emph{does not} add any advances
+to the generalizability of results.
 
@@
 e.g.,][]{SnowbergYariv_2021, GuptaRigottiWilson_2021, GoodmanPaolacci2017, AmirEtAl2012}
-by focusing on an \emph{inconvenient} sample (i.e.~one that is
+by focusing on an \emph{inconvenient} sample (i.e.~one that is a
 completely inexperienced sample that has not been exposed to interactive
 experiments before) playing a computationally more complex game. This
-required me to design a robust (and thus, more complex) software to
-minimize attrition. I collected paradata---which captures screen time
+required me to design robust (and thus, more complex) software to
+minimize attrition. I collected para data---which capture screen time
 and survey navigation, for instance---to assess the desired fluency and
@@
 reproduction is reported in Section~\ref{sec-replication}, the online
-feasibility in Section~\ref{sec-feasibility} and the generalizability in
-Section~\ref{sec-generalizability}. Section~\ref{sec-conclusion}
+feasibility in Section~\ref{sec-feasibility}, and the generalizability
+in Section~\ref{sec-generalizability}. Section~\ref{sec-conclusion}
 concludes. Because I observed some (qualitatively inconsequential)
@@
 
-Well before credibility crises comprised a variety disciplines,
-\citet[p.~2]{bemwriting} indirectly conceded discrepancies between fuzzy
-research processes and the polished article that results from it:
+Well before credibility crises comprised a variety of
+disciplines\footnote{See e.g., \citet{CamererEtAl2016};
+  \citet{BrodeurEtAl2016}; \citet{BrodeurEtAl2020};
+  \citet{ChristensenMiguel2018}; \citet{FerraroShukla2020} who focus on
+  economics.}, \citet[p.~2]{bemwriting} indirectly conceded
+discrepancies between fuzzy research processes and the polished article
+that results from it:
 
@@
 
-Now, 20 years later, we accustom ourselves with mechanisms designed to
+Now, 20 years later, we accustom ourselves to mechanisms designed to
 unravel the fuzzy back-and-forth between exploratory and confirmatory
 research. Prominently, pre-registrations were established to tie the
-researchers' hands when doing confirmatory research--reducing observable
-discrepancies between Daryl Bem's above-mentioned (a) and (b). Today,
-researchers can not only choose where to pre-register but also decide
-about the level of detail they provide. More severely, nothing stops
-researchers from pre-registering multiple hypotheses opposing each other
-\citetext{\citealp[see, e.g.,][]{SimmonsEtAl2021}; \citealp[and][ for a
-discussion]{PhamEtAl2021}}.
-
-\citet{WaldronAllen2022} report a wide variety of depth of
-pre-registrations in the field of Neuropsychopharmacology and document
-that the \emph{`pre-registered'} label can be obtained with minimal
-effort. In absence of transparency and scrutiny pre-registrations run
-into danger to miss the target of making science more credible. Even
-more so, they may have adverse effects as the \emph{`pre-registered'}
-label becomes cheap (too) to acquire.
-
-Discussing the costs and benefits of pre-registrations,
-\citet{Olken2015} stresses the uncertainty of research processes and
-promotes moderate approaches. As \citet{WaldronAllen2022}, he argues
-that pre-registrations not necessarily eliminate flexibility. These
-`moderate' or `flexible' approaches require transparency to reduce
-concerns of \emph{`data-mining'} \citep[ p.~61]{Olken2015} by showing
-(a) the analyses I planned to run, (b) the analysis that made most sense
-after collecting the data and the transition from (a) to (b). Because
-this is neither incentivized nor easy to verify, we need tools that make
-transparency convenient to establish and to scrutinize. I propose
-version control (such as Git) as one such tool and illustrate its
-application on this paper: GitHub is a website and cloud-based service
-where developers---and researchers alike---can store and manage their
-code. The service is based on Git\footnote{Git is a specific open-source
-  version control system developed in 2005.} and designed for version
-control. Importantly, changes are time-stamped and can be tracked.
-Moreover, one can create branches, that is, duplicates of code either to
-work collaboratively or to archive a certain state.
-
-To sum up, pre-registrations alone are necessary but not sufficient to
-restore the credibility in experimental sciences. Pre-registrations must
-come with additional emphasis on transparency covering the whole
-research process as well as with a higher level of scrutiny that looks
-beyond mere labels.
-
-In fact, the experiment reported in this article qualifies for the
-\emph{`pre-registered'} label at a first glance: The analysis was
+researchers' hands with respect to p-hacking and ex-post theorizing when
+doing confirmatory research---reducing observable discrepancies between
+Daryl Bem's above-mentioned (a) and (b).
+
+While pre-registrations could help to make empirical sciences more
+credible, they come at costs that are discussed by \citet{Olken2015} as
+well as \citet{Krishna2021}, \citet{SimmonsEtAl2021}, and
+\citet{PhamEtAl2021}. One important concern is that strict
+pre-registrations may severely discount any additional analysis of the
+data inspired by surprise results. In practice, there are at least two
+ways to approach that problem: First, one could (and should) add
+unforeseen analyses to the article but label them as exploratory.
+Second, one could write a minimal pre-registration leaving enough
+degrees of freedom for the researcher to incorporate such surprises
+without further notice. The key difference between the two approaches is
+the deliberate omission of transparency.
+
+For the field of neuropsychopharmacology \citet{WaldronAllen2022}
+document that the depth of pre-registrations differs indeed: it is
+spanning from notes on hypotheses only to fully specified, detailed
+experimental protocols with accompanying power analyses and sampling
+plans. Treating all pre-registrations equally may thus lead to an
+adverse effect: If one can acquire the \emph{`pre-registered'} label
+with minimal effort and maximum flexibility, the label itself may run
+into danger to become worthless and to miss the target of making science
+more credible.
+
+This erosion of credibility can be avoided by the means of
+transparency---not because transparency can tighten the ties but also
+because it facilitates scrutiny, policing
+\citep[see][]{AnkelPetersFialaNeubauer2023} and forensics: transparent
+research practices make it easier for others to track and understand a
+researcher's reaction to surprises in the data, which, in turn, gives
+the researcher more flexibility to react to these surprises. As
+additional transparency is associated with additional effort, I propose
+version control as a natural and easy-to-implement solution augmenting
+pre-registrations.
+
+Contemporary experimental research is, to a certain degree, a
+computational science: experiments often require complex software and
+the analysis thereof can result in complicated scripts. In addition,
+much research is carried out in collaborative efforts. For these reasons
+alone, it makes sense to implement version control systems such as
+GitHub and GitLab as well as OSF (albeit less powerful) that ensure that
+files are stored consistently and that changes are tracked. When these
+systems are implemented in the whole research process, one can archive
+different states of the software and visualize differences between
+different states. For instance, one can archive the analysis before and
+after the data was collected or the experimental software used in a
+pilot and the eventual experiment. Importantly, one can keep projects
+private and change their visibility to public only after the
+corresponding article is accepted for publication. Taken together, these
+features \emph{automatically} enhance transparency and facilitate
+scrutiny, policing, and forensics whilst also making software
+development and collaboration more efficient. As a consequence, the
+implementation and eventual disclosure of version control come not only
+with meta-scientific but also with organizational benefits.
+
+The experiment reported in this article qualifies for the
+\emph{`pre-registered'} label at first glance: The analysis was
 pre-registered in the American Economic Association's RCT Registry
@@
 planned to run when I designed the experiment on
-\href{https://shorturl.at/bAGKY}{GitHub}.\footnote{https://shorturl.at/bAGKY
-  to run the code, you need to execute the .Rmd files in this repository
-  in the order that is indicated by file names.}
-
-At a second glance, the analysis that made the most sense after having
+\href{https://github.com/Howquez/GMTV/tree/July21Replication/analysis/R}{GitHub}.\footnote{bit.ly/3Pnak5H.
+  To run the code, you need to execute the .Rmd files in this repository
+  in the order that is indicated by file names. Detailed instructions
+  can be found in the README file accompanying the analysis scripts.}
+
+At second glance, the analysis that made the most sense after having
 collected the data and that is reported here is a little different
@@
 
-Accordingly, I edited many of the analyses scripts.\footnote{The source
+Accordingly, I edited many of the analysis scripts.\footnote{The source
   code of this document contains the analysis and can be found
-  \href{https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}{here}:
-  https://shorturl.at/ilpAG} However, because the originally planned
+  \href{https://github.com/Howquez/GMTV/blob/main/analysis/article/paper.qmd}{here}:
+  https://bit.ly/43LCyLw} However, because the originally planned
 analysis code is archived and reproducible, these changes are
@@
 software to do and the explanation one tells human beings one told the
-statistical software to do. As such, (a), (b) and the transition from
+statistical software to do. As such, (a), (b), and the transition from
 (a) to (b) are not only transparent but also comprehensible.
@@
 In the terminology of \citet{Hamermesh2007}, I ran both a \emph{pure} as
-well as a \emph{scientific} reproduction\footnote{\citet{Parsons2022}
-  use the term of a \emph{conceptual replication} which means the same.}
-of one treatment of GMTVs' dynamic public goods game. The pure
-reproduction re-analyzes the original data.
+well as a \emph{scientific} reproduction\footnote{In fact,
+  \citet{Hamermesh2007} uses the term \emph{replication} instead of
+  \emph{reproduction}. The reason I deviate is that I do not compare
+  different treatments with each other to \emph{replicate} a treatment
+  effect. Instead, I \emph{reproduce} the results of one specific
+  treatment arm.} of one treatment of GMTVs' dynamic public goods game.
+The pure reproduction re-analyzes the original data.
 \protect\hyperlink{A:-Pure-Replication}{Appendix A} documents
-\href{}{errors I identified} in the original paper. The scientific
+\href{}{the errors I identified} in the original paper. The scientific
 reproduction, where I utilize a different sample drawn from a different
@@
 
-Considering the design, the only differences between such a
+Considering the design, the `only' differences between such a
 \emph{static} game (with partner matching) and GMTVs' design are
@@
 a European level. Finally, I informed the participants that the
-documentation of individual and aggregate contributions were to be
-posted immediately after the concluding the sessions online. To avoid
+documentation of individual and aggregate contributions was to be posted
+immediately after the conclusion of the sessions online. To avoid
 privacy or social image concerns, participants learned their unique and
@@
 
-I recruited the participants from the so called
+I recruited the participants from the so-called
 \emph{\href{https://www.wiso.uni-hamburg.de/forschung/forschungslabor/umfragelabor/aktuelle-umfragen/hamburgpanel.html}{HamburgPanel}}
@@
 
-Throughout this paper, I will compare results of my experiment with the
-results of GMTVs' NOPUNISH 10 Period treatments. I am thus, referring to
-three different samples utilized at two points in time: the University
-of Nottingham's students (in late 2012), Hamburg's citizens and the
-University Hamburg's students (both in July 2021).
+Throughout this paper, I will compare the results of my experiment with
+the results of GMTVs' NOPUNISH 10 Period treatments. I am thus,
+referring to three different samples utilized at two points in time: the
+University of Nottingham's students (in late 2012), Hamburg's citizens,
+and the University of Hamburg's students (both in July 2021).
 Table~\ref{tbl-sample-properties} gives an overview.
@@
 This makes dropouts not only more likely but also more expensive, which
-is why attrition was a major concern implementing the experiment.
+is why attrition was a major concern in implementing the experiment.
 
 I chose oTree \citep{oTree} to implement the experiment because it is
-open-source, well documented and very flexible. Its
+open-source, well-documented, and very flexible. Its
 \href{https://getbootstrap.com/}{Bootstrap} (a powerful frontend
 toolkit) integration allowed me to make the graphical user interface
-interactive, appealing and easy to navigate. The
+interactive, appealing, and easy to navigate. The
 \href{https://www.highcharts.com/}{Highcharts library} made it easy to
-visualize results and to communicate dynamics. Insofar, oTree served a
+visualize results and communicate dynamics. Insofar, oTree served as a
 good tool to enhance the participants' user experience and thus, to make
@@
 times and boredom for other participants. Section~\ref{sec-feasibility}
-shows that the first feature became effective in some cases, wheres the
+shows that the first feature became effective in some cases, whereas the
 second feature did not.
@@
 exposed to the decision screen over ten periods. At the end of the last
-period, participants saw results of all periods. Subsequently, they made
-their VCA decision, before I elicited risk preferences
+period, participants saw the results of all periods. Subsequently, they
+made their VCA decision, before I elicited risk preferences
 \citep{HoltLaury2002} and finished with GMTVs' questionnaire.
@@
 The experiment lasted around 25 minutes on average. The earnings
-averaged 11.23 Euros (sd = 4.85).\footnote{This values include earnings
+averaged 11.23 Euros (sd = 4.85).\footnote{This value include earnings
   from the incentivized risk elicitation task that is not part of the
@@
 \hypertarget{sec-replication}{%
-\subsection{Pre-registered GMTV Reproduction}\label{sec-replication}}
+\subsection{Reproducibility}\label{sec-replication}}
 
@@
 average (median and mean). Moreover, both samples' initial contributions
-resemble initial contributions participants usually make in the static
-game with partner matching.\footnote{See Figure 3B in
+resemble the initial contributions participants usually make in the
+static game with partner matching.\footnote{See Figure 3B in
   \citet[p.989]{fehrgaechter2000}, for instance.} However, in the
-dynamic game presented here, I are particularly interested in the
+dynamic game presented here, I am particularly interested in the
 subsequent periods because differences add up exponentially. Do the two
@@
 In particular, do the two samples' contributions follow the same path
-over the 10 periods they played? The answer is \emph{no}.
-Figure~\ref{fig-share-of-contributions} illustrates that the samples
-make similar contributions at the beginning and the end of the game but
+over the 10 periods they played? The answer is \emph{yes and no}.
+Figure~\ref{fig-share-of-contributions} and
+Table~\ref{tbl-contribution-periods} illustrate that the samples make
+similar contributions at the beginning and the end of the game but
 behave differently in between. More precisely, the left panel--depicting
@@
 usually make in the static game with partner matching: contributions
-equal approximately half of endowments in the very first period and
+equal approximately half of the endowments in the very first period and
 decrease to around ten percent of endowments by the last
@@
 dynamic game presented here, however, different paths lead to different
-levels of wealth -- even if they share the same start- and end-points. I
+levels of wealth -- even if they share the same start- and endpoints. I
 am thus, more interested in the contributions' implications for wealth
@@
 
-How do the different contribution-paths translate into
+How do the different contribution paths translate into
 wealth?\footnote{To measure wealth and growth, I define a variable
@@
   given group at the end of the round (that is, after the contributions
-  have been made, multiplied and redistributed).} Given that the
+  have been made, multiplied, and redistributed).} Given that the
 original sample contributed more, one would expect the respective groups
@@
 average group in the original sample accumulated about 478 tokens. In
-contrast, an average group in the reproduction sample accumulated about
+contrast, the average group in the reproduction sample accumulated about
 380 tokens. This difference is insignificant at conventional levels
 though: A two-sided rank sum test (comparing differences between
-samples) yields p=0.136 for the mean stock in last period of the game.
+samples) yields p=0.136 for the mean stock in the last period of the
+game.
 
 Although there clearly is growth, groups do not realize the maximal
-potential efficiency: under full cooperation, a group can accumulate at
-maximum 4613 tokens or EUR 230. This is depicted in the left panel of
+potential efficiency: under full cooperation, a group can accumulate a
+maximum of 4613 tokens or EUR 230. This is depicted in the left panel of
 Figure~\ref{fig-growth-heterogeneity}, where one can see the average
@@
 Given the different samples and the possibility of endogenous
-growth--which essentially is the main feature of the game--I ask whether
-and how the inequality grows \emph{within} groups.
+growth---which essentially is the main feature of the game---I ask
+whether and how the inequality grows \emph{within} groups.
 Figure~\ref{fig-gini-time-series} illustrates that inequality did grow:
@@
   two-sided rank sum test (comparing differences between samples) yields
-  p=0.606 for the mean Gini coefficient in last round of the game.}
+  p=0.606 for the mean Gini coefficient in the last round of the game.}
 Because every participant started with the same initial endowment (in
@@
 be replicated because the replication data resemble the original data
-with respect to initial and final contributions, wealth and growth as
+with respect to initial and final contributions, wealth, and growth as
 well as inequality.}
@@
 different software and user interface as well as the online setting
-during the COVID19 pandemic. The result suggests that, by and large, the
+during the COVID-19 pandemic. The result suggests that by and large, the
 sum of these factors did not affect people's preferences towards
@@
 nobody indicated that he or she did not understand the situation at all.
-There is some behavioral data supporting this finding: The user
-interface offered a popup to review instructions or contact information.
-I tracked both and find that none of the participants ever opened these
-popups even though they were clearly visible in the decision screens'
-header and introduced in the instructions. To further analyze how
-participants coped with the situation, I consider three additional
-metrics: selection into the experiment, attrition as well as the time
-spent on each page.
+Some behavioral data are supporting this finding: The user interface
+offered a popup to review instructions or contact information. I tracked
+both and find that none of the participants ever opened these popups
+even though they were clearly visible in the decision screens' header
+and introduced in the instructions. To further analyze how participants
+coped with the situation, I consider three additional metrics: selection
+into the experiment, attrition as well as the time spent on each page.
 
@@
 to recruit the sample. The panel counted 1.209 non-students of which I
-were able to recruit 130 participants who finished the experiment---even
+was able to recruit 130 participants who finished the experiment---even
 though I varied the weekdays and timing of the sessions (which were
-conducted during a nation-wide lockdown with home office regime). For
+conducted during a nationwide lockdown with home office regime). For
 this reason, I also recruited students in the last session which
@@
 Although I intended to refrain from the recruitment of students
-initially, this particular sub sample enabled me to investigate the
+initially, this particular sub-sample enabled me to investigate the
 generalizability of my results as I will discuss in
@@
 the dynamic public goods game as \citet{Anderhub2001} did. How many
-seconds did the participants need to make a decision in each period of
-the game? Not too many. Figure~\ref{fig-time-spent} illustrates an
-intuitive pattern: The first decision took about 22 seconds. The second
-decision--where participants first learned about the other group
-members' previous decisions--took longer (about 33 seconds).
+seconds did the participants need to decide in each period of the game?
+Not too many. Figure~\ref{fig-time-spent} illustrates an intuitive
+pattern: The first decision took about 22 seconds. The second
+decision---where participants first learned about the other group
+members' previous decisions---took longer (about 33 seconds).
 Subsequently, decision times first declined and stabilized at 19
 seconds. Importantly, decision times were so short that crosstalk, that
-is, communication through private channels--a common concern\footnote{See,
+is, communication through private channels---a common concern\footnote{See,
   for instance, the discussion section in \citet[p.~119]{AGM2018}.} in
-online experiments--was unlikely, especially because it would require
+online experiments---was unlikely, especially because it would require
 the identification of other group members.\footnote{There were only 9
@@
 
-\caption{\label{fig-time-spent}Average Time Spent for each Contribution
+\caption{\label{fig-time-spent}Average Time Spent for Each Contribution
 per Period}
@@
 procedure, attrition was as negligible as it is in physical
-laboratories---where (a) not every invited person shows up and (b) a
-number of participants divisible by the group size is required as well.}
+laboratories---where (a) not every invited person shows up and (b)
+several participants divisible by the group size are required as well.}
 
@@
 panels illustrate the behavior of the student sample. The left panels
-show the behavior in the VCA. The right panels show the behavior in
+show the behavior in the VCA. The right panels show the behavior in the
 first period of the game. A visual inspection shows that (a) mean
@@
 is for students. Or, to put it differently, the general population's
-behavior in the abstract game better predicts their behavior in
+behavior in the abstract game better predicts their behavior in a
 real-world mitigation context.
@@
 status negatively affects VCA donations in column two but disappears if
-one controls for age in column three. Importantly, the interaction of
-student status and first-period contributions is not significant. This
-suggests that the general population sample's transferability is just as
-bad as the student sample's. I thus, find a similar result as
-\citet[p.6]{GKLS2020}.
+one controls for age in column three. Importantly, the interaction
+between student status and first-period contributions is not
+significant. This suggests that the general population sample's
+transferability is just as bad as the student sample's. I thus, find a
+similar result as \citet[p.6]{GKLS2020}.
 
@@
 contribution behavior in the dynamic abstract setting is not linked to
-behavior in the real world -- neither for students nor a more
+behavior in the real world---neither for students nor a more
 representative sample.
@@
 highlights that even logistically complex experiments can be conducted
-online with---not only with clickworkers but also with a true general
+online---not only with clickworkers but also with a true general
 population sample. The third result questions whether recruiting from
-more representative samples is worth the efforts because it did not
-affect transferability of abstract results to the real world.
+more representative samples is worth the effort because it did not
+affect the transferability of abstract results to the real world.
 
@@
 paradigm is reproducible across samples (yes) and whether it is feasible
-employ it online (also yes). The question that is \emph{not} answered
+to employ it online (also yes). The question that is \emph{not} answered
 is, whether GMTVs' treatment effects replicate well because I did not
 focus on treatments and treatment effects. It thus, remains an open
-question, whether the causal effect of GMTVs' treatments replicate well.
-Further, we do not know whether their treatments affect real-world
-behavior. How generalizable are treatment effects in public goods games
-in general? Albeit this study does not address these questions, it
+question, whether the causal effects of GMTVs' treatments replicate
+well. Further, we do not know whether their treatments affect real-world
+behavior. So, how generalizable are treatment effects in public goods
+games in general? Albeit this study does not address these questions, it
 provides methods suited to investigate them---even with inconvenient
@@
 Climatic Change, and Society'' (project 390683824). I thank Stefan Traub
-and participants of the CLICCS B5 group for helpful discussions.
+and the participants of the CLICCS B5 group for helpful discussions.
 
@@
 members. According to the authors, the Gini coefficient should equal
-\texttt{GINI=}0.127 for all subjects in the group. Instead, participant
+\texttt{GINI=}0.127 for all subjects in the group. Instead, participants
 \texttt{112} and \texttt{113} who have an equal endowment deviate from
@@
 \hline
-1 & 0.134 & 0.111 - 0.157 & 0.131 & 0.111 - 0.151 & 0.825\\
+1 & 0.134 & 0.111 - 0.157 & 0.131 & 0.111 - 0.151 & 0.818\\
 \hline

### 2023-06-28 analysis/article/paper.qmd
pre-submission commit

@@
       cite-style: authoryear
-      highlights:
-        - Highlight 1
-        - Highlight 2 
-        - Highlight 3
 ---
@@
 
+# Importantly, as of today, I don't remember how to perfectly identify students in the last session.
+Hence, I label all participants in that session as students.
+This is reasonable when analyzing group level outcomes because it is likely that there was at least one student in many of the groups.
+It is somewhat problematic in the generalization discussion.
+However, using age as an additional variable to guess student status (e.g.
+non-student if age > 30) does not not change the results qualitatively.
+
 main[, student := FALSE]
@@
 @AGM2018 conducted static public goods games in the lab and on MTurk to draw (and report) lessons from online experimentation.
-This study extends this literature [see, e.g., @SnowbergYariv_2021; @GuptaRigottiWilson_2021; @GoodmanPaolacci2017; @AmirEtAl2012] by focusing on an _inconvenient_ sample (i.e.
-one that is a completely inexperienced sample that has not been exposed to interactive experiments before) playing a computationally more complex game.
+This study extends this literature [see, e.g., @KrantzEtAl1997, @AmirEtAl2012; @KleinEtAl2014; @PaolacciChandler2014; @GoodmanPaolacci2017; @SnowbergYariv_2021; @GuptaRigottiWilson_2021; @BusoEtAl2021] by focusing on an _inconvenient_ sample (i.e.
+one that is a completely inexperienced sample [see also @BenndorfEtAl2017] that has not been exposed to interactive experiments before) playing a computationally more complex game during a time that was characterized by more inattentiveness in online samples [@ArecharRand2021; @PeytonEtAl2022].
 This required me to design robust (and thus, more complex) software to minimize attrition.
-I collected para data---which capture screen time and survey navigation, for instance---to assess the desired fluency and feasibility of the experiment.
+I collected para data [@Parsons2022 p.
+12]---which capture screen time and survey navigation, for instance---to assess the desired fluency and feasibility of the experiment.
 Like @AGM2018, this research is of practical relevance as it reports on the robust design that made the dynamic game feasible.
@@
 
-Well before credibility crises comprised a variety of disciplines^[See e.g., @CamererEtAl2016; @BrodeurEtAl2016; @BrodeurEtAl2020; @ChristensenMiguel2018; @FerraroShukla2020 who focus on economics.], @bemwriting [p.
+Well before credibility crises comprised a variety of disciplines^[See e.g., @CamererEtAl2016; @BrodeurEtAl2016; @BrodeurEtAl2020; @ChristensenMiguel2018; @FerraroShukla2020; @PageEtAl2021 who focus on economics.], @bemwriting [p.
 2] indirectly conceded discrepancies between fuzzy research processes and the polished article that results from it:
@@
 Now, 20 years later, we accustom ourselves to mechanisms designed to unravel the fuzzy back-and-forth between exploratory and confirmatory research.
-Prominently, pre-registrations were established to tie the researchers' hands with respect to p-hacking and ex-post theorizing when doing confirmatory research---reducing observable discrepancies between Daryl Bem's above-mentioned (a) and (b).
-
-While pre-registrations could help to make empirical sciences more credible, they come at costs that are discussed by @Olken2015 as well as @Krishna2021, @SimmonsEtAl2021, and @PhamEtAl2021.
+Prominently, pre-registrations and pre-analysis plans (PAP) [see, e.g., @BrodeurEtAl2022] were established to tie the researchers' hands with respect to p-hacking and ex-post theorizing when doing confirmatory research---reducing observable discrepancies between Daryl Bem's above-mentioned (a) and (b).
+
+While pre-registrations and PAPs could help to make empirical sciences more credible, they come at costs that are discussed by @Olken2015, @PageEtAl2021, as well as @Krishna2021, @SimmonsEtAl2021, and @PhamEtAl2021.
 One important concern is that strict pre-registrations may severely discount any additional analysis of the data inspired by surprise results.
@@
 
-This erosion of credibility can be avoided by the means of transparency---not because transparency can tighten the ties but also because it facilitates scrutiny, policing [see @AnkelPetersFialaNeubauer2023] and forensics: transparent research practices make it easier for others to track and understand a researcher's reaction to surprises in the data, which, in turn, gives the researcher more flexibility to react to these surprises.
+This erosion of credibility can be avoided by the means of transparency---not because transparency can tighten the ties but because it facilitates scrutiny, policing [see @AnkelPetersFialaNeubauer2023] and forensics [see, e.g., @SimonsohnEtAl2023]: transparent research practices make it easier for others to track and understand a researcher's reaction to surprises in the data, which, in turn, gives the researcher more flexibility to react to these surprises.
 As additional transparency is associated with additional effort, I propose version control as a natural and easy-to-implement solution augmenting pre-registrations.
@@
 The analysis was pre-registered in the American Economic Association's RCT Registry [@preregistration].
-Further, I pre-registered the exact analyses I planned to run when I designed the experiment on [GitHub](https://github.com/Howquez/GMTV/tree/July21Replication/analysis/R).^[bit.ly/3Pnak5H.
+Further, I pre-registered the exact analyses I planned to run (PAP) when I designed the experiment on [GitHub](https://github.com/Howquez/GMTV/tree/July21Replication/analysis/R).^[bit.ly/3Pnak5H.
 To run the code, you need to execute the .Rmd files in this repository in the order that is indicated by file names.
@@
 Third, the underlying game was dynamic and interdependent.
-This makes dropouts not only more likely but also more expensive, which is why attrition was a major concern in implementing the experiment.
+This makes dropouts not only more likely but also more expensive, which is why attrition  was a major concern in implementing the experiment.^[see @ZhouFischbach2016 for a nice illustration of how (selective) attrition affects identification.]
 
@@
 Not too many.
-@fig-time-spent illustrates an intuitive pattern: The first decision took about `r tmp[round == 1, round(time_spent)]` seconds.
+@fig-time-spent illustrates an plausible pattern: The first decision took about `r tmp[round == 1, round(time_spent)]` seconds.
 The second decision---where participants first learned about the other group members' previous decisions---took longer (about `r tmp[round == 2, round(time_spent)]` seconds).
@@
 I gratefully acknowledge support by the German Research Foundation (DFG) under Germany’s Excellence Strategy, cluster EXC 2037 “Climate, Climatic Change, and Society” (project 390683824).
-I thank Stefan Traub and the participants of the CLICCS B5 group for helpful discussions.
+I thank Stefan Traub, whoever proofreads this and the participants of the CLICCS B5 group for helpful discussions.
 

### 2023-06-28 analysis/article/paper.tex
pre-submission commit

@@
 
-\begin{highlights}
-\item Highlight 1\item Highlight 2\item Highlight 3
-\end{highlights}
-
 \begin{keyword}
@@
 \end{keyword}
-\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced, sharp corners, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi
+\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced, interior hidden, boxrule=0pt]}{\end{tcolorbox}}\fi
 
@@
 MTurk to draw (and report) lessons from online experimentation. This
-study extends this literature \citep[see,
-e.g.,][]{SnowbergYariv_2021, GuptaRigottiWilson_2021, GoodmanPaolacci2017, AmirEtAl2012}
+study extends this literature \citetext{\citealp[see,
+e.g.,][\citet{AmirEtAl2012}]{KrantzEtAl1997}; \citealp{KleinEtAl2014}; \citealp{PaolacciChandler2014}; \citealp{GoodmanPaolacci2017}; \citealp{SnowbergYariv_2021}; \citealp{GuptaRigottiWilson_2021}; \citealp{BusoEtAl2021}}
 by focusing on an \emph{inconvenient} sample (i.e.~one that is a
-completely inexperienced sample that has not been exposed to interactive
-experiments before) playing a computationally more complex game. This
-required me to design robust (and thus, more complex) software to
-minimize attrition. I collected para data---which capture screen time
-and survey navigation, for instance---to assess the desired fluency and
-feasibility of the experiment. Like \citet{AGM2018}, this research is of
-practical relevance as it reports on the robust design that made the
-dynamic game feasible.
+completely inexperienced sample \citep[see also][]{BenndorfEtAl2017}
+that has not been exposed to interactive experiments before) playing a
+computationally more complex game during a time that was characterized
+by more inattentiveness in online samples
+\citep{ArecharRand2021, PeytonEtAl2022}. This required me to design
+robust (and thus, more complex) software to minimize attrition. I
+collected para data \citep[ p.~12]{Parsons2022}---which capture screen
+time and survey navigation, for instance---to assess the desired fluency
+and feasibility of the experiment. Like \citet{AGM2018}, this research
+is of practical relevance as it reports on the robust design that made
+the dynamic game feasible.
 
@@
   \citet{BrodeurEtAl2016}; \citet{BrodeurEtAl2020};
-  \citet{ChristensenMiguel2018}; \citet{FerraroShukla2020} who focus on
-  economics.}, \citet[p.~2]{bemwriting} indirectly conceded
-discrepancies between fuzzy research processes and the polished article
-that results from it:
+  \citet{ChristensenMiguel2018}; \citet{FerraroShukla2020};
+  \citet{PageEtAl2021} who focus on economics.},
+\citet[p.~2]{bemwriting} indirectly conceded discrepancies between fuzzy
+research processes and the polished article that results from it:
 
@@
 unravel the fuzzy back-and-forth between exploratory and confirmatory
-research. Prominently, pre-registrations were established to tie the
+research. Prominently, pre-registrations and pre-analysis plans (PAP)
+\citep[see, e.g.,][]{BrodeurEtAl2022} were established to tie the
 researchers' hands with respect to p-hacking and ex-post theorizing when
@@
 
-While pre-registrations could help to make empirical sciences more
-credible, they come at costs that are discussed by \citet{Olken2015} as
-well as \citet{Krishna2021}, \citet{SimmonsEtAl2021}, and
-\citet{PhamEtAl2021}. One important concern is that strict
-pre-registrations may severely discount any additional analysis of the
-data inspired by surprise results. In practice, there are at least two
-ways to approach that problem: First, one could (and should) add
-unforeseen analyses to the article but label them as exploratory.
-Second, one could write a minimal pre-registration leaving enough
-degrees of freedom for the researcher to incorporate such surprises
-without further notice. The key difference between the two approaches is
-the deliberate omission of transparency.
+While pre-registrations and PAPs could help to make empirical sciences
+more credible, they come at costs that are discussed by
+\citet{Olken2015}, \citet{PageEtAl2021}, as well as \citet{Krishna2021},
+\citet{SimmonsEtAl2021}, and \citet{PhamEtAl2021}. One important concern
+is that strict pre-registrations may severely discount any additional
+analysis of the data inspired by surprise results. In practice, there
+are at least two ways to approach that problem: First, one could (and
+should) add unforeseen analyses to the article but label them as
+exploratory. Second, one could write a minimal pre-registration leaving
+enough degrees of freedom for the researcher to incorporate such
+surprises without further notice. The key difference between the two
+approaches is the deliberate omission of transparency.
 
@@
 This erosion of credibility can be avoided by the means of
-transparency---not because transparency can tighten the ties but also
-because it facilitates scrutiny, policing
-\citep[see][]{AnkelPetersFialaNeubauer2023} and forensics: transparent
-research practices make it easier for others to track and understand a
-researcher's reaction to surprises in the data, which, in turn, gives
-the researcher more flexibility to react to these surprises. As
-additional transparency is associated with additional effort, I propose
-version control as a natural and easy-to-implement solution augmenting
-pre-registrations.
+transparency---not because transparency can tighten the ties but because
+it facilitates scrutiny, policing
+\citep[see][]{AnkelPetersFialaNeubauer2023} and forensics \citep[see,
+e.g.,][]{SimonsohnEtAl2023}: transparent research practices make it
+easier for others to track and understand a researcher's reaction to
+surprises in the data, which, in turn, gives the researcher more
+flexibility to react to these surprises. As additional transparency is
+associated with additional effort, I propose version control as a
+natural and easy-to-implement solution augmenting pre-registrations.
 
@@
 \citep{preregistration}. Further, I pre-registered the exact analyses I
-planned to run when I designed the experiment on
+planned to run (PAP) when I designed the experiment on
 \href{https://github.com/Howquez/GMTV/tree/July21Replication/analysis/R}{GitHub}.\footnote{bit.ly/3Pnak5H.
@@
 This makes dropouts not only more likely but also more expensive, which
-is why attrition was a major concern in implementing the experiment.
+is why attrition was a major concern in implementing the
+experiment.\footnote{see \citet{ZhouFischbach2016} for a nice
+  illustration of how (selective) attrition affects identification.}
 
@@
 seconds did the participants need to decide in each period of the game?
-Not too many. Figure~\ref{fig-time-spent} illustrates an intuitive
+Not too many. Figure~\ref{fig-time-spent} illustrates an plausible
 pattern: The first decision took about 22 seconds. The second
@@
 under Germany's Excellence Strategy, cluster EXC 2037 ``Climate,
-Climatic Change, and Society'' (project 390683824). I thank Stefan Traub
-and the participants of the CLICCS B5 group for helpful discussions.
+Climatic Change, and Society'' (project 390683824). I thank Stefan
+Traub, whoever proofreads this and the participants of the CLICCS B5
+group for helpful discussions.
 

### 2023-06-28 otreeLite/A_Intro/__init__.py

@@ -34,9 +34,10 @@ class A_Welcome(Page):
     pass
 
 
-class B_Instructions(Page):
+class B_Instructions_1(Page):
     form_model = "player"
-    form_fields = ["formula_shown"]
+    # form_fields = ["formula_shown"]
+
     @staticmethod
     def before_next_page(player, timeout_happened):
         player.participant.waited_too_long = False
@@ -53,6 +54,97 @@ class B_Instructions(Page):
             max_mpcr=round((player.session.config["efficiency_factor"]/player.session.config["group_size"])*100, 1),
         )
 
+class B_Instructions_2(Page):
+    form_model = "player"
+    # form_fields = ["formula_shown"]
+
+    @staticmethod
+    def before_next_page(player, timeout_happened):
+        player.participant.waited_too_long = False
+        player.participant.wait_page_arrival = time.time()
+
+    @staticmethod
+    def vars_for_template(player: Player):
+        return dict(
+            redirect="",
+            damage=int(player.session.config["damage"] * 100),
+            risk=int(player.session.config["risk"] * 100),
+            group_members=player.session.config["group_size"] - 1,
+            min_mpcr=round((player.session.config["efficiency_factor"] / player.session.config["group_size"] -
+                            player.session.config["risk"] * player.session.config["damage"]) * 100, 1),
+            max_mpcr=round((player.session.config["efficiency_factor"] / player.session.config["group_size"]) * 100,
+                           1),
+        )
+
+class B_Instructions_3(Page):
+    form_model = "player"
+    # form_fields = ["formula_shown"]
+
+    @staticmethod
+    def before_next_page(player, timeout_happened):
+        player.participant.waited_too_long = False
+        player.participant.wait_page_arrival = time.time()
+
+    @staticmethod
+    def vars_for_template(player: Player):
+        return dict(
+            redirect="",
+            damage=int(player.session.config["damage"] * 100),
+            risk=int(player.session.config["risk"] * 100),
+            group_members=player.session.config["group_size"] - 1,
+            min_mpcr=round((player.session.config["efficiency_factor"] / player.session.config["group_size"] -
+                            player.session.config["risk"] * player.session.config["damage"]) * 100, 1),
+            max_mpcr=round((player.session.config["efficiency_factor"] / player.session.config["group_size"]) * 100,
+                           1),
+        )
+
+class B_Instructions_4(Page):
+    form_model = "player"
+    # form_fields = ["formula_shown"]
+
+    @staticmethod
+    def before_next_page(player, timeout_happened):
[…]

### 2023-06-28 otreeLite/settings.py

@@ -11,23 +11,7 @@ SESSION_CONFIGS = [
         risk=0,
         damage=0,
         initial_endowment=20,
-    ),
-    dict(
-        name="Clubs",
-        app_sequence=["A_Intro", "B_Clubs", "D_Outro"],
-        num_demo_participants=2,
-    ),
-    dict(
-        name="EWE",
-        app_sequence=["A_Intro", "B_EWE", "D_Outro"],
-        num_demo_participants=3,
-        num_rounds=10,
-        group_size=3,
-        efficiency_factor=1.5,
-        risk=0.2,
-        damage=0.5,
-        initial_endowment=20,
-    ),
+    )
 ]
 
 # if you set a property in SESSION_CONFIG_DEFAULTS, it will be inherited by all configs

### 2023-07-04 analysis/article/paper.qmd
repair table lables & some writing

@@
   - Generalizability
-  - Online Experiment
+  - Online experiment
   - Climate change mitigation
@@
 <!-- Think of lifetime consumption‐smoothing and save more tomorrow -->
-Opting for environmentally friendly policies today not only reduces carbon dioxide emissions immediately but also helps us to reach the Paris climate targets tomorrow.
-Deferring these policies, may not necessarily prevent us from reaching these targets, but it requires more effort in the future compared to a path that includes immediate action [@HaenselEtAl2022].
-Aiming at certain goals, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of paths one can choose from that lead to that specific goal.
+For example, opting for environmentally friendly policies today not only reduces carbon dioxide emissions immediately, but also helps us reach the Paris climate targets tomorrow.
+Deferring these policies to a later state, may not necessarily prevent us from reaching these targets, but it will require more effort in the future compared to a path which includes immediate action [@HaenselEtAl2022].
+Aiming at certain goals, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of viable paths one can choose from that lead to that specific goal.
 
 Public good (or public bad) games---although often intended to inform climate policies [e.g.
-@MilinskiEtAl2006; @TavoniEtAl2011; @Hauser2014; @BrickEtAl2015; @GomezEtAl2018; @CalzolariEtAl2018; @CookEtAl2019]---miss these temporal interdependencies simply because participants have the same set of actions in each period.
+@MilinskiEtAl2006; @TavoniEtAl2011; @Hauser2014; @BrickEtAl2015; @GomezEtAl2018; @CalzolariEtAl2018; @CookEtAl2019]---fail to include these temporal interdependencies simply because participants have the same set of actions in each period.
 Accordingly, participants' actions in a given period do not affect their action space in subsequent periods.
-To see the lack of realism, consider carbon dioxide emissions, where the current stock will last for well over a millennium [@Inman2008; @CalzolariEtAl2018].
+To better capture the lack of realism, consider carbon dioxide emissions, where the current stock will last for well over a millennium [@Inman2008; @CalzolariEtAl2018].
 Playing with fresh endowments in each period is as if one could just undo carbon dioxide emissions at no cost.
 
-A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017 hereafter, GMTV] as well as Stefan Große (unpublished), shows that it is fairly simple to add this element of realism.
+A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017 hereafter, GMTV] as well as Stefan Große (unpublished), shows that it is relatively simple to include this element of realism.
 They incorporate interdependencies into a _dynamic_ public goods game (dPGG) by defining endowments as the income of previous periods.
@@
 
-Because there is surprisingly little experimental research on interdependencies^[See e.g.
+As there is surprisingly little experimental research on interdependencies^[See e.g.
 @BattagliniEtAl2016, @Rockenbach2017 or @Moser2019.], I reproduced one of GMTVs' treatments to compare dynamics across (in)experienced samples to investigate its generalizability.
 @GKLS2020 find that static public goods games do not generalize well to real-world climate action.
-They also find that generalizability depends on the structural resemblance of the public goods game with the context of climate change mitigation: Greater resemblance improves generalizability.
+They also find that generalizability is dependent on the structural resemblance of the public goods game with the context of climate change mitigation: Greater resemblance improves generalizability.
 Because GMTVs' dynamic setting has a more realistic property—namely, interdependencies—one would expect it to be better suited to inform public policy.
-To test this intuition, I not only ran the experiment with different samples but also
+As means to test this intuition, I not only ran the experiment with different samples but also
 <!--, that is, with participants who make their decisions in an environment which is more natural than the lab.-->
@@
 one that is a completely inexperienced sample [see also @BenndorfEtAl2017] that has not been exposed to interactive experiments before) playing a computationally more complex game during a time that was characterized by more inattentiveness in online samples [@ArecharRand2021; @PeytonEtAl2022].
-This required me to design robust (and thus, more complex) software to minimize attrition.
+With this background in mind, it required me to design robust (and thus, more complex) software to minimize attrition.
 I collected para data [@Parsons2022 p.
@@
 
-Now, 20 years later, we accustom ourselves to mechanisms designed to unravel the fuzzy back-and-forth between exploratory and confirmatory research.
-Prominently, pre-registrations and pre-analysis plans (PAP) [see, e.g., @BrodeurEtAl2022] were established to tie the researchers' hands with respect to p-hacking and ex-post theorizing when doing confirmatory research---reducing observable discrepancies between Daryl Bem's above-mentioned (a) and (b).
+Today, 20 years later, we have accustomed ourselves to mechanisms designed to unravel the fuzzy back-and-forth between exploratory and confirmatory research.
+Prominently, pre-registrations and pre-analysis plans (PAP) [see, e.g., @BrodeurEtAl2022] were established as a means to tie the researchers' hands with respect to p-hacking and ex-post theorizing when doing confirmatory research---reducing observable discrepancies between Daryl Bem's above-mentioned (a) and (b).
 
@@
 One important concern is that strict pre-registrations may severely discount any additional analysis of the data inspired by surprise results.
-In practice, there are at least two ways to approach that problem: First, one could (and should) add unforeseen analyses to the article but label them as exploratory.
+In practice, there are at least two ways to approach that problem: First, one could (and should) add unforeseen analyses to the article but be sure to label them as exploratory.
 Second, one could write a minimal pre-registration leaving enough degrees of freedom for the researcher to incorporate such surprises without further notice.
@@
 For the field of neuropsychopharmacology @WaldronAllen2022 document that the depth of pre-registrations differs indeed: it is spanning from notes on hypotheses only to fully specified, detailed experimental protocols with accompanying power analyses and sampling plans.
-Treating all pre-registrations equally may thus lead to an adverse effect: If one can acquire the _'pre-registered'_ label with minimal effort and maximum flexibility, the label itself may run into danger to become worthless and to miss the target of making science more credible.
-
-This erosion of credibility can be avoided by the means of transparency---not because transparency can tighten the ties but because it facilitates scrutiny, policing [see @AnkelPetersFialaNeubauer2023] and forensics [see, e.g., @SimonsohnEtAl2023]: transparent research practices make it easier for others to track and understand a researcher's reaction to surprises in the data, which, in turn, gives the researcher more flexibility to react to these surprises.
+Treating all pre-registrations equally may thus lead to an adverse effect: If one can acquire the _'pre-registered'_ label with minimal effort and maximum flexibility, the label itself may run into danger by becomming worthless and to missing the target of making science more credible.
+
+This erosion of credibility can be avoided by the means of transparency---not because transparency can tighten the ties but because it facilitates scrutiny, policing [see @AnkelPetersFialaNeubauer2023] and forensics [see, e.g., @SimonsohnEtAl2023]: transparent research practices make it easier for others to track and understand a researcher's reaction to surprises within the data, which, in turn, gives the researcher more flexibility to react to said surprises.
 As additional transparency is associated with additional effort, I propose version control as a natural and easy-to-implement solution augmenting pre-registrations.
@@
 For these reasons alone, it makes sense to implement version control systems such as GitHub and GitLab as well as OSF (albeit less powerful) that ensure that files are stored consistently and that changes are tracked.
-When these systems are implemented in the whole research process, one can archive different states of the software and visualize differences between different states.
+When these systems are implemented throughout the entire research process, one can archive different states of the software and visualize differences between different states.
 For instance, one can archive the analysis before and after the data was collected or the experimental software used in a pilot and the eventual experiment.
 Importantly, one can keep projects private and change their visibility to public only after the corresponding article is accepted for publication.
-Taken together, these features _automatically_ enhance transparency and facilitate scrutiny, policing, and forensics whilst also making software development and collaboration more efficient.
+Taken together, these features _automatically_ enhance transparency and facilitate scrutiny, policing, and forensics whilst making software development and collaboration more efficient.
 As a consequence, the implementation and eventual disclosure of version control come not only with meta-scientific but also with organizational benefits.
@@
 The analysis was pre-registered in the American Economic Association's RCT Registry [@preregistration].
-Further, I pre-registered the exact analyses I planned to run (PAP) when I designed the experiment on [GitHub](https://github.com/Howquez/GMTV/tree/July21Replication/analysis/R).^[bit.ly/3Pnak5H.
+Furthermore, I pre-registered the exact analyses I planned to run (PAP) when I designed the experiment on [GitHub](https://github.com/Howquez/GMTV/tree/July21Replication/analysis/R).^[bit.ly/3Pnak5H.
 To run the code, you need to execute the .Rmd files in this repository in the order that is indicated by file names.
@@
 
-At second glance, the analysis that made the most sense after having collected the data and that is reported here is a little different though: Because the more representative subject pool was exhausted earlier than expected, I recruited students which opened up a new research direction: assessing generalizability.
+At second glance, the analysis that made the most sense after having collected the data and that is reported here is a little different though: Because the more representative subject pool was exhausted earlier than anticipated, I recruited students which opened up a new research direction: assessing generalizability.
 Hence, this article combines both confirmatory as well as exploratory research.
 
-Accordingly, I edited many of the analysis scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/GMTV/blob/main/analysis/article/paper.qmd): https://bit.ly/43LCyLw] However, because the originally planned analysis code is archived and reproducible, these changes are transparent.
+Accordingly, I edited many of the analysis scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/GMTV/blob/main/analysis/article/paper.qmd): https://bit.ly/43LCyLw] However, because the originally planned analysis code is archived and reproducieable, these changes are transparent.
 Importantly, I followed a literate programming approach [@Knuth_1984; @AkhtarYe_2023].
@@
 The pure reproduction re-analyzes the original data.
-[Appendix A](#A:-Pure-Replication) documents [the errors I identified]() in the original paper.
+[Appendix A](#A:-Pure-Replication) documents [the errors I identified]() within the original paper.
 The scientific reproduction, where I utilize a different sample drawn from a different population in a different situation, is described in the following sections.
@@
 
-Like GMTV I employ a real giving task after the abstract game.
+In the same stroke as GMTV I employ a real giving task after the abstract game.
 Specifically, I employed a (charitable) dictator game where each participant is a dictator dividing her budget between herself and some organization.
@@
 Throughout this paper, I will compare the results of my experiment with the results of GMTVs' NOPUNISH 10 Period treatments.
-I am thus, referring to three different samples utilized at two points in time: the University of Nottingham's students (in late 2012), Hamburg's citizens, and the University of Hamburg's students (both in July 2021).
+I am thus, referring to three different samples utilized at two different points in time: the University of Nottingham's students (in late 2012), Hamburg's citizens, and the University of Hamburg's students (both in July 2021).
 @tbl-sample-properties gives an overview.
@@
 Its [Bootstrap](https://getbootstrap.com/) (a powerful frontend toolkit) integration allowed me to make the graphical user interface interactive, appealing, and easy to navigate.
-The [Highcharts library](https://www.highcharts.com/) made it easy to visualize results and communicate dynamics.
+The [Highcharts library](https://www.highcharts.com/) additionally made it easy to visualize results and communicate dynamics.
 Insofar, oTree served as a good tool to enhance the participants' user experience and thus, to make dropouts less likely.
@@
 First, participants had to be matched to form a group _after_ comprehension questions were answered successfully.
-Importantly, participants were grouped by the order they answered these questions to reduce waiting times.
+Importantly, participants were grouped according to the order they answered these questions to reduce waiting times.
 While waiting for other players to form the group, the participants saw a wait-page informing them that they are waiting for other participants to arrive and that they do not have to wait for longer than 10 minutes.
@@
 
-While I stuck to GMTVs' protocol as close as possible, I deviated in a few aspects.
+Overall, I stuck to GMTVs' protocol as close as possible, however, I deviated in a few aspects.
 First, the instructions were German and also covered topics inherent to the online setting (dropouts and bots, for instance).
@@
 
-The experiment lasted around `r total_completion_time` minutes on average.
+The experiment lasted on average for around `r total_completion_time` minutes.
 The earnings  averaged `r earningsMean %>% round(digits = 2)` Euros (sd = `r earningsSD  %>% round(digits = 2)`).^[This value include earnings from the incentivized risk elicitation task that is not part of the analysis.]
@@
 In particular, do the two samples' contributions follow the same path over the 10 periods they played?
-The answer is _yes and no_.
+The answer is both _yes and no_.
 @fig-share-of-contributions and @tbl-contribution-periods illustrate that the samples make similar contributions at the beginning and the end of the game but behave differently in between.
@@
 Note that increasing contributions over time imply increasing endowments over time.
-Hence, absolute contributions do not tell much about the willingness to cooperate.
+Hence, absolute contributions do not say much about the willingness to cooperate.
 For this reason, the right panel in @fig-share-of-contributions shows the average _share of endowments contributed_ over time.
-Both samples exhibit a similar pattern: their share of endowments contributed declined and did not stabilize.
+Both samples exhibit a similar pattern: Their share of endowments contributed declined and did not stabilize.
 However, both samples also differ with respect to one aspect: the reproduction sample's share of contributions declines faster.
@@
 
-This is remarkable given the different sample and language, the different software and user interface as well as the online setting during the COVID-19 pandemic.
+This finding is remarkable given the different sample and language, the different software and user interface as well as the online setting during the COVID-19 pandemic.
 The result suggests that by and large, the sum of these factors did not affect people’s preferences towards cooperation.
@@
 I first comment on the selection into the experiment: It was difficult to recruit the sample.
-The panel counted 1.209 non-students of which I was able to recruit `r main[student == FALSE, .N]` participants who finished the experiment---even though I varied the weekdays and timing of the sessions (which were conducted during a nationwide lockdown with home office regime).
+The panel counted 1.209 non-students of which I was able to recruit `r main[student == FALSE, .N]` participants who finished the experiment---even though I varied the weekdays and timing of the sessions (which were conducted during a nationwide lockdown under mandatory home office regime).
 For this reason, I also recruited students in the last session which explains the relatively large number of showups in @tbl-meta.
@@
 In contrast, all of the dropouts left while reading the instructions and before being matched to other group members.
-Moreover, they got no payment at all.
+Moreover, they received no payment at all.
 Hence, attrition was no concern considering the dynamic public goods game or the expenses.
@@
           intercept.bottom = TRUE,
-          order = c(1, 2, 6, 3, 4, 5),
+          order = c(1, 2, 5, 3, 4),
           covariate.labels = c("First-period contribution in percent", "Student (1 = yes)", "First-period contr. x Student", "Age", "Female (1 = yes)", "Risk Aversion (1-12)"),
@@
 I gratefully acknowledge support by the German Research Foundation (DFG) under Germany’s Excellence Strategy, cluster EXC 2037 “Climate, Climatic Change, and Society” (project 390683824).
-I thank Stefan Traub, whoever proofreads this and the participants of the CLICCS B5 group for helpful discussions.
+I thank Stefan Traub, Alexandrea Swanson, and the participants of the CLICCS B5 group for helpful discussions.
 

### 2023-07-04 analysis/article/paper.tex
repair table lables & some writing

@@
   pdfkeywords={Public goods, Dynamic
-games, Reproducibility, Generalizability, Online Experiment, Climate
+games, Reproducibility, Generalizability, Online experiment, Climate
 change mitigation},
@@
 games \sep Reproducibility \sep Generalizability \sep Online
-Experiment \sep 
+experiment \sep 
     Climate change mitigation
 \end{keyword}
-\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced, interior hidden, boxrule=0pt]}{\end{tcolorbox}}\fi
+\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, sharp corners, frame hidden, interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, enhanced]}{\end{tcolorbox}}\fi
 
@@
 current decisions affect future outcomes and with it, future decision
-spaces. Opting for environmentally friendly policies today not only
-reduces carbon dioxide emissions immediately but also helps us to reach
-the Paris climate targets tomorrow. Deferring these policies, may not
-necessarily prevent us from reaching these targets, but it requires more
-effort in the future compared to a path that includes immediate action
-\citep{HaenselEtAl2022}. Aiming at certain goals, today's actions (or
-the omission thereof) not only affect intermediate outcomes but also the
-number of paths one can choose from that lead to that specific goal.
+spaces. For example, opting for environmentally friendly policies today
+not only reduces carbon dioxide emissions immediately, but also helps us
+reach the Paris climate targets tomorrow. Deferring these policies to a
+later state, may not necessarily prevent us from reaching these targets,
+but it will require more effort in the future compared to a path which
+includes immediate action \citep{HaenselEtAl2022}. Aiming at certain
+goals, today's actions (or the omission thereof) not only affect
+intermediate outcomes but also the number of viable paths one can choose
+from that lead to that specific goal.
 
@@
 climate policies
-\citep[e.g.][]{MilinskiEtAl2006, TavoniEtAl2011, Hauser2014, BrickEtAl2015, GomezEtAl2018, CalzolariEtAl2018, CookEtAl2019}---miss
-these temporal interdependencies simply because participants have the
-same set of actions in each period. Accordingly, participants' actions
-in a given period do not affect their action space in subsequent
-periods. To see the lack of realism, consider carbon dioxide emissions,
-where the current stock will last for well over a millennium
+\citep[e.g.][]{MilinskiEtAl2006, TavoniEtAl2011, Hauser2014, BrickEtAl2015, GomezEtAl2018, CalzolariEtAl2018, CookEtAl2019}---fail
+to include these temporal interdependencies simply because participants
+have the same set of actions in each period. Accordingly, participants'
+actions in a given period do not affect their action space in subsequent
+periods. To better capture the lack of realism, consider carbon dioxide
+emissions, where the current stock will last for well over a millennium
 \citep{Inman2008, CalzolariEtAl2018}. Playing with fresh endowments in
@@
 hereafter, GMTV]{GMTV2017} as well as Stefan Große (unpublished), shows
-that it is fairly simple to add this element of realism. They
+that it is relatively simple to include this element of realism. They
 incorporate interdependencies into a \emph{dynamic} public goods game
@@
 
-Because there is surprisingly little experimental research on
+As there is surprisingly little experimental research on
 interdependencies\footnote{See e.g. \citet{BattagliniEtAl2016},
@@
 public goods games do not generalize well to real-world climate action.
-They also find that generalizability depends on the structural
+They also find that generalizability is dependent on the structural
 resemblance of the public goods game with the context of climate change
@@
 interdependencies---one would expect it to be better suited to inform
-public policy. To test this intuition, I not only ran the experiment
-with different samples but also observed the participants' behavior in
-voluntary climate actions (VCA).\footnote{The VCA is a (charitable)
-  dictator game where each participant is a dictator dividing her budget
-  between herself and some organization linked to the reduction of CO2
-  emissions. \citet{EckelGrossman1996} were the first to implement a
-  charitable dictator game observing contributions of 30\% of the
-  endowments. Like \citet{GKLS2020}, \citet{CarpenterEtAl2008} report
-  that students make lower contributions to charity than community
-  members.} This yielded a setting similar to the one of
-\citet{GKLS2020}, which allows me to analyze how behavior in the
-abstract game translates into real-world action across samples. This
-research shows that the dynamic setting \emph{does not} add any advances
-to the generalizability of results.
+public policy. As means to test this intuition, I not only ran the
+experiment with different samples but also observed the participants'
+behavior in voluntary climate actions (VCA).\footnote{The VCA is a
+  (charitable) dictator game where each participant is a dictator
+  dividing her budget between herself and some organization linked to
+  the reduction of CO2 emissions. \citet{EckelGrossman1996} were the
+  first to implement a charitable dictator game observing contributions
+  of 30\% of the endowments. Like \citet{GKLS2020},
+  \citet{CarpenterEtAl2008} report that students make lower
+  contributions to charity than community members.} This yielded a
+setting similar to the one of \citet{GKLS2020}, which allows me to
+analyze how behavior in the abstract game translates into real-world
+action across samples. This research shows that the dynamic setting
+\emph{does not} add any advances to the generalizability of results.
 
@@
 by more inattentiveness in online samples
-\citep{ArecharRand2021, PeytonEtAl2022}. This required me to design
-robust (and thus, more complex) software to minimize attrition. I
-collected para data \citep[ p.~12]{Parsons2022}---which capture screen
-time and survey navigation, for instance---to assess the desired fluency
-and feasibility of the experiment. Like \citet{AGM2018}, this research
-is of practical relevance as it reports on the robust design that made
-the dynamic game feasible.
+\citep{ArecharRand2021, PeytonEtAl2022}. With this background in mind,
+it required me to design robust (and thus, more complex) software to
+minimize attrition. I collected para data \citep[
+p.~12]{Parsons2022}---which capture screen time and survey navigation,
+for instance---to assess the desired fluency and feasibility of the
+experiment. Like \citet{AGM2018}, this research is of practical
+relevance as it reports on the robust design that made the dynamic game
+feasible.
 
@@
 
-Now, 20 years later, we accustom ourselves to mechanisms designed to
-unravel the fuzzy back-and-forth between exploratory and confirmatory
-research. Prominently, pre-registrations and pre-analysis plans (PAP)
-\citep[see, e.g.,][]{BrodeurEtAl2022} were established to tie the
-researchers' hands with respect to p-hacking and ex-post theorizing when
-doing confirmatory research---reducing observable discrepancies between
-Daryl Bem's above-mentioned (a) and (b).
+Today, 20 years later, we have accustomed ourselves to mechanisms
+designed to unravel the fuzzy back-and-forth between exploratory and
+confirmatory research. Prominently, pre-registrations and pre-analysis
+plans (PAP) \citep[see, e.g.,][]{BrodeurEtAl2022} were established as a
+means to tie the researchers' hands with respect to p-hacking and
+ex-post theorizing when doing confirmatory research---reducing
+observable discrepancies between Daryl Bem's above-mentioned (a) and
+(b).
 
@@
 are at least two ways to approach that problem: First, one could (and
-should) add unforeseen analyses to the article but label them as
-exploratory. Second, one could write a minimal pre-registration leaving
-enough degrees of freedom for the researcher to incorporate such
+should) add unforeseen analyses to the article but be sure to label them
+as exploratory. Second, one could write a minimal pre-registration
+leaving enough degrees of freedom for the researcher to incorporate such
 surprises without further notice. The key difference between the two
@@
 with minimal effort and maximum flexibility, the label itself may run
-into danger to become worthless and to miss the target of making science
-more credible.
+into danger by becomming worthless and to missing the target of making
+science more credible.
 
@@
 easier for others to track and understand a researcher's reaction to
-surprises in the data, which, in turn, gives the researcher more
-flexibility to react to these surprises. As additional transparency is
+surprises within the data, which, in turn, gives the researcher more
+flexibility to react to said surprises. As additional transparency is
 associated with additional effort, I propose version control as a
@@
 files are stored consistently and that changes are tracked. When these
-systems are implemented in the whole research process, one can archive
-different states of the software and visualize differences between
-different states. For instance, one can archive the analysis before and
-after the data was collected or the experimental software used in a
-pilot and the eventual experiment. Importantly, one can keep projects
-private and change their visibility to public only after the
+systems are implemented throughout the entire research process, one can
+archive different states of the software and visualize differences
+between different states. For instance, one can archive the analysis
+before and after the data was collected or the experimental software
+used in a pilot and the eventual experiment. Importantly, one can keep
+projects private and change their visibility to public only after the
 corresponding article is accepted for publication. Taken together, these
 features \emph{automatically} enhance transparency and facilitate
-scrutiny, policing, and forensics whilst also making software
-development and collaboration more efficient. As a consequence, the
-implementation and eventual disclosure of version control come not only
-with meta-scientific but also with organizational benefits.
+scrutiny, policing, and forensics whilst making software development and
+collaboration more efficient. As a consequence, the implementation and
+eventual disclosure of version control come not only with
+meta-scientific but also with organizational benefits.
 
@@
 pre-registered in the American Economic Association's RCT Registry
-\citep{preregistration}. Further, I pre-registered the exact analyses I
-planned to run (PAP) when I designed the experiment on
+\citep{preregistration}. Furthermore, I pre-registered the exact
+analyses I planned to run (PAP) when I designed the experiment on
 \href{https://github.com/Howquez/GMTV/tree/July21Replication/analysis/R}{GitHub}.\footnote{bit.ly/3Pnak5H.
@@
 though: Because the more representative subject pool was exhausted
-earlier than expected, I recruited students which opened up a new
+earlier than anticipated, I recruited students which opened up a new
 research direction: assessing generalizability. Hence, this article
@@
   https://bit.ly/43LCyLw} However, because the originally planned
-analysis code is archived and reproducible, these changes are
+analysis code is archived and reproducieable, these changes are
 transparent. Importantly, I followed a literate programming approach
@@
 \protect\hyperlink{A:-Pure-Replication}{Appendix A} documents
-\href{}{the errors I identified} in the original paper. The scientific
-reproduction, where I utilize a different sample drawn from a different
-population in a different situation, is described in the following
-sections.
+\href{}{the errors I identified} within the original paper. The
+scientific reproduction, where I utilize a different sample drawn from a
+different population in a different situation, is described in the
+following sections.
 
@@
 
-Like GMTV I employ a real giving task after the abstract game.
-Specifically, I employed a (charitable) dictator game where each
-participant is a dictator dividing her budget between herself and some
-organization. Whereas GMTV chose \emph{Doctors without Borders} as a
-receiver, I chose another organization in another context: like
+In the same stroke as GMTV I employ a real giving task after the
+abstract game. Specifically, I employed a (charitable) dictator game
+where each participant is a dictator dividing her budget between herself
+and some organization. Whereas GMTV chose \emph{Doctors without Borders}
+as a receiver, I chose another organization in another context: like
 \citet{GKLS2020}, I employed a VCA, where participants could donate any
@@
 the results of GMTVs' NOPUNISH 10 Period treatments. I am thus,
-referring to three different samples utilized at two points in time: the
-University of Nottingham's students (in late 2012), Hamburg's citizens,
-and the University of Hamburg's students (both in July 2021).
+referring to three different samples utilized at two different points in
+time: the University of Nottingham's students (in late 2012), Hamburg's
+citizens, and the University of Hamburg's students (both in July 2021).
 Table~\ref{tbl-sample-properties} gives an overview.
@@
 interactive, appealing, and easy to navigate. The
-\href{https://www.highcharts.com/}{Highcharts library} made it easy to
-visualize results and communicate dynamics. Insofar, oTree served as a
-good tool to enhance the participants' user experience and thus, to make
-dropouts less likely.
+\href{https://www.highcharts.com/}{Highcharts library} additionally made
+it easy to visualize results and communicate dynamics. Insofar, oTree
+served as a good tool to enhance the participants' user experience and
+thus, to make dropouts less likely.
 
@@
 to be matched to form a group \emph{after} comprehension questions were
-answered successfully. Importantly, participants were grouped by the
-order they answered these questions to reduce waiting times. While
-waiting for other players to form the group, the participants saw a
-wait-page informing them that they are waiting for other participants to
-arrive and that they do not have to wait for longer than 10 minutes. The
-screen also informed them that they would receive a \emph{patience
+answered successfully. Importantly, participants were grouped according
+to the order they answered these questions to reduce waiting times.
+While waiting for other players to form the group, the participants saw
+a wait-page informing them that they are waiting for other participants
+to arrive and that they do not have to wait for longer than 10 minutes.
+The screen also informed them that they would receive a \emph{patience
 bonus} of one Euro after the expiration of that time (or what was left
@@
 
-While I stuck to GMTVs' protocol as close as possible, I deviated in a
-few aspects. First, the instructions were German and also covered topics
-inherent to the online setting (dropouts and bots, for instance).
-Second, I used another software (oTree instead of zTree) which also
-affected the graphical user interface participants were exposed to.
-Third, GMTV gave participants the opportunity to donate to \emph{Doctors
-without Borders} whereas I offered carbon dioxide offsets.
-
-The experiment lasted around 25 minutes on average. The earnings
+Overall, I stuck to GMTVs' protocol as close as possible, however, I
+deviated in a few aspects. First, the instructions were German and also
+covered topics inherent to the online setting (dropouts and bots, for
+instance). Second, I used another software (oTree instead of zTree)
+which also affected the graphical user interface participants were
+exposed to. Third, GMTV gave participants the opportunity to donate to
+\emph{Doctors without Borders} whereas I offered carbon dioxide offsets.
+
+The experiment lasted on average for around 25 minutes. The earnings
 averaged 11.23 Euros (sd = 4.85).\footnote{This value include earnings
@@
 In particular, do the two samples' contributions follow the same path
-over the 10 periods they played? The answer is \emph{yes and no}.
+over the 10 periods they played? The answer is both \emph{yes and no}.
 Figure~\ref{fig-share-of-contributions} and
@@
 Note that increasing contributions over time imply increasing endowments
-over time. Hence, absolute contributions do not tell much about the
+over time. Hence, absolute contributions do not say much about the
 willingness to cooperate. For this reason, the right panel in
@@
 endowments contributed} over time. Both samples exhibit a similar
-pattern: their share of endowments contributed declined and did not
+pattern: Their share of endowments contributed declined and did not
 stabilize. However, both samples also differ with respect to one aspect:
@@
 
-This is remarkable given the different sample and language, the
+This finding is remarkable given the different sample and language, the
 different software and user interface as well as the online setting
@@
 though I varied the weekdays and timing of the sessions (which were
-conducted during a nationwide lockdown with home office regime). For
-this reason, I also recruited students in the last session which
-explains the relatively large number of showups in Table~\ref{tbl-meta}.
-Although I intended to refrain from the recruitment of students
-initially, this particular sub-sample enabled me to investigate the
-generalizability of my results as I will discuss in
+conducted during a nationwide lockdown under mandatory home office
+regime). For this reason, I also recruited students in the last session
+which explains the relatively large number of showups in
+Table~\ref{tbl-meta}. Although I intended to refrain from the
+recruitment of students initially, this particular sub-sample enabled me
+to investigate the generalizability of my results as I will discuss in
 Section~\ref{sec-generalizability}.
@@
 contrast, all of the dropouts left while reading the instructions and
-before being matched to other group members. Moreover, they got no
+before being matched to other group members. Moreover, they received no
 payment at all. Hence, attrition was no concern considering the dynamic
@@
   & & & \\ 
- First-period contr. x Student & 4.00$^{***}$ & 3.96$^{***}$ & 3.94$^{***}$ \\ 
-  & (0.11) & (0.11) & (0.11) \\ 
+ First-period contr. x Student &  & 0.46 & 0.50 \\ 
+  &  & (0.34) & (0.34) \\ 
   & & & \\ 
@@
   & & & \\ 
- Risk Aversion (1-12) &  & 0.46 & 0.50 \\ 
-  &  & (0.34) & (0.34) \\ 
+ Risk Aversion (1-12) & 4.00$^{***}$ & 3.96$^{***}$ & 3.94$^{***}$ \\ 
+  & (0.11) & (0.11) & (0.11) \\ 
   & & & \\ 
@@
 Climatic Change, and Society'' (project 390683824). I thank Stefan
-Traub, whoever proofreads this and the participants of the CLICCS B5
-group for helpful discussions.
+Traub, Alexandrea Swanson, and the participants of the CLICCS B5 group
+for helpful discussions.
 

### 2024-02-07 analysis/article/paper.qmd
update Paper for OSF Preprint Submission

@@
   - name: Hauke Roggenkamp
-    email: hauke.roggenkamp@unisg.ch
+    email: Hauke.Roggenkamp@unisg.ch
+    orcid: 0009-0005-5176-4718
     affiliations:
@@
           postal-code: 9000
-    # attributes:
-    #     corresponding: true
-    # note: This is the first author footnote.
 abstract: |
@@
 
-```{r packages}
-# install this package once, it'll then install and load all remaining packages
-# install.packages("pacman")
-
-pacman::p_load(magrittr, data.table, stringr, lubridate, glue, haven, DescTools, censReg, stargazer, vtable, ggplot2, patchwork, Rmisc, knitr, rang)
-```
-
-```{r system_requirements}
-#| eval: false
-packages <- pacman::p_loaded()
-
-graph <- rang::resolve(pkgs = packages,
-                       snapshot_date = '2023-06-14')
-
-export_rang(graph, '../requirements/article.R')
-save(graph, file = '../requirements/article.rda')
+```{r}
+#| warning: false
+
+if (!requireNamespace("groundhog", quietly = TRUE)) {
+    install.packages("groundhog")
+    library("groundhog")
+}
+
+pkgs <- c("magrittr", "data.table", "stringr", "lubridate", "glue", "haven",
+          "DescTools", "censReg", "stargazer", "vtable", "ggplot2",
+          "patchwork", "Rmisc", "knitr")
+
+groundhog::groundhog.library(pkg = pkgs,
+                             date = "2024-01-01")
+
+rm(pkgs)
 ```
@@
           order = c(1, 2, 5, 3, 4),
-          covariate.labels = c("First-period contribution in percent", "Student (1 = yes)", "First-period contr. x Student", "Age", "Female (1 = yes)", "Risk Aversion (1-12)"),
+          covariate.labels = c("First-period contribution in percent", "Student (1 = yes)", "First-period contr. x Student", "Age", "Female (1 = yes)"),
           type = "latex", digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE

### 2024-02-07 analysis/article/paper.tex
update Paper for OSF Preprint Submission

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else  
+    % xetex/luatex font selection
 \fi
@@
 \makeatletter
-\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
+\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
 \makeatother
@@
 \@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
+\makeatother
+\makeatletter
 \makeatother
@@
 }
- \ead{hauke.roggenkamp@unisg.ch}
+ \ead{Hauke.Roggenkamp@unisg.ch}
 
@@
 \end{keyword}
-\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, sharp corners, frame hidden, interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, enhanced]}{\end{tcolorbox}}\fi
+\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, sharp corners, breakable, frame hidden, interior hidden, enhanced]}{\end{tcolorbox}}\fi
 
@@
 \hline
-Age & 52 & 48 & 15 & 64 & 26 & 7.6 & 92 & 33 & 2.6 & F$=88.98^{***}$ \\ 
+Age & 52 & 48 & 15 & 64 & 26 & 7.6 & 92 & 34 & 2.6 & F$=87.278^{***}$ \\ 
 Female & 52 & 0.48 & 0.5 & 64 & 0.56 & 0.5 & 92 & 0.38 & 0.49 & F$=2.596^{*}$ \\ 
@@
   & & & \\ 
- Risk Aversion (1-12) & 4.00$^{***}$ & 3.96$^{***}$ & 3.94$^{***}$ \\ 
+ logSigma & 4.00$^{***}$ & 3.96$^{***}$ & 3.94$^{***}$ \\ 
   & (0.11) & (0.11) & (0.11) \\ 
